### 2019-12-10 Paper/Outline_DB_Paper.tex
Added (not finished)  Outline of Paper

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{float}
\usepackage[table,xcdraw]{xcolor}
%\usepackage[sort&compress,square,comma,authoryear]{natbib}
\usepackage{booktabs}
\usepackage{graphicx}
\graphicspath{ {"/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures"} }
\usepackage{longtable}

\usepackage[
backend=biber,
style=authoryear,
sorting=nyt % sort by name year title
]{biblatex}
\addbibresource{Ref_invertebrate_DB.bib}

\title{ OUTLINE: Harmonized macroinvertebrate trait database, Aggregation of traits, Trait definitions, Sources }
\author{}%Stefan Kunz 
\date{}%June 2019

\begin{document}
%TODO: Use citep & citet instead of cite
\maketitle

\section{Introduction}

Intro: For what are traits used?
\\
\\
\\
Knowledge on macroinvertebrate traits $\rightarrow$ trait databases
\\
\\
\\
Goal: 
We harmonized information from different trait databases of four regions in the world,
namely: Australia, Europe, North America, and New Zealand. \\
\\
Studies that use information on aquatic invertebrate traits from different regions and/or aggregate trait information 
are increasing %! Change wording & State examples: Brown Paper
\\
\\
In this paper we examine difficulties that ecologists face when using different macroinvertebrate trait databases together. 
We explore the effect of different decisions researches have to make when working with trait data from several regions/sources, 
involving harmonization, handling different codings, normalization, and aggregation of traits. 
Therefore, we harmonized six traits from four trait databases and aggregated the trait information to family level. % ?Name Traits
Our paper also compares the references for the used trait information that were specified in the used trait databases. 
Finally, we present an overview of differences in trait definitions among databases.

That means: 
\begin{itemize}
    \item How to harmonize different trait databases when the task involves using 
    traits from different regions (e.g. for comparing trait profiles across regions) $\rightarrow$ Harmonization
    \item Thereby, we will examine differences in trait definitions
    \item Look on the sources of various trait databases 
    \item Furthermore, show effect of different ways of aggregating traits (inter alia Problem of different
     coding styles (fuzzy vs binary))
\end{itemize}

\section{Description of harmonized trait database} %TODO: Change heading to more expressive

% Mention restriction to certain orders
The harmonized database consists of the available information on aquatic invertebrate traits for the regions 
Europe, North America, Australia, and New Zealand and comprises the traits locomotion, feeding mode, respiration, voltinism, 
size, and body form. The pattern of development (holometabolous or hemimetabolous) was added as an additional trait 
based on the orders of the taxa included in each database. 
Traits for Europe were retrieved from the freshwaterecology trait database (\url{https://www.freshwaterecology.info/}) 
and complemented by information from Tachet (\cite{usseglio-polatera_biomonitoring_2000}). 
North American macroinvertebrate traits were taken from Laura Twardochleb and complemented by trait information from Viera (\cite{vieira_database_nodate}). 
% TODO: Insert citation
An overview of the used databases can be found in table \ref{tab:trait_databases}. \\ 
In the following paragraphs, we describe the data processing steps required to establish a harmonized 
macroinvertebrate trait database.

\begin{table}[H]
    \centering
    \caption{Overview of trait databases.}
    \label{tab:trait_databases}
    \begin{tabular}{lll}
    \toprule
   Region & Coding of trait states & Reference \\ 
    \hline
   Europe & Largely fuzzy & \cite{schmidt-kloiber_www.freshwaterecology.info_2015}\\ 
   Central Europe & Fuzzy coded & \cite{usseglio-polatera_biomonitoring_2000} \\ 
   North America & Largely binary & \cite{vieira_database_nodate}\\
   North America & Largely binary & cite Laura Twardochleb \\
   Australia & Binary \& fuzzy coding  & \cite{kefford_ben_AST_DB_2019}\\ 
   New Zealand & Fuzzy coded & \\ %TODO: Create entry for more recent NZ reference
    \bottomrule
    \end{tabular}
\end{table}

\section{Harmonization of traits}

\begin{itemize}
    \item Harmonization process: See also Schmera 2015 et al 
    \item Differences in trait definitions
    \item Sources of traits
\end{itemize}

\section{Aggregation of traits}

\begin{itemize}
    \item Describing \& testing different approaches
    \item Problem of coding of traits
\end{itemize}

\section*{Additional ideas}

Section Description of databases:
\begin{itemize}
    \item Describe different databases briefly?
    \item State goal of analysis $\rightarrow$ reference to second paper?
\end{itemize}

\end{document}

### 2019-12-10 Paper/__latexindent_temp.tex
Added (not finished)  Outline of Paper

--- 2019-12-10 Paper/Outline_DB_Paper.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
-\usepackage{hyperref}
-\usepackage{float}
-\usepackage[table,xcdraw]{xcolor}
-%\usepackage[sort&compress,square,comma,authoryear]{natbib}
-\usepackage{booktabs}
-\usepackage{graphicx}
-\graphicspath{ {"/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures"} }
-\usepackage{longtable}
+\begin{itemize}
+    \item Usage trait databases: 
+    \begin{itemize}
+    \item
 
-\usepackage[
-backend=biber,
-style=authoryear,
-sorting=nyt % sort by name year title
-]{biblatex}
-\addbibresource{Ref_invertebrate_DB.bib}
-
-\title{ OUTLINE: Harmonized macroinvertebrate trait database, Aggregation of traits, Trait definitions, Sources }
-\author{}%Stefan Kunz 
-\date{}%June 2019
-
-\begin{document}
-%TODO: Use citep & citet instead of cite
-\maketitle
-
-\section{Introduction}
-
-Intro: For what are traits used?
-\\
-\\
-\\
-Knowledge on macroinvertebrate traits $\rightarrow$ trait databases
-\\
-\\
-\\
-Goal: 
-We harmonized information from different trait databases of four regions in the world,
-namely: Australia, Europe, North America, and New Zealand. \\
-\\
-Studies that use information on aquatic invertebrate traits from different regions and/or aggregate trait information 
-are increasing %! Change wording & State examples: Brown Paper
-\\
-\\
-In this paper we examine difficulties that ecologists face when using different macroinvertebrate trait databases together. 
-We explore the effect of different decisions researches have to make when working with trait data from several regions/sources, 
-involving harmonization, handling different codings, normalization, and aggregation of traits. 
-Therefore, we harmonized six traits from four trait databases and aggregated the trait information to family level. % ?Name Traits
-Our paper also compares the references for the used trait information that were specified in the used trait databases. 
-Finally, we present an overview of differences in trait definitions among databases.
-
-That means: 
-\begin{itemize}
-    \item How to harmonize different trait databases when the task involves using 
-    traits from different regions (e.g. for comparing trait profiles across regions) $\rightarrow$ Harmonization
-    \item Thereby, we will examine differences in trait definitions
-    \item Look on the sources of various trait databases 
-    \item Furthermore, show effect of different ways of aggregating traits (inter alia Problem of different
-     coding styles (fuzzy vs binary))
     \end{itemize}
-
-\section{Description of harmonized trait database} %TODO: Change heading to more expressive
-
-% Mention restriction to certain orders
-The harmonized database consists of the available information on aquatic invertebrate traits for the regions 
-Europe, North America, Australia, and New Zealand and comprises the traits locomotion, feeding mode, respiration, voltinism, 
-size, and body form. The pattern of development (holometabolous or hemimetabolous) was added as an additional trait 
-based on the orders of the taxa included in each database. 
-Traits for Europe were retrieved from the freshwaterecology trait database (\url{https://www.freshwaterecology.info/}) 
-and complemented by information from Tachet (\cite{usseglio-polatera_biomonitoring_2000}). 
-North American macroinvertebrate traits were taken from Laura Twardochleb and complemented by trait information from Viera (\cite{vieira_database_nodate}). 
-% TODO: Insert citation
-An overview of the used databases can be found in table \ref{tab:trait_databases}. \\ 
-In the following paragraphs, we describe the data processing steps required to establish a harmonized 
-macroinvertebrate trait database.
-
-\begin{table}[H]
-    \centering
-    \caption{Overview of trait databases.}
-    \label{tab:trait_databases}
-    \begin{tabular}{lll}
-    \toprule
-   Region & Coding of trait states & Reference \\ 
-    \hline
-   Europe & Largely fuzzy & \cite{schmidt-kloiber_www.freshwaterecology.info_2015}\\ 
-   Central Europe & Fuzzy coded & \cite{usseglio-polatera_biomonitoring_2000} \\ 
-   North America & Largely binary & \cite{vieira_database_nodate}\\
-   North America & Largely binary & cite Laura Twardochleb \\
-   Australia & Binary \& fuzzy coding  & \cite{kefford_ben_AST_DB_2019}\\ 
-   New Zealand & Fuzzy coded & \\ %TODO: Create entry for more recent NZ reference
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-\section{Harmonization of traits}
-
-\begin{itemize}
-    \item Harmonization process: See also Schmera 2015 et al 
-    \item Differences in trait definitions
-    \item Sources of traits
 \end{itemize}
-
-\section{Aggregation of traits}
-
-\begin{itemize}
-    \item Describing \& testing different approaches
-    \item Problem of coding of traits
-\end{itemize}
-
-\section*{Additional ideas}
-
-Section Description of databases:
-\begin{itemize}
-    \item Describe different databases briefly?
-    \item State goal of analysis $\rightarrow$ reference to second paper?
-\end{itemize}
-
-\end{document}

### 2020-01-07 R/02_AUS_harmonize_traits.R
Fixed feeding mode and size harmonization

@@ -134,7 +134,8 @@ Trait_AUS[, feed_predator := apply(.SD, 1, max),
                       "feed_predator",
                       "Trop_predator_botwe",
                       "Predator_proportion_of_feeding_fam_Chessman2017",
-                      "Predator_proportion_of_feeding_genus_Chessman2017")]
+                      "Predator_proportion_of_feeding_genus_Chessman2017",
+                      "Feeding_piercers_VicEPA")]
 Trait_AUS[, feed_parasite := apply(.SD, 1, max),
           .SDcols = c("feed_parasite",
                       "feed_parasite_Schaefer",
@@ -287,15 +288,15 @@ Trait_AUS[, c("Respiration_tegument_VicEPA",
 # size_large: size > 16 mm (EU: size > 20 mm)
 # _________________________________________________________________________ 
 Trait_AUS[, size_small := apply(.SD, 1, max), 
-          .SDcols = c("Max_size_less_than_5_VicEPA", 
+          .SDcols = c("Max_size_less_than_5_VicEPA",
+                      "Max_size_5_to_10_VicEPA",
                       "Size1_botwe",
                       "size_small", 
                       "size_small_Schaefer",
                       "size_small_fam_Chessman",
                       "size_small_genus_Chessman")]
 Trait_AUS[, size_medium := apply(.SD, 1, max), 
-          .SDcols = c("Max_size_5_to_10_VicEPA", 
-                      "Max_size_10_to_20_VicEPA",
+          .SDcols = c("Max_size_10_to_20_VicEPA",
                       "Size2_botwe",
                       "size_medium", 
                       "size_medium_Schaefer",

### 2020-01-07 R/05_NOA_NEW_harmonize_traits.R
Fixed locom crawl

@@ -59,10 +59,10 @@ Trait_Noa_new[, locom_swim := apply(.SD, 1, max),
                       "Habit_prim_Skater")]
 # Crawler 
 Trait_Noa_new[, locom_crawl := apply(.SD, 1, max),
-          .SDcols = c("Habit_prim_Sprawler",
+          .SDcols = c("Habit_prim_Crawler",
+                      "Habit_prim_Sprawler",
                       "Habit_prim_Climber",
                       "Habit_prim_Clinger")]
-
 # _________________________________________________________________________
 #### Size ####
 # specifically: Maximum body size

### 2020-01-07 R/Ratio_fam_agg_init.R
Added comparison of family number initial dataset and aggregated

@@ -1,0 +1,101 @@
+# How many families end up in the final
+# aggregated trait datasets compared to the initial
+# (not aggregated) trait datasets?
+# This gives us insight how much and how consistent
+# information is covered in these trait databases
+
+
+# _______________________________________________
+#### Load initial & aggregated final dataset ####
+# _______________________________________________
+
+# initial datasets
+files_init <- dir(data_cleaned,
+  recursive = TRUE,
+  full.names = TRUE,
+  pattern = "harmonized"
+)
+
+# create list with initial datasets
+datasets_init <- lapply(files_init, readRDS)
+
+# get file names
+file_names <- sub("(\\/.*)(\\/.*)(\\/)(.*)(\\.rds)", "\\4", files_init)
+
+# assign names to list
+for (i in seq_along(file_names)) {
+  names(datasets_init)[[i]] <- file_names[[i]]
+}
+
+EU_init <- datasets_init[c(".Trait_EU_pp_harmonized", ".Trait_Tachet_pp_harmonized")]
+NOA_init <- datasets_init[c(".Trait_US_LauraT_pp_harmonized", "Trait_US_pp_harmonized")]
+
+# TODO: Check Zeallot
+# c(AUS_init, NZ_init) %<-% c(datasets_init$.Trait_AUS_harmonized,
+#                             datasets_init$.Trait_NZ_pp_harmonized)
+
+str(datasets_init$.Trait_AUS_harmonized)
+
+# aggregated datasets
+files_agg <- list.files(path = file.path(data_out), pattern = ".*\\.rds")
+datasets_agg <-
+  lapply(seq_along(files_agg), function(i)
+    readRDS(file.path(data_out, files_agg[[i]])))
+
+# assign names for each list element
+for (i in seq_along(files_agg)) {
+  names(datasets_agg)[[i]] <- files_agg[[i]]
+}
+
+# _______________________________________________
+#### Calcule coverage of families per region ####
+# _______________________________________________
+
+# aggregated datasets
+cov_agg <- rbindlist(lapply(datasets_agg, function(y) {
+  y[order %in% c(
+    "Ephemeroptera",
+    "Hemiptera",
+    "Odonata",
+    "Trichoptera",
+    "Coleoptera",
+    "Plecoptera",
+    "Diptera"
+  ), .(family, order)]
+}),
[…]

### 2020-01-07 R/Categories_per_region.R
Added categories per region skript

@@ -1,0 +1,175 @@
+# EU
+Trait_EU <- readRDS(file.path(data_cleaned, "EU", "Trait_Freshecol_pp.rds"))
+
+# Tachet
+tachet <-  fread(file.path(data_in, "EU", "Tachet_mod_S.csv"))
+
+# AUS
+Trait_AUS <- readRDS(
+  file = file.path(
+    data_cleaned,
+    "Australia",
+    "Trait_AUS_preproc.rds"
+  )
+)
+
+# NZ
+Trait_NZ <- readRDS(file.path(data_cleaned, "NZ", "Trait_NZ_taxa_pp.rds"))
+
+# NOA new (Laura Twardochleb)
+Trait_Noa_new <- readRDS(file = file.path(data_cleaned, "North_America", "Traits_US_pp_LauraT.rds"))
+
+# NOA old (Vieira)
+Trait_Noa <- readRDS(file = file.path(data_cleaned, "North_America", "Traits_US_pp.rds"))
+
+# get categories for each trait per region and synthesize
+# function
+fun <- function(x, id.vars, region) {
+  x %>%
+    melt(., id.vars = id.vars) %>%
+    .[, .(Trait_state = unique(variable))] %>%
+    .[, .(
+      Trait = sub("\\_.*", "", Trait_state),
+      Trait_state
+    )] %>%
+    .[, .(Trait_state,
+      Trait,
+      Region = rep(region, nrow(.))
+    )]
+}
+
+# Freshwaterecology
+fun(
+  x = Trait_EU,
+  id.vars = c(
+    "order",
+    "family",
+    "genus",
+    "species"
+  ),
+  region = "EU_freshwaterecology"
+)
+
+# Tachet
+fun(
+  x = tachet,
+  id.vars = c(
+    "Group",
+    "Family",
+    "Subfamily",
+    "Genus",
+    "Species",
+    "Taxa"
+  ),
+  region = "EU_tachet"
+)
+
+# AUS
+fun(
+  x = Trait_AUS,
+  id.vars = c(
+    "unique_id",
+    "Order",
+    "Family",
+    "Genus",
+    "Species"
+  ),
+  region = "Australia"
+) %>%
+  .[grepl("(?i)Habi", Trait), ]
+
+
+# NZ
+# Needs some further preprocessing
+fun(
+  x = Trait_NZ,
+  id.vars = c(
+    "Taxon",
+    "Order",
+    "Family",
+    "Genus",
+    "Species"
+  ),
[…]

### 2020-01-07 Paper/Outline_DB_Paper.tex
update outline

@@
 \usepackage{graphicx}
-\graphicspath{ {"/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures"} }
+\graphicspath{{Figures/}}
 \usepackage{longtable}
@@
 
-Intro: For what are traits used?
-\\
-\\
-\\
+Intro: For what are traits used?\\
 Knowledge on macroinvertebrate traits $\rightarrow$ trait databases
@@
 \\
-Goal: 
-We harmonized information from different trait databases of four regions in the world,
-namely: Australia, Europe, North America, and New Zealand. \\
-\\
-Studies that use information on aquatic invertebrate traits from different regions and/or aggregate trait information 
-are increasing %! Change wording & State examples: Brown Paper
+Studies that use information on aquatic invertebrate traits from different regions
+and/or aggregate trait information are increasing %! Change wording & State examples: Brown Paper
 \\
 \\
-In this paper we examine difficulties that ecologists face when using different macroinvertebrate trait databases together. 
-We explore the effect of different decisions researches have to make when working with trait data from several regions/sources, 
-involving harmonization, handling different codings, normalization, and aggregation of traits. 
-Therefore, we harmonized six traits from four trait databases and aggregated the trait information to family level. % ?Name Traits
-Our paper also compares the references for the used trait information that were specified in the used trait databases. 
-Finally, we present an overview of differences in trait definitions among databases.
+\\
+%!Goal of our analysis:
+In this paper we examine difficulties that ecologists face when using 
+different macroinvertebrate trait databases together. We explore the 
+effect of different decisions researches have to make when working with
+trait data from several regions/sources, involving harmonization, 
+handling different codings, normalization, and aggregation of traits.
+\\
+\\
+\\
+%! Trait terminology
+%TODO: Apply unified terminology -> Use Schmera et al's suggestion?
 
-That means: 
-\begin{itemize}
-    \item How to harmonize different trait databases when the task involves using 
-    traits from different regions (e.g. for comparing trait profiles across regions) $\rightarrow$ Harmonization
-    \item Thereby, we will examine differences in trait definitions
-    \item Look on the sources of various trait databases 
-    \item Furthermore, show effect of different ways of aggregating traits (inter alia Problem of different
-     coding styles (fuzzy vs binary))
-\end{itemize}
+One of the problems in macroinvertebrate trait research is the use
+of inconsistent terminology across studies (but see \cite{schmera_proposed_2015}). 
+For example, some studies used the term "trait" to describe a general 
+organismal property like "generations per year" (\cite{statzner_reproductive_1997}, 
+\cite{ussegliopolatera_biological_2000}), while in other studies this 
+term was related to trait categories/states like "bi/multivoltine" 
+(\cite{haybach_use_2004}, \cite{vieira_database_nodate}). 
+Here, we follow the proposal of Schmera et al. (2015) and use the term 
+\textit{trait} for a morphological, physiological, or phenological 
+feature measurable at the individual organism (e.g. tegument, gills, etc.) 
+and the term \textit{grouping feature} to describe a general property 
+of related organismal traits (e.g. respiration).
+\\
+\\
+\\
+%!What we did:
+Therefore, we harmonized six grouping features from four trait databases and 
+aggregated the trait information to family level. % ?Name Traits
+We discuss the harmonization and show the effect of different ways of aggregating 
+traits (inter alia Problem of different coding styles (fuzzy vs binary)).
+We also present an overview of differences in trait definitions among databases.
+Finally, our paper compares the references for the trait information that 
+were specified in the trait databases we used.
 
-\section{Description of harmonized trait database} %TODO: Change heading to more expressive
+\section{Description of harmonized trait database} %TODO: Change heading to be more expressive
 
-% Mention restriction to certain orders
-The harmonized database consists of the available information on aquatic invertebrate traits for the regions 
-Europe, North America, Australia, and New Zealand and comprises the traits locomotion, feeding mode, respiration, voltinism, 
-size, and body form. The pattern of development (holometabolous or hemimetabolous) was added as an additional trait 
-based on the orders of the taxa included in each database. 
-Traits for Europe were retrieved from the freshwaterecology trait database (\url{https://www.freshwaterecology.info/}) 
-and complemented by information from Tachet (\cite{usseglio-polatera_biomonitoring_2000}). 
-North American macroinvertebrate traits were taken from Laura Twardochleb and complemented by trait information from Viera (\cite{vieira_database_nodate}). 
+% TODO Give a motivation (better in introduction?)
+The harmonized database consists of the available information on aquatic 
+insect traits for the regions Europe, North America, Australia, and New Zealand
+and comprises the grouping features locomotion, feeding mode, respiration, 
+voltinism, size, and body form. The pattern of development (holometabolous or hemimetabolous) 
+was added as an additional grouping feature based on the orders of the taxa 
+included in each database. 
+% TODO: Few words why these traits have been selected
+% TODO: Reasoning why no ecological traits have been used
+Trait information for Australia and New Zealand were retrieved from 
+single database. For Europe we gathered trait information from the 
+freshwaterecology trait database (\url{https://www.freshwaterecology.info/}) 
+and complemented missing information with the 
+Tachet trait database (\cite{usseglio-polatera_biomonitoring_2000}). 
+North American macroinvertebrate traits were retrievied from Laura Twardochleb and 
+complemented by trait information from Vieira et al (\cite{vieira_database_nodate}). 
+% TODO Mention restriction to certain orders
+We did not use the entire data on macroinvertebrates, 
+but limited our analysis to orders of aquatic insects that occurred in all used
+databases, specifically the orders:
+...
 % TODO: Insert citation
-An overview of the used databases can be found in table \ref{tab:trait_databases}. \\ 
-In the following paragraphs, we describe the data processing steps required to establish a harmonized 
-macroinvertebrate trait database.
+Table \ref{tab:trait_databases} gives an overview of the used databases. \\ 
+In the following paragraphs, we describe the data processing steps required to 
+establish a harmonized macroinvertebrate trait database.
 
@@
 
-\section{Harmonization of traits}
+\begin{itemize}
+    \item Various preprocessing steps: Taxonomical corrections; Range normalization [0-1] (e.g. in Australia); a few 
+    words about spreadsheets etc?
+    \item Harmonization 
+    \item (RowSum) Normalization/Standardization %!Wording
+    \item Aggregation of traits
+\end{itemize}
 
+\subsection{Harmonization of traits}
 \begin{itemize}
@@
 \end{itemize}
+
+% !What is harmonization? & Why is it needed?
+Harmonization of traits is the process of amalgamating several similar trait states
+into a single trait state. Harmonization has to be undertaken when e.g. traits from
+different sources (e.g. different regions) are compared and the traits have not
+the same trait states. %?Give an example -> Clusteranalysis
+\\
+\\
+\\
+% !How was the harmonization done? -> technical aspect.
+Traits that differed in their trait states among databases have been harmonised by 
+condensing the trait states for each trait in such a way that in the end the same 
+traits in all four databases consisted of the same trait states. 
+This meant reducing the trait states to the smallest number of trait states that
+occur for a particular trait among all databases. Thereby, trait states were 
+amalgamated based on ecological knowledge or expert judgment. %!Wording 
+Our approach of harmonizing the traits of the used databases is outlined in figures 
+\ref{fig:harmon_overview_1} and \ref{fig:harmon_overview_2}.
+
+\begin{figure}[H]
+   \centering
+   \includegraphics[width=16.5cm, height=10cm]{trait_overview1.jpg}
+   \caption{Proposed harmonization scheme for the grouping features
+   voltinism, feeding mode and locomotion. Shown are all traits for the 
+   used grouping features in the investigated trait databases and 
+   the harmonized traits in the end. Traits in curly brackets were 
+   harmonized to one trait. Traits highlighted in Grey were omitted. \newline
+   \textit{* Trait parasite was not available in New Zealand trait database.}
+   }
+   \label{fig:harmon_overview_1}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{trait_overview2.jpg}
+    \caption{Proposed harmonization scheme for the grouping features
+    respiration, size and body form.\newline
+    \textit{* Body form information provided by Philippe 
+    Usseglio-Polatera.}\newline
+    \textit{** Bluff(blocky) taxa have been reclassified
+    by Philippe Usseglio-Polatera using the traits streamlined,
+    flattened, cylindrical and spherical.} }
+    \label{fig:harmon_overview_2}
+ \end{figure}
 

### 2020-01-08 R/Set_up.R
Added zeallot

@@ -1,7 +1,7 @@
 # Set up script:
 # Loads required packages for Trait data cleaning & Harmonization
 # Loads scripts with used functions
-# Loads paths with location for data 
+# Loads paths with location for data
 
 # Data location
 data_in <- "./Data"
@@ -12,7 +12,7 @@ data_cleaned <- "./Cleaned_data"
 # Path for data to fill missing values
 data_missing <- "./Missing_data"
 
-# Path for output 
+# Path for output
 data_out <- "./Output"
 
 # Location for R scripts
@@ -25,6 +25,7 @@ library(readxl) # read in xlsx /xls files
 library(taxize) # retrieve taxonomical information
 library(Hmisc) # quick overview over data
 library(testthat) # unit testing
+library(zeallot) # %<-% assignment
 
 # source script with used functions
 source(file = file.path(data_scr, "functions_used_TDB.R"))

### 2020-01-08 R/Ratio_fam_agg_init.R
Completed calc ratio agg/init fam per dataset

@@ -3,7 +3,7 @@
 # (not aggregated) trait datasets?
 # This gives us insight how much and how consistent
 # information is covered in these trait databases
-
+# TODO: Identify missing families
 
 # _______________________________________________
 #### Load initial & aggregated final dataset ####
@@ -28,13 +28,9 @@ for (i in seq_along(file_names)) {
 }
 
 EU_init <- datasets_init[c(".Trait_EU_pp_harmonized", ".Trait_Tachet_pp_harmonized")]
-NOA_init <- datasets_init[c(".Trait_US_LauraT_pp_harmonized", "Trait_US_pp_harmonized")]
-
-# TODO: Check Zeallot
-# c(AUS_init, NZ_init) %<-% c(datasets_init$.Trait_AUS_harmonized,
-#                             datasets_init$.Trait_NZ_pp_harmonized)
-
-str(datasets_init$.Trait_AUS_harmonized)
+NOA_init <- datasets_init[c(".Traits_US_LauraT_pp_harmonized", ".Traits_US_pp_harmonized")]
+c(AUS_init, NZ_init) %<-% list(datasets_init$.Trait_AUS_harmonized,
+                            datasets_init$.Trait_NZ_pp_harmonized)
 
 # aggregated datasets
 files_agg <- list.files(path = file.path(data_out), pattern = ".*\\.rds")
@@ -67,7 +63,12 @@ idcol = "file"
 ) %>%
   .[, .(family, .N), by = .(file, order)]
 
-# EU
+#### EU ####
+# prepare aggregated data for EU
+cov_agg_EU <- cov_agg[grepl("Trait_EU.*", file), ] %>%
+  .[!duplicated(order), -("family")]
+
+# EU initial data
 cov_EU_init <- rbindlist(lapply(EU_init, function(y)
   y[order %in% c(
     "Ephemeroptera",
@@ -82,20 +83,122 @@ cov_EU_init <- rbindlist(lapply(EU_init, function(y)
   .[!duplicated(family), .(file, family, .N),
     by = order]
 
-cov_agg_EU <- cov_agg[grepl("Trait_EU.*", file), ] %>%
-  .[!duplicated(order), -("family")]
-
+# Calculate taxonomical coverage EU
 cov_agg_EU[cov_EU_init,
   `:=`(N_init = i.N),
   on = "order"
 ] %>%
-  .[, .(file,
-        order,
[…]

### 2020-03-05 Paper/Outline_DB_Paper.tex
Updata paper

@@
 
-Intro: For what are traits used?\\
-Knowledge on macroinvertebrate traits $\rightarrow$ trait databases
-\\
-\\
-\\
-Studies that use information on aquatic invertebrate traits from different regions
-and/or aggregate trait information are increasing %! Change wording & State examples: Brown Paper
-\\
-\\
-\\
-%!Goal of our analysis:
-In this paper we examine difficulties that ecologists face when using 
-different macroinvertebrate trait databases together. We explore the 
-effect of different decisions researches have to make when working with
-trait data from several regions/sources, involving harmonization, 
-handling different codings, normalization, and aggregation of traits.
-\\
-\\
-\\
-%! Trait terminology
-%TODO: Apply unified terminology -> Use Schmera et al's suggestion?
+% !General introduction: Invertebrates importance/biodiversity and stressor
+% ? use Traits mechanistic relationship, environmental filtering
+% Half of all described freshwater invertebrates are aquatic insects
 
-One of the problems in macroinvertebrate trait research is the use
-of inconsistent terminology across studies (but see \cite{schmera_proposed_2015}). 
+In the age of the Anthropocene invertebrates are exposed to multiple stressors such 
+as chemical pollution, hydro-morphological modifications, invasive species and climate change. %?Sources 
+Freshwater invertebrates play a crucial role for many ecosystem processes such as 
+carbon cycling and water purification. In addition to their functional role, 10 \% of all 
+described species live in freshwaters, most of which being invertebrates, and thus represent a
+large part of animal biodiversity.
+Understanding distributions of invertebrate communities and predicting effects of 
+potential stressors is a long time goal of freshwater research. Since the 1970s 
+ecologists have started using organismal traits to group aquatic insect species % ?to understand what -> Check Cummins
+
+Traits are biological characteristics or ecological preferences measurable at the 
+individual organism. %? Source Lancaster? Find precises definition
+They reflect an organisms adaptation to its habitat. Trait based approaches in 
+ecology are based on the habitat template theory, that predicts where environmental conditions
+are similar trait composition should also converge, even across biogeographic boundaries. %?Source
+Furthermore, several studies suggested that trait variability is lesser on larger geographical
+scales than taxonomic variability. %?Source Bonada 
+Hence, trait based approaches can be a suitable tool for comparing the effect of various 
+environmental stressors to invertebrate communities on large scales or across regions. 
+%!General studies? Or more specific to studies for several regions
+% They have been used to understand species distributions, in predicting effects of various environmental
+% stressors to invertebrate communities, and as tool in biomonitoring. %? Source: Statzner & Beche 2010, Ralf Paper, Cummins Paper?
+Consequently, studies have been carried out that e.g. examine the relationship between climate
+and freshwater community assemblages using species traits. % TODO: Cite Bhowmik, cite Brown 
+% TODO: Enrich with examples -> Maybe for toxicants as well?
+Many of such studies combine information from several trait databases. For example, 
+Brown et al. used in their study traits from invertebrate trait databases from
+Europe, North America and New Zealand to investigate the effect of decreasing glacier cover
+to river ecosystems. %TODO Cite Brown
+
+% Studies that use information on aquatic invertebrate traits from different regions
+% and/or aggregate trait information are increasing 
+% !Transition into trait data
+In fact, invertebrate trait data are increasingly available. Over the last decades aquatic 
+ecologists have compiled comprehensive databases on invertebrate traits for different regions 
+(see table \ref{tab:trait_databases} for examples). 
+% !Mention various problems with trait databases 
+However, researchers face various problems when they need to synthesize information from 
+multiple invertebrate trait databases. 
+% !Trait terminology
+i) The use of inconsistent terminology across studies (see \cite{schmera_proposed_2015}
+for a comprehensive discussion). 
 For example, some studies used the term "trait" to describe a general 
@@
 \cite{ussegliopolatera_biological_2000}), while in other studies this 
-term was related to trait categories/states like "bi/multivoltine" 
-(\cite{haybach_use_2004}, \cite{vieira_database_nodate}). 
-Here, we follow the proposal of Schmera et al. (2015) and use the term 
-\textit{trait} for a morphological, physiological, or phenological 
-feature measurable at the individual organism (e.g. tegument, gills, etc.) 
-and the term \textit{grouping feature} to describe a general property 
-of related organismal traits (e.g. respiration).
-\\
-\\
-\\
-%!What we did:
-Therefore, we harmonized six grouping features from four trait databases and 
-aggregated the trait information to family level. % ?Name Traits
+term was related to categories like "bi/multivoltine" 
+(\cite{haybach_use_2004}, \cite{vieira_database_nodate}). Here, we follow 
+the proposal of Schmera et al. (2015) and use the term \textit{trait} for a morphological,
+physiological, or phenomenological feature measurable at the individual
+organism (e.g. tegument, gills, etc.) and the term \textit{grouping feature} to describe 
+a general property of related organismal traits (e.g. respiration). 
+%? Include measurement scale?
+%TODO: in concordance with previous paragraphs on trait definitions
+%! Different traits used/definitions
+ii) Invertebrate trait databases from different regions are not standardized. 
+Often, the same grouping features are categorized using different traits. 
+% TODO Example
+This is complicated by the use of different measurement scales. For example, trait databases 
+from North America use traditionally a binary coding (i.e. trait is expressed or not), 
+whereas most other trait databases (e.g. Tachet, freshwaterecology, and New Zealand) 
+use fuzzy coding (i.e. trait is expressed to a certain extent by the organism). 
+Hence, transformation of nominal scale to ratio scale or vice versa is required. %? Wording
+Furthermore, definitions for some traits differ as well across databases. 
+% TODO Example feeding!
+%! Taxonomical resolution & traits aggregation -> no guidance
+%! Wording: taxonomical resolution -> high -> species level 
+% high taxonomical level -> high -> genus/family,...(Schmidt-Kloiber et al.)
+iii) Taxonomical resolution between databases differs, further complicating the
+synthesis of trait data from different regions. Some trait databases have recorded
+information on mixed levels of taxonomical resolution like the North American trait
+database or the Australian trait database. In contrast, trait information in the 
+freshwaterecology database is entirely recorded on species-level. %?ref to graphic
+%TODO: Percentages of different levels of taxonomical resolutions in process overview graph 
+Using trait information on varying taxonomical levels is only possible when 
+traits are aggregated to the lowest taxonomical level that is shared by all used databases. 
+However, iv) so far studies comparing different ways of aggregating traits are lacking.
+% Hence, guidance on how to perform a robust trait aggregation is missing. 
+% TODO Poff Paper example, check Brown and other literature
+
+%!Incentive of our analysis:
+% no API/R packages 
+Given the problems mentioned above extensive data processing is required before researchers 
+can use multiple invertebrate trait databases for their work. 
+In this paper we examine difficulties that ecologists face when synthesizing trait 
+information from different invertebrate trait databases. We explore the effect of different
+decisions researches have to make when working with invertebrate trait data 
+from several sources, involving trait harmonization, handling different codings,
+normalization, and aggregation of traits.
+%?Effect of a statistical analysis -> Clustering?
+%!What we did/Goal:
+Therefore, we harmonized six grouping features of different trait databases from four
+regions and aggregated the trait information to family-level. % ?Name Traits
 We discuss the harmonization and show the effect of different ways of aggregating 
@@
 
-\section{Description of harmonized trait database} %TODO: Change heading to be more expressive
+%TODO: Change heading to be more expressive
+\section{Methods}
+
+\subsection{Description of harmonized trait databases}
 
 % TODO Give a motivation (better in introduction?)
-The harmonized database consists of the available information on aquatic 
-insect traits for the regions Europe, North America, Australia, and New Zealand
-and comprises the grouping features locomotion, feeding mode, respiration, 
-voltinism, size, and body form. The pattern of development (holometabolous or hemimetabolous) 
-was added as an additional grouping feature based on the orders of the taxa 
-included in each database. 
-% TODO: Few words why these traits have been selected
-% TODO: Reasoning why no ecological traits have been used
+The harmonized databases are using the available information on aquatic invertebrate
+traits for the regions Europe, North America, Australia, and New Zealand. 
+Due to the different number and identity of grouping features in each database, 
+the following six grouping features were chosen for this study: locomotion, feeding mode, 
+respiration, voltinism, size, and body form. 
+%? Next two sentences can be removed?
+% Comment: For C of TPG Development pattern added
+% TODO: Few words why these grouping features have been selected
+% TODO: Reasoning why no ecological grouping features have been used
 Trait information for Australia and New Zealand were retrieved from 
-single database. For Europe we gathered trait information from the 
+a single database, respectively. For Europe we gathered trait information from the 
 freshwaterecology trait database (\url{https://www.freshwaterecology.info/}) 
-and complemented missing information with the 
+and complemented where possible missing information with the 
 Tachet trait database (\cite{usseglio-polatera_biomonitoring_2000}). 
-North American macroinvertebrate traits were retrievied from Laura Twardochleb and 
-complemented by trait information from Vieira et al (\cite{vieira_database_nodate}). 
-% TODO Mention restriction to certain orders
-We did not use the entire data on macroinvertebrates, 
-but limited our analysis to orders of aquatic insects that occurred in all used
-databases, specifically the orders:
-...
-% TODO: Insert citation
-Table \ref{tab:trait_databases} gives an overview of the used databases. \\ 
+North American invertebrate traits were retrieved from Laura Twardochleb and 
+complemented where possible by trait information from Vieira et al (\cite{vieira_database_nodate}).
+From now on, if we use the term European or North American trait database we refer to the combined 
+databases unless explicitly stated otherwise.
+We used all available information on invertebrates in the databases but restricted
+our analysis to those taxa that have complete trait profiles for the grouping features
+mentioned earlier. We are aware that imputation methods exist, which infer missing 
+information for traits by interpolating from related traits. % TODO: Cite Penone
+However, by using only complete data we were able to evaluate the taxonomical coverage
+per order within the databases. We consider this a helpful information for researchers
+who strive to fill data gaps.
+Table \ref{tab:trait_databases} gives an overview of the used databases. 
 In the following paragraphs, we describe the data processing steps required to 
-establish a harmonized macroinvertebrate trait database.
+establish a harmonized invertebrate trait database.
 
@@
 
-\begin{itemize}
-    \item Various preprocessing steps: Taxonomical corrections; Range normalization [0-1] (e.g. in Australia); a few 
-    words about spreadsheets etc?
-    \item Harmonization 
-    \item (RowSum) Normalization/Standardization %!Wording
-    \item Aggregation of traits
-\end{itemize}
+\subsection{Normalization \& data conversion}
 
-\subsection{Harmonization of traits}
-\begin{itemize}
-    \item Harmonization process: See also Schmera 2015 et al 
-    \item Differences in trait definitions
-    \item Sources of traits
-\end{itemize}
+%TODO Mention taxonomical corrections?
+% !Issues with coding & scale in the trait databases
+Establishing a harmonized database required traits on the same measurement scale to 
+enable comparability. However, in the used databases traits varied within and among databases 
+in terms of measurement scale. Traits were either fuzzy coded, binary coded or 
+to a small extent coded as continuous variable (e.g. size). Fuzzy codes capture the variation 
+(i.e. temporal or spatial) in a trait and are represented by affinity scores 
+(sometimes termed membership state) which express a preference of a taxon to a certain trait.
+Usually, these scores range from 0 representing no affinity to an arbitrary maximum value which 
+represents high affinity. This type of coding uses the ratio scale and not the ordinal
+scale as one might intuitively assume. In fact, the intention of the developers of this 
+coding system was to convert affinity scores to percentages per trait, e.g. 
+for a grouping feature with four traits affinity scores of \textit{5, 6, 2, 2} are equal
+to \textit{1/3, 2/5, 2/15, 2/15} or \textit{33.3 \%, 40 \%, 13.3 \%, 13.3 \%} (\cite{chevenet_francois_fuzzy_1994}).
+We used fuzzy coded traits for establishing our harmonized databases where possible, otherwise binary traits. 
+Categorical and continuous traits across all used databases were converted into binary traits. 
+Implicitly, we assumed for binary variables that a value of 1 for a particular trait corresponded
+to the maximum affinity of a taxon for that particular trait.
+
+Two databases needed further data processing. Firstly, the Australian database which is a collection of seven trait databases. 
+Thus, several grouping features occur multiple times but with traits that have different types of codings and ranges.
+For example, body size occurs as continuous variable, with traits that are fuzzy coded, and with traits that are binary coded. 
+The same traits originating from different sub-databases in the Australian trait database were allocated. 
+To enable allocation of fuzzy coded and binary traits we applied a range normalization by dividing each fuzzy coded 
+trait by its potential maximum value. Consequently, the values of each trait were converted to a range from 0 to 1.
+
+Secondly, the North American trait database which only contained traits on the nominal scale. 
+We first converted nominal traits into binary traits. As a second approach we converted nominal traits for taxa 
+on species and genus-level into "pseudo" fuzzy codes by calculating the percentage of occurrence for each
+trait per genera and grouping feature. Both approaches were compared regarding the trait values they yielded.
+We refer to the version with binary traits as \textit{NOA\_bin} and to the version with pseudo fuzzy codes as 
+\textit{NOA\_fuzzy}. 
+% Better wording? traits from NOA data were converted to fuzzy codes by allocating at genus level using frequency on species level
+
+% Furthermore, in some databases fuzzy coded information occurred in different ranges 
+% (e.g. from 0 to 3 and from 0 to 5 in the Tachet database, from 0 to 10 in the 
+% freshwaterecology database).
+
+% !Issue of duplicate taxa
+The Australian, Tachet, and the North American trait databases contained duplicate taxa entries
+- either on species, genus or family-level - which were amalgamated. 
+The duplicate entries in the Australian trait database originated from the different sub-databases. 
+As a result, many of the duplicate entries complemented each other (e.g. for a given trait one duplicate contained a value, 
+the other not). In those cases where several different values for a trait occurred, the average trait value was calculated. 
+The NOA\_bin database only contained 0 and 1 as entries. Hence, for duplicates the maximum value was taken.
+% Tachet: Fuzzy codes -> Mean
+For the tachet trait database duplicate entries were allocated using the mean if they contained contrasting
+information on the same trait. 
+% ?What about zero's -> were disregarded
+
+% !Normalization/Standardization 
+Finally, every trait within each grouping feature was standardized by the sum of all traits 
+within this particular grouping feature per taxon to convert traits to percentages per trait. 
+% which can be used to compare and harmonize taxa regarding their traits. %!Wording
+
+\subsection{Harmonization of traits and taxa}
+% TODO Differences in trait definitions
+% TODO Sources of traits
 
 % !What is harmonization? & Why is it needed?
-Harmonization of traits is the process of amalgamating several similar trait states
-into a single trait state. Harmonization has to be undertaken when e.g. traits from
-different sources (e.g. different regions) are compared and the traits have not
-the same trait states. %?Give an example -> Clusteranalysis
-\\
-\\
-\\
+Harmonization of traits means amalgamating several similar traits into a single trait. 
+It has to be undertaken when grouping features from different sources (e.g. different regions) are
+used and the grouping features do not contain the same traits. 
+For example, in our study for the grouping feature locomotion the lowest number of traits that occur
+across all databases was in the New Zealand trait database ("Swimmer", "Burrower", "Crawler", "Sessil"). 
+Hence, in all other databases locomotion traits have been allocated into these four traits (see \ref{fig:harmon_overview_1}
+and \ref{fig:harmon_overview_2}).
+% !Taxonomical harmonization
+% Harmonization is crucial -> number of cases & comparability
+%?Give an example -> Clusteranalysis
+
 % !How was the harmonization done? -> technical aspect.
-Traits that differed in their trait states among databases have been harmonised by 
-condensing the trait states for each trait in such a way that in the end the same 
-traits in all four databases consisted of the same trait states. 
-This meant reducing the trait states to the smallest number of trait states that
-occur for a particular trait among all databases. Thereby, trait states were 
-amalgamated based on ecological knowledge or expert judgment. %!Wording 
-Our approach of harmonizing the traits of the used databases is outlined in figures 
+Grouping features that differed in their traits among databases have been harmonised by condensing the traits in such a way
+that in the end the same grouping features in all databases consisted of the same traits.  
+Thereby, traits were amalgamated based on ecological knowledge or expert judgment. %!Wording 
+Our approach of harmonizing the traits in the used databases is outlined in figures 
 \ref{fig:harmon_overview_1} and \ref{fig:harmon_overview_2}.
 
+% TODO: Harmonization for feeding mode AUS needs to be finished!
 \begin{figure}[H]
@@
 
-\section{Aggregation of traits}
+% TODO: Go deeper -> Trait definitions
+% !Trait harmonization subjective & always dangerous
+Not only the categorization of grouping features but also the definitions of individual traits vary between
+databases, complicating harmonization. 
+% TODO: Present definition comparison -> For all traits?
 
-\begin{itemize}
-    \item Describing \& testing different approaches
-    \item Problem of coding of traits
-\end{itemize}
+\subsection{Aggregation of traits}
+% TODO Describing \& testing different approaches
+% TODO Problem of coding of traits
 
-\section*{Additional ideas}
+%! Description trait aggregation
+% ? Aggregation considering different levels of taxonomical resolution
+Traits in the processed and harmonized trait databases were aggregated using three approaches.
+I) taxa on species-level and genus-level were stepwise aggregated to the family-level by initially 
+allocating them at the genus-level using the median. Then all traits were aggregated to family-level by using the mode. 
+In cases where it was not possible to take the mode, e.g. only distinct values, multiple duplicates, or multiple 
+duplicates and distinct values occurred the mean was taken. Hereafter, we abbreviate this aggregation type as \textit{stepwise\_agg}.
+II) we directly aggregated taxa to family level using the median. We denote this aggregation as \textit{direct\_agg}.
+III) taxa were aggregated using a weighted approach, denoted as \textit{weighted\_agg}. 
+The weights were determined as the ratio of how many taxa on species or genus-level were initially present per genera compared to  
+how many taxa on species or genus-level were present after selecting only taxa with complete trait profiles. 
+After determining the weights, taxa on species and genus-level were were aggregated to genus-level by multiplying their
+trait values by their respective weights. Then the weighted trait values were summed up per family for each trait.
 
-Section Description of databases:
-\begin{itemize}
-    \item Describe different databases briefly?
-    \item State goal of analysis $\rightarrow$ reference to second paper?
-\end{itemize}
+The resulting aggregated trait values were compared to trait values assigned at family-level by experts. 
+Trait assignments on family-level existed for the Australian database and the North American database, 
+but only for a limited subset of grouping features and taxa. For the Australian database we could
+compare aggregated trait values with assigned trait values for the grouping features feeding mode and 
+size. For the North American database we compared aggregated trait values with assigned trait values for
+the grouping features feeding mode, respiration, size, voltinism and locomotion, 
+albeit only for aquatic insects. 
+% TODO: Cite Chessman & Matt Pyne
+% TODO: At for which traits
+% TODO: ATM done with all Taxa, just subset to Species data (does this make sense?)
+
+\section{Results}
+% TODO: For Results & Discussion taxonomic overlap between databases rather small
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MAIN RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Data preparation complex -> many decisions
+% Databases are not ideal (not standardized, different trait definitions)
+% Report missing information -> How many families not "get lost"
+% Effect of trait aggregation
+% Trait values only slightly vary between complex and direct aggregation
+ % -> compare with family assignments: Roughly 25 % are classified differently
+    % -> Which and why? 
+    % -> Add statistical technique -> Maybe clustering?  
+ % -> test with weights?
+ % -> (effect of transforming binary to fuzzy codes -> US data subset test)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MAIN RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%!General overview, how many taxa, distinct orders, ...
+\subsection{Taxonomical coverage}
+Regarding the taxonomical coverage the New Zealand database has, as expected, the smallest 
+taxon pool. In total 492 taxa are covered by this database. Thereof, 404 taxa resolved on species-level, 47 taxa 
+on genus-level and 27 taxa on family-level. The remaining entries are on a lower taxonomical resolution. 
+73 \% of taxa in the New Zealand database belong to the group of aquatic insects.
+The largest taxon pool is spanned by the European trait database, with 4224 taxa of 76 different orders. 
+48 \% of the taxa in this database belong to the group of aquatic insects. The European database is 
+mostly on the highest taxonomical resolution possible, with 3953 taxa on species-level (approximately 93,6 \%).
+253 entries are resolved on genus-level and 18 entries on family-level.
+The Australian database has 1404 taxa of 64 orders. 52 \% of the taxa covered are aquatic insects. 
+564 taxa are resolved on species-level, 578 on genus-level and 260 on family-level.
+The North American trait database contained trait information for 3542 taxa of 42 different orders, 
+although 63 \% of the taxa in the database belong to the aquatic insects. 2142 entries are on 
+species-level, 1074 on genus-level and 50 on family-level.
+
+%! How big is the data gap?
+\subsection{Completeness of trait information}
+The percentage of entries with available information for the individual grouping features in the Australian, European and
+North American trait databases varied between 5 \% and 99 \%. By contrast, the New Zealand trait database
+contained complete trait information for 99 \% to 100 \% of their entries for the individual grouping features (\ref{tab:trait_coverage}).
+The greatest data gap was for the grouping feature body form where information was only present for 7 \% of entries
+in the Australian and European database, and 26 \% of entries in the North American database. % TODO: Comment in Draft file for Ralf
+Selecting only taxa with complete trait profiles for the six grouping features and resolved at least at 
+family-level lead to the omission of many taxa in all databases except for the New Zealand database. 
+Out of the 21 orders that the New Zealand database covers, taxa of 20 orders remained after the selection process.
+For most orders, all families initially included were also included after selecting taxa with complete trait profiles (table \ref{tab:fam_preproc/fam_init}).
+By contrast, in the Australian database, only taxa from five orders (Ephemeroptera, Megaloptera, Odonata, Plecoptera, 
+and Trichoptera) remained. Within these five orders, there was none where all families included in the database
+contained complete trait profiles. % Clearly the lack of data for body form results in the omission of many taxa
+In the North American database, taxa of 18 orders had complete trait profiles, in the European database 9 orders.
+
+\begin{table}[H]
+  \centering
+  \caption{How many entries have information for the 
+  individual grouping features per database.} 
+  \label{tab:trait_coverage}
+  \begin{tabular}{llr}
+    \hline
+  Database & Grouping feature & Trait covered [\%] \\ 
+    \hline
+  Australia & Body form & 5.00 \\ 
+    Australia & Feeding mode & 99.00 \\ 
+    Australia & Locomotion & 42.00 \\ 
+    Australia & Respiration & 70.00 \\ 
+    Australia & Size & 78.00 \\ 
+    Australia & Voltinism & 49.00 \\ 
+    Europe & Body form & 7.00 \\ 
+    Europe & Feeding mode & 65.00 \\ 
+    Europe & Locomotion & 33.00 \\ 
+    Europe & Respiration & 56.00 \\ 
+    Europe & Size & 11.00 \\ 
+    Europe & Voltinism & 24.00 \\ 
+    New Zealand & Body form & 100.00 \\ 
+    New Zealand & Feeding mode & 99.00 \\ 
+    New Zealand & Locomotion & 99.00 \\ 
+    New Zealand & Respiration & 100.00 \\ 
+    New Zealand & Size & 100.00 \\ 
+    New Zealand & Voltinism & 100.00 \\ 
+    North America & Body form & 26.00 \\ 
+    North America & Feeding mode & 61.00 \\ 
+    North America & Locomotion & 51.00 \\ 
+    North America & Respiration & 44.00 \\ 
+    North America & Size & 75.00 \\ 
+    North America & Voltinism & 47.00 \\ 
+    \hline
+  \end{tabular}
+  \end{table}
+
+% ?Overview how complete each trait is, by order
+
+% TODO: Mention orders that are not represented at all 
+% TODO: Which entries have 0 %, which were not present initially?
+% ? Why difference for NOA & NOA_FC? -> rather exclude NOA_FC since it is a special case
+\begin{table}[H]
+  \centering
+  \caption{Proportion of families per order that remain
+  after only taxa with complete trait profiles have been selected from the total
+  number of distinctive families in the databases.} 
+  \label{tab:fam_preproc/fam_init}
+  \begin{tabular}{lrrrr}
+    \hline
+  Order & Australia & New Zealand & Europe & North America \\ 
+    \hline
+  Amphipoda &  & 100.00 & 37.50 & 10.00 \\ 
+    Anthoathecata &  & 100.00 &  &  \\ 
+    Architaenioglossa &  &  &  & 100.00 \\ 
+    Arhynchobdellida &  &  &  & 100.00 \\ 
+    Branchiopoda &  &  &  & 100.00 \\ 
+    Coleoptera &  & 88.89 & 83.33 & 15.62 \\ 
+    Cycloneritida &  &  &  & 100.00 \\ 
+    Decapoda &  & 100.00 &  &  \\ 
+    Diptera &  & 100.00 & 46.15 & 21.62 \\ 
+    Ephemeroptera & 50.00 & 100.00 & 66.67 & 73.91 \\ 
+    Hemiptera &  & 50.00 & 63.64 & 47.06 \\ 
+    Hexapoda &  & 100.00 &  &  \\ 
+    Lepidoptera &  & 100.00 &  &  \\ 
+    Littorinimorpha &  &  &  & 66.67 \\ 
+    Mecoptera &  & 100.00 &  &  \\ 
+    Megaloptera & 50.00 & 100.00 &  & 50.00 \\ 
+    Mollusca &  & 100.00 &  &  \\ 
+    Mysida &  & 100.00 &  &  \\ 
+    Nemertea &  & 100.00 &  &  \\ 
+    Neuroptera &  & 100.00 &  &  \\ 
+    Odonata & 6.90 & 100.00 & 100.00 & 50.00 \\ 
+    Oligochaeta &  & 100.00 &  &  \\ 
+    Onychura &  &  &  & 100.00 \\ 
+    Plecoptera & 25.00 & 100.00 & 100.00 & 88.89 \\ 
+    Rhynchobdellida &  & 100.00 &  & 50.00 \\ 
+    Spinicaudata &  &  &  & 100.00 \\ 
+    Tanaidacea &  & 100.00 &  &  \\ 
+    Trichoptera & 52.17 & 100.00 & 95.45 & 71.43 \\ 
+    Venerida &  &  & 100.00 & 33.33 \\ 
+     \hline
+  \end{tabular}
+  \end{table}
+
+\subsection{Deviance in trait values}
+% !How many taxa end up with different trait values after aggregation?(%) 
+% TODO: Improve R script
+% TODO: Write paragraph
+% TODO: Add graphs?
+% Generally both methods result in similar values on family-level.
+% When deviations, then rather small
+% Complex agg: Seems to make only sense with cases where many observations 
+% -> many species per Genera, many genera per family
+
+% Deviating cases: mostly Trichoptera, North America Ephemeroptera
+% No family that shows deviating results across all databases
+
+% TODO: Comment -> Suggest to Ralf other approaches, if time test them
+The \textit{stepwise\_agg} and \textit{direct\_agg} approaches yielded for the majority of taxa 
+the same trait values (table \ref{tab:diff_trait_agg_methods}) across all grouping features.  
+The two aggregation methods differed the most when applied to the Australian trait database, with 3.52 \% 
+cases differently classified. 
+% ? How much are trait values deviating?
+
+%! Taxa on family-level that were wrongly classified in all databases
+
+% ! Which traits/grouping features show mainly different values between both aggregation methods?
+% in all four databases: feed_herbivore, feed_gatherer, feed_shredder,
+% resp_gil, resp_teg, size_medium, size_small result 
+\begin{table}[ht]
+    \centering
+    \caption{Percentage of cases where the \textit{stepwise\_agg} and \textit{direct\_agg} methods 
+    resulted in different trait values on family-level.}
+    \label{tab:diff_trait_agg_methods}
+    \begin{tabular}{lr}
+      \hline
+    Database & Deviating cases [\%] \\ 
+      \hline
+    Australia & 3.52 \\ 
+      Europe & 2.17 \\ 
+      New Zealand & 1.03 \\ 
+      North America & 2.66 \\ 
+       \hline
+    \end{tabular}
+    \end{table}
+
+% ! Comparison with traits assigned on family level
+% ? Influence on hierarchical clustering
+
+% ! Comparison trait definitions?
+%
+
+%%%%%%%%%%%%%%%%%%%% \section*{Additional ideas} %%%%%%%%%%%%%%%%%%%%
+
+% Section Description of databases:
+% \begin{itemize}
+%     \item Describe different databases briefly?
+%     \item State goal of analysis $\rightarrow$ reference to second paper?
+% \end{itemize}
 

### 2020-03-05 Paper/__latexindent_temp.tex
Updata paper

@@
+\documentclass{article}
+\usepackage[utf8]{inputenc}
+\usepackage{hyperref}
+\usepackage{float}
+\usepackage[table,xcdraw]{xcolor}
+%\usepackage[sort&compress,square,comma,authoryear]{natbib}
+\usepackage{booktabs}
+\usepackage{graphicx}
+\graphicspath{{Figures/}}
+\usepackage{longtable}
+
+\usepackage[
+backend=biber,
+style=authoryear,
+sorting=nyt % sort by name year title
+]{biblatex}
+\addbibresource{Ref_invertebrate_DB.bib}
+
+\title{ OUTLINE: Harmonized macroinvertebrate trait database, Aggregation of traits, Trait definitions, Sources }
+\author{}%Stefan Kunz 
+\date{}%June 2019
+
+\begin{document}
+%TODO: Use citep & citet instead of cite
+\maketitle
+
+\section{Introduction}
+
+% !General introduction: Invertebrates importance/biodiversity and stressor
+% ? use Traits mechanistic relationship, environmental filtering
+% Half of all described freshwater invertebrates are aquatic insects
+
+In the age of the Anthropocene invertebrates are exposed to multiple stressors such 
+as chemical pollution, hydro-morphological modifications, invasive species and climate change. %?Sources 
+Freshwater invertebrates play a crucial role for many ecosystem processes such as 
+carbon cycling and water purification. In addition to their functional role, 10 \% of all 
+described species live in freshwaters, most of which being invertebrates, and thus represent a
+large part of animal biodiversity.
+Understanding distributions of invertebrate communities and predicting effects of 
+potential stressors is a long time goal of freshwater research. Since the 1970s 
+ecologists have started using organismal traits to group aquatic insect species % ?to understand what -> Check Cummins
+
+Traits are biological characteristics or ecological preferences measurable at the 
+individual organism. %? Source Lancaster? Find precises definition
+They reflect an organisms adaptation to its habitat. Trait based approaches in 
+ecology are based on the habitat template theory, that predicts where environmental conditions
+are similar trait composition should also converge, even across biogeographic boundaries. %?Source
+Furthermore, several studies suggested that trait variability is lesser on larger geographical
+scales than taxonomic variability %?Source Bonada 
+Hence, trait based approaches can be a suitable tool for comparing the effect of various 
+environmental stressors to invertebrate communities on large scales or across regions. 
+%!General studies? Or more specific to studies for several regions
+% They have been used to understand species distributions, in predicting effects of various environmental
+% stressors to invertebrate communities, and as tool in biomonitoring. %? Source: Statzner & Beche 2010, Ralf Paper, Cummins Paper?
+Consequently, studies have been carried out that e.g. examine the relationship between climate
+and freshwater community assemblages using species traits. % TODO: Cite Bhowmik, cite Brown 
+% TODO: Enrich with examples -> Maybe for toxicants as well?
+Many of such studies combine information from several trait databases. For example, 
+Brown et al. used in their study traits from invertebrate trait databases from
+Europe, North America and New Zealand to investigate the effect of decreasing glacier cover
+to river ecosystems. %TODO Cite Brown
+
+% Studies that use information on aquatic invertebrate traits from different regions
+% and/or aggregate trait information are increasing 
+% !Transition into trait data
+In fact, invertebrate trait data are increasingly available. Over the last decades aquatic 
+ecologists have compiled comprehensive databases on invertebrate traits for different regions 
+(see table \ref{tab:trait_databases} for examples). 
+% !Mention various problems with trait databases 
+However, researchers face various problems when the need to synthesize information from 
+multiple invertebrate trait databases. 
+% !Trait terminology
+i) The use of inconsistent terminology across studies (see \cite{schmera_proposed_2015}
+for a comprehensive discussion). 
+For example, some studies used the term "trait" to describe a general 
+organismal property like "generations per year" (\cite{statzner_reproductive_1997}, 
+\cite{ussegliopolatera_biological_2000}), while in other studies this 
+term was related to categories like "bi/multivoltine" 
+(\cite{haybach_use_2004}, \cite{vieira_database_nodate}). Here, we follow 
+the proposal of Schmera et al. (2015) and use the term \textit{trait} for a morphological,
+physiological, or phenomenological feature measurable at the individual
+organism (e.g. tegument, gills, etc.) and the term \textit{grouping feature} to describe 
+a general property of related organismal traits (e.g. respiration). 
+%? Include measurement scale?
+%TODO: in concordance with previous paragraphs on trait definitions
+%! Different traits used/definitions
+ii) Invertebrate trait databases from different regions are not standardized. 
+Often, the same grouping features are categorized using different traits. 
+% TODO Example
+This is complicated by the use of different measurement scales. For example, trait databases 
+from North America use traditionally a binary coding (i.e. trait is expressed or not), 
+whereas most other trait databases (e.g. Tachet, freshwaterecology, and New Zealand) 
+use fuzzy coding (i.e. trait is expressed to a certain extent). 
+Hence, transformation of nominal scale to ratio scale or vice versa is required. %? Wording
+Furthermore, definitions for some traits differ as well across databases. 
+% TODO Example feeding!
+%! Taxonomical resolution & traits aggregation -> no guidance
+iii) Taxonomical resolution between databases differs, further complicating the
+synthesis of trait data from different regions. For example, some databases have recorded
+trait information on mixed levels of taxonomical resolution like the North American trait
+database or the Australian trait database. In contrast, trait information in the 
+freshwaterecology database is entirely recorded on species-level. %?ref to graphic
+%TODO: Percentages of different levels of taxonomical resolutions in process overview graph 
+Using trait information on varying taxonomical levels is only possible when 
+traits are aggregated to the lowest taxonomical level that is shared by all used databases. 
+However, so far no one studied the effect of different trait aggregations 
+Hence, iiii) guidance on how to perform a robust trait aggregation is missing. 
+% TODO Poff Paper example, check Brown and other literature
+
+%!Incentive of our analysis:
+% no API/R packages 
+Given the problems mentioned above extensive data processing is required before researchers 
+can use multiple invertebrate trait databases for their work. 
+In this paper we examine difficulties that ecologists face when synthesizing trait 
+information from different invertebrate trait databases. We explore the effect of different
+decisions researches have to make when working with invertebrate trait data 
+from several sources, involving trait harmonization, handling different codings,
+normalization, and aggregation of traits.
+%?Effect of a statistical analysis -> Clustering?
+%!What we did/Goal:
+Therefore, we harmonized six grouping features of different trait databases from four
+regions and aggregated the trait information to family-level. % ?Name Traits
+We discuss the harmonization and show the effect of different ways of aggregating 
+traits (inter alia Problem of different coding styles (fuzzy vs binary)).
+We also present an overview of differences in trait definitions among databases.
+Finally, our paper compares the references for the trait information that 
+were specified in the trait databases we used.
+
+%TODO: Change heading to be more expressive
+\section{Description of harmonized trait database}
+
+% TODO Give a motivation (better in introduction?)
+The harmonized database uses the available information on aquatic 
+insect traits for the regions Europe, North America, Australia, and New Zealand. 
+Due to the different number and identity of grouping features in each database, 
+the following six grouping features were chosen for this study: locomotion, feeding mode, 
+respiration, voltinism, size, and body form. 
+The pattern of development (with the traits holometabolous or hemimetabolous) was added as
+an additional grouping feature based on the orders of the taxa included in each database. 
+% TODO: Few words why these grouping features have been selected
+% TODO: Reasoning why no ecological grouping features have been used
+Trait information for Australia and New Zealand were retrieved from 
+a single database, respectively. For Europe we gathered trait information from the 
+freshwaterecology trait database (\url{https://www.freshwaterecology.info/}) 
+and complemented missing information with the 
+Tachet trait database (\cite{usseglio-polatera_biomonitoring_2000}). 
+North American macroinvertebrate traits were retrieved from Laura Twardochleb and 
+complemented by trait information from Vieira et al (\cite{vieira_database_nodate}). 
+We used all available information on invertebrates in the databases but restricted
+our analysis to taxa that have complete trait profiles for the grouping features
+mentioned earlier 
+% !Short paragraph on imputation
+
+% TODO: Insert citation
+Table \ref{tab:trait_databases} gives an overview of the used databases. \\ 
+In the following paragraphs, we describe the data processing steps required to 
+establish a harmonized macroinvertebrate trait database.
+
+\begin{table}[H]
+    \centering
+    \caption{Overview of trait databases.}
+    \label{tab:trait_databases}
+    \begin{tabular}{lll}
+    \toprule
+   Region & Coding of trait states & Reference \\ 
+    \hline
+   Europe & Largely fuzzy & \cite{schmidt-kloiber_www.freshwaterecology.info_2015}\\ 
+   Central Europe & Fuzzy coded & \cite{usseglio-polatera_biomonitoring_2000} \\ 
+   North America & Largely binary & \cite{vieira_database_nodate}\\
+   North America & Largely binary & cite Laura Twardochleb \\
+   Australia & Binary \& fuzzy coding  & \cite{kefford_ben_AST_DB_2019}\\ 
+   New Zealand & Fuzzy coded & \\ %TODO: Create entry for more recent NZ reference
+    \bottomrule
+    \end{tabular}
+\end{table}
+
+\subsection{Normalization \& data conversion}
+
+% !Coding & Scale general
+Traits in the used databases were either coded by fuzzy codes, binary coded or 
+to a small extent coded as continuous variable (e.g. size). 
+Fuzzy codes capture the variation (i.e. temporal or spatial) in a trait making them 
+superior to binary coding. Fuzzy coding is often represented by assigning affinity 
+scores to a taxon to express its preference to a certain trait. Usually, these 
+scores range from 0 representing no affinity to an arbitrary maximum value (often 3) 
+which represents high affinity. This type of coding uses the ratio scale
+and not the ordinal scale as one might intuitively assume. In fact, the intention of the 
+developers of this coding system was to convert affinity scores to percentages 
+per trait, e.g. for a grouping feature with four traits affinity scores of 
+\textit{5, 6, 2, 2} are equal to \textit{1/3, 2/5, 2/15, 2/15} or 
+\textit{33.3 \%, 40 \%, 13.3 \%, 13.3 \%} (\cite{chevenet_francois_fuzzy_1994}).
+
+% !Issues with coding & scale in the trait databases
+Establishing a harmonized database required traits on the same measurement scale to 
+enable comparability. However, in the used databases traits varied within and among databases 
+in terms of measurement scale. 
+This problem was particularly apparent in the Australian database which is a collection 
+of seven trait databases. Thus, several grouping features occur multiple times but with 
+traits that have different types of codings and ranges. 
+For example, body size occurs as continuous variable, with traits that are fuzzy coded,
+and also with traits that are binary coded. Hence, continuous variables needed to be converted to 
+binary variables. Ranges of the fuzzy coded traits (0 - 3) and binary (0 - 1) traits needed to be 
+normalized in order to be able to meaningfully allocate the same traits later on 
+(e.g. allocating body size small from several sources).
+Similarly, the type of coding for a grouping feature varied among the databases. %?give example
+Furthermore, in some databases fuzzy coded information occurred in different ranges 
+(e.g. from 0 to 3 and from 0 to 5 in the Tachet database, from 0 to 10 in the 
+freshwaterecology database).
+
+% !How to circumvent aforementioned issues
+First of all, categorical traits were dummy coded into binary variables and continuous
+traits such as maximum body size were converted into binary traits. 
+% TODO: traits from NOA data were converted to fuzzy codes by allocating at genus level using frequency on species level
+For the Australian trait database we applied a range normalization by dividing each fuzzy
+coded trait by its potential maximum value. Consequently, the values of each trait
+were converted to a range from 0 to 1 which allowed allocating the same trait from various
+sources in the next step. Implicitly, we assumed for binary variables that a value of 1 
+for a particular trait corresponded to the maximum affinity for that particular trait.
+
+% !Issue of duplicate taxa
+Furthermore, in the Australian, Tachet, and the North American databases duplicate taxon entries 
+(either on species, genus or family level) existed that were amalgamated. 
+In case duplicate entries contained contrasting information on the same trait state the median 
+was taken. % ?What about zero's -> were disregarded
+
+% !Normalization/Standardization 
+Every trait within each grouping feature was standardized by the sum of all traits within 
+this particular grouping feature per taxon to get percentages per trait which can be used to 
+compare and harmonize taxa regarding their traits. %!Wording
+
+% TODO Various preprocessing steps: Taxonomical corrections
+
+% TODO a few words about spreadsheets etc?
+
+\subsection{Harmonization of traits and taxa}
 \begin{itemize}
-    \item Usage trait databases: 
+    \item Harmonization process: See also Schmera 2015 et al 
+    \item Differences in trait definitions
+    \item Sources of traits
+\end{itemize}
+
+% !What is harmonization? & Why is it needed?
+% The previous paragraphs described the data preparation steps needed in order to be able to harmonize
+% aquatic insect traits. 
+Harmonization of traits means amalgamating several similar traits into a single trait. 
+It has to be undertaken when grouping features from different sources (e.g. different regions) are
+used and the grouping features do not contain the same traits. 
+For example, in our study for the grouping feature locomotion the lowest number of traits that occur
+for all databases was in the New Zealand trait database ("Swimmer", "Burrower", "Crawler", "Sessil"). 
+Hence, in all other databases locomotion traits have been allocated into these four traits (see \ref{fig:harmon_overview_1}
+and \ref{fig:harmon_overview_2}).
+% !Taxonomical harmonization
+% Harmonization is crucial -> number of cases & comparability
+%?Give an example -> Clusteranalysis
+
+% !How was the harmonization done? -> technical aspect.
+Grouping features that differed in their traits among databases have been harmonised by 
+condensing the traits in such a way that in the end the same grouping features in all databases
+consisted of the same traits.  
+Thereby, traits were amalgamated based on ecological knowledge or expert judgment. %!Wording 
+Our approach of harmonizing the traits of the used databases is outlined in figures 
+\ref{fig:harmon_overview_1} and \ref{fig:harmon_overview_2}.
+
+% TODO: HArmonization for feeding mode AUS needs to be finished!
+\begin{figure}[H]
+   \centering
+   \includegraphics[width=16.5cm, height=10cm]{trait_overview1.jpg}
+   \caption{Proposed harmonization scheme for the grouping features
+   voltinism, feeding mode and locomotion. Shown are all traits for the 
+   used grouping features in the investigated trait databases and 
+   the harmonized traits in the end. Traits in curly brackets were 
+   harmonized to one trait. Traits highlighted in Grey were omitted. \newline
+   \textit{* Trait parasite was not available in New Zealand trait database.}
+   }
+   \label{fig:harmon_overview_1}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{trait_overview2.jpg}
+    \caption{Proposed harmonization scheme for the grouping features
+    respiration, size and body form.\newline
+    \textit{* Body form information provided by Philippe 
+    Usseglio-Polatera.}\newline
+    \textit{** Bluff(blocky) taxa have been reclassified
+    by Philippe Usseglio-Polatera using the traits streamlined,
+    flattened, cylindrical and spherical.} }
+    \label{fig:harmon_overview_2}
+ \end{figure}
+
+% TODO: Go deeper -> Trait definitions
+% !Trait harmonization subjective & always dangerous
+Not only the categorization of grouping features but also the definitions of 
+individual traits vary between databases, complicating harmonization. 
+% TODO: Present definition comparison -> For all traits?
+
+\section{Aggregation of traits}
+% TODO Describing \& testing different approaches
+% TODO Problem of coding of traits
+%! Why would one want to aggregate traits?
+% See Poff paper
+
+Two approaches were employed. 1) we used the preprocessed trait databases and 
+aggregated taxa from species level to family level by allocating them at the genus 
+level using the median. Then traits on genus-level were aggregated to
+family-level by using the mode. In cases where it was not possible to take the mode 
+(e.g. only distinct values or trait values like "1,1,2,2,3") the median was taken as well. 
+% TODO improve example
+2) we directly aggregated taxa to family level using the median.
+
+Finally, the resulting aggregated trait values were compared to traits assigned at 
+family level by experts. Those expert assignments on family level were not available for 
+all databases nor for all traits assigned. Hence, we restricted our analysis to ...
+% TODO: Comparison with traits assigned at family level for AUS & 
+% TODO North America (on subsets only possible) -> Find suitable subet
+% TODO: ATM done with all Taxa, just subset to Species data (does this make sense?)
+
+\section{Results}
+% TODO: For Results & Discussion taxonomic overlap between databases rather small
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MAIN RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Data preparation complex -> many decisions
+% Databases are not ideal (not standardized, different trait definitions)
+% Effect of trait aggregation
+% Trait values only slightly vary between complex and direct aggregation
+ % -> compare with family assignments: Roughly 25 % are classified differently
+    % -> Which and why? 
+    % -> Add statistical technique -> Maybe clustering?  
+ % -> test with weights?
+ % -> (effect of transforming binary to fuzzy codes -> US data subset test)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MAIN RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Additional ideas}
+
+Section Description of databases:
 \begin{itemize}
-    \item
+    \item Describe different databases briefly?
+    \item State goal of analysis $\rightarrow$ reference to second paper?
+\end{itemize}
 
-    \end{itemize}
-\end{itemize}
+\end{document}

### 2020-07-29 Paper/Draft_harmonization_paper.tex
29.07.2020: Paper - Res. almost ready for Co-Authors. Check calculation of missing information

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{float}
\usepackage[table,xcdraw]{xcolor}
\usepackage{color, colortbl}
\usepackage{longtable}
%\usepackage[sort&compress,square,comma,authoryear]{natbib}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{multirow}
% \graphicspath{{/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures/}}
\graphicspath{{Figures/}}
\usepackage{rotating}
\usepackage{geometry}
\usepackage{array}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{hhline}
\usepackage[
backend=biber,
style=authoryear,
sorting=nyt % sort by name year title
]{biblatex}
\addbibresource{Ref_invertebrate_DB.bib}

\usepackage{subfiles} % Best loaded last in the preamble

% functions and definitions
\definecolor{Gray}{gray}{0.9}

% horizontal space between two columns
\setlength{\tabcolsep}{2mm}

\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\renewcommand*{\thefootnote}{\alph{footnote}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{ OVERVIEW RESULTS: Harmonized invertebrate grouping feature databases}
\author{}%Stefan Kunz 
\date{}

\begin{document}
\maketitle

%\section{Introduction}

%! Understanding distribution of organisms and predicting the response to natural and anthropogenic stressors

%! Classification of species into groups with similar traits → expected consistent reaction to environmental gradients.

%! Definition how the term “trait” is used in this study

%! Trait-based approaches also used to understand community assembly, as a tool for biomonitoring, and to study effects of stressors to freshwater communities

%! As a result, comprehensive (but distinct) invertebrate trait databases have been compiled in the last decades for different regions

%! Trait-based approaches well suited for studies across regions

%! Large-scale studies require harmonized invertebrate trait databases (e.g. Brown et al. 2018)

%! -> How should such databases look like?:
%  Harmonized traits
%  Consistent scale of the used traits (e.g. fuzzy coding, binary coding, …)
%  (Consistent taxonomical resolution → depends on the study)
%  (Similar taxonomical coverage for the investigated traits across the used databases → depends on the study)

% !Goal:
%  Present a harmonized invertebrate trait database (for the regions Europe, North America, New Zealand & Australia)
%  How exactly are traits defined in each database? → We present an overview of definition discrepancies
%  How does the usage of harmonized trait data yields to different results in trait analysis compare to non harmonized trait data?  Re-analyzing the effect of anthropogenic salinization on biological traits in the River Werra (Germany, Szöcs et al. 2014)
%  Testing different ways of aggregating trait data → aggregation of traits often required (e.g. different taxonomical resolution between trait and abundance data)

%\section{Methods}
% !Present single invertebrate trait databases:
%  Which taxonomical groups are covered
%  Which traits are covered?
%  Traits from the following grouping features have been selected: 
%  - Voltinism, Reproduction, Body Form, Respiration, Size, Locomotion, Feeding Mode
% Why have these traits been selected?: 
%  Represent certain parts of the organisms biology:
%  - Life-History, Morphology, Ecology
%  No ecological traits: 
%  - not reported in New Zealand trait database
%  - (often correlated with environmental variables)
%  - (Relatively good taxonomical overlap for these traits between the used databases)
% Compare original databases in a table for better overview

%! Data processing:
%  Nominal and continuous traits converted to binary traits 
%  Normalize fuzzy codes to range [0 – 1]
%  Transform trait values in percentages
%  Selecting only taxa with complete trait profiles for the investigated traits
% Show data processing using a figure

%! Describe harmonization of traits:
%  Which similar traits were harmonized and how? Describe in figure
%  Problem of different definitions for the same traits between the used databases

%! Describe trait aggregation:
% Aggregation to family-level: 
%  Stepwise aggregation (Median to genus-level, Mode to family-level. If the mode does not exist the median is taken.)
%  Direct aggregation to family-level
%  Weighted aggregation: We calculated weights as the ratio of the number of taxa on species or genera-level per family of the taxa with complete trait profiles to taxa on species or genus-level per family initially present in the databases. Taxa on species and genus-level were aggregated by multiplying their trait values with the obtained weights. Then the weighted trait values were summed up per family for each trait.
% Present aggregation in a figure

%! Describe data analysis of harmonized traits:
%   We want replicate the trait analysis in an example study using our harmonized traits. Therefore, we use the study from Szöcs et al. 2014 on the effect of anthropogenic salinization on biological traits. For this small scale study we re-analyze the change in trait composition along the conductivity gradient using the traits we could harmonize. 
%  Using the same data analysis approach as Szöcs et al. 2014 our goal is to investigate if downstream and upstream sites in the study will still be characterized by the same traits.
%  Where trait information needs to be aggregated we will compare the different aggregation approaches with regard to how characterization of upstream and downstream sites will change.

%\section{Results \& Discussion}

\section*{Results harmonized grouping feature databases}

We used information on invertebrate traits for the regions Europe, North America, Australia, and New Zealand to establish harmonized grouping feature databases. Trait information for Europe was obtained by the Freshwaterecology database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}) and complemented by Tachet (\cite{usseglio-polatera_biomonitoring_2000}) when information was missing (e.g. for the grouping feature size). Trait information for North America was obtained from Laura Twardochleb and complemented by Vieira et al. 2006 (\cite{vieira_database_nodate}). Philippe Usseglio-Polatera provided information on body form for European and North American taxa. 
For Australia and New Zealand we used trait databases from Kefford et al. (\cite{kefford_integrated_2020}) and Philips and Smith respectively (\cite{Philips_and_Smith_NZ_DB_2018}).

We selected seven grouping features that we harmonized into 26 traits. The grouping features were chosen based on the availability of trait information across databases and so that they describe different parts of the biology of an organism: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
We used fuzzy coded traits for establishing our harmonized databases unless data quality prohibited and then we used binary traits, i.e categorical and continuous traits were converted into binary traits. Data processing prior harmonization also involved amalgamation of duplicate taxa on species, genus or family-level and conversion of trait affinities to percentages per trait. We omitted taxa with a lower taxonomic resolution than family-level. The following results relate to the harmonized grouping feature databases.

%! Completeness of trait information and taxonomical coverage
\subfile{Results/Taxonomic_cov_and_info_compl}

\newpage 
%! Comparison of trait aggregation methods
\subfile{Results/Results_trait_agg}

%! Presenting results of trait analysis using harmonized traits:
%  Did using harmonized traits yield different results regarding trait composition of down and upstream sites in Szöcs et al. 2014?
%  Had various trait aggregation methods an impact?
\newpage

\subfile{Results/Results_trait_harmonization}

\newpage

%! Discrepancies in trait definitions
% ?(Discuss history of trait values)
\subfile{Trait_def_table/Trait_definitions_table}

% Bibliography
\printbibliography
\newpage

%! SI
\subfile{Results/SI}

% Trait definitions 
\subfile{Trait_def_table/SI_trait_def_table2.tex}

\end{document}

### 2020-07-29 Paper/Old_Drafts/Outline_DB_Paper.tex
29.07.2020: Paper - Res. almost ready for Co-Authors. Check calculation of missing information

--- 2020-03-05 Paper/Outline_DB_Paper.tex
@@
 \usepackage{graphicx}
-\graphicspath{{Figures/}}
+\graphicspath{{Old_Figures/}}
 \usepackage{longtable}
+\usepackage{rotating}
+\usepackage{geometry}
+\usepackage{array}
 
@@
 
-\title{ OUTLINE: Harmonized macroinvertebrate trait database, Aggregation of traits, Trait definitions, Sources }
+\title{ DRAFT: Harmonized macroinvertebrate trait database, Aggregation of traits, Trait definitions }
 \author{}%Stefan Kunz 
@@
 \section{Introduction}
+% Half of all described freshwater invertebrates are aquatic insects
+% In the age of the Anthropocene invertebrates are exposed to multiple stressors such as chemical pollution, hydro-morphological modifications, invasive species and climate change. %?Sources 
+% Freshwater invertebrates play a crucial role for many ecosystem processes such as carbon cycling and water purification. In addition to their functional role,
+% Ten \% of all described species live in freshwaters, most of them being invertebrates, and thus represent a large part of animal biodiversity.
 
-% !General introduction: Invertebrates importance/biodiversity and stressor
-% ? use Traits mechanistic relationship, environmental filtering
-% Half of all described freshwater invertebrates are aquatic insects
+%! Understanding species distributions
+Understanding distributions of invertebrate communities and predicting effects of potential natural or anthropogenic stressors is a long time goal of freshwater research.
+Since the 1970s ecologists have started using organismal characteristics or traits to group aquatic insect species to understand their diversity.
+The first to do so was Cummins by assigning feeding mechanisms to aquatic insects (\cite{cummins_trophic_1973}).
+Since then many studies have been carried out trying to use invertebrate traits to understand ecosystem processes, as tool for biomonitoring, and the effects of multiple stressors on freshwater communities (\cite{statzner_can_2010, menezes_beyond_2010}).
+% TODO: needs further citation
+As a result, comprehensive databases on freshwater invertebrate traits have been compiled over the years (see table \ref{tab:trait_databases} for examples).
 
-In the age of the Anthropocene invertebrates are exposed to multiple stressors such 
-as chemical pollution, hydro-morphological modifications, invasive species and climate change. %?Sources 
-Freshwater invertebrates play a crucial role for many ecosystem processes such as 
-carbon cycling and water purification. In addition to their functional role, 10 \% of all 
-described species live in freshwaters, most of which being invertebrates, and thus represent a
-large part of animal biodiversity.
-Understanding distributions of invertebrate communities and predicting effects of 
-potential stressors is a long time goal of freshwater research. Since the 1970s 
-ecologists have started using organismal traits to group aquatic insect species % ?to understand what -> Check Cummins
-
-Traits are biological characteristics or ecological preferences measurable at the 
-individual organism. %? Source Lancaster? Find precises definition
-They reflect an organisms adaptation to its habitat. Trait based approaches in 
-ecology are based on the habitat template theory, that predicts where environmental conditions
-are similar trait composition should also converge, even across biogeographic boundaries. %?Source
-Furthermore, several studies suggested that trait variability is lesser on larger geographical
-scales than taxonomic variability. %?Source Bonada 
-Hence, trait based approaches can be a suitable tool for comparing the effect of various 
-environmental stressors to invertebrate communities on large scales or across regions. 
-%!General studies? Or more specific to studies for several regions
-% They have been used to understand species distributions, in predicting effects of various environmental
-% stressors to invertebrate communities, and as tool in biomonitoring. %? Source: Statzner & Beche 2010, Ralf Paper, Cummins Paper?
-Consequently, studies have been carried out that e.g. examine the relationship between climate
-and freshwater community assemblages using species traits. % TODO: Cite Bhowmik, cite Brown 
-% TODO: Enrich with examples -> Maybe for toxicants as well?
-Many of such studies combine information from several trait databases. For example, 
-Brown et al. used in their study traits from invertebrate trait databases from
-Europe, North America and New Zealand to investigate the effect of decreasing glacier cover
-to river ecosystems. %TODO Cite Brown
-
+Traits are defined as measurable characteristics and ecological preferences at the individual organism. %TODO: add citation
+They reflect an organisms adaptation to its habitat and provide a mechanistic link between a species and its environment.
+Trait based approaches in ecology have its theoretical foundation in the habitat template theory, that predicts where environmental conditions are similar trait composition should also converge, even across biogeographic boundaries (\cite{southwood_habitat_1977}).
+%TODO: cite Poff
+Several studies suggested that trait variability is lesser on larger geographical scales than taxonomic variability (\cite{bonada_taxonomic_2007}).
+Therefore, trait based approaches can be a suitable tool for comparing the effect of various environmental stressors to invertebrate communities on large scales or across regions.
+%? Source: Statzner & Beche 2010, Ralf Paper
+Consequently, studies have been carried that e.g.
+examine the relationship between climate change and freshwater community assemblages using species traits (\cite{bhowmik_large_2015, brown_functional_2018}).
+% More citations
+% ? Enrich with examples -> Maybe for toxicants as well?
+Many of such studies combine information from several trait databases.
+For example, Brown et al.
+used invertebrate trait databases from Europe, North America and New Zealand to investigate the effect of decreasing glacier cover to river ecosystems (\cite{brown_functional_2018}).
 % Studies that use information on aquatic invertebrate traits from different regions
@@
 % !Transition into trait data
-In fact, invertebrate trait data are increasingly available. Over the last decades aquatic 
-ecologists have compiled comprehensive databases on invertebrate traits for different regions 
-(see table \ref{tab:trait_databases} for examples). 
+As mentioned earlier, invertebrate trait data have become increasingly available over the last decades, also for different regions.
+
 % !Mention various problems with trait databases 
-However, researchers face various problems when they need to synthesize information from 
-multiple invertebrate trait databases. 
+However, researchers face various problems when they need to synthesize information from multiple invertebrate trait databases. 
 % !Trait terminology
-i) The use of inconsistent terminology across studies (see \cite{schmera_proposed_2015}
-for a comprehensive discussion). 
-For example, some studies used the term "trait" to describe a general 
-organismal property like "generations per year" (\cite{statzner_reproductive_1997}, 
-\cite{ussegliopolatera_biological_2000}), while in other studies this 
-term was related to categories like "bi/multivoltine" 
-(\cite{haybach_use_2004}, \cite{vieira_database_nodate}). Here, we follow 
-the proposal of Schmera et al. (2015) and use the term \textit{trait} for a morphological,
-physiological, or phenomenological feature measurable at the individual
-organism (e.g. tegument, gills, etc.) and the term \textit{grouping feature} to describe 
-a general property of related organismal traits (e.g. respiration). 
-%? Include measurement scale?
-%TODO: in concordance with previous paragraphs on trait definitions
+I) The use of inconsistent terminology across studies (see \cite{schmera_proposed_2015} for a comprehensive discussion). 
+For example, some studies used the term \textit{trait} to describe a general organismal property like "generations per year" (\cite{statzner_reproductive_1997}, \cite{ussegliopolatera_biological_2000}), while in other studies this
+term was related to categories like "bi/multivoltine" (\cite{haybach_use_2004}, \cite{vieira_database_nodate}). Here, we follow 
+the proposal of Schmera et al.
+(2015) and use the term \textit{trait} for a morphological, physiological, or phenomenological feature measurable at the individual organism (e.g.
+tegument, gills, etc.) and the term \textit{grouping feature} to describe a general property of related organismal traits (e.g.
+respiration).
+The \textit{membership state} gives the measurement scale (normally nominal or ratio scale) the trait is described on.
 %! Different traits used/definitions
-ii) Invertebrate trait databases from different regions are not standardized. 
-Often, the same grouping features are categorized using different traits. 
+II) Invertebrate trait databases from different regions are not standardized. Often, the same grouping features are categorized using different traits. 
 % TODO Example
-This is complicated by the use of different measurement scales. For example, trait databases 
-from North America use traditionally a binary coding (i.e. trait is expressed or not), 
-whereas most other trait databases (e.g. Tachet, freshwaterecology, and New Zealand) 
-use fuzzy coding (i.e. trait is expressed to a certain extent by the organism). 
-Hence, transformation of nominal scale to ratio scale or vice versa is required. %? Wording
-Furthermore, definitions for some traits differ as well across databases. 
-% TODO Example feeding!
+This is complicated by the use of different measurement scales.
+For example, trait databases from North America use traditionally a binary coding (i.e.
+trait is expressed or not), whereas most other trait databases (e.g.
+Tachet, freshwaterecology, and New Zealand) use fuzzy coding (i.e.
+trait is expressed to a certain extent by the organism).
+Hence, transformation of nominal scale to ratio scale or vice versa is required.
+%?
+Wording
+Furthermore, definitions and terminology applied to traits differ as well across databases.
+Recently, Schneider et al.
+advocated standard terminologies and ontologies for trait definitions after finding that trait databases for different organism groups (inter alia invertebrates) are rarely standardized and have low potential for data synthesis (\cite{schneider_towards_2019}).
+% ?Example (feeding)
 %! Taxonomical resolution & traits aggregation -> no guidance
@@
 % high taxonomical level -> high -> genus/family,...(Schmidt-Kloiber et al.)
-iii) Taxonomical resolution between databases differs, further complicating the
-synthesis of trait data from different regions. Some trait databases have recorded
-information on mixed levels of taxonomical resolution like the North American trait
-database or the Australian trait database. In contrast, trait information in the 
-freshwaterecology database is entirely recorded on species-level. %?ref to graphic
+III) Taxonomical resolution between databases differs, further complicating the synthesis of trait data from multiple regions.
+Some trait databases have recorded information on mixed levels of taxonomical resolution like the North American trait database or the Australian trait database.
+In contrast, trait information in the freshwaterecology database is entirely recorded on species-level.
+%?ref to graphic
 %TODO: Percentages of different levels of taxonomical resolutions in process overview graph 
-Using trait information on varying taxonomical levels is only possible when 
-traits are aggregated to the lowest taxonomical level that is shared by all used databases. 
-However, iv) so far studies comparing different ways of aggregating traits are lacking.
+Using trait information on varying taxonomical levels is only possible when traits are aggregated to the lowest taxonomical level that is shared by all used databases.
+However, IV) so far studies comparing different ways of aggregating traits are lacking.
 % Hence, guidance on how to perform a robust trait aggregation is missing. 
@@
 %!Incentive of our analysis:
-% no API/R packages 
-Given the problems mentioned above extensive data processing is required before researchers 
-can use multiple invertebrate trait databases for their work. 
-In this paper we examine difficulties that ecologists face when synthesizing trait 
-information from different invertebrate trait databases. We explore the effect of different
-decisions researches have to make when working with invertebrate trait data 
-from several sources, involving trait harmonization, handling different codings,
-normalization, and aggregation of traits.
+Given the problems mentioned above extensive data processing is required before researchers can use multiple invertebrate trait databases for their work.
+In this paper we examine difficulties that ecologists face when synthesizing trait information from multiple databases.
+We explore the effect of different decisions researches have to make when working with invertebrate trait data from several sources, involving trait harmonization, handling different codings, normalization, and aggregation of traits.
 %?Effect of a statistical analysis -> Clustering?
 %!What we did/Goal:
-Therefore, we harmonized six grouping features of different trait databases from four
-regions and aggregated the trait information to family-level. % ?Name Traits
-We discuss the harmonization and show the effect of different ways of aggregating 
-traits (inter alia Problem of different coding styles (fuzzy vs binary)).
+Therefore, we harmonized six grouping features of different macroinvertebrate trait databases from four regions and aggregated the trait information to family-level. % ?Name Traits
+We discuss the harmonization and show the effect of different ways of aggregating traits.
 We also present an overview of differences in trait definitions among databases.
-Finally, our paper compares the references for the trait information that 
-were specified in the trait databases we used.
+Finally, our paper compares the references for the trait information that were specified in the trait databases we used.
 
@@
 % TODO Give a motivation (better in introduction?)
-The harmonized databases are using the available information on aquatic invertebrate
-traits for the regions Europe, North America, Australia, and New Zealand. 
-Due to the different number and identity of grouping features in each database, 
-the following six grouping features were chosen for this study: locomotion, feeding mode, 
-respiration, voltinism, size, and body form. 
-%? Next two sentences can be removed?
-% Comment: For C of TPG Development pattern added
+The harmonized databases are using the available information on aquatic invertebrate traits for the regions Europe, North America, Australia, and New Zealand.
+Due to the different number and identity of grouping features in each database, the following six grouping features were chosen for this study: locomotion, feeding mode, respiration, voltinism, size, and body form.
 % TODO: Few words why these grouping features have been selected
 % TODO: Reasoning why no ecological grouping features have been used
-Trait information for Australia and New Zealand were retrieved from 
-a single database, respectively. For Europe we gathered trait information from the 
-freshwaterecology trait database (\url{https://www.freshwaterecology.info/}) 
-and complemented where possible missing information with the 
-Tachet trait database (\cite{usseglio-polatera_biomonitoring_2000}). 
-North American invertebrate traits were retrieved from Laura Twardochleb and 
+Trait information for Australia and New Zealand were retrieved from a single database, respectively.
+For Europe we gathered trait information from the freshwaterecology trait database (\url{https://www.freshwaterecology.info/}) and complemented where possible missing information with the
+Tachet trait database (\cite{usseglio-polatera_biomonitoring_2000}). North American invertebrate traits were retrieved from Laura Twardochleb and 
 complemented where possible by trait information from Vieira et al (\cite{vieira_database_nodate}).
-From now on, if we use the term European or North American trait database we refer to the combined 
-databases unless explicitly stated otherwise.
-We used all available information on invertebrates in the databases but restricted
-our analysis to those taxa that have complete trait profiles for the grouping features
-mentioned earlier. We are aware that imputation methods exist, which infer missing 
-information for traits by interpolating from related traits. % TODO: Cite Penone
-However, by using only complete data we were able to evaluate the taxonomical coverage
-per order within the databases. We consider this a helpful information for researchers
-who strive to fill data gaps.
+From now on, if we use the term European or North American trait database we refer to the combined databases.
+We used all available information on invertebrates in the databases but restricted our analysis to those taxa that have complete trait profiles for the investigated grouping features.
+We are aware that imputation methods exist, which infer missing information for traits by interpolating from related traits (\cite{penone_imputation_2014}).
+However, by using only complete data we were able to evaluate the taxonomical coverage within the databases.
+We consider this a helpful information for researchers who strive to fill data gaps.
 Table \ref{tab:trait_databases} gives an overview of the used databases.
-In the following paragraphs, we describe the data processing steps required to 
-establish a harmonized invertebrate trait database.
-
+% In the following paragraphs, we describe the data processing steps required to establish a harmonized invertebrate trait database.
+The results section trait aggregation methods are compared with each other and with traits assigned at family-level
+% The rest of the paper is structured as following:
+ % Trait definitions are compared and discussed in chapter...
 \begin{table}[H]
@@
 % !Issues with coding & scale in the trait databases
-Establishing a harmonized database required traits on the same measurement scale to 
-enable comparability. However, in the used databases traits varied within and among databases 
-in terms of measurement scale. Traits were either fuzzy coded, binary coded or 
-to a small extent coded as continuous variable (e.g. size). Fuzzy codes capture the variation 
-(i.e. temporal or spatial) in a trait and are represented by affinity scores 
-(sometimes termed membership state) which express a preference of a taxon to a certain trait.
-Usually, these scores range from 0 representing no affinity to an arbitrary maximum value which 
-represents high affinity. This type of coding uses the ratio scale and not the ordinal
-scale as one might intuitively assume. In fact, the intention of the developers of this 
-coding system was to convert affinity scores to percentages per trait, e.g. 
-for a grouping feature with four traits affinity scores of \textit{5, 6, 2, 2} are equal
-to \textit{1/3, 2/5, 2/15, 2/15} or \textit{33.3 \%, 40 \%, 13.3 \%, 13.3 \%} (\cite{chevenet_francois_fuzzy_1994}).
+Establishing a harmonized database required traits on the same measurement scale to enable comparability.
+However, in the used databases traits varied within and among databases in terms of measurement scale.
+Traits were either fuzzy coded, binary coded or to a small extent coded as continuous variable (e.g.
+size).
+Fuzzy codes capture the variation (i.e.
+temporal or spatial) in a trait and are represented by affinity scores which express the preference of a taxon to a certain trait.
+Usually, these scores range from 0 representing no affinity to an arbitrary maximum value which represents high affinity.
+This type of coding uses the ratio scale and not the ordinal scale.
+In fact, the intention of the developers of this coding system was to convert affinity scores to percentages per trait, e.g.
+for a grouping feature with four traits affinity scores of \textit{5, 6, 2, 2} are equal to \textit{1/3, 2/5, 2/15, 2/15} or \textit{33.3 \%, 40 \%, 13.3 \%, 13.3 \%} (\cite{chevenet_francois_fuzzy_1994}).
 We used fuzzy coded traits for establishing our harmonized databases where possible, otherwise binary traits.
 Categorical and continuous traits across all used databases were converted into binary traits.
-Implicitly, we assumed for binary variables that a value of 1 for a particular trait corresponded
-to the maximum affinity of a taxon for that particular trait.
+Implicitly, we assumed for binary variables that a value of 1 for a particular trait corresponded to the maximum affinity of a taxon for that particular trait.
 
-Two databases needed further data processing. Firstly, the Australian database which is a collection of seven trait databases. 
+Two databases needed further data processing.
+Firstly, the Australian database which is a collection of seven trait databases.
 Thus, several grouping features occur multiple times but with traits that have different types of codings and ranges.
@@
 The same traits originating from different sub-databases in the Australian trait database were allocated.
-To enable allocation of fuzzy coded and binary traits we applied a range normalization by dividing each fuzzy coded 
-trait by its potential maximum value. Consequently, the values of each trait were converted to a range from 0 to 1.
+To enable allocation of fuzzy coded and binary traits we applied a range normalization by dividing each fuzzy coded trait by its potential maximum value.
+Consequently, the values of each trait were converted to a range from 0 to 1.
 
 Secondly, the North American trait database which only contained traits on the nominal scale.
-We first converted nominal traits into binary traits. As a second approach we converted nominal traits for taxa 
-on species and genus-level into "pseudo" fuzzy codes by calculating the percentage of occurrence for each
-trait per genera and grouping feature. Both approaches were compared regarding the trait values they yielded.
-We refer to the version with binary traits as \textit{NOA\_bin} and to the version with pseudo fuzzy codes as 
-\textit{NOA\_fuzzy}. 
+We first converted nominal traits into binary traits.
+As a second approach we converted nominal traits for taxa on species and genus-level into "pseudo" fuzzy codes by calculating the percentage of occurrence for each trait per genera and grouping feature.
+Both approaches were compared regarding the trait values they yielded.
+% We refer to the version with binary traits as \textit{NOA\_bin} and to the version with pseudo fuzzy codes as \textit{NOA\_fuzzy}.
 % Better wording? traits from NOA data were converted to fuzzy codes by allocating at genus level using frequency on species level
@@
 % !Issue of duplicate taxa
-The Australian, Tachet, and the North American trait databases contained duplicate taxa entries
-- either on species, genus or family-level - which were amalgamated. 
+The Australian, Tachet, and the North American trait databases contained duplicate taxa entries - either on species, genus or family-level - which were amalgamated.
 The duplicate entries in the Australian trait database originated from the different sub-databases.
-As a result, many of the duplicate entries complemented each other (e.g. for a given trait one duplicate contained a value, 
-the other not). In those cases where several different values for a trait occurred, the average trait value was calculated. 
-The NOA\_bin database only contained 0 and 1 as entries. Hence, for duplicates the maximum value was taken.
+As a result, many of the duplicate entries complemented each other (e.g.
+for a given trait one duplicate contained a value, the other not).
+In those cases where several different values for a trait occurred, the average trait value was calculated.
+The North American database only contained 0 and 1 as entries.
+Hence, for duplicates the maximum value was taken.
 % Tachet: Fuzzy codes -> Mean
-For the tachet trait database duplicate entries were allocated using the mean if they contained contrasting
-information on the same trait. 
+For the tachet trait database duplicate entries were allocated using the mean if they contained contrasting information on the same trait. 
 % ?What about zero's -> were disregarded
@@
 % !Normalization/Standardization 
-Finally, every trait within each grouping feature was standardized by the sum of all traits 
-within this particular grouping feature per taxon to convert traits to percentages per trait. 
+Finally, every trait within each grouping feature was standardized by the sum of all traits within this particular grouping feature to convert traits to percentages per trait. 
 % which can be used to compare and harmonize taxa regarding their traits. %!Wording
@@
 % !What is harmonization? & Why is it needed?
-Harmonization of traits means amalgamating several similar traits into a single trait. 
-It has to be undertaken when grouping features from different sources (e.g. different regions) are
-used and the grouping features do not contain the same traits. 
-For example, in our study for the grouping feature locomotion the lowest number of traits that occur
-across all databases was in the New Zealand trait database ("Swimmer", "Burrower", "Crawler", "Sessil"). 
-Hence, in all other databases locomotion traits have been allocated into these four traits (see \ref{fig:harmon_overview_1}
-and \ref{fig:harmon_overview_2}).
+Harmonization of traits is the amalgamation of several similar traits into a single trait.
+It has to be undertaken when synthesizing a grouping feature from different sources which is not classified with the same traits.
+For example, in our study for the grouping feature locomotion the lowest number of traits that occur across all databases was in the New Zealand trait database ("Swimmer", "Burrower", "Crawler", "Sessil").
+Hence, in all other databases locomotion traits have been allocated into these four traits (figures \ref{fig:harmon_overview_1} and \ref{fig:harmon_overview_2}).
 % !Taxonomical harmonization
@@
 %?Give an example -> Clusteranalysis
-
 % !How was the harmonization done? -> technical aspect.
-Grouping features that differed in their traits among databases have been harmonised by condensing the traits in such a way
-that in the end the same grouping features in all databases consisted of the same traits.  
-Thereby, traits were amalgamated based on ecological knowledge or expert judgment. %!Wording 
+Grouping features that differed in their traits among databases have been harmonized by condensing the traits in such a way that in the end the same grouping features in all databases consisted of the same traits.
+Thereby, traits were amalgamated based on ecological knowledge or expert judgment.
+%!Wording
 Our approach of harmonizing the traits in the used databases is outlined in figures 
-\ref{fig:harmon_overview_1} and \ref{fig:harmon_overview_2}.
+\ref{fig:harmon_overview_1} and \ref{fig:harmon_overview_2}. Overall, the six grouping features were harmonized into 23 traits.
 
@@
 
-% TODO: Go deeper -> Trait definitions
-% !Trait harmonization subjective & always dangerous
-Not only the categorization of grouping features but also the definitions of individual traits vary between
-databases, complicating harmonization. 
-% TODO: Present definition comparison -> For all traits?
+ % !Present definition comparison 
+Not only the categorization of grouping features into traits but also the definitions of individual traits varies between databases, complicating harmonization. 
+%Thus, we present a differences in definitions of traits between the used databases.
 
@@
 % ? Aggregation considering different levels of taxonomical resolution
-Traits in the processed and harmonized trait databases were aggregated using three approaches.
-I) taxa on species-level and genus-level were stepwise aggregated to the family-level by initially 
-allocating them at the genus-level using the median. Then all traits were aggregated to family-level by using the mode. 
-In cases where it was not possible to take the mode, e.g. only distinct values, multiple duplicates, or multiple 
-duplicates and distinct values occurred the mean was taken. Hereafter, we abbreviate this aggregation type as \textit{stepwise\_agg}.
-II) we directly aggregated taxa to family level using the median. We denote this aggregation as \textit{direct\_agg}.
+Traits in the processed and harmonized trait databases were aggregated to family-level using three approaches.
+I) taxa on species-level and genus-level were stepwise aggregated to the family-level by initially allocating them at the genus-level using the median.
+Then all traits were aggregated to family-level by using the mode.
+In cases where it was not possible to take the mode, e.g.
+only distinct values, multiple duplicates, or multiple duplicates and distinct values occurred the mean was taken.
+Hereafter, we abbreviate this aggregation type as \textit{stepwise\_agg}.
+II) we directly aggregated taxa to family level using the median.
+We denote this aggregation as \textit{direct\_agg}.
 III) taxa were aggregated using a weighted approach, denoted as \textit{weighted\_agg}.
-The weights were determined as the ratio of how many taxa on species or genus-level were initially present per genera compared to  
-how many taxa on species or genus-level were present after selecting only taxa with complete trait profiles. 
-After determining the weights, taxa on species and genus-level were were aggregated to genus-level by multiplying their
-trait values by their respective weights. Then the weighted trait values were summed up per family for each trait.
+The weights were determined as the ratio of how many taxa on species or genus-level were initially present per genera compared to how many taxa on species or genus-level were present after selecting only taxa with complete trait profiles.
+After determining the weights, taxa on species and genus-level were were aggregated to genus-level by multiplying their trait values by their respective weights.
+Then the weighted trait values were summed up per family for each trait.
 
 The resulting aggregated trait values were compared to trait values assigned at family-level by experts.
-Trait assignments on family-level existed for the Australian database and the North American database, 
-but only for a limited subset of grouping features and taxa. For the Australian database we could
-compare aggregated trait values with assigned trait values for the grouping features feeding mode and 
-size. For the North American database we compared aggregated trait values with assigned trait values for
-the grouping features feeding mode, respiration, size, voltinism and locomotion, 
-albeit only for aquatic insects. 
-% TODO: Cite Chessman & Matt Pyne
-% TODO: At for which traits
-% TODO: ATM done with all Taxa, just subset to Species data (does this make sense?)
+Trait assignments on family-level existed for the Australian database and the North American database, but only for a limited subset of grouping features and taxa.
+For the Australian database we could compare aggregated trait values with assigned trait values resolved at family-level for the grouping features feeding mode and size by using data from Chessman et al.
+% TODO Cite Chessman
+% TODO: Comment here that the Chessman traits are also part of the AUS DB -> isn't this a bit a problem? Have been used in calculating
+% aggregated trait values
+For the North American database we could compare aggregated trait values with assigned trait values 
+on family-level for the grouping features feeding mode, respiration, size, voltinism and locomotion. 
+The trait information was obtained from the trait database by Pyne et al, which contains trait information
+for aquatic insects resolved on genus and family-level. Trait information on family-level was available for 
+94 families of which 61 (approximately 65 \%) were present in the aggregated North American trait database. 
+Trait information in the Pyne database was on the nominal scale and was converted to binary traits prior to the comparison with aggregated traits values. 
+% TODO: Cite Pyne
 
 \section{Results}
-% TODO: For Results & Discussion taxonomic overlap between databases rather small
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% MAIN RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 in the Australian and European database, and 26 \% of entries in the North American database. % TODO: Comment in Draft file for Ralf
-Selecting only taxa with complete trait profiles for the six grouping features and resolved at least at 
-family-level lead to the omission of many taxa in all databases except for the New Zealand database. 
+Selecting only taxa resolved at least at 
+family-level and with complete trait profiles for the six grouping features lead to the omission of many taxa in all databases except for the New Zealand database. 
 Out of the 21 orders that the New Zealand database covers, taxa of 20 orders remained after the selection process.
@@
 By contrast, in the Australian database, only taxa from five orders (Ephemeroptera, Megaloptera, Odonata, Plecoptera, 
-and Trichoptera) remained. Within these five orders, there was none where all families included in the database
-contained complete trait profiles. % Clearly the lack of data for body form results in the omission of many taxa
+and Trichoptera) remained.
+Within these five orders, there was none where all families included in the database contained complete trait profiles.
+% Clearly the lack of data for body form results in the omission of many taxa
 In the North American database, taxa of 18 orders had complete trait profiles, in the European database 9 orders.
@@
   \centering
-  \caption{How many entries have information for the 
+  \caption{Percentage of entries that have information for the 
   individual grouping features per database.} 
@@
 % TODO: Which entries have 0 %, which were not present initially?
-% ? Why difference for NOA & NOA_FC? -> rather exclude NOA_FC since it is a special case
 \begin{table}[H]
@@
 
+\subsection{Taxonomical overlap between trait databases}
+% TODO: taxonomic overlap between databases rather small
+
 \subsection{Deviance in trait values}
@@
 the same trait values (table \ref{tab:diff_trait_agg_methods}) across all grouping features.
-The two aggregation methods differed the most when applied to the Australian trait database, with 3.52 \% 
-cases differently classified. 
-% ? How much are trait values deviating?
-
-%! Taxa on family-level that were wrongly classified in all databases
+The amount of cases for were the two aggregation methods resulted in different trait values varied between approximately 1 \% and 3.5 \%.
+One case here is a taxa resolved on family-level with a specific trait.
 
 % ! Which traits/grouping features show mainly different values between both aggregation methods?
-% in all four databases: feed_herbivore, feed_gatherer, feed_shredder,
-% resp_gil, resp_teg, size_medium, size_small result 
+% In cases were \textit{stepwise\_agg} and \textit{direct\_agg} resulted in different trait values, they mostly deviated for the grouping features feeding mode and body size. 
+% Feeding mode herbivore, size medium and small were 3 families for the Australian trait database. Size medium was differently for 6 families in the European trait database. 
+% Feeding mode shredder 4 times New Zealand
+% Feeding mode gatherer, size small, size medium, resp gil 6 times North American
+%! Taxa that were differently classified in all databases
+% give Leptophelibidae example & 
+% Among the differently classified taxa are mostly aquatic insects.
+
+There was no family that had diverging trait values produced by the aggregation methods in all databases, although for Leptophlebiidae (order Ephemeroptera) the aggregation methods produced different trait values in the European, North American and Australian trait databases.
+%! How much are trait values deviating?
+% TODO: Maybe leave out and put in later
+% If aggregated trait values were deviating between the \textit{stepwise\_agg} and \textit{direct\_agg} they
+% mostly ranged
+
 \begin{table}[ht]
@@
       \label{tab:diff_trait_agg_methods}
-    \begin{tabular}{lr}
+      \begin{tabular}{lrr}
         \hline
-    Database & Deviating cases [\%] \\ 
+      Database & Deviating cases [\%] & Number of cases \\ 
         \hline
-    Australia & 3.52 \\ 
-      Europe & 2.17 \\ 
-      New Zealand & 1.03 \\ 
-      North America & 2.66 \\ 
+      Australia & 3.52 & 483 \\ 
+        Europe & 2.17 & 2024 \\ 
+        New Zealand & 1.03 & 2134 \\ 
+        North America & 2.66 & 2139 \\ 
         \hline
@@
 % ! Comparison with traits assigned on family level
-% ? Influence on hierarchical clustering
+\subsection{Comparison aggregated trait values and trait values assigned at family-level}
 
-% ! Comparison trait definitions?
-%
+\subsubsection{Australia}
+
+\subsubsection{North America}
+Overall, approximately 21 \% of trait values evaluated at family-level by Pyne et al.
+were different to the trait values obtained by \textit{direct\_agg} in the North American trait database for families both databases share.
+Compared to the \textit{stepwise\_agg}, 22 \% of trait values from Pyne et al.
+were different.
+Trait values for body \textit{size medium} were most often deviating between the \textit{direct\_agg} and traits assigned at family-level (45.9 \% of all families, total number of taxa on family-level: 61), followed by voltinism
+\textit{univoltine} (36 \%), and feeding mode \textit{gatherer} (32.8 \%).
+Since both aggregation methods mostly resulted in similar trait values, differences in trait values between \textit{stepwise\_agg} and traits assigned at family-level were similar to the differences for \textit{direct\_agg}.
+The most deviating trait was again body \textit{size medium} (47.5 \% of all families), followed by voltinism \textit{univoltine} (37.7 \%), and \textit{size small} (29.5 \%).
+Among all compared traits there were always differences in aggregated trait values and
+assigned values at family-level for at least families from one order.
+Tables S\ref{tab:SI_perc_dir_agg_expert_NOA} and S\ref{tab:SI_perc_stepwise_agg_expert_NOA} give an overview over how many families were differently evaluated by the aggregation methods compared to Pyne's database for all investigated traits.
+%! Most deviating cases per order?
+Regarding deviating cases per order, families from Ephemeroptera had most often different assigned trait values compared to the trait values obtained by the \textit{direct\_agg} (24.37 \% of cases, table S\ref{tab:SI_perc_dir_agg_expert_family_NOA}).
+For the \textit{stepwise\_agg} families from Trichoptera (24.51 \% of cases, table S\ref{tab:SI_perc_stepwise_agg_expert_family_NOA}) were deviating from the assigned trait values.
+For both aggregation methods families from Odonata differed the least often to the assigned trait values (16.18 \% respectively).
+
+%! Discuss range of trait deviations
+Trait values ranged between $0$ and $1$.
+Hence, the maximum deviation possible is 1 (100 \%).
+Regarding the cases with deviations in trait values between \textit{direct\_agg} and at family-level assigned traits, 26 \% of the cases showed a deviation of 100 \%, i.e.
+the value obtained by \textit{direct\_agg} was 0 or 1 while the value on family-level assigned was 1 or 0 (Figures S\ref{fig:trait_dev_dir_agg_feeding} to S\ref{fig:trait_dev_stepwise_agg_volt}.).
+Maximum deviations occurred within all orders except for Dipterans.
+Most often the trait \textit{size medium} (8 times, 14 \% of all maximum deviations) deviated by 100 \%, followed by the trait \textit{univoltine} (7 times, 12.3 \% of all maximum deviations) and trait \textit{size small} (7 times).
+
+Comparison of the cases with deviations in trait values between \textit{stepwise\_agg} and at family-level assigned traits shows a s similar picture.
+25.8 \% of the cases showed a deviation of 100 \%.
+Maximum deviations occurred as well within all orders except for Dipterans.
+Most often the trait \textit{size medium} (8 times, 13.3 \% of all maximum deviations) deviated by 100 \%, followed by the trait \textit{size large} (7 times, 11.7 \% of all maximum deviations), trait \textit{size small} and trait \textit{univoltine} (both 6 times, 10 \% of all maximum deviations).
+
+% For all cases were  
+% trait values from assigned traits at family-level and trait values by \textit{direct\_agg} deviated, approximately 
+% 20 \% deviated by 25 \%, i.e. the aggregated value was either 0.25 or 0.75, while the assigned value at family-level was 0 or 1
+% 42 \% of cases showed a deviation of 50 \%. In these cases \textit{direct\_agg} was always resulted 0.5 and family-level was 0 or 1.
+% % 8.2 % of cases 75 \% deviation
+
+% ? Influence on hierarchical clustering -> suggest to Ralf
+
+\subsection{Discrepencies in trait definitions}
+
+\subsubsection{Feeding Mode}
+The determination of the feeding mode of an organism is derived from the classification into functional-feeding guilds and is based on what organisms consume, their morphology of mouthparts and their feeding behavior.
+% TODO: cite Moog
+The freshwaterecology database, the Tachet database and the North American trait database state trait explanations describing the food sources for each trait related to the feeding mode.
+In the North American the method of dietary intake is also roughly described (e.g.
+piercers pierce prey tissues and suck fluids).
+The other databases give no deeper description of how exactly traits of the grouping feature feeding mode are defined.
+As mentioned earlier, each databases uses different traits to describe the feeding mode (\ref{fig:harmon_overview_1}).
+There are also gradual differences within the definitions between the traits that occur in all databases belonging to the grouping feature feeding mode.
+For example, in the North American trait database shredders are defined as insects that shred on decomposing vascular plant tissue.
+However, freshwaterecology and tachet database include both decomposing and living plant material as food source for shredders and also additionally coarse particulate organic material (CPOM).
+The North American trait database summarizes taxa that scrape, shred or pierce living aquatic plants with another trait termed herbivore.
+
+The freshwaterecology database states as reference for their classification of the grouping feature feeding mode Moog et al.
+(\cite{moog_comprehensive_nodate}), who in turn based their classification on Cummins (\cite{cummins_trophic_1973}), Cummins and Klug (\cite{cummins_feeding_1979}), and Merrit and Cummins.
+%TODO: cite Cummins & Merrit
+Also in the North American database, the classification of nutritional forms is derived from the publication of Cummins (\cite{cummins_trophic_1973}).
+For the New Zealand trait databases it is not explicitly stated how they derived their classification of the feeding mode.
+
+% Tachet cites generally: Tachet H., Bournaud M., Richoux P. & Usseglio-Polatera P. (2000) - Invertébrés d'eau douce : systématique, biologie, écologie. CNRS Editions, Paris, 588 p.
+
+% Australia: Collection of 7 different trait databases
+
+%\input{Trait_def_table/Trait_definitions_table.tex}
+
+\newpage
+\printbibliography
+
+\section{Supporting Information}
+
+\begin{table}[H]
+  \centering
+  \caption{Percentage of families differently evaluated by 
+  \textit{direct\_agg} and Pyne et al. for all compared traits.} 
+  \label{tab:SI_perc_dir_agg_expert_NOA}
+  \begin{tabular}{lr}
+    \hline
+  Trait & Families differently evaluated [\%] \\ 
+    \hline
+    size\_medium & 45.90 \\ 
+    volt\_uni & 36.07 \\ 
+    feed\_gatherer & 32.79 \\ 
+    size\_small & 31.15 \\ 
+    size\_large & 22.95 \\ 
+    locom\_crawl & 22.95 \\ 
+    volt\_bi\_multi & 22.95 \\ 
+    resp\_teg & 22.95 \\ 
+    resp\_gil & 21.31 \\ 
+    feed\_filter & 16.39 \\ 
+    feed\_herbivore & 16.39 \\ 
+    volt\_semi & 14.75 \\ 
+    locom\_swim & 13.11 \\ 
+    feed\_shredder & 13.11 \\ 
+    locom\_burrow & 9.84 \\ 
+    resp\_pls\_spi & 8.20 \\ 
+    feed\_predator & 8.20 \\ 
+     \hline
+  \end{tabular}
+  \end{table}
+
+\begin{table}[H]
+    \centering
+    \caption{Percentage of families differently evaluated by
+    \textit{stepwise\_agg} and Pyne et al.for all compared traits.} 
+    \label{tab:SI_perc_stepwise_agg_expert_NOA}
+    \begin{tabular}{lr}
+      \hline
+    Trait & Families differently evaluated [\%] \\ 
+      \hline
+    size\_medium & 47.54 \\ 
+      volt\_uni & 37.70 \\ 
+      size\_small & 29.51 \\ 
+      resp\_gil & 29.51 \\ 
+      resp\_teg & 29.51 \\ 
+      feed\_gatherer & 29.51 \\ 
+      size\_large & 26.23 \\ 
+      locom\_crawl & 24.59 \\ 
+      volt\_bi\_multi & 22.95 \\ 
+      volt\_semi & 16.39 \\ 
+      feed\_filter & 16.39 \\ 
+      feed\_herbivore & 14.75 \\ 
+      locom\_swim & 13.11 \\ 
+      feed\_shredder & 13.11 \\ 
+      locom\_burrow & 9.84 \\ 
+      resp\_pls\_spi & 9.84 \\ 
+      feed\_predator & 9.84 \\ 
+       \hline
+    \end{tabular}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \caption{Percentage of families differently evaluated
+  by \textit{direct\_agg} and Pyne et al. for all compared orders.} 
+  \label{tab:SI_perc_dir_agg_expert_family_NOA}
+  \begin{tabular}{lr}
+  \hline
+  Order & Families differently evaluated direct\_agg [\%] \\ 
+  \hline
+  Ephemeroptera & 24.37 \\ 
+    Coleoptera & 23.53 \\ 
+    Megaloptera & 23.53 \\ 
+    Trichoptera & 21.24 \\ 
+    Diptera & 20.59 \\ 
+    Plecoptera & 19.85 \\ 
+    Hemiptera & 16.47 \\ 
+    Odonata & 16.18 \\ 
+  \hline
+  \end{tabular}
+  \end{table}
+
+\begin{table}[H]  
+  \centering
+  \caption{Percentage of families differently evaluated
+  by \textit{stepwise\_agg} and Pyne et al. for all compared orders.} 
+  \label{tab:SI_perc_stepwise_agg_expert_family_NOA}
+  \begin{tabular}{lr}
+  \hline
+  Order & Families differently evaluated stepwise\_agg [\%] \\ 
+  \hline
+  Trichoptera & 24.51 \\ 
+    Ephemeroptera & 23.95 \\ 
+    Coleoptera & 23.53 \\ 
+    Megaloptera & 23.53 \\ 
+    Hemiptera & 21.18 \\ 
+    Diptera & 20.59 \\ 
+    Plecoptera & 19.85 \\ 
+    Odonata & 16.18 \\ 
+  \hline
+  \end{tabular}
+  \end{table}
+
+\begin{figure}[H]
+  \centering
+  \caption{Deviance of trait values obtained with \textit{direct\_agg} compared to at family level assigned traits by Pyne et al. \newline
+  \textit{N} denotes the number of families per order.}
+  \label{fig:trait_dev_dir_agg_feeding}
+  \includegraphics[width=14cm, height=7.5cm]{trait_deviations_dir_famlvl_feed.png}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{.}
+  \label{fig:trait_dev_dir_agg_locom}
+  \includegraphics[width=14cm, height=7.5cm]{trait_deviations_dir_famlvl_locom.png}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{.}
+  \label{fig:trait_dev_dir_agg_resp}
+  \includegraphics[width=14cm, height=7.5cm]{trait_deviations_dir_famlvl_resp.png}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{.}
+  \label{fig:trait_dev_dir_agg_size}
+  \includegraphics[width=14cm, height=7.5cm]{trait_deviations_dir_famlvl_size.png}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{.}
+  \label{fig:trait_dev_dir_agg_volt}
+  \includegraphics[width=14cm, height=7.5cm]{trait_deviations_dir_famlvl_size.png}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{.}
+  \label{fig:trait_dev_stepwise_agg_volt}
+  \includegraphics[width=14cm, height=7.5cm]{trait_deviations_stepwise_famlvl_feed.png}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{.}
+  \label{fig:trait_dev_stepwise_agg_locom}
+  \includegraphics[width=14cm, height=7.5cm]{trait_deviations_stepwise_famlvl_locom.png}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{.}
+  \label{fig:trait_dev_stepwise_agg_resp}
+  \includegraphics[width=14cm, height=7.5cm]{trait_deviations_stepwise_famlvl_resp.png}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{.}
+  \label{fig:trait_dev_stepwise_agg_size}
+  \includegraphics[width=14cm, height=7.5cm]{trait_deviations_stepwise_famlvl_size.png}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \caption{.}
+  \label{fig:trait_dev_stepwise_agg_volt}
+  \includegraphics[width=14cm, height=7.5cm]{trait_deviations_stepwise_famlvl_size.png}
+\end{figure}
 

### 2020-07-29 Paper/Results/Results_trait_harmonization.tex
29.07.2020: Paper - Res. almost ready for Co-Authors. Check calculation of missing information

\documentclass[../Draft_harmonization_paper.tex]{subfiles}
% \documentclass{article}
% \usepackage[utf8]{inputenc}
% \usepackage{hyperref}
% \usepackage{float}
% \usepackage[table,xcdraw]{xcolor}
% \usepackage{color, colortbl}
% \usepackage{longtable}
% %\usepackage[sort&compress,square,comma,authoryear]{natbib}
% \usepackage{booktabs}
% \usepackage{graphicx}
% \graphicspath{{/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures/}}
% \usepackage{longtable}
% \usepackage{rotating}
% \usepackage{geometry}
% \usepackage{array}

% \definecolor{Gray}{gray}{0.9}

% \newcommand{\specialcell}[2][c]{%
%   \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\begin{document}
%! Trait (species) scores along segments of river

\section{Re-analysis of Szöcs et al. 2014 using harmonized and aggregated grouping features}

To investigate how harmonizing grouping features and aggregating invertebrate traits might change the results in analysis of trait-environment relationships we replicated the data analysis of Szöcs et al. 2014 (\cite{szocs_effects_2014}) using the harmonized grouping features \textit{Body size, Feeding mode, Locomotion, Reproduction/Oviposition, Respiration, and Voltinism} (21 grouping features have been used in total) and aggregated traits using the aforementioned aggregation methods. The harmonized grouping features used are those that responded strongly to salinity in the study of Szöcs et. al. 2014, except for life cycle duration. %!Aggr. methods
For testing the effect of aggregated traits we assigned to each taxon in Szöcs et al. 2014 the aggregated trait value from the established harmonized European grouping feature database for its corresponding family.

Here, we limit our analysis to the RDA of traits constrained by electric conductivity of the original publication (see appendix \ref{subsec:SI_szoecs_reanalysis} for a more in depth comparison to the original results). Overall, using the harmonized grouping features lead only to slightly different results in comparison to the original analysis. Sites with high salinity were characterized by multivoltine, ovivoparous, gill-respirating, and shredder species. Only species with the trait life cycle duration $> 1$ year fail to characterize sites with high salinization. Also, life cycle duration $<= 1$ year is not anymore characterizing sites not impacted by salinity. Like in the original analysis, transition and upstream sites from the point source are characterized by univoltine species and species that lay their eggs in an aquatic environment. The usage of aggregated traits yielded similar species scores for every aggregation method. Also, for every aggregation method compared, using at family-level aggregated traits did only slightly change the RDA species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}). Hence, the interpretation of the trait composition follows is the same as when only using harmonized grouping features. An overview over the harmonization for the European trait databases can be found in the supporting information in section \ref{sec:SI_harmonization_EU}.

% Mention that threshold according to mahalanobis distance is almost reached for life cycle duration

% Species scores
\begin{figure}[H]
    \label{fig:rda_species_scores}
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
    \caption{Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonized traits, and using harmonized traits and assigning traits aggregated to family level)}
    \label{fig:rda_species_scores}
\end{figure}

\end{document}

### 2020-07-29 Paper/Results/SI.tex
29.07.2020: Paper - Res. almost ready for Co-Authors. Check calculation of missing information

\documentclass[../Draft_harmonization_paper.tex]{subfiles}

\begin{document}

\section*{Supporting Information}

\subsection*{Comparison of the trait aggregation methods with each other}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Comparison_trait_agg_methods.png}
    \caption{Shown are mean absolute differences with standard deviations per regions. Compared aggregation methods are displayed on the y axis. N indicates the number of cases where differences occurred.}
\end{figure}

% \subsection*{Differences in trait affinities obtained by trait aggregation methods compared to traits assigned at family-level}
%? Cases where trait affinities aggregated through \textit{direct\_agg} differed more than 60 \% from trait affinities assigned at family-level by Chessman 2017

\newpage

\subsection*{Re-analysis of Szöcs et al. 2014 using harmonized and aggregated grouping features.}
\label{subsec:SI_szoecs_reanalysis}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{RDA_traits_harmonized.png}
    \caption{RDA of traits constrained by electric conductivity using harmonized grouping features. Boxplot of site scores along the conductivity axis ($31.44 \%$ explained variance, p = 0.001, 1000 permutations). Rug on the left indicates trait scores on the conductivity axis. Only traits with a mahalanobis distance greater than 5.02 were labeled in accordance to the procedure in Szöcs et al. 2014.
    } 
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{RDA_traits_Szoecs_2014.png}
    \caption{RDA of traits constrained by electric conductivity. Boxplot of site scores along the conductivity axis ($30.09 \%$ explained variance, p = 0.001, 1000 permutations). Rug on the left indicates trait scores on the conductivity axis. Only traits with a mahalanobis distance greater than 5.02 were labeled.
    } 
\end{figure}

\section*{Trait distribution along first RDA axis} 
\begin{figure}[H]
    \centering
    \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_harmonized.png}
    \caption{Trait scores on the first RDA axis for harmonized traits and traits of the grouping feature \textit{life cycle duration}.
    } 
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_Szoecs_2014.png}
    \caption{Trait scores on the first RDA axis for the traits responding to high salinity in Szöcs et al. 2014
    .
    }
\end{figure}

\newpage
\section*{Linear models of trait proportions}
\textit{Linear models of trait proportions with harmonized traits:}
\begin{table}[ht]
    \centering
    \caption{Results of linear models for the four selected harmonized traits and life cycle duration $>$ 1 year. Trait proportions were logit transformed prior model building, estimates are on the logit scale. Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically significant effects (p $<$ 0.05).}
    \begin{tabular}{lccccc}
    \hline
    & \specialcell{Feeding mode:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell{Voltinism:\\ bi- or multivoltine} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\ 
    \hline
    Intercept ($=$ upstream) & \textbf{-1.041} & \textbf{-0.486} & 0.375* & \textbf{-0.823} & 0.092\\ 
    Downstream & \textbf{0.926} & \textbf{0.605} & \textbf{1.376} & \textbf{1.684} & \textbf{0.854}\\ 
    Downstream x 2008 & -0.117 & 0.106 & -0.235 & -0.088 & -0.317\\ 
    Downstream x 2009 & 0.030 & -0.056 & 0.001 & 0.245 & 0.180\\ 
    Year 2008 & -0.167 & -0.115 & 0.033 & -0.182 & -0.151\\ 
    Year 2009 & 0.175 & 0.086 & -0.088 & 0.246 & 0.141\\ 
    \hline
    \end{tabular}
    \textit{* p.value = 0.055}
\end{table}
\newline
\newline
\newline
\textit{Linear models of trait proportions Szöcs et al. 2014:}
\begin{table}[ht]
    \centering
    \caption{Results of linear models for the five selected traits for Szöcs et al. 2014. Trait proportions were logit transformed prior model building, estimates are on the logit scale.
    Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically
    significant effects (p $<$ 0.05).}
    \begin{tabular}{lccccc}
    \hline
    & \specialcell{Feeding habits:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell {Cycles per year:\\ $>$ 1} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\ 
    \hline
    Intercept ($=$ upstream) & \textbf{-0.853} & \textbf{-0.478} & \textbf{0.603} & \textbf{-0.838} & 0.111 \\ 
    Downstream & \textbf{0.819} & \textbf{0.594} & \textbf{1.297} & \textbf{1.679} & \textbf{0.839} \\ 
    Downstream x 2008 & -0.155 & 0.102 & -0.227 & -0.070 & -0.314 \\ 
    Downstream x 2009 & 0.073 & -0.053 & -0.020 & 0.248 & 0.176 \\ 
    Year 2008 & -0.122 & -0.112 & 0.026 & -0.192 & -0.154 \\ 
    Year 2009 & 0.167 & 0.084 & -0.104 & 0.250 & 0.139 \\ 
    \hline
    \end{tabular} 
\end{table}

\section*{Trait proportions over time}
\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_harmonized.png}
    \caption{Proportions for the four harmonized traits that have been promoted by salinization and life cycle duration $>$ 1 year for down- and upstream sites.
    } 
\end{figure}

% Trait proportions over time
\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_Szoecs_2014.png}
    \caption{Proportions for five selected traits for down- and upstream sites (traits that have been promoted by salinization) from Szöcs et al. 2014.} 
\end{figure}

\newpage

\section*{Harmonization of the European trait databases}
\label{sec:SI_harmonization_EU}

% \cellcolor{blue!25}
\begin{longtable}{llll}
%\begin{table}[ht]
%    \centering
    \caption{Representation of traits per grouping feature for the used trait databases. The color coding indicates traits that have been harmonized. Cyan colored traits have not been used because they either represented ambiguous traits or traits that were not compatible with the traits of the other databases. Harmonization was done by assigning the maximum affinity of the allocated traits for the respective taxa to the harmonized trait.}
    \endfirsthead
    \endhead
    %\begin{tabular}{llll}
    \hline
    Grouping feature & Freshwater ecology & Tachet & Harmonized traits \\ 
    \hline
    \hline
    Voltinism & Semivoltine & Semivoltine & Semivoltine \\ 
    Voltinism & Univoltine & Univoltine & Univoltine \\ 
    \rowcolor{gray!25}
    Voltinism & Bivoltine & Polyvoltine & Bi/Multivoltine \\ 
    \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Trivoltine &  &  \\ 
    \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Multivoltine &  &  \\ 
    \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Flexible &  &  \\ 
    \rowcolor{blue!25}
    \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Shredder & Shredder & Shredder \\ 
    \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Miner & Deposit-feeder & Gatherer \\ 
    \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Xylophagus & \cellcolor{blue!50}Absorber & \cellcolor{blue!50}Filterer \\ 
    Feeding Mode & Gatherer & \cellcolor{blue!50}Filter-feeder & Herbivore \\ 
    \cellcolor{blue!50}Feeding Mode & \cellcolor{blue!50}Active filterer & Scraper & Predator \\ 
    \cellcolor{blue!50}Feeding Mode & \cellcolor{blue!50}Passive filterer & Predator & Parasite \\ 
    Feeding Mode & Grazer & Parasite &  \\ 
    Feeding Mode & Predator & \color{cyan}Piercer (plants or animals) &  \\ 
    Feeding Mode & Parasite &  &  \\ 
    \color{cyan}Feeding Mode & \color{cyan}Other &  &  \\ 
    \hline
    \rowcolor{green!25}
    Locomotion & Swimming/scating & Surface swimmer & Swimmer \\ 
    \cellcolor{green!25}Locomotion & \cellcolor{green!25}Swimming/diving & \cellcolor{green!25}Full water swimmer & Burrower \\ 
    Locomotion & Burrowing/boring & Burrower & Crawler \\ 
    Locomotion & Sprawling/walking & Crawler & \cellcolor{green!50}Sessil \\ 
    \cellcolor{green!50}Locomotion & \cellcolor{green!50}(semi) sessil & \cellcolor{green!50}Temporarily attachted &  \\ 
    \color{cyan}Locomotion & \color{cyan}Other & \cellcolor{green!50}Permanently attached &  \\ 
    \color{cyan}Locomotion &  & \color{cyan}Interstitial &  \\ 
    \color{cyan}Locomotion &  & \color{cyan}Flier &  \\
    \hline
    Respiration & Tegument & Tegument & Tegument \\ 
    Respiration & Gill & Gill & Gills \\ 
    \rowcolor{orange!25}
    Respiration & Plastron & Plastron & Plastron, spiracle \\ 
    \cellcolor{orange!25}Respiration & \cellcolor{orange!25}Spiracle (aerial) & \cellcolor{orange!25}Spiracle (aerial) &  \\ 
    \color{cyan}Respiration & \color{cyan}Hydrostatic vesicle & \color{cyan}Hydrostatic vesicle (aerial) &  \\ 
    \color{cyan}Respiration & \color{cyan}Tapping (air stores of aq. plants) &  &  \\ 
    \color{cyan}Respiration & \color{cyan}Excursion/Extension (to surface) &  &  \\ 
    \hline
    Body size &  & $<$= 0.25cm & Small ($<$ 1 cm) \\ 
    Body size &  & $>$ 0.25 - 0.5cm & Medium ($>$= 1cm - 2 cm) \\ 
    Body size &  & $>$ 0.5- 1cm & Large ($>$= 2 cm) \\ 
    Body size &  & $>$ 1 – 2 cm &  \\ 
    Body size &  & 2 – 4 cm &  \\ 
    Body size &  & 4 – 8 cm &  \\ 
    Body size &  & $>$ 8 cm &  \\ 
    \hline
    Reproduction & ovovivipar & ovoviviparity & ovoviviparity \\ 
    \rowcolor{purple!25}
    Reproduction & free isolated eggs & isolated eggs, free & aquatic eggs \\ 
    \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}cemented isolated eggs & \cellcolor{purple!25}isolated eggs, cemented & terrestrial eggs \\
    \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}fixed clutches & \cellcolor{purple!25}clutches, cemented or fixed &  \\ 
    \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}free clutches & \cellcolor{purple!25}clutches, free &  \\ 
    \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}clutches in vegetation & \cellcolor{purple!25}clutches, in vegetation &  \\ 
    Reproduction & terrestrial clutches & clutches, terrestrial &  \\ 
    \color{cyan}Reproduction & \color{cyan}asexual & \color{cyan}asexual reproduction &  \\ 
    \color{cyan}Reproduction & \color{cyan}parasitic &  &  \\ 
    \hline
    %\end{tabular}
%\end{table}
\end{longtable}

%%%%%%%%%%%%%%%%%%%% OLD %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection*{Deviance in trait affinities between \textit{stepwise\_agg} and \textit{direct\_agg (median)}}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{Deviances_stepwise_dir_overview.png}
%     \caption{Affinity deviances for all deviating cases between the \textit{stepwise\_agg} and \textit{direct\_agg}, see section \ref{sec:dev_stepwise_direct_agg}.}
%     \label{fig:stepwise_dir_agg}
% \end{figure}

% \subsection*{Comparison of trait affinity values \textit{direct\_agg} using median or mean}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{Deviances_dir_median_mean_overview.png}
%     \caption{Affinity deviances for all deviating cases between the \textit{direct\_agg (median)} and \textit{direct\_agg (mean)}, see section \ref{sec:comp_direct_agg_median_mean}.}
%     \label{fig:dir_agg_median_mean}
% \end{figure}

% \subsection*{Deviances in trait affinities between \textit{direct\_agg} and \textit{weighted\_agg}}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{Deviances_dir_weighted_overview.png}
%     \caption{Affinity deviances for all deviating cases of comparisons between the \textit{direct\_agg (median)} and \textit{direct\_agg (mean)} with \textit{weighted\_agg}, see section \ref{sec:dev_dir_agg_weighted}.}
%     \label{fig:dir_agg_median_mean_weighted}
% \end{figure}

\end{document}

### 2020-07-29 Paper/Results/Taxonomic_cov_and_info_compl.tex
29.07.2020: Paper - Res. almost ready for Co-Authors. Check calculation of missing information

% \documentclass{article}
\documentclass[../Draft_harmonization_paper.tex]{subfiles}

% \usepackage[utf8]{inputenc}
% \usepackage{hyperref}
% \usepackage{float}
% \usepackage[table,xcdraw]{xcolor}
% \usepackage{color, colortbl}
% \usepackage{longtable}
% %\usepackage[sort&compress,square,comma,authoryear]{natbib}
% \usepackage{booktabs}
% \usepackage{graphicx}
% \graphicspath{{/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures/}}
% \usepackage{longtable}
% \usepackage{rotating}
% \usepackage{geometry}
% \usepackage{array}

% \definecolor{Gray}{gray}{0.9}

% \newcommand{\specialcell}[2][c]{%
%   \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\begin{document}

\section{Taxonomic coverage of the trait databases}

Regarding the taxonomical coverage, the New Zealand database has, as expected, the smallest taxon pool (Table \ref{tab:tax_coverage}). By contrast, the largest taxon pool is spanned by the European trait database with 4225 taxa followed by the North American trait database that contained trait information on 3542 taxa. The Australian database contains 1404 taxa. The European, New Zealand, and North American databases have most taxa on the highest taxonomical resolution while the Australian database has a similar number of taxa on species and genus-level.

% \begin{table}[ht]
%   \centering
%   \caption{Number of taxa per harmonized database and per taxonomic level. Numbers in parenthesis show relative frequencies in percentage.}
%   \label{tab:tax_coverage}
%   \begin{tabular}{lccccc}
%     \hline
%   Database & Nr. of taxa & Species & Genus & Family & Aquatic insects \\ 
%   \hline
%   EU & 4225 & 3951 (93.51) & 257 (6.08) & 17 (0.4) & 3654 (86.49) \\ 
%   NOA & 3542 & 2418 (68.27) & 1074 (30.32) & 50 (1.41) & 3144 (88.76) \\ 
%   AUS & 1402 & 564 (40.23) & 578 (41.23) & 260 (18.54) & 1015 (72.4) \\ 
%   NZ & 478 & 404 (84.52) & 47 (9.83) & 27 (5.65) & 443 (92.68) \\ 
%   \hline
%   \end{tabular}
%   \end{table}

\begin{table}[ht]
    \centering
    \caption{Number of taxa per harmonized database and per taxonomic level. Numbers in parenthesis show relative frequencies in percentage.}
    \label{tab:tax_coverage}
    \begin{tabular}{lccccc}
    \hline
    Database & Nr. of taxa & Species & Genus & Family & Nr. aquatic taxa \\ 
    \hline
    Europe & 4110 & 3848 (93.63) & 237 (5.77) & 25 (0.61) & 3579 (87.08) \\ 
      North America & 3753 & 2414 (64.32) & 1163 (30.99) & 176 (4.69) & 3305 (88.06) \\ 
      Australia & 1402 & 564 (40.23) & 578 (41.23) & 260 (18.54) & 1016 (72.47) \\ 
      New Zealand & 478 & 404 (84.52) & 47 (9.83) & 27 (5.65) & 443 (92.68) \\ 
    \hline
    \end{tabular}
\end{table}

\newpage

\section{Completeness of trait information}

The amount of entries with available information for the individual grouping features varied strongly for the European, North American and Australian databases (Table \ref{tab:trait_coverage}). By contrast, the New Zealand database contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).

\begin{table}[ht]
    \centering
    \caption{Displayed is the percentage of entries that have information for the individual grouping features per database.} 
    \label{tab:trait_coverage}
    \begin{tabular}{llllllll}
    \hline
    Database & Body form & Oviposition & Voltinism & Locomotion & Size & Respiration & Feeding mode \\ 
    \hline
    EU & 7 & 16 & 24 & 33 & 11 & 56 & 65 \\ 
    NOA & 26 & 12 & 47 & 51 & 75 & 44 & 61 \\ 
    AUS & 5 & 48 & 51 & 42 & 78 & 70 & 99 \\ 
    NZ & 100 & 94 & 100 & 99 & 100 & 100 & 99 \\ 
    \hline
    \end{tabular}
    \end{table}

\end{document}

### 2020-07-29 Paper/Trait_def_table/Trait_definitions_table.tex
29.07.2020: Paper - Res. almost ready for Co-Authors. Check calculation of missing information

\documentclass[../Draft_harmonization_paper.tex]{subfiles}
% \documentclass{article}
% \usepackage{rotating} 
% \usepackage{geometry}
% \usepackage{array}
% \usepackage{lscape}
% \usepackage{longtable}
% \usepackage{hhline}

\begin{document}

% ! Things to notice
% * Feeding Mode:
% ** Often described what is consumed, different assessments (e.g. for % predator) 
% ** Seldom reference to the mouthparts (Tachet)
% Shredder definitions actually not that different
% The Australian trait database was created out of seven sub-databases. Hence some grouping features occurred multiple times with different traits.

% TODO: Mention that NOA Vieira, AUS & NZ mostly don't give precise trait definitions
% TODO: - trait does not exist in database, mention that AUS, NZ and NOA (Vieira) do not provide detailed definitions.
% TODO: Voltinism freshwaterecology -> life cycles connected with thermal conditions -> taxa classified for different floristic regions
% TODO Use abbreviation for no precise definition given
% TODO Reproduction traits not mentioned since only the differentiation differed between databases, Similarly for Body Form
% TODO Start with mentioning that two core differences can exist: 1) definitions can be different semantically; 2) traits can be combined or more differentiated 
\section{Discrepancies of invertebrate trait definitions}

Definitions of grouping features and traits varied in their level of detail. The Tachet, Freshwaterecology, and North American (Twardochleb) trait databases provided more detailed descriptions of their trait information compared to the North American (Vieira) and New Zealand databases. An exception is the Australian trait database which is a collection of seven trait datasets (\cite{kefford_integrated_2020}). Thus, grouping features occur multiple times with varying differentiation into traits. Depending on the dataset trait information is described with more or less detail. %? use term membership state (Schmera)

The definition of grouping features varied across databases mainly with regard to their differentiation into traits but also in their scope. We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{tab:trait_definitions}). Both, differences in differentiation and scope can lead to discrepancies in trait definitions. For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways. Tachet defines predators as carvers, engulfers and swallowers. By contrast, in the North American (Twardochleb) database predators are defined as engulfers and carnivorous piercers. In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers. Furthermore, the scope in the Freshwaterecology database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition. Therefore, the Freshwaterecology database defines e.g. predator as "eating from prey", while the other databases use the mouthpart morphology in their definition. The Tachet database captures the food source in an additional grouping feature. Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (see for details \ref{tab:trait_databases_coding_differentiation} and S\ref{tab:trait_definitions}). Locomotion definitions differ also in scope between databases. Freshwaterecology and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation, the North American (Vieira) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb) database includes among the way of movement also the location of movement. Similarly, regarding reproduction trait databases differ in their scope. Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the Freshwaterecology and Tachet databases. North America (Vieira) provides information on the oviposition location but not on reproductive behavior. The Australian database report traits for reproductive behavior but also on oviposition site. The New Zealand database distinguishes three grouping features related to reproduction: reproductive technique, oviposition site (e.g. water surface, terrestrial), and egg/egg mass (e.g. free, cemented).

All databases report the coding of their traits (e.g. binary, fuzzy, continuous). The freshwaterecology and Australian use different codings throughout their databases. Tachet and the New Zealand database use exclusively fuzzy coding. Both North American trait databases contain categorical grouping features which can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}). Binary coding represents a simple approach in which a taxon either expresses a trait or not. Fuzzy coding characterizes the affinity of an organism to exert a certain trait. It is used to account for plasticity in traits, e.g. taking into account that traits can change over the development time of an organism and is usually converted into proportional values. Continuous coding is used for traits like body size.

% * Feeding mode:
% \begin{itemize}
%     \item freshwaterecology: describes primarily the food sources of a species, (e.g. algal tissues, CPOM, fallen leaves), except for filterers. Source: \cite{moog_comprehensive_nodate}
%     \item tachet: describes strategy/strategies adopted by the taxa for acquiring food, (e.g. taking into account mouthpart morphology). The food preference/food source has been described separately as a trait in Tachet et al. Source: \cite{usseglio-polatera_biomonitoring_2000}
%     \item North America (Twardochleb): Differentiates according to mode of food acquisition and food source, Source: \cite{cummins_trophic_1973}
%     \item North America (Vieira): Method of food collection based on mouthparts(termed feeding guild based)
%     \item Australia: Description of food source (e.g. Schäfer) also based on food acquisition (mouthpart morphology)
%     \item New Zealand: Description based on food description 
% \end{itemize}

% * Voltinism: 
% Not many differences
% \begin{itemize}
%     \item Freshwaterecology: taxa classified on floristic regions (e.g arctic, boreal). Six traits to describe voltinism. Distinguish Bivoltine, trivoltine and multivoltine in contrast to all other databases
%     \item ?Reproductive cycle vs. generations per year 
%     \item 
% \end{itemize}

% * Locomotion:
% differentiation varies between databases 
% \begin{itemize}
%     \item freshwaterecology: Way of movement of an organism
%     \item tachet: locomotion and substrate relation
%     \item North America (Twardochleb): Termed habit; way of movement and where (crawler -> floating leaves, fine sediments); Source: % Cummins & Merrit 2008
%     \item North America (Vieira): Habit -> how to deal with flow
%     \item Australia: Attachment
%     \item New Zealand: Way of movement of organism within its habitat. Trait termed attachment to substrate 
% \end{itemize}

% None of the seven grouping features compared here has the same differentiation of traits across all databases (Table \ref{tab:trait_databases})
% Table with diff trait states and coding
\begin{landscape}
    \begin{longtable}{|m{2.5cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}|}
    \caption{Number of traits per grouping feature and type of coding of the traits for the respective grouping feature per database.}
    \endfirsthead
    \hline
    \label{tab:trait_databases_coding_differentiation}
    Database & Feeding Mode & Voltinism & Locomotion & Respiration & Reproduction & Size & Body Form \\ 
    \hline
    \hline
    \multirow{2}{*}[-5mm]{ \specialcell{Freshwater- \\ ecology}} & 
    10 & 
    6 &
    6 & 
    7 & 
    9 & 
    - & 
    - 
    \\
    \cline{2-8} & 
    \specialcell{10 point \\ assignment \\ system} &
    \specialcell{single category \\ assignment \\ system} &
    \specialcell{10 point \\ assignment \\ system} &
    \multicolumn{2}{c |}{\specialcell{presence/absence assignment \\ system}} &
    - & 
    - \\
    \hline
    \hline
    \multirow{2}{*}{Tachet} & 
    7 & 
    3 &
    8 & 
    5 & 
    8 & 
    7 & 
    - 
    \\
    \cline{2-8} &
    \multicolumn{2}{c |}{fuzzy $[0-3]$} &
    fuzzy $[0-5]$ & 
    \multicolumn{3}{c |}{fuzzy $[0-3]$} & 
    -
    \\
    \hline
    \hline
    \multirow{2}{*}{\specialcell{North America \\ (Twardochleb)}} & 
    6 & 
    3 &
    10 & 
    3 & 
    10 & 
    3 & 
    - 
    \\
    \cline{2-8} &
    \multicolumn{6}{c |}{binary} &
    -
    \\
    \hline
    \hline
    \multirow{2}{*}{\specialcell{North America \\ (Vieira)}} & 
    8 & 
    3 &
    9 & 
    8 & 
    10 & 
    3 & 
    5 
    \\
    \cline{2-8} &
    \multicolumn{7}{c |}{binary}
    \\
    \hline
    \hline
    \multirow{2}{*}[-4mm]{Australia} & 
    16 \textsuperscript{\textit{a}} & 
    7 &
    9 & 
    10 &
    13 \textsuperscript{\textit{b}} & 
    9 & 
    4
    \\
    \cline{2-8} & 
    \multicolumn{2}{c |}{\specialcell{binary; proportional $[0 - 1]$; \\ fuzzy $[0 - 3]$}} & 
    binary; fuzzy $[0 - 3]$ & 
    \specialcell{binary; proportional \\ scale $[0 - 1]$; \\ fuzzy $[0 - 3]$} & 
    categorical & 
    \specialcell{binary; \\ numeric; \\ fuzzy $[0 - 3]$} & 
    fuzzy codes $[0-3]$
    \\
    \hline
    \hline
    \multirow{2}{*}{New Zealand} & 
    6 & 
    3 & 
    4 & 
    4 & 
    4 & 
    5 & 
    4
    \\
    \cline{2-8} & 
    \multicolumn{7}{c |}{fuzzy $[0-3]$}
    \\
    \hline
    \end{longtable}
    \begin{minipage}{\linewidth}\small
        \textit{a} Some of the traits were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
        \newline
        \textit{b} Many traits were rather comments than traits in the original database and were not considered.
    \end{minipage}
\end{landscape}

% ! Things to notice
% * Feeding Mode:
% ** Often described what is consumed, different assessments (e.g. for % predator) 
% ** Seldom reference to the mouthparts (Tachet)
% Shredder definitions actually not that different

% The Australian trait database was created out of seven sub-databases. Hence some grouping features occurred multiple times with different traits.

\end{document}

### 2020-07-31 Paper/Results/Results_trait_harmonization.tex
31.07.2020: Results to Co-Authors

@@
 
-To investigate how harmonizing grouping features and aggregating invertebrate traits might change the results in analysis of trait-environment relationships we replicated the data analysis of Szöcs et al.
-2014 (\cite{szocs_effects_2014}) using the harmonized grouping features \textit{Body size, Feeding mode, Locomotion, Reproduction/Oviposition, Respiration, and Voltinism} (21 grouping features have been used in total) and aggregated traits using the aforementioned aggregation methods.
+To investigate how harmonizing grouping features and aggregating invertebrate traits might change the results in the analysis of trait-environment relationships we replicated the data analysis of Szöcs et al.
+2014 (\cite{szocs_effects_2014}) using the harmonized grouping features \textit{Body size, Feeding mode, Locomotion, Reproduction/Oviposition, Respiration} and \textit{Voltinism} (21 grouping features have been used in total) and aggregated traits using the aforementioned aggregation methods.
 The harmonized grouping features used are those that responded strongly to salinity in the study of Szöcs et.
@@
 
-Here, we limit our analysis to the RDA of traits constrained by electric conductivity of the original publication (see appendix \ref{subsec:SI_szoecs_reanalysis} for a more in depth comparison to the original results).
+Here, we limit our analysis to the RDA of traits constrained by electric conductivity of the original publication (see appendix \ref{subsec:SI_szoecs_reanalysis} for a more in-depth comparison to the original results).
 Overall, using the harmonized grouping features lead only to slightly different results in comparison to the original analysis.
@@
 Also, for every aggregation method compared, using at family-level aggregated traits did only slightly change the RDA species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}).
-Hence, the interpretation of the trait composition follows is the same as when only using harmonized grouping features.
-An overview over the harmonization for the European trait databases can be found in the supporting information in section \ref{sec:SI_harmonization_EU}.
+Hence, the interpretation of the trait composition is the same as when only using harmonized grouping features.
+An overview of the harmonization for the European trait databases can be found in the supporting information in section \ref{sec:SI_harmonization_EU}.
 
@@
     \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
-    \caption{Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonized traits, and using harmonized traits and assigning traits aggregated to family level)}
+    \caption{Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonized grouping features, and using harmonized grouping features with assigned trait affinities from traits aggregated to family-level.}
     \label{fig:rda_species_scores}

### 2020-07-31 Paper/Results/SI.tex
31.07.2020: Results to Co-Authors

@@
     \includegraphics[width=16.5cm, height=10cm]{Comparison_trait_agg_methods.png}
-    \caption{Shown are mean absolute differences with standard deviations per regions.
-Compared aggregation methods are displayed on the y axis.
+    \caption{Means of absolute differences in trait affinities with standard deviations per region for all grouping features.
+Compared aggregation methods are displayed on the y-axis.
 N indicates the number of cases where differences occurred.}
@@
 % \cellcolor{blue!25}
-\begin{longtable}{llll}
+\begin{longtable}{lll|l}
 %\begin{table}[ht]
 %    \centering
-    \caption{Representation of traits per grouping feature for the used trait databases.
+    \caption{Representation of traits per grouping feature and their harmonization for the European trait databases.
 The color coding indicates traits that have been harmonized.
@@
     Feeding Mode & Grazer & Parasite &  \\ 
-    Feeding Mode & Predator & \color{cyan}Piercer (plants or animals) &  \\ 
+    Feeding Mode & Predator & \textit{Piercer (plants or animals)} \textsuperscript{\textit{a}} &  \\ 
     Feeding Mode & Parasite &  &  \\ 
@@
     \hline
-    \rowcolor{green!25}
+    \rowcolor{green!15}
     Locomotion & Swimming/scating & Surface swimmer & Swimmer \\ 
-    \cellcolor{green!25}Locomotion & \cellcolor{green!25}Swimming/diving & \cellcolor{green!25}Full water swimmer & Burrower \\ 
-    Locomotion & Burrowing/boring & Burrower & Crawler \\ 
-    Locomotion & Sprawling/walking & Crawler & \cellcolor{green!50}Sessil \\ 
-    \cellcolor{green!50}Locomotion & \cellcolor{green!50}(semi) sessil & \cellcolor{green!50}Temporarily attachted &  \\ 
-    \color{cyan}Locomotion & \color{cyan}Other & \cellcolor{green!50}Permanently attached &  \\ 
-    \color{cyan}Locomotion &  & \color{cyan}Interstitial &  \\ 
+    \cellcolor{green!15}Locomotion & \cellcolor{green!15}Swimming/diving & \cellcolor{green!15}Full water swimmer & \cellcolor{green!50}Burrower \\ 
+    \cellcolor{green!50}Locomotion & \cellcolor{green!50}Burrowing/boring & \cellcolor{green!50}Burrower & Crawler \\
+    Locomotion &  & \cellcolor{green!50}Interstitial & \cellcolor{green!95}Sessil \\
+    Locomotion & Sprawling/walking & Crawler &  \\ 
+    \cellcolor{green!95}Locomotion & \cellcolor{green!95}(semi) sessil & \cellcolor{green!95}Temporarily attachted &  \\ 
+    \color{cyan}Locomotion & \color{cyan}Other & \cellcolor{green!95}Permanently attached &  \\ 
     \color{cyan}Locomotion &  & \color{cyan}Flier &  \\
@@
 \end{longtable}
+\begin{minipage}{\linewidth}\small
+    \textit{a} Taxa exhibiting this trait have been assigned to predators or herbivores based on a classification by Philippe Usseglio-Polatera.
+\end{minipage}
 

### 2020-07-31 Paper/Results/Taxonomic_cov_and_info_compl.tex
31.07.2020: Results to Co-Authors

@@
 
-Regarding the taxonomical coverage, the New Zealand database has, as expected, the smallest taxon pool (Table \ref{tab:tax_coverage}).
-By contrast, the largest taxon pool is spanned by the European trait database with 4225 taxa followed by the North American trait database that contained trait information on 3542 taxa.
-The Australian database contains 1404 taxa.
+Regarding the taxonomical coverage, the New Zealand database has, as expected, the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
+By contrast, the largest taxon pool is spanned by the European trait database with 4110 taxa followed by the North American trait database that contained trait information on 3753 taxa.
+The Australian database contains 1402 taxa.
 The European, New Zealand, and North American databases have most taxa on the highest taxonomical resolution while the Australian database has a similar number of taxa on species and genus-level.
@@
 
-The amount of entries with available information for the individual grouping features varied strongly for the European, North American and Australian databases (Table \ref{tab:trait_coverage}).
+The amount of entries with available information for the individual grouping features varied strongly for the European, North American, and Australian databases (Table \ref{tab:trait_coverage}).
 By contrast, the New Zealand database contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
@@
     EU & 7 & 16 & 24 & 33 & 11 & 56 & 65 \\ 
-    NOA & 26 & 12 & 47 & 51 & 75 & 44 & 61 \\ 
+    NOA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
     AUS & 5 & 48 & 51 & 42 & 78 & 70 & 99 \\ 

### 2020-07-31 Paper/Trait_def_table/Trait_definitions_table.tex
31.07.2020: Results to Co-Authors

@@
 
-The definition of grouping features varied across databases mainly with regard to their differentiation into traits but also in their scope.
+The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope.
 We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{tab:trait_definitions}).
@@
 The Tachet database captures the food source in an additional grouping feature.
-Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (see for details \ref{tab:trait_databases_coding_differentiation} and S\ref{tab:trait_definitions}).
+Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (see for details Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{tab:trait_definitions}).
 Locomotion definitions differ also in scope between databases.
@@
 
-All databases report the coding of their traits (e.g.
+Various codings of traits are used throughout the databases (e.g.
 binary, fuzzy, continuous).
-The freshwaterecology and Australian use different codings throughout their databases.
+The freshwaterecology and Australian use different codings in their databases.
 Tachet and the New Zealand database use exclusively fuzzy coding.
-Both North American trait databases contain categorical grouping features which can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
+Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
 Binary coding represents a simple approach in which a taxon either expresses a trait or not.
@@
 It is used to account for plasticity in traits, e.g.
-taking into account that traits can change over the development time of an organism and is usually converted into proportional values.
+taking into account that traits can change over the development time of an organism.
+Usually, fuzzy coded affinities are converted into proportional values.
 Continuous coding is used for traits like body size.
@@
     categorical & 
-    \specialcell{binary; \\ numeric; \\ fuzzy $[0 - 3]$} & 
+    \specialcell{binary; \\ continuous; \\ fuzzy $[0 - 3]$} & 
     fuzzy codes $[0-3]$

### 2020-08-18 Paper/Draft_harmonization_paper.tex
31.07.2020: Results to Co-Authors
18.07.2020: Paper: Intro+Methods 90%

@@
 \usepackage[
-backend=biber,
-style=authoryear,
-sorting=nyt % sort by name year title
+backend = biber,
+style = numeric,
+citestyle = numeric-comp,
+sorting = none % sort by name year title
 ]{biblatex}
 \addbibresource{Ref_invertebrate_DB.bib}
+
+% TODO: Change citation style
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{ OVERVIEW RESULTS: Harmonized invertebrate grouping feature databases}
+\title{OVERVIEW RESULTS: Harmonized invertebrate grouping feature databases}
 \author{}%Stefan Kunz 
@@
 
-%\section{Introduction}
+\section*{Introduction}
 
-%! Understanding distribution of organisms and predicting the response to natural and anthropogenic stressors
+Explaining and predicting how aquatic communities are shaped by environmental factors is a main goal of freshwater ecology.
+Organismal traits, defined as measurable properties of an organism (\cite{mcgill_rebuilding_2006}), are increasingly incorporated into freshwater ecology to support this goal, e.g.
+by relating macroinvertebrate trait composition to environmental factors or as trait metrics in biomonitoring (\cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}).
+Traits evolve through adaptations (e.g., physiological, behavioral) of organisms to their environment and indicate direct or indirect linkages between biological response of an organism to its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
+% TODO cite also Statzner and Beche 2010?
+Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches may be suitable for large scale analysis since variability in trait responses is less than for taxonomic responses (\cite{bonada_taxonomic_2007}).
 
-%! Classification of species into groups with similar traits → expected consistent reaction to environmental gradients.
+In the last decades, freshwater ecologists developed comprehensive invertebrate trait databases for various biogeographic regions (\cite{usseglio-polatera_biomonitoring_2000, schmidt-kloiber_www.freshwaterecology.info_2015, vieira_database_nodate, Philips_and_Smith_NZ_DB_2018, kefford_integrated_2020, tomanova_trophic_2006}).
+% ? Cite also Twarodochleb/
+% Tomanova -> rather small database
+%(see Table \ref{tab:overview_trait_dbs} for a summary). %? Reasoning/Motivation
+The availability of invertebrate trait data from different biogeographic regions enables comparisons of trait variation and their relation to environmental factors across large scales.
+However, such analysis have been carried out mostly within one biogeographic region, using information from one or two trait databases.
+For example, \cite{bonada_taxonomic_2007} compared trait composition for mediterranean and temperate regions in Europe using traits from \cite{usseglio-polatera_biomonitoring_2000}, \cite{poff_developing_2010} characterized trait composition across sites in the Western US using traits from \cite{poff_functional_2006}, and \cite{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from \cite{poff_functional_2006} and \cite{schafer_trait_2011}.
+% ? Include Saito for South America 
+Rarely have analysis on invertebrate traits been carried out that synthesize information on traits and grouping features from more than two different biogeographic regions.
+A grouping feature is a general property (e.g.
+feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species" (\cite{schmera_proposed_2015}).
+To our knowledge, only \cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases in a study on the influence of decreasing glacier cover in nine biogeographic regions on functional diversity and community assembly of invertebrates.
+% TODO: short Literature search for similar studies like Brown
 
-%! Definition how the term “trait” is used in this study
+We suspect that the heterogeneity of descriptions of the invertebrate trait databases is likely to be one of the reasons why information of these databases is rarely combined.
+In order to harmonize trait data from different regions, first commonly accepted and unambiguous trait definitions are required (\cite{schneider_towards_2019}).
+In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonized using standardized terminology.
+However, a lack of standardized terminology of trait definitions and poor metadata quality in many trait databases is a common issue throughout the field of trait-based ecology (\cite{baird_toward_2011, schneider_towards_2019}).
+Secondly, consistent coding of traits facilitates the compatibility of trait data from different databases.
+Traits can be binary (i.e.
+trait exists or not), continuous, or fuzzy coded variables.
+Fuzzy codes represent the affinity of an organism to express a certain trait.
+They are used to account for plasticity in traits and are usually converted to percentages.
+Continuous values are typically used for grouping features hat can be measured, like body size.
+However, invertebrate trait databases are heterogeneous with regard to the coding they use for their traits (\cite{culp_incorporating_2011}, see also Table \ref{tab:trait_databases_coding_differentiation}).
+\cite{brown_functional_2018} harmonized grouping features based on trait databases from Europe, North America, and New Zealand since in these trait databases identical grouping features are classified differently into traits depending on the database.
+Also, because traits from North America were differently coded (binary) than those from Europe and New Zealand (fuzzy coded), the authors consulted experts to assign traits from North America or inferred them from the European database.
+% TODO: Tax res. not high enough in the used databases -> aggr. observations
+Thus, it becomes apparent that using invertebrate trait data from several regions requires extensive data processing prior to the actual data analysis.
 
-%! Trait-based approaches also used to understand community assembly, as a tool for biomonitoring, and to study effects of stressors to freshwater communities
+% TODO: Look into modelling papers 
+Differing taxonomic resolutions between the observed taxa in a study and the used trait database is another challenge when working with trait data.
+When observations are on a lower taxonomic level than data available in the trait databases (e.g.
+observations on species-level, trait data on genus-level) trait data of the higher taxonomic level are often assigned (e.g.
+\cite{szocs_effects_2014}).
+% TODO: another reference
+Conversely, if trait information is only available on lower taxonomic levels than the observed taxa, traits are aggregated to a higher taxonomic level (e.g.
+\cite{poff_functional_2006, szocs_effects_2014, piliere_a._f._h._importance_2016}).
+Thereby, trait aggregation is often done by using the median or the mode.
+Up to now, studies on how and to which extent different trait aggregation methods compare to assessments by trait experts are missing.
+%? cite Poff
+%? Taxonomic coverage
+% Piliere: Family Monitoring data -> Trait data only on Genus level
+% Brown: Monitoring data on species level -> Trait on genus or subfamily
 
-%! As a result, comprehensive (but distinct) invertebrate trait databases have been compiled in the last decades for different regions
-
-%! Trait-based approaches well suited for studies across regions
-
-%! Large-scale studies require harmonized invertebrate trait databases (e.g. Brown et al. 2018)
-
-%! -> How should such databases look like?:
-%  Harmonized traits
-%  Consistent scale of the used traits (e.g. fuzzy coding, binary coding, …)
-%  (Consistent taxonomical resolution → depends on the study)
+% Example Poff 2006; TODO check in modelling papers
 % (Similar taxonomical coverage for the investigated traits across the used databases → depends on the study)
 
-% !Goal:
-%  Present a harmonized invertebrate trait database (for the regions Europe, North America, New Zealand & Australia)
-%  How exactly are traits defined in each database? → We present an overview of definition discrepancies
-%  How does the usage of harmonized trait data yields to different results in trait analysis compare to non harmonized trait data?
-Re-analyzing the effect of anthropogenic salinization on biological traits in the River Werra (Germany, Szöcs et al.
-2014)
-%  Testing different ways of aggregating trait data → aggregation of traits often required (e.g. different taxonomical resolution between trait and abundance data)
+% TODO: Make sentences less difficult
+In this study we (1) present four harmonized invertebrate grouping feature databases for seven grouping features based on information from trait databases of the regions Europe, North America, New Zealand and Australia.
+%?
+Outline challenges of data preparation process
+Furthermore, we (2) compare to family-level aggregated trait values obtained by different trait aggregation methods to trait values assigned at family-level by experts.
+We (3) analyze how the usage of harmonized and/or aggregated trait data alters the results compared to non harmonized and non aggregated trait data by re-analyzing data on the effect of anthropogenic salinization on biological traits by \cite{szocs_effects_2014}.
+Finally, we (4) present an overview of discrepancies in trait definition between the used invertebrate trait databases and discuss challenges of trait data synthesis.
+% The next sections are organised as follows: we first describe the used trait databases and outline the data preparation process. Then different trait aggregation
 
-%\section{Methods}
-% !Present single invertebrate trait databases:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Methods}
+
+\subsection*{Selection of traits and harmonization of trait databases}
+
+% TODO:
+%  Nominal and continuous traits converted to binary traits 
+%  Normalize fuzzy codes to range [0 – 1]
+%  Transform trait values in percentages
+% ? Show data processing using a figure
+
+We established four harmonized grouping feature databases using information available in invertebrate trait databases from Europe, North America, Australia, and New Zealand.
+Trait information for Europe was obtained by the Freshwaterecology database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}) and complemented by Tachet (\cite{usseglio-polatera_biomonitoring_2000}) when information was missing (e.g.
+for the grouping feature size).
+Trait information for North America was obtained from Laura Twardochleb (\textit{in prep.}) and complemented by Vieira et al.
+2006 (\cite{vieira_database_nodate}).
+Philippe Usseglio-Polatera provided information on body form for European and North American taxa.
+For Australia and New Zealand, we used trait databases from Kefford et al.
+(\cite{kefford_integrated_2020}) and Philips and Smith respectively (\cite{Philips_and_Smith_NZ_DB_2018}).
+
+We selected traits of seven grouping features based on the availability of trait information across databases and so that they describe different parts of the biology of an organism: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
+%?
+frequently used traits
+We did not include ecological traits that describe habitat preferences (e.g.
+temperature preference) as these traits are not reported in the New Zealand trait database.
+Since the grouping features were differently classified across the databases we harmonized them into 26 traits (Table \ref{tab:traits_harmonization}).
+Harmonization was undertaken by amalgamating similar traits into one trait (e.g.
+crawlers and sprawlers into crawlers).
+Thereby, the highest trait affinity was assigned to the harmonized trait per taxa.
+% ?Problem of different definitions for the same traits between the used databases -> mention comparison
+
+We used fuzzy coded traits for establishing our harmonized databases unless data quality prohibited and then we used binary traits, i.e.
+categorical and continuous traits were converted into binary traits.
+Fuzzy codes are reported with different ranges in the trait databases (e.g.
+freshwaterecology 0 to 10, Tachet 0 to 3 or 0 to 5).
+We standardized them to a range between 0 and 1 and converted trait affinities to percentages.
+% ? fuzzy coded and binary traits are in the same range now
+
+Prior harmonization we amalgamated duplicate taxa on species, genus or family-level if present. We omitted taxa with a lower taxonomic resolution than family-level.
+
+% TODO: Present single invertebrate trait databases:
 %  Which taxonomical groups are covered
 %  Which traits are covered?
-%  Traits from the following grouping features have been selected: 
-%  - Voltinism, Reproduction, Body Form, Respiration, Size, Locomotion, Feeding Mode
-% Why have these traits been selected?: 
-%  Represent certain parts of the organisms biology:
-%  - Life-History, Morphology, Ecology
-%  No ecological traits: 
-%  - not reported in New Zealand trait database
 %  - (often correlated with environmental variables)
@@
 % Compare original databases in a table for better overview
+% TODO: Mention scripts for data processing and analysis (two github repos)
 
-%! Data processing:
-%  Nominal and continuous traits converted to binary traits 
-%  Normalize fuzzy codes to range [0 – 1]
-%  Transform trait values in percentages
-%  Selecting only taxa with complete trait profiles for the investigated traits
-% Show data processing using a figure
+\begin{table}[H]
+\centering
+\caption{Traits of the harmonized grouping features. The last column indicates traits that were amalgamated (no amalgamation needed if empty).}
+\label{tab:traits_harmonization}
+\begin{tabular}{lll}
+\\
+Grouping feature & Trait & Amalgamated traits\\
+\toprule[.1em]
+Voltinism    & \begin{tabular}[c]{@{}l@{}}Semivoltine\\ Univoltine\\ Bi/multivoltine\end{tabular}                                & \begin{tabular}[c]{@{}l@{}}\textless 1 generation per year\\ 1 generation per year\\ \textgreater 1 generation per year\end{tabular}                                                                                                                                            \\
+\midrule
+Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Round (humped)\\ Dorsoventrally flattened\\ Tubular\\ Fusiform\end{tabular}                                                                                                                                                                          \\
+\midrule
+Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm (Tachet: \textless 10 mm)\\ 9 - 16 mm (Tachet: 10 - 20 mm)\\ \textgreater 16 mm (Tachet: \textgreater 20 mm)\end{tabular}                                                                                                                \\
+\midrule
+Respiration  & \begin{tabular}[c]{@{}l@{}}Gills\\ Plastron/Spiracle\\ \\ \\ Tegument\end{tabular}                             & \begin{tabular}[c]{@{}l@{}}Temporary air store, tracheal gills\\ Spiracular gills, atmospheric breathers, \\ plant breathers, functional spiracles, \\ air (plants), aerial\\ Cutaneous\end{tabular}                                                                         \\
+\midrule
+Locomotion   & \begin{tabular}[c]{@{}l@{}}Burrower\\ Crawler\\ Sessil\\ Swimmer \end{tabular}                                     & \begin{tabular}[c]{@{}l@{}}Interstitial, boring\\ Sprawler, walking, climber, clinger\\ Attached\\ Skating, diving, planctonic\end{tabular}                                                                                                                 \\
+\midrule
+Feeding mode & \begin{tabular}[c]{@{}l@{}}Filterer\\ \\ Gatherer\\ \\ Herbivore\\ \\ Parasite\\ Predator\\ Shredder\end{tabular} & \begin{tabular}[c]{@{}l@{}}Active/passive filterer, absorber, \\ filter-feeder, collector-filterer\\ Deposit-feeder, collector-gatherer, \\ detrivore\\ Grazer, scraper, piercer herbivore, \\ algal piercer\\ \\ Piercer \\ Miner, xylophagus, shredder detrivore\end{tabular} \\
+\hline
+Oviposition  & \begin{tabular}[c]{@{}l@{}}Aquatic eggs\\ \\ Ovoviviparity\\ Terrestrial eggs\end{tabular}                            & \begin{tabular}[c]{@{}l@{}}Eggs attached to substrate/plants/stones,\\ free/fixed eggs/clutches\\ \\ Terrestrial clutches\end{tabular}     \\
+\bottomrule[.1em]
+\end{tabular}
+\end{table}
 
-%! Describe harmonization of traits:
-%  Which similar traits were harmonized and how? Describe in figure
-%  Problem of different definitions for the same traits between the used databases
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Trait aggregation}
 
-%! Describe trait aggregation:
-% Aggregation to family-level: 
-%  Stepwise aggregation (Median to genus-level, Mode to family-level. If the mode does not exist the median is taken.)
-%  Direct aggregation to family-level
-%  Weighted aggregation: We calculated weights as the ratio of the number of taxa on species or genera-level per family of the taxa with complete trait profiles to taxa on species or genus-level per family initially present in the databases.
-Taxa on species and genus-level were aggregated by multiplying their trait values with the obtained weights.
-Then the weighted trait values were summed up per family for each trait.
-% Present aggregation in a figure
+Traits of the harmonized grouping feature databases were aggregated to family-level using three approaches.
+I) we directly aggregated taxa to family-level giving equal weight to every species.
+We denote this aggregation as \textit{direct\_agg}.
+For the \textit{direct\_agg} we tested aggregating with the median and the mean.
+We added \textit{median} or \textit{mean} to \textit{direct\_agg} to indicate when we used which method.
+II) taxa were aggregated stepwise, i.e first to the genus-level and subsequently to the family-level.
+By using this approach, we give equal weights to each genus.
+Hereafter, we abbreviate this aggregation type as \textit{stepwise\_agg}.
+We tested the \textit{stepwise\_agg} using the mean and the median, using the same naming as for the \textit{direct\_agg}.
+III) taxa were aggregated using a weighted mean approach, denoted as \textit{weighted\_agg}.
+This method weights the genera according to the number of their species present in the databases.
+As mentioned above, trait affinities ranged between 0 and 1.
+Hence, the maximum differences possible is 1 or -1 (corresponds to 100 \%).
+For convenience, we report absolute trait differences.
 
-%! Describe data analysis of harmonized traits:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Data analysis with harmonized grouping features and aggregated traits}
+
+To investigate how harmonizing grouping features and aggregating invertebrate traits might change the results in the analysis of trait-environment relationships we replicated the data analysis of Szöcs et al.
+2014 (\cite{szocs_effects_2014}) using the harmonized grouping features \textit{Body size, Feeding mode, Locomotion, Reproduction/Oviposition, Respiration} and \textit{Voltinism} (21 grouping features have been used in total) and additionally aggregated traits using the aforementioned aggregation methods.
+The harmonized grouping features used are those that responded strongly to salinity in the study of Szöcs et.
+al.
+2014, except for life cycle duration.
+For testing the effect of aggregated traits we assigned to each taxon in \cite{szocs_effects_2014} the aggregated trait value from the established harmonized European grouping feature database for its corresponding family.
+We limit our analysis to the RDA of traits constrained by electric conductivity of the original publication (see appendix \ref{subsec:SI_szoecs_reanalysis} for a more in-depth comparison to the original results).
+An overview of the harmonization for the European trait databases can be found in the supporting information in section \ref{sec:SI_harmonization_EU}.
+
 %   We want replicate the trait analysis in an example study using our harmonized traits.
@@
 For this small scale study we re-analyze the change in trait composition along the conductivity gradient using the traits we could harmonize.
-%  Using the same data analysis approach as Szöcs et al. 2014 our goal is to investigate if downstream and upstream sites in the study will still be characterized by the same traits.
-%  Where trait information needs to be aggregated we will compare the different aggregation approaches with regard to how characterization of upstream and downstream sites will change.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
 \section*{Results harmonized grouping feature databases}
@@
 Philippe Usseglio-Polatera provided information on body form for European and North American taxa.
-For Australia and New Zealand we used trait databases from Kefford et al. (\cite{kefford_integrated_2020}) and Philips and Smith respectively (\cite{Philips_and_Smith_NZ_DB_2018}).
+For Australia and New Zealand, we used trait databases from Kefford et al.
+(\cite{kefford_integrated_2020}) and Philips and Smith respectively (\cite{Philips_and_Smith_NZ_DB_2018}).
 
@@
 
+\section*{Discussion}
+
+% Stat. techniques developed -> cannot use full potential
+% if data quality is poor, when synthesizing information is hard
+
 % Bibliography
@@
 \end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%% Examples of trait databases %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % ? Also mention Tomanova? -> not used here
+% \begin{table}[ht]
+%   \centering
+%     \caption{Examples of aquatic invertebrate trait databases established in the last decades.
+Differences in codings and trait definitions are outlined for these databases in Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{tab:trait_definitions}.}
+%     \label{tab:overview_trait_dbs}
+%     \begin{tabular}{lcccl}
+%     \hline
+%     Database & \specialcell{Nr. of grouping \\ features} & \specialcell{Main organism \\ groups} & \specialcell{Taxa and \\ resolution} & Citation \\ 
+%     \hline
+%     Freshwaterecology & 40 & \specialcell{Invertebrates, biased \\ towards aquatic insects} & Species-level & \cite{schmidt-kloiber_www.freshwaterecology.info_2015} \\ 
+%     Tachet & 21 & \specialcell{Invertebrates, biased \\ towards aquatic insects} & \specialcell{Taxa on species, \\ genus, and family-level} & \cite{usseglio-polatera_biomonitoring_2000} \\ 
+%     \specialcell{North America \\ (Vieira)} & 62 & \specialcell{Invertebrates, biased \\ towards aquatic insects} & \specialcell{Taxa on species, \\ genus, and family-level} & \cite{vieira_database_nodate} \\
+%     \specialcell{North America \\ (Twardochleb)} & 11 & Aquatic insects & \specialcell{Taxa on species, \\ genus, and family-level} & \cite{vieira_database_nodate} & \textit{In prep.} \\ 
+%     Australia & & \specialcell{Invertebrates, biased \\ towards aquatic insects} & \specialcell{Taxa on species, \\ genus, and family-level} & \cite{kefford_integrated_2020} \\
+%     New Zealand & & & & \cite{Philips_and_Smith_NZ_DB_2018}\\
+%     \hline
+%     \end{tabular}
+% \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-08-31 Paper/Draft_harmonization_paper.tex
31.08: Intro+Methods+Results update

--- 2020-07-29 Paper/Draft_harmonization_paper.tex
@@
 \usepackage{multirow}
+\usepackage{tikz}
 % \graphicspath{{/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures/}}
@@
 \usepackage[
-backend=biber,
-style=authoryear,
-sorting=nyt % sort by name year title
+backend = biber,
+style = numeric,
+citestyle = numeric-comp,
+sorting = none % sort by name year title
 ]{biblatex}
@@
 
-%\section{Introduction}
+\section*{Introduction}
 
-%! Understanding distribution of organisms and predicting the response to natural and anthropogenic stressors
+% TODO: Allgemeiner nur auf Ökologie bezogen
+% What is special re freshwaterecology trait research?
+% Difficult to measure some traits (e.g. feeding mode -> Moog)
+% Plant traits can be measured directly -> standardized database developed 
+% list numbers of traits and recorded taxa
+% Areas where freshwater ecology traits are used (move second sentence)
 
-%! Classification of species into groups with similar traits → expected consistent reaction to environmental gradients.
+Explaining and predicting how aquatic communities are shaped by environmental factors is one of the main goals of freshwater ecology.
+Organismal traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, are increasingly incorporated into freshwater ecology to support this goal, e.g.
+by relating macroinvertebrate trait composition to environmental factors or as trait metrics in biomonitoring \cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}.
+Traits evolve through adaptations (e.g., physiological, behavioral, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
+Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches may be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
+% Traits of freshwater invertebrates are difficult to assess, because, unlike plants, their characteristics often cannot be measured directly.
+For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community.
+% cite Moog!
+% Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g. to ...
 
-%! Definition how the term “trait” is used in this study
+In the last decades, freshwater ecologists developed comprehensive invertebrate trait databases for various biogeographic regions \cite{usseglio-polatera_biomonitoring_2000, schmidt-kloiber_www.freshwaterecology.info_2015, vieira_database_nodate, Philips_and_Smith_NZ_DB_2018, kefford_integrated_2020, tomanova_trophic_2006}.
+% ? Cite also Twarodochleb/
+The availability of invertebrate trait data from different biogeographic regions enables comparisons of trait variation and their relation to environmental factors across large scales.
+However, such analyses have been carried out mostly within biogeographic regions, using information from one or two trait databases.
+For example, Bonada et al.
+\cite{bonada_taxonomic_2007} compared trait composition for mediterranean and temperate regions in Europe using traits from Usseglio-Polatera et al.
+\cite{usseglio-polatera_biomonitoring_2000}, Poff et al.
+(2010) \cite{poff_developing_2010} characterized trait composition across sites in the Western US using traits from Poff et al.
+(2006) \cite{poff_functional_2006}, and Botwe et al.
+\cite{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from Poff et al.
+(2006) \cite{poff_functional_2006} and Schäfer et al.
+\cite{schafer_trait_2011}.
+% ? Include Saito for South America 
+Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different biogeographic regions are rare.
+A grouping feature is defined by Schmera et al.
+2015 as a general property (e.g.
+feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species" \cite{schmera_proposed_2015}.
+To our knowledge, only Brown et al.
+2018 \cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
+% TODO: Search for trait convergence Doledec!
 
-%! Trait-based approaches also used to understand community assembly, as a tool for biomonitoring, and to study effects of stressors to freshwater communities
+We suspect that the heterogeneity of information in freshwater invertebrate trait databases is likely a major reason for the lack of studies across biogeographic regions.
+To harmonize grouping features from different regions, first commonly accepted and unambiguous trait definitions are required \cite{schneider_towards_2019}.
+In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonized using standardized terminology.
+However, a lack of standardized terminology of trait definitions and poor metadata quality in many trait databases is a common issue throughout the field of trait-based ecology \cite{baird_toward_2011, schneider_towards_2019}.
+Secondly, consistent coding of traits facilitates the compatibility of trait data from different databases.
+Traits can be binary (i.e.
+trait exists or not), continuous, or fuzzy coded variables.
+Fuzzy codes represent the affinity of an organism to express a certain trait.
+They are used to account for plasticity in traits and are usually converted to percentages.
+Continuous values are typically used for grouping features that can be measured, like body size.
+However, invertebrate trait databases are heterogeneous with regard to the coding they use for their traits \cite{culp_incorporating_2011} (Table \ref{tab:trait_databases_coding_differentiation}).
+Brown et al.
+2018 \cite{brown_functional_2018} harmonized grouping features based on trait databases from Europe, North America, and New Zealand because in these trait databases identical grouping features are classified differently into traits.
+As the traits from North America were coded binary in contrast to the fuzzy coded traits from from Europe and New Zealand, the authors consulted experts to assign fuzzy coded traits to North American taxa or inferred them from the European trait database.
+Thus, it becomes apparent that using invertebrate trait data from several regions requires extensive data processing prior to the actual data analysis.
+A centralized database with standardized and unambiguous traits and a consistent coding of traits would minimize data processing effort.
+% TODO: Wieso ist es gut zentrale standardisierte definition und traits zu haben?
 
-%! As a result, comprehensive (but distinct) invertebrate trait databases have been compiled in the last decades for different regions
+Differing taxonomic resolutions between the observed taxa in a study and the used trait database is another challenge when working with trait data.
+When observations are on a lower taxonomic level than data available in the trait databases (e.g.
+observations on species-level, trait data on genus-level) trait data of the higher taxonomic level are often assigned, e.g.
+\cite{szocs_effects_2014, vos_taxonomic_2017}.
+Conversely, if trait information is only available on lower taxonomic levels than the observed taxa, traits are aggregated to a higher taxonomic level, e.g.
+\cite{poff_functional_2006, szocs_effects_2014, piliere_a._f._h._importance_2016, aspin_extreme_2019}.
+Thereby, trait aggregation is often done using the mean \cite{magliozzi_functional_2019}, median \cite{szocs_effects_2014} or the mode \cite{piliere_a._f._h._importance_2016}.
+Up to now, studies on how and to which extent different trait aggregation methods influence trait-based analysis are missing.
+% TODO: Satz wieso es gut wäre wenn man das wissen würde -> lead to last paragraph
 
-%! Trait-based approaches well suited for studies across regions
+We analyzed the influence of grouping feature harmonization and trait aggregation on trait-environment relationships. 
+Therefore, we (1) harmonized four invertebrate grouping feature datasets for seven grouping features based on information from trait databases of the regions Europe, North America, New Zealand, and Australia.
+Furthermore, we (2) compare trait affinities obtained through different trait aggregation methods to trait affinities assigned at family-level by experts.
+We (3) re-analyze data on the effect of anthropogenic salinization on biological traits by Szöcs et al.
+\cite{szocs_effects_2014} using harmonized grouping features and harmonized grouping features with aggregated traits.
+By comparison with the original analysis, we investigate how harmonizing and aggregating trait data can alter the outcome of trait-environment relationships.
+Finally, we (4) present an overview of discrepancies in trait definition between the used invertebrate trait datasets and discuss challenges of trait data synthesis.
 
-%! Large-scale studies require harmonized invertebrate trait databases (e.g. Brown et al. 2018)
+\newpage
 
-%! -> How should such databases look like?:
-%  Harmonized traits
-%  Consistent scale of the used traits (e.g. fuzzy coding, binary coding, …)
-%  (Consistent taxonomical resolution → depends on the study)
-%  (Similar taxonomical coverage for the investigated traits across the used databases → depends on the study)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% !Goal:
-%  Present a harmonized invertebrate trait database (for the regions Europe, North America, New Zealand & Australia)
-%  How exactly are traits defined in each database? → We present an overview of definition discrepancies
-%  How does the usage of harmonized trait data yields to different results in trait analysis compare to non harmonized trait data?
-Re-analyzing the effect of anthropogenic salinization on biological traits in the River Werra (Germany, Szöcs et al.
-2014)
-%  Testing different ways of aggregating trait data → aggregation of traits often required (e.g. different taxonomical resolution between trait and abundance data)
+\section*{Methods}
 
-%\section{Methods}
-% !Present single invertebrate trait databases:
-%  Which taxonomical groups are covered
-%  Which traits are covered?
-%  Traits from the following grouping features have been selected: 
-%  - Voltinism, Reproduction, Body Form, Respiration, Size, Locomotion, Feeding Mode
-% Why have these traits been selected?: 
-%  Represent certain parts of the organisms biology:
-%  - Life-History, Morphology, Ecology
-%  No ecological traits: 
-%  - not reported in New Zealand trait database
-%  - (often correlated with environmental variables)
-%  - (Relatively good taxonomical overlap for these traits between the used databases)
-% Compare original databases in a table for better overview
+\subsection*{Selection of traits and harmonization of trait databases}
 
-%! Data processing:
-%  Nominal and continuous traits converted to binary traits 
-%  Normalize fuzzy codes to range [0 – 1]
-%  Transform trait values in percentages
-%  Selecting only taxa with complete trait profiles for the investigated traits
-% Show data processing using a figure
+We extracted information from 4 trait databases from Europe, North America, Australia, and New Zealand and harmonized 7 grouping features.
+Trait information for Europe was obtained from the Freshwaterecology database \cite{schmidt-kloiber_www.freshwaterecology.info_2015} and complemented by Tachet \cite{usseglio-polatera_biomonitoring_2000} to fill missing information (e.g.
+for size).
+% TODO: mention that tachet and freshwaterecology are not seperate (but we did it separately)
+Trait information for North America was obtained from Laura Twardochleb (\textit{in prep.}) and complemented by Vieira et al.
+2006 \cite{vieira_database_nodate}.
+Data on body for European and North American taxa was provided based on expert knowledge \cite{polatera_personal_information_2020}.
+For Australia and New Zealand, we used trait databases from Kefford et al.
+\cite{kefford_integrated_2020} and Philips and Smith respectively \cite{Philips_and_Smith_NZ_DB_2018}.
 
-%! Describe harmonization of traits:
-%  Which similar traits were harmonized and how? Describe in figure
-%  Problem of different definitions for the same traits between the used databases
+We selected traits of seven grouping features that were available in all databases, are commonly used, and describe different parts of the biology of an organism: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
+We omitted ecological traits that describe habitat preferences (e.g.
+temperature preference) because these traits are missing in the New Zealand trait database.
+The grouping features were differently classified across the databases, we therefore harmonized them into 26 traits (Table \ref{tab:traits_harmonization}).
+Harmonization was undertaken by amalgamating similar traits into one trait (e.g.
+crawlers and sprawlers into crawlers).
+Thereby, the highest trait affinity among the amalgamated traits was taken.
 
-%! Describe trait aggregation:
-% Aggregation to family-level: 
-%  Stepwise aggregation (Median to genus-level, Mode to family-level. If the mode does not exist the median is taken.)
-%  Direct aggregation to family-level
-%  Weighted aggregation: We calculated weights as the ratio of the number of taxa on species or genera-level per family of the taxa with complete trait profiles to taxa on species or genus-level per family initially present in the databases.
-Taxa on species and genus-level were aggregated by multiplying their trait values with the obtained weights.
-Then the weighted trait values were summed up per family for each trait.
-% Present aggregation in a figure
+We used fuzzy coded traits for establishing our harmonized datasets unless data quality prohibited and then we used binary traits, i.e.
+categorical and continuous traits were converted into binary traits.
+Implicitly, we assumed for binary traits that a value of 1 corresponds to the highest affinity for a particular trait and 0 to no affinity for a particular trait.
+Fuzzy codes are reported with different ranges in the trait databases (e.g.
+freshwaterecology 0 to 10, Tachet 0 to 3 or 0 to 5).
+We standardized them to a range between 0 and 1 and converted trait affinities to percentages.
+Thus, fuzzy coded and binary traits were in the same range.
 
-%! Describe data analysis of harmonized traits:
-%   We want replicate the trait analysis in an example study using our harmonized traits.
-Therefore, we use the study from Szöcs et al.
-2014 on the effect of anthropogenic salinization on biological traits.
-For this small scale study we re-analyze the change in trait composition along the conductivity gradient using the traits we could harmonize.
-%  Using the same data analysis approach as Szöcs et al. 2014 our goal is to investigate if downstream and upstream sites in the study will still be characterized by the same traits.
-%  Where trait information needs to be aggregated we will compare the different aggregation approaches with regard to how characterization of upstream and downstream sites will change.
+Prior harmonization we amalgamated duplicate taxa on species, genus or family-level if present. We omitted taxa with a lower taxonomic resolution than family-level.
 
-%\section{Results \& Discussion}
+\begin{table}[H]
+\centering
+\caption{Traits of the harmonized grouping features. The last column indicates traits that were amalgamated for harmonization (no amalgamation needed if empty).}
+\label{tab:traits_harmonization}
+\begin{tabular}{lll}
+\\
+Grouping feature & Trait & Amalgamated traits\\
+\toprule[.1em]
+Voltinism    & \begin{tabular}[c]{@{}l@{}}Semivoltine\\ Univoltine\\ Bi/multivoltine\end{tabular}                                & \begin{tabular}[c]{@{}l@{}}\textless 1 generation per year\\ 1 generation per year\\ \textgreater 1 generation per year\end{tabular}                                                                                                                                            \\
+\midrule
+Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, round (humped)\\ Flattend, dorsoventrally flattened\\ Spherical, tubular\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
+\midrule
+Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm (Tachet: \textless 10 mm)\\ 9 - 16 mm (Tachet: 10 - 20 mm)\\ \textgreater 16 mm (Tachet: \textgreater 20 mm)\end{tabular}                                                                                                                \\
+\midrule
+Respiration  & \begin{tabular}[c]{@{}l@{}}Gills\\ Plastron/Spiracle\\ \\ \\ Tegument\end{tabular}                             & \begin{tabular}[c]{@{}l@{}}Temporary air store, tracheal gills, gills\\ Spiracular gills, atmospheric breathers, \\ plant breathers, functional spiracles, \\ air (plants), aerial, plastron/spiracle\\ Cutaneous, tegument \end{tabular}                                                                         \\
+\midrule
+Locomotion   & \begin{tabular}[c]{@{}l@{}}Burrower\\ Crawler\\ Sessil\\ Swimmer \end{tabular}                                     & \begin{tabular}[c]{@{}l@{}}Interstitial, boring, burrowing\\ Sprawler, walking, climber, clinger, crawler\\ Attached, sessil\\ Skating, diving, planctonic, swimming\end{tabular}                                                                                                                 \\
+\midrule
+Feeding mode & \begin{tabular}[c]{@{}l@{}}Filterer\\ \\ Gatherer\\ \\ Herbivore\\ \\ Parasite\\ Predator\\ Shredder \\ \\ \end{tabular} & \begin{tabular}[c]{@{}l@{}}Active/passive filterer, absorber, \\ filter-feeder, collector-filterer, filterer\\ Deposit-feeder, collector-gatherer, \\ detrivore, gatherer\\ Grazer, scraper, piercer herbivore, \\ herbivore, algal piercer, piercer (plants)\textsuperscript{\textit{a}}\\ \\ Piercer (animals)\textsuperscript{\textit{a}}, predator \\ Miner, xylophagus, shredder, \\ shredder detrivore\end{tabular} \\
+\hline
+Oviposition  & \begin{tabular}[c]{@{}l@{}}Aquatic eggs\\ \\ Ovoviviparity\\ Terrestrial eggs\end{tabular}                            & \begin{tabular}[c]{@{}l@{}}Eggs attached to substrate/plants/stones,\\ free/fixed eggs/clutches\\ \\ Terrestrial clutches, terrestrial \end{tabular}     \\
+\bottomrule[.1em]
+\end{tabular}
+\end{table}
+\begin{minipage}{\linewidth}\small
+    \textit{a} The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases \cite{usseglio-polatera_biomonitoring_2000}.
+Taxa exhibiting this trait have been assigned to predators or herbivores based on expert knowledge \cite{polatera_personal_information_piercer_2020}.
+\end{minipage}
 
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Trait aggregation}
+
+Traits of the harmonized grouping feature datasets were aggregated to family-level using three approaches.
+I) direct aggregation of taxa to family-level giving equal weight to every species using the mean or median, denote \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively.
+II) stepwise aggregation, i.e first to the genus-level and subsequently to the family-level using the mean or median.
+This approach gives equal weights to each genus.
+Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{mean}} or \textit{stepwise\_agg\textsubscript{median}}, respectively.
+III) aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
+This method weights the genera according to the number of their species in the databases.
+
+\begin{figure}
+  \centering
+  \subfile{Flowchart/Flowchart_methods.tex}
+  \caption{Data processing steps of the selected traits.
+Intermediate (gray) and main (orange) steps of data preparation are depicted.
+The dashed bottom box illustrates the different trait aggregation methods using a small made-up example (data in the upper left corner).
+Displayed are the aggregation methods (blue) and intermediate steps of the aggregation methods (purple).
+For the stepwise and weighted aggregation only results for one trait are displayed.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Comparison of aggregated traits with traits assigned by experts}
+
+Aggregated trait affinities of the five trait aggregation methods (\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg}) were compared to trait affinities assigned at family-level by experts, which were available for the Australian and North American database for a subset of grouping features and taxa.
+For the Australian database, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman et al.
+\cite{chessman_dissolved-oxygen_2018}.
+In Chessman et al.
+\cite{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the harmonized Australian database except that the trait parasite is missing.
+We conducted the comparison for the 220 families available in Chessman et al.
+\cite{chessman_dissolved-oxygen_2018}.
+Considering each factor combination of family and trait (in total 8) this amounts to 1760 cases.
+
+For the North American database, we compared aggregated trait affinities with assigned trait affinities on family-level for the grouping features feeding mode, respiration, size, voltinism, and locomotion.
+The assigned trait affinities at family-level are part of the North American database (\textit{Laura Twardochleb in prep.}) and originate from expert knowledge \cite{twardochleb_personal_information_mpyne_2020}.
+Trait information was available for 94 families of which all were present in the aggregated North American database (total number of cases 1598).
+The traits were on the categorical scale and were converted to binary traits prior to the comparison with aggregated trait affinities.
+
+As mentioned above, trait affinities ranged from 0 to 1.
+Hence, the maximum difference possible in trait affinities is 1 or -1 (corresponds to 100 \%).
+For convenience and to improve interpretation, we report absolute trait differences.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Analysis of the effect of harmonization and trait aggregation on trait-environment relationships}
+
+We repeated the analysis in Szöcs et al.
+\cite{szocs_effects_2014} who studied the effect of anthropogenic salinization on invertebrates in the River Werra in Germany.
+As a case study, we used for the re-analysis the established harmonized grouping features for Europe and additionally aggregated traits using the aforementioned aggregation methods.
+
+The river has been subject to effluents from the potash industry since the mid of the 20th century and allows to study responses of invertebrates and their trait compositions to salinization.
+Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition.
+Further details can be found in \cite{szocs_effects_2014}.
+We compared the species scores obtained from redundancy analysis (RDA) for traits constrained by electric conductivity from the original study to species scores when including harmonized grouping features.
+We used the same grouping features that Szöcs et al.
+\cite{szocs_effects_2014} used, but 6 of them have been harmonized from the European harmonized grouping feature dataset for our analysis.
+The harmonized grouping features used were \textit{Size, Feeding mode, Locomotion, Reproduction/Oviposition, Respiration}, and \textit{Voltinism}.
+Traits of those grouping features responded strongly to salinity in the study of \cite{szocs_effects_2014}.
+Additionally, for testing the effect of aggregated traits we assigned to each taxon in \cite{szocs_effects_2014} the aggregated trait value for its corresponding family and repeated the RDA.
+
+% TODO FIX reference to SI
+% ?(see SI for a more in-depth comparison to the original results using harmonized grouping features)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Data analysis}
+
+The data processing and aforementioned analysis were carried out using R (Version 3.6.1).
+Raw data and the R code for data processing and grouping feature harmonization is located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
+Scripts and data to reproduce the trait aggregation and analysis with aggregated traits are located in the Github repository \url{https://github.com/KunzstLD/Trait-aggregation}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
 \section*{Results harmonized grouping feature databases}
-
-We used information on invertebrate traits for the regions Europe, North America, Australia, and New Zealand to establish harmonized grouping feature databases.
-Trait information for Europe was obtained by the Freshwaterecology database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}) and complemented by Tachet (\cite{usseglio-polatera_biomonitoring_2000}) when information was missing (e.g.
-for the grouping feature size).
-Trait information for North America was obtained from Laura Twardochleb and complemented by Vieira et al.
-2006 (\cite{vieira_database_nodate}).
-Philippe Usseglio-Polatera provided information on body form for European and North American taxa.
-For Australia and New Zealand we used trait databases from Kefford et al. (\cite{kefford_integrated_2020}) and Philips and Smith respectively (\cite{Philips_and_Smith_NZ_DB_2018}).
-
-We selected seven grouping features that we harmonized into 26 traits.
-The grouping features were chosen based on the availability of trait information across databases and so that they describe different parts of the biology of an organism: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
-We used fuzzy coded traits for establishing our harmonized databases unless data quality prohibited and then we used binary traits, i.e categorical and continuous traits were converted into binary traits.
-Data processing prior harmonization also involved amalgamation of duplicate taxa on species, genus or family-level and conversion of trait affinities to percentages per trait.
-We omitted taxa with a lower taxonomic resolution than family-level.
-The following results relate to the harmonized grouping feature databases.
 
@@
 
-%! Presenting results of trait analysis using harmonized traits:
-%  Did using harmonized traits yield different results regarding trait composition of down and upstream sites in Szöcs et al. 2014?
-%  Had various trait aggregation methods an impact?
 \newpage
 
+%! Presenting results of trait analysis using harmonized traits:
 \subfile{Results/Results_trait_harmonization}
+% TODO: Fix reference to SI!
 
@@
 
-% Bibliography
+\section*{Discussion}
+
+% Stat. techniques developed -> cannot use full potential
+% if data quality is poor, when synthesizing information is hard
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \printbibliography

### 2020-08-31 Paper/Flowchart/Flowchart_methods.tex
31.08: Intro+Methods+Results update

\documentclass[../Draft_harmonization_paper.tex]{subfiles}
\usetikzlibrary{trees,
                arrows,
                shapes.geometric,
                positioning,
                calc,
                backgrounds,
                fit,
                matrix,
                shapes.geometric}

\begin{document}

\tikzset{
	font = {\sffamily},
	intstepsnode/.style = {rectangle, draw = black, fill = gray!50, minimum width = 4cm, minimum height = 1cm, text centered, rounded corners, very thick},
  aggrtypesnode/.style = {rectangle, draw = black, fill = blue!25, minimum width = 4cm, minimum height = 1cm, text centered, rounded corners, very thick},
  aggrstepsnode/.style = {rectangle, draw = black, fill = purple!40, minimum width = 4cm, minimum height = 1cm, text centered, rounded corners, very thick},
  mainnode/.style = {rectangle, draw = black, fill = orange!50, minimum width = 4cm, minimum height = 1.5cm, text centered, rounded corners, very thick},
  frame/.style = {draw, rectangle, rounded corners, dashed, black, line width = 1pt, inner sep = 2.5mm},
  roundnode/.style={circle, draw=green!60, fill=green!5, very thick, minimum size=7mm},
  arrow1/.style = {->, > = stealth, draw = black, color = gray!80, line width = 2.5pt}
}

\begin{tikzpicture}
      %% Nodes
      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Allocating duplicate taxa \\ NOA \& AUS DB};
      \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{AUS traits standardized to [0-1] \\ because multiple codings used \\ throughout this database};
      \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Omitted taxa lower \\ family-level};

      \node (frameProcessing) [frame, fit = (duplTaxa) (normalAUS) (omission) ] {};
      \node (frameText) [above, black, inner sep = 2mm] at (frameProcessing.north){Data preprocessing};

      \node(harmonization)[mainnode, align = center, xshift = -5cm, yshift = -2.5cm]{Harmonization};

      \node(conversionPerc)[intstepsnode, align = center, xshift = 0cm, yshift = -2.5cm]{Traits converted to percentages \\ and normalized to [0-1]};

      \node(traitAgg)[mainnode, align = center, xshift = 5cm, yshift = -2.5cm]{Trait aggregation};

      \node(frameHarmAggr) [frame, fit = (harmonization) (traitAgg)] {};

      \node(tab_aggregation)[xshift = -3cm, yshift = -6.6cm]{
        \begin{tabular}{ccc|ccc}
        Family & Genus & Species & \specialcell{Trait \\ A\_h\textsubscript{1}} & \specialcell{Trait \\ A\_h\textsubscript{2}} & \specialcell{Trait \\ A\_h\textsubscript{3}} \\
        \hline
         F\textsubscript{1} & G\textsubscript{1} & S\textsubscript{1} & 0.25 & 0.75 & 0\\
         F\textsubscript{1} & G\textsubscript{1} & S\textsubscript{2} & 0.5 & 0.5 & 0\\
         F\textsubscript{1} & G\textsubscript{1} & S\textsubscript{3} & 0.5 & 0.5 & 0 \\
         F\textsubscript{1} & G\textsubscript{2} & S\textsubscript{4} & 0 & 1.0 & 0 \\
         F\textsubscript{1} & G\textsubscript{2} & \textit{NA} & 0.25 & 0.75 & 0 \\
         F\textsubscript{1} & \textit{NA} & \textit{NA} & 0.25 & 0.75 & 0 \\
      \end{tabular}};

      \node(directAgg)[aggrtypesnode, align = center, xshift = 4cm, yshift = -5cm]{Direct aggregation};

      \node(tab_direct_agg)[xshift = 4cm, yshift = -7.5cm]{
        \begin{tabular}{c|ccc}
        Family & Trait & Method & Value \\
        \hline
        F\textsubscript{1} & A\_h\textsubscript{1} & mean & 0.29 \\
        F\textsubscript{1} & A\_h\textsubscript{2} & mean & 0.71 \\
        F\textsubscript{1} & A\_h\textsubscript{3} & mean & 0 \\
        \hline
        F\textsubscript{1} & A\_h\textsubscript{1} & median & 0.25 \\
        F\textsubscript{1} & A\_h\textsubscript{2} & median & 0.75 \\
        F\textsubscript{1} & A\_h\textsubscript{3} & median & 0 \\
      \end{tabular}};

      \node(stepwiseAgg)[aggrtypesnode, align = center, xshift = -3.5cm, yshift = -10.3cm]{Stepwise aggregation};

      \node(tab_stepwise_agg)[xshift = -3.5cm, yshift = -12.5cm]{
        \begin{tabular}{cc|ccc}
        Family &Genus & Trait & Method & Value \\
        \hline
        F\textsubscript{1}& G\textsubscript{1} & A\_h\textsubscript{1} & mean & 0.4167\\
        F\textsubscript{1}& G\textsubscript{2} & A\_h\textsubscript{1} & mean & 0.125\\
        F\textsubscript{1}& NA & A\_h\textsubscript{1} & - & 0.25\\
      \end{tabular}};

      \node(stepwiseAgg2)[aggrstepsnode, align = center, xshift = -3.5cm, yshift = -14.7cm]{ $A\_h_1 = mean(0.4167, 0.125, 0.25)$ \\ $ = 0.26$};

      \node(weightedAgg)[aggrtypesnode, xshift = 4cm, yshift = -10.3cm]{Weighted aggregation};

      \node(weights)[aggrstepsnode, align = center, xshift = 4cm, yshift = -12.7cm]{Weights based on \\ species per genera: \\
      $3$ for $G_1$, $1$ for $G_2$, \\
      weight for $F_1$ set to $1$};

      \node(weights2)[aggrstepsnode, align = center, xshift = 4cm, yshift = -15.1cm]{$A\_h_1 = \frac{0.25*3+0.5*3+...+ 0.25*1}{3+3...+1}$ \\ \\ $ = 0.35$};

      \node(frameExample) [frame, fit = (tab_aggregation) (directAgg)(tab_direct_agg) (weights2)] {};

      %%lines
      \draw[->] (duplTaxa.east) -- (normalAUS.west);
      \draw[->] (normalAUS.east) -- (omission.west);
      \draw[->] (harmonization.east) -- (conversionPerc.west);
      \draw[->] (conversionPerc.east) -- (traitAgg.west);
      \draw[arrow1] (traitAgg.south) -- (frameExample.north);
      \draw[->] (directAgg.south) -- (tab_direct_agg.north);
      \draw[->] (stepwiseAgg.south) -- (tab_stepwise_agg.north);
      \draw[->] (tab_stepwise_agg.south) -- (stepwiseAgg2.north);
      \draw[->] (weightedAgg.south) -- (weights.north);
      \draw[->] (weights.south) -- (weights2.north);
\end{tikzpicture}

\end{document}

### 2020-08-31 Paper/Results/Results_trait_harmonization.tex
31.08: Intro+Methods+Results update

@@
 
-\section{Re-analysis of Szöcs et al. 2014 using harmonized and aggregated grouping features}
+\subsection*{Re-analysis of Szöcs et al. 2014 using harmonized and aggregated grouping features}
 
-To investigate how harmonizing grouping features and aggregating invertebrate traits might change the results in the analysis of trait-environment relationships we replicated the data analysis of Szöcs et al.
-2014 (\cite{szocs_effects_2014}) using the harmonized grouping features \textit{Body size, Feeding mode, Locomotion, Reproduction/Oviposition, Respiration} and \textit{Voltinism} (21 grouping features have been used in total) and aggregated traits using the aforementioned aggregation methods.
-The harmonized grouping features used are those that responded strongly to salinity in the study of Szöcs et.
-al.
-2014, except for life cycle duration.
-%!Aggr.
-methods
-For testing the effect of aggregated traits we assigned to each taxon in Szöcs et al.
-2014 the aggregated trait value from the established harmonized European grouping feature database for its corresponding family.
-
-Here, we limit our analysis to the RDA of traits constrained by electric conductivity of the original publication (see appendix \ref{subsec:SI_szoecs_reanalysis} for a more in-depth comparison to the original results).
-Overall, using the harmonized grouping features lead only to slightly different results in comparison to the original analysis.
-Sites with high salinity were characterized by multivoltine, ovivoparous, gill-respirating, and shredder species.
+Overall, using the harmonized grouping features lead only to slightly different results in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and SI \ref{subsec:SI_szoecs_reanalysis}).
+According to the RDA of trait composition sites with high salinity were characterized by multivoltine, ovivoparous, gill-respirating, and shredder species.
 Only species with the trait life cycle duration $> 1$ year fail to characterize sites with high salinization.
@@
 Like in the original analysis, transition and upstream sites from the point source are characterized by univoltine species and species that lay their eggs in an aquatic environment.
-The usage of aggregated traits yielded similar species scores for every aggregation method.
-Also, for every aggregation method compared, using at family-level aggregated traits did only slightly change the RDA species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}).
+We constructed also the linear models of the original analyses, using the traits on the extremes of the conductivity axis and found similar results as the original analysis (SI \ref{subsec:SI_szoecs_reanalysis}).
+
+For every aggregation method compared, using at family-level aggregated traits did only slightly change the species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}).
 Hence, the interpretation of the trait composition is the same as when only using harmonized grouping features.
-An overview of the harmonization for the European trait databases can be found in the supporting information in section \ref{sec:SI_harmonization_EU}.
 

### 2020-08-31 Paper/Results/SI.tex
31.08: Intro+Methods+Results update

--- 2020-07-29 Paper/Results/SI.tex
@@
 \section*{Supporting Information}
+\label{sec:SI}
 
@@
 
-\subsection*{Re-analysis of Szöcs et al. 2014 using harmonized and aggregated grouping features.}
+\subsection*{Re-analysis of Szöcs et al. 2014 using harmonized grouping features.}
 \label{subsec:SI_szoecs_reanalysis}
@@
 
-\newpage
+% \section*{Harmonization of the European trait databases}
+% \label{sec:SI_harmonization_EU}
 
-\section*{Harmonization of the European trait databases}
-\label{sec:SI_harmonization_EU}
-
-% \cellcolor{blue!25}
-\begin{longtable}{llll}
-%\begin{table}[ht]
-%    \centering
-    \caption{Representation of traits per grouping feature for the used trait databases.
+% % \cellcolor{blue!25}
+% \begin{longtable}{lll|l}
+% %\begin{table}[ht]
+% %    \centering
+%     \caption{Representation of traits per grouping feature and their harmonization for the European trait databases.
 The color coding indicates traits that have been harmonized.
-Cyan colored traits have not been used because they either represented ambiguous traits or traits that were not compatible with the traits of the other databases.
-Harmonization was done by assigning the maximum affinity of the allocated traits for the respective taxa to the harmonized trait.}
-    \endfirsthead
-    \endhead
-    %\begin{tabular}{llll}
-    \hline
-    Grouping feature & Freshwater ecology & Tachet & Harmonized traits \\ 
-    \hline
-    \hline
-    Voltinism & Semivoltine & Semivoltine & Semivoltine \\ 
-    Voltinism & Univoltine & Univoltine & Univoltine \\ 
-    \rowcolor{gray!25}
-    Voltinism & Bivoltine & Polyvoltine & Bi/Multivoltine \\ 
-    \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Trivoltine &  &  \\ 
-    \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Multivoltine &  &  \\ 
-    \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Flexible &  &  \\ 
-    \rowcolor{blue!25}
-    \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Shredder & Shredder & Shredder \\ 
-    \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Miner & Deposit-feeder & Gatherer \\ 
-    \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Xylophagus & \cellcolor{blue!50}Absorber & \cellcolor{blue!50}Filterer \\ 
-    Feeding Mode & Gatherer & \cellcolor{blue!50}Filter-feeder & Herbivore \\ 
-    \cellcolor{blue!50}Feeding Mode & \cellcolor{blue!50}Active filterer & Scraper & Predator \\ 
-    \cellcolor{blue!50}Feeding Mode & \cellcolor{blue!50}Passive filterer & Predator & Parasite \\ 
-    Feeding Mode & Grazer & Parasite &  \\ 
-    Feeding Mode & Predator & \color{cyan}Piercer (plants or animals) &  \\ 
-    Feeding Mode & Parasite &  &  \\ 
-    \color{cyan}Feeding Mode & \color{cyan}Other &  &  \\ 
-    \hline
-    \rowcolor{green!25}
-    Locomotion & Swimming/scating & Surface swimmer & Swimmer \\ 
-    \cellcolor{green!25}Locomotion & \cellcolor{green!25}Swimming/diving & \cellcolor{green!25}Full water swimmer & Burrower \\ 
-    Locomotion & Burrowing/boring & Burrower & Crawler \\ 
-    Locomotion & Sprawling/walking & Crawler & \cellcolor{green!50}Sessil \\ 
-    \cellcolor{green!50}Locomotion & \cellcolor{green!50}(semi) sessil & \cellcolor{green!50}Temporarily attachted &  \\ 
-    \color{cyan}Locomotion & \color{cyan}Other & \cellcolor{green!50}Permanently attached &  \\ 
-    \color{cyan}Locomotion &  & \color{cyan}Interstitial &  \\ 
-    \color{cyan}Locomotion &  & \color{cyan}Flier &  \\
-    \hline
-    Respiration & Tegument & Tegument & Tegument \\ 
-    Respiration & Gill & Gill & Gills \\ 
-    \rowcolor{orange!25}
-    Respiration & Plastron & Plastron & Plastron, spiracle \\ 
-    \cellcolor{orange!25}Respiration & \cellcolor{orange!25}Spiracle (aerial) & \cellcolor{orange!25}Spiracle (aerial) &  \\ 
-    \color{cyan}Respiration & \color{cyan}Hydrostatic vesicle & \color{cyan}Hydrostatic vesicle (aerial) &  \\ 
-    \color{cyan}Respiration & \color{cyan}Tapping (air stores of aq. plants) &  &  \\ 
-    \color{cyan}Respiration & \color{cyan}Excursion/Extension (to surface) &  &  \\ 
-    \hline
-    Body size &  & $<$= 0.25cm & Small ($<$ 1 cm) \\ 
-    Body size &  & $>$ 0.25 - 0.5cm & Medium ($>$= 1cm - 2 cm) \\ 
-    Body size &  & $>$ 0.5- 1cm & Large ($>$= 2 cm) \\ 
-    Body size &  & $>$ 1 – 2 cm &  \\ 
-    Body size &  & 2 – 4 cm &  \\ 
-    Body size &  & 4 – 8 cm &  \\ 
-    Body size &  & $>$ 8 cm &  \\ 
-    \hline
-    Reproduction & ovovivipar & ovoviviparity & ovoviviparity \\ 
-    \rowcolor{purple!25}
-    Reproduction & free isolated eggs & isolated eggs, free & aquatic eggs \\ 
-    \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}cemented isolated eggs & \cellcolor{purple!25}isolated eggs, cemented & terrestrial eggs \\
-    \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}fixed clutches & \cellcolor{purple!25}clutches, cemented or fixed &  \\ 
-    \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}free clutches & \cellcolor{purple!25}clutches, free &  \\ 
-    \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}clutches in vegetation & \cellcolor{purple!25}clutches, in vegetation &  \\ 
-    Reproduction & terrestrial clutches & clutches, terrestrial &  \\ 
-    \color{cyan}Reproduction & \color{cyan}asexual & \color{cyan}asexual reproduction &  \\ 
-    \color{cyan}Reproduction & \color{cyan}parasitic &  &  \\ 
-    \hline
-    %\end{tabular}
-%\end{table}
-\end{longtable}
+Cyan colored traits have not been used because they were too different from the amalgamated traits.}
+%     \endfirsthead
+%     \endhead
+%     %\begin{tabular}{llll}
+%     \hline
+%     Grouping feature & Freshwater ecology & Tachet & Amalgamated traits \\ 
+%     \hline
+%     \hline
+%     Voltinism & Semivoltine & Semivoltine & Semivoltine \\ 
+%     Voltinism & Univoltine & Univoltine & Univoltine \\ 
+%     \rowcolor{gray!25}
+%     Voltinism & Bivoltine & Polyvoltine & Bi/Multivoltine \\ 
+%     \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Trivoltine &  &  \\ 
+%     \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Multivoltine &  &  \\ 
+%     \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Flexible &  &  \\ 
+%     \rowcolor{blue!25}
+%     \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Shredder & Shredder & Shredder \\ 
+%     \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Miner & Deposit-feeder & Gatherer \\ 
+%     \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Xylophagus & \cellcolor{blue!50}Absorber & \cellcolor{blue!50}Filterer \\ 
+%     Feeding Mode & Gatherer & \cellcolor{blue!50}Filter-feeder & Herbivore \\ 
+%     \cellcolor{blue!50}Feeding Mode & \cellcolor{blue!50}Active filterer & Scraper & Predator \\ 
+%     \cellcolor{blue!50}Feeding Mode & \cellcolor{blue!50}Passive filterer & Predator & Parasite \\ 
+%     Feeding Mode & Grazer & Parasite &  \\ 
+%     Feeding Mode & Predator & \textit{Piercer (plants or animals)} \textsuperscript{\textit{a}} &  \\ 
+%     Feeding Mode & Parasite &  &  \\ 
+%     \color{cyan}Feeding Mode & \color{cyan}Other &  &  \\ 
+%     \hline
+%     \rowcolor{green!15}
+%     Locomotion & Swimming/scating & Surface swimmer & Swimmer \\ 
+%     \cellcolor{green!15}Locomotion & \cellcolor{green!15}Swimming/diving & \cellcolor{green!15}Full water swimmer & \cellcolor{green!50}Burrower \\ 
+%     \cellcolor{green!50}Locomotion & \cellcolor{green!50}Burrowing/boring & \cellcolor{green!50}Burrower & Crawler \\
+%     Locomotion &  & \cellcolor{green!50}Interstitial & \cellcolor{green!95}Sessil \\
+%     Locomotion & Sprawling/walking & Crawler &  \\ 
+%     \cellcolor{green!95}Locomotion & \cellcolor{green!95}(semi) sessil & \cellcolor{green!95}Temporarily attachted &  \\ 
+%     \color{cyan}Locomotion & \color{cyan}Other & \cellcolor{green!95}Permanently attached &  \\ 
+%     \color{cyan}Locomotion &  & \color{cyan}Flier &  \\
+%     \hline
+%     Respiration & Tegument & Tegument & Tegument \\ 
+%     Respiration & Gill & Gill & Gills \\ 
+%     \rowcolor{orange!25}
+%     Respiration & Plastron & Plastron & Plastron, spiracle \\ 
+%     \cellcolor{orange!25}Respiration & \cellcolor{orange!25}Spiracle (aerial) & \cellcolor{orange!25}Spiracle (aerial) &  \\ 
+%     \color{cyan}Respiration & \color{cyan}Hydrostatic vesicle & \color{cyan}Hydrostatic vesicle (aerial) &  \\ 
+%     \color{cyan}Respiration & \color{cyan}Tapping (air stores of aq. plants) &  &  \\ 
+%     \color{cyan}Respiration & \color{cyan}Excursion/Extension (to surface) &  &  \\ 
+%     \hline
+%     Body size &  & $<$= 0.25cm & Small ($<$ 1 cm) \\ 
+%     Body size &  & $>$ 0.25 - 0.5cm & Medium ($>$= 1cm - 2 cm) \\ 
+%     Body size &  & $>$ 0.5- 1cm & Large ($>$= 2 cm) \\ 
+%     Body size &  & $>$ 1 – 2 cm &  \\ 
+%     Body size &  & 2 – 4 cm &  \\ 
+%     Body size &  & 4 – 8 cm &  \\ 
+%     Body size &  & $>$ 8 cm &  \\ 
+%     \hline
+%     Reproduction & ovovivipar & ovoviviparity & ovoviviparity \\ 
+%     \rowcolor{purple!25}
+%     Reproduction & free isolated eggs & isolated eggs, free & aquatic eggs \\ 
+%     \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}cemented isolated eggs & \cellcolor{purple!25}isolated eggs, cemented & terrestrial eggs \\
+%     \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}fixed clutches & \cellcolor{purple!25}clutches, cemented or fixed &  \\ 
+%     \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}free clutches & \cellcolor{purple!25}clutches, free &  \\ 
+%     \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}clutches in vegetation & \cellcolor{purple!25}clutches, in vegetation &  \\ 
+%     Reproduction & terrestrial clutches & clutches, terrestrial &  \\ 
+%     \color{cyan}Reproduction & \color{cyan}asexual & \color{cyan}asexual reproduction &  \\ 
+%     \color{cyan}Reproduction & \color{cyan}parasitic &  &  \\ 
+%     \hline
+%     %\end{tabular}
+% %\end{table}
+% \end{longtable}
+% \begin{minipage}{\linewidth}\small
+%     \textit{a} Taxa exhibiting this trait have been assigned to predators or herbivores based on a classification by Philippe Usseglio-Polatera.
+% \end{minipage}
 

### 2020-08-31 Paper/Results/Taxonomic_cov_and_info_compl.tex
31.08: Intro+Methods+Results update

--- 2020-07-29 Paper/Results/Taxonomic_cov_and_info_compl.tex
@@
 
-% \usepackage[utf8]{inputenc}
-% \usepackage{hyperref}
-% \usepackage{float}
-% \usepackage[table,xcdraw]{xcolor}
-% \usepackage{color, colortbl}
-% \usepackage{longtable}
-% %\usepackage[sort&compress,square,comma,authoryear]{natbib}
-% \usepackage{booktabs}
-% \usepackage{graphicx}
-% \graphicspath{{/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures/}}
-% \usepackage{longtable}
-% \usepackage{rotating}
-% \usepackage{geometry}
-% \usepackage{array}
-
-% \definecolor{Gray}{gray}{0.9}
-
-% \newcommand{\specialcell}[2][c]{%
-%   \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
-
 \begin{document}
 
-\section{Taxonomic coverage of the trait databases}
+\subsection*{Taxonomic coverage of the harmonized trait datasets}
 
-Regarding the taxonomical coverage, the New Zealand database has, as expected, the smallest taxon pool (Table \ref{tab:tax_coverage}).
-By contrast, the largest taxon pool is spanned by the European trait database with 4225 taxa followed by the North American trait database that contained trait information on 3542 taxa.
-The Australian database contains 1404 taxa.
-The European, New Zealand, and North American databases have most taxa on the highest taxonomical resolution while the Australian database has a similar number of taxa on species and genus-level.
-
-% \begin{table}[ht]
-%   \centering
-%   \caption{Number of taxa per harmonized database and per taxonomic level. Numbers in parenthesis show relative frequencies in percentage.}
-%   \label{tab:tax_coverage}
-%   \begin{tabular}{lccccc}
-%     \hline
-%   Database & Nr. of taxa & Species & Genus & Family & Aquatic insects \\ 
-%   \hline
-%   EU & 4225 & 3951 (93.51) & 257 (6.08) & 17 (0.4) & 3654 (86.49) \\ 
-%   NOA & 3542 & 2418 (68.27) & 1074 (30.32) & 50 (1.41) & 3144 (88.76) \\ 
-%   AUS & 1402 & 564 (40.23) & 578 (41.23) & 260 (18.54) & 1015 (72.4) \\ 
-%   NZ & 478 & 404 (84.52) & 47 (9.83) & 27 (5.65) & 443 (92.68) \\ 
-%   \hline
-%   \end{tabular}
-%   \end{table}
+Regarding the taxonomical coverage, the New Zealand dataset has, as expected, the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
+By contrast, the largest taxon pool is spanned by the European trait dataset with 4110 taxa followed by the North American trait dataset that contained trait information on 3753 taxa.
+The Australian dataset contains 1402 taxa.
+The European, New Zealand, and North American datasets have most taxa on the highest taxonomical resolution while the Australian dataset has a similar number of taxa on species and genus-level.
 
@@
     \begin{tabular}{lccccc}
-    \hline
+    \\
     Database & Nr. of taxa & Species & Genus & Family & Nr. aquatic taxa \\ 
-    \hline
-    Europe & 4110 & 3848 (93.63) & 237 (5.77) & 25 (0.61) & 3579 (87.08) \\ 
-      North America & 3753 & 2414 (64.32) & 1163 (30.99) & 176 (4.69) & 3305 (88.06) \\ 
-      Australia & 1402 & 564 (40.23) & 578 (41.23) & 260 (18.54) & 1016 (72.47) \\ 
-      New Zealand & 478 & 404 (84.52) & 47 (9.83) & 27 (5.65) & 443 (92.68) \\ 
-    \hline
+    \toprule[.1em]
+    EU & 4110 & 3848 (93.63) & 237 (5.77) & 25 (0.61) & 3579 (87.08) \\ 
+    NOA & 3753 & 2414 (64.32) & 1163 (30.99) & 176 (4.69) & 3305 (88.06) \\ 
+    AUS & 1402 & 564 (40.23) & 578 (41.23) & 260 (18.54) & 1016 (72.47) \\ 
+    NZ & 478 & 404 (84.52) & 47 (9.83) & 27 (5.65) & 443 (92.68) \\ 
+    \bottomrule
     \end{tabular}
@@
 
-\newpage
+\subsection*{Completeness of trait information}
 
-\section{Completeness of trait information}
-
-The amount of entries with available information for the individual grouping features varied strongly for the European, North American and Australian databases (Table \ref{tab:trait_coverage}).
-By contrast, the New Zealand database contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
+The amount of entries with available information for the selected grouping features varied strongly for the European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
+By contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
 
@@
     \begin{tabular}{llllllll}
-    \hline
+    \\
     Database & Body form & Oviposition & Voltinism & Locomotion & Size & Respiration & Feeding mode \\ 
-    \hline
+    \toprule[.1em]
     EU & 7 & 16 & 24 & 33 & 11 & 56 & 65 \\ 
-    NOA & 26 & 12 & 47 & 51 & 75 & 44 & 61 \\ 
+    NOA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
     AUS & 5 & 48 & 51 & 42 & 78 & 70 & 99 \\ 
     NZ & 100 & 94 & 100 & 99 & 100 & 100 & 99 \\ 
-    \hline
+    \bottomrule
     \end{tabular}

### 2020-09-02 Paper/Draft_harmonization_paper.tex
Paper: 01.09.2020

@@
 backend = biber,
-style = numeric,
+style = ieee,
 citestyle = numeric-comp,
+maxbibnames=99,
 sorting = none % sort by name year title
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{OVERVIEW RESULTS: Harmonized invertebrate grouping feature databases}
+\title{DRAFT: Harmonized and trait aggregation paper }
 \author{}%Stefan Kunz 
@@
 
-% TODO: Allgemeiner nur auf Ökologie bezogen
-% What is special re freshwaterecology trait research?
-% Difficult to measure some traits (e.g. feeding mode -> Moog)
-% Plant traits can be measured directly -> standardized database developed 
-% list numbers of traits and recorded taxa
-% Areas where freshwater ecology traits are used (move second sentence)
+% Alternative version: 
+Explaining and predicting how communities are shaped by environmental factors is one of the main goals of ecology.
+Organismal traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, might be beneficial in achieving this goal \cite{heino_jani_macroecological_2013}.
+Traits evolve through adaptations (e.g., physiological, behavioral, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
+Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches may be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
+Traits of freshwater invertebrates are difficult to determine because, unlike plants, their traits often cannot be measured directly.
+For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community \cite{moog_comprehensive_nodate}.
+Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
+by relating macroinvertebrate trait composition to environmental factors or as trait metrics in biomonitoring \cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}.
 
-Explaining and predicting how aquatic communities are shaped by environmental factors is one of the main goals of freshwater ecology.
+% Explaining and predicting how aquatic communities are shaped by environmental factors is one of the main goals of freshwater ecology.
 Organismal traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, are increasingly incorporated into freshwater ecology to support this goal, e.g.
@@
 Traits evolve through adaptations (e.g., physiological, behavioral, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
-Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches may be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
-% Traits of freshwater invertebrates are difficult to assess, because, unlike plants, their characteristics often cannot be measured directly.
-For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community.
-% cite Moog!
-% Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g. to ...
+% Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches may be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
 
 In the last decades, freshwater ecologists developed comprehensive invertebrate trait databases for various biogeographic regions \cite{usseglio-polatera_biomonitoring_2000, schmidt-kloiber_www.freshwaterecology.info_2015, vieira_database_nodate, Philips_and_Smith_NZ_DB_2018, kefford_integrated_2020, tomanova_trophic_2006}.
-% ? Cite also Twarodochleb/
 The availability of invertebrate trait data from different biogeographic regions enables comparisons of trait variation and their relation to environmental factors across large scales.
@@
 A grouping feature is defined by Schmera et al.
-2015 as a general property (e.g.
+as a general property (e.g.
 feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species" \cite{schmera_proposed_2015}.
 To our knowledge, only Brown et al.
-2018 \cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
+\cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
 % TODO: Search for trait convergence Doledec!
@@
 Brown et al.
-2018 \cite{brown_functional_2018} harmonized grouping features based on trait databases from Europe, North America, and New Zealand because in these trait databases identical grouping features are classified differently into traits.
+\cite{brown_functional_2018} harmonized grouping features based on trait databases from Europe, North America, and New Zealand because in these trait databases identical grouping features are classified differently into traits.
 As the traits from North America were coded binary in contrast to the fuzzy coded traits from from Europe and New Zealand, the authors consulted experts to assign fuzzy coded traits to North American taxa or inferred them from the European trait database.
@@
 A centralized database with standardized and unambiguous traits and a consistent coding of traits would minimize data processing effort.
-% TODO: Wieso ist es gut zentrale standardisierte definition und traits zu haben?
 
@@
 We (3) re-analyze data on the effect of anthropogenic salinization on biological traits by Szöcs et al.
-\cite{szocs_effects_2014} using harmonized grouping features and harmonized grouping features with aggregated traits.
+\cite{szocs_effects_2014} using harmonized grouping features and aggregated traits.
 By comparison with the original analysis, we investigate how harmonizing and aggregating trait data can alter the outcome of trait-environment relationships.
@@
 
-We extracted information from 4 trait databases from Europe, North America, Australia, and New Zealand and harmonized 7 grouping features.
+We extracted information from 6 trait databases from Europe, North America, Australia, and New Zealand and harmonized 7 grouping features.
 Trait information for Europe was obtained from the Freshwaterecology database \cite{schmidt-kloiber_www.freshwaterecology.info_2015} and complemented by Tachet \cite{usseglio-polatera_biomonitoring_2000} to fill missing information (e.g.
@@
 % TODO: mention that tachet and freshwaterecology are not seperate (but we did it separately)
-Trait information for North America was obtained from Laura Twardochleb (\textit{in prep.}) and complemented by Vieira et al.
-2006 \cite{vieira_database_nodate}.
+Trait information for North America was obtained from Twardochleb et al.
+\cite{twardochleb_trait_data_2020} and complemented by Vieira et al.
+\cite{vieira_database_nodate}.
 Data on body for European and North American taxa was provided based on expert knowledge \cite{polatera_personal_information_2020}.
@@
 \begin{tabular}{lll}
-\\
+\toprule[.1em]
 Grouping feature & Trait & Amalgamated traits\\
@@
 \midrule
-Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm (Tachet: \textless 10 mm)\\ 9 - 16 mm (Tachet: 10 - 20 mm)\\ \textgreater 16 mm (Tachet: \textgreater 20 mm)\end{tabular}                                                                                                                \\
+Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm, \textless 10 mm\\ 9 - 16 mm, 10 - 20 mm\\ \textgreater 16 mm, \textgreater 20 mm\end{tabular}                                                                                                                \\
 \midrule
@@
 Traits of the harmonized grouping feature datasets were aggregated to family-level using three approaches.
-I) direct aggregation of taxa to family-level giving equal weight to every species using the mean or median, denote \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively.
-II) stepwise aggregation, i.e first to the genus-level and subsequently to the family-level using the mean or median.
+I) direct aggregation of taxa to family-level giving equal weight to every species using the mean or median, denoted \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively.
+II) stepwise aggregation, i.e.
+first to the genus-level and subsequently to the family-level using the mean or median.
 This approach gives equal weights to each genus.
@@
 For the North American database, we compared aggregated trait affinities with assigned trait affinities on family-level for the grouping features feeding mode, respiration, size, voltinism, and locomotion.
-The assigned trait affinities at family-level are part of the North American database (\textit{Laura Twardochleb in prep.}) and originate from expert knowledge \cite{twardochleb_personal_information_mpyne_2020}.
+The assigned trait affinities at family-level are part of the North American database (\cite{twardochleb_trait_data_2020}) and originate from expert knowledge.
 Trait information was available for 94 families of which all were present in the aggregated North American database (total number of cases 1598).
@@
 \cite{szocs_effects_2014} used, but 6 of them have been harmonized from the European harmonized grouping feature dataset for our analysis.
-The harmonized grouping features used were \textit{Size, Feeding mode, Locomotion, Reproduction/Oviposition, Respiration}, and \textit{Voltinism}.
+The harmonized grouping features used were \textit{Size, Feeding mode, Locomotion, Oviposition, Respiration}, and \textit{Voltinism}.
 Traits of those grouping features responded strongly to salinity in the study of \cite{szocs_effects_2014}.
-Additionally, for testing the effect of aggregated traits we assigned to each taxon in \cite{szocs_effects_2014} the aggregated trait value for its corresponding family and repeated the RDA.
-
-% TODO FIX reference to SI
-% ?(see SI for a more in-depth comparison to the original results using harmonized grouping features)
+Additionally, for testing the effect of aggregated traits we assigned to each taxon in Szöcs et al.
+\cite{szocs_effects_2014} the aggregated trait value for its corresponding family and repeated the RDA.
+% ? reference to SI
 
@@
 \newpage
-\section*{Results harmonized grouping feature databases}
+\section*{Results}
 
@@
 % if data quality is poor, when synthesizing information is hard 
+% In general, differences produced by the aggregation methods seem to arise by using mean or median, not driven by different weighting approaches (direct vs. stepwise vs. weighted)
+
+\newpage
 
@@
 \printbibliography
+
 \newpage
 
-%! SI
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%% Supporting information %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\setcounter{table}{0}
+\setcounter{figure}{0}
+
 \subfile{Results/SI}

### 2020-09-02 Paper/Results/Results_trait_harmonization.tex
Paper: 01.09.2020

@@
 
-Overall, using the harmonized grouping features lead only to slightly different results in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and SI \ref{subsec:SI_szoecs_reanalysis}).
-According to the RDA of trait composition sites with high salinity were characterized by multivoltine, ovivoparous, gill-respirating, and shredder species.
+Overall, using the harmonized grouping features lead only to slightly different results in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and SI).
+According to the RDA of the trait composition sites with high salinity were characterized by multivoltine, ovivoparous, gill-respirating, and shredder species.
 Only species with the trait life cycle duration $> 1$ year fail to characterize sites with high salinization.
@@
 Like in the original analysis, transition and upstream sites from the point source are characterized by univoltine species and species that lay their eggs in an aquatic environment.
-We constructed also the linear models of the original analyses, using the traits on the extremes of the conductivity axis and found similar results as the original analysis (SI \ref{subsec:SI_szoecs_reanalysis}).
+We constructed also the linear models of the original analyses, using the traits on the extremes of the conductivity axis and found results similar to the original analysis (Table S\ref{stab:linear_models_new} and S\ref{stab:linear_models_edi}).
 
@@
     \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
-    \caption{Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonized grouping features, and using harmonized grouping features with assigned trait affinities from traits aggregated to family-level.}
+    \caption{Species scores obtained by RDA from the original analysis \cite{szocs_effects_2014}, using harmonized grouping features, and using harmonized grouping features with assigned trait affinities aggregated to family-level.}
     \label{fig:rda_species_scores}

### 2020-09-02 Paper/Results/SI.tex
Paper: 01.09.2020

@@
 \subsection*{Comparison of the trait aggregation methods with each other}
+\label{sec:compa_aggr_methods}
 
@@
     \includegraphics[width=16.5cm, height=10cm]{Comparison_trait_agg_methods.png}
-    \caption{Means of absolute differences in trait affinities with standard deviations per region for all grouping features.
+    \caption{Comparison of trait aggregation methods when aggregating over all traits for all datasets.
+Displayed are means of absolute differences in trait affinities with standard deviations (truncated at 0).
 Compared aggregation methods are displayed on the y-axis.
-N indicates the number of cases where differences occurred.}
+N indicates the number of cases where differences occurred.
+Total number of cases: Australia 2223, Europe 3352, New Zealand 777, and North America 4080.}
+    \label{fig:comp_aggr_methods}
 \end{figure}
@@
 
-\subsection*{Re-analysis of Szöcs et al. 2014 using harmonized grouping features.}
+\subsection*{Re-analysis of Szöcs et al. using harmonized grouping features.}
 \label{subsec:SI_szoecs_reanalysis}
@@
 Bold values indicate statistically significant effects (p $<$ 0.05).}
-    \begin{tabular}{lccccc}
-    \hline
+    \label{stab:linear_models_new}
+    \begin{tabular}{l|ccccc}
+    \toprule[.1em]
     & \specialcell{Feeding mode:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell{Voltinism:\\ bi- or multivoltine} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
-    \hline
+    \toprule[.1em]
     Intercept ($=$ upstream) & \textbf{-1.041} & \textbf{-0.486} & 0.375* & \textbf{-0.823} & 0.092\\ 
@@
     Year 2009 & 0.175 & 0.086 & -0.088 & 0.246 & 0.141\\ 
-    \hline
+    \bottomrule
     \end{tabular}
@@
     significant effects (p $<$ 0.05).}
-    \begin{tabular}{lccccc}
-    \hline
+    \label{stab:linear_models_edi}
+    \begin{tabular}{l|ccccc}
+    \toprule[.1em]
     & \specialcell{Feeding habits:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell {Cycles per year:\\ $>$ 1} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
-    \hline
+    \toprule[.1em]
     Intercept ($=$ upstream) & \textbf{-0.853} & \textbf{-0.478} & \textbf{0.603} & \textbf{-0.838} & 0.111 \\ 
@@
     Year 2009 & 0.167 & 0.084 & -0.104 & 0.250 & 0.139 \\ 
-    \hline
+    \bottomrule
     \end{tabular} 

### 2020-09-02 Paper/Trait_def_table/Trait_definitions_table.tex
31.08: Intro+Methods+Results update
Paper: 01.09.2020

@@
 \documentclass[../Draft_harmonization_paper.tex]{subfiles}
-% \documentclass{article}
-% \usepackage{rotating} 
-% \usepackage{geometry}
-% \usepackage{array}
-% \usepackage{lscape}
-% \usepackage{longtable}
-% \usepackage{hhline}
 
@@
 % TODO Start with mentioning that two core differences can exist: 1) definitions can be different semantically; 2) traits can be combined or more differentiated 
-\section{Discrepancies of invertebrate trait definitions}
+\subsection*{Discrepancies of invertebrate trait definitions}
 
 Definitions of grouping features and traits varied in their level of detail.
-The Tachet, Freshwaterecology, and North American (Twardochleb) trait databases provided more detailed descriptions of their trait information compared to the North American (Vieira) and New Zealand databases.
-An exception is the Australian trait database which is a collection of seven trait datasets (\cite{kefford_integrated_2020}).
+The Freshwaterecology database, and databases from Tachet and Twardochleb et al.
+provided more detailed descriptions of their trait information compared to the databases from Vieira et al.
+and New Zealand.
+An exception is the Australian trait database which is a collection of seven trait datasets \cite{kefford_integrated_2020}.
 Thus, grouping features occur multiple times with varying differentiation into traits.
 Depending on the dataset trait information is described with more or less detail.
-%?
-use term membership state (Schmera)
 
 The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope.
-We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{tab:trait_definitions}).
+We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{stab:trait_definitions}).
 Both, differences in differentiation and scope can lead to discrepancies in trait definitions.
@@
 Therefore, the Freshwaterecology database defines e.g.
-predator as "eating from prey", while the other databases use the mouthpart morphology in their definition.
+predator as "eating from prey", while the other databases use the mouthpart morphology as basis of their definition.
 The Tachet database captures the food source in an additional grouping feature.
-Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (see for details Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{tab:trait_definitions}).
+Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{stab:trait_definitions}).
 Locomotion definitions differ also in scope between databases.
@@
 \begin{landscape}
-    \begin{longtable}{|m{2.5cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}|}
+    \begin{longtable}{m{2.5cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
     \caption{Number of traits per grouping feature and type of coding of the traits for the respective grouping feature per database.}
     \endfirsthead
-    \hline
+    \toprule[.1em]
     \label{tab:trait_databases_coding_differentiation}
     Database & Feeding Mode & Voltinism & Locomotion & Respiration & Reproduction & Size & Body Form \\ 
-    \hline
-    \hline
+    \toprule[.1em]
     \multirow{2}{*}[-5mm]{ \specialcell{Freshwater- \\ ecology}} & 
@@
     \cline{2-8} &
-    \multicolumn{7}{c |}{binary}
+    \multicolumn{7}{c }{binary}
     \\
@@
     \cline{2-8} & 
-    \multicolumn{7}{c |}{fuzzy $[0-3]$}
+    \multicolumn{7}{c }{fuzzy $[0-3]$}
     \\
-    \hline
+    \bottomrule
     \end{longtable}

### 2020-09-04 Paper/Draft_harmonization_paper.tex
04.09.2020: Intor+Method+Res send to Co-Authors

@@
 
-% Alternative version: 
 Explaining and predicting how communities are shaped by environmental factors is one of the main goals of ecology.
@@
 Traits evolve through adaptations (e.g., physiological, behavioral, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
-Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches may be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
+Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
 Traits of freshwater invertebrates are difficult to determine because, unlike plants, their traits often cannot be measured directly.
@@
 
+%%% Old Version:
 % Explaining and predicting how aquatic communities are shaped by environmental factors is one of the main goals of freshwater ecology.
@@
 % Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches may be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \cite{usseglio-polatera_biomonitoring_2000}, Poff et al.
-(2010) \cite{poff_developing_2010} characterized trait composition across sites in the Western US using traits from Poff et al.
-(2006) \cite{poff_functional_2006}, and Botwe et al.
+\cite{poff_developing_2010} characterized trait composition across sites in the Western US using traits from Poff et al.
+\cite{poff_functional_2006}, and Botwe et al.
 \cite{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from Poff et al.
-(2006) \cite{poff_functional_2006} and Schäfer et al.
+\cite{poff_functional_2006} and Schäfer et al.
 \cite{schafer_trait_2011}.
@@
 \cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
-% TODO: Search for trait convergence Doledec!
+% TODO: ?Paper trait convergence Doledec
 
@@
 Up to now, studies on how and to which extent different trait aggregation methods influence trait-based analysis are missing.
-% TODO: Satz wieso es gut wäre wenn man das wissen würde -> lead to last paragraph
+Knowing this can aid the choice of aggregation method for future studies.
 
@@
 \cite{vieira_database_nodate}.
-Data on body for European and North American taxa was provided based on expert knowledge \cite{polatera_personal_information_2020}.
+Data on body form for European and North American taxa was provided based on expert knowledge \cite{polatera_personal_information_2020}.
 For Australia and New Zealand, we used trait databases from Kefford et al.
@@
 Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition.
-Further details can be found in \cite{szocs_effects_2014}.
+Further details can be found in Szöcs et al.
+\cite{szocs_effects_2014}.
 We compared the species scores obtained from redundancy analysis (RDA) for traits constrained by electric conductivity from the original study to species scores when including harmonized grouping features.

### 2020-09-04 Paper/Results/Taxonomic_cov_and_info_compl.tex
Paper: 01.09.2020
04.09.2020: Intor+Method+Res send to Co-Authors

@@
     \begin{tabular}{lccccc}
-    \\
+    \toprule[.1em]
     Database & Nr. of taxa & Species & Genus & Family & Nr. aquatic taxa \\ 
@@
     \centering
-    \caption{Displayed is the percentage of entries that have information for the individual grouping features per database.} 
+    \caption{Displayed is the percentage of entries that have information for the individual grouping features per dataset.} 
     \label{tab:trait_coverage}
     \begin{tabular}{llllllll}
-    \\
+    \toprule[.1em]
     Database & Body form & Oviposition & Voltinism & Locomotion & Size & Respiration & Feeding mode \\ 

### 2020-09-05 Paper/Results/SI.tex
05.09.2020: Minor edits SI

@@
 
+\subsubsection*{RDA of trait composition}
+
 \begin{figure}[H]
@@
 Only traits with a mahalanobis distance greater than 5.02 were labeled in accordance to the procedure in Szöcs et al.
-2014.
+\cite{szocs_effects_2014}.
     } 
@@
 
-\section*{Trait distribution along first RDA axis} 
+\subsubsection*{Trait distribution along first RDA axis} 
 \begin{figure}[H]
@@
     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_Szoecs_2014.png}
-    \caption{Trait scores on the first RDA axis for the traits responding to high salinity in Szöcs et al. 2014
+    \caption{Trait scores on the first RDA axis for the traits responding to high salinity in Szöcs et al. \cite{szocs_effects_2014}
     .
@@
 \newpage
-\section*{Linear models of trait proportions}
+\subsubsection*{Linear models of trait proportions}
+
 \textit{Linear models of trait proportions with harmonized traits:}
@@
 \newline
-\textit{Linear models of trait proportions Szöcs et al. 2014:}
+\textit{Linear models of trait proportions Szöcs et al. :}
 \begin{table}[ht]
     \centering
-    \caption{Results of linear models for the five selected traits for Szöcs et al. 2014. Trait proportions were logit transformed prior model building, estimates are on the logit scale.
+    \caption{Results of linear models for the five selected traits for Szöcs et al.
+\cite{szocs_effects_2014}.
+Trait proportions were logit transformed prior model building, estimates are on the logit scale.
     Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically
@@
 
-\section*{Trait proportions over time}
+\subsubsection*{Trait proportions over time}
 \begin{figure}[H]
@@
     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_Szoecs_2014.png}
-    \caption{Proportions for five selected traits for down- and upstream sites (traits that have been promoted by salinization) from Szöcs et al. 2014.} 
+    \caption{Proportions for five selected traits for down- and upstream sites (traits that have been promoted by salinization) from Szöcs et al. \cite{szocs_effects_2014}.} 
 \end{figure}
 
-% \section*{Harmonization of the European trait databases}
-% \label{sec:SI_harmonization_EU}
+\subsection*{Discrepancies in trait definitions}
 
-% % \cellcolor{blue!25}
-% \begin{longtable}{lll|l}
-% %\begin{table}[ht]
-% %    \centering
-%     \caption{Representation of traits per grouping feature and their harmonization for the European trait databases.
-The color coding indicates traits that have been harmonized.
-Cyan colored traits have not been used because they were too different from the amalgamated traits.}
-%     \endfirsthead
-%     \endhead
-%     %\begin{tabular}{llll}
-%     \hline
-%     Grouping feature & Freshwater ecology & Tachet & Amalgamated traits \\ 
-%     \hline
-%     \hline
-%     Voltinism & Semivoltine & Semivoltine & Semivoltine \\ 
-%     Voltinism & Univoltine & Univoltine & Univoltine \\ 
-%     \rowcolor{gray!25}
-%     Voltinism & Bivoltine & Polyvoltine & Bi/Multivoltine \\ 
-%     \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Trivoltine &  &  \\ 
-%     \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Multivoltine &  &  \\ 
-%     \cellcolor{gray!25}Voltinism & \cellcolor{gray!25}Flexible &  &  \\ 
-%     \rowcolor{blue!25}
-%     \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Shredder & Shredder & Shredder \\ 
-%     \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Miner & Deposit-feeder & Gatherer \\ 
-%     \cellcolor{blue!25}Feeding Mode & \cellcolor{blue!25}Xylophagus & \cellcolor{blue!50}Absorber & \cellcolor{blue!50}Filterer \\ 
-%     Feeding Mode & Gatherer & \cellcolor{blue!50}Filter-feeder & Herbivore \\ 
-%     \cellcolor{blue!50}Feeding Mode & \cellcolor{blue!50}Active filterer & Scraper & Predator \\ 
-%     \cellcolor{blue!50}Feeding Mode & \cellcolor{blue!50}Passive filterer & Predator & Parasite \\ 
-%     Feeding Mode & Grazer & Parasite &  \\ 
-%     Feeding Mode & Predator & \textit{Piercer (plants or animals)} \textsuperscript{\textit{a}} &  \\ 
-%     Feeding Mode & Parasite &  &  \\ 
-%     \color{cyan}Feeding Mode & \color{cyan}Other &  &  \\ 
-%     \hline
-%     \rowcolor{green!15}
-%     Locomotion & Swimming/scating & Surface swimmer & Swimmer \\ 
-%     \cellcolor{green!15}Locomotion & \cellcolor{green!15}Swimming/diving & \cellcolor{green!15}Full water swimmer & \cellcolor{green!50}Burrower \\ 
-%     \cellcolor{green!50}Locomotion & \cellcolor{green!50}Burrowing/boring & \cellcolor{green!50}Burrower & Crawler \\
-%     Locomotion &  & \cellcolor{green!50}Interstitial & \cellcolor{green!95}Sessil \\
-%     Locomotion & Sprawling/walking & Crawler &  \\ 
-%     \cellcolor{green!95}Locomotion & \cellcolor{green!95}(semi) sessil & \cellcolor{green!95}Temporarily attachted &  \\ 
-%     \color{cyan}Locomotion & \color{cyan}Other & \cellcolor{green!95}Permanently attached &  \\ 
-%     \color{cyan}Locomotion &  & \color{cyan}Flier &  \\
-%     \hline
-%     Respiration & Tegument & Tegument & Tegument \\ 
-%     Respiration & Gill & Gill & Gills \\ 
-%     \rowcolor{orange!25}
-%     Respiration & Plastron & Plastron & Plastron, spiracle \\ 
-%     \cellcolor{orange!25}Respiration & \cellcolor{orange!25}Spiracle (aerial) & \cellcolor{orange!25}Spiracle (aerial) &  \\ 
-%     \color{cyan}Respiration & \color{cyan}Hydrostatic vesicle & \color{cyan}Hydrostatic vesicle (aerial) &  \\ 
-%     \color{cyan}Respiration & \color{cyan}Tapping (air stores of aq. plants) &  &  \\ 
-%     \color{cyan}Respiration & \color{cyan}Excursion/Extension (to surface) &  &  \\ 
-%     \hline
-%     Body size &  & $<$= 0.25cm & Small ($<$ 1 cm) \\ 
-%     Body size &  & $>$ 0.25 - 0.5cm & Medium ($>$= 1cm - 2 cm) \\ 
-%     Body size &  & $>$ 0.5- 1cm & Large ($>$= 2 cm) \\ 
-%     Body size &  & $>$ 1 – 2 cm &  \\ 
-%     Body size &  & 2 – 4 cm &  \\ 
-%     Body size &  & 4 – 8 cm &  \\ 
-%     Body size &  & $>$ 8 cm &  \\ 
-%     \hline
-%     Reproduction & ovovivipar & ovoviviparity & ovoviviparity \\ 
-%     \rowcolor{purple!25}
-%     Reproduction & free isolated eggs & isolated eggs, free & aquatic eggs \\ 
-%     \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}cemented isolated eggs & \cellcolor{purple!25}isolated eggs, cemented & terrestrial eggs \\
-%     \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}fixed clutches & \cellcolor{purple!25}clutches, cemented or fixed &  \\ 
-%     \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}free clutches & \cellcolor{purple!25}clutches, free &  \\ 
-%     \cellcolor{purple!25}Reproduction & \cellcolor{purple!25}clutches in vegetation & \cellcolor{purple!25}clutches, in vegetation &  \\ 
-%     Reproduction & terrestrial clutches & clutches, terrestrial &  \\ 
-%     \color{cyan}Reproduction & \color{cyan}asexual & \color{cyan}asexual reproduction &  \\ 
-%     \color{cyan}Reproduction & \color{cyan}parasitic &  &  \\ 
-%     \hline
-%     %\end{tabular}
-% %\end{table}
-% \end{longtable}
-% \begin{minipage}{\linewidth}\small
-%     \textit{a} Taxa exhibiting this trait have been assigned to predators or herbivores based on a classification by Philippe Usseglio-Polatera.
-% \end{minipage}
-
-%%%%%%%%%%%%%%%%%%%% OLD %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection*{Deviance in trait affinities between \textit{stepwise\_agg} and \textit{direct\_agg (median)}}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Deviances_stepwise_dir_overview.png}
-%     \caption{Affinity deviances for all deviating cases between the \textit{stepwise\_agg} and \textit{direct\_agg}, see section \ref{sec:dev_stepwise_direct_agg}.}
-%     \label{fig:stepwise_dir_agg}
-% \end{figure}
-
-% \subsection*{Comparison of trait affinity values \textit{direct\_agg} using median or mean}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Deviances_dir_median_mean_overview.png}
-%     \caption{Affinity deviances for all deviating cases between the \textit{direct\_agg (median)} and \textit{direct\_agg (mean)}, see section \ref{sec:comp_direct_agg_median_mean}.}
-%     \label{fig:dir_agg_median_mean}
-% \end{figure}
-
-% \subsection*{Deviances in trait affinities between \textit{direct\_agg} and \textit{weighted\_agg}}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Deviances_dir_weighted_overview.png}
-%     \caption{Affinity deviances for all deviating cases of comparisons between the \textit{direct\_agg (median)} and \textit{direct\_agg (mean)} with \textit{weighted\_agg}, see section \ref{sec:dev_dir_agg_weighted}.}
-%     \label{fig:dir_agg_median_mean_weighted}
-% \end{figure}
+\begin{landscape}
+    \begin{longtable}{m{1.7cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}}
+        \caption{Comparison of trait definitions between invertebrate trait databases.
+Only traits that are differently described across databases are listed.
+The definition is quoted if it enables differences to be identified, otherwise the differences are described.
+The hyphen indicates a missing trait.
+Reproduction was captured in multiple grouping features per database.
+Hence, differences for reproduction have been described in the paper.
+Body form traits are not different between databases, except that the North America (Vieira) database contains the trait Bluff (blocky) which does not appear in the other databases.}
+        \label{stab:trait_definitions}
+        \endfirsthead
+        \toprule[.1em]
+        Trait & Freshwaterecology & Tachet & \specialcell{North America \\ (Twardochleb)} & 
+        North America (Vieira) & Australia & New Zealand \\
+        \toprule[.1em]
+        Feeding shredder & 
+        "Feed from fallen leaves, plant tissues, CPOM" & 
+        "Eat coarse detritus, plants or \textit{animal material}" & 
+        \begin{itemize}
+            \item "Shred decomposing vascular plant tissue"
+            \item Trait herbivore includes among others insect that shred \textit{living aquatic plants} 
+        \end{itemize} & 
+        Shredder & 
+        \begin{itemize}
+            \item Detrivore \textsuperscript{\textit{a}}
+            \item Trait herbivore includes among others the trait shredder
+        \end{itemize} & 
+        Shredders
+        \\ 
+        \midrule
+        Feeding predator & 
+        "Eating from prey" & 
+        \begin{itemize}
+            \item Carvers, engulfers \& swallowers
+            \item Piercers (plants \& animals) are an additional trait
+        \end{itemize} & % Notes: Tachet -> Piercer (plants & animals)
+        Engulfers ("ingest prey whole or in parts") \& 
+        piercers ("prey tissues and suck fluids") & 
+        Predator &
+        Piercer \& engulfer &
+        Predator
+        \\ 
+        \midrule
+        Feeding filter-feeder & 
+        Distinguishes between active and passive &
+        No distinction between active and passive &
+        No distinction between active and passive &
+        No distinction between active and passive &
+        No distinction between active and passive &
+        No distinction between active and passive
+        \\
+        \toprule[.1em]
+        Semivoltine & 
+        "One generation in two years" & 
+        "Life cycle lasts \textit{at least} two years" & 
+        "$< 1$ generation per year" & 
+        "$< 1$ generation per year" & 
+        "$< 1$ generation per year" & 
+        "$< 1$ reproductive cycle per year"
+        \\
+        \midrule
+        Multivoltine & 
+        "More than \textit{three} generations per year" \textsuperscript{\textit{b}}& 
+        "Able to complete \textit{at least} two successive generations per year" &
+        "$> 1$ generations per year" &
+        "$> 1$ generations per year" & 
+        \begin{itemize}
+            \item 1-2 generations per year
+            \item bi/multivoltine
+            \item up to 5 generations per year
+            \item up to 10 generations per year
+        \end{itemize}
+        & 
+        "$> 1$ reproductive cycles per year"
+        \\
+        \toprule[.1em]
+        Locomotion swimming & 
+        \begin{itemize}
+            \item Passive movement like floating or drifting (trait swimming/scating)
+            \item Active movement (trait swimming/diving)
+        \end{itemize}. &
+        \begin{itemize}
+            \item Surface swimmers (over and under the water surface)
+            \item Full water swimmers (e.g. Baetidae).
+        \end{itemize} & 
+        "Adapted for "fishlike" swimming" & 
+        Swimmer & 
+        Distinguishes swimmer and skater & 
+        Swimmers (water column)
+        \\
+        \midrule
+        Locomotion burrowing & 
+        "Burrowing in \textit{soft} substrates or boring in \textit{hard} substrates" & 
+        \begin{itemize}
+            \item Burrowing "within the first centimeters of the benthic fine sediment"
+            \item Differentiates also the trait interstitial (endobenthic)
+        \end{itemize} & 
+        "Inhabiting \textit{fine} sediment of streams and lakes" &
+        Burrower & 
+        "Moving deep into the substrate and thus avoiding flow" &
+        Burrowers (infauna)
+        \\
+        \midrule
+        Locomotion sprawling \& walking & 
+        "Sprawling or walking actively with legs, pseudopods or on a mucus" &
+        - & 
+        Sprawling: "inhabiting the surface of floating leaves of vascular hydrophytes or fine sediments" & 
+        Sprawler &
+        - & 
+        - \\
+        \midrule
+        Locomotion crawling & 
+        - &
+        "Crawling over the bottom substrate" & 
+        Defined as crawling on the surface of floating leaves or fine sediments on the bottom & 
+        - & 
+        Database contains traits crawler, 
+        sprawler, climber and clinger. &
+        Crawlers (epibenthic) \\
+        \midrule
+        Locomotion sessil & 
+        Does not distinguish temporarily and permanently attached & 
+        Distinguishes temporarily and permanently attached & 
+        Does not distinguish temporarily and permanently attached & 
+        Does not distinguish temporarily and permanently attached & 
+        Distinguishes temporarily and permanently attached & 
+        Does not distinguish temporarily and permanently attached \\
+        \toprule[.1em]
+        Respiration plastron \& spiracle & 
+        Plastron and spiracle (aerial) are two separate traits & 
+        Definition includes respiration using air stores of aquatic plants & 
+        Plastron and spiracle combined into one trait & 
+        Distinguishes spiracular gills, plastron, atmospheric breathers and plant breathers &
+        Plastron and spiracle (termed aerial) occur as separate and combined traits. Contains also traits: air (plants), atmospheric, and functional spiracles &
+        Distinguishes plastron and spiracle (termed aerial) \\
+        \toprule[.1em]
+        Body size small & 
+        - &
+        \multirow{3}{*}{\specialcell{Multiple size \\ classifications \textsuperscript{\textit{d}}}} & 
+        $<$ 9 mm & 
+        $<$ 9 mm & 
+        $<$ 9 mm \textsuperscript{\textit{a;c}} &
+        \multirow{3}{*}{\specialcell{Multiple size \\ classifications \textsuperscript{\textit{e}}}}
+        \\
+        \cline{1-2}
+        \cline{4-6}
+        Body size medium & 
+        - &
+        &
+        9 - 16 mm & 
+        9 - 16 mm & 
+        9 - 16 mm &
+        \\
+        \cline{1-2}
+        \cline{4-6}
+        Body size large & 
+        - &
+        &
+        $>$ 16 mm &
+        $>$ 16 mm &
+        $>$ 16 mm &
+        \\
+        \bottomrule
+    \end{longtable}
+    \begin{minipage}{\linewidth}\small
+        \textit{a} Traits from Botwe et al.
+        \newline
+        \textit{b} Contains also bivoltine (two generations per year), trivoltine (three generations per year) and flexible.
+        \newline
+        \textit{c} Contains a size trait with numeric size values. Contains also traits classifying size like Tachet and like the North American trait databases. 
+        \newline
+        \textit{d} Size classifications: \textit{$<=0.25$ cm, $> 0.25-0.5$ cm, $0.5-1$ cm, $1-2$ cm, $2-4$ cm, $4-8$ cm, $> 8$ cm}. No distinction into small, medium and large.
+        \newline
+        \textit{e} Size classifications: \textit{$> 0.25-0.5$ cm, $0.5-1$ cm, $1-2$ cm, $2-4$ cm, $4-8$ cm}. No distinction into small, medium and large.
+    \end{minipage}
+\end{landscape}
 

### 2020-10-04 Paper/Draft_harmonization_paper.tex
04.10: First res base simulation 04.10: First res base simulation

@@
 \cite{brown_functional_2018} harmonized grouping features based on trait databases from Europe, North America, and New Zealand because in these trait databases identical grouping features are classified differently into traits.
-As the traits from North America were coded binary in contrast to the fuzzy coded traits from from Europe and New Zealand, the authors consulted experts to assign fuzzy coded traits to North American taxa or inferred them from the European trait database.
+As the traits from North America were coded binary in contrast to the fuzzy coded traits from Europe and New Zealand, the authors consulted experts to assign fuzzy coded traits to North American taxa or inferred them from the European trait database.
 Thus, it becomes apparent that using invertebrate trait data from several regions requires extensive data processing prior to the actual data analysis.
@@
 Aggregated trait affinities of the five trait aggregation methods (\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg}) were compared to trait affinities assigned at family-level by experts, which were available for the Australian and North American database for a subset of grouping features and taxa.
-For the Australian database, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman et al.
-\cite{chessman_dissolved-oxygen_2018}.
-In Chessman et al.
-\cite{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the harmonized Australian database except that the trait parasite is missing.
-We conducted the comparison for the 220 families available in Chessman et al.
-\cite{chessman_dissolved-oxygen_2018}.
+For the Australian database, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman \cite{chessman_dissolved-oxygen_2018}.
+In Chessman \cite{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the harmonized Australian database except that the trait parasite is missing.
+We conducted the comparison for the 220 families available in Chessman \cite{chessman_dissolved-oxygen_2018}.
 Considering each factor combination of family and trait (in total 8) this amounts to 1760 cases.
@@
 
-% Stat. techniques developed -> cannot use full potential
-% if data quality is poor, when synthesizing information is hard 
-% In general, differences produced by the aggregation methods seem to arise by using mean or median, not driven by different weighting approaches (direct vs. stepwise vs. weighted)
+% Influence of aggregation methods on trait-environment relationships:
+% 1) In general, differences produced by the aggregation methods seem to arise by using mean or median, 
+% not driven by different weighting approaches (direct vs. stepwise vs. weighted) 
+% -> link to taxonomic hierarchy, many families have only a few genera
+% -> Similarly, many genera have only a few species
+% -> linear relationship: the more genus per family, the more species (although there are exceptions -> e.g. Europe)
+% 
+% Differences for NOA greater due to coding?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Ben's Comment: -> But another issues is that these aggregation methods were being compared to traits assigned at the family level, which I understand was often done by expert opinion.
+So, these traits assigned at the family level may not be really “correct”!
+The difference between the trait aggregated to family and its designation at the family level could indicate: (a) the aggregation method is “no good”, (b) the trait assigned at the family level was “no good”, or (c) both a and b.
+
+% Simulation result: 
+% -  base simulation with similar amount of speices per genus and genera per family and varying trait values
+% results can vary when variation in trait values increases 
+% However, mostly the different aggregation methods result in similar trait affinities
+% when differences occur, only for: 
+% dir_median vs stepwise median
+% direct mean vs stepwise median
+% stepwise mean vs stepwise median
+% direct mean vs direct median
+% stepwise median vs weighed agg
+% Trait variability: 0.3 and greater
+% Max diff ~ 0.2
+
+% - Results for varying taxonomic hierarchy:
+% Which levels?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% 2) Harmonization: Minor influence on RDA species scores
+% RDA species scores 
+%   -> Normalized eigenvectors
+%   -> dependent on nr. of variables? Nr. of response variables not really influential 
+% We used only a small-scale study -> What's different to large-scale studies?
+
+% Further aggr. after harmonization: no difference to the harmonized dataset
+% ?Logical because trait aggr. methods themselves showed only minor differences
+
+% Complex Stat. techniques developed -> cannot use full potential
 
@@
 
-% Trait definitions 
-\subfile{Trait_def_table/SI_trait_def_table2.tex}
-
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%% Examples of trait databases %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % ? Also mention Tomanova? -> not used here
-% \begin{table}[ht]
-%   \centering
-%     \caption{Examples of aquatic invertebrate trait databases established in the last decades.
-Differences in codings and trait definitions are outlined for these databases in Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{tab:trait_definitions}.}
-%     \label{tab:overview_trait_dbs}
-%     \begin{tabular}{lcccl}
-%     \hline
-%     Database & \specialcell{Nr. of grouping \\ features} & \specialcell{Main organism \\ groups} & \specialcell{Taxa and \\ resolution} & Citation \\ 
-%     \hline
-%     Freshwaterecology & 40 & \specialcell{Invertebrates, biased \\ towards aquatic insects} & Species-level & \cite{schmidt-kloiber_www.freshwaterecology.info_2015} \\ 
-%     Tachet & 21 & \specialcell{Invertebrates, biased \\ towards aquatic insects} & \specialcell{Taxa on species, \\ genus, and family-level} & \cite{usseglio-polatera_biomonitoring_2000} \\ 
-%     \specialcell{North America \\ (Vieira)} & 62 & \specialcell{Invertebrates, biased \\ towards aquatic insects} & \specialcell{Taxa on species, \\ genus, and family-level} & \cite{vieira_database_nodate} \\
-%     \specialcell{North America \\ (Twardochleb)} & 11 & Aquatic insects & \specialcell{Taxa on species, \\ genus, and family-level} & \cite{vieira_database_nodate} & \textit{In prep.} \\ 
-%     Australia & & \specialcell{Invertebrates, biased \\ towards aquatic insects} & \specialcell{Taxa on species, \\ genus, and family-level} & \cite{kefford_integrated_2020} \\
-%     New Zealand & & & & \cite{Philips_and_Smith_NZ_DB_2018}\\
-%     \hline
-%     \end{tabular}
-% \end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-10-12 Paper/Draft_harmonization_paper.tex
Backup draft

@@
 Explaining and predicting how communities are shaped by environmental factors is one of the main goals of ecology.
-Organismal traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, might be beneficial in achieving this goal \cite{heino_jani_macroecological_2013}.
-Traits evolve through adaptations (e.g., physiological, behavioral, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
-Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
-Traits of freshwater invertebrates are difficult to determine because, unlike plants, their traits often cannot be measured directly.
+Species traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, might be beneficial in achieving this goal \cite{heino_jani_macroecological_2013}.
+%?just traits
+Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
+% TODO: PUP: Not only „of an organism“, but also „of a population“ (at least for some of the traits related to reproduction; e.g. difficult to describe „voltinism“ as the organism scale!).
+Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than in taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
+Traits of freshwater invertebrate individuals are difficult to determine because - unlike plants - their traits often cannot be measured directly.
 For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community \cite{moog_comprehensive_nodate}. 
+% PUP says: But the trait-based approach can benefit from two centuries of detailed, published observations on biological traits and ecological preferences made by zoologists/ecologists on a large range of species in various environmental conditions.
 Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
 by relating macroinvertebrate trait composition to environmental factors or as trait metrics in biomonitoring \cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}.
-
-%%% Old Version:
-% Explaining and predicting how aquatic communities are shaped by environmental factors is one of the main goals of freshwater ecology.
-Organismal traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, are increasingly incorporated into freshwater ecology to support this goal, e.g.
-by relating macroinvertebrate trait composition to environmental factors or as trait metrics in biomonitoring \cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}.
-Traits evolve through adaptations (e.g., physiological, behavioral, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
-% Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches may be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 For example, Bonada et al.
-\cite{bonada_taxonomic_2007} compared trait composition for mediterranean and temperate regions in Europe using traits from Usseglio-Polatera et al.
+\cite{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from Usseglio-Polatera et al.
 \cite{usseglio-polatera_biomonitoring_2000}, Poff et al.
@@
 
+% Sampled from a truncated normal distribution values for three traits
+% (upper and lower boundaries 0 and 1)
+% Traits were normalized so that they sum up to one
+% Three different taxonomic hierarchies were simulated: 
+% Simulated one family with 25 species 
+% -> 1) 5 Genera:  5 Species respectively
+% -> 2) 5 Genera: 1 Genus 13 Species (more than ~ 50 %); 4 Genera with 3 species
+% -> 3) 5 Genera: All have different amount of species
+
 % Simulation result: 

### 2020-10-16 Paper/Draft_harmonization_paper.tex
16.10: Paper Update, first implm. of Co-Authors

@@
 \usepackage{hhline}
+\usepackage{lmodern}
 \usepackage[
@@
 Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 % TODO: PUP: Not only „of an organism“, but also „of a population“ (at least for some of the traits related to reproduction; e.g. difficult to describe „voltinism“ as the organism scale!).
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than in taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
@@
 For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community \cite{moog_comprehensive_nodate}. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 % PUP says: But the trait-based approach can benefit from two centuries of detailed, published observations on biological traits and ecological preferences made by zoologists/ecologists on a large range of species in various environmental conditions.
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
@@
 
-In the last decades, freshwater ecologists developed comprehensive invertebrate trait databases for various biogeographic regions \cite{usseglio-polatera_biomonitoring_2000, schmidt-kloiber_www.freshwaterecology.info_2015, vieira_database_nodate, Philips_and_Smith_NZ_DB_2018, kefford_integrated_2020, tomanova_trophic_2006}.
-The availability of invertebrate trait data from different biogeographic regions enables comparisons of trait variation and their relation to environmental factors across large scales.
-However, such analyses have been carried out mostly within biogeographic regions, using information from one or two trait databases.
+In the last decades, freshwater ecologists developed comprehensive invertebrate trait databases for various continents \cite{usseglio-polatera_biomonitoring_2000, schmidt-kloiber_www.freshwaterecology.info_2015, vieira_database_nodate, Philips_and_Smith_NZ_DB_2018, kefford_integrated_2020, tomanova_trophic_2006}.
+The availability of invertebrate trait data from different continents enables comparisons of trait variation and their relation to environmental factors across large scales.
+However, such analyses have been carried out mostly within continents, using information from one or two trait databases.
 For example, Bonada et al.
-\cite{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from Usseglio-Polatera et al.
-\cite{usseglio-polatera_biomonitoring_2000}, Poff et al.
+\cite{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from the Tachet database \cite{usseglio-polatera_biomonitoring_2000}, Poff et al.
 \cite{poff_developing_2010} characterized trait composition across sites in the Western US using traits from Poff et al.
@@
 \cite{schafer_trait_2011}.
-% ? Include Saito for South America 
-Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different biogeographic regions are rare.
-A grouping feature is defined by Schmera et al.
-as a general property (e.g.
+Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different continents are rare.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% biogeographic regions substituted with continents
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PUP & ASK: So „grouping features“ are „traits“ (in most of the published databases) described by „traits“ (i.e. several „related categories“). 
+% I agree that these definitions have to be made more clear, i.e.
+that you are using the term „grouping feature“ for what most published articles call “traits” and that what others call “categories” (within the traits) are your “traits”.
+Maybe add a “definition” of terms at the beginning ...also your use of “affinity” needs to be included there…
+% Put into definitons of terms?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this study, we follow the terminology proposed by Schmera et al., where a grouping feature is defined as a general property (e.g.
 feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species" \cite{schmera_proposed_2015}.
+Thus, we use the term grouping feature in place of which many studies use the term "trait", and the term trait instead of "trait state", "modality" or "trait category".
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% TODO: Description of affinity
+% A trait can described using a binary coding (exists or not), or using affinity scores that indicate the which extent an organism expresses a certain trait.  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 To our knowledge, only Brown et al.
@@
 
-We suspect that the heterogeneity of information in freshwater invertebrate trait databases is likely a major reason for the lack of studies across biogeographic regions.
+We suspect that the heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents.
 To harmonize grouping features from different regions, first commonly accepted and unambiguous trait definitions are required \cite{schneider_towards_2019}.
 In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonized using standardized terminology.
-However, a lack of standardized terminology of trait definitions and poor metadata quality in many trait databases is a common issue throughout the field of trait-based ecology \cite{baird_toward_2011, schneider_towards_2019}.
+However, a lack of standardized terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology \cite{baird_toward_2011, schneider_towards_2019}.
 Secondly, consistent coding of traits facilitates the compatibility of trait data from different databases.
-Traits can be binary (i.e.
-trait exists or not), continuous, or fuzzy coded variables.
-Fuzzy codes represent the affinity of an organism to express a certain trait.
-They are used to account for plasticity in traits and are usually converted to percentages.
-Continuous values are typically used for grouping features that can be measured, like body size.
-However, invertebrate trait databases are heterogeneous with regard to the coding they use for their traits \cite{culp_incorporating_2011} (Table \ref{tab:trait_databases_coding_differentiation}).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% BK: I am not sure that the it is binary which is the defining issue, rather it is that there is no uncertainty.
+E.g.
+respiration type as more than two opitions but not undertainty into which a species fall into.
+% PUP: OK in your definition of „grouping features“ and „traits“, it is probably more the „trait description“ than the „trait“ (itself) which can be „binary“.
+% ASK to Voltinism: I think this not an appropriate example for multiple categories except you include different regions for which different categories can apply; i.e.
+multivoltine in the temperate region and univoltine in the boreal region for the same species
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Alternative from Ben:
+Traits can be described in a binary fashion with no uncertainty how the trait is expressed in any particularly organism (e.g.
+adult terrestrial stage, presence of gills), continuous (e.g.
+tolerance of pollution, body size) or using multiple descriptions (e.g.
+locomotion) with some uncertainty as to which trait the organism should be coded to.
+One approach for dealing with the uncertainty in the latter is the use of fuzzy coded variables.
+Fuzzy codes are used to account for plasticity in traits, variability in traits within taxonomic groups above species, and incomplete knowledge and are usually converted to proportions.
+
+However, invertebrate trait databases are heterogeneous regarding the coding they use for their traits \cite{culp_incorporating_2011} 
+%(Table \ref{tab:trait_databases_coding_differentiation}).
+% TODO: Don't use table 5 and maybe find another reference?
 Brown et al.
 \cite{brown_functional_2018} harmonized grouping features based on trait databases from Europe, North America, and New Zealand because in these trait databases identical grouping features are classified differently into traits.
-As the traits from North America were coded binary in contrast to the fuzzy coded traits from Europe and New Zealand, the authors consulted experts to assign fuzzy coded traits to North American taxa or inferred them from the European trait database.
+As the traits from North America were coded binary in contrast to the traits from Europe and New Zealand which have been established using affinity scores, the authors consulted experts to assign fuzzy coded traits to North American taxa or inferred them from the European trait database.
 Thus, it becomes apparent that using invertebrate trait data from several regions requires extensive data processing prior to the actual data analysis.
 A centralized database with standardized and unambiguous traits and a consistent coding of traits would minimize data processing effort.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PUP: Taking into account your definition of traits (= „trait categories“ or „trait modalities“ in Tachet et al., 2010) and grouping features (= „traits“ in Tachet et al., 2010), the fuzzy coding approach is not applied to the „trait“ scale, but to the „grouping feature“ scale.
+At the „trait“ scale, „only“ an affinity score is allocated to a given taxon.
+The binary/quantitative character of this score is probably not the only important criterion to consider.
+One of the major characteristics of the fuzzy coding approach is, at the „grouping feature“ scale, to allow several „traits“ to be simultaneously present (possibly with different affinity scores) in a given „grouping feature“ for a given taxon (i.e.
+a non-disjunctive approach).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Differing taxonomic resolutions between the observed taxa in a study and the used trait database is another challenge when working with trait data.
-When observations are on a lower taxonomic level than data available in the trait databases (e.g.
-observations on species-level, trait data on genus-level) trait data of the higher taxonomic level are often assigned, e.g.
-\cite{szocs_effects_2014, vos_taxonomic_2017}.
-Conversely, if trait information is only available on lower taxonomic levels than the observed taxa, traits are aggregated to a higher taxonomic level, e.g.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ASK: this is something that should not appear in the introduction, at least not in such detail…
+% ASK: I would suggest not to use “higher/lower” as this is used in different ways in different publications (low can mean low (i.e.
+imprecise) identification level, but it also can mean low in terms of systematic hierarchy, which then would mean more precise id level…); I would suggest to use terms like precise/imprecise, accurate or the like…
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Differing taxonomic resolutions (e.g.
+species, genus or family) between the observed taxa in a study and the used trait database is another challenge when working with trait data.
+When observations are on a more precise taxonomic level than data available in the trait databases (e.g.
+observations on species-level, trait data on genus-level) trait information of the less precise taxonomic level is often assigned (e.g.
+\cite{szocs_effects_2014, vos_taxonomic_2017}).
+Conversely, if trait information is only available on more precise taxonomic levels than the observed taxa, traits are aggregated to a less precise taxonomic level, e.g.
 \cite{poff_functional_2006, szocs_effects_2014, piliere_a._f._h._importance_2016, aspin_extreme_2019}.
-Thereby, trait aggregation is often done using the mean \cite{magliozzi_functional_2019}, median \cite{szocs_effects_2014} or the mode \cite{piliere_a._f._h._importance_2016}.
+Thereby, trait aggregation is often done using the mean \cite{magliozzi_functional_2019},
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PUP: Sometimes weighted by the rarity/commonality of individual taxa (e.g.
+genera) at large spatial scale (e.g.
+ecoregions), within the higher level taxonomic unit (e.g.
+family), because the probability of the commonest taxa to be present in a given sample is higher (at large spatial scale).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+median \cite{szocs_effects_2014} or the mode \cite{piliere_a._f._h._importance_2016}.
 Up to now, studies on how and to which extent different trait aggregation methods influence trait-based analysis are missing.
@@
 
-We analyzed the influence of grouping feature harmonization and trait aggregation on trait-environment relationships. 
-Therefore, we (1) harmonized four invertebrate grouping feature datasets for seven grouping features based on information from trait databases of the regions Europe, North America, New Zealand, and Australia.
-Furthermore, we (2) compare trait affinities obtained through different trait aggregation methods to trait affinities assigned at family-level by experts.
-We (3) re-analyze data on the effect of anthropogenic salinization on biological traits by Szöcs et al.
+We aimed to determine the influence of grouping feature harmonization and trait aggregation on trait-environment relationships.
+In particular, we aimed to (1) determine the effect of different harmonization methods using 4 invertebrate grouping feature datasets for seven grouping features from Europe, North America, New Zealand, and Australia.
+Furthermore, we (2) compared trait affinities obtained through different trait aggregation methods to trait affinities assigned at family-level by experts.
+We (3) re-analysed data on the effect of anthropogenic salinisation on biological traits by Szöcs et al.
 \cite{szocs_effects_2014} using harmonized grouping features and aggregated traits.
-By comparison with the original analysis, we investigate how harmonizing and aggregating trait data can alter the outcome of trait-environment relationships.
+By comparison with the original analysis, we investigated how harmonizing and aggregating trait data can modify the outcome of trait-environment relationships.
 Finally, we (4) present an overview of discrepancies in trait definition between the used invertebrate trait datasets and discuss challenges of trait data synthesis.
@@
 We extracted information from 6 trait databases from Europe, North America, Australia, and New Zealand and harmonized 7 grouping features.
-Trait information for Europe was obtained from the Freshwaterecology database \cite{schmidt-kloiber_www.freshwaterecology.info_2015} and complemented by Tachet \cite{usseglio-polatera_biomonitoring_2000} to fill missing information (e.g.
-for size).
-% TODO: mention that tachet and freshwaterecology are not seperate (but we did it separately)
+Trait information for Europe was obtained from the freshwaterecology.info database \cite{schmidt-kloiber_www.freshwaterecology.info_2015} and the Tachet database \cite{usseglio-polatera_biomonitoring_2000}.
+The freshwaterecology.info contains taxa on species-level, while taxa recorded in the Tachet database are on species, genus and family-level.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% freshwater.info requested from ASK
+% Slightly changed - Comment from ASK: this is rather confusing at this stage as most of the assignments in freshwaterecology.info (fwe) are on species level whereas Tachet et al.
+have mostly genus and family level data in their database
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Trait information for North America was obtained from Twardochleb et al.
@@
 \cite{kefford_integrated_2020} and Philips and Smith respectively \cite{Philips_and_Smith_NZ_DB_2018}.
+To increase readability we refer to the databases as well as the datasets we extracted from them by the name of the continent they originate from.
+Excluded from this are the European databases, which we refer to by their commonly used names (freshwaterecology.info and Tachet database).
+% Eingefügt da die Bennung uneinheitlich im Manuskript war, auch von den Co-Autoren kritisiert wurde
 
-We selected traits of seven grouping features that were available in all databases, are commonly used, and describe different parts of the biology of an organism: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
+We selected traits of seven grouping features that were available in all databases, are commonly used, and describe different parts of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
 We omitted ecological traits that describe habitat preferences (e.g.
@@
 crawlers and sprawlers into crawlers).
-Thereby, the highest trait affinity among the amalgamated traits was taken.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Does it mean that the relative frequency of „non-amalgamated“ traits could be modified in the „grouping feature“ profiles of taxa?
+(because the highest score could be lower than the sum of the affinity scores of the amalgamated traits)
+Thereby, for a particular taxa the highest trait affinity score among the amalgamated traits was taken.
 
-We used fuzzy coded traits for establishing our harmonized datasets unless data quality prohibited and then we used binary traits, i.e.
+We used fuzzy coded traits for establishing our harmonized datasets unless data quality prohibited.
+In the latter case we used binary traits, i.e.
 categorical and continuous traits were converted into binary traits.
+For example, in the  freshwaterecology.info database taxa were classified according to different floristic regions for the trait voltinism.
+Hence, the entries of the voltinism traits such as "arctic" or "boreal" were substituted with a value of 1.
 Implicitly, we assumed for binary traits that a value of 1 corresponds to the highest affinity for a particular trait and 0 to no affinity for a particular trait.
 Fuzzy codes are reported with different ranges in the trait databases (e.g.
-freshwaterecology 0 to 10, Tachet 0 to 3 or 0 to 5).
+freshwaterecology.info 0 to 10, Tachet database 0 to 3 or 0 to 5).
 We standardized them to a range between 0 and 1 and converted trait affinities to percentages.
@@
 
-Prior harmonization we amalgamated duplicate taxa on species, genus or family-level if present. We omitted taxa with a lower taxonomic resolution than family-level.
+Prior to harmonization we consolidated duplicate taxa on species, genus or family-level if present, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
+We omitted taxa with a less precise taxonomic resolution than family-level.
 
@@
 \midrule
-Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, round (humped)\\ Flattend, dorsoventrally flattened\\ Spherical, tubular\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
+Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattend, dorsoventrally flattened \textsuperscript{\textit{a}}\\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
 \midrule
-Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm, \textless 10 mm\\ 9 - 16 mm, 10 - 20 mm\\ \textgreater 16 mm, \textgreater 20 mm\end{tabular}                                                                                                                \\
+Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm, \textless 10 mm \textsuperscript{\textit{b}}\\ 9 - 16 mm, 10 - 20 mm\\ \textgreater 16 mm, \textgreater 20 mm\end{tabular}                                                                                                                \\
 \midrule
@@
 \midrule
-Feeding mode & \begin{tabular}[c]{@{}l@{}}Filterer\\ \\ Gatherer\\ \\ Herbivore\\ \\ Parasite\\ Predator\\ Shredder \\ \\ \end{tabular} & \begin{tabular}[c]{@{}l@{}}Active/passive filterer, absorber, \\ filter-feeder, collector-filterer, filterer\\ Deposit-feeder, collector-gatherer, \\ detrivore, gatherer\\ Grazer, scraper, piercer herbivore, \\ herbivore, algal piercer, piercer (plants)\textsuperscript{\textit{a}}\\ \\ Piercer (animals)\textsuperscript{\textit{a}}, predator \\ Miner, xylophagus, shredder, \\ shredder detrivore\end{tabular} \\
+Feeding mode & \begin{tabular}[c]{@{}l@{}}Filterer\\ \\ Gatherer\\ \\ Herbivore\\ \\ Parasite\\ Predator\\ Shredder \\ \\ \end{tabular} & \begin{tabular}[c]{@{}l@{}}Active/passive filterer, absorber, \\ filter-feeder, collector-filterer, filterer\\ Deposit-feeder, collector-gatherer, \\ detrivore, gatherer\\ Grazer, scraper, piercer herbivore, \\ herbivore, algal piercer, piercer (plants)\textsuperscript{\textit{c}}\\ \\ Piercer (animals)\textsuperscript{\textit{c}}, predator \\ Miner, xylophagus, shredder, \\ shredder detrivore\end{tabular} \\
 \hline
@@
 \end{table}
-\begin{minipage}{\linewidth}\small
-    \textit{a} The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases \cite{usseglio-polatera_biomonitoring_2000}.
+\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
+    \textit{a} The trait "bluff (blocky)" occurred in the Vieira et al.
+\cite{vieira_database_nodate} database and was newly classified by expert knowledge into cylindrical and flattened \cite{polatera_personal_information_2020}.
+\\
+    \textit{b} Reflects the different size classifications by the North American trait databases and the other trait databases. \\
+    \textit{c} The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases \cite{usseglio-polatera_biomonitoring_2000}.
 Taxa exhibiting this trait have been assigned to predators or herbivores based on expert knowledge \cite{polatera_personal_information_piercer_2020}.
+}
 \end{minipage}
@@
 Traits of the harmonized grouping feature datasets were aggregated to family-level using three approaches.
-I) direct aggregation of taxa to family-level giving equal weight to every species using the mean or median, denoted \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively.
-II) stepwise aggregation, i.e.
+I) Direct aggregation of taxa to family-level giving equal weight to every taxon using the mean or median, denoted \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively.
+II) Stepwise aggregation, i.e.
 first to the genus-level and subsequently to the family-level using the mean or median.
@@
 Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{mean}} or \textit{stepwise\_agg\textsubscript{median}}, respectively.
-III) aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
-This method weights the genera according to the number of their species in the databases.
+III) Aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
+This method weights the genera according to the number of their species in the trait datasets regardless if for every used grouping feature information was available.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PUP: Is it the „potential number of species“ (i.e.
+the number of species potentially present at the selected spatial scale) or the number of species with traits/grouping features described?
+The grouping feature information can be available for a different set of species from a grouping feature to another.
+Does it mean that genus weights can be different in the aggregated family profile according to the information available on traits (regardless of the actual number of species in these different genera?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The dashed bottom box illustrates the different trait aggregation methods using a small made-up example (data in the upper left corner).
-Displayed are the aggregation methods (blue) and intermediate steps of the aggregation methods (purple).
-For the stepwise and weighted aggregation only results for one trait are displayed.}
+The aggregation methods (blue) and intermediate steps of the aggregation methods (purple) are displayed.
+Abbreviations: EU: Europe, NOA: North America, AUS: Australia, NZ: New Zealand, DB: Database.}
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PUP: 
+% Difficult to understand, with your example, what has been done based on your description of the calculation.
+% If you have allocated a weight of „3“ to each species of G1 (as indicated in your detailed calculation; i.e.
+0,25*3 + 0.5*3 + ...), the final contribution of G1 will be nine times greater than that of a genus only described by a single species (not really consistent).
+
+% In my opinion (and taking into account your rationale when defining the other strategies), it would have been more coherent to allocate (i) a weight of „3“ to the mean score of G1 (because 3 species from this genus), (ii) a weight of „2“ (not „1“) to the mean score of G2 (because two descriptions : sp4 and genus sp.
+or spp.
+...
+even if we can question the relevance of averaging information that is at least partially redundant) and a weight of „1“ to the family score (idem, this information is at least partially redundant with the information provided by genera G1 and G2).
+
+% Response: Weight of 2 is thinkable! However, disagree with PUP because what he proposes is basically the direct aggregation using the mean. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\subsection*{Comparison of aggregated traits with traits assigned by experts}
+\subsection*{Comparison of family-level aggregated traits with family-level assigned traits}
 
-Aggregated trait affinities of the five trait aggregation methods (\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg}) were compared to trait affinities assigned at family-level by experts, which were available for the Australian and North American database for a subset of grouping features and taxa.
-For the Australian database, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman \cite{chessman_dissolved-oxygen_2018}.
-In Chessman \cite{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the harmonized Australian database except that the trait parasite is missing.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ASK: I would change the heading; basically it is comparing family-level-aggregated traits to family-level assigned traits… both, the formerly species-level traits as well as the family-level traits were assigned by experts….
+the point are not the experts but the level of assignment…
+
+% btw. did you try to compare this on genus level as well, e.g. the aggregated genus-level traits from fwe to the assigned genus-level traits from f et al.; this would be highly interesting!
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Aggregated trait affinities of the five trait aggregation methods (\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg}) were compared to trait affinities assigned at family-level by experts, which were available for Australia and North America for a subset of grouping features and taxa.
+For the Australian dataset, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman \cite{chessman_dissolved-oxygen_2018}.
+In Chessman \cite{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the Australian dataset except that the trait parasite is missing.
 We conducted the comparison for the 220 families available in Chessman \cite{chessman_dissolved-oxygen_2018}.
@@
 
-For the North American database, we compared aggregated trait affinities with assigned trait affinities on family-level for the grouping features feeding mode, respiration, size, voltinism, and locomotion.
-The assigned trait affinities at family-level are part of the North American database (\cite{twardochleb_trait_data_2020}) and originate from expert knowledge.
-Trait information was available for 94 families of which all were present in the aggregated North American database (total number of cases 1598).
+For the North American dataset, we compared aggregated trait affinities with assigned trait affinities on family-level for the grouping features feeding mode, respiration, size, voltinism, and locomotion.
+The assigned trait affinities at family-level are part of the North American database (Twardochleb) \cite{twardochleb_trait_data_2020}) and originate from expert knowledge.
+Trait information was available for 94 families of which all were present in the North American dataset (total number of cases 1598).
 The traits were on the categorical scale and were converted to binary traits prior to the comparison with aggregated trait affinities.
@@
 
-We repeated the analysis in Szöcs et al.
+We repeated the analysis of Szöcs et al.
 \cite{szocs_effects_2014} who studied the effect of anthropogenic salinization on invertebrates in the River Werra in Germany.
-As a case study, we used for the re-analysis the established harmonized grouping features for Europe and additionally aggregated traits using the aforementioned aggregation methods.
+For the re-analysis we used the established harmonized grouping features for Europe and additionally aggregated traits using the aforementioned aggregation methods.
 
-The river has been subject to effluents from the potash industry since the mid of the 20th century and allows to study responses of invertebrates and their trait compositions to salinization.
-Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition.
-Further details can be found in Szöcs et al.
-\cite{szocs_effects_2014}.
-We compared the species scores obtained from redundancy analysis (RDA) for traits constrained by electric conductivity from the original study to species scores when including harmonized grouping features.
-We used the same grouping features that Szöcs et al.
-\cite{szocs_effects_2014} used, but 6 of them have been harmonized from the European harmonized grouping feature dataset for our analysis.
-The harmonized grouping features used were \textit{Size, Feeding mode, Locomotion, Oviposition, Respiration}, and \textit{Voltinism}.
-Traits of those grouping features responded strongly to salinity in the study of \cite{szocs_effects_2014}.
+The river Werra has been subject to effluents from the potash industry since the mid of the 20th century and allows to study responses of invertebrates and their trait compositions to salinization \cite{bathe_biological_2011}.
+% BK : Want to add some general refs about salinization and salinization on this river. 
+Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition. Further details can be found in Szöcs et al. \cite{szocs_effects_2014}.
+
+We substituted 6 of the grouping features from the original data with harmonized grouping features from the European trait dataset.
+We compared the results of the redundancy analysis (RDA) from the original study to the case when using harmonized grouping features.
+Specifically, the trait composition expressed as community weighted mean (CWM) traits was ordinated along an electric conductivity gradient.
+We compared the species scores obtained from the RDA, i.e.
+the coordinates of the tips of the vectors representing the CWM traits in the bi- or triplots.
+For our analysis, we used the same 21 grouping features that Szöcs et al.
+\cite{szocs_effects_2014} used.
+The 6 harmonized grouping features used were \textit{Size, Feeding mode, Locomotion, Oviposition, Respiration}, and \textit{Voltinism}.
+%Traits of those grouping features responded strongly to salinity in the study of \cite{szocs_effects_2014}.
 Additionally, for testing the effect of aggregated traits we assigned to each taxon in Szöcs et al.
@@
 
-The data processing and aforementioned analysis were carried out using R (Version 3.6.1).
+The data processing and aforementioned analysis were carried out using R (Version 3.6.1 and 4.0.3).
 Raw data and the R code for data processing and grouping feature harmonization is located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
@@
 
-% Influence of aggregation methods on trait-environment relationships:
-% 1) In general, differences produced by the aggregation methods seem to arise by using mean or median, 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 1) Trait aggr methods vs assigned traits:
+% - BK:
+%  All range from about 0 to 1 and all have mean values which fall within the error bars (stand dev) of the other methods. 
+% Figure 3, however, does suggest some differences in terms of range, with the methods which use median have narrow ranges.
+In terms of mean values perhaps more difference than for the Australian analysis but even still considering the +/- the error bars I think they all overlap.
+% It then becomes what to make of all this. Are the slight differences between the methods important or unimportant?
+% Also why the differences between the Australian and NA datasets?
+
+% 2) Influence of aggregation methods on trait-environment relationships:
+% - In general, differences produced by the aggregation methods seem to arise by using mean or median, 
 % not driven by different weighting approaches (direct vs. stepwise vs. weighted) 
@@
 % We used only a small-scale study -> What's different to large-scale studies?
-
 % Further aggr. after harmonization: no difference to the harmonized dataset
 % ?Logical because trait aggr. methods themselves showed only minor differences
+% Complex Stat. techniques developed -> cannot use full potential
 
-% Complex Stat. techniques developed -> cannot use full potential
+% Suggestions from Co-Authors:
+% should include where the classifications come from
+% what do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge?
+% are the differences between continents because of evolution or only because scientists have done more research in one of the continents?
 

### 2020-10-16 Paper/Results/Results_trait_harmonization.tex
05.09.2020: Minor edits SI
16.10: Paper Update, first implm. of Co-Authors

@@
 
-\subsection*{Re-analysis of Szöcs et al. 2014 using harmonized and aggregated grouping features}
+\subsection*{Re-analysis of Szöcs et al. using harmonized and aggregated grouping features}
 
-Overall, using the harmonized grouping features lead only to slightly different results in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and SI).
-According to the RDA of the trait composition sites with high salinity were characterized by multivoltine, ovivoparous, gill-respirating, and shredder species.
-Only species with the trait life cycle duration $> 1$ year fail to characterize sites with high salinization.
-Also, life cycle duration $<= 1$ year is not anymore characterizing sites not impacted by salinity.
-Like in the original analysis, transition and upstream sites from the point source are characterized by univoltine species and species that lay their eggs in an aquatic environment.
-We constructed also the linear models of the original analyses, using the traits on the extremes of the conductivity axis and found results similar to the original analysis (Table S\ref{stab:linear_models_new} and S\ref{stab:linear_models_edi}).
+Overall, using the harmonized grouping features led to only slightly different results in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and SI).
+According to the RDA of the trait composition, sites with high salinity were characterized by families that possess the traits multivoltinism, ovoviviparity, gill-respiration, and feeding mode shredder.
+Only families with the trait life cycle duration $> 1$ year failed to characterize sites with high salinization.
+Also, life cycle duration $<= 1$ year did not characterise sites not impacted by salinity.
+Like in the original analysis, transition and upstream sites from the point source were characterised by univoltine taxa and taxa that lay their eggs in aquatic environments.
+We also constructed the linear models of the original analyses, using the traits on the extremes of the conductivity axis and found results similar to the original analyses (Table S\ref{stab:linear_models_new} and S\ref{stab:linear_models_edi}).
 
 For every aggregation method compared, using at family-level aggregated traits did only slightly change the species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}). 
-Hence, the interpretation of the trait composition is the same as when only using harmonized grouping features.
-
-% Mention that threshold according to mahalanobis distance is almost reached for life cycle duration
+% Hence, the interpretation of the trait composition is the same as when only using harmonized grouping features. 
+%? Mention that threshold according to mahalanobis distance is almost reached for life cycle duration
 
@@
 
+% PUP comment: 
+% What are exactly „RDA species scores“? The coordinates of species along the first factorial axis in RDA?
+% If „yes“, I’m not sure this result presentation is suitable.
+In fact the box-plots summarizing the distributions of the set of species in the RDA analysis, after applying different strategies of trait description, can be very similar (it’s not surprising, because in each case the mean coordinate of species is 0), but the individual locations of species along each axis can be very different from an RDA to another axis (i.e.
+from a grouping feature definition strategy to another).
+It would be probably far more interesting to represent the distribution of deviations between the RDA scores provided by each strategy and the original RDA scores (from Szöcs et al., 2018)..
+
 \end{document}

### 2020-10-16 Paper/Results/SI.tex
16.10: Paper Update, first implm. of Co-Authors

@@
 Boxplot of site scores along the conductivity axis ($31.44 \%$ explained variance, p = 0.001, 1000 permutations).
-Rug on the left indicates trait scores on the conductivity axis.
+Rug on the right indicates trait scores on the conductivity axis.
 Only traits with a mahalanobis distance greater than 5.02 were labeled in accordance to the procedure in Szöcs et al.
@@
 Boxplot of site scores along the conductivity axis ($30.09 \%$ explained variance, p = 0.001, 1000 permutations).
-Rug on the left indicates trait scores on the conductivity axis.
+Rug on the right indicates trait scores on the conductivity axis.
 Only traits with a mahalanobis distance greater than 5.02 were labeled.
@@
 \subsubsection*{Trait distribution along first RDA axis}
+
+% ASK: 
+% - there seems to be some overlap of text on the top left
+% - Why mention life cylce duration separately?
 \begin{figure}[H]
@@
 \begin{landscape}
-    \begin{longtable}{m{1.7cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}}
+    \begin{longtable}{m{1.8cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}}
         \caption{Comparison of trait definitions between invertebrate trait databases.
@@
         \toprule[.1em]
-        Trait & Freshwaterecology & Tachet & \specialcell{North America \\ (Twardochleb)} & 
+        Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & \specialcell{North America \\ (Twardochleb)} & 
         North America (Vieira) & Australia & New Zealand \\
@@
         Multivoltine & 
-        "More than \textit{three} generations per year" \textsuperscript{\textit{b}}& 
+        "\textit{Three} or more generations per year" \textsuperscript{\textit{b}}& 
         "Able to complete \textit{at least} two successive generations per year" &

### 2020-10-16 Paper/Results/Taxonomic_cov_and_info_compl.tex
16.10: Paper Update, first implm. of Co-Authors

@@
 Regarding the taxonomical coverage, the New Zealand dataset has, as expected, the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
-By contrast, the largest taxon pool is spanned by the European trait dataset with 4110 taxa followed by the North American trait dataset that contained trait information on 3753 taxa.
+By contrast, the largest taxon pool is spanned by the European trait dataset with 4496 taxa followed by the North American trait dataset that contained trait information on 3753 taxa.
 The Australian dataset contains 1402 taxa.
-The European, New Zealand, and North American datasets have most taxa on the highest taxonomical resolution while the Australian dataset has a similar number of taxa on species and genus-level.
+The European, New Zealand, and North American datasets have most taxa on the species-level while the Australian dataset has a similar number of taxa on species and genus-level.
 
@@
     \centering
-    \caption{Number of taxa per harmonized database and per taxonomic level. Numbers in parenthesis show relative frequencies in percentage.}
+    \caption{Number of taxa per harmonized dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percentage.} 
     \label{tab:tax_coverage}
@@
     \toprule[.1em]
-    Database & Nr. of taxa & Species & Genus & Family & Nr. aquatic taxa \\ 
+    Database & Nr. of taxa & Species & Genus & Family & Nr. aquatic insects \\ 
     \toprule[.1em]
-    EU & 4110 & 3848 (93.63) & 237 (5.77) & 25 (0.61) & 3579 (87.08) \\ 
-    NOA & 3753 & 2414 (64.32) & 1163 (30.99) & 176 (4.69) & 3305 (88.06) \\ 
-    AUS & 1402 & 564 (40.23) & 578 (41.23) & 260 (18.54) & 1016 (72.47) \\ 
-    NZ & 478 & 404 (84.52) & 47 (9.83) & 27 (5.65) & 443 (92.68) \\ 
+    EU & 4496 & 3691 (82) & 647 (14) & 158 (4) & 3838 (85) \\ 
+    NOA & 3753 & 2414 (64) & 1163 (31) & 176 (5) & 3305 (88) \\ 
+    AUS & 1402 & 564 (40) & 578 (41) & 260 (19) & 1016 (72) \\ 
+    NZ & 478 & 404 (85) & 47 (10) & 27 (6) & 443 (93) \\ 
     \bottomrule
@@
 
-The amount of entries with available information for the selected grouping features varied strongly for the European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
+The amount of entries with available information for the selected grouping features varied strongly for the preprocessed European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
 By contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
@@
     \centering
-    \caption{Displayed is the percentage of entries that have information for the individual grouping features per dataset.} 
+    \caption{Rounded percentage of entries that have 
+    information for the individual grouping features
+    shown per trait dataset.}
     \label{tab:trait_coverage}
-    \begin{tabular}{llllllll}
+    \begin{tabular}{lccccccc}
     \toprule[.1em]
@@
     \toprule[.1em]
-    EU & 7 & 16 & 24 & 33 & 11 & 56 & 65 \\ 
+    EU & 8 & 15 & 21 & 36 & 10 & 49 & 75 \\ 
     NOA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
-    AUS & 5 & 48 & 51 & 42 & 78 & 70 & 99 \\ 
+    AUS & 4 & 46 & 49 & 39 & 75 & 68 & 99 \\ 
     NZ & 100 & 94 & 100 & 99 & 100 & 100 & 99 \\ 

### 2020-10-16 Paper/Trait_def_table/Trait_definitions_table.tex
16.10: Paper Update, first implm. of Co-Authors

@@
 
-Definitions of grouping features and traits varied in their level of detail.
-The Freshwaterecology database, and databases from Tachet and Twardochleb et al.
-provided more detailed descriptions of their trait information compared to the databases from Vieira et al.
-and New Zealand.
-An exception is the Australian trait database which is a collection of seven trait datasets \cite{kefford_integrated_2020}.
+Definitions of grouping features and traits varied in their level of detail in the original trait databases.
+The freshwaterecology.info database, the Tachet database and the North American database (Twardochleb et al.) provided more detailed descriptions of their trait information compared to the North American (Vieira et al.) and New Zealand database.
+An exception is the Australian trait database which is a collection of seven specific trait datasets \cite{kefford_integrated_2020}.
 Thus, grouping features occur multiple times with varying differentiation into traits.
@@
 For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways.
-Tachet defines predators as carvers, engulfers and swallowers.
-By contrast, in the North American (Twardochleb) database predators are defined as engulfers and carnivorous piercers.
+The Tachet database defines predators as carvers, engulfers and swallowers.
+By contrast, in the North American (Twardochleb et al.) database predators are defined as engulfers and carnivorous piercers.
 In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers.
-Furthermore, the scope in the Freshwaterecology database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition.
-Therefore, the Freshwaterecology database defines e.g.
+Furthermore, the scope in the freshwaterecology.info database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition.
+Therefore, the freshwaterecology.info database defines e.g.
 predator as "eating from prey", while the other databases use the mouthpart morphology as basis of their definition.
@@
 Locomotion definitions differ also in scope between databases.
-Freshwaterecology and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation, the North American (Vieira) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb) database includes among the way of movement also the location of movement.
-Similarly, regarding reproduction trait databases differ in their scope.
-Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the Freshwaterecology and Tachet databases.
-North America (Vieira) provides information on the oviposition location but not on reproductive behavior.
+Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the North American (Vieira et al.) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb et al.) database includes not only the way of movement, but also the location of movement.
+Similarly, regarding the reproduction traits, databases differ in their scope.
+Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases.
+North America (Vieira et al.) provides information on the oviposition location but not on reproductive behavior.
 The Australian database report traits for reproductive behavior but also on oviposition site.
@@
 binary, fuzzy, continuous).
-The freshwaterecology and Australian use different codings in their databases.
-Tachet and the New Zealand database use exclusively fuzzy coding.
+The freshwaterecology.info and Australian use different codings in their databases.
+Tachet and the New Zealand database exclusively use fuzzy coding.
 Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
@@
 Continuous coding is used for traits like body size.
+% Last sentences are a bit redundant
 
@@
     \toprule[.1em]
-    \multirow{2}{*}[-5mm]{ \specialcell{Freshwater- \\ ecology}} & 
+    \multirow{2}{*}[-5mm]{ \specialcell{Freshwater- \\ ecology.info}} & 
     10 & 
@@
     \specialcell{10 point \\ assignment \\ system} &
-    \multicolumn{2}{c |}{\specialcell{presence/absence assignment \\ system}} &
+    \multicolumn{2}{c |}{\specialcell{binary}} &
     - & 

### 2020-10-16 R/02_EU_harmonize_new.R
16.10: Resp_tegument fix and add na.rm to harmonization

@@ -491,7 +491,7 @@ Trait_EU[
 # table(Trait_EU$resp_tap)
 # table(Trait_EU$resp_sur)
 # _________________________________________________________________________
-Trait_EU[, resp_tegument := apply(.SD, 1, max, na.rm = TRUE),
+Trait_EU[, resp_teg := apply(.SD, 1, max, na.rm = TRUE),
   .SDcols = c(
     "resp_tegument",
     "resp_tegument_tachet"
@@ -523,6 +523,7 @@ Trait_EU[, c(
   "resp_plastron",
   "resp_plastron_tachet",
   "resp_gill_tachet",
+  "resp_tegument",
   "resp_tegument_tachet"
 ) := NULL]
 
@@ -557,7 +558,7 @@ Trait_EU[, c(
 # rep_parasitic no entries
 # rep_asexual is deleted
 # _________________________________________________________________________
-Trait_EU[, ovip_aqu := apply(.SD, 1, max),
+Trait_EU[, ovip_aqu := apply(.SD, 1, max, na.rm = TRUE),
   .SDcols = c(
     "rep_egg_cem_iso",
     "rep_egg_free_iso",
@@ -571,14 +572,14 @@ Trait_EU[, ovip_aqu := apply(.SD, 1, max),
     "rep_clutch_veg_tachet"
   )
 ]
-Trait_EU[, ovip_ovo := apply(.SD, 1, max),
+Trait_EU[, ovip_ovo := apply(.SD, 1, max, na.rm = TRUE),
   .SDcols = c(
     "rep_parasitic",
     "rep_ovovivipar",
     "rep_ovovivipar_tachet"
   )
 ]
-Trait_EU[, ovip_ter := apply(.SD, 1, max),
+Trait_EU[, ovip_ter := apply(.SD, 1, max, na.rm = TRUE),
   .SDcols = c(
     "rep_clutch_ter",
     "rep_clutch_ter_tachet"
@@ -689,14 +690,14 @@ Trait_EU[Trait_subset,
 # size_medium: 9 mm < size > 16 mm (EU: 10 mm < size > 20 mm)
 # size_large: size > 16 mm (EU: size > 20 mm)
 # _________________________________________________________________________
-Trait_EU[, size_small := apply(.SD, 1, max),
+Trait_EU[, size_small := apply(.SD, 1, max, na.rm = TRUE),
   .SDcols = c(
     "size_&le; 0.25 cm_tachet",
[…]

### 2020-10-16 R/01_EU_preprocess_new.R
16.10: Corrected consolidation of duplicates

@@ -17,20 +17,22 @@ trait_EU <- trait_EU[, .SD,
 ]
 
 # Voltinism trait contains thermal conditions, change every string to 1
-col <- grep("^volt.*", names(trait_EU), value = TRUE)
+col <- grep("(?=volt.*)(?!.*tachet)", 
+  names(trait_EU), value = TRUE, perl = TRUE)
+
 trait_EU[, (col) := lapply(.SD, function(y) {
   ifelse(!is.na(y), 1, NA)
-}), .SDcols = names(trait_EU) %like% "^volt.*"]
+}), .SDcols = col]
 
 
 # get trait columns and transform all to numeric
-cols <- grep("order|family|genus|species|taxon.*",
+col <- grep("order|family|genus|species|taxon.*",
   names(trait_EU),
   value = TRUE,
   invert = TRUE
 )
-trait_EU[, (cols) := lapply(.SD, as.numeric),
-  .SDcols = !names(trait_EU) %like% "order|family|genus|species|taxon.*"
+trait_EU[, (col) := lapply(.SD, as.numeric),
+  .SDcols = col
 ]
 
 # select only taxa that have at least information for one trait
@@ -38,63 +40,97 @@ no_info <- trait_EU[, apply(.SD, 1, function(y) {
   is.na(y) %>%
     sum()
 }),
-.SDcols = cols
+.SDcols = col
 ]
-pos <- no_info == ncol(trait_EU[, ..cols])
+pos <- no_info == ncol(trait_EU[, ..col])
 trait_EU <- trait_EU[!pos, ]
 
-# aggr. duplicated species
+# __________________________________
+#### Consolidate duplicate taxa ####
+# __________________________________
+
+# binary columns -> aggr via max
+# fuzzy coded columns -> aggr via median
+cols_bin <- grep("(?=volt.*|resp.*)(?!.*tachet)",
+                 names(trait_EU),
+                 value = TRUE,
+                 perl = TRUE
+)  
+cols_fuzzy <- grep("(?=volt.*|resp.*|species|genus|family|order|taxon.*)(?!.*tachet)",
+                   names(trait_EU),
+                   value = TRUE,
+                   invert = TRUE,
+                   perl = TRUE
+)
+
+
+# - aggr. duplicated species:
 dupl_species <- trait_EU[!is.na(species), ] %>%
[…]

### 2020-10-16 R/03_NOA_harmonize_traits.R
16.10: Add assessment for taxa with locom & feeding mode other. Correction respiration temp. air store

@@ -8,6 +8,10 @@ Trait_Noa <- readRDS(file = file.path(data_cleaned,
                                       "North_America",
                                       "Traits_US_pp.rds"))
 
+# convert integer cols to double
+int_cols <- names(Filter(is.integer, Trait_Noa))
+Trait_Noa[, (int_cols) := lapply(.SD, as.double), .SDcols = int_cols]
+
 # _________________________________________________________________________
 #### Voltinism ####
 # volt_semi
@@ -125,7 +129,114 @@ Trait_Noa[detrivores,
 # omnivorous to predators?
 # mouthparts of shredders often suited for scavenging
 
+# Add from final preprocessed EU data
+Trait_EU <-
+  readRDS(file = file.path(data_cleaned, "EU", "Trait_freshecol_2020_pp_harmonized.rds"))
+taxa_other_feed_mode <-
+  Trait_Noa[`Feed_mode_prim_Other (specify in comments)` > 0,
+            .(Species,
+              Genus,
+              Family,
+              Order)]
+taxa_other_feed_mode[, taxa := coalesce(Species, Genus, Family, Order)]
+
+# 98 species with feed_mode other
+# of those 10 species are covered in EU DB
+# taxa_other_feed_mode[!is.na(Species), ]
+# Trait_EU[species %in% taxa_other_feed_mode[!is.na(Species), Species], ]
+Trait_Noa[Trait_EU[species %in% taxa_other_feed_mode$taxa,
+                   .(
+                     species,
+                     genus,
+                     family,
+                     order,
+                     feed_filter,
+                     feed_gatherer,
+                     feed_predator,
+                     feed_parasite,
+                     feed_shredder,
+                     feed_herbivore
+                   )],
+          `:=`(
+            feed_filter = i.feed_filter,
+            feed_gatherer = i.feed_gatherer,
+            feed_predator = i.feed_predator,
+            feed_parasite = i.feed_parasite,
+            feed_shredder = i.feed_shredder,
+            feed_herbivore = i.feed_herbivore,
+            `Feed_mode_prim_Other (specify in comments)` = 0
+          ),
+          on = c(Species = "species")]
+
+# create taxa column for Trait_Noa
+Trait_Noa[, Taxa := coalesce(Species, Genus, Family, Order)]
+
+# 58 taxa on genus-level with feed_mode other
+# Of these, 11 genera covered in EU data (data on genus level)
[…]

### 2020-10-16 R/05_NOA_NEW_harmonize_traits.R
16.10: Minor edits

@@ -139,10 +139,11 @@ Trait_Noa_new <- normalize_by_rowSum(
 # _________________________________________________________________________
 
 # Load harmoized & normalized Trait NOA
-Trait_Noa <- readRDS(file.path(data_cleaned, "North_America", "Traits_US_pp_harmonized.rds"))
-# Trait_Noa$order %>% table()
+Trait_Noa <-
+  readRDS(file.path(data_cleaned, "North_America", "Traits_US_pp_harmonized.rds"))
 
 # Subset to relevant orders
+# Trait_Noa$order %>% table()
 # Trait_Noa <- Trait_Noa[order %in% c(
 #   "Coleoptera",
 #   "Diptera",
@@ -302,26 +303,30 @@ name_vec <- grep("unique_id|order|family|genus|species",
 # % NA val before 
 # na_before <- sum(is.na(Trait_Noa_new))/(sum(is.na(Trait_Noa_new))+ sum(!is.na(Trait_Noa_new)))
 final <- Trait_Noa_new
-for(i in name_vec){
-  
+for (i in name_vec) {
   # check if for a certain grouping feature all the traits contain NA values
-  subset_vec <- !(rowSums(is.na(final[, .SD, .SDcols = names(final) %like% i])) == 0)
+  subset_vec <-
+    !(rowSums(is.na(final[, .SD, .SDcols = names(final) %like% i])) == 0)
   
   # subset to NA values
   # complemented with information from NOA old (if possible)
   # data need(!) to be normalized for this operation
-  step <- coalesce_join(x = final[subset_vec, ],
-                        y = Trait_Noa[!is.na(species), .SD,
-                                   .SDcols = names(Trait_Noa) %like% paste0(i, "|", "species")],
-                        by = "species",
-                        join = dplyr::left_join)
+  step <- coalesce_join(
+    x = final[subset_vec,],
+    y = Trait_Noa[!is.na(species), .SD,
+                  .SDcols = names(Trait_Noa) %like% paste0(i, "|", "species")],
+    by = "species",
+    join = dplyr::left_join
+  )
   setDT(step)
   # merge back to whole dataset
-  final <- coalesce_join(x = final,
-                         y = step[!is.na(species), 
-                                  .SD, .SDcols = names(step) %like% paste0(i, "|", "species")],
-                         by = "species",
-                         join = dplyr::left_join) 
+  final <- coalesce_join(
+    x = final,
[…]

### 2020-10-16 R/01_AUS_preprocessing.R
16.10: Minor edits

@@ -205,6 +205,9 @@ Trait_AUS[, `:=`(
   ovip_ovo_Schaefer = ifelse(grepl("(?i)ovo", Reproduction_type_Schaefer), 1, 0))]
 Trait_AUS[, Reproduction_type_Schaefer := NULL]
 
+# rm Changes_time_until_repro_bugs_gbr column
+Trait_AUS[, "Changes_time_until_repro_bugs_gbr" := NULL]
+
 # _________________________________________________________________________
 #### Feeding mode ####
 # feed_shredder: shredder (chewers, miners, xylophagus, herbivore piercers)
@@ -404,6 +407,14 @@ Trait_AUS[grepl("Mesostigmata", Family), `:=`(
 # Family NULL?
 Trait_AUS[grepl("NULL", Family), Family := NA]
 
+# "Naididae", "Hydrobiidae", "Hydridae" assigned to different orders
+Trait_AUS[Family == "Naididae", Order := "Haplotaxida"]
+Trait_AUS[Family == "Hydrobiidae", Order := "Littorinimorpha"]
+Trait_AUS[Family == "Hydridae", Order := "Anthoathecata"]
+
+# Temnocephalidae
+Trait_AUS[Family == "Temnocephalidae", Order := "Rhabdocoela"]
+
 # one entry without genus and family information
 Trait_AUS[Species == "Cheumatopsyche deani", 
           `:=`(Genus = "Cheumatopsyche",
@@ -475,8 +486,8 @@ for(i in trait_author_pattern) {
 }
 
 # back to wide format
-Trait_AUS <- data.table::dcast(Trait_AUS, 
-                               unique_ID+Species+Genus+Family+Order ~ variable)
+Trait_AUS <- data.table::dcast(Trait_AUS,
+                               unique_ID + Species + Genus + Family + Order ~ variable)
 
 # change column names from Chessman that contain word "genus"
 setnames(
@@ -511,14 +522,9 @@ cols <- grep("(?i)unique_id|species|genus|family|order",
 #    .[, .(diff(value)), by = c("Genus", "variable")] %>%
 #    .[V1 != 0, ]
 
-# For cases where duplicate taxa entries differ for a trait by
-# 0 and 1 (or 0 and any other number) the maximum value is taken
-# since data originate from seven different databases (i.e. data 
-# complement each other).
-# This procedure is different compared to the amalgamation of duplicates
[…]

### 2020-10-16 R/01_NZ_preprocessing.R

@@ -260,7 +260,7 @@ cols <- grep("(?i)unique_id|species|genus|family|order|class|phylum",
              invert = TRUE)
 
 Trait_NZ[is.na(Species) & is.na(Genus) & !is.na(Family),
-         (cols) := lapply(.SD, mean), .SDcols = cols]
+         (cols) := lapply(.SD, median), .SDcols = cols]
 
 # rm duplicated families
 ids <- Trait_NZ[is.na(Species) & is.na(Genus) & !is.na(Family), ] %>% 
@@ -268,7 +268,7 @@ ids <- Trait_NZ[is.na(Species) & is.na(Genus) & !is.na(Family), ] %>%
 Trait_NZ <- Trait_NZ[!unique_id %in% ids, ]
 
 # save
-saveRDS(Trait_NZ, 
-        file = file.path(data_cleaned, 
-                         "NZ", 
+saveRDS(Trait_NZ,
+        file = file.path(data_cleaned,
+                         "NZ",
                          "Trait_NZ_taxa_pp.rds"))

### 2020-10-16 R/02_AUS_harmonize_traits.R

@@ -145,6 +145,9 @@ Trait_AUS[, feed_parasite := apply(.SD, 1, max),
           .SDcols = c("feed_parasite",
                       "feed_parasite_Schaefer",
                       "feeding_parasite_maxwell")]
+
+Trait_AUS$h
+
 Trait_AUS[, c(
   "feeding_shredder_Marchant",
   "Feeding_shredders_VicEPA",
@@ -476,4 +479,11 @@ saveRDS(
     "Australia",
     "Trait_AUS_harmonized.rds"
   )
+)
+saveRDS(
+  object = Trait_AUS,
+  file = file.path(
+    data_aggr,
+    "Data",
+    "Trait_AUS_harmonized.rds")
 )

### 2020-10-16 R/02_NOA_preprocessing.R

@@ -16,6 +16,20 @@ Trait_Noa <- Trait_Noa[, .SD, .SDcols = names(Trait_Noa) %like% cols]
 # Add ID col as unique identifier
 Trait_Noa[, unique_id := 1:nrow(Trait_Noa)]
 
+# taxonomical corrections
+# Parapoynx & Petrophilia
+Trait_Noa[Genus %in% c("Parapoynx",
+                       "Petrophila"), Family := "Crambidae"]
+
+# Rossiana
+Trait_Noa[Genus == "Rossiana", Family := "Rossianidae"]
+
+# Sperchonopsis
+Trait_Noa[Genus == "Sperchonopsis", Family := "Sperchonidae"]
+
+# Corbiculidae
+Trait_Noa[Family == "Corbiculidae", Order := "Venerida"]
+
 #__________________________________________________________________________
 #### Create two DB versions with different codings ####
 #__________________________________________________________________________

### 2020-10-16 R/02_NZ_harmonize_traits.R

@@ -232,3 +232,11 @@ Trait_NZ <- Trait_NZ[!(is.na(species) & is.na(genus) & is.na(family)), ]
 # save
 saveRDS(object = Trait_NZ,
         file = file.path(data_cleaned, "NZ", "Trait_NZ_pp_harmonized.rds"))
+
+saveRDS(
+  object = Trait_NZ,
+  file = file.path(
+    data_aggr,
+    "Data",
+    "Trait_NZ_pp_harmonized.rds")
+)

### 2020-10-16 R/03_AUS_aggregate_traits.R

@@ -39,7 +39,7 @@ completeness_trait_data(
 # Subset to relevant traits & orders
 Trait_AUS <- Trait_AUS[, .SD,
                        .SDcols = names(Trait_AUS) %like%
-                         "locom|feed|resp|volt|size|bf|dev|unique_id|species|genus|family|order"] %>%
+                         "locom|feed|resp|volt|size|bf|dev|ovip|unique_id|species|genus|family|order"] %>%
   .[order %in% c(
     "Ephemeroptera",
     "Hemiptera",
@@ -47,97 +47,17 @@ Trait_AUS <- Trait_AUS[, .SD,
     "Trichoptera",
     "Coleoptera",
     "Plecoptera",
-    "Diptera"
+    "Diptera",
+    "Megaloptera",
+    "Neuroptera"
   ),]
 
-# just return rows where for each trait there is an observation 
-Trait_AUS <- na.omit(Trait_AUS,
-  cols = names(Trait_AUS[, -c(
-    "unique_id",
-    "species",
-    "genus",
-    "family",
-    "order"#,
-    # "bf_cylindrical",
-    # "bf_flattened",
-    # "bf_spherical",
-    # "bf_streamlined"
-  )])
-)
-# rm unique id col
-Trait_AUS[, unique_id := NULL]
 
-# _________________________________________________________________________
-#### Aggregation of traits ####
-# - Aggregation: 
-# Median to Genus/ 
-# Mode for Family 
-# -> differing amount of values to calculate value for each modality
-# sum(table(Trait_AUS[grepl("Chirono.*", family)]$temp_eurytherm))
+# create taxa column
+Trait_AUS[, taxa := coalesce(species, genus, family, order)]
 
-# Poff et al. 2006: most common genus-level modality assigned (genus level
-# trait data with family-level monitoring data)
-# which(table(Trait_AUS$genus) == max(table(Trait_AUS$genus), na.rm = TRUE))
-# _________________________________________________________________________
-
-# get names of trait columns
-trait_col <- names(Trait_AUS[, -c("family",
-                                  "genus",
-                                  "species",
-                                  "order")])
-
-# subset so that no NA values occur in Species data (otherwise all NA entries are viewed as a group &
-# aggregated as well)
-Trait_AUS_genus <- Trait_AUS[!is.na(species), lapply(.SD, median, na.rm = TRUE), 
-                             .SDcols = trait_col, 
[…]

### 2020-10-16 R/03_NZ_aggregate_traits.R

@@ -14,7 +14,8 @@ Trait_NZ <- normalize_by_rowSum(
   non_trait_cols = c("order",
                      "family",
                      "genus",
-                     "species")
+                     "species",
+                     "unique_id")
 )
 
 # test how complete trait sets are 
@@ -23,14 +24,8 @@ completeness_trait_data(x = Trait_NZ,
                         non_trait_cols = c("order",
                                            "family",
                                            "genus",
-                                           "species"))
-
-# just return rows where for each trait there is an observation 
-Trait_NZ <- na.omit(Trait_NZ,
-                    cols = names(Trait_NZ[, -c("species", 
-                                               "genus", 
-                                               "family",
-                                               "order")]))
+                                           "species",
+                                           "unique_id"))
 
 # Subset to interesting orders:
 #   "Amphipoda" & "Venerida" missing
@@ -41,90 +36,38 @@ Trait_NZ <- Trait_NZ[order %in% c(
   "Trichoptera",
   "Coleoptera",
   "Plecoptera",
-  "Diptera"
+  "Diptera",
+  "Megaloptera",
+  "Neuroptera"
 ), ]
 
-# _________________________________________________________________________
-#### Aggregate to genus level ####
 
-# Interesting? 
-  # Depending on aggregation method:
-  # How many species used for Aggregation
-  # from Species to Genus 
-  # from Genus to Family (already implemented)
-# _________________________________________________________________________
+# Direct aggregation using the median
+Trait_NZ_agg <- direct_agg(
+  trait_data = Trait_NZ,
+  non_trait_cols = c("species",
+                     "genus",
+                     "family",
+                     "order",
+                     "unique_id"),
+  method = median
+)
 
-# create vector with trait names
-trait_col <- names(Trait_NZ[, -c("family",
-                                 "genus",
-                                 "species",
-                                 "order")])
+# just return rows where for each trait there is an observation 
+# add feeding mode parasite not present in NZ -> add "artificial" column
+# and normalize again!
+Trait_NZ_agg <-
[…]

### 2020-10-16 R/04_EU_aggregate_traits.R

@@ -3,6 +3,7 @@
 # =========================================================================
 
 # read in harmonized, preprocessed & already normalized EU Trait DB
+# data are already normalized!
 Trait_EU <-
   readRDS(file = file.path(data_cleaned, "EU", "Trait_EU_pp_harmonized.rds"))
 
@@ -17,7 +18,7 @@ completeness_trait_data(x = Trait_EU,
 # Choose traits &
 # restrict to certain orders
 Trait_EU <- Trait_EU[, .SD,
-                     .SDcols = names(Trait_EU) %like% "locom|feed|resp|volt|size|bf|dev|species|genus|family|order"] %>%
+                     .SDcols = names(Trait_EU) %like% "locom|feed|resp|volt|size|bf|ovip|dev|species|genus|family|order"] %>%
   .[order %in% c(
     "Ephemeroptera",
     "Hemiptera",
@@ -25,79 +26,33 @@ Trait_EU <- Trait_EU[, .SD,
     "Trichoptera",
     "Coleoptera",
     "Plecoptera",
-    "Diptera"
-  ), ]
+    "Diptera",
+    "Megaloptera",
+    "Neuroptera"
+  ),]
 
-# just return rows where for each trait there is an observation
-Trait_EU <- na.omit(Trait_EU,
-  cols = names(Trait_EU[, -c("species", "genus", "family", "order")])
+
+# trait aggregation to family-lvl
+Trait_EU_agg <- direct_agg(
+  trait_data = Trait_EU,
+  non_trait_cols = c("species",
+                     "genus",
+                     "family",
+                     "order"),
+  method = median
 )
 
-# _______________________________________________________________________
-#### Aggregate to genus level ####
-# _______________________________________________________________________
+# just return rows where for each trait there is an observation
+Trait_EU_agg <- normalize_by_rowSum(x = Trait_EU_agg,
+                                    non_trait_cols = c("order",
+                                                       "family")) %>%
+  na.omit(.,
+          cols = names(.[, -c("family",
+                              "order")]))
 
-# create name pattern to choose traits
-trait_col <- names(Trait_EU[, -c("family",
-                                 "genus",
-                                 "species",
-                                 "order")])
-# First aggregation step 
-Trait_EU_genus <- Trait_EU[!is.na(species), lapply(.SD, median, na.rm = TRUE),
[…]

### 2020-10-16 R/04_NOA_NEW_preprocessing.R

@@ -53,8 +53,17 @@ for(j in names(Trait_Noa_new)) {
 # There are duplicates in the species column hence we assign a unique_id column
 Trait_Noa_new[, unique_id := 1:nrow(Trait_Noa_new)]
 
+# Taxonomical corrections
+# Crambiidae to Crambidae
+Trait_Noa_new[Family == "Crambiidae", Family := "Crambidae"]
+
+# Hydrochus Hydrochidae? 
+Trait_Noa_new[Genus == "Hydrochus", Family := "Hydrochidae"]
+
 #__________________________________________________________________________
 #### Create two DB versions with different codings ####
+# fuzzy coded was just an experiment which I have not pursued 
+# The code for this is commented out
 #__________________________________________________________________________
 
 # binary coding
@@ -84,19 +93,19 @@ Trait_Noa_new <- data.table::dcast(
 
 # fuzzy coding based on frequency
 # code Laura Twardochleb with slight modifications
-Trait_Noa_new_fc <- Trait_Noa_new_lf %>%
-  filter(!is.na(Trait) & !is.na(Genus)) %>%
-  group_by(Genus, Trait_group, Trait) %>%
-  tally() %>%
-  mutate(Percent = n / sum(n)) %>%
-  dcast(., Genus ~ Trait) 
-setDT(Trait_Noa_new_fc)
-
-# merge information on family and order level back
-Trait_Noa_new_fc[Trait_Noa_new_lf,
-                 `:=`(Order = i.Order,
-                      Family = i.Family),
-                 on = "Genus"]
+# Trait_Noa_new_fc <- Trait_Noa_new_lf %>%
+#   filter(!is.na(Trait) & !is.na(Genus)) %>%
+#   group_by(Genus, Trait_group, Trait) %>%
+#   tally() %>%
+#   mutate(Percent = n / sum(n)) %>%
+#   dcast(., Genus ~ Trait) 
+# setDT(Trait_Noa_new_fc)
+# 
+# # merge information on family and order level back
+# Trait_Noa_new_fc[Trait_Noa_new_lf,
+#                  `:=`(Order = i.Order,
+#                       Family = i.Family),
+#                  on = "Genus"]
 # DT Version:
 # Trait_Noa_new_lf %>% 
 #   .[!is.na(Trait), .(.N),
@@ -106,26 +115,26 @@ Trait_Noa_new_fc[Trait_Noa_new_lf,
[…]

### 2020-10-16 R/06_NOA_NEW_aggregate_traits.R

@@ -22,88 +22,42 @@ completeness_trait_data(x = Trait_Noa_new,
 # currently, oviposition not used
 Trait_Noa_new <- Trait_Noa_new[,.SD,
                                 .SDcols = names(Trait_Noa_new) %like%
-                                "locom|feed|resp|volt|bf|size|dev|unique_id|species|genus|family|order"]
+                                "locom|feed|resp|volt|bf|size|dev|ovip|unique_id|species|genus|family|order"]
 
-Trait_Noa_new <- na.omit(Trait_Noa_new,
-                         cols = names(Trait_Noa_new[, - c("unique_id", 
-                                                          "species", 
-                                                          "genus", 
-                                                          "family", 
-                                                          "order")]))
-# _________________________________________________________________________
-#### First aggregation step ####
-# _________________________________________________________________________
+# subset to aq. insect orders
+Trait_Noa_new <- Trait_Noa_new[order %in% c(
+  "Ephemeroptera",
+  "Hemiptera",
+  "Odonata",
+  "Trichoptera",
+  "Coleoptera",
+  "Plecoptera",
+  "Diptera",
+  "Megaloptera",
+  "Neuroptera"
+), ]
 
-# create vector with trait names
-trait_col <- names(Trait_Noa_new[, - c("unique_id",
-                                      "family",
-                                      "genus",
-                                      "species",
-                                      "order")])
 
-# aggregate species data to genus level via median
-Trait_Noa_new_genus <-
-  Trait_Noa_new[!is.na(species), lapply(.SD, median, na.rm = TRUE),
-                .SDcols = trait_col, by = "genus"]
+# aggregate to family-lvl using direct-agg via median
+Trait_Noa_new_agg <- direct_agg(
+  trait_data = Trait_Noa_new,
+  non_trait_cols = c("species",
+                     "genus",
+                     "family",
+                     "order",
+                     "unique_id"),
+  method = median
+)
 
-# merge family information back 
-Trait_Noa_new_genus[Trait_Noa_new[!is.na(species),],
-                `:=`(family = i.family,
-                     order = i.order),
-                     on = "genus"]
-
-# rbind with Trait data resolved on genus level 
[…]

### 2020-10-16 R/NZ_potential_parasites.R

@@ -1,0 +1,79 @@
+Trait_NZ[, taxa := coalesce(Species,Genus,Family,Order)]
+
+# families with parasites in AUS
+Trait_NZ[Family %in% c("Erpobdellidae",
+                       "Glossiphoniidae",
+                       "Ornithobdellidae",
+                       "Richardsonianidae",
+                       "Corallanidae",
+                       "Cirolanidae"),]
+
+# Check worms and leeches in NZ
+# Rhynchobdellida
+# Arguloida (parasitic crustaceans)
+# Gordioidea (parasitic worms)
+# Arhynchobdellida
+# "Branchiobdellida" (few cases live as parasites)
+# "Unionida" (mussels)
+# "Mermithida"
+Trait_NZ[Order %in% c("Rhynchobdellida", 
+                      "Arguloida",
+                      "Gordioidea",
+                      "Arhynchobdellida", 
+                      "Unionida",
+                      "Mermithida"), ]
+
+# critical species: "Alboglossiphonia heteroclita"
+# -> Predator
+
+
+
+# AUS
+Trait_AUS <- readRDS(
+  file = file.path(
+    data_cleaned,
+    "Australia",
+    "Trait_AUS_harmonized.rds"
+  )
+)
+parasite_taxa_AUS <- Trait_AUS[feed_parasite == 1, coalesce(species,
+                                                            genus,
+                                                            family,
+                                                            order)]
+
+Trait_NZ[taxa %in% parasite_taxa_AUS,]
+
+# NOA
+Trait_Noa_new <- readRDS(file = file.path(data_cleaned,
+                                          "North_America",
+                                          "Traits_US_LauraT_pp_harmonized.rds"))
+
+parasite_taxa_NOA <-
+  Trait_Noa_new[feed_parasite > 0, coalesce(species, genus,
+                                            family, order)]
+Trait_NZ[taxa %in% parasite_taxa_NOA, ]
+
+# EU
+Trait_EU <-
+  readRDS(file = file.path(data_cleaned, "EU", "Trait_EU_pp_harmonized.rds"))
+
+parasite_taxa_EU <-
+  Trait_EU[feed_parasite > 0, coalesce(species, genus, family, order)]
+
+Trait_EU[feed_parasite > 0, unique(order)]
+
+# Scimyzidae and Ephydridae potentially parasites (Sciomyzidae 
+# in gastropods):
+# From Resh and Carde: 
[…]

### 2020-10-16 R/Not_compatible_traits.R

@@ -71,6 +71,15 @@ tachet[tachet[, Reduce(`&`, lapply(.SD, `==`, 0)),.SDcols = sel_col],
        .SDcols = names(tachet) %like% "species|genus|family|order|feed.*"]
 
 
+# tachet locomotion 
+write.csv(
+  tachet[loc_flier_t > 0 | loc_interstitial_t > 0, .SD,
+         .SDcols = names(tachet) %like% "species|genus|family|order|loc.*"] %>%
+    .[order(-loc_flier_t, -loc_interstitial_t),],
+  file = file.path(data_out, "tachet_not_compatible_locomotion.csv"),
+  row.names = FALSE
+)
+
 #### North America (Vieira et al.) ####
 Trait_Noa <- readRDS(file = file.path(data_cleaned, 
                                       "North_America",
@@ -222,6 +231,53 @@ sel_col <- c("Air_respiration_aquatic_stages_fam_Chessman2017",
 Trait_AUS_resp[Trait_AUS_resp[, Reduce(`&`, lapply(.SD, `==`, 0)), .SDcols = sel_col],
                .SD,
                .SDcols = names(Trait_AUS_resp) %like% "Species|Genus|Family|Order|resp.*"]
+
+
+
+# parasite taxa
+# EU
+Trait_EU <-
+  readRDS(file = file.path(data_cleaned, "EU", "Trait_EU_pp_harmonized.rds"))
+
+cols <- grep("order|family|genus|species|feed.*", names(Trait_EU),
+             value = TRUE)
+
+write.csv(
+  Trait_EU[feed_parasite > 0, .SD, .SDcols = cols] %>%
+    .[order(-feed_parasite), ],
+  file = file.path(data_out, "EU_parasite.csv"),
+  row.names = FALSE
+)
+
+# NOA
+Trait_Noa_new <- readRDS(file = file.path(data_cleaned,
+                                          "North_America",
+                                          "Traits_US_LauraT_pp_harmonized.rds"))
+
+cols <- grep("(?i)order|family|genus|species|feed.*", names(Trait_Noa_new),
+             value = TRUE)
+
+write.csv(
+  Trait_Noa_new[feed_parasite > 0, .SD, .SDcols = cols] %>%
+    .[order(-feed_parasite),],
+  file = file.path(data_out, "NOA_parasite.csv"),
+  row.names = FALSE
+)
+
+# AUS
+Trait_AUS <- readRDS(
+  file = file.path(
[…]

### 2020-10-16 R/Run.R

@@ -1,0 +1,18 @@
+#### Run script ####
+
+# Packages, paths and functions
+source("./R/Set_up.R")
+
+#### OLD ####
+
+# EU:
+# all scripts can be run separately 
+# preprocessing freshwaterecol (taxa)
+source("./R/01_EU_preprocessing_freshecol.R")
+
+# preprocessing & harmonizing tachet
+source("./R/02_EU_preprocessing_tachet.R")
+source("./R/02_01_EU_harmonize_tachet.R")
+
+# harmonisation freshecol & integration tachet
+source("./R/03_EU_harmonize_traits.R")

### 2020-10-16 R/Set_up.R

@@ -5,20 +5,20 @@
 
 # libraries
 # data transformation and data handling
-library(dplyr)     
-library(data.table) 
-library(tidyr)  
-library(readxl) 
-library(zeallot) 
+library(dplyr)
+library(data.table)
+library(tidyr)
+library(readxl)
+library(zeallot)
 
-# taxonomical information 
-library(taxize) 
+# taxonomical information
+# library(taxize)
 
 # data overview
-library(Hmisc) 
+library(Hmisc)
 
 # unit testing
-library(testthat) 
+library(testthat)
 
 # Data location
 data_in <- "./Data"
@@ -29,11 +29,15 @@ data_cleaned <- "./Cleaned_data"
 # Path for data to fill missing values
 data_missing <- "./Missing_data"
 
+# data location for trait aggregation project
+data_aggr <- "/home/kunzst/Dokumente/Projects/Trait_DB/Trait-aggregation"
+
 # Path for output
 data_out <- "./Output"
 
 # Location for R scripts
 data_scr <- "./R"
+
 
 # source script with used functions
 source(file = file.path(data_scr, "functions_used_TDB.R"))

### 2020-10-16 R/functions_used_TDB.R

@@ -298,191 +298,3 @@ direct_agg <- function(trait_data,
            ]
   agg_data
 }
-
-# _________________________________________________________________________
-#### Aggregate duplicate taxa entries ####
-# _________________________________________________________________________
-
-# Simple aggregation function for DB that in itself consist of
-# multiple DBs (e.g. Australian trait DB)
-# There, duplicates originate from the different original databases
-# and often produce entries like (1, 0) where 
-aggr_dupl_multDB <- function(y) {
-  if(sum(y) == 0)
-    0
-  else
-    mean(y[y != 0])
-}
-
-# NOTICE: Not used anymore, far to complex for what they were 
-# actually for
-# Duplicate taxa with numeric values are condensed:
-# The Mode is taken when the same taxa occurs multiple times
-# If all values are distinct, the median is taken.
-# See also the documentation of "condense_dupl_numeric_agg"
-# requires:
-# dataset
-# column with duplicates
-# all non trait columns
-# condense_dupl_numeric <- function(trait_data, col_with_dupl_entries, non_trait_cols) {
-# 
-#   #
-#   if (nrow(trait_data[duplicated(get(col_with_dupl_entries)), ]) == 0) {
-#     stop("Input data has no duplicates. Check for duplicates first before applying this function.")
-#   }
-# 
-#   # subset to duplicate taxa
-#   dupl_taxa <-
-#     trait_data[
-#       duplicated(get(col_with_dupl_entries)),
-#       unique(get(col_with_dupl_entries))
-#     ]
-# 
-#   # create data.tables with and without duplicates
-#   dupl <- trait_data[get(col_with_dupl_entries) %in% dupl_taxa, ]
-#   without_dupl <-
-#     trait_data[!(get(col_with_dupl_entries) %in% dupl_taxa), ]
-# 
-#   # transform duplicates into long format
-#   # function should have the possibility to choose id.vars (non trait columns)
-#   dupl_lf <- melt(
-#     data = dupl,
-#     id.vars = non_trait_cols
-#   )
-# 
-#   # Actual condensation of trait values
-#   # rather take Mode but throw out zero? instead of median in second ifelse() statement
-#   dupl_lf[, `:=`(value = ifelse(
-# 
-#     # is TRUE when NOT all values are distinct
-#     length(value) != length(unique(value)),
-#     #  is TRUE when not just zeros are present
-#     ifelse(
-#       !identical(value[value != 0], numeric(0)),
[…]

### 2020-10-17 R/Preprocessing_raw/03_preprocess_new_freshecol_taxa.R
17.10: Taxonomic fix

@@ -236,6 +236,9 @@ freshwaterecol[grepl("Microhydra sowerbyi", species), `:=`(
 # Bythinella
 freshwaterecol[genus == "Bythinella", family := "Hydrobiidae"]
 
+# Tipulidae is order Diptera
+freshwaterecol[family == "Tipulidae", order := "Diptera"]
+
 # set column order
 setcolorder(
   freshwaterecol,

### 2020-10-17 R/01_EU_preprocess_new.R
17.10: Fix column names

@@ -70,12 +70,12 @@ dupl_species <- trait_EU[!is.na(species), ] %>%
   .[duplicated(.)]
 # agg via median except voltinism
 trait_EU[species %in% dupl_species,
-  (cols_wo_volt) := lapply(.SD, median, na.rm = TRUE),
+  (cols_fuzzy) := lapply(.SD, median, na.rm = TRUE),
   .SDcols = cols_fuzzy,
   by = "species"
 ]
 trait_EU[species %in% dupl_species,
-         (cols_volt) := lapply(.SD, max, na.rm = TRUE),
+         (cols_bin) := lapply(.SD, max, na.rm = TRUE),
          .SDcols = cols_bin,
          by = "species"
 ]
@@ -89,12 +89,12 @@ dupl_genus <- trait_EU[is.na(species) & !is.na(genus), ] %>%
   .[!duplicated(.)]
 # agg via median except voltinism
 trait_EU[is.na(species) & genus %in% dupl_genus,
-  (cols_wo_volt) := lapply(.SD, median, na.rm = TRUE),
+  (cols_fuzzy) := lapply(.SD, median, na.rm = TRUE),
   .SDcols = cols_fuzzy,
   by = "genus"
 ]
 trait_EU[is.na(species) & genus %in% dupl_genus,
-         (cols_volt) := lapply(.SD, max, na.rm = TRUE),
+         (cols_bin) := lapply(.SD, max, na.rm = TRUE),
          .SDcols = cols_bin,
          by = "genus"
 ]
@@ -110,13 +110,13 @@ dupl_families <- trait_EU[is.na(species) & is.na(genus) & !is.na(family), ] %>%
   .[!duplicated(.)]
 # agg via median except voltinism
 trait_EU[is.na(species) & is.na(genus) & family %in% dupl_families,
-  (cols_wo_volt) := lapply(.SD, median, na.rm = TRUE),
-  .SDcols = cols_wo_volt,
+  (cols_fuzzy) := lapply(.SD, median, na.rm = TRUE),
+  .SDcols = cols_fuzzy,
   by = "family"
 ]
 trait_EU[is.na(species) & is.na(genus) & family %in% dupl_families,
-         (cols_volt) := lapply(.SD, max, na.rm = TRUE),
-         .SDcols = cols_volt,
+         (cols_bin) := lapply(.SD, max, na.rm = TRUE),
+         .SDcols = cols_bin,
          by = "family"
 ]
 

### 2020-10-20 Paper/Draft_harmonization_paper.tex
20.10: Updat Paper

@@
 
+% BK:
+% # I wonder if some simulation could be useful to determine in what
+% # circumstances the different aggregation methods will produce similar
+% # or different results. E.g. If all families were to have the same number of
+% # genus and all genus the same number of species (something which would
+% #  never happen),
+% # then it will not matter (much) whether direct, stepwise or
+% # weighted aggregation is used.
+% # It only becomes important if direct, stepwise or weighted is used,
+% # as the number of genus per family and/or species per genus differ.
+% # Some simulation that varies the taxonomic hierarchy and variability in traits
+% # between genus within a family and species within genus, ….,
+
+To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we simulated three different taxonomic hierarchies. 
+Sim1) A family with equal number of genera and species (5 genera each with 5 species respectively).
+Sim2) A family were one genus has a much larger number of species as the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively). 
+Sim3) A family were all genera have a different number of species (8, 2, 7, 3, 5)
+Every simulated taxonomic hierarchy was assigned a hypothetical grouping feature with 3 traits.
+The individual affinities for each trait were sampled from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviation (0.2, 0.4, 0.6, 0.8 and 1) respectively to simulate trait variability.
+The truncated normal distribution was bound to 0 and 1.
+The traits were normalized so that they sum up to one for each species, similar to the data processing of the trait databases.
+100 Simulations for each standard deviation were carried out.
+Hence,
+500 simulations were run for each simulation scenario (in total 1500). 
+All trait aggregation methods were applied to each simulated dataset and the results were compared.   
+% Sampled from a truncated normal distribution values for three traits
+% (upper and lower boundaries 0 and 1)
+% Traits were normalized so that they sum up to one
+% Three different taxonomic hierarchies were simulated: 
+% Simulated one family with 25 species 
+% -> 1) 5 Genera:  5 Species respectively
+% -> 2) 5 Genera: 1 Genus 13 Species (more than ~ 50 %); 4 Genera with 3 species
+% -> 3) 5 Genera: All have different amount of species
+
 \begin{figure}
@@
 Aggregated trait affinities of the five trait aggregation methods (\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg}) were compared to trait affinities assigned at family-level by experts, which were available for Australia and North America for a subset of grouping features and taxa.
-For the Australian dataset, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman \cite{chessman_dissolved-oxygen_2018}.
-In Chessman \cite{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the Australian dataset except that the trait parasite is missing.
-We conducted the comparison for the 220 families available in Chessman \cite{chessman_dissolved-oxygen_2018}.
+For the Australian dataset, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman et al.
+\cite{chessman_dissolved-oxygen_2018}.
+In Chessman et al.
+\cite{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the Australian dataset except that the trait parasite is missing.
+We conducted the comparison for the 220 families available in Chessman et al.
+\cite{chessman_dissolved-oxygen_2018}.
 Considering each factor combination of family and trait (in total 8) this amounts to 1760 cases.
@@
 For the North American dataset, we compared aggregated trait affinities with assigned trait affinities on family-level for the grouping features feeding mode, respiration, size, voltinism, and locomotion.
-The assigned trait affinities at family-level are part of the North American database (Twardochleb) \cite{twardochleb_trait_data_2020}) and originate from expert knowledge.
+The assigned trait affinities at family-level are part of the North American database (Twardochleb et al.) \cite{twardochleb_trait_data_2020} and originate from expert knowledge.
 Trait information was available for 94 families of which all were present in the North American dataset (total number of cases 1598).
@@
 
-% Sampled from a truncated normal distribution values for three traits
-% (upper and lower boundaries 0 and 1)
-% Traits were normalized so that they sum up to one
-% Three different taxonomic hierarchies were simulated: 
-% Simulated one family with 25 species 
-% -> 1) 5 Genera:  5 Species respectively
-% -> 2) 5 Genera: 1 Genus 13 Species (more than ~ 50 %); 4 Genera with 3 species
-% -> 3) 5 Genera: All have different amount of species
-
 % Simulation result: 
-% -  base simulation with similar amount of speices per genus and genera per family and varying trait values
+% -  base simulation with similar amount of species per genus and genera per family and varying trait values
 % results can vary when variation in trait values increases 

### 2020-10-20 Paper/Draft_harmonization_paper.tex
Updates from Overleaf

--- 2020-10-12 Paper/Draft_harmonization_paper.tex
@@
 Explaining and predicting how communities are shaped by environmental factors is one of the main goals of ecology.
-Species traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, might be beneficial in achieving this goal \cite{heino_jani_macroecological_2013}.
-%?just traits
-Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
-% TODO: PUP: Not only „of an organism“, but also „of a population“ (at least for some of the traits related to reproduction; e.g. difficult to describe „voltinism“ as the organism scale!).
-Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than in taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
-Traits of freshwater invertebrate individuals are difficult to determine because - unlike plants - their traits often cannot be measured directly.
+Organismal traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, might be beneficial in achieving this goal \cite{heino_jani_macroecological_2013}.
+Traits evolve through adaptations (e.g., physiological, behavioral, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
+Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
+Traits of freshwater invertebrates are difficult to determine because, unlike plants, their traits often cannot be measured directly.
 For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community \cite{moog_comprehensive_nodate}.
-% PUP says: But the trait-based approach can benefit from two centuries of detailed, published observations on biological traits and ecological preferences made by zoologists/ecologists on a large range of species in various environmental conditions.
 Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
 by relating macroinvertebrate trait composition to environmental factors or as trait metrics in biomonitoring \cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}.
+
+%%% Old Intro Version %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Explaining and predicting how aquatic communities are shaped by environmental factors is one of the main goals of freshwater ecology.
+Organismal traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, are increasingly incorporated into freshwater ecology to support this goal, e.g.
+by relating macroinvertebrate trait composition to environmental factors or as trait metrics in biomonitoring \cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}.
+Traits evolve through adaptations (e.g., physiological, behavioral, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
+% Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches may be suitable for large scale analysis because the variability in trait responses is lower than for taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 For example, Bonada et al.
-\cite{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from Usseglio-Polatera et al.
+\cite{bonada_taxonomic_2007} compared trait composition for mediterranean and temperate regions in Europe using traits from Usseglio-Polatera et al.
 \cite{usseglio-polatera_biomonitoring_2000}, Poff et al.
@@
 \cite{brown_functional_2018} harmonized grouping features based on trait databases from Europe, North America, and New Zealand because in these trait databases identical grouping features are classified differently into traits.
-As the traits from North America were coded binary in contrast to the fuzzy coded traits from Europe and New Zealand, the authors consulted experts to assign fuzzy coded traits to North American taxa or inferred them from the European trait database.
+As the traits from North America were coded binary in contrast to the fuzzy coded traits from from Europe and New Zealand, the authors consulted experts to assign fuzzy coded traits to North American taxa or inferred them from the European trait database.
 Thus, it becomes apparent that using invertebrate trait data from several regions requires extensive data processing prior to the actual data analysis.
@@
 Aggregated trait affinities of the five trait aggregation methods (\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg}) were compared to trait affinities assigned at family-level by experts, which were available for the Australian and North American database for a subset of grouping features and taxa.
-For the Australian database, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman \cite{chessman_dissolved-oxygen_2018}.
-In Chessman \cite{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the harmonized Australian database except that the trait parasite is missing.
-We conducted the comparison for the 220 families available in Chessman \cite{chessman_dissolved-oxygen_2018}.
+For the Australian database, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman et al.
+\cite{chessman_dissolved-oxygen_2018}.
+In Chessman et al.
+\cite{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the harmonized Australian database except that the trait parasite is missing.
+We conducted the comparison for the 220 families available in Chessman et al.
+\cite{chessman_dissolved-oxygen_2018}.
 Considering each factor combination of family and trait (in total 8) this amounts to 1760 cases.
@@
 \subfile{Results/Results_trait_harmonization}
-% TODO: Fix reference to SI!
 
@@
 
-% Influence of aggregation methods on trait-environment relationships:
-% 1) In general, differences produced by the aggregation methods seem to arise by using mean or median, 
-% not driven by different weighting approaches (direct vs. stepwise vs. weighted) 
-% -> link to taxonomic hierarchy, many families have only a few genera
-% -> Similarly, many genera have only a few species
-% -> linear relationship: the more genus per family, the more species (although there are exceptions -> e.g. Europe)
-% 
-% Differences for NOA greater due to coding?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Ben's Comment: -> But another issues is that these aggregation methods were being compared to traits assigned at the family level, which I understand was often done by expert opinion.
-So, these traits assigned at the family level may not be really “correct”!
-The difference between the trait aggregated to family and its designation at the family level could indicate: (a) the aggregation method is “no good”, (b) the trait assigned at the family level was “no good”, or (c) both a and b.
-
-% Sampled from a truncated normal distribution values for three traits
-% (upper and lower boundaries 0 and 1)
-% Traits were normalized so that they sum up to one
-% Three different taxonomic hierarchies were simulated: 
-% Simulated one family with 25 species 
-% -> 1) 5 Genera:  5 Species respectively
-% -> 2) 5 Genera: 1 Genus 13 Species (more than ~ 50 %); 4 Genera with 3 species
-% -> 3) 5 Genera: All have different amount of species
-
-% Simulation result: 
-% -  base simulation with similar amount of speices per genus and genera per family and varying trait values
-% results can vary when variation in trait values increases 
-% However, mostly the different aggregation methods result in similar trait affinities
-% when differences occur, only for: 
-% dir_median vs stepwise median
-% direct mean vs stepwise median
-% stepwise mean vs stepwise median
-% direct mean vs direct median
-% stepwise median vs weighed agg
-% Trait variability: 0.3 and greater
-% Max diff ~ 0.2
-
-% - Results for varying taxonomic hierarchy:
-% Which levels?
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% 2) Harmonization: Minor influence on RDA species scores
-% RDA species scores 
-%   -> Normalized eigenvectors
-%   -> dependent on nr. of variables? Nr. of response variables not really influential 
-% We used only a small-scale study -> What's different to large-scale studies?
-
-% Further aggr. after harmonization: no difference to the harmonized dataset
-% ?Logical because trait aggr. methods themselves showed only minor differences
-
+% In general, differences produced by the aggregation methods seem to arise by using mean or median, not driven by different weighting approaches (direct vs. stepwise vs. weighted) 
 % Complex Stat. techniques developed -> cannot use full potential
@@
 
+% Trait definitions 
+\subfile{Trait_def_table/SI_trait_def_table2.tex}
+
 \end{document}

### 2020-10-20 Paper/Draft_harmonization_paper.tex

--- 2020-10-20 Paper/Draft_harmonization_paper.tex
@@
 Species traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, might be beneficial in achieving this goal \cite{heino_jani_macroecological_2013}.
-%?just traits
-Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TODO: PUP: Not only „of an organism“, but also „of a population“ (at least for some of the traits related to reproduction; e.g. difficult to describe „voltinism“ as the organism scale!).
-%%%%%%%%%%%%%%%%%%%%%%%%%%
+Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism or a population to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
 Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than in taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
@@
 For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community \cite{moog_comprehensive_nodate}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PUP says: But the trait-based approach can benefit from two centuries of detailed, published observations on biological traits and ecological preferences made by zoologists/ecologists on a large range of species in various environmental conditions.
-%%%%%%%%%%%%%%%%%%%%%%%%%%
 Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
@@
 For example, Bonada et al.
-\cite{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from the Tachet database \cite{usseglio-polatera_biomonitoring_2000}, Poff et al.
+\cite{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from the Usseglio-Polatera et al.
+\cite{usseglio-polatera_biomonitoring_2000}, Poff et al.
 \cite{poff_developing_2010} characterized trait composition across sites in the Western US using traits from Poff et al.
@@
 Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different continents are rare.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% biogeographic regions substituted with continents
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PUP & ASK: So „grouping features“ are „traits“ (in most of the published databases) described by „traits“ (i.e. several „related categories“). 
-% I agree that these definitions have to be made more clear, i.e.
-that you are using the term „grouping feature“ for what most published articles call “traits” and that what others call “categories” (within the traits) are your “traits”.
-Maybe add a “definition” of terms at the beginning ...also your use of “affinity” needs to be included there…
-% Put into definitons of terms?
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 In this study, we follow the terminology proposed by Schmera et al., where a grouping feature is defined as a general property (e.g.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% BK: I am not sure that the it is binary which is the defining issue, rather it is that there is no uncertainty.
-E.g.
-respiration type as more than two opitions but not undertainty into which a species fall into.
-% PUP: OK in your definition of „grouping features“ and „traits“, it is probably more the „trait description“ than the „trait“ (itself) which can be „binary“.
-% ASK to Voltinism: I think this not an appropriate example for multiple categories except you include different regions for which different categories can apply; i.e.
-multivoltine in the temperate region and univoltine in the boreal region for the same species
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 tolerance of pollution, body size) or using multiple descriptions (e.g.
-locomotion) with some uncertainty as to which trait the organism should be coded to.
+feeding mode) with some uncertainty as to which trait the organism should be coded to.
 One approach for dealing with the uncertainty in the latter is the use of fuzzy coded variables.
@@
 A centralized database with standardized and unambiguous traits and a consistent coding of traits would minimize data processing effort.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PUP: Taking into account your definition of traits (= „trait categories“ or „trait modalities“ in Tachet et al., 2010) and grouping features (= „traits“ in Tachet et al., 2010), the fuzzy coding approach is not applied to the „trait“ scale, but to the „grouping feature“ scale.
-At the „trait“ scale, „only“ an affinity score is allocated to a given taxon.
-The binary/quantitative character of this score is probably not the only important criterion to consider.
-One of the major characteristics of the fuzzy coding approach is, at the „grouping feature“ scale, to allow several „traits“ to be simultaneously present (possibly with different affinity scores) in a given „grouping feature“ for a given taxon (i.e.
-a non-disjunctive approach).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ASK: this is something that should not appear in the introduction, at least not in such detail…
-% ASK: I would suggest not to use “higher/lower” as this is used in different ways in different publications (low can mean low (i.e.
-imprecise) identification level, but it also can mean low in terms of systematic hierarchy, which then would mean more precise id level…); I would suggest to use terms like precise/imprecise, accurate or the like…
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Differing taxonomic resolutions (e.g.
@@
 \cite{poff_functional_2006, szocs_effects_2014, piliere_a._f._h._importance_2016, aspin_extreme_2019}.
-Thereby, trait aggregation is often done using the mean \cite{magliozzi_functional_2019},
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PUP: Sometimes weighted by the rarity/commonality of individual taxa (e.g.
-genera) at large spatial scale (e.g.
-ecoregions), within the higher level taxonomic unit (e.g.
-family), because the probability of the commonest taxa to be present in a given sample is higher (at large spatial scale).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-median \cite{szocs_effects_2014} or the mode \cite{piliere_a._f._h._importance_2016}.
+Thereby, trait aggregation is often done using the mean \cite{magliozzi_functional_2019}, median \cite{szocs_effects_2014} or the mode \cite{piliere_a._f._h._importance_2016}.
 Up to now, studies on how and to which extent different trait aggregation methods influence trait-based analysis are missing.
@@
 \newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The freshwaterecology.info contains taxa on species-level, while taxa recorded in the Tachet database are on species, genus and family-level.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% freshwater.info requested from ASK
-% Slightly changed - Comment from ASK: this is rather confusing at this stage as most of the assignments in freshwaterecology.info (fwe) are on species level whereas Tachet et al.
-have mostly genus and family level data in their database
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Trait information for North America was obtained from Twardochleb et al.
@@
 Excluded from this are the European databases, which we refer to by their commonly used names (freshwaterecology.info and Tachet database).
-% Eingefügt da die Bennung uneinheitlich im Manuskript war, auch von den Co-Autoren kritisiert wurde
 
@@
 crawlers and sprawlers into crawlers).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Does it mean that the relative frequency of „non-amalgamated“ traits could be modified in the „grouping feature“ profiles of taxa?
-(because the highest score could be lower than the sum of the affinity scores of the amalgamated traits)
 Thereby, for a particular taxa the highest trait affinity score among the amalgamated traits was taken.
@@
 
-Prior to harmonization we consolidated duplicate taxa on species, genus or family-level if present, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
+Prior to harmonization we consolidated duplicate taxa on species, genus or family-level if present within a dataset, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
 We omitted taxa with a less precise taxonomic resolution than family-level.
@@
 This method weights the genera according to the number of their species in the trait datasets regardless if for every used grouping feature information was available.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PUP: Is it the „potential number of species“ (i.e.
-the number of species potentially present at the selected spatial scale) or the number of species with traits/grouping features described?
-The grouping feature information can be available for a different set of species from a grouping feature to another.
-Does it mean that genus weights can be different in the aggregated family profile according to the information available on traits (regardless of the actual number of species in these different genera?
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% BK:
-% # I wonder if some simulation could be useful to determine in what
-% # circumstances the different aggregation methods will produce similar
-% # or different results. E.g. If all families were to have the same number of
-% # genus and all genus the same number of species (something which would
-% #  never happen),
-% # then it will not matter (much) whether direct, stepwise or
-% # weighted aggregation is used.
-% # It only becomes important if direct, stepwise or weighted is used,
-% # as the number of genus per family and/or species per genus differ.
-% # Some simulation that varies the taxonomic hierarchy and variability in traits
-% # between genus within a family and species within genus, ….,
 
 To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we simulated three different taxonomic hierarchies. 
-Sim1) A family with equal number of genera and species (5 genera each with 5 species respectively).
-Sim2) A family were one genus has a much larger number of species as the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively). 
-Sim3) A family were all genera have a different number of species (8, 2, 7, 3, 5)
+Sim1) A family with an equal number of genera and species (5 genera each with 5 species respectively).
+Sim2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively). 
+Sim3) A family where all genera have a different number of species (8, 2, 7, 3, 5).
 Every simulated taxonomic hierarchy was assigned a hypothetical grouping feature with 3 traits.
-The individual affinities for each trait were sampled from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviation (0.2, 0.4, 0.6, 0.8 and 1) respectively to simulate trait variability.
+The affinities for each trait were sampled from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviation (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability.
 The truncated normal distribution was bound to 0 and 1.
@@
 Hence,
-500 simulations were run for each simulation scenario (in total 1500). 
-All trait aggregation methods were applied to each simulated dataset and the results were compared.   
-% Sampled from a truncated normal distribution values for three traits
-% (upper and lower boundaries 0 and 1)
-% Traits were normalized so that they sum up to one
-% Three different taxonomic hierarchies were simulated: 
-% Simulated one family with 25 species 
-% -> 1) 5 Genera:  5 Species respectively
-% -> 2) 5 Genera: 1 Genus 13 Species (more than ~ 50 %); 4 Genera with 3 species
-% -> 3) 5 Genera: All have different amount of species
+500 simulations were run for each simulation scenario (in total 1500). All trait aggregation methods were applied to each simulated dataset and the results were compared.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PUP: 
-% Difficult to understand, with your example, what has been done based on your description of the calculation.
-% If you have allocated a weight of „3“ to each species of G1 (as indicated in your detailed calculation; i.e.
-0,25*3 + 0.5*3 + ...), the final contribution of G1 will be nine times greater than that of a genus only described by a single species (not really consistent).
-
-% In my opinion (and taking into account your rationale when defining the other strategies), it would have been more coherent to allocate (i) a weight of „3“ to the mean score of G1 (because 3 species from this genus), (ii) a weight of „2“ (not „1“) to the mean score of G2 (because two descriptions : sp4 and genus sp.
-or spp.
-...
-even if we can question the relevance of averaging information that is at least partially redundant) and a weight of „1“ to the family score (idem, this information is at least partially redundant with the information provided by genera G1 and G2).
-
-% Response: Weight of 2 is thinkable! However, disagree with PUP because what he proposes is basically the direct aggregation using the mean. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ASK: I would change the heading; basically it is comparing family-level-aggregated traits to family-level assigned traits… both, the formerly species-level traits as well as the family-level traits were assigned by experts….
-the point are not the experts but the level of assignment…
-
-% btw. did you try to compare this on genus level as well, e.g. the aggregated genus-level traits from fwe to the assigned genus-level traits from f et al.; this would be highly interesting!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The river Werra has been subject to effluents from the potash industry since the mid of the 20th century and allows to study responses of invertebrates and their trait compositions to salinization \cite{bathe_biological_2011}.
-% BK : Want to add some general refs about salinization and salinization on this river. 
-Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition. Further details can be found in Szöcs et al. \cite{szocs_effects_2014}.
+Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition.
+Further details can be found in Szöcs et al.
+\cite{szocs_effects_2014}.
 
@@
 The 6 harmonized grouping features used were \textit{Size, Feeding mode, Locomotion, Oviposition, Respiration}, and \textit{Voltinism}.
-%Traits of those grouping features responded strongly to salinity in the study of \cite{szocs_effects_2014}.
 Additionally, for testing the effect of aggregated traits we assigned to each taxon in Szöcs et al.
 \cite{szocs_effects_2014} the aggregated trait value for its corresponding family and repeated the RDA.
-% ? reference to SI
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \newpage 
-
 %! Presenting results of trait analysis using harmonized traits:
 \subfile{Results/Results_trait_harmonization}
-% TODO: Fix reference to SI!
 
 \newpage 
-
 %! Discrepancies in trait definitions
-% ?(Discuss history of trait values)
 \subfile{Trait_def_table/Trait_definitions_table}

### 2020-10-21 Paper/Draft_harmonization_paper.tex
21.10: Started results simulation

@@
 To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we simulated three different taxonomic hierarchies. 
-Sim1) A family with an equal number of genera and species (5 genera each with 5 species respectively).
-Sim2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively). 
-Sim3) A family where all genera have a different number of species (8, 2, 7, 3, 5).
+1) A family with an equal number of genera and species (5 genera each with 5 species respectively) 
+% denoted as \textit{equal scenario}.
+2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively). 
+3) A family where all genera have a different number of species (8, 2, 7, 3, 5).
 Every simulated taxonomic hierarchy was assigned a hypothetical grouping feature with 3 traits.
@@
 100 Simulations for each standard deviation were carried out.
-Hence,
-500 simulations were run for each simulation scenario (in total 1500). All trait aggregation methods were applied to each simulated dataset and the results were compared.
+Hence, 500 simulations were run for each simulation scenario (in total 1500).
+All trait aggregation methods were applied to each simulated dataset and the results were compared.
 

### 2020-10-21 Paper/Draft_harmonization_paper.tex
21.10: Improved writing sim method section

@@
 
-To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we simulated three different taxonomic hierarchies. 
+To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we created three hypothetical examples of different taxonomic hierarchies.
 1) A family with an equal number of genera and species (5 genera each with 5 species respectively) 
@@
 3) A family where all genera have a different number of species (8, 2, 7, 3, 5).
-Every simulated taxonomic hierarchy was assigned a hypothetical grouping feature with 3 traits.
-The affinities for each trait were sampled from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviation (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability.
+Every hypothetical taxonomic hierarchy was assigned a hypothetical grouping feature with 3 traits.
+The affinities for each trait were simulated by sampling from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviation (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability.
 The truncated normal distribution was bound to 0 and 1.

### 2020-10-21 Paper/Results/SI.tex
21.10: Started results simulation
21.10: Improved writing sim method section

@@
 
-\subsection*{Comparison of the trait aggregation methods with each other}
+\subsection*{Differences in trait affinities obtained by trait aggregation methods com-pared to traits assigned at family-level}
+
+\subsubsection*{Comparison of the trait aggregation methods with each other}
 \label{sec:compa_aggr_methods}
@@
 
-% \subsection*{Differences in trait affinities obtained by trait aggregation methods compared to traits assigned at family-level}
-%? Cases where trait affinities aggregated through \textit{direct\_agg} differed more than 60 \% from trait affinities assigned at family-level by Chessman 2017
+\subsubsection*{Simulation of varying taxonomic hierarchies}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
+    \caption{Ranges of aggregated trait affinities for the three scenarios and simulated levels of trait variability.
+Each scenario encompasses a family with 25 species with a different taxonomic hierarchy.
+Boxplots depict aggregated trait affinities of 100 runs for every trait aggregation method.
+T1 to T3 are the simulated traits.}
+    \label{fig:overview_sim_results}
+\end{figure}
 

### 2020-10-22 Paper/Draft_harmonization_paper.tex
22.10.: Paper Update: Sim Results, Discussion points

@@
 To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we created three hypothetical examples of different taxonomic hierarchies.
-1) A family with an equal number of genera and species (5 genera each with 5 species respectively) 
-% denoted as \textit{equal scenario}.
-2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively). 
-3) A family where all genera have a different number of species (8, 2, 7, 3, 5).
-Every hypothetical taxonomic hierarchy was assigned a hypothetical grouping feature with 3 traits.
-The affinities for each trait were simulated by sampling from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviation (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability.
+1) A family with an equal number of genera and species (5 genera each with 5 species respectively), denoted as \textit{sim\_base}.
+2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively), denotes as \textit{sim\_extreme}. 
+3) A family where all genera have a different number of species (8, 2, 7, 3, 5), denotes as \textit{sim\_variation}.
+In total every family consisted of 25 species.
+To each hypothetical taxonomic hierarchy a hypothetical grouping feature with 3 traits was assigned.
+The 25 affinities for each trait were simulated by sampling from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviations (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability.
 The truncated normal distribution was bound to 0 and 1.
-The traits were normalized so that they sum up to one for each species, similar to the data processing of the trait databases.
-100 Simulations for each standard deviation were carried out.
-Hence, 500 simulations were run for each simulation scenario (in total 1500).
+Simulated trait affinities were converted to percentages, similar to the data processing of the trait databases.
+The sampling was repeated 100 times for each standard deviation.
+Hence, in total 12500 ($25 * 5 * 100$) trait affinities were simulated.
 All trait aggregation methods were applied to each simulated dataset and the results were compared.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{itemize}
+  \item \textbf{aggregated vs assigned traits}
+  \begin{itemize}
+    \item In general, differences produced by the aggregation methods seem to arise by using mean or median, not so much driven by the different weighting approaches (direct vs. stepwise vs. weighted)
+    \item Approaches that used the median resulted in fewer differences to the assigned traits, albeit if differences occured to the assigned traits, they were greater. 
+    \item Simulation shows that approaches using the median generally produce a larger range of values $\rightarrow$ Especially with higher trait variability for situations where one genus has a lot more species than the other genera within the family
+    \item Differences greater for the NOA dataset because of binary coding $\rightarrow$ differences are greater between traits
+    \item How is the taxonomic hierarchy in the investigated datasets? 
+    % -> link to taxonomic hierarchy, many families have only a few genera
+    % -> Similarly, many genera have only a few species
+    % -> linear relationship: the more genus per family, the more species (although there are exceptions -> e.g. Europe)
+    \item There is no "true" value to compare to, i.e. assigned traits can be biased. Comparison of species-lvl traits in fwe and traits on genus-lvl in tachet would be interesting in this context? 
+    \item  Suggestions from Co-Authors: \\
+     $\rightarrow$ should include where the classifications come from \\
+     $\rightarrow$ what do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? \\
+     $\rightarrow$ are the differences between continents because of evolution or only because scientists have done more research in one of the continents?
+  \end{itemize}
+  \item \textbf{Influence of aggregation methods on trait-environment relationships}
+  \begin{itemize}
+    \item We re-analysed only a small-scale study, what would be different when applying a large-scale study?
+  \end{itemize}
+\end{itemize}
+
 % 1) Trait aggr methods vs assigned traits:
@@
 
-% 2) Influence of aggregation methods on trait-environment relationships:
-% - In general, differences produced by the aggregation methods seem to arise by using mean or median, 
-% not driven by different weighting approaches (direct vs. stepwise vs. weighted) 
-% -> link to taxonomic hierarchy, many families have only a few genera
-% -> Similarly, many genera have only a few species
-% -> linear relationship: the more genus per family, the more species (although there are exceptions -> e.g. Europe)
-% 
-% Differences for NOA greater due to coding?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Ben's Comment: -> But another issues is that these aggregation methods were being compared to traits assigned at the family level, which I understand was often done by expert opinion.
@@
 
-% Simulation result: 
-% -  base simulation with similar amount of species per genus and genera per family and varying trait values
-% results can vary when variation in trait values increases 
-% However, mostly the different aggregation methods result in similar trait affinities
-% when differences occur, only for: 
-% dir_median vs stepwise median
-% direct mean vs stepwise median
-% stepwise mean vs stepwise median
-% direct mean vs direct median
-% stepwise median vs weighed agg
-% Trait variability: 0.3 and greater
-% Max diff ~ 0.2
-
-% - Results for varying taxonomic hierarchy:
-% Which levels?
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% 2) Harmonization: Minor influence on RDA species scores
+% 2) Influence of aggregation methods on trait-environment relationships: 
+% 
+% Harmonization: Minor influence on RDA species scores
 % RDA species scores 
@@
 % Complex Stat. techniques developed -> cannot use full potential
-
-% Suggestions from Co-Authors:
-% should include where the classifications come from
-% what do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge?
-% are the differences between continents because of evolution or only because scientists have done more research in one of the continents?
 

### 2020-10-22 Paper/Results/SI.tex
22.10.: Paper Update: Sim Results, Discussion points

@@
     \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
-    \caption{Ranges of aggregated trait affinities for the three scenarios and simulated levels of trait variability.
-Each scenario encompasses a family with 25 species with a different taxonomic hierarchy.
-Boxplots depict aggregated trait affinities of 100 runs for every trait aggregation method.
+    \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
+Boxplots depict results for each trait aggregation method of 100 simulations.
 T1 to T3 are the simulated traits.}
     \label{fig:overview_sim_results}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
+    \caption{Comparison of the results of the trait aggregation methods for every simulated dataset.
+Simulated datasets where absolute differences between aggregated trait affinities were greater than 0.1 are depicted.
+Only the comparisons are shown were differences greater than 0.1 occurred.}
+    \label{fig:sim_indv_runs}
 \end{figure}

### 2020-10-22 R/Preprocessing_raw/01_preprocess_new_freshecol_2020.R
22.10: Added AQEM

@@ -45,6 +45,25 @@ freshwaterecol <- Reduce(f = cbind, output_db)
 setnames(freshwaterecol, "V1", "taxon")
 freshwaterecol[, EU := NULL]
 
+# -add AQEM codes:
+aqem_path <- file.path(data_raw, "AQEM.csv")
+ind <- grep("Taxon", readLines(aqem_path))
+
+# read in
+aqem <- fread(aqem_path,
+              skip = ind,
+              sep = ";",
+              header = TRUE,
+              na.strings = (""),
+              fill = TRUE
+)
+aqem <- aqem[!(V1 %like% "Statistics|number.*"), ]
+setnames(aqem, "V1", "taxon")
+
+# merge ID
+freshwaterecol[aqem, ID_AQEM := `i.ID-AQEM (ID-fwe)`, on = "taxon"]
+
+
 # trait preparation ----
 
 # pH preference

### 2020-10-22 R/Preprocessing_raw/03_preprocess_new_freshecol_taxa.R
22.10: Added commented code for .rds files

@@ -53,6 +53,7 @@ taxa <- freshwaterecol[
 ] %>% unique()
 ID_gbif <- get_gbifid(taxa, rows = 1)
 saveRDS(ID_gbif, file = "./R/Preprocessing_raw/Cache/ID_gbif_family.rds")
+# ID_gbif <- readRDS(file = "./R/Preprocessing_raw/Cache/ID_gbif_family.rds")
 
 tax_classf <- classification(
   id = ID_gbif,
@@ -78,6 +79,7 @@ ID_subf_gbif <- get_gbifid(taxa_subfamily,
 saveRDS(ID_subf_gbif,
   file = "./R/Preprocessing_raw/Cache/ID_gbif_subfamily.rds"
 )
+# ID_subf_gbif <- readRDS(file = "./R/Preprocessing_raw/Cache/ID_gbif_subfamily.rds")
 
 taxa_subf_classf <- classification(
   id = ID_subf_gbif,
@@ -108,6 +110,7 @@ ID_subf2_gbif <- get_tsn(taxa_subf_2,
 saveRDS(ID_subf2_gbif,
   file = "./R/Preprocessing_raw/Cache/ID_gbif_subfamily_2.rds"
 )
+# ID_subf2_gbif <- readRDS(file = "./R/Preprocessing_raw/Cache/ID_gbif_subfamily_2.rds")
 
 taxa_subf2_classf <- classification(
   id = ID_subf2_gbif,

### 2020-10-23 Paper/Draft_harmonization_paper.tex
23.10: Minor points for discussion

@@
 \midrule
-Respiration  & \begin{tabular}[c]{@{}l@{}}Gills\\ Plastron/Spiracle\\ \\ \\ Tegument\end{tabular}                             & \begin{tabular}[c]{@{}l@{}}Temporary air store, tracheal gills, gills\\ Spiracular gills, atmospheric breathers, \\ plant breathers, functional spiracles, \\ air (plants), aerial, plastron/spiracle\\ Cutaneous, tegument \end{tabular}                                                                         \\
+Respiration  & \begin{tabular}[c]{@{}l@{}}Gills\\ Plastron/Spiracle\\ \\ \\ \\ Tegument\end{tabular}                             & \begin{tabular}[c]{@{}l@{}} Tracheal gills, gills\\ Temporary air store, Spiracular gills, \\ atmospheric breathers, plant breathers, \\ functional spiracles, air (plants), aerial, \\ plastron/spiracle\\ Cutaneous, tegument \end{tabular}                                                                         \\
 \midrule
@@
     \item In general, differences produced by the aggregation methods seem to arise by using mean or median, not so much driven by the different weighting approaches (direct vs. stepwise vs. weighted)
-    \item Approaches that used the median resulted in fewer differences to the assigned traits, albeit if differences occured to the assigned traits, they were greater. 
+    \item Approaches that used the median resulted in fewer differences to the assigned traits, albeit if differences occurred to the assigned traits, they were greater. 
     \item Simulation shows that approaches using the median generally produce a larger range of values $\rightarrow$ Especially with higher trait variability for situations where one genus has a lot more species than the other genera within the family
-    \item Differences greater for the NOA dataset because of binary coding $\rightarrow$ differences are greater between traits
-    \item How is the taxonomic hierarchy in the investigated datasets? 
-    % -> link to taxonomic hierarchy, many families have only a few genera
+    \item Differences greater for the NOA dataset because of the binary coding $\rightarrow$ differences are greater between traits
+    \item Taxonomic hierarchy in the investigated datasets? \\
+     $\rightarrow$ In every investigated dataset, most families have only one genus  
     % -> Similarly, many genera have only a few species
@@
 
-% 1) Trait aggr methods vs assigned traits:
-% - BK:
-%  All range from about 0 to 1 and all have mean values which fall within the error bars (stand dev) of the other methods. 
-% Figure 3, however, does suggest some differences in terms of range, with the methods which use median have narrow ranges.
-In terms of mean values perhaps more difference than for the Australian analysis but even still considering the +/- the error bars I think they all overlap.
-% It then becomes what to make of all this. Are the slight differences between the methods important or unimportant?
-% Also why the differences between the Australian and NA datasets?
-
-% Ben's Comment: -> But another issues is that these aggregation methods were being compared to traits assigned at the family level, which I understand was often done by expert opinion.
-So, these traits assigned at the family level may not be really “correct”!
-The difference between the trait aggregated to family and its designation at the family level could indicate: (a) the aggregation method is “no good”, (b) the trait assigned at the family level was “no good”, or (c) both a and b.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % 2) Influence of aggregation methods on trait-environment relationships: 
-% 
 % Harmonization: Minor influence on RDA species scores

### 2020-10-23 Paper/Results/SI.tex
23.10.: Added caption for taxonomic hierarchy graphs

@@
     \label{fig:sim_indv_runs}
+\end{figure}
+
+\subsubsection*{Taxonomic hierarchy in the analysed trait datasets}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_EU.png}
+    \caption{Number of genera per family and species per genus for the European trait dataset. For better visual display only families with more than 10 genera are displayed.}
+    \label{fig:tax_hierarchy_EU}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NOA.png}
+    \caption{Number of genera per family and species per genus for the North American trait dataset. For better visual display only families with more than 15 genera are displayed.}
+    \label{fig:tax_hierarchy_NOA}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_AUS.png}
+    \caption{Number of genera per family and species per genus for the Australian trait dataset. For better visual display only families with more than 7 genera are displayed.}
+    \label{fig:tax_hierarchy_AUS}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NZ.png}
+    \caption{Number of genera per family and species per genus for the New Zealand trait dataset. For better visual display only families with more than 5 genera are displayed.}
+    \label{fig:tax_hierarchy_NZ}
 \end{figure}

### 2020-10-25 Paper/Results/Results_trait_harmonization.tex
Removed comments and moved to overleaf review section
25.10: Minor updates

@@
 For every aggregation method compared, using at family-level aggregated traits did only slightly change the species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}).
-% Hence, the interpretation of the trait composition is the same as when only using harmonized grouping features. 
-%? Mention that threshold according to mahalanobis distance is almost reached for life cycle duration
 
-% Species scores
 \begin{figure}[H]
@@
     \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
-    \caption{Species scores obtained by RDA from the original analysis \cite{szocs_effects_2014}, using harmonized grouping features, and using harmonized grouping features with assigned trait affinities aggregated to family-level.}
+    \caption{Species scores obtained by RDA from the original analysis \cite{szocs_effects_2014}, using harmonized grouping features, and using harmonized grouping features with trait affinities aggregated to family-level.}
     \label{fig:rda_species_scores}
@@
 
-% PUP comment: 
-% What are exactly „RDA species scores“? The coordinates of species along the first factorial axis in RDA?
-% If „yes“, I’m not sure this result presentation is suitable.
-In fact the box-plots summarizing the distributions of the set of species in the RDA analysis, after applying different strategies of trait description, can be very similar (it’s not surprising, because in each case the mean coordinate of species is 0), but the individual locations of species along each axis can be very different from an RDA to another axis (i.e.
-from a grouping feature definition strategy to another).
-It would be probably far more interesting to represent the distribution of deviations between the RDA scores provided by each strategy and the original RDA scores (from Szöcs et al., 2018)..
-
 \end{document}

### 2020-10-28 Paper/Draft_harmonization_paper.tex
25.10: Minor updates
28.10: Changes before send to Ralf

@@
 Thus, we use the term grouping feature in place of which many studies use the term "trait", and the term trait instead of "trait state", "modality" or "trait category".
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % TODO: Description of affinity
-% A trait can described using a binary coding (exists or not), or using affinity scores that indicate the which extent an organism expresses a certain trait.  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 To our knowledge, only Brown et al.
 \cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
-% TODO: ?Paper trait convergence Doledec
 
@@
 Secondly, consistent coding of traits facilitates the compatibility of trait data from different databases.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Alternative from Ben:
@@
 III) Aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
-This method weights the genera according to the number of their species in the trait datasets regardless if for every used grouping feature information was available.
+This method weights the genera according to the number of their species in the trait datasets regardless if for every used grouping feature information was available (Figure \ref{fig:data_proc_overview}).
 
@@
 Abbreviations: EU: Europe, NOA: North America, AUS: Australia, NZ: New Zealand, DB: Database.}
+  \label{fig:data_proc_overview}
 \end{figure}
@@
     \item Taxonomic hierarchy in the investigated datasets? \\
-     $\rightarrow$ In every investigated dataset, most families have only one genus  
-    % -> Similarly, many genera have only a few species
-    % -> linear relationship: the more genus per family, the more species (although there are exceptions -> e.g. Europe)
-    \item There is no "true" value to compare to, i.e. assigned traits can be biased. Comparison of species-lvl traits in fwe and traits on genus-lvl in tachet would be interesting in this context? 
+     $\rightarrow$ In every investigated dataset families have only 1 to few genera. 76 (North America) to 93 \% (New Zealand) of the families have 5 or less genera (see SI). 
+    \item There is no "true" value to compare to, i.e.
+assigned traits at genus or family level can be biased as well (i.e.
+the person who assigned the trait was thinking about particular species within a genus not all).
+Comparison of species-level traits in fwe and traits on genus-level in tachet would be interesting in this context?
     \item  Suggestions from Co-Authors: \\

### 2020-11-01 R/01_EU_preprocess_new.R
01.11: Put sp. in species column, assigned sp. data to new sp.

@@ -13,7 +13,7 @@ trait_EU <- readRDS(
 
 # Subset to relevant traits
 trait_EU <- trait_EU[, .SD,
-  .SDcols = names(trait_EU) %like% "^order$|^family$|genus|species|taxon.*|feed|loco|resp|volt|rep|size"
+  .SDcols = names(trait_EU) %like% "^order$|^family$|genus|species|taxon.*|feed|loco|resp|volt|rep|size|ID.*"
 ]
 
 # Voltinism trait contains thermal conditions, change every string to 1
@@ -24,9 +24,8 @@ trait_EU[, (col) := lapply(.SD, function(y) {
   ifelse(!is.na(y), 1, NA)
 }), .SDcols = col]
 
-
 # get trait columns and transform all to numeric
-col <- grep("order|family|genus|species|taxon.*",
+col <- grep("order|family|genus|species|taxon.*|ID.*",
   names(trait_EU),
   value = TRUE,
   invert = TRUE
@@ -47,6 +46,10 @@ trait_EU <- trait_EU[!pos, ]
 
 # __________________________________
 #### Consolidate duplicate taxa ####
+# only for family-level
+# species and genus duplicates have been introduced in the past
+# by rm e.g. "new Gen. sp." from some species
+# has not been done now
 # __________________________________
 
 # binary columns -> aggr via max
@@ -56,59 +59,59 @@ cols_bin <- grep("(?=volt.*|resp.*)(?!.*tachet)",
                  value = TRUE,
                  perl = TRUE
 )  
-cols_fuzzy <- grep("(?=volt.*|resp.*|species|genus|family|order|taxon.*)(?!.*tachet)",
+cols_fuzzy <- grep("(?=volt.*|resp.*|species|genus|family|order|taxon.*|ID.*)(?!.*tachet)",
                    names(trait_EU),
                    value = TRUE,
                    invert = TRUE,
                    perl = TRUE
 )
 
-
 # - aggr. duplicated species:
-dupl_species <- trait_EU[!is.na(species), ] %>%
-  .[duplicated(species) | duplicated(species, fromLast = TRUE), species] %>%
-  .[duplicated(.)]
-# agg via median except voltinism
-trait_EU[species %in% dupl_species,
-  (cols_fuzzy) := lapply(.SD, median, na.rm = TRUE),
[…]

### 2020-11-01 R/02_EU_harmonize_new.R

@@ -19,7 +19,8 @@ Trait_EU <- cbind(
       "genus",
       "family",
       "order",
-      "taxon_cp"
+      "taxon_cp",
+      "ID_AQEM"
     )
   ),
   normalize_by_rowSum(Trait_EU[, ..tachet_cols])
@@ -133,9 +134,6 @@ normalize_by_rowSum(
 
 # new taxa col for trait EU
 Trait_EU[, taxa := coalesce(species, genus, family, order)]
-
-# create also unique_id col for merges later on
-Trait_EU[, unique_id := 1:nrow(Trait_EU)]
 
 # merge PUP comments
 Trait_EU[piercer_pup,
@@ -255,7 +253,7 @@ Trait_EU_piercer <-
     feed_predator_tachet,
     feed_parasite_tachet,
     feed_scraper_tachet,
-    unique_id
+    ID_AQEM
   )])
 
 Trait_EU_piercer[lookup_piercer,
@@ -274,7 +272,7 @@ Trait_EU[Trait_EU_piercer,
     feed_parasite_tachet = i.feed_parasite_tachet,
     feed_scraper_tachet = i.feed_scraper_tachet
   ),
-  on = "unique_id"
+  on = "ID_AQEM"
 ]
 
 # manual assignment for few species
@@ -651,7 +649,6 @@ body_form_pup[, (cols) := lapply(.SD, function(y) {
 # subset to EU data
 bf_EU <- body_form_pup[grepl("EU.*", array), ]
 
-
 # merge on species-level
 Trait_EU[bf_EU[!is.na(species), ],
   `:=`(
@@ -681,7 +678,7 @@ Trait_EU[Trait_subset,
     bf_cylindrical = i.bf_cylindrical,
     bf_streamlined = i.bf_streamlined
   ),
-  on = "unique_id"
+  on = "ID_AQEM"
 ]
 
 # _________________________________________________________________________
@@ -768,7 +765,7 @@ normalize_by_rowSum(
     "family",
     "genus",
     "species",
-    "unique_id",
+    "ID_AQEM",
     "taxon_cp",
     "taxa"
   )
@@ -782,7 +779,7 @@ newcolorder <- c(
   "order",
   "taxon_cp",
   "taxa",
-  "unique_id",
+  "ID_AQEM",
   grep("feed", names(Trait_EU), value = TRUE),
   grep("resp", names(Trait_EU), value = TRUE),
   grep("volt", names(Trait_EU), value = TRUE),
[…]

### 2020-11-01 R/Preprocessing_raw/01_preprocess_new_freshecol_2020.R

@@ -1,4 +1,3 @@
-
 #### read taxaexports ####
 filelinks <- list.files(
   path = data_raw,
@@ -45,11 +44,11 @@ freshwaterecol <- Reduce(f = cbind, output_db)
 setnames(freshwaterecol, "V1", "taxon")
 freshwaterecol[, EU := NULL]
 
-# -add AQEM codes:
+# - add AQEM codes:
 aqem_path <- file.path(data_raw, "AQEM.csv")
 ind <- grep("Taxon", readLines(aqem_path))
 
-# read in
+# read in aqem
 aqem <- fread(aqem_path,
               skip = ind,
               sep = ";",

### 2020-11-01 R/Preprocessing_raw/02_preprocess_new_freshecol_taxa.R

@@ -29,7 +29,7 @@ freshwaterecol[
 freshwaterecol[, order_or_higher := copy_till_next_occur(x = order_or_higher)]
 
 # - sort out all taxa with zero information
-trait_cols <- grep("taxon.*|EU|genus|family|order.*",
+trait_cols <- grep("taxon.*|EU|genus|family|order.*|ID_AQEM",
   names(freshwaterecol),
   value = TRUE,
   invert = TRUE
@@ -43,9 +43,8 @@ no_info <- freshwaterecol[, apply(.SD, 1, function(y) {
 pos <- no_info == ncol(freshwaterecol[, ..trait_cols])
 freshwaterecol <- freshwaterecol[!pos, ]
 
-# - Add gen. sp with endign dae/nae/ini to family column
+# - Add gen. sp with ending dae/nae/ini to family column
 # or subfamily column
-# delete the rest frp, genus col
 freshwaterecol[grep(".*dae.*Gen\\..+", taxon), `:=`(
   family = taxon,
   taxon = NA_character_
@@ -57,60 +56,40 @@ freshwaterecol[grep("(?i).*ini Gen\\. sp\\.|.*nae Gen\\. sp\\.", taxon), `:=`(
 freshwaterecol[grep("Gen\\. sp\\.", taxon), taxon := NA_character_]
 
 # - Proceed with creating genus col
-# everything with sp. to genus column
-freshwaterecol[
-  grep("(?!.*ssp\\.)(?=[[:space:]]sp\\.)", taxon, perl = TRUE),
-  `:=`(
-    genus = taxon,
-    taxon = NA_character_
-  )
-]
+# add genera from first name of species col
+# leave sp. into species col
+freshwaterecol[!is.na(taxon), genus := sub("([A-z]{1,})([[:space:]])(.*)", "\\1", taxon)]
 
-# - add genera from first name of species col
-freshwaterecol[
-  !is.na(taxon),
-  genus := sub(
-    "([A-z]{1,})([[:space:]])(.+)",
-    "\\1", taxon
-  )
-]
+# new sp. GR are newly not yet in the studied area observed taxa
+# If no values assigned take values from corresponding sp.!
+target <- freshwaterecol[grepl("new sp\\. GR", taxon), sub("([A-z]{1,})([[:space:]])(sp\\.)(.*)", 
[…]

### 2020-11-01 R/Preprocessing_raw/03_preprocess_new_freshecol_taxa.R

@@ -51,8 +51,8 @@ taxa <- freshwaterecol[
   is.na(order_or_higher) & !is.na(family),
   family
 ] %>% unique()
-ID_gbif <- get_gbifid(taxa, rows = 1)
-saveRDS(ID_gbif, file = "./R/Preprocessing_raw/Cache/ID_gbif_family.rds")
+# ID_gbif <- get_gbifid(taxa, rows = 1)
+# saveRDS(ID_gbif, file = "./R/Preprocessing_raw/Cache/ID_gbif_family.rds")
 # ID_gbif <- readRDS(file = "./R/Preprocessing_raw/Cache/ID_gbif_family.rds")
 
 tax_classf <- classification(
@@ -68,18 +68,17 @@ tax_classf <- rbindlist(tax_classf, fill = TRUE)
 setDT(tax_classf)
 tax_classf[, "." := NULL]
 
-
 # for subfamilies
 # - first, take the genus (easier to find and match)
 taxa_subfamily <- freshwaterecol[!is.na(subfamily_or_tribe), genus] %>%
   unique()
-ID_subf_gbif <- get_gbifid(taxa_subfamily,
-  rows = 1
-)
-saveRDS(ID_subf_gbif,
-  file = "./R/Preprocessing_raw/Cache/ID_gbif_subfamily.rds"
-)
-# ID_subf_gbif <- readRDS(file = "./R/Preprocessing_raw/Cache/ID_gbif_subfamily.rds")
+# ID_subf_gbif <- get_gbifid(taxa_subfamily,
+#   rows = 1
+# )
+# saveRDS(ID_subf_gbif,
+#   file = "./R/Preprocessing_raw/Cache/ID_gbif_subfamily.rds"
+# )
+ID_subf_gbif <- readRDS(file = "./R/Preprocessing_raw/Cache/ID_gbif_subfamily.rds")
 
 taxa_subf_classf <- classification(
   id = ID_subf_gbif,
@@ -104,13 +103,13 @@ taxa_subf_2 <- freshwaterecol[
 ] %>%
   sub(" Gen\\. sp\\.", "", .) %>%
   unique()
-ID_subf2_gbif <- get_tsn(taxa_subf_2,
-  rows = 1
-)
-saveRDS(ID_subf2_gbif,
-  file = "./R/Preprocessing_raw/Cache/ID_gbif_subfamily_2.rds"
-)
[…]

### 2020-11-01 R/Preprocessing_raw/Set_up.R

@@ -1,10 +1,0 @@
-# link to raw data
-data_raw <- "./Data/EU/Raw_freshecol/2020"
-
-# packages
-library(data.table)
-library(dplyr)
-library(taxize)
-
-# script with helper functions
-source(file = "./R/Preprocessing_raw/functions_used.R")

### 2020-11-01 R/Run.R

@@ -2,17 +2,3 @@
 
 # Packages, paths and functions
 source("./R/Set_up.R")
-
-#### OLD ####
-
-# EU:
-# all scripts can be run separately 
-# preprocessing freshwaterecol (taxa)
-source("./R/01_EU_preprocessing_freshecol.R")
-
-# preprocessing & harmonizing tachet
-source("./R/02_EU_preprocessing_tachet.R")
-source("./R/02_01_EU_harmonize_tachet.R")
-
-# harmonisation freshecol & integration tachet
-source("./R/03_EU_harmonize_traits.R")

### 2020-11-01 R/Set_up.R

@@ -10,6 +10,7 @@ library(data.table)
 library(tidyr)
 library(readxl)
 library(zeallot)
+library(taxize)
 
 # taxonomical information
 # library(taxize)
@@ -29,7 +30,7 @@ data_cleaned <- "./Cleaned_data"
 # Path for data to fill missing values
 data_missing <- "./Missing_data"
 
-# data location for trait aggregation project
+# Data location for trait aggregation project
 data_aggr <- "/home/kunzst/Dokumente/Projects/Trait_DB/Trait-aggregation"
 
 # Path for output
@@ -38,6 +39,11 @@ data_out <- "./Output"
 # Location for R scripts
 data_scr <- "./R"
 
+# Link to raw data
+data_raw <- "./Data/EU/Raw_freshecol/2020"
 
 # source script with used functions
 source(file = file.path(data_scr, "functions_used_TDB.R"))
+
+# script with helper functions for preprocessing of raw data
+source(file = "./R/Preprocessing_raw/functions_used.R")

### 2020-11-02 R/01_EU_preprocess_new.R
02.11: Fixed taxa on genus-lvl, updated Run.R

@@ -83,8 +83,8 @@ cols_fuzzy <- grep("(?=volt.*|resp.*|species|genus|family|order|taxon.*|ID.*)(?!
 # ]
 # # rm duplicates
 # trait_EU <- trait_EU[!(!is.na(species) & duplicated(species)), ]
-# 
-# 
+ 
+
 # # aggr. duplicated genus
 # dupl_genus <- trait_EU[is.na(species) & !is.na(genus), ] %>%
 #   .[duplicated(genus) | duplicated(genus, fromLast = TRUE), genus] %>%

### 2020-11-02 R/02_EU_harmonize_new.R

@@ -6,7 +6,6 @@
 Trait_EU <-
   readRDS(file.path(data_cleaned, "EU", "Trait_freshecol_2020_pp_for_harm.rds"))
 
-
 # normalize freshecol & tachet separately
 tachet_cols <- grep("tachet.*", names(Trait_EU), value = TRUE)
 fc_cols <- grep("tachet.*", names(Trait_EU), value = TRUE, invert = TRUE)
@@ -134,6 +133,7 @@ normalize_by_rowSum(
 
 # new taxa col for trait EU
 Trait_EU[, taxa := coalesce(species, genus, family, order)]
+Trait_EU[, taxa_adjusted := sub(" sp\\.", "", taxa)]
 
 # merge PUP comments
 Trait_EU[piercer_pup,
@@ -148,7 +148,7 @@ Trait_EU[piercer_pup,
     feed_piercer_tachet = i.feed_piercer_t,
     comment_piercer = i.comment_piercer
   ),
-  on = "taxa"
+  on = c(taxa_adjusted = "taxa")
 ]
 
 # assign affinities from feed_piercer_tachet to
@@ -661,24 +661,14 @@ Trait_EU[bf_EU[!is.na(species), ],
 ]
 
 # merge on genus-level
-Trait_subset <- Trait_EU[is.na(species) & !is.na(genus), ]
-Trait_subset[bf_EU,
+Trait_EU[bf_EU,
   `:=`(
     bf_flattened = i.flattened,
     bf_spherical = i.spherical,
     bf_cylindrical = i.cylindrical,
     bf_streamlined = i.streamlined
   ),
-  on = "genus"
-]
-Trait_EU[Trait_subset,
-  `:=`(
-    bf_flattened = i.bf_flattened,
-    bf_spherical = i.bf_spherical,
-    bf_cylindrical = i.bf_cylindrical,
-    bf_streamlined = i.bf_streamlined
-  ),
-  on = "ID_AQEM"
+  on = c(taxa_adjusted = "genus")
 ]
 
 # _________________________________________________________________________

### 2020-11-02 R/Preprocessing_raw/02_preprocess_new_freshecol_taxa.R

@@ -56,24 +56,29 @@ freshwaterecol[grep("(?i).*ini Gen\\. sp\\.|.*nae Gen\\. sp\\.", taxon), `:=`(
 freshwaterecol[grep("Gen\\. sp\\.", taxon), taxon := NA_character_]
 
 # - Proceed with creating genus col
+# move sp. into genus col
+freshwaterecol[grepl("(?![[:space:]]ssp\\.)(?=[[:space:]]sp\\.)", taxon, perl = TRUE),
+               `:=`(genus = taxon,
+                    taxon = NA)]
+
 # add genera from first name of species col
-# leave sp. into species col
 freshwaterecol[!is.na(taxon), genus := sub("([A-z]{1,})([[:space:]])(.*)", "\\1", taxon)]
 
 # new sp. GR are newly not yet in the studied area observed taxa
 # If no values assigned take values from corresponding sp.!
-target <- freshwaterecol[grepl("new sp\\. GR", taxon), sub("([A-z]{1,})([[:space:]])(sp\\.)(.*)", 
-                                                           "\\1", taxon)]
+target <- freshwaterecol[grepl("new sp\\. GR", genus), sub("([A-z]{1,})([[:space:]])(sp\\.)(.*)", 
+                                                           "\\1", genus)]
 target <- target[!duplicated(target)]
 target <- paste(target, "sp\\.")
 
 for(sp_taxa in target){
-  assign <- freshwaterecol[taxon %like% sp_taxa, ][1, ..trait_cols]
-  freshwaterecol[taxon %like% sp_taxa, (trait_cols) := assign]
+  assign <- freshwaterecol[genus %like% sp_taxa, ][1, ..trait_cols]
+  freshwaterecol[genus %like% sp_taxa, (trait_cols) := assign]
 }
 
-# rm Lv. from taxa in taxon col
+# rm "Lv." from taxa names in taxon & genus col
 freshwaterecol[, taxon := sub(" Lv\\.", "", taxon)]
+freshwaterecol[, genus := sub(" Lv\\.", "", genus)]
 
 # - create species column from taxon column
 setnames(freshwaterecol, "taxon", "species")

### 2020-11-02 R/Preprocessing_raw/03_preprocess_new_freshecol_taxa.R

@@ -53,7 +53,7 @@ taxa <- freshwaterecol[
 ] %>% unique()
 # ID_gbif <- get_gbifid(taxa, rows = 1)
 # saveRDS(ID_gbif, file = "./R/Preprocessing_raw/Cache/ID_gbif_family.rds")
-# ID_gbif <- readRDS(file = "./R/Preprocessing_raw/Cache/ID_gbif_family.rds")
+ID_gbif <- readRDS(file = "./R/Preprocessing_raw/Cache/ID_gbif_family.rds")
 
 tax_classf <- classification(
   id = ID_gbif,
@@ -93,7 +93,6 @@ taxa_subf_classf <- lapply(taxa_subf_classf, function(y) {
 })
 taxa_subf_classf <- rbindlist(taxa_subf_classf, fill = TRUE)
 taxa_subf_classf[, "." := NULL]
-
 
 # subfamilies where no genus
 # information was available

### 2020-11-02 R/Run.R

@@ -1,4 +1,28 @@
+# ________________________________________________________________________________
 #### Run script ####
+# ________________________________________________________________________________
 
 # Packages, paths and functions
 source("./R/Set_up.R")
+
+# ________________________________________________________________________________
+#### preprocessing raw data ####
+# 03_preprocess_new_freshecol_taxa.R creates an .rds file which is
+# then used in the harmonization scripts
+# ________________________________________________________________________________
+
+# combine raw freshecol exports 
+# and change trait names
+source("./R/Preprocessing_raw/01_preprocess_new_freshecol_2020.R")
+
+# taxa cleaning and formation
+source("./R/Preprocessing_raw/02_preprocess_new_freshecol_taxa.R")
+
+# retrieving taxonomic information where missing and manual correction of some 
+# taxonomic entries
+source("./R/Preprocessing_raw/03_preprocess_new_freshecol_taxa.R")
+
+# ________________________________________________________________________________
+#### Harmonization scripts ####
+# an intermediate .rds file is created at the end of each script
+# ________________________________________________________________________________

### 2020-11-03 Paper/Results/Taxonomic_cov_and_info_compl.tex
03.11: Update Paper (EU trait data updated -> sp.)

@@
 
-Regarding the taxonomical coverage, the New Zealand dataset has, as expected, the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
-By contrast, the largest taxon pool is spanned by the European trait dataset with 4496 taxa followed by the North American trait dataset that contained trait information on 3753 taxa.
+Regarding the taxonomic coverage, the New Zealand dataset has, as expected, the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
+By contrast, the largest taxon pool is spanned by the European trait dataset with 4601 taxa followed by the North American trait dataset that contained trait information on 3753 taxa.
 The Australian dataset contains 1402 taxa.
@@
     \toprule[.1em]
-    EU & 4496 & 3691 (82) & 647 (14) & 158 (4) & 3838 (85) \\ 
+    EU & 4601 & 3739 (81) & 704 (15) & 158 (3) & 3942 (86) \\ 
     NOA & 3753 & 2414 (64) & 1163 (31) & 176 (5) & 3305 (88) \\ 
@@
     \toprule[.1em]
-    EU & 8 & 15 & 21 & 36 & 10 & 49 & 75 \\ 
+    EU & 8 & 15 & 23 & 36 & 11 & 57 & 76 \\ 
     NOA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 

### 2020-11-09 Paper/Draft_harmonization_paper.tex
09.11: Edit's Ralf

@@
 Species traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, might be beneficial in achieving this goal \cite{heino_jani_macroecological_2013}.
-Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism or a population to its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
+Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism or a population and its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
 Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than in taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
-Traits of freshwater invertebrate individuals are difficult to determine because - unlike plants - their traits often cannot be measured directly.
+Traits of freshwater invertebrate individuals are difficult to determine because - unlike plant traits - they often can not be measured directly.
 For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community \cite{moog_comprehensive_nodate}.
 Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
-by relating macroinvertebrate trait composition to environmental factors or as trait metrics in biomonitoring \cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}.
+by relating macroinvertebrate trait composition to environmental factors and as trait metrics in biomonitoring \cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}.
 
-In the last decades, freshwater ecologists developed comprehensive invertebrate trait databases for various continents \cite{usseglio-polatera_biomonitoring_2000, schmidt-kloiber_www.freshwaterecology.info_2015, vieira_database_nodate, Philips_and_Smith_NZ_DB_2018, kefford_integrated_2020, tomanova_trophic_2006}.
-The availability of invertebrate trait data from different continents enables comparisons of trait variation and their relation to environmental factors across large scales.
+In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases for various continents \cite{usseglio-polatera_biomonitoring_2000, schmidt-kloiber_www.freshwaterecology.info_2015, vieira_database_nodate, Philips_and_Smith_NZ_DB_2018, kefford_integrated_2020, tomanova_trophic_2006}.
+The availability of invertebrate trait data from different continents enables comparisons of trait variation and analyses of their relation to environmental factors across large scales.
 However, such analyses have been carried out mostly within continents, using information from one or two trait databases.
 For example, Bonada et al.
-\cite{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from the Usseglio-Polatera et al.
-\cite{usseglio-polatera_biomonitoring_2000}, Poff et al.
+\cite{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from Usseglio-Polatera et al.
+\cite{usseglio-polatera_biomonitoring_2000}(typically referred to as Tachet database); Poff et al.
 \cite{poff_developing_2010} characterized trait composition across sites in the Western US using traits from Poff et al.
@@
 Thus, we use the term grouping feature in place of which many studies use the term "trait", and the term trait instead of "trait state", "modality" or "trait category".
-% TODO: Description of affinity
+Traits can be described using different codings (binary, fuzzy) that represent the prevalence of a characteristic in an organism.
+% TODO: bring affinity/affinity scores in
 
 To our knowledge, only Brown et al.
-\cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
+\cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
 
@@
 % Alternative from Ben:
-Traits can be described in a binary fashion with no uncertainty how the trait is expressed in any particularly organism (e.g.
-adult terrestrial stage, presence of gills), continuous (e.g.
-tolerance of pollution, body size) or using multiple descriptions (e.g.
-feeding mode) with some uncertainty as to which trait the organism should be coded to.
-One approach for dealing with the uncertainty in the latter is the use of fuzzy coded variables.
+Traits can be described in a binary fashion, or with multiple categories, ignoring uncertainty how the trait is expressed in any particular organism (e.g.
+adult terrestrial stage, presence of gills) or continuous (e.g.
+tolerance of pollution, body size).
+One approach for dealing with uncertainty is the use of fuzzy coded variables, where the traits are assigned probabilistic values.
 Fuzzy codes are used to account for plasticity in traits, variability in traits within taxonomic groups above species, and incomplete knowledge and are usually converted to proportions.
+% TODO: add affinitiy scores here?
 
-However, invertebrate trait databases are heterogeneous regarding the coding they use for their traits \cite{culp_incorporating_2011} 
-%(Table \ref{tab:trait_databases_coding_differentiation}).
-% TODO: Don't use table 5 and maybe find another reference?
+However, invertebrate trait databases are heterogeneous regarding the coding they use for their traits \cite{culp_incorporating_2011}.
 Brown et al.
@@
 A centralized database with standardized and unambiguous traits and a consistent coding of traits would minimize data processing effort.
-Differing taxonomic resolutions (e.g.
-species, genus or family) between the observed taxa in a study and the used trait database is another challenge when working with trait data.
+Discrepancies in the taxonomic resolutions (e.g.
+species, genus or family) when linking observational taxonomic data to trait database represents another challenge.
 When observations are on a more precise taxonomic level than data available in the trait databases (e.g.
@@
 \cite{poff_functional_2006, szocs_effects_2014, piliere_a._f._h._importance_2016, aspin_extreme_2019}.
-Thereby, trait aggregation is often done using the mean \cite{magliozzi_functional_2019}, median \cite{szocs_effects_2014} or the mode \cite{piliere_a._f._h._importance_2016}.
+Studies have used different methods of trait aggregation, e.g.
+the mean \cite{magliozzi_functional_2019}, median \cite{szocs_effects_2014} or the mode \cite{piliere_a._f._h._importance_2016}.
 Up to now, studies on how and to which extent different trait aggregation methods influence trait-based analysis are missing.
-Knowing this can aid the choice of aggregation method for future studies.
+However, related knowledge would inform future studies regarding the choice of the aggregation method.
 
-We aimed to determine the influence of grouping feature harmonization and trait aggregation on trait-environment relationships.
-In particular, we aimed to (1) determine the effect of different harmonization methods using 4 invertebrate grouping feature datasets for seven grouping features from Europe, North America, New Zealand, and Australia.
+% TODO: clarify, see Ralf's comment
+% Add novel harmonised trait databases?
+We studied the influence of grouping feature harmonization and trait aggregation on trait-environment relationships.
+In particular, we aimed to (1) determine the effect of different harmonization methods using 4 invertebrate trait database for 7 grouping features from Europe, North America, New Zealand, and Australia.
 Furthermore, we (2) compared trait affinities obtained through different trait aggregation methods to trait affinities assigned at family-level by experts.
@@
 \cite{vieira_database_nodate}.
-Data on body form for European and North American taxa was provided based on expert knowledge \cite{polatera_personal_information_2020}.
+Data on body form for European and North American taxa was based on expert knowledge \cite{polatera_personal_information_2020}.
 For Australia and New Zealand, we used trait databases from Kefford et al.
 \cite{kefford_integrated_2020} and Philips and Smith respectively \cite{Philips_and_Smith_NZ_DB_2018}.
-To increase readability we refer to the databases as well as the datasets we extracted from them by the name of the continent they originate from.
-Excluded from this are the European databases, which we refer to by their commonly used names (freshwaterecology.info and Tachet database).
+To increase readability we refer to the databases as well as the datasets we extracted from them by the name of the continent they originate from, except for European databases, which we refer to by their commonly used names (freshwaterecology.info and Tachet database).
 
-We selected traits of seven grouping features that were available in all databases, are commonly used, and describe different parts of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
+We selected traits of seven grouping features that were available in all databases, are commonly applied in trait-based ecological studies, and describe different parts of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
 We omitted ecological traits that describe habitat preferences (e.g.
@@
 categorical and continuous traits were converted into binary traits.
-For example, in the  freshwaterecology.info database taxa were classified according to different floristic regions for the trait voltinism.
-Hence, the entries of the voltinism traits such as "arctic" or "boreal" were substituted with a value of 1.
-Implicitly, we assumed for binary traits that a value of 1 corresponds to the highest affinity for a particular trait and 0 to no affinity for a particular trait.
+For example, in the  freshwaterecology.info database, the classification of the trait voltinism accounts for different faunistic regions.
+Hence, the entries such as "arctic" or "boreal" of the e.g.
+the trait univoltine were substituted with a value of 1.
+Implicitly, we assumed for binary traits that a value of 1 and 0 corresponds to the highest and no affinity for a particular trait.
 Fuzzy codes are reported with different ranges in the trait databases (e.g.
 freshwaterecology.info 0 to 10, Tachet database 0 to 3 or 0 to 5).
-We standardized them to a range between 0 and 1 and converted trait affinities to percentages.
+We standardized these to a range between 0 and 1 and converted trait affinities to percentages.
 Thus, fuzzy coded and binary traits were in the same range.
@@
 Prior to harmonization we consolidated duplicate taxa on species, genus or family-level if present within a dataset, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
-We omitted taxa with a less precise taxonomic resolution than family-level.
+We omitted taxa with a lower taxonomic precision than family-level.
 
@@
 \midrule
-Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattend, dorsoventrally flattened \textsuperscript{\textit{a}}\\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
+Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattenend, dorsoventrally flattened \textsuperscript{\textit{a}}\\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
 \midrule
@@
 \midrule
-Locomotion   & \begin{tabular}[c]{@{}l@{}}Burrower\\ Crawler\\ Sessil\\ Swimmer \end{tabular}                                     & \begin{tabular}[c]{@{}l@{}}Interstitial, boring, burrowing\\ Sprawler, walking, climber, clinger, crawler\\ Attached, sessil\\ Skating, diving, planctonic, swimming\end{tabular}                                                                                                                 \\
+Locomotion   & \begin{tabular}[c]{@{}l@{}}Burrower\\ Crawler\\ Sessile\\ Swimmer \end{tabular}                                     & \begin{tabular}[c]{@{}l@{}}Interstitial, boring, burrowing\\ Sprawler, walking, climber, clinger, crawler\\ Attached, sessile\\ Skating, diving, planctonic, swimming\end{tabular}                                                                                                                 \\
 \midrule
@@
 1) A family with an equal number of genera and species (5 genera each with 5 species respectively), denoted as \textit{sim\_base}.
-2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively), denotes as \textit{sim\_extreme}. 
-3) A family where all genera have a different number of species (8, 2, 7, 3, 5), denotes as \textit{sim\_variation}.
+2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively), denoted as \textit{sim\_extreme}. 
+3) A family where all genera have a different number of species (8, 2, 7, 3, 5), denoted as \textit{sim\_variation}.
 In total every family consisted of 25 species.
@@
 
-The data processing and aforementioned analysis were carried out using R (Version 3.6.1 and 4.0.3).
+The data processing and aforementioned analyses were carried out using R (Version 3.6.1).
 Raw data and the R code for data processing and grouping feature harmonization is located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
@@
 
+% Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
+I wonder if this indicates that Family richness is really higher in Australia.
+Perhaps it might be as Australia has a wider range of evolutionary histories.
+This would be worth considering in the discussion
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-11-09 Paper/Results/Results_trait_harmonization.tex
09.11: Edit's Ralf

@@
 
-Overall, using the harmonized grouping features led to only slightly different results in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and SI).
-According to the RDA of the trait composition, sites with high salinity were characterized by families that possess the traits multivoltinism, ovoviviparity, gill-respiration, and feeding mode shredder.
-Only families with the trait life cycle duration $> 1$ year failed to characterize sites with high salinization.
-Also, life cycle duration $<= 1$ year did not characterise sites not impacted by salinity.
-Like in the original analysis, transition and upstream sites from the point source were characterised by univoltine taxa and taxa that lay their eggs in aquatic environments.
-We also constructed the linear models of the original analyses, using the traits on the extremes of the conductivity axis and found results similar to the original analyses (Table S\ref{stab:linear_models_new} and S\ref{stab:linear_models_edi}).
+The original RDA in Szöcs et al.
+(\cite{szocs_effects_2014}) indicated that downstream sites (high salinity) were characterized by the traits feeding mode shredder, ovoviviparity, multivoltinism, long life cycle ($> 1$ year), and gill respiration and upstream sites (low salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
+Using harmonized grouping features led to slightly different results in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and SI).
+According to the RDA of the trait composition, downstream sites were characterized by taxa that possess the traits multivoltinism and ovoviviparity and upstream sites were characterized by univoltine taxa that lay their eggs in an aquatic environment.
+The traits shredder, gill respiration and long life cycle duration did not anymore characterize sites with high salinisation.
+Also, the trait short life cycle duration year did not characterise sites upstream sites with low salinity.% TODO: two graphics in one in the results part
+We also constructed the linear models of the original analyses, using the traits on bith extremes of the conductivity axis and found results similar to the original analyses (Table S\ref{stab:linear_models_new} and S\ref{stab:linear_models_edi}).
 
-For every aggregation method compared, using at family-level aggregated traits did only slightly change the species scores compared to not aggregated traits (Figure \ref{fig:rda_species_scores}).
+Results changed slightly when comparing at family-level aggregated traits to the original analysis. (Figure \ref{fig:rda_species_scores}). 
+% Weighted, direct_agg (mean) and direct_agg (median) similar
+% In addition to the results of harmonized: + gil respiration, long life cycle duration
+% Short life cycle duration for upstream sites
+
+% Stepwise_agg (mean), stepwise_agg (median) similar 
+% In addition to the results of harmonized: + resp_gil
+
+% In our comparison the family-level aggregation yielded to the least change in species scores of all methods.
 

### 2020-11-09 Paper/Results/Taxonomic_cov_and_info_compl.tex
09.11: Edit's Ralf

@@
 
-Regarding the taxonomic coverage, the New Zealand dataset has, as expected, the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
-By contrast, the largest taxon pool is spanned by the European trait dataset with 4601 taxa followed by the North American trait dataset that contained trait information on 3753 taxa.
+Regarding the taxonomic coverage, the New Zealand dataset has the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
+By contrast, the European trait dataset has the largest taxon pool with 4601 taxa followed by the North American trait dataset that contained trait information on 3753 taxa.
 The Australian dataset contains 1402 taxa.
-The European, New Zealand, and North American datasets have most taxa on the species-level while the Australian dataset has a similar number of taxa on species and genus-level.
+The European, New Zealand, and North American datasets have most taxa on the species-level whereas the Australian dataset has a similar number of taxa on species and genus-level.
 

### 2020-11-11 Paper/Draft_harmonization_paper.tex
11.11: Paper Update text

@@
 \usepackage{tikz}
+\usepackage{rotating}
 % \graphicspath{{/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures/}}
@@
 Hence, in total 12500 ($25 * 5 * 100$) trait affinities were simulated.
-All trait aggregation methods were applied to each simulated dataset and the results were compared.
+All trait aggregation methods were applied to each simulated dataset.
+The results were compared based on the produced range of aggregated trait affinities between levels of trait variability and hypothetical taxonomic hierarchies.
+We also compared for each simulated dataset the differences in trait affinities obtained by each aggregation method.
 
@@
 \subsection*{Comparison of family-level aggregated traits with family-level assigned traits}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 the coordinates of the tips of the vectors representing the CWM traits in the bi- or triplots.
+Following the original study, we identified traits associated with high or low salinity based on their distance to the ordination axis median using the mahalanobis distance.
+Traits with a mahalanobis distance greater than the $97.5 \%$ -quantile of the Chi-square distribution (5.02) were regarded as traits responding to either low or high salinity.
 For our analysis, we used the same 21 grouping features that Szöcs et al.
@@
 
-%! Completeness of trait information and taxonomical coverage
-\subfile{Results/Taxonomic_cov_and_info_compl}
+\subsection*{Taxonomic coverage of the harmonized trait datasets}
+
+Regarding the taxonomic coverage, the New Zealand dataset has the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
+By contrast, the European trait dataset has the largest taxon pool with 4601 taxa followed by the North American trait dataset that contained trait information on 3753 taxa.
+The Australian dataset contains 1402 taxa.
+The European, New Zealand, and North American datasets have most taxa on the species-level whereas the Australian dataset has a similar number of taxa on species and genus-level.
+
+\begin{table}[ht]
+    \centering
+    \caption{Number of taxa per harmonized dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percentage.} 
+    \label{tab:tax_coverage}
+    \begin{tabular}{lccccc}
+    \toprule[.1em]
+    Database & Nr. of taxa & Species & Genus & Family & Nr. aquatic insects \\ 
+    \toprule[.1em]
+    EU & 4601 & 3739 (81) & 704 (15) & 158 (3) & 3942 (86) \\ 
+    NOA & 3753 & 2414 (64) & 1163 (31) & 176 (5) & 3305 (88) \\ 
+    AUS & 1402 & 564 (40) & 578 (41) & 260 (19) & 1016 (72) \\ 
+    NZ & 478 & 404 (85) & 47 (10) & 27 (6) & 443 (93) \\ 
+    \bottomrule
+    \end{tabular}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Completeness of trait information}
+
+The amount of entries with available information for the selected grouping features varied strongly for the preprocessed European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
+By contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
+
+\begin{table}[ht]
+    \centering
+    \caption{Rounded percentage of entries that have 
+    information for the individual grouping features
+    shown per trait dataset.} 
+    \label{tab:trait_coverage}
+    \begin{tabular}{lccccccc}
+    \toprule[.1em]
+    Database & Body form & Oviposition & Voltinism & Locomotion & Size & Respiration & Feeding mode \\ 
+    \toprule[.1em]
+    EU & 8 & 15 & 23 & 36 & 11 & 57 & 76 \\ 
+    NOA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
+    AUS & 4 & 46 & 49 & 39 & 75 & 68 & 99 \\ 
+    NZ & 100 & 94 & 100 & 99 & 100 & 100 & 99 \\ 
+    \bottomrule
+    \end{tabular}
+\end{table}
 
 \newpage
-%! Comparison of trait aggregation methods
-\subfile{Results/Results_trait_agg}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Simulation of varying taxonomic hierarchies}
+
+We evaluate the simulation results based on the range of produced aggregated trait affinities and by comparing results of every simulated dataset.
+
+% range base simulation
+The trait aggregation methods \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}} and \textit{weighted\_agg} yielded similar ranges of aggregated trait affinities within each level of trait variability for the \textit{sim\_base} scenario.
+
+Aggregation methods using the median yielded greater ranges of aggregated trait affinities than methods using the mean.
+Thereby, the \textit(stepwise\_agg \textsubscript{median}) yielded the greatest range of aggregated trait affinities (Figure S\ref{fig:overview_sim_results}).
+
+% Other simulation scenarios
+By contrast, the ranges of trait affinities differed for all aggregation methods for the simulation scenarios \textit{sim\_extreme} and \textit{sim\_variation}.
+\textit{Weighted\_agg} and \textit{stepwise\_agg\textsubscript{mean}} produced a wider range of values than the \textit{direct\_agg\textsubscript{mean}} in the \textit{sim\_extreme} scenario.
+For most levels of trait variability the \textit{stepwise\_agg \textsubscript{median}} resulted in the largest range of trait affinities in both scenarios
+
+Analysing the individual simulation runs showed that differences between the results of the aggregation methods increased with increasing trait variability.
+Most differences occurred for the \textit{sim\_extreme} scenario.
+Differences greater than an absolute trait affinity of 0.1 occurred between methods using the median and the mean.
+Thereby, the most frequent differences above 0.1 were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure S\ref{fig:sim_indv_runs}).
+
+% TODO: What's good and what's bad -> that's maybe the wrong question, but what's the direction of each method? 
+% Overall,
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
+  \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
+Boxplots depict results for each trait aggregation method of 100 simulations.
+T1, T2, and T3 are the simulated traits.}
+  \label{fig:overview_sim_results}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
+  \caption{Comparison of the results of the trait aggregation methods for every simulated dataset.
+Simulated datasets where absolute differences between aggregated trait affinities were greater than 0.1 are depicted.
+Only the comparisons are shown were differences greater than 0.1 occurred.}
+  \label{fig:sim_indv_runs}
+\end{figure}
+
+\subsection*{Differences in trait affinities obtained by trait aggregation methods compared to traits assigned at family-level}
+\label{sec:diff_trait_agg_chessman}
+
+The percentage of differing cases of trait affinities obtained by the trait aggregation methods compared to trait affinities originally assigned at family-level varied between 16.2 \% and 22.9 \% for the Australian dataset.
+For the North American dataset, comparison of the trait aggregation methods to trait affinities assigned at family-level yielded between 15.3 \% and 47 \% differing cases (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
+
+In general, trait aggregation methods using the median yielded fewer cases with differences compared to approaches using the mean.
+However, aggregation methods using the median produced greater differences for both datasets.
+Standard deviations of absolute differences were similar for all tested aggregation methods.
+For both datasets maximum differences of 1 occurred for all investigated grouping features (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
+
+A comparison of the aggregation methods with each other for the 4 datasets revealed that differences in aggregated trait affinities were largest between the \textit{stepwise\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{median}} (Figure S\ref{fig:comp_aggr_methods}).
+
+\begin{table}[H]
+  \centering
+  \caption{Amount of differing cases, the minimum and maximum, and means and standard deviations of absolute differences between trait affinities assigned at family-level and aggregated trait affinities.}
+  \label{tab:summary_stat_aggr_vs_fam_assigned}
+  \begin{tabular}{ll|ccccc}
+  \toprule[.1em]
+  Database & \specialcell{Comparison to\\ traits at fam.-lvl.} & \specialcell{Differing \\ cases [\%]} & \specialcell{Min.
+\\ differences} & \specialcell{Max.
+\\ differences} & \specialcell{Mean abs.
+\\ differences} & \specialcell{SD abs.
+\\ differences} \\
+  \toprule[.1em]
+  \multirow{4}{*}{\specialcell{Australia \\ (Chessman)}} & \specialcell{direct\_agg (median)} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
+  & \specialcell{direct\_agg (mean)} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
+  & \specialcell{stepwise\_agg (median)} & 17.90 & 0.01 & 1.00 & 0.42 & 0.26 \\ 
+  & \specialcell{stepwise\_agg (mean)} & 23.24 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
+  & \specialcell{weighted\_agg} & 23.24 & $< 0.01$ & 1.00 & 0.34 & 0.24 \\ 
+  \midrule
+  \multirow{4}{*}{\specialcell{North America}} & \specialcell{direct\_agg (median)} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
+  & \specialcell{direct\_agg (mean)} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
+  & \specialcell{stepwise\_agg (median)} & 18.00 & 0.08 & 1.00 & 0.63 & 0.28 \\ 
+  & \specialcell{stepwise\_agg (mean)} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.27 \\ 
+  & \specialcell{weighted\_agg} & 47.00 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
+  \bottomrule
+  \end{tabular}
+\end{table}
 
 \newpage
-%! Presenting results of trait analysis using harmonized traits:
-\subfile{Results/Results_trait_harmonization}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_chessman.png}
+  \caption{Display of the cases where differences occurred between aggregated traits and traits assigned at family-level.
+Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the Australian dataset for the grouping features feeding mode and body size.
+Absolute differences in trait affinities are depicted as gray dots.
+N denotes the number of cases per comparison where differences occurred.
+The blue dot indicates the mean of absolute differences and the error bars the standard deviation.
+The gray vertical lines show the 25th, 50th and 75th quantile of the density estimate.}
+  \label{fig:diff_aggr_traits_chessman}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_pyne.png}
+  \caption{Display of the cases where differences occurred between aggregated traits and traits assigned at family-level.
+Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
+Absolute differences in trait affinities are depicted as gray dots.
+N denotes the number of cases per comparison where differences occurred.
+The black dot indicates the mean of absolute differences and the error bars the standard deviation.
+The gray vertical lines show the 25th, 50th and 75th quantile of the density estimate.}
+  \label{fig:diff_aggr_traits_pyne}
+\end{figure}
 
 \newpage
-%! Discrepancies in trait definitions
-\subfile{Trait_def_table/Trait_definitions_table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Re-analysis of Szöcs et al. using harmonized and aggregated grouping features}
+
+The original RDA in Szöcs et al.
+\cite{szocs_effects_2014} indicated that downstream sites (high salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle ($> 1$ year), and gill respiration and upstream sites (low salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
+
+Using harmonized grouping features resulted in fewer traits that distinguish upstream and downstream sites in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+According to the RDA of the trait composition, downstream sites were characterised by taxa with the traits multivoltinism and ovoviviparity and upstream sites were characterised by univoltine taxa that lay their eggs in an aquatic environment (aquatic eggs).
+The traits shredder, gill respiration and long life cycle duration did not characterise sites with high salinisation.
+Also, the trait short life cycle duration did not characterise upstream sites with low salinity.
+
+Using at family-level aggregated traits from the harmonized dataset showed results similar to the original analysis (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg}
+characterised the downstream sites with the same traits as the original analysis except that downstream sites were not characterised by the trait shredder.
+Upstream sites were characterised by the traits univoltinism, aquatic eggs and short life cycle duration.
+The trait aquatic eggs of the harmonized grouping feature oviposition has been derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonization}).
+The same results were obtained when re-analysing the data with traits aggregated by the \textit{stepwise\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, with the exception that none of the life cycle traits characterised upstream or downstream sites.
+Thus, in our comparison the direct and weighted family-level aggregation methods yielded to the least change in species scores of all methods compared to the original results.
+
+\begin{figure}[H]
+    \label{fig:rda_species_scores}
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
+    \caption{Species scores obtained by RDA from the original analysis \cite{szocs_effects_2014}, using harmonized grouping features, and using harmonized grouping features with traits aggregated to family-level.
+The dots represent the individual species scores for each analysed trait.
+The violin plot shows the density estimate of the species scores.
+Gray vertical lines indicate the median of the obtained species scores.}
+\end{figure}
+
+\begin{sidewaysfigure}
+  \label{fig:boxplots_scores_on_constrained_axis}
+  \centering
+  \includegraphics[width= 22cm, height=12cm]{Scores_on_constrained_axis_combined.pdf}
+  \caption{RDA of traits constrained by electric conductivity for the tested methods and the original study.
+Shown are boxplots of the site scores along the conductivity axis.
+The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
+Only traits with a mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.}
+\end{sidewaysfigure}
+
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Discrepancies of invertebrate trait definitions}
+
+Definitions of grouping features and traits varied in their level of detail in the original trait databases.
+The freshwaterecology.info database, the Tachet database and the North American database (Twardochleb et al.) provided more detailed descriptions of their trait information compared to the North American (Vieira et al.) and New Zealand database.
+An exception is the Australian trait database which is a collection of seven specific trait datasets \cite{kefford_integrated_2020}.
+Thus, grouping features occur multiple times with varying differentiation into traits.
+Depending on the dataset trait information is described with more or less detail.
+
+The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope.
+We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{stab:trait_definitions}).
+Both, differences in differentiation and scope can lead to discrepancies in trait definitions.
+For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways.
+The Tachet database defines predators as carvers, engulfers and swallowers.
+By contrast, in the North American (Twardochleb et al.) database predators are defined as engulfers and carnivorous piercers.
+In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers.
+Furthermore, the scope in the freshwaterecology.info database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition.
+Therefore, the freshwaterecology.info database defines e.g.
+predator as "eating from prey", while the other databases use the mouthpart morphology as basis of their definition.
+The Tachet database captures the food source in an additional grouping feature.
+Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{stab:trait_definitions}).
+Locomotion definitions differ also in scope between databases.
+Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the North American (Vieira et al.) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb et al.) database includes not only the way of movement, but also the location of movement.
+Similarly, regarding the reproduction traits, databases differ in their scope.
+Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases.
+North America (Vieira et al.) provides information on the oviposition location but not on reproductive behavior.
+The Australian database report traits for reproductive behavior but also on oviposition site.
+The New Zealand database distinguishes three grouping features related to reproduction: reproductive technique, oviposition site (e.g.
+water surface, terrestrial), and egg/egg mass (e.g.
+free, cemented).
+
+Various codings of traits are used throughout the databases (e.g.
+binary, fuzzy, continuous).
+The freshwaterecology.info and Australian use different codings in their databases.
+Tachet and the New Zealand database exclusively use fuzzy coding.
+Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
+Binary coding represents a simple approach in which a taxon either expresses a trait or not.
+Fuzzy coding characterizes the affinity of an organism to exert a certain trait.
+It is used to account for plasticity in traits, e.g.
+taking into account that traits can change over the development time of an organism.
+Usually, fuzzy coded affinities are converted into proportional values.
+Continuous coding is used for traits like body size.
+% Last sentences are a bit redundant
+
+% None of the seven grouping features compared here has the same differentiation of traits across all databases (Table \ref{tab:trait_databases})
+\begin{landscape}
+    \begin{longtable}{m{2.5cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
+    \caption{Number of traits per grouping feature and type of coding of the traits for the respective grouping feature per database.}
+    \endfirsthead
+    \toprule[.1em]
+    \label{tab:trait_databases_coding_differentiation}
+    Database & Feeding Mode & Voltinism & Locomotion & Respiration & Reproduction & Size & Body Form \\ 
+    \toprule[.1em]
+    \multirow{2}{*}[-5mm]{ \specialcell{Freshwater- \\ ecology.info}} & 
+    10 & 
+    6 &
+    6 & 
+    7 & 
+    9 & 
+    - & 
+    - 
+    \\
+    \cline{2-8} & 
+    \specialcell{10 point \\ assignment \\ system} &
+    \specialcell{single category \\ assignment \\ system} &
+    \specialcell{10 point \\ assignment \\ system} &
+    \multicolumn{2}{c |}{\specialcell{binary}} &
+    - & 
+    - \\
+    \hline
+    \hline
+    \multirow{2}{*}{Tachet} & 
+    7 & 
+    3 &
+    8 & 
+    5 & 
+    8 & 
+    7 & 
+    - 
+    \\
+    \cline{2-8} &
+    \multicolumn{2}{c |}{fuzzy $[0-3]$} &
+    fuzzy $[0-5]$ & 
+    \multicolumn{3}{c |}{fuzzy $[0-3]$} & 
+    -
+    \\
+    \hline
+    \hline
+    \multirow{2}{*}{\specialcell{North America \\ (Twardochleb)}} & 
+    6 & 
+    3 &
+    10 & 
+    3 & 
+    10 & 
+    3 & 
+    - 
+    \\
+    \cline{2-8} &
+    \multicolumn{6}{c |}{binary} &
+    -
+    \\
+    \hline
+    \hline
+    \multirow{2}{*}{\specialcell{North America \\ (Vieira)}} & 
+    8 & 
+    3 &
+    9 & 
+    8 & 
+    10 & 
+    3 & 
+    5 
+    \\
+    \cline{2-8} &
+    \multicolumn{7}{c }{binary}
+    \\
+    \hline
+    \hline
+    \multirow{2}{*}[-4mm]{Australia} & 
+    16 \textsuperscript{\textit{a}} & 
+    7 &
+    9 & 
+    10 &
+    13 \textsuperscript{\textit{b}} & 
+    9 & 
+    4
+    \\
+    \cline{2-8} & 
+    \multicolumn{2}{c |}{\specialcell{binary; proportional $[0 - 1]$; \\ fuzzy $[0 - 3]$}} & 
+    binary; fuzzy $[0 - 3]$ & 
+    \specialcell{binary; proportional \\ scale $[0 - 1]$; \\ fuzzy $[0 - 3]$} & 
+    categorical & 
+    \specialcell{binary; \\ continuous; \\ fuzzy $[0 - 3]$} & 
+    fuzzy codes $[0-3]$
+    \\
+    \hline
+    \hline
+    \multirow{2}{*}{New Zealand} & 
+    6 & 
+    3 & 
+    4 & 
+    4 & 
+    4 & 
+    5 & 
+    4
+    \\
+    \cline{2-8} & 
+    \multicolumn{7}{c }{fuzzy $[0-3]$}
+    \\
+    \bottomrule
+    \end{longtable}
+    \begin{minipage}{\linewidth}\small
+        \textit{a} Some of the traits were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
+        \newline
+        \textit{b} Many traits were rather comments than traits in the original database and were not considered.
+    \end{minipage}
+\end{landscape}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 % 2) Influence of aggregation methods on trait-environment relationships: 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \printbibliography
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%% Supporting information %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supporting information %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \setcounter{table}{0}

### 2020-11-11 Paper/Results/SI.tex
11.11: Paper Update text

@@
 
-\subsubsection*{Simulation of varying taxonomic hierarchies}
+%\subsubsection*{Simulation of varying taxonomic hierarchies}
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
-    \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
+%     \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
 Boxplots depict results for each trait aggregation method of 100 simulations.
 T1 to T3 are the simulated traits.}
-    \label{fig:overview_sim_results}
-\end{figure}
+%     \label{fig:overview_sim_results}
+% \end{figure}
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
-    \caption{Comparison of the results of the trait aggregation methods for every simulated dataset.
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
+%     \caption{Comparison of the results of the trait aggregation methods for every simulated dataset.
 Simulated datasets where absolute differences between aggregated trait affinities were greater than 0.1 are depicted.
 Only the comparisons are shown were differences greater than 0.1 occurred.}
-    \label{fig:sim_indv_runs}
-\end{figure}
+%     \label{fig:sim_indv_runs}
+% \end{figure}
 
@@
 
-\subsection*{Re-analysis of Szöcs et al. using harmonized grouping features.}
-\label{subsec:SI_szoecs_reanalysis}
+%\subsection*{Re-analysis of Szöcs et al. using harmonized grouping features.}
+%\label{subsec:SI_szoecs_reanalysis}
 
-\subsubsection*{RDA of trait composition}
+% \subsubsection*{RDA of trait composition}
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{RDA_traits_harmonized.png}
-    \caption{RDA of traits constrained by electric conductivity using harmonized grouping features.
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{RDA_traits_harmonized.png}
+%     \caption{RDA of traits constrained by electric conductivity using harmonized grouping features.
 Boxplot of site scores along the conductivity axis ($31.44 \%$ explained variance, p = 0.001, 1000 permutations).
@@
 \cite{szocs_effects_2014}.
-    } 
-\end{figure}
+%     } 
+% \end{figure}
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{RDA_traits_Szoecs_2014.png}
-    \caption{RDA of traits constrained by electric conductivity.
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{RDA_traits_Szoecs_2014.png}
+%     \caption{RDA of traits constrained by electric conductivity.
 Boxplot of site scores along the conductivity axis ($30.09 \%$ explained variance, p = 0.001, 1000 permutations).
@@
 Only traits with a mahalanobis distance greater than 5.02 were labeled.
-    } 
-\end{figure}
+%     } 
+% \end{figure}
 
-\subsubsection*{Trait distribution along first RDA axis}
+% Not sure if the next two sections are really needed
+% Need also to run analysis again
+%\subsubsection*{Trait distribution along first RDA axis}
 
-% ASK: 
-% - there seems to be some overlap of text on the top left
-% - Why mention life cylce duration separately?
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_harmonized.png}
-    \caption{Trait scores on the first RDA axis for harmonized traits and traits of the grouping feature \textit{life cycle duration}.
-    } 
-\end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_harmonized.png}
+%     \caption{Trait scores on the first RDA axis for harmonized traits and traits of the grouping feature \textit{life cycle duration}.
+%     } 
+% \end{figure}
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_Szoecs_2014.png}
-    \caption{Trait scores on the first RDA axis for the traits responding to high salinity in Szöcs et al. \cite{szocs_effects_2014}
-    .
-    }
-\end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_Szoecs_2014.png}
+%     \caption{Trait scores on the first RDA axis for the traits responding to high salinity in Szöcs et al. \cite{szocs_effects_2014}
+%     .
+%     }
+% \end{figure}
 
 \newpage
-\subsubsection*{Linear models of trait proportions}
+% \subsubsection*{Linear models of trait proportions}
 
-\textit{Linear models of trait proportions with harmonized traits:}
-\begin{table}[ht]
-    \centering
-    \caption{Results of linear models for the four selected harmonized traits and life cycle duration $>$ 1 year.
+% \textit{Linear models of trait proportions with harmonized traits:}
+% \begin{table}[ht]
+%     \centering
+%     \caption{Results of linear models for the four selected harmonized traits and life cycle duration $>$ 1 year.
 Trait proportions were logit transformed prior model building, estimates are on the logit scale.
@@
 Bold values indicate statistically significant effects (p $<$ 0.05).}
-    \label{stab:linear_models_new}
-    \begin{tabular}{l|ccccc}
-    \toprule[.1em]
-    & \specialcell{Feeding mode:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell{Voltinism:\\ bi- or multivoltine} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
-    \toprule[.1em]
-    Intercept ($=$ upstream) & \textbf{-1.041} & \textbf{-0.486} & 0.375* & \textbf{-0.823} & 0.092\\ 
-    Downstream & \textbf{0.926} & \textbf{0.605} & \textbf{1.376} & \textbf{1.684} & \textbf{0.854}\\ 
-    Downstream x 2008 & -0.117 & 0.106 & -0.235 & -0.088 & -0.317\\ 
-    Downstream x 2009 & 0.030 & -0.056 & 0.001 & 0.245 & 0.180\\ 
-    Year 2008 & -0.167 & -0.115 & 0.033 & -0.182 & -0.151\\ 
-    Year 2009 & 0.175 & 0.086 & -0.088 & 0.246 & 0.141\\ 
-    \bottomrule
-    \end{tabular}
-    \textit{* p.value = 0.055}
-\end{table}
-\newline
-\newline
-\newline
-\textit{Linear models of trait proportions Szöcs et al. :}
-\begin{table}[ht]
-    \centering
-    \caption{Results of linear models for the five selected traits for Szöcs et al.
+%     \label{stab:linear_models_new}
+%     \begin{tabular}{l|ccccc}
+%     \toprule[.1em]
+%     & \specialcell{Feeding mode:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell{Voltinism:\\ bi- or multivoltine} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
+%     \toprule[.1em]
+%     Intercept ($=$ upstream) & \textbf{-1.041} & \textbf{-0.486} & 0.375* & \textbf{-0.823} & 0.092\\ 
+%     Downstream & \textbf{0.926} & \textbf{0.605} & \textbf{1.376} & \textbf{1.684} & \textbf{0.854}\\ 
+%     Downstream x 2008 & -0.117 & 0.106 & -0.235 & -0.088 & -0.317\\ 
+%     Downstream x 2009 & 0.030 & -0.056 & 0.001 & 0.245 & 0.180\\ 
+%     Year 2008 & -0.167 & -0.115 & 0.033 & -0.182 & -0.151\\ 
+%     Year 2009 & 0.175 & 0.086 & -0.088 & 0.246 & 0.141\\ 
+%     \bottomrule
+%     \end{tabular}
+%     \textit{* p.value = 0.055}
+% \end{table}
+% \newline
+% \newline
+% \newline
+% \textit{Linear models of trait proportions Szöcs et al. :}
+% \begin{table}[ht]
+%     \centering
+%     \caption{Results of linear models for the five selected traits for Szöcs et al.
 \cite{szocs_effects_2014}.
 Trait proportions were logit transformed prior model building, estimates are on the logit scale.
-    Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically
-    significant effects (p $<$ 0.05).}
-    \label{stab:linear_models_edi}
-    \begin{tabular}{l|ccccc}
-    \toprule[.1em]
-    & \specialcell{Feeding habits:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell {Cycles per year:\\ $>$ 1} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
-    \toprule[.1em]
-    Intercept ($=$ upstream) & \textbf{-0.853} & \textbf{-0.478} & \textbf{0.603} & \textbf{-0.838} & 0.111 \\ 
-    Downstream & \textbf{0.819} & \textbf{0.594} & \textbf{1.297} & \textbf{1.679} & \textbf{0.839} \\ 
-    Downstream x 2008 & -0.155 & 0.102 & -0.227 & -0.070 & -0.314 \\ 
-    Downstream x 2009 & 0.073 & -0.053 & -0.020 & 0.248 & 0.176 \\ 
-    Year 2008 & -0.122 & -0.112 & 0.026 & -0.192 & -0.154 \\ 
-    Year 2009 & 0.167 & 0.084 & -0.104 & 0.250 & 0.139 \\ 
-    \bottomrule
-    \end{tabular} 
-\end{table}
+%     Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically
+%     significant effects (p $<$ 0.05).}
+%     \label{stab:linear_models_edi}
+%     \begin{tabular}{l|ccccc}
+%     \toprule[.1em]
+%     & \specialcell{Feeding habits:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell {Cycles per year:\\ $>$ 1} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
+%     \toprule[.1em]
+%     Intercept ($=$ upstream) & \textbf{-0.853} & \textbf{-0.478} & \textbf{0.603} & \textbf{-0.838} & 0.111 \\ 
+%     Downstream & \textbf{0.819} & \textbf{0.594} & \textbf{1.297} & \textbf{1.679} & \textbf{0.839} \\ 
+%     Downstream x 2008 & -0.155 & 0.102 & -0.227 & -0.070 & -0.314 \\ 
+%     Downstream x 2009 & 0.073 & -0.053 & -0.020 & 0.248 & 0.176 \\ 
+%     Year 2008 & -0.122 & -0.112 & 0.026 & -0.192 & -0.154 \\ 
+%     Year 2009 & 0.167 & 0.084 & -0.104 & 0.250 & 0.139 \\ 
+%     \bottomrule
+%     \end{tabular} 
+% \end{table}
 
-\subsubsection*{Trait proportions over time}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_harmonized.png}
-    \caption{Proportions for the four harmonized traits that have been promoted by salinization and life cycle duration $>$ 1 year for down- and upstream sites.
-    } 
-\end{figure}
+% \subsubsection*{Trait proportions over time}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_harmonized.png}
+%     \caption{Proportions for the four harmonized traits that have been promoted by salinization and life cycle duration $>$ 1 year for down- and upstream sites.
+%     } 
+% \end{figure}
 
-% Trait proportions over time
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_Szoecs_2014.png}
-    \caption{Proportions for five selected traits for down- and upstream sites (traits that have been promoted by salinization) from Szöcs et al. \cite{szocs_effects_2014}.} 
-\end{figure}
+% % Trait proportions over time
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_Szoecs_2014.png}
+%     \caption{Proportions for five selected traits for down- and upstream sites (traits that have been promoted by salinization) from Szöcs et al. \cite{szocs_effects_2014}.} 
+% \end{figure}
 

### 2020-11-18 Paper/Draft_harmonization_paper.tex
18.11: Paper discussion progress

@@
 % TODO: bring affinity/affinity scores in
+% Could say that we call the proportionate description (0-1) "affinity"
 
@@
 % TODO: clarify, see Ralf's comment
-% Add novel harmonised trait databases?
-We studied the influence of grouping feature harmonization and trait aggregation on trait-environment relationships.
-In particular, we aimed to (1) determine the effect of different harmonization methods using 4 invertebrate trait database for 7 grouping features from Europe, North America, New Zealand, and Australia.
-Furthermore, we (2) compared trait affinities obtained through different trait aggregation methods to trait affinities assigned at family-level by experts.
-We (3) re-analysed data on the effect of anthropogenic salinisation on biological traits by Szöcs et al.
-\cite{szocs_effects_2014} using harmonized grouping features and aggregated traits.
+The necessity to aggregate and harmonize trait data due to the discrepancies in trait definitions motivated us to compare different trait aggregation methods and evaluate whether the harmonization of trait data ...
+As a basis for our analysis, we (1) established 4 novel invertebrate trait datasets consisting of  7 grouping features based on trait databases from Europe, North America, Australia, and New Zealand.
+To evaluate different trait aggregation methods we (2) compared trait affinities obtained through different trait aggregation methods to trait affinities assigned at family-level by experts for two of the established trait datasets.
+% Mention simulation
+(3) To evaluate how harmonizing grouping features and aggregating traits can modify results of trait-environment relationships we re-analysed data on the effect of anthropogenic salinisation on biological traits by Szöcs et al.
+\cite{szocs_effects_2014} using trait data from the established harmonized European trait datasets.
 By comparison with the original analysis, we investigated how harmonizing and aggregating trait data can modify the outcome of trait-environment relationships.
@@
 For example, in the  freshwaterecology.info database, the classification of the trait voltinism accounts for different faunistic regions.
-Hence, the entries such as "arctic" or "boreal" of the e.g.
+Hence, entries such as "arctic" or "boreal" of e.g.
 the trait univoltine were substituted with a value of 1.
@@
 The sampling was repeated 100 times for each standard deviation.
-Hence, in total 12500 ($25 * 5 * 100$) trait affinities were simulated.
+Hence, in total 100 datasets for each level of trait variability were simulated, resulting in 12500 simulated trait affinities ($25$ species per family $* 5$ levels of trait variability $* 100$ replicates).
 All trait aggregation methods were applied to each simulated dataset.
@@
 
-We evaluate the simulation results based on the range of produced aggregated trait affinities and by comparing results of every simulated dataset.
+We evaluate the simulation results based on the produced range of aggregated trait affinities and by comparing results of every simulated dataset.
 
-% range base simulation
 The trait aggregation methods \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}} and \textit{weighted\_agg} yielded similar ranges of aggregated trait affinities within each level of trait variability for the \textit{sim\_base} scenario.
+The \textit(stepwise\_agg \textsubscript{median}) and \textit(direct\_agg \textsubscript{median}) yielded mostly greater ranges of aggregated trait affinities for the \textit{sim\_base} scenario.
+As expected with increasing trait variability the produced range of trait affinities increased (Figure \ref{fig:overview_sim_results}).
+By contrast, the ranges of trait affinities slightly differed for all aggregation methods for the simulation scenarios \textit{sim\_extreme} and \textit{sim\_variation}.
+\textit{Weighted\_agg} and \textit{stepwise\_agg\textsubscript{mean}} produced a wider range of trait affinities than the \textit{direct\_agg\textsubscript{mean}} in the \textit{sim\_extreme} scenario.
+For most levels of trait variability the \textit{stepwise\_agg \textsubscript{median}} resulted in the largest range of trait affinities in the \textit{sim\_extreme} and \textit{sim\_variation} scenarios.
 
-Aggregation methods using the median yielded greater ranges of aggregated trait affinities than methods using the mean.
-Thereby, the \textit(stepwise\_agg \textsubscript{median}) yielded the greatest range of aggregated trait affinities (Figure S\ref{fig:overview_sim_results}).
+% 10 unique comparisons, 100 datasets, 5 levels of trait variability, 3 sim scenarios  
+A comparison of the results of the aggregation methods for each simulated data set showed that in most simulated datasets the differences between the aggregated traits were small.
+Only 1.42 \% (213 out of 15.000) of all comparisons showed a difference equal or greater than an absolute trait affinity of 0.1.
+Most of these differences occurred for the \textit{sim\_extreme} scenario (83.5 \%).
+The majority of the differences equal or above 0.1 were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure S\ref{fig:sim_indv_runs}).
+% Differences were rather small, largest difference 0.265 for sim_extreme (stepwise_median vs weighted_agg)
 
-% Other simulation scenarios
-By contrast, the ranges of trait affinities differed for all aggregation methods for the simulation scenarios \textit{sim\_extreme} and \textit{sim\_variation}.
-\textit{Weighted\_agg} and \textit{stepwise\_agg\textsubscript{mean}} produced a wider range of values than the \textit{direct\_agg\textsubscript{mean}} in the \textit{sim\_extreme} scenario.
-For most levels of trait variability the \textit{stepwise\_agg \textsubscript{median}} resulted in the largest range of trait affinities in both scenarios
-
-Analysing the individual simulation runs showed that differences between the results of the aggregation methods increased with increasing trait variability.
-Most differences occurred for the \textit{sim\_extreme} scenario.
-Differences greater than an absolute trait affinity of 0.1 occurred between methods using the median and the mean.
-Thereby, the most frequent differences above 0.1 were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure S\ref{fig:sim_indv_runs}).
-
-% TODO: What's good and what's bad -> that's maybe the wrong question, but what's the direction of each method? 
-% Overall,
+Overall, differences between the results of the aggregation methods for each simulated dataset increased with increasing trait variability.
+According to the simulation results, the different aggregation methods often result in similar trait affinities.
+If differences occurred, than mostly between aggregation methods using the median and aggregation methods using the mean.
 
@@
   \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
-  \caption{Comparison of the results of the trait aggregation methods for every simulated dataset.
-Simulated datasets where absolute differences between aggregated trait affinities were greater than 0.1 are depicted.
-Only the comparisons are shown were differences greater than 0.1 occurred.}
+  \caption{Comparison of the aggregated trait affinities produced by the different trait aggregation methods for every simulated dataset across all 3 simulated traits.
+Dots depict comparisons where absolute differences between aggregated trait affinities were greater than 0.1.
+\newline
+  Comparison: \newline
+  1) Direct\_agg (median) - Stepwise\_agg (mean) \newline
+  2) Direct\_agg (median) - Weighted\_agg, \newline
+  3) Stepwise\_agg (mean) - Stepwise\_agg (median), \newline
+  4) Stepwise\_agg (mean) - Weighted\_agg, \newline  
+  5) Direct\_agg (mean) - Stepwise\_agg (median), \newline
+  6) Direct\_agg (median) - Stepwise\_agg (median), \newline
+  7) Stepwise\_agg (median) - Weighted\_agg \newline
+  }
   \label{fig:sim_indv_runs}
 \end{figure}
+
+\newpage
 
@@
 For the North American dataset, comparison of the trait aggregation methods to trait affinities assigned at family-level yielded between 15.3 \% and 47 \% differing cases (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
-
 In general, trait aggregation methods using the median yielded fewer cases with differences compared to approaches using the mean.
@@
 
+% Is that necessary?
 A comparison of the aggregation methods with each other for the 4 datasets revealed that differences in aggregated trait affinities were largest between the \textit{stepwise\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{median}} (Figure S\ref{fig:comp_aggr_methods}).
@@
   \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_chessman.png}
-  \caption{Display of the cases where differences occurred between aggregated traits and traits assigned at family-level.
+  \caption{Display of the cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family-level.
 Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the Australian dataset for the grouping features feeding mode and body size.
@@
   \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_pyne.png}
-  \caption{Display of the cases where differences occurred between aggregated traits and traits assigned at family-level.
+  \caption{Display of the cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family-level.
 Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
@@
 N denotes the number of cases per comparison where differences occurred.
-The black dot indicates the mean of absolute differences and the error bars the standard deviation.
+The blue dot indicates the mean of absolute differences and the error bars the standard deviation.
 The gray vertical lines show the 25th, 50th and 75th quantile of the density estimate.}
@@
 
+\subsection*{Differences in trait affinities obtained by trait aggregation methods compared to traits assigned at family-level}
+
+% Summarize briefly results and synthesize (with Simulation)  
+Our results show that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level, i.e. it yields less differing cases. 
+% This part needs to be improved:
+% However, aggregation methods using the median tend to produce greater differences between aggregated and assigned traits.
+The different weighting methods, i.e.
+aggregating stepwise, direct or weighted, did not seem to have a strong impact, because the distribution of absolute trait affinity differences to assigned traits obtained by the \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}} and \textit{weighted\_agg} were relatively similar in both tested datasets.
+%as well as for direct\agg (median) and stepwise\_agg (median)
+Instead, using the mean or the median changed the distribution of differences in trait affinities between aggregated and assigned traits.
+% Wording!
+A reason that using different weightings for the taxa when aggregating doesn't seem to have a big influence is on the one hand, that the used taxa had only a low number of genera in the used trait datasets or don't have species entries at all.
+From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \%, 61.7 \% were resolved on genus-level.
+52.1 \% had 5 or less genera and 12.8 \% contained just one genus (Figure S\ref{fig:tax_hierarchy_NOA}).
+In the Australian dataset 21.4 \% of the compared taxa had trait information resolved on family-level, 39.5 \% resolved on genus level, and 39.1 \% resolved on species-level.
+67.73 \% of the taxa contain 5 or less genera and 39.6 \% just contained one genus (Figure S\ref{fig:tax_hierarchy_AUS}).
+The simulation results indicated that the choice of the aggregation method for small numbers of genera per family (5) can be important when one genus has a much larger number of species compared to other genera within a particular family.
+% How often in the trait datasets?
+However, inspecting the simulated datasets revealed that often aggregated traits only differ slightly obtained from the different aggregation methods .
+
+% Differences between datasets 
+Observed differences between aggregated and assigned traits were higher for the North American trait dataset.
+This can be explained by the binary coding of the traits in the North American dataset.
+As a results, traits have been assigned affinities of either 1 or 0.
+Thus naturally, even after normalization, traits of a particular grouping feature have a high difference of trait affinities to each other compared to when they were coded using fuzzy codes.
+
+% Of course all the comparisons have no "generellen Gültigkeisanspruch" - what's the true aggregated trait affinity characterising a particular family?
+Expert assignments maybe also biased based on experience with a particular group of taxa within a family.
+Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular organism on family-level is.
+It is indeed questionable whether the aggregation of trait information on species or genus-level to a point estimate on family-level can be an adequate description of a particular trait at all, especially for traits with a high variability.
+In fact, traits can vary strongly on more precise taxonomic levels than the family-level.
+For example, Monaghan and Soares found a high dispersion of trait affinities at genus-level within families in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}.
+Furthermore, studies focusing on the lability of traits, i.e.
+how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g.
+thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006,wilkes_traitbased_2020}.
+Thus, it is likely that assigned traits and aggregated traits at family-level will especially differ in affinities for the aforementioned traits.
+Our analysis could confirm this partially.
+The highest possible difference of 1 between aggregated trait affinities and assigned trait affinities (in total in 6.9 \% of all cases) for the Australian dataset occurred most often for body size large and medium (42.5 \% and 39.2 \% of all cases with a difference of 1, respectively) across all comparisons.
+Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all tested comparisons (mean size medium 0.5, sd 0.29; mean size large 0.59, sd 0.32).
+For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with a maximum difference), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference).
+Respiration via plastron and spiracle showed the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).
+
+% Outlook: combine trait information for priors like in species distribution models/population growth models,
+% see Kindvater et al and Brown & Roff 
+% ? Constructing priors from fuzzy coded traits
+
+% Further ideas: 
+%   - Differences across grouping features
+%   - Still some similarities between compared datasets -> Where does the classification come from?
+%     Few sources used in NOA also used in AUS:
+%     AUS: Merrit & Cummins 1978/1984 for feeding mode for a few genera and families 
+%     NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait   %     description "Cummins, K. W. Trophic Relations of Aquatic Insects" was used
+%   - Could not include all data due to data gaps -> much needed to be filled -> would maybe change the picture?
+
+\subsection*{Re-analysis of Szöcs et al. using harmonized and aggregated grouping features}
+
+% Were the traits promoted by the harmonized dataset on the most extreme points on the conductivity axis?
+% Large scale studies?
+
+% What does this imply for future studies -> return to the introduction
+
 \begin{itemize}

### 2020-11-18 Paper/Results/SI.tex
18.11: Paper discussion progress

@@
 
-\subsubsection*{Taxonomic hierarchy in the analysed trait datasets}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_EU.png}
-    \caption{Number of genera per family and species per genus for the European trait dataset. For better visual display only families with more than 10 genera are displayed.}
-    \label{fig:tax_hierarchy_EU}
-\end{figure}
+\subsubsection*{Taxonomic hierarchy in the trait datasets used for comparisons with assigned traits at family-level}
+\label{sec:taxonomic_hierarchy}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_EU.png}
+%     \caption{Number of genera per family and species per genus for the European trait dataset. For better visual display only families with more than 10 genera are displayed.}
+%     \label{fig:tax_hierarchy_EU}
+% \end{figure}
 
@@
     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NOA.png}
-    \caption{Number of genera per family and species per genus for the North American trait dataset. For better visual display only families with more than 15 genera are displayed.}
+    \caption{Number of genera per family and species per genus for those families of the North American trait dataset that have been compared to assigned traits at family level.
+For better visual display only families with more than 15 genera are displayed.}
     \label{fig:tax_hierarchy_NOA}
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NZ.png}
-    \caption{Number of genera per family and species per genus for the New Zealand trait dataset. For better visual display only families with more than 5 genera are displayed.}
-    \label{fig:tax_hierarchy_NZ}
-\end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NZ.png}
+%     \caption{Number of genera per family and species per genus for the New Zealand trait dataset. For better visual display only families with more than 5 genera are displayed.}
+%     \label{fig:tax_hierarchy_NZ}
+% \end{figure}
 

### 2020-11-20 Paper/Draft_harmonization_paper.tex
Update 20.11: Rough draft for discussion

@@
 The original RDA in Szöcs et al.
-\cite{szocs_effects_2014} indicated that downstream sites (high salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle ($> 1$ year), and gill respiration and upstream sites (low salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
+\cite{szocs_effects_2014} indicated that downstream sites (high salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle duration ($> 1$ year), and gill respiration and upstream sites (low salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
 
-Using harmonized grouping features resulted in fewer traits that distinguish upstream and downstream sites in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
-According to the RDA of the trait composition, downstream sites were characterised by taxa with the traits multivoltinism and ovoviviparity and upstream sites were characterised by univoltine taxa that lay their eggs in an aquatic environment (aquatic eggs).
-The traits shredder, gill respiration and long life cycle duration did not characterise sites with high salinisation.
-Also, the trait short life cycle duration did not characterise upstream sites with low salinity.
+Using harmonized grouping features resulted in less traits that distinguish upstream and downstream sites in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+According to the RDA of the trait composition, downstream sites were characterised by taxa with the traits multivoltinism, ovoviviparity and long life cycle duration.
+Upstream sites were characterised by univoltine taxa with a short life cycle duration that lay their eggs in an aquatic environment (aquatic eggs).
+The trait aquatic eggs of the harmonized grouping feature oviposition has been derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonization}).
+The traits shredder and gill respiration did not characterise sites with high salinisation.
 
-Using at family-level aggregated traits from the harmonized dataset showed results similar to the original analysis (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+Using at family-level aggregated traits from the harmonized dataset showed also results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
 The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg}
@@
 Upstream sites were characterised by the traits univoltinism, aquatic eggs and short life cycle duration.
-The trait aquatic eggs of the harmonized grouping feature oviposition has been derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonization}).
 The same results were obtained when re-analysing the data with traits aggregated by the \textit{stepwise\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, with the exception that none of the life cycle traits characterised upstream or downstream sites.
-Thus, in our comparison the direct and weighted family-level aggregation methods yielded to the least change in species scores of all methods compared to the original results.
+Thus, in our comparison aggregating by \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg} yielded to the least change in interpretation of the RDA results compared to the original results.
 
@@
 % Summarize briefly results and synthesize (with Simulation)  
-Our results show that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level, i.e. it yields less differing cases. 
-% This part needs to be improved:
-% However, aggregation methods using the median tend to produce greater differences between aggregated and assigned traits.
+Our results show that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level, i.e.
+it yields less differing cases.
+However, in those cases where differences in the trait aggregation methods that use the median occurred, these differences were greater compared to the aggregation methods that used the mean.
 The different weighting methods, i.e.
 aggregating stepwise, direct or weighted, did not seem to have a strong impact, because the distribution of absolute trait affinity differences to assigned traits obtained by the \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}} and \textit{weighted\_agg} were relatively similar in both tested datasets.
-%as well as for direct\agg (median) and stepwise\_agg (median)
+This also applies to the distributions of absolute trait affinity differences obtained by \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}.
 Instead, using the mean or the median changed the distribution of differences in trait affinities between aggregated and assigned traits.
-% Wording!
-A reason that using different weightings for the taxa when aggregating doesn't seem to have a big influence is on the one hand, that the used taxa had only a low number of genera in the used trait datasets or don't have species entries at all.
-From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \%, 61.7 \% were resolved on genus-level.
+A possible reason why the use of different weightings for taxa appears to have little impact on trait aggregation is that a considerable portion of taxa used have a low numbers of genera or species entries.
+From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \% were resolved on family-level and 61.7 \% were resolved on genus-level.
 52.1 \% had 5 or less genera and 12.8 \% contained just one genus (Figure S\ref{fig:tax_hierarchy_NOA}).
@@
 % How often in the trait datasets?
-However, inspecting the simulated datasets revealed that often aggregated traits only differ slightly obtained from the different aggregation methods .
+In general however, inspecting the simulated datasets revealed that often aggregated traits obtained from the different aggregation methods only differ slightly.
 
@@
 Expert assignments maybe also biased based on experience with a particular group of taxa within a family.
-Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular organism on family-level is.
+Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
 It is indeed questionable whether the aggregation of trait information on species or genus-level to a point estimate on family-level can be an adequate description of a particular trait at all, especially for traits with a high variability.
 In fact, traits can vary strongly on more precise taxonomic levels than the family-level.
-For example, Monaghan and Soares found a high dispersion of trait affinities at genus-level within families in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}.
+For example, Monaghan and Soares found a high dispersion of trait affinities for genera within families in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}.
 Furthermore, studies focusing on the lability of traits, i.e.
@@
 The highest possible difference of 1 between aggregated trait affinities and assigned trait affinities (in total in 6.9 \% of all cases) for the Australian dataset occurred most often for body size large and medium (42.5 \% and 39.2 \% of all cases with a difference of 1, respectively) across all comparisons.
-Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all tested comparisons (mean size medium 0.5, sd 0.29; mean size large 0.59, sd 0.32).
-For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with a maximum difference), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference).
+Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all tested comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32).
+For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1).
 Respiration via plastron and spiracle showed the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).
+% What to do with these traits? Also briefly talk about traits that are more consistent?
 
@@
 %     AUS: Merrit & Cummins 1978/1984 for feeding mode for a few genera and families 
-%     NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait   %     description "Cummins, K. W. Trophic Relations of Aquatic Insects" was used
+%     NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait description "Cummins, K.
+W.
+Trophic Relations of Aquatic Insects" was used for feeding mode
 %   - Could not include all data due to data gaps -> much needed to be filled -> would maybe change the picture?
@@
 
-% Were the traits promoted by the harmonized dataset on the most extreme points on the conductivity axis?
+The re-analysis showed that neither using harmonised grouping features nor aggregated traits changed drastically the results of the original study.
+The traits that did not respond to the salinity gradient (i.e.
+not on the extremes of the conductivity axis) in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits.
+During harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder).
+As a result, the trait affinities in the original dataset have a higher mean and standard deviation than in the aggregated and harmonized datasets (Table S\ref{tab:SI_resp_traits_summary_stats}).
+% TODO: Check naming of tables! 
+Thus, the signal in the original data for the trait shredder has presumably been weakened by the harmonization, which might be the reason that shredders showed a less strong reaction to the salinity gradient.
+
+% Resp gil complicated: Original data has a lot of zeros, not in the harmonized & aggregated datasets
+% Aggregated data look similar to the harmonized ones, but resp gil is here one of the "extreme" traits 
+% on the conductivity axis
+
+% Why did some aggregation methods promote life cycle duration and others not?
+% Mean, median and sd's are all relatively similar across tested datasets for these traits
+
 % Large scale studies?

### 2020-11-20 Paper/Results/SI.tex
Update 20.11: Rough draft for discussion

@@
 \newpage
+
+\subsection*{Re-analysis of Szöcs et al. using harmonized and aggregated grouping features}
+
+\begin{table}[ht]
+    \centering
+    \caption{Mean, median and standard deviation of the traits that were responsive to the salinity gradient in the original study but not when re-analysis with the harmonized dataset trait dataset.} 
+    \label{tab:SI_resp_traits_summary_stats}
+    \begin{tabular}{llccc}
+    \toprule[.1em]
+    Dataset & Trait & Mean & Median & SD \\ 
+    \toprule[.1em]
+    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 \\ 
+      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 \\ 
+      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 \\ 
+      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 \\ 
+      Weighted & Shredder & 0.19 & 0.14 & 0.22 \\ 
+      Harmonized; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 \\ 
+      Original & Shredder & 0.25 & 0.14 & 0.32 \\ 
+      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 \\ 
+      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 \\ 
+      Direct\_median & Gills & 0.30 & 0.30 & 0.32 \\ 
+      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 \\ 
+      Weighted & Gills & 0.30 & 0.30 & 0.32 \\ 
+      Harmonized; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 \\ 
+      Original & Gills & 0.28 & 0.00 & 0.33 \\ 
+      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 \\ 
+      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 \\ 
+      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 \\ 
+      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
+      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
+      Harmonized; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
+      Original & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
+      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 \\ 
+      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 \\ 
+      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 \\ 
+      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
+      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
+      Harmonized; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
+      Original & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
+    \bottomrule
+    \end{tabular}
+\end{table}
 

### 2020-11-23 Paper/Draft_harmonization_paper.tex
22.10: Small update

@@
 \cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
-
 We suspect that the heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents.
@@
 Fuzzy codes are used to account for plasticity in traits, variability in traits within taxonomic groups above species, and incomplete knowledge and are usually converted to proportions.
-% TODO: add affinitiy scores here?
+In this study we denote the proportionate description (between 0-1) of traits as affinities or affinity scores.
 
@@
 Thus, it becomes apparent that using invertebrate trait data from several regions requires extensive data processing prior to the actual data analysis.
-A centralized database with standardized and unambiguous traits and a consistent coding of traits would minimize data processing effort.
+A centralized database with standardized and unambiguous traits and a consistent coding of traits would minimize the data processing effort.
 Discrepancies in the taxonomic resolutions (e.g.
@@
 
-% TODO: clarify, see Ralf's comment
-The necessity to aggregate and harmonize trait data due to the discrepancies in trait definitions motivated us to compare different trait aggregation methods and evaluate whether the harmonization of trait data ...
-As a basis for our analysis, we (1) established 4 novel invertebrate trait datasets consisting of  7 grouping features based on trait databases from Europe, North America, Australia, and New Zealand.
+The outlined difficulties when working with or synthesizing trait data motivated us to (1) investigate discrepancies in trait definition between trait databases from Europe, North America, Australia, and New Zealand.
+As a basis for further evaluating different trait aggregation methods and how harmonising definition discrepancies between grouping features can influence trait-environment relationships, we established 4 novel invertebrate trait datasets from these trait databases by harmonising 7 grouping features.
+We evaluate different trait aggregation methods by (2) comparing aggregated traits with assigned traits by experts at family-level for two of the established trait datasets.
+(3) we re-analysed data on the effect of anthropogenic salinisation on biological traits by Szöcs et al.
+\cite{szocs_effects_2014} using trait data from the established harmonized European trait datasets and aggregated traits.
+By comparison with the original analysis, we investigated how harmonizing and aggregating trait data can modify the outcome of trait-environment relationships.
+
+% The necessity to aggregate and harmonize trait data due to the discrepancies in trait definitions motivated us to compare different trait aggregation methods and evaluate whether the harmonization of trait data ...
+% As a basis for our analysis, we (1) established 4 novel invertebrate trait datasets consisting of  7 grouping features based on trait databases from Europe, North America, Australia, and New Zealand.
 To evaluate different trait aggregation methods we (2) compared trait affinities obtained through different trait aggregation methods to trait affinities assigned at family-level by experts for two of the established trait datasets.
 % Mention simulation
-(3) To evaluate how harmonizing grouping features and aggregating traits can modify results of trait-environment relationships we re-analysed data on the effect of anthropogenic salinisation on biological traits by Szöcs et al.
+% (3) To evaluate how harmonizing grouping features and aggregating traits can modify results of trait-environment relationships we re-analysed data on the effect of anthropogenic salinisation on biological traits by Szöcs et al.
 \cite{szocs_effects_2014} using trait data from the established harmonized European trait datasets.
@@
 
+\subsection*{Discrepancies of invertebrate trait definitions}
+
+Definitions of grouping features and traits varied in their level of detail in the original trait databases.
+The freshwaterecology.info database, the Tachet database and the North American database (Twardochleb et al.) provided more detailed descriptions of their trait information compared to the North American (Vieira et al.) and New Zealand database.
+An exception is the Australian trait database which is a collection of seven specific trait datasets \cite{kefford_integrated_2020}.
+Thus, grouping features occur multiple times with varying differentiation into traits.
+Depending on the dataset trait information is described with more or less detail.
+
+The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope.
+We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{stab:trait_definitions}).
+Both, differences in differentiation and scope can lead to discrepancies in trait definitions.
+For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways.
+The Tachet database defines predators as carvers, engulfers and swallowers.
+By contrast, in the North American (Twardochleb et al.) database predators are defined as engulfers and carnivorous piercers.
+In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers.
+Furthermore, the scope in the freshwaterecology.info database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition.
+Therefore, the freshwaterecology.info database defines e.g.
+predator as "eating from prey", while the other databases use the mouthpart morphology as basis of their definition.
+The Tachet database captures the food source in an additional grouping feature.
+Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{stab:trait_definitions}).
+Locomotion definitions differ also in scope between databases.
+Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the North American (Vieira et al.) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb et al.) database includes not only the way of movement, but also the location of movement.
+Similarly, regarding the reproduction traits, databases differ in their scope.
+Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases.
+North America (Vieira et al.) provides information on the oviposition location but not on reproductive behavior.
+The Australian database report traits for reproductive behavior but also on oviposition site.
+The New Zealand database distinguishes three grouping features related to reproduction: reproductive technique, oviposition site (e.g.
+water surface, terrestrial), and egg/egg mass (e.g.
+free, cemented).
+
+Various codings of traits are used throughout the databases (e.g.
+binary, fuzzy, continuous).
+The freshwaterecology.info and Australian use different codings in their databases.
+Tachet and the New Zealand database exclusively use fuzzy coding.
+Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
+Binary coding represents a simple approach in which a taxon either expresses a trait or not.
+Fuzzy coding characterizes the affinity of an organism to exert a certain trait.
+It is used to account for plasticity in traits, e.g.
+taking into account that traits can change over the development time of an organism.
+Usually, fuzzy coded affinities are converted into proportional values.
+Continuous coding is used for traits like body size.
+% Last sentences are a bit redundant
+
+% None of the seven grouping features compared here has the same differentiation of traits across all databases (Table \ref{tab:trait_databases})
+
+\begin{landscape}
+  \begin{longtable}{m{2.5cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
+  \caption{Number of traits per grouping feature and type of coding of the traits for the respective grouping feature per database.}
+  \endfirsthead
+  \toprule[.1em]
+  \label{tab:trait_databases_coding_differentiation}
+  Database & Feeding Mode & Voltinism & Locomotion & Respiration & Reproduction & Size & Body Form \\ 
+  \toprule[.1em]
+  \multirow{2}{*}[-5mm]{ \specialcell{Freshwater- \\ ecology.info}} & 
+  10 & 
+  6 &
+  6 & 
+  7 & 
+  9 & 
+  - & 
+  - 
+  \\
+  \cline{2-8} & 
+  \specialcell{10 point \\ assignment \\ system} &
+  \specialcell{single category \\ assignment \\ system} &
+  \specialcell{10 point \\ assignment \\ system} &
+  \multicolumn{2}{c |}{\specialcell{binary}} &
+  - & 
+  - \\
+  \hline
+  \hline
+  \multirow{2}{*}{Tachet} & 
+  7 & 
+  3 &
+  8 & 
+  5 & 
+  8 & 
+  7 & 
+  - 
+  \\
+  \cline{2-8} &
+  \multicolumn{2}{c |}{fuzzy $[0-3]$} &
+  fuzzy $[0-5]$ & 
+  \multicolumn{3}{c |}{fuzzy $[0-3]$} & 
+  -
+  \\
+  \hline
+  \hline
+  \multirow{2}{*}{\specialcell{North America \\ (Twardochleb)}} & 
+  6 & 
+  3 &
+  10 & 
+  3 & 
+  10 & 
+  3 & 
+  - 
+  \\
+  \cline{2-8} &
+  \multicolumn{6}{c |}{binary} &
+  -
+  \\
+  \hline
+  \hline
+  \multirow{2}{*}{\specialcell{North America \\ (Vieira)}} & 
+  8 & 
+  3 &
+  9 & 
+  8 & 
+  10 & 
+  3 & 
+  5 
+  \\
+  \cline{2-8} &
+  \multicolumn{7}{c }{binary}
+  \\
+  \hline
+  \hline
+  \multirow{2}{*}[-4mm]{Australia} & 
+  16 \textsuperscript{\textit{a}} & 
+  7 &
+  9 & 
+  10 &
+  13 \textsuperscript{\textit{b}} & 
+  9 & 
+  4
+  \\
+  \cline{2-8} & 
+  \multicolumn{2}{c |}{\specialcell{binary; proportional $[0 - 1]$; \\ fuzzy $[0 - 3]$}} & 
+  binary; fuzzy $[0 - 3]$ & 
+  \specialcell{binary; proportional \\ scale $[0 - 1]$; \\ fuzzy $[0 - 3]$} & 
+  categorical & 
+  \specialcell{binary; \\ continuous; \\ fuzzy $[0 - 3]$} & 
+  fuzzy codes $[0-3]$
+  \\
+  \hline
+  \hline
+  \multirow{2}{*}{New Zealand} & 
+  6 & 
+  3 & 
+  4 & 
+  4 & 
+  4 & 
+  5 & 
+  4
+  \\
+  \cline{2-8} & 
+  \multicolumn{7}{c }{fuzzy $[0-3]$}
+  \\
+  \bottomrule
+  \end{longtable}
+  \begin{minipage}{\linewidth}\small
+      \textit{a} Some of the traits were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
+      \newline
+      \textit{b} Many traits were rather comments than traits in the original database and were not considered.
+  \end{minipage}
+\end{landscape}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection*{Simulation of varying taxonomic hierarchies}
@@
 
-Definitions of grouping features and traits varied in their level of detail in the original trait databases.
-The freshwaterecology.info database, the Tachet database and the North American database (Twardochleb et al.) provided more detailed descriptions of their trait information compared to the North American (Vieira et al.) and New Zealand database.
-An exception is the Australian trait database which is a collection of seven specific trait datasets \cite{kefford_integrated_2020}.
-Thus, grouping features occur multiple times with varying differentiation into traits.
-Depending on the dataset trait information is described with more or less detail.
-
-The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope.
-We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{stab:trait_definitions}).
-Both, differences in differentiation and scope can lead to discrepancies in trait definitions.
-For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways.
-The Tachet database defines predators as carvers, engulfers and swallowers.
-By contrast, in the North American (Twardochleb et al.) database predators are defined as engulfers and carnivorous piercers.
-In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers.
-Furthermore, the scope in the freshwaterecology.info database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition.
-Therefore, the freshwaterecology.info database defines e.g.
-predator as "eating from prey", while the other databases use the mouthpart morphology as basis of their definition.
-The Tachet database captures the food source in an additional grouping feature.
-Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{stab:trait_definitions}).
-Locomotion definitions differ also in scope between databases.
-Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the North American (Vieira et al.) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb et al.) database includes not only the way of movement, but also the location of movement.
-Similarly, regarding the reproduction traits, databases differ in their scope.
-Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases.
-North America (Vieira et al.) provides information on the oviposition location but not on reproductive behavior.
-The Australian database report traits for reproductive behavior but also on oviposition site.
-The New Zealand database distinguishes three grouping features related to reproduction: reproductive technique, oviposition site (e.g.
-water surface, terrestrial), and egg/egg mass (e.g.
-free, cemented).
-
-Various codings of traits are used throughout the databases (e.g.
-binary, fuzzy, continuous).
-The freshwaterecology.info and Australian use different codings in their databases.
-Tachet and the New Zealand database exclusively use fuzzy coding.
-Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
-Binary coding represents a simple approach in which a taxon either expresses a trait or not.
-Fuzzy coding characterizes the affinity of an organism to exert a certain trait.
-It is used to account for plasticity in traits, e.g.
-taking into account that traits can change over the development time of an organism.
-Usually, fuzzy coded affinities are converted into proportional values.
-Continuous coding is used for traits like body size.
-% Last sentences are a bit redundant
-
-% None of the seven grouping features compared here has the same differentiation of traits across all databases (Table \ref{tab:trait_databases})
-\begin{landscape}
-    \begin{longtable}{m{2.5cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
-    \caption{Number of traits per grouping feature and type of coding of the traits for the respective grouping feature per database.}
-    \endfirsthead
-    \toprule[.1em]
-    \label{tab:trait_databases_coding_differentiation}
-    Database & Feeding Mode & Voltinism & Locomotion & Respiration & Reproduction & Size & Body Form \\ 
-    \toprule[.1em]
-    \multirow{2}{*}[-5mm]{ \specialcell{Freshwater- \\ ecology.info}} & 
-    10 & 
-    6 &
-    6 & 
-    7 & 
-    9 & 
-    - & 
-    - 
-    \\
-    \cline{2-8} & 
-    \specialcell{10 point \\ assignment \\ system} &
-    \specialcell{single category \\ assignment \\ system} &
-    \specialcell{10 point \\ assignment \\ system} &
-    \multicolumn{2}{c |}{\specialcell{binary}} &
-    - & 
-    - \\
-    \hline
-    \hline
-    \multirow{2}{*}{Tachet} & 
-    7 & 
-    3 &
-    8 & 
-    5 & 
-    8 & 
-    7 & 
-    - 
-    \\
-    \cline{2-8} &
-    \multicolumn{2}{c |}{fuzzy $[0-3]$} &
-    fuzzy $[0-5]$ & 
-    \multicolumn{3}{c |}{fuzzy $[0-3]$} & 
-    -
-    \\
-    \hline
-    \hline
-    \multirow{2}{*}{\specialcell{North America \\ (Twardochleb)}} & 
-    6 & 
-    3 &
-    10 & 
-    3 & 
-    10 & 
-    3 & 
-    - 
-    \\
-    \cline{2-8} &
-    \multicolumn{6}{c |}{binary} &
-    -
-    \\
-    \hline
-    \hline
-    \multirow{2}{*}{\specialcell{North America \\ (Vieira)}} & 
-    8 & 
-    3 &
-    9 & 
-    8 & 
-    10 & 
-    3 & 
-    5 
-    \\
-    \cline{2-8} &
-    \multicolumn{7}{c }{binary}
-    \\
-    \hline
-    \hline
-    \multirow{2}{*}[-4mm]{Australia} & 
-    16 \textsuperscript{\textit{a}} & 
-    7 &
-    9 & 
-    10 &
-    13 \textsuperscript{\textit{b}} & 
-    9 & 
-    4
-    \\
-    \cline{2-8} & 
-    \multicolumn{2}{c |}{\specialcell{binary; proportional $[0 - 1]$; \\ fuzzy $[0 - 3]$}} & 
-    binary; fuzzy $[0 - 3]$ & 
-    \specialcell{binary; proportional \\ scale $[0 - 1]$; \\ fuzzy $[0 - 3]$} & 
-    categorical & 
-    \specialcell{binary; \\ continuous; \\ fuzzy $[0 - 3]$} & 
-    fuzzy codes $[0-3]$
-    \\
-    \hline
-    \hline
-    \multirow{2}{*}{New Zealand} & 
-    6 & 
-    3 & 
-    4 & 
-    4 & 
-    4 & 
-    5 & 
-    4
-    \\
-    \cline{2-8} & 
-    \multicolumn{7}{c }{fuzzy $[0-3]$}
-    \\
-    \bottomrule
-    \end{longtable}
-    \begin{minipage}{\linewidth}\small
-        \textit{a} Some of the traits were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
-        \newline
-        \textit{b} Many traits were rather comments than traits in the original database and were not considered.
-    \end{minipage}
-\end{landscape}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section*{Discussion}
@@
 Respiration via plastron and spiracle showed the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).
+% Check for those cases that deviate a lot -> how have the aggregation and assignements performed when looking back at the original data?
+
 % What to do with these traits? Also briefly talk about traits that are more consistent?
@@
   \begin{itemize}
-    \item In general, differences produced by the aggregation methods seem to arise by using mean or median, not so much driven by the different weighting approaches (direct vs. stepwise vs. weighted)
-    \item Approaches that used the median resulted in fewer differences to the assigned traits, albeit if differences occurred to the assigned traits, they were greater. 
-    \item Simulation shows that approaches using the median generally produce a larger range of values $\rightarrow$ Especially with higher trait variability for situations where one genus has a lot more species than the other genera within the family
-    \item Differences greater for the NOA dataset because of the binary coding $\rightarrow$ differences are greater between traits
-    \item Taxonomic hierarchy in the investigated datasets? \\
-     $\rightarrow$ In every investigated dataset families have only 1 to few genera. 76 (North America) to 93 \% (New Zealand) of the families have 5 or less genera (see SI). 
     \item There is no "true" value to compare to, i.e.

### 2020-11-23 Paper/Draft_harmonization_paper.tex
23.11: Polishing/minor changes

@@
 Traits can be described using different codings (binary, fuzzy) that represent the prevalence of a characteristic in an organism.
-% TODO: bring affinity/affinity scores in
-% Could say that we call the proportionate description (0-1) "affinity"
 
@@
 
-% Alternative from Ben:
 Traits can be described in a binary fashion, or with multiple categories, ignoring uncertainty how the trait is expressed in any particular organism (e.g.
@@
 tolerance of pollution, body size).
-One approach for dealing with uncertainty is the use of fuzzy coded variables, where the traits are assigned probabilistic values.
+One approach for dealing with uncertainty is the use of fuzzy coded grouping features, where the traits are assigned probabilistic values.
 Fuzzy codes are used to account for plasticity in traits, variability in traits within taxonomic groups above species, and incomplete knowledge and are usually converted to proportions.
-In this study we denote the proportionate description (between 0-1) of traits as affinities or affinity scores.
+In this study we denote the proportionate description (0-1) of traits as affinities or affinity scores.
 
 However, invertebrate trait databases are heterogeneous regarding the coding they use for their traits \cite{culp_incorporating_2011}.
-Brown et al.
-\cite{brown_functional_2018} harmonized grouping features based on trait databases from Europe, North America, and New Zealand because in these trait databases identical grouping features are classified differently into traits.
-As the traits from North America were coded binary in contrast to the traits from Europe and New Zealand which have been established using affinity scores, the authors consulted experts to assign fuzzy coded traits to North American taxa or inferred them from the European trait database.
-Thus, it becomes apparent that using invertebrate trait data from several regions requires extensive data processing prior to the actual data analysis.
+For example, in the study from Brown et al.
+\cite{brown_functional_2018} the authors needed to reclassify traits using expert knowledge given that the individual databases employed different coding approaches (i.e.
+European and New Zealand databases fuzzy coding, North American database binary coding).
 A centralized database with standardized and unambiguous traits and a consistent coding of traits would minimize the data processing effort.
@@
 By comparison with the original analysis, we investigated how harmonizing and aggregating trait data can modify the outcome of trait-environment relationships.
-
-% The necessity to aggregate and harmonize trait data due to the discrepancies in trait definitions motivated us to compare different trait aggregation methods and evaluate whether the harmonization of trait data ...
-% As a basis for our analysis, we (1) established 4 novel invertebrate trait datasets consisting of  7 grouping features based on trait databases from Europe, North America, Australia, and New Zealand.
-To evaluate different trait aggregation methods we (2) compared trait affinities obtained through different trait aggregation methods to trait affinities assigned at family-level by experts for two of the established trait datasets.
-% Mention simulation
-% (3) To evaluate how harmonizing grouping features and aggregating traits can modify results of trait-environment relationships we re-analysed data on the effect of anthropogenic salinisation on biological traits by Szöcs et al.
-\cite{szocs_effects_2014} using trait data from the established harmonized European trait datasets.
-By comparison with the original analysis, we investigated how harmonizing and aggregating trait data can modify the outcome of trait-environment relationships.
-Finally, we (4) present an overview of discrepancies in trait definition between the used invertebrate trait datasets and discuss challenges of trait data synthesis.
 
@@
 
-We used fuzzy coded traits for establishing our harmonized datasets unless data quality prohibited.
+We used fuzzy coding for establishing our harmonized datasets unless data quality prohibited.
 In the latter case we used binary traits, i.e.
@@
 For example, in the  freshwaterecology.info database, the classification of the trait voltinism accounts for different faunistic regions.
-Hence, entries such as "arctic" or "boreal" of e.g.
-the trait univoltine were substituted with a value of 1.
+Hence, entries such as "arctic" or "boreal" in the voltinism traits were substituted with a value of 1.
 Implicitly, we assumed for binary traits that a value of 1 and 0 corresponds to the highest and no affinity for a particular trait.
@@
 
-To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we created three hypothetical examples of different taxonomic hierarchies.
+To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we created three hypothetical examples of different taxonomic hierarchies (scenarios).
 1) A family with an equal number of genera and species (5 genera each with 5 species respectively), denoted as \textit{sim\_base}.
@@
 The sampling was repeated 100 times for each standard deviation.
-Hence, in total 100 datasets for each level of trait variability were simulated, resulting in 12500 simulated trait affinities ($25$ species per family $* 5$ levels of trait variability $* 100$ replicates).
-All trait aggregation methods were applied to each simulated dataset.
+Hence, in total 100 datasets for each level of trait variability were simulated, resulting in 12500 simulated trait affinities for each scenario ($25$ species per family $* 5$ levels of trait variability $* 100$ replicates).
+All trait aggregation methods were applied to each simulated dataset resulting in 500 aggregated trait values per scenario.
 The results were compared based on the produced range of aggregated trait affinities between levels of trait variability and hypothetical taxonomic hierarchies.
@@
 
-Definitions of grouping features and traits varied in their level of detail in the original trait databases.
+Definitions of grouping features and traits varied in their level of detail in the investigated trait databases.
 The freshwaterecology.info database, the Tachet database and the North American database (Twardochleb et al.) provided more detailed descriptions of their trait information compared to the North American (Vieira et al.) and New Zealand database.
@@
 Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
-Binary coding represents a simple approach in which a taxon either expresses a trait or not.
-Fuzzy coding characterizes the affinity of an organism to exert a certain trait.
-It is used to account for plasticity in traits, e.g.
-taking into account that traits can change over the development time of an organism.
-Usually, fuzzy coded affinities are converted into proportional values.
-Continuous coding is used for traits like body size.
-% Last sentences are a bit redundant
-
-% None of the seven grouping features compared here has the same differentiation of traits across all databases (Table \ref{tab:trait_databases})
 
@@
 
-% 10 unique comparisons, 100 datasets, 5 levels of trait variability, 3 sim scenarios  
-A comparison of the results of the aggregation methods for each simulated data set showed that in most simulated datasets the differences between the aggregated traits were small.
+Comparing the aggregated trait affinities, in total 15000 ($500$ aggregated traits $*10$ unique comparisons of trait affinities and $3$ scenarios), for each simulated dataset showed that in most simulated datasets the differences between the aggregated traits were small.
 Only 1.42 \% (213 out of 15.000) of all comparisons showed a difference equal or greater than an absolute trait affinity of 0.1.
@@
     \caption{Species scores obtained by RDA from the original analysis \cite{szocs_effects_2014}, using harmonized grouping features, and using harmonized grouping features with traits aggregated to family-level.
-The dots represent the individual species scores for each analysed trait.
+The dots represent the individual species scores for each analysed trait along the conductivity axis.
 The violin plot shows the density estimate of the species scores.
@@
 
-\subsection*{Discrepancies of invertebrate trait definitions}
-
 \section*{Discussion}
@@
 
-% Summarize briefly results and synthesize (with Simulation)  
-Our results show that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level, i.e.
-it yields less differing cases.
+% Discussion/Comparison aggr. methods  
+Our results show that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level.
 However, in those cases where differences in the trait aggregation methods that use the median occurred, these differences were greater compared to the aggregation methods that used the mean.
@@
 Instead, using the mean or the median changed the distribution of differences in trait affinities between aggregated and assigned traits.
-A possible reason why the use of different weightings for taxa appears to have little impact on trait aggregation is that a considerable portion of taxa used have a low numbers of genera or species entries.
+A possible reason why the use of different weightings for taxa had little impact on trait aggregation is that a considerable portion of taxa used have a low numbers of genera or species entries.
 From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \% were resolved on family-level and 61.7 \% were resolved on genus-level.
@@
 
-% Differences between datasets 
+% Differences between Results of AUS and NOA dataset
 Observed differences between aggregated and assigned traits were higher for the North American trait dataset.
@@
 As a results, traits have been assigned affinities of either 1 or 0.
-Thus naturally, even after normalization, traits of a particular grouping feature have a high difference of trait affinities to each other compared to when they were coded using fuzzy codes.
+Therefore, traits of a certain grouping feature have a higher difference in trait affinities to each other than if they were coded with fuzzy codes.
 
-% Of course all the comparisons have no "generellen Gültigkeisanspruch" - what's the true aggregated trait affinity characterising a particular family?
-Expert assignments maybe also biased based on experience with a particular group of taxa within a family.
+% Discussion on differences between aggregated and assigned traits  
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
@@
 thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006,wilkes_traitbased_2020}.
-Thus, it is likely that assigned traits and aggregated traits at family-level will especially differ in affinities for the aforementioned traits.
+It is likely that assigned traits and aggregated traits at family-level will especially differ in affinities for the aforementioned grouping features.
 Our analysis could confirm this partially.
@@
 For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1).
-Respiration via plastron and spiracle showed the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).
-% Check for those cases that deviate a lot -> how have the aggregation and assignements performed when looking back at the original data?
+Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).
+% Check for those cases that deviate a lot -> how have the aggregation and assignments performed when looking back at the original data?
 
-% What to do with these traits? Also briefly talk about traits that are more consistent?
+% Also briefly talk about traits that are more consistent?
 
-% Outlook: combine trait information for priors like in species distribution models/population growth models,
-% see Kindvater et al and Brown & Roff 
-% ? Constructing priors from fuzzy coded traits
+% Include?:
+% What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
+% Are the differences between continents because of evolution or only because scientists have done more research in one of the continents?
+
+% Outlook: Are there alternatives to trait aggregation?
+Some statistical models combine trait information for priors (species distribution models/population growth models, see Kindvater et al 2018 and Brown & Roff)
 
 % Further ideas: 
-%   - Differences across grouping features
 %   - Still some similarities between compared datasets -> Where does the classification come from?
@@
 As a result, the trait affinities in the original dataset have a higher mean and standard deviation than in the aggregated and harmonized datasets (Table S\ref{tab:SI_resp_traits_summary_stats}).
-% TODO: Check naming of tables! 
-Thus, the signal in the original data for the trait shredder has presumably been weakened by the harmonization, which might be the reason that shredders showed a less strong reaction to the salinity gradient.
+Hence, the signal in the original data for the trait shredder has presumably been weakened by the harmonization, which might be the reason that shredders showed a less strong reaction to the salinity gradient.
 
@@
 
-\begin{itemize}
-  \item \textbf{aggregated vs assigned traits}
-  \begin{itemize}
-    \item There is no "true" value to compare to, i.e.
-assigned traits at genus or family level can be biased as well (i.e.
-the person who assigned the trait was thinking about particular species within a genus not all).
-Comparison of species-level traits in fwe and traits on genus-level in tachet would be interesting in this context?
-    \item  Suggestions from Co-Authors: \\
-     $\rightarrow$ should include where the classifications come from \\
-     $\rightarrow$ what do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? \\
-     $\rightarrow$ are the differences between continents because of evolution or only because scientists have done more research in one of the continents?
-  \end{itemize}
-  \item \textbf{Influence of aggregation methods on trait-environment relationships}
-  \begin{itemize}
-    \item We re-analysed only a small-scale study, what would be different when applying a large-scale study?
-  \end{itemize}
-\end{itemize}
-
 % Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
@@
 This would be worth considering in the discussion
-
-% 2) Influence of aggregation methods on trait-environment relationships: 
-% Harmonization: Minor influence on RDA species scores
-% RDA species scores 
-%   -> Normalized eigenvectors
-%   -> dependent on nr. of variables? Nr. of response variables not really influential 
-% We used only a small-scale study -> What's different to large-scale studies?
-% Further aggr. after harmonization: no difference to the harmonized dataset
-% ?Logical because trait aggr. methods themselves showed only minor differences
-% Complex Stat. techniques developed -> cannot use full potential
 
@@
 \setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thefigure}{S\arabic{figure}}
 

### 2020-11-23 Paper/Results/SI.tex
23.11: Polishing/minor changes

@@
     \centering
-    \caption{Mean, median and standard deviation of the traits that were responsive to the salinity gradient in the original study but not when re-analysis with the harmonized dataset trait dataset.} 
+    \caption{Mean, median and standard deviation of affinities of the traits that were responsive to the salinity gradient in the original study but not when re-analysis with the harmonized dataset trait dataset.}
     \label{tab:SI_resp_traits_summary_stats}

### 2020-11-24 Paper/Draft_harmonization_paper.tex
24.11:	Paper update

@@
 
-% Discussion/Comparison aggr. methods  
+% Discussion/Comparison aggr. methods/assigned traits  
 Our results show that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level.
-However, in those cases where differences in the trait aggregation methods that use the median occurred, these differences were greater compared to the aggregation methods that used the mean.
+However, in those cases where differences between trait aggregation methods that use the median and assigned traits occurred, these differences were greater compared to the aggregation methods that used the mean.
 The different weighting methods, i.e.
@@
 From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \% were resolved on family-level and 61.7 \% were resolved on genus-level.
-52.1 \% had 5 or less genera and 12.8 \% contained just one genus (Figure S\ref{fig:tax_hierarchy_NOA}).
+52.1 \% had 5 or less genera and 12.8 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
 In the Australian dataset 21.4 \% of the compared taxa had trait information resolved on family-level, 39.5 \% resolved on genus level, and 39.1 \% resolved on species-level.
-67.73 \% of the taxa contain 5 or less genera and 39.6 \% just contained one genus (Figure S\ref{fig:tax_hierarchy_AUS}).
+67.73 \% of the taxa contain 5 or less genera and 39.6 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}).
 The simulation results indicated that the choice of the aggregation method for small numbers of genera per family (5) can be important when one genus has a much larger number of species compared to other genera within a particular family.
 % How often in the trait datasets?
-In general however, inspecting the simulated datasets revealed that often aggregated traits obtained from the different aggregation methods only differ slightly.
 
@@
 As a results, traits have been assigned affinities of either 1 or 0.
-Therefore, traits of a certain grouping feature have a higher difference in trait affinities to each other than if they were coded with fuzzy codes.
+Therefore, traits of a certain grouping feature have in most cases a higher difference in trait affinities to each other than if they were coded with fuzzy codes.
 
@@
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
-It is indeed questionable whether the aggregation of trait information on species or genus-level to a point estimate on family-level can be an adequate description of a particular trait at all, especially for traits with a high variability.
+Indeed, it is questionable whether the aggregation of trait information on species or genus-level to a point estimate on family-level can be an adequate description of a particular trait at all, especially for traits with a high variability.
 In fact, traits can vary strongly on more precise taxonomic levels than the family-level.
-For example, Monaghan and Soares found a high dispersion of trait affinities for genera within families in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}.
+For example, Monaghan and Soares found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}.
 Furthermore, studies focusing on the lability of traits, i.e.
 how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g.
-thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006,wilkes_traitbased_2020}.
-It is likely that assigned traits and aggregated traits at family-level will especially differ in affinities for the aforementioned grouping features.
-Our analysis could confirm this partially.
-The highest possible difference of 1 between aggregated trait affinities and assigned trait affinities (in total in 6.9 \% of all cases) for the Australian dataset occurred most often for body size large and medium (42.5 \% and 39.2 \% of all cases with a difference of 1, respectively) across all comparisons.
-Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all tested comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32).
+thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}.
+Our analysis showed that disagreement between aggregated and assigned traits was largest for body size and respiration traits.
+The highest possible difference of 1 between aggregated trait affinities and assigned trait affinities (in total in 6.9 \% of all cases) for the Australian dataset occurred most often for body size large and medium (42.5 \% and 39.2 \% of all cases with a difference of 1, respectively) across all comparisons of aggregated and assigned traits.
+Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32).
+% Mention that body size is binary coded?
 For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1).
 Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).
-% Check for those cases that deviate a lot -> how have the aggregation and assignments performed when looking back at the original data?
+% Include which traits are more consistent?
+% ? How have the aggregation and assignments performed when looking back at the original data?
 
-% Also briefly talk about traits that are more consistent?
+% Conclude:
+% The uncertainty of trait information should be taken into account when developing trait databases and appropriate measures to capture this uncertainty should be established.
+% One should be cautious when aggregating traits with an high intra-family variation. 
+% Taxonomic determination to more precise taxonomic levels
 
@@
 % What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
-% Are the differences between continents because of evolution or only because scientists have done more research in one of the continents?
-
-% Outlook: Are there alternatives to trait aggregation?
-Some statistical models combine trait information for priors (species distribution models/population growth models, see Kindvater et al 2018 and Brown & Roff)
-
-% Further ideas: 
-%   - Still some similarities between compared datasets -> Where does the classification come from?
+%   - Where does the classification come from?
 %     Few sources used in NOA also used in AUS:
@@
 %   - Could not include all data due to data gaps -> much needed to be filled -> would maybe change the picture?
+% Are the differences between continents because of evolution or only because scientists have done more research in one of the continents?
 
@@
 % Resp gil complicated: Original data has a lot of zeros, not in the harmonized & aggregated datasets
-% Aggregated data look similar to the harmonized ones, but resp gil is here one of the "extreme" traits 
-% on the conductivity axis
+% Aggregated data look similar to the harmonized ones, but resp_gil is here one of the traits 
+% responding to conductivity, while it is not when using harmonized trait data
 
 % Why did some aggregation methods promote life cycle duration and others not?
-% Mean, median and sd's are all relatively similar across tested datasets for these traits
+% Mean, median and SD of these traits are all relatively similar across the aggregated datasets
 
-% Large scale studies?
+% Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?
 
-% What does this imply for future studies -> return to the introduction
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.

### 2020-11-25 Paper/Draft_harmonization_paper.tex
25.11: Minor update

@@
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
-Indeed, it is questionable whether the aggregation of trait information on species or genus-level to a point estimate on family-level can be an adequate description of a particular trait at all, especially for traits with a high variability.
+Aggregation of trait information on species or genus-level to a point estimate on family-level suggests a precision which is not necessarily present, especially not for traits with a high variability or if trait information on species-level is missing.
 In fact, traits can vary strongly on more precise taxonomic levels than the family-level.
@@
 Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32).
-% Mention that body size is binary coded?
+A reason for this is also that body size was coded binary.
 For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1).
 Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).
-% Include which traits are more consistent?
-% ? How have the aggregation and assignments performed when looking back at the original data?
+
+% Our attempt to synthesize trait information showed
 
 % Conclude:
-% The uncertainty of trait information should be taken into account when developing trait databases and appropriate measures to capture this uncertainty should be established.
-% One should be cautious when aggregating traits with an high intra-family variation. 
-% Taxonomic determination to more precise taxonomic levels
+% The uncertainty of trait information should be taken into account when aggregating traits is necessary and appropriate measures to capture this uncertainty should be established. 
+% ? What measures could this be, e.g. report SD
+
+% Include which traits are more consistent?
+% How have the aggregation and assignments performed when looking back at the original data?
 

### 2020-11-25 Paper/Draft_harmonization_paper.tex
25.11: Small changes before send to Ralf

@@
 The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope.
-We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{stab:trait_definitions}).
+We provide a summary of discrepancies in trait definitions in the appendix (Table \ref{stab:trait_definitions}).
 Both, differences in differentiation and scope can lead to discrepancies in trait definitions.
@@
 The Tachet database captures the food source in an additional grouping feature.
-Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{stab:trait_definitions}).
+Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table \ref{stab:trait_definitions}).
 Locomotion definitions differ also in scope between databases.
@@
 
-Comparing the aggregated trait affinities, in total 15000 ($500$ aggregated traits $*10$ unique comparisons of trait affinities and $3$ scenarios), for each simulated dataset showed that in most simulated datasets the differences between the aggregated traits were small.
+Comparing the aggregated trait affinities, in total 15000 ($500$ aggregated traits $*10$ unique comparisons of trait affinities and $3$ scenarios) for each simulated dataset showed that in most simulated datasets the differences between the aggregated traits were small.
 Only 1.42 \% (213 out of 15.000) of all comparisons showed a difference equal or greater than an absolute trait affinity of 0.1.
 Most of these differences occurred for the \textit{sim\_extreme} scenario (83.5 \%).
-The majority of the differences equal or above 0.1 were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure S\ref{fig:sim_indv_runs}).
+The majority of the differences equal or above 0.1 were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure \ref{fig:sim_indv_runs}).
 % Differences were rather small, largest difference 0.265 for sim_extreme (stepwise_median vs weighted_agg)
@@
 % Is that necessary?
-A comparison of the aggregation methods with each other for the 4 datasets revealed that differences in aggregated trait affinities were largest between the \textit{stepwise\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{median}} (Figure S\ref{fig:comp_aggr_methods}).
+A comparison of the aggregation methods with each other for the 4 datasets revealed that differences in aggregated trait affinities were largest between the \textit{stepwise\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{median}} (Figure \ref{fig:comp_aggr_methods}).
 
@@
 
-% Discussion/Comparison aggr. methods/assigned traits  
-Our results show that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level.
+Our results indicated that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level.
 However, in those cases where differences between trait aggregation methods that use the median and assigned traits occurred, these differences were greater compared to the aggregation methods that used the mean.
-The different weighting methods, i.e.
+The different weightings used by the aggregation methods, i.e.
 aggregating stepwise, direct or weighted, did not seem to have a strong impact, because the distribution of absolute trait affinity differences to assigned traits obtained by the \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}} and \textit{weighted\_agg} were relatively similar in both tested datasets.
@@
 Instead, using the mean or the median changed the distribution of differences in trait affinities between aggregated and assigned traits.
-A possible reason why the use of different weightings for taxa had little impact on trait aggregation is that a considerable portion of taxa used have a low numbers of genera or species entries.
+A possible reason why the use of different weightings for taxa had little impact on trait aggregation is that a considerable portion of taxa used have low numbers of genera or species entries.
 From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \% were resolved on family-level and 61.7 \% were resolved on genus-level.
@@
 
-% Differences between Results of AUS and NOA dataset
+% Improve wording
 Observed differences between aggregated and assigned traits were higher for the North American trait dataset.
 This can be explained by the binary coding of the traits in the North American dataset.
-As a results, traits have been assigned affinities of either 1 or 0.
+As a result, traits have been assigned affinities of either 1 or 0.
 Therefore, traits of a certain grouping feature have in most cases a higher difference in trait affinities to each other than if they were coded with fuzzy codes.
@@
 Aggregation of trait information on species or genus-level to a point estimate on family-level suggests a precision which is not necessarily present, especially not for traits with a high variability or if trait information on species-level is missing.
-In fact, traits can vary strongly on more precise taxonomic levels than the family-level.
+Some traits can vary strongly on more precise taxonomic levels than the family-level.
 For example, Monaghan and Soares found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}.
@@
 thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}.
+% ?Mention intra-species variation of some traits (voltinism varies along climatic gradients)
+% ? Mention: obtaining trait information on species-level is challenging
+% Could lead to data gaps in the datasets
+% ?Would like to connect both parts, but maybe this doesn't make too much sense
 Our analysis showed that disagreement between aggregated and assigned traits was largest for body size and respiration traits.
@@
 Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32).
-A reason for this is also that body size was coded binary.
+% A reason for this is also that body size was coded binary.
 For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1).
 Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).
-
-% Our attempt to synthesize trait information showed
+% So these traits might be highly variable, confirming the earlier mentioned studies partially.
 
@@
 % The uncertainty of trait information should be taken into account when aggregating traits is necessary and appropriate measures to capture this uncertainty should be established. 
-% ? What measures could this be, e.g. report SD
-
-% Include which traits are more consistent?
-% How have the aggregation and assignments performed when looking back at the original data?
+% Fuzzy coding is one option to express uncertainty but is not only used for variabality in traits within taxononomic groups above species-level.
+Also, for variation in traits during development of an organism,
+% ? 
+% ? Other measures possible, e.g. report SD
 
 % Include?:
+% Which traits are more consistent
+% How have the aggregation and assignments performed when looking back at the original data?
 % What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
@@
 The re-analysis showed that neither using harmonised grouping features nor aggregated traits changed drastically the results of the original study.
-The traits that did not respond to the salinity gradient (i.e.
+The traits that did not respond t<o the salinity gradient (i.e.
 not on the extremes of the conductivity axis) in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits.
@@
 
-% Resp gil complicated: Original data has a lot of zeros, not in the harmonized & aggregated datasets
-% Aggregated data look similar to the harmonized ones, but resp_gil is here one of the traits 
-% responding to conductivity, while it is not when using harmonized trait data
+% Situation with Resp gil complicated: 
+% - Original data has a lot of zeros, which are not anymore present in the harmonized & aggregated datasets (see Table S2)
+% - In the analysis with the harmonized dataset resp_gil is not responding to the salinity gradient 
+% - Aggregated data look similar to the harmonized ones, but resp_gil is here one of the traits 
+% responding to conductivity!
 
-% Why did some aggregation methods promote life cycle duration and others not?
-% Mean, median and SD of these traits are all relatively similar across the aggregated datasets
+% Why did some aggregated datasets promote life cycle duration traits and others not?
+% - Results using trait data obtained when aggregating with stepwise_agg (median) and stepwise_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites. 
+% Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites.
+% However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets.
 

### 2020-11-25 Paper/Results/SI.tex
25.11: Small changes before send to Ralf

--- 2020-11-20 Paper/Results/SI.tex
@@
 \label{sec:SI}
-
-\subsection*{Differences in trait affinities obtained by trait aggregation methods com-pared to traits assigned at family-level}
-
-\subsubsection*{Comparison of the trait aggregation methods with each other}
-\label{sec:compa_aggr_methods}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{Comparison_trait_agg_methods.png}
-    \caption{Comparison of trait aggregation methods when aggregating over all traits for all datasets.
-Displayed are means of absolute differences in trait affinities with standard deviations (truncated at 0).
-Compared aggregation methods are displayed on the y-axis.
-N indicates the number of cases where differences occurred.
-Total number of cases: Australia 2223, Europe 3352, New Zealand 777, and North America 4080.}
-    \label{fig:comp_aggr_methods}
-\end{figure}
-
-%\subsubsection*{Simulation of varying taxonomic hierarchies}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
-%     \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
-Boxplots depict results for each trait aggregation method of 100 simulations.
-T1 to T3 are the simulated traits.}
-%     \label{fig:overview_sim_results}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
-%     \caption{Comparison of the results of the trait aggregation methods for every simulated dataset.
-Simulated datasets where absolute differences between aggregated trait affinities were greater than 0.1 are depicted.
-Only the comparisons are shown were differences greater than 0.1 occurred.}
-%     \label{fig:sim_indv_runs}
-% \end{figure}
-
-\subsubsection*{Taxonomic hierarchy in the trait datasets used for comparisons with assigned traits at family-level}
-\label{sec:taxonomic_hierarchy}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_EU.png}
-%     \caption{Number of genera per family and species per genus for the European trait dataset. For better visual display only families with more than 10 genera are displayed.}
-%     \label{fig:tax_hierarchy_EU}
-% \end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NOA.png}
-    \caption{Number of genera per family and species per genus for those families of the North American trait dataset that have been compared to assigned traits at family level.
-For better visual display only families with more than 15 genera are displayed.}
-    \label{fig:tax_hierarchy_NOA}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_AUS.png}
-    \caption{Number of genera per family and species per genus for the Australian trait dataset. For better visual display only families with more than 7 genera are displayed.}
-    \label{fig:tax_hierarchy_AUS}
-\end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NZ.png}
-%     \caption{Number of genera per family and species per genus for the New Zealand trait dataset. For better visual display only families with more than 5 genera are displayed.}
-%     \label{fig:tax_hierarchy_NZ}
-% \end{figure}
-
-\newpage
-
-\subsection*{Re-analysis of Szöcs et al. using harmonized and aggregated grouping features}
-
-\begin{table}[ht]
-    \centering
-    \caption{Mean, median and standard deviation of the traits that were responsive to the salinity gradient in the original study but not when re-analysis with the harmonized dataset trait dataset.} 
-    \label{tab:SI_resp_traits_summary_stats}
-    \begin{tabular}{llccc}
-    \toprule[.1em]
-    Dataset & Trait & Mean & Median & SD \\ 
-    \toprule[.1em]
-    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 \\ 
-      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 \\ 
-      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 \\ 
-      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 \\ 
-      Weighted & Shredder & 0.19 & 0.14 & 0.22 \\ 
-      Harmonized; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 \\ 
-      Original & Shredder & 0.25 & 0.14 & 0.32 \\ 
-      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 \\ 
-      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 \\ 
-      Direct\_median & Gills & 0.30 & 0.30 & 0.32 \\ 
-      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 \\ 
-      Weighted & Gills & 0.30 & 0.30 & 0.32 \\ 
-      Harmonized; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 \\ 
-      Original & Gills & 0.28 & 0.00 & 0.33 \\ 
-      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 \\ 
-      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 \\ 
-      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 \\ 
-      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
-      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
-      Harmonized; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
-      Original & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
-      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 \\ 
-      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 \\ 
-      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 \\ 
-      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
-      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
-      Harmonized; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
-      Original & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-%\subsection*{Re-analysis of Szöcs et al. using harmonized grouping features.}
-%\label{subsec:SI_szoecs_reanalysis}
-
-% \subsubsection*{RDA of trait composition}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{RDA_traits_harmonized.png}
-%     \caption{RDA of traits constrained by electric conductivity using harmonized grouping features.
-Boxplot of site scores along the conductivity axis ($31.44 \%$ explained variance, p = 0.001, 1000 permutations).
-Rug on the right indicates trait scores on the conductivity axis.
-Only traits with a mahalanobis distance greater than 5.02 were labeled in accordance to the procedure in Szöcs et al.
-\cite{szocs_effects_2014}.
-%     } 
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{RDA_traits_Szoecs_2014.png}
-%     \caption{RDA of traits constrained by electric conductivity.
-Boxplot of site scores along the conductivity axis ($30.09 \%$ explained variance, p = 0.001, 1000 permutations).
-Rug on the right indicates trait scores on the conductivity axis.
-Only traits with a mahalanobis distance greater than 5.02 were labeled.
-%     } 
-% \end{figure}
-
-% Not sure if the next two sections are really needed
-% Need also to run analysis again
-%\subsubsection*{Trait distribution along first RDA axis}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_harmonized.png}
-%     \caption{Trait scores on the first RDA axis for harmonized traits and traits of the grouping feature \textit{life cycle duration}.
-%     } 
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_Szoecs_2014.png}
-%     \caption{Trait scores on the first RDA axis for the traits responding to high salinity in Szöcs et al. \cite{szocs_effects_2014}
-%     .
-%     }
-% \end{figure}
-
-\newpage
-% \subsubsection*{Linear models of trait proportions}
-
-% \textit{Linear models of trait proportions with harmonized traits:}
-% \begin{table}[ht]
-%     \centering
-%     \caption{Results of linear models for the four selected harmonized traits and life cycle duration $>$ 1 year.
-Trait proportions were logit transformed prior model building, estimates are on the logit scale.
-Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation.
-Bold values indicate statistically significant effects (p $<$ 0.05).}
-%     \label{stab:linear_models_new}
-%     \begin{tabular}{l|ccccc}
-%     \toprule[.1em]
-%     & \specialcell{Feeding mode:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell{Voltinism:\\ bi- or multivoltine} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
-%     \toprule[.1em]
-%     Intercept ($=$ upstream) & \textbf{-1.041} & \textbf{-0.486} & 0.375* & \textbf{-0.823} & 0.092\\ 
-%     Downstream & \textbf{0.926} & \textbf{0.605} & \textbf{1.376} & \textbf{1.684} & \textbf{0.854}\\ 
-%     Downstream x 2008 & -0.117 & 0.106 & -0.235 & -0.088 & -0.317\\ 
-%     Downstream x 2009 & 0.030 & -0.056 & 0.001 & 0.245 & 0.180\\ 
-%     Year 2008 & -0.167 & -0.115 & 0.033 & -0.182 & -0.151\\ 
-%     Year 2009 & 0.175 & 0.086 & -0.088 & 0.246 & 0.141\\ 
-%     \bottomrule
-%     \end{tabular}
-%     \textit{* p.value = 0.055}
-% \end{table}
-% \newline
-% \newline
-% \newline
-% \textit{Linear models of trait proportions Szöcs et al. :}
-% \begin{table}[ht]
-%     \centering
-%     \caption{Results of linear models for the five selected traits for Szöcs et al.
-\cite{szocs_effects_2014}.
-Trait proportions were logit transformed prior model building, estimates are on the logit scale.
-%     Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically
-%     significant effects (p $<$ 0.05).}
-%     \label{stab:linear_models_edi}
-%     \begin{tabular}{l|ccccc}
-%     \toprule[.1em]
-%     & \specialcell{Feeding habits:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell {Cycles per year:\\ $>$ 1} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
-%     \toprule[.1em]
-%     Intercept ($=$ upstream) & \textbf{-0.853} & \textbf{-0.478} & \textbf{0.603} & \textbf{-0.838} & 0.111 \\ 
-%     Downstream & \textbf{0.819} & \textbf{0.594} & \textbf{1.297} & \textbf{1.679} & \textbf{0.839} \\ 
-%     Downstream x 2008 & -0.155 & 0.102 & -0.227 & -0.070 & -0.314 \\ 
-%     Downstream x 2009 & 0.073 & -0.053 & -0.020 & 0.248 & 0.176 \\ 
-%     Year 2008 & -0.122 & -0.112 & 0.026 & -0.192 & -0.154 \\ 
-%     Year 2009 & 0.167 & 0.084 & -0.104 & 0.250 & 0.139 \\ 
-%     \bottomrule
-%     \end{tabular} 
-% \end{table}
-
-% \subsubsection*{Trait proportions over time}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_harmonized.png}
-%     \caption{Proportions for the four harmonized traits that have been promoted by salinization and life cycle duration $>$ 1 year for down- and upstream sites.
-%     } 
-% \end{figure}
-
-% % Trait proportions over time
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_Szoecs_2014.png}
-%     \caption{Proportions for five selected traits for down- and upstream sites (traits that have been promoted by salinization) from Szöcs et al. \cite{szocs_effects_2014}.} 
-% \end{figure}
 
@@
 
+\subsection*{Differences in trait affinities obtained by trait aggregation methods com-pared to traits assigned at family-level}
+
+\subsubsection*{Comparison of the trait aggregation methods with each other}
+\label{sec:compa_aggr_methods}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{Comparison_trait_agg_methods.png}
+    \caption{Comparison of trait aggregation methods when aggregating over all traits for all datasets.
+Displayed are means of absolute differences in trait affinities with standard deviations (truncated at 0).
+Compared aggregation methods are displayed on the y-axis.
+N indicates the number of cases where differences occurred.
+Total number of cases: Australia 2223, Europe 3352, New Zealand 777, and North America 4080.}
+    \label{fig:comp_aggr_methods}
+\end{figure}
+
+%\subsubsection*{Simulation of varying taxonomic hierarchies}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
+%     \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
+Boxplots depict results for each trait aggregation method of 100 simulations.
+T1 to T3 are the simulated traits.}
+%     \label{fig:overview_sim_results}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
+%     \caption{Comparison of the results of the trait aggregation methods for every simulated dataset.
+Simulated datasets where absolute differences between aggregated trait affinities were greater than 0.1 are depicted.
+Only the comparisons are shown were differences greater than 0.1 occurred.}
+%     \label{fig:sim_indv_runs}
+% \end{figure}
+
+\subsubsection*{Taxonomic hierarchy in the trait datasets used for comparisons with assigned traits at family-level}
+\label{sec:taxonomic_hierarchy}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_EU.png}
+%     \caption{Number of genera per family and species per genus for the European trait dataset. For better visual display only families with more than 10 genera are displayed.}
+%     \label{fig:tax_hierarchy_EU}
+% \end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NOA.png}
+    \caption{Number of genera per family and species per genus for those families of the North American trait dataset that have been compared to assigned traits at family level.
+For better visual display only families with more than 15 genera are displayed.}
+    \label{fig:tax_hierarchy_NOA}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_AUS.png}
+    \caption{Number of genera per family and species per genus for the Australian trait dataset. For better visual display only families with more than 7 genera are displayed.}
+    \label{fig:tax_hierarchy_AUS}
+\end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NZ.png}
+%     \caption{Number of genera per family and species per genus for the New Zealand trait dataset. For better visual display only families with more than 5 genera are displayed.}
+%     \label{fig:tax_hierarchy_NZ}
+% \end{figure}
+
+\newpage
+
+\subsection*{Re-analysis of Szöcs et al. using harmonized and aggregated grouping features}
+
+\begin{table}[ht]
+    \centering
+    \caption{Mean, median and standard deviation of trait affinities that were responsive to the salinity gradient in the original study but not when re-analysis with the harmonized dataset trait dataset.}
+    \label{tab:SI_resp_traits_summary_stats}
+    \begin{tabular}{llccc}
+    \toprule[.1em]
+    Dataset & Trait & Mean & Median & SD \\ 
+    \toprule[.1em]
+    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 \\ 
+      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 \\ 
+      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 \\ 
+      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 \\ 
+      Weighted & Shredder & 0.19 & 0.14 & 0.22 \\ 
+      Harmonized; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 \\ 
+      Original & Shredder & 0.25 & 0.14 & 0.32 \\ 
+      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 \\ 
+      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 \\ 
+      Direct\_median & Gills & 0.30 & 0.30 & 0.32 \\ 
+      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 \\ 
+      Weighted & Gills & 0.30 & 0.30 & 0.32 \\ 
+      Harmonized; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 \\ 
+      Original & Gills & 0.28 & 0.00 & 0.33 \\ 
+      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 \\ 
+      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 \\ 
+      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 \\ 
+      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
+      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
+      Harmonized; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
+      Original & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
+      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 \\ 
+      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 \\ 
+      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 \\ 
+      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
+      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
+      Harmonized; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
+      Original & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
+    \bottomrule
+    \end{tabular}
+\end{table}
+
+%\subsection*{Re-analysis of Szöcs et al. using harmonized grouping features.}
+%\label{subsec:SI_szoecs_reanalysis}
+
+% \subsubsection*{RDA of trait composition}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{RDA_traits_harmonized.png}
+%     \caption{RDA of traits constrained by electric conductivity using harmonized grouping features.
+Boxplot of site scores along the conductivity axis ($31.44 \%$ explained variance, p = 0.001, 1000 permutations).
+Rug on the right indicates trait scores on the conductivity axis.
+Only traits with a mahalanobis distance greater than 5.02 were labeled in accordance to the procedure in Szöcs et al.
+\cite{szocs_effects_2014}.
+%     } 
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{RDA_traits_Szoecs_2014.png}
+%     \caption{RDA of traits constrained by electric conductivity.
+Boxplot of site scores along the conductivity axis ($30.09 \%$ explained variance, p = 0.001, 1000 permutations).
+Rug on the right indicates trait scores on the conductivity axis.
+Only traits with a mahalanobis distance greater than 5.02 were labeled.
+%     } 
+% \end{figure}
+
+% Not sure if the next two sections are really needed
+% Need also to run analysis again
+%\subsubsection*{Trait distribution along first RDA axis}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_harmonized.png}
+%     \caption{Trait scores on the first RDA axis for harmonized traits and traits of the grouping feature \textit{life cycle duration}.
+%     } 
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_Szoecs_2014.png}
+%     \caption{Trait scores on the first RDA axis for the traits responding to high salinity in Szöcs et al. \cite{szocs_effects_2014}
+%     .
+%     }
+% \end{figure}
+
+\newpage
+% \subsubsection*{Linear models of trait proportions}
+
+% \textit{Linear models of trait proportions with harmonized traits:}
+% \begin{table}[ht]
+%     \centering
+%     \caption{Results of linear models for the four selected harmonized traits and life cycle duration $>$ 1 year.
+Trait proportions were logit transformed prior model building, estimates are on the logit scale.
+Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation.
+Bold values indicate statistically significant effects (p $<$ 0.05).}
+%     \label{stab:linear_models_new}
+%     \begin{tabular}{l|ccccc}
+%     \toprule[.1em]
+%     & \specialcell{Feeding mode:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell{Voltinism:\\ bi- or multivoltine} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
+%     \toprule[.1em]
+%     Intercept ($=$ upstream) & \textbf{-1.041} & \textbf{-0.486} & 0.375* & \textbf{-0.823} & 0.092\\ 
+%     Downstream & \textbf{0.926} & \textbf{0.605} & \textbf{1.376} & \textbf{1.684} & \textbf{0.854}\\ 
+%     Downstream x 2008 & -0.117 & 0.106 & -0.235 & -0.088 & -0.317\\ 
+%     Downstream x 2009 & 0.030 & -0.056 & 0.001 & 0.245 & 0.180\\ 
+%     Year 2008 & -0.167 & -0.115 & 0.033 & -0.182 & -0.151\\ 
+%     Year 2009 & 0.175 & 0.086 & -0.088 & 0.246 & 0.141\\ 
+%     \bottomrule
+%     \end{tabular}
+%     \textit{* p.value = 0.055}
+% \end{table}
+% \newline
+% \newline
+% \newline
+% \textit{Linear models of trait proportions Szöcs et al. :}
+% \begin{table}[ht]
+%     \centering
+%     \caption{Results of linear models for the five selected traits for Szöcs et al.
+\cite{szocs_effects_2014}.
+Trait proportions were logit transformed prior model building, estimates are on the logit scale.
+%     Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically
+%     significant effects (p $<$ 0.05).}
+%     \label{stab:linear_models_edi}
+%     \begin{tabular}{l|ccccc}
+%     \toprule[.1em]
+%     & \specialcell{Feeding habits:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell {Cycles per year:\\ $>$ 1} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
+%     \toprule[.1em]
+%     Intercept ($=$ upstream) & \textbf{-0.853} & \textbf{-0.478} & \textbf{0.603} & \textbf{-0.838} & 0.111 \\ 
+%     Downstream & \textbf{0.819} & \textbf{0.594} & \textbf{1.297} & \textbf{1.679} & \textbf{0.839} \\ 
+%     Downstream x 2008 & -0.155 & 0.102 & -0.227 & -0.070 & -0.314 \\ 
+%     Downstream x 2009 & 0.073 & -0.053 & -0.020 & 0.248 & 0.176 \\ 
+%     Year 2008 & -0.122 & -0.112 & 0.026 & -0.192 & -0.154 \\ 
+%     Year 2009 & 0.167 & 0.084 & -0.104 & 0.250 & 0.139 \\ 
+%     \bottomrule
+%     \end{tabular} 
+% \end{table}
+
+% \subsubsection*{Trait proportions over time}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_harmonized.png}
+%     \caption{Proportions for the four harmonized traits that have been promoted by salinization and life cycle duration $>$ 1 year for down- and upstream sites.
+%     } 
+% \end{figure}
+
+% % Trait proportions over time
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_Szoecs_2014.png}
+%     \caption{Proportions for five selected traits for down- and upstream sites (traits that have been promoted by salinization) from Szöcs et al. \cite{szocs_effects_2014}.} 
+% \end{figure}
+
 \end{document}

### 2020-11-26 Paper/Draft_harmonization_paper.tex
26.11: Improved comments for further discussion

@@
 
-\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For convenience and to improve interpretation, we report absolute trait differences.
+\textit{\color{blue} Comment Ralf: Bei Abbildung 1 - finde ich hier nicht, sollte es "lower than" heißen}
 
@@
 
-\newpage
 \section*{Results}
@@
 The simulation results indicated that the choice of the aggregation method for small numbers of genera per family (5) can be important when one genus has a much larger number of species compared to other genera within a particular family.
-% How often in the trait datasets?
+\textit{\color{blue} Maybe include: How often does such a taxonomic data occur in the trait datasets?}
 
-% Improve wording
+\textit{\color{red}Need to improve the wording in the next paragraph}
+
 Observed differences between aggregated and assigned traits were higher for the North American trait dataset.
@@
 
-% Discussion on differences between aggregated and assigned traits  
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
@@
 thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}.
-% ?Mention intra-species variation of some traits (voltinism varies along climatic gradients)
-% ? Mention: obtaining trait information on species-level is challenging
-% Could lead to data gaps in the datasets
-% ?Would like to connect both parts, but maybe this doesn't make too much sense
+\textit{\color{blue} Could mention here: \begin{itemize}
+  \item Intra-species variation of some traits (voltinism varies along climatic gradients)
+  \item Obtaining trait information on species-level is challenging
+\end{itemize}}
+
 Our analysis showed that disagreement between aggregated and assigned traits was largest for body size and respiration traits.
@@
 Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32).
-% A reason for this is also that body size was coded binary.
+A reason for the large differences we obtained is also that body size was coded binary.
 For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1).
 Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).
-% So these traits might be highly variable, confirming the earlier mentioned studies partially.
 
-% Conclude:
-% The uncertainty of trait information should be taken into account when aggregating traits is necessary and appropriate measures to capture this uncertainty should be established. 
-% Fuzzy coding is one option to express uncertainty but is not only used for variabality in traits within taxononomic groups above species-level.
-Also, for variation in traits during development of an organism,
-% ? 
-% ? Other measures possible, e.g. report SD
+\textit{\color{blue} This paragraph misses a connection to the paragraph above, e.g.: 
+\begin{itemize}
+  \item These traits might be highly variable, confirming the earlier mentioned studies partially.
+\end{itemize}}
 
-% Include?:
-% Which traits are more consistent
-% How have the aggregation and assignments performed when looking back at the original data?
-% What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
-%   - Where does the classification come from?
-%     Few sources used in NOA also used in AUS:
-%     AUS: Merrit & Cummins 1978/1984 for feeding mode for a few genera and families 
-%     NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait description "Cummins, K.
+\textit{\color{blue} Ideas for concluding this section:
+\begin{itemize}
+  \item The uncertainty of trait information should be taken into account when aggregating traits and appropriate measures to capture this uncertainty should be established.
+  \item Fuzzy coding is one option to express uncertainty, but it's not only used for variability in traits within taxononomic groups above species-level.
+It's also used for variation in traits during the development of an organism.
+So it's not really clear for fuzzy coded taxa on family-level what uncertainty is expressed?
+  \item Are other measures of uncertainty thinkable, e.g. based on SD or Variance 
+\end{itemize}
+}
+
+\textit{\color{blue} Further ideas what could be included: 
+\begin{itemize}
+  \item Which traits are more consistent
+  \item How have the aggregation and assignments performed when looking back at the original data?
+  \item hat do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
+  \item Where does the classification come from?
+  \begin{itemize}
+    \item  Where does the classification come from? Few sources used in NOA also used in AUS:
+    \item AUS: Merrit \& Cummins 1978/1984 for feeding mode for a few genera and families 
+    \item     NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait description "Cummins, K.
 W.
 Trophic Relations of Aquatic Insects" was used for feeding mode
-%   - Could not include all data due to data gaps -> much needed to be filled -> would maybe change the picture?
-% Are the differences between continents because of evolution or only because scientists have done more research in one of the continents?
+  \end{itemize}
+  \item Could not include all data due to data gaps. Would the picture change if these would be filled?
+  \item Are the differences between continents because of evolution or only because scientists have done more research in one of the continents? (from Co-authors)
+\end{itemize}
+}
 
@@
 
-% Situation with Resp gil complicated: 
-% - Original data has a lot of zeros, which are not anymore present in the harmonized & aggregated datasets (see Table S2)
-% - In the analysis with the harmonized dataset resp_gil is not responding to the salinity gradient 
-% - Aggregated data look similar to the harmonized ones, but resp_gil is here one of the traits 
-% responding to conductivity!
-
-% Why did some aggregated datasets promote life cycle duration traits and others not?
-% - Results using trait data obtained when aggregating with stepwise_agg (median) and stepwise_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites. 
-% Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites.
-% However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets.
-
-% Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
+\textit{\color{blue}
+\begin{itemize}
+  \item Resp gills: Original data has a lot of zeros, which are not present in the harmonized \& aggregated datasets (see Table S2)
+  \begin{itemize}
+    \item In the analysis with the harmonized dataset resp gills is not responding to the salinity gradient
+    \item Aggregated data look similar to the harmonized ones, but resp gills is here one of the traits 
+    responding to conductivity!
+  \end{itemize} 
+  \item Why did some aggregated datasets promote life cycle duration traits and others not
+  \begin{itemize}
+    \item Results using trait data obtained when aggregating with stepwise\_agg (median) and stepwise\_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites.
+    \item Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites
+    \item However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets (see Table S2). 
+  \end{itemize}
+  \item Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?
+  \item Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
 I wonder if this indicates that Family richness is really higher in Australia.
@@
 This would be worth considering in the discussion
-
+\end{itemize}
+}
 \newpage

### 2020-11-30 Paper/Draft_harmonization_paper.tex
30.11: Added Ralfs comments

@@
 For convenience and to improve interpretation, we report absolute trait differences.
-\textit{\color{blue} Comment Ralf: Bei Abbildung 1 - finde ich hier nicht, sollte es "lower than" heißen}
 
@@
 
+% Start general
+% Why do we need trait-based analysis, what's the problem with the state of data coverage
+% Implications of trait definitions chapter
+
+% Keine Überscrhiften kopieren: sollte eher eine generelle Aussage haben
 \subsection*{Differences in trait affinities obtained by trait aggregation methods compared to traits assigned at family-level}
 
-Our results indicated that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level.
+% Hier erstmal ein Satz allgemeiner Einstieg
+% Z.B.: We analysed the difference between aggregated and traits assigned by experts for two data sets on..
+Our results indicated that aggregation of traits by median compared to aggregating by mean is often closer to the assigned traits at family level. 
+% Those cases...R: schwierig einzuordnen - waren das viele - was sind das für fälle
 However, in those cases where differences between trait aggregation methods that use the median and assigned traits occurred, these differences were greater compared to the aggregation methods that used the mean.
 The different weightings used by the aggregation methods, i.e.
-aggregating stepwise, direct or weighted, did not seem to have a strong impact, because the distribution of absolute trait affinity differences to assigned traits obtained by the \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}} and \textit{weighted\_agg} were relatively similar in both tested datasets.
+aggregating stepwise, direct or weighted, had a minor impact,
+% R: Unverständlich - kann auch sein, weil ich die neue Sodom nebenbei höre - aber soll das erklären, warum der impact minor war - oder erklärt das noch mal die Ergebnisse
+because the distribution of absolute trait affinity differences to assigned traits obtained by the \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}} and \textit{weighted\_agg} were relatively similar in both tested datasets.
 This also applies to the distributions of absolute trait affinity differences obtained by \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}.
+% R: Steht das nicht schon im zweiten Satz? True rm!
+% Klarstellen was gemacht wurde 
 Instead, using the mean or the median changed the distribution of differences in trait affinities between aggregated and assigned traits.
-A possible reason why the use of different weightings for taxa had little impact on trait aggregation is that a considerable portion of taxa used have low numbers of genera or species entries.
+The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species entries.
+% R: Too much precision with the numbers
 From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \% were resolved on family-level and 61.7 \% were resolved on genus-level.
 52.1 \% had 5 or less genera and 12.8 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
+% R: Das Argument ist schwer greifbar für den Leser - es wäre einfacher zu folgen, wenn Du schreiben würdest, wann man denn mit unterschieden rechnen würde und warum - und dann deine Daten beschreiben.
+Also wenn es sehr viele Genera und diese mit sehr unterschiedlicher Anzahl an Arten wären usw.
+.
+Die Diskussion sollte vor allen Dingen allgemeiner verständniclih sein und nicht technisch die Resultate fortsetzen.
 In the Australian dataset 21.4 \% of the compared taxa had trait information resolved on family-level, 39.5 \% resolved on genus level, and 39.1 \% resolved on species-level.
@@
 The simulation results indicated that the choice of the aggregation method for small numbers of genera per family (5) can be important when one genus has a much larger number of species compared to other genera within a particular family.
+
+% R: Allgemein in Trait data sets - ja geht in die Richtung, wobei du ja hier nicht noch analysen für alle möglichen Tiere und traits machen kannst, aber zumindest aufzeigen unter welchen Umständen es bedeutsam ist - und was dann gemacht werden sollte.
+Der Leser will ja aus der Diskussion etwas mitnehmen, ggf.
+auch was er tun soll
 \textit{\color{blue} Maybe include: How often does such a taxonomic data occur in the trait datasets?}
 
-\textit{\color{red}Need to improve the wording in the next paragraph}
-
+% R: OK - hier soll einfach gesagt werden, dass bei 0 1 Codierung die Differenzen auch größer werden.
+Macht Sinn, kann man so schreiben - sollte aber auch stärker mit dem vorherigen Abschnitt verknüpft werden.
+The differences between aggregated and assigned traits (kann man das nicht irgendwo kürzer und eleganter beschreiben?) depended on the coding.
+The database with ..
+coding had the highest..
 Observed differences between aggregated and assigned traits were higher for the North American trait dataset.
@@
 
+% R: Man könnte das ggf.
+auch an den Anfang ziehen.
+Also einleitend: Warum ist die Frage wichtig, was haben wir überhaupt gemacht - und dann eben erst mal sagen, dass die Analysen zwischen aggregated und assigned traits jetzt nicht die ultimative Wahrheit sind.
+Gleichwohl unsere Ergebnisse anzeigen können, welche Methoden überhaupt und unter welchen Umständen zu unterschiedlichen Ergebnissen führen, so dass die Leser dort entsprechend vorsichtig sein müssten
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
@@
 thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}.
+
+% R: Könnte man beides erwähnen - aber insgesamt würde ich nicht zu viele Sachen reinpacken, sonst mäandert es so sehr.
+Aber ein Hinweis, dass es bei großskaligen Analysen vielleicht auch wichtiger ist usw.
+wegen klimatischer Unterschiede - wobei die ja eher dann auch intra-species variieren und das ja gar nicht viel mit dem aktuellen Vergleich der aggregationsmethoden zu tun hat.
+Im Prinzip gehört das eher in einen einleitenden Abschnitt zu traits allgemeiner
 \textit{\color{blue} Could mention here: \begin{itemize}
@@
 
+% Das liest sich wie einer erweiterte Resultate Sectioin - das ist nicht Sinn der Diskussion.
+Du sollst da nicht neue Ergebnisse vorstellen sondern dann eher auf eine Abbildung verweisen und in der Regel in 2-3 Sätzen die Ergebnissen in einfachen Sätzen nennen und diskutieren d.h.
+in Kontext anderer Studien stellen - oder wenn es diese nicht gibt, was auch gesagt werden müsste, dann sagen, was daraus folgt.
 Our analysis showed that disagreement between aggregated and assigned traits was largest for body size and respiration traits.
@@
 
+% Stay focused!
+Schneide nicht zu viele Themen an - Du musst nicht jedes einzelne Thema diskutieren.
+Generell kann die Diskussion so 3-4 Abschnitte haben, die jeweils die wichtigsten Resultate oder Aspekte diskutieren.
+Eine generelle Diskussion der Fuzzy Coding und intra-species variation wäre aus meiner Sicht eher ein eigener, wenn auch nicht allzulanger Abschnit
 \textit{\color{blue} Ideas for concluding this section:
@@
   \item How have the aggregation and assignments performed when looking back at the original data?
+
+  % eigenes Thema/abschnitt - sicherlich nicht umspannen - wäre eher so am ende auch, was an Forschung noch notwendig ist - quality evaluation of traits als Thema..
   \item hat do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
@@
   \end{itemize}
-  \item Could not include all data due to data gaps. Would the picture change if these would be filled?
-  \item Are the differences between continents because of evolution or only because scientists have done more research in one of the continents? (from Co-authors)
 \end{itemize}
@@
 
-The re-analysis showed that neither using harmonised grouping features nor aggregated traits changed drastically the results of the original study.
-The traits that did not respond t<o the salinity gradient (i.e.
+% R: Misses a starting sentence, Why did we conduct this analysis?
+The re-analysis showed that both using harmonised grouping features and aggregated traits lead to similar results as the original study.
+% R: Schwer zu verstehen - versuche positive Sätze nicht negative - also nicht "did not respond" eher "without response" or eben wirklcih positiv "traits that responded only in the original analysis but were non-responsive in the reanalysis
+The traits that did not respond to the salinity gradient (i.e.
 not on the extremes of the conductivity axis) in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits.
@@
 
+% Keep it simple!
 \textit{\color{blue}
@@
   \item Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?
+
+ % R: Ja, müsste aber wenn an den Anfang wo es um generell um Traits geht, siehe auch email.
+Könnte mir vorstellen 4 Abschnitte zu machen: 1.
+Trait Database - Unterschiede zwischen Regionen und Trait Genauigkeit - Was kann man machen - Andere Studien zur Trait Harmonisierung usw.
+2.
++ 3.
+die aktuellen Abschnitte (obwohl sie auch etwas ähnliche Themen beinhalten - geht ja immer um was ähnliches - wie gut sind die Aggregationsmethoden - könnte man vielleicht auch zusammenfassen 4.
+Ausblick und offene Fragen für zukünftige Studien
+
   \item Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
@@
 }
+
+% 1. Allgemeiner Satz zum Thema, der auf eine offene Frage o.ä. hinweist
+% 2. Was haben wir herausgefunden?
+% 3. Was haben andere schon herausgefunden
+% 4. Was bedeutet das für zukünftige Studien?
+
 \newpage

### 2020-12-03 Paper/Draft_harmonization_paper.tex
03.12.2020: Update Discussion

--- 2020-11-25 Paper/Draft_harmonization_paper.tex
@@
 In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonized using standardized terminology.
-However, a lack of standardized terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology \cite{baird_toward_2011, schneider_towards_2019}.
+However, a lack of standardized terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology \cite{baird_toward_2011, kissling_towards_2018}.
 Secondly, consistent coding of traits facilitates the compatibility of trait data from different databases.
@@
 tolerance of pollution, body size).
-One approach for dealing with uncertainty is the use of fuzzy coded grouping features, where the traits are assigned probabilistic values.
+One approach for dealing with uncertainty is the use of fuzzy coding, where the traits are assigned probabilistic values.
 Fuzzy codes are used to account for plasticity in traits, variability in traits within taxonomic groups above species, and incomplete knowledge and are usually converted to proportions.
-In this study we denote the proportionate description (0-1) of traits as affinities or affinity scores.
+In this study we denote the probabilistic values (0-1) of traits as affinities or affinity scores.
 
@@
 
-Various codings of traits are used throughout the databases (e.g.
+Various codings to describe traits are used throughout the databases (e.g.
 binary, fuzzy, continuous).
@@
 
-\subsection*{Differences in trait affinities obtained by trait aggregation methods compared to traits assigned at family-level}
+% 1. Allgemeiner Satz zum Thema, der auf eine offene Frage o.ä. hinweist
+% 2. Was haben wir herausgefunden?
+% 3. Was haben andere schon herausgefunden
+% 4. Was bedeutet das für zukünftige Studien?
 
-Our results indicated that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level.
-However, in those cases where differences between trait aggregation methods that use the median and assigned traits occurred, these differences were greater compared to the aggregation methods that used the mean.
-The different weightings used by the aggregation methods, i.e.
-aggregating stepwise, direct or weighted, did not seem to have a strong impact, because the distribution of absolute trait affinity differences to assigned traits obtained by the \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}} and \textit{weighted\_agg} were relatively similar in both tested datasets.
-This also applies to the distributions of absolute trait affinity differences obtained by \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}.
-Instead, using the mean or the median changed the distribution of differences in trait affinities between aggregated and assigned traits.
-A possible reason why the use of different weightings for taxa had little impact on trait aggregation is that a considerable portion of taxa used have low numbers of genera or species entries.
-From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \% were resolved on family-level and 61.7 \% were resolved on genus-level.
-52.1 \% had 5 or less genera and 12.8 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
-In the Australian dataset 21.4 \% of the compared taxa had trait information resolved on family-level, 39.5 \% resolved on genus level, and 39.1 \% resolved on species-level.
-67.73 \% of the taxa contain 5 or less genera and 39.6 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}).
-The simulation results indicated that the choice of the aggregation method for small numbers of genera per family (5) can be important when one genus has a much larger number of species compared to other genera within a particular family.
-% How often in the trait datasets?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 1. Trait Database 
+%- Unterschiede zwischen Regionen und Trait Genauigkeit
+%- Was kann man machen
+%- Andere Studien zur Trait Harmonisierung usw.
 
-% Improve wording
-Observed differences between aggregated and assigned traits were higher for the North American trait dataset.
-This can be explained by the binary coding of the traits in the North American dataset.
-As a result, traits have been assigned affinities of either 1 or 0.
-Therefore, traits of a certain grouping feature have in most cases a higher difference in trait affinities to each other than if they were coded with fuzzy codes.
+% Why do we need trait-based analysis, especially across regions?
+Synthesizing trait information from various trait databases is crucial to unfold the full potential of trait-based approaches, e.g.
+for studying community trait responses to environmental gradients worldwide.
+Our attempt of harmonising trait information from multiple trait databases showed that grouping feature harmonisation is labour-intensive because grouping features are differentiated differently into traits between trait databases.
+In addition, the same traits are sometimes defined differently in the investigated databases, requiring expert knowledge to amalgamate these traits (e.g.
+the trait piercer in the Tachet database, Table \ref{tab:traits_harmonization}).
+Thus, the field of freshwater ecology needs terminological standards to facilitate data synthesis.
+Harmonised definitions and concepts of traits have been for example developed for plants with the \textit{Thesaurus Of Plant characteristics} (TOP) initiative \cite{garnier_towards_2017}.
+The core of this harmonisation initiative is not only to provide standardized trait definitions but also to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field.
+Such initiatives could be a role model for freshwater science to establish unambiguous terminologies for invertebrate traits.
+The existing freshwater invertebrate trait databases could then be linked through standardised terminologies or ontologies, as suggested by Baird et al.
+almost a decade ago \cite{baird_toward_2011}.
+By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS) providers of invertebrate trait data could connect their traits to such ontologies \cite{schneider_towards_2019}.
+Once standardised trait definitions are established, these will improve trait data sharing, trait data processing when working with multiple trait databases, and ultimately improve interpretation of derived results.
+% What is not mentioned here is how traits are measured, for which measurement protocols exist I believe.
+I think this is an separate issue.
 
-% Discussion on differences between aggregated and assigned traits  
+%%% No section on codings?
+% Besides semantic heterogeneity between traits and grouping features, codings used to describe traits differ between trait databases.
+% We showed that fuzzy coded and binary coded could be used together but a lot of assumptions have been made here?
+%%% Section to different codings -> what is an appropriate question?
+% Maybe this section is not necessary and just one or two sentences to various codings is sufficient
+% The European and Australian trait databases use several codings for their traits (fuzzy, binary and continuous) while the North American databases only use binary coding and the New Zealand database only fuzzy coding.
+% due to a lack of species trait information.
+% Differences in fuzzy coding:
+% freshecol: 
+% It is based on the average distributions, occurrences or behaviours of a taxon within the environmental gradient or organismic flexibility under consideration.
+The ten point assignment system was first introduced by Zelinka and Marvan (1961) for the classification of saprobic valences and was extended by Moog (1995) to other parameters, such as stream zonation preferences and feeding types.
+Within freshwaterecology.info the ten point assignment system was used for coding the majority of those parameters, which comprise several categories.
+% Example for the parameter "stream zonation preference": If 70% of a species’ records are observed in spring brooks and 30% in the upper trout region, 7 out of 10 points will be allocated to the category "hypocrenal" (spring brook) and 3 points to "epirhithral" (upper trout region) to describe the expected occurrence of this species within the longitudinal zonation of a river.
+For all other categories "0" will be used.
+% Tachet: 0 - 5: Thereby, the relevant features of a taxon were described by the relative distribution of the information among the categories of each trait.
+This procedure was a pertinent and simple way to "translate" the available knowledge about species traits of organisms into numerical values.
+It also avoided the obligate assignment of a taxon to a single category, which can lead to inaccurate characterisation of biological or ecological trait profiles
+% Can be converted so that they can be used together 
+% As already stated fuzzy coding is used to express uncertainty in traits, for variability in traits within taxononomic groups above species-level or for variation in traits during the development of an organism.
+So it's not really clear for fuzzy coded taxa on family-level what uncertainty is expressed
+% Fuzzy coding captures uncertainty. Nice way but has also drawbacks -> correlated variables, needs specific statistic methods, cannot be used in bayesian priors etc.
+% Binary coding is, transformed to 0 and 1, and thus converted just a "variant" of fuzzy coding?
+% Problems fuzzy coding: Which uncertainty do they cover?
+% Stay focused!
+Schneide nicht zu viele Themen an - Du musst nicht jedes einzelne Thema diskutieren.
+Generell kann die Diskussion so 3-4 Abschnitte haben, die jeweils die wichtigsten Resultate oder Aspekte diskutieren.
+Eine generelle Diskussion der Fuzzy Coding und intra-species variation wäre aus meiner Sicht eher ein eigener, wenn auch nicht allzulanger Abschnit
+% \textit{\color{blue} Ideas for concluding this section:
+% \begin{itemize}
+%   \item The uncertainty of trait information should be taken into account when aggregating traits and appropriate measures to capture this uncertainty should be established.
+%   \item Are other measures of uncertainty thinkable, e.g. based on SD or Variance 
+% \end{itemize}
+% }
+
+%%%%%%% Section on taxonomic levels and data coverage
+%? What's the problem with the state of data coverage
+Our analysis aimed to use most of the available trait information for different regions to establish harmonised grouping feature datasets.
+Although many taxa are coverd in the trait databases, the availability of trait information varies strongly across grouping features and taxonomic resolution differs between databases.
+% freshwaterecolgy.info on species-level, Australia mainy taxa on genus and family-level
+% Pointing to the problem of how accurate information on levels with lower taxonomic precision is 
+% For some groups, species and genus-level identification important since information varies considerably in these groups; see Serra Paper!
+% Erwähnen? Obtaining trait information on species-level is challenging
+% How would this change our results?
+
+% Include Ben's point?
+% Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
+I wonder if this indicates that Family richness is really higher in Australia.
+Perhaps it might be as Australia has a wider range of evolutionary histories.
+This would be worth considering in the discussion
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 2.
++ 3.
+die aktuellen Abschnitte (obwohl sie auch etwas ähnliche Themen beinhalten - geht ja immer um was ähnliches - wie gut sind die Aggregationsmethoden - könnte man vielleicht auch zusammenfassen
+% Hier: Überschrift mit genereller Aussage?
+
+% Why is it important to investigate trait aggregation methods? And trait harmonisation?
+
+% R: Man könnte das ggf.
+auch an den Anfang ziehen.
+Also einleitend: Warum ist die Frage wichtig, was haben wir überhaupt gemacht - und dann eben erst mal sagen, dass die Analysen zwischen aggregated und assigned traits jetzt nicht die ultimative Wahrheit sind.
+Gleichwohl unsere Ergebnisse anzeigen können, welche Methoden überhaupt und unter welchen Umständen zu unterschiedlichen Ergebnissen führen, so dass die Leser dort entsprechend vorsichtig sein müssten
+
+As outlined in the introduction, various trait aggregation methods are used by researchers when trait data are on more precise taxonomic levels than observational data.
+We aggregated traits from an Australian and North American trait dataset to family-level using 5 different aggregation methods and compared the results to traits assigned at family-level for these regions.
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
@@
 thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}.
-% ?Mention intra-species variation of some traits (voltinism varies along climatic gradients)
-% ? Mention: obtaining trait information on species-level is challenging
-% Could lead to data gaps in the datasets
-% ?Would like to connect both parts, but maybe this doesn't make too much sense
-Our analysis showed that disagreement between aggregated and assigned traits was largest for body size and respiration traits.
-The highest possible difference of 1 between aggregated trait affinities and assigned trait affinities (in total in 6.9 \% of all cases) for the Australian dataset occurred most often for body size large and medium (42.5 \% and 39.2 \% of all cases with a difference of 1, respectively) across all comparisons of aggregated and assigned traits.
-Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32).
-% A reason for this is also that body size was coded binary.
-For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1).
-Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).
-% So these traits might be highly variable, confirming the earlier mentioned studies partially.
+However, if trait aggregation is necessary our study can give guidance, under which circumstances the choice of aggregation method might be important.
+The 5 aggregation methods we tested use either the mean or the median and different weightings.
+Our results indicated that 1) aggregation of traits using \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{mean}} (median aggregation methods) compared to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_mean} (mean aggregation methods) is often closer to the assigned traits at family-level and 2) that the different weightings tested exerted a minor impact on the aggregated trait affinities.
+We obtained for both datasets more differing cases for mean aggregation methods, irrespective of the weighting.
+In the Australian dataset, the amount of differing cases was slightly higher for the mean aggregation methods (23 \%) than for median aggregation methods (16 to 18 \% differing cases).
+In the North American dataset, mean aggregation methods yielded in 47 \% of the cases a difference to the assigned traits, much higher in comparison to the median aggregation methods (between 15 and 18 \%, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
+However, when there were differences between median aggregation methods and assigned traits, these differences were greater compared to the mean aggregation methods, particularly for the North American trait dataset.
+The mean absolute differences for the median aggregations was twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
+The differences can be explained by the binary coding used in the North American trait dataset and in the assigned traits for North America.
+As a result, traits have affinities of either 1 or 0.
+Therefore, traits of a particular grouping feature have in most cases a higher difference in trait affinities to each other than if they were fuzzy coded.
+Using the median to aggregate binary coded taxa will often result in a value of 0 or 1, while using the mean will often result in values between 0 and 1.
+Thus, using the median led for the North American dataset in many cases either to agreement with the assigned traits or the difference between median aggregated traits and assigned traits was often 1.
+% except for traits were binary coding was not mutually exclusive and when same number of 0 and 1
+% Binary coding also explains the amount of differing cases, median often right for binary data, must be cautious when a lot of traits are unknown?
+The number of differing cases and the mean absolute differences to the assigned traits were similar within the mean aggregation and within the median aggregation methods, which confirms our second finding, the small influence of weighting on the aggregation methods.
+Furthermore, the distributions of absolute trait affinity differences to assigned traits obtained were relatively similar for the mean aggregation methods and the median aggregation methods in both tested datasets (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
+The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species entries.
+From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 14 \% were resolved on family-level and 62 \% were resolved on genus-level.
+52 \% had 5 or less genera and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
+In the Australian dataset 21 \% of the taxa were resolved on family-level, 40 \% were resolved on genus level, and 39 \% were resolved on species-level.
+68 \% of the taxa contain 5 or less genera and 40 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}).
 
-% Conclude:
-% The uncertainty of trait information should be taken into account when aggregating traits is necessary and appropriate measures to capture this uncertainty should be established. 
-% Fuzzy coding is one option to express uncertainty but is not only used for variabality in traits within taxononomic groups above species-level.
-Also, for variation in traits during development of an organism,
-% ? 
-% ? Other measures possible, e.g. report SD
+Although the simulation results showed only small differences between the results of the aggregation methods the choice of the aggregation method for small numbers of genera per family can be important when one genus has a much larger number of species compared to other genera within a particular family.
+% R: Das Argument ist schwer greifbar für den Leser - es wäre einfacher zu folgen, wenn Du schreiben würdest, wann man denn mit unterschieden rechnen würde und warum - und dann deine Daten beschreiben.
+Also wenn es sehr viele Genera und diese mit sehr unterschiedlicher Anzahl an Arten wären usw.
+.
+Die Diskussion sollte vor allen Dingen allgemeiner verständniclih sein und nicht technisch die Resultate fortsetzen.
 
-% Include?:
-% Which traits are more consistent
-% How have the aggregation and assignments performed when looking back at the original data?
+% R: Allgemein in Trait data sets - ja geht in die Richtung, wobei du ja hier nicht noch analysen für alle möglichen Tiere und traits machen kannst, aber zumindest aufzeigen unter welchen Umständen es bedeutsam ist - und was dann gemacht werden sollte.
+Der Leser will ja aus der Diskussion etwas mitnehmen, ggf.
+auch was er tun soll
+\textit{\color{blue} Maybe include: How often does such a taxonomic data occur in the trait datasets?}
+% Das liest sich wie einer erweiterte Resultate Sectioin - das ist nicht Sinn der Diskussion.
+Du sollst da nicht neue Ergebnisse vorstellen sondern dann eher auf eine Abbildung verweisen und in der Regel in 2-3 Sätzen die Ergebnissen in einfachen Sätzen nennen und diskutieren d.h.
+in Kontext anderer Studien stellen - oder wenn es diese nicht gibt, was auch gesagt werden müsste, dann sagen, was daraus folgt.
+
+% R: Misses a starting sentence, Why did we conduct this analysis?
+In the re-analysis where we investigated how using harmonised and aggregated traits might change the results of trait-environment relationships we found similar results compared the original study.
+Traits that responded only in the original analysis but were non-response in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits.
+For example, during harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder).
+As a result, the trait affinities in the original dataset have a higher mean and standard deviation than in the aggregated and harmonized datasets (Table S\ref{tab:SI_resp_traits_summary_stats}).
+Hence, the signal in the original data for the trait shredder has presumably been weakened by the harmonization, which might be the reason that shredders showed a less strong reaction to the salinity gradient.
+
+% Keep it simple!
+% Resp gills: Original data has a lot of zeros, which are not present in the harmonized \& aggregated datasets (see % In the analysis with the harmonized dataset resp gills is not responding to the salinity gradient
+% Aggregated data look similar to the harmonized ones, but resp gills is here one of the traits responding to conductivity!
+% Why did some aggregated datasets promote life cycle duration traits and others not
+% Results using trait data obtained when aggregating with stepwise\_agg (median) and stepwise\_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites.
+% Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites
+% However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets (see Table S2). 
+% Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 4. Ausblick und offene Fragen für zukünftige Studien
+
 % What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
-%   - Where does the classification come from?
-%     Few sources used in NOA also used in AUS:
-%     AUS: Merrit & Cummins 1978/1984 for feeding mode for a few genera and families 
+% quality evaluation of traits als Thema..
+
+% Where does the classification come from? Few sources used in NOA also used in AUS:
+% AUS: Merrit \& Cummins 1978/1984 for feeding mode for a few genera and families 
 % NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait description "Cummins, K.
@@
 Trophic Relations of Aquatic Insects" was used for feeding mode
-%   - Could not include all data due to data gaps -> much needed to be filled -> would maybe change the picture?
-% Are the differences between continents because of evolution or only because scientists have done more research in one of the continents?
-
-\subsection*{Re-analysis of Szöcs et al. using harmonized and aggregated grouping features}
-
-The re-analysis showed that neither using harmonised grouping features nor aggregated traits changed drastically the results of the original study.
-The traits that did not respond t<o the salinity gradient (i.e.
-not on the extremes of the conductivity axis) in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits.
-During harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder).
-As a result, the trait affinities in the original dataset have a higher mean and standard deviation than in the aggregated and harmonized datasets (Table S\ref{tab:SI_resp_traits_summary_stats}).
-Hence, the signal in the original data for the trait shredder has presumably been weakened by the harmonization, which might be the reason that shredders showed a less strong reaction to the salinity gradient.
-
-% Situation with Resp gil complicated: 
-% - Original data has a lot of zeros, which are not anymore present in the harmonized & aggregated datasets (see Table S2)
-% - In the analysis with the harmonized dataset resp_gil is not responding to the salinity gradient 
-% - Aggregated data look similar to the harmonized ones, but resp_gil is here one of the traits 
-% responding to conductivity!
-
-% Why did some aggregated datasets promote life cycle duration traits and others not?
-% - Results using trait data obtained when aggregating with stepwise_agg (median) and stepwise_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites. 
-% Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites.
-% However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets.
-
-% Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
-I wonder if this indicates that Family richness is really higher in Australia.
-Perhaps it might be as Australia has a wider range of evolutionary histories.
-This would be worth considering in the discussion
 

### 2020-12-08 Paper/Draft_harmonization_paper.tex
08.12: Discussion updates

@@
 % Why do we need trait-based analysis, especially across regions?
-Synthesizing trait information from various trait databases is crucial to unfold the full potential of trait-based approaches, e.g.
+Synthesizing trait information from multiple trait databases is crucial to unfold the full potential of trait-based approaches, e.g.
 for studying community trait responses to environmental gradients worldwide.
-Our attempt of harmonising trait information from multiple trait databases showed that grouping feature harmonisation is labour-intensive because grouping features are differentiated differently into traits between trait databases.
-In addition, the same traits are sometimes defined differently in the investigated databases, requiring expert knowledge to amalgamate these traits (e.g.
+Our attempt of harmonising invertebrate trait information from trait databases of different regions showed that grouping feature harmonisation is labour-intensive because grouping features are differentiated differently into traits between trait databases and various codings are used to describe traits.
+In addition, the same traits are sometimes defined differently in the investigated databases, requiring expert knowledge to reclassify these traits (e.g.
 the trait piercer in the Tachet database, Table \ref{tab:traits_harmonization}).
-Thus, the field of freshwater ecology needs terminological standards to facilitate data synthesis.
-Harmonised definitions and concepts of traits have been for example developed for plants with the \textit{Thesaurus Of Plant characteristics} (TOP) initiative \cite{garnier_towards_2017}.
-The core of this harmonisation initiative is not only to provide standardized trait definitions but also to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field.
+Although, others have noted the lack of standardized trait terminology in freshwater ecology \cite{baird_toward_2011, brink_traits-based_2011} we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
+To resolve definition discrepancies and facilitate data synthesis terminological standards are needed.
+Harmonised definitions and concepts of traits have been developed in the past, e.g.
+for plants with the \textit{Thesaurus Of Plant characteristics} (TOP) initiative \cite{garnier_towards_2017}.
+The core of this harmonisation initiative is to provide standardized trait definitions and to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field.
 Such initiatives could be a role model for freshwater science to establish unambiguous terminologies for invertebrate traits.
 The existing freshwater invertebrate trait databases could then be linked through standardised terminologies or ontologies, as suggested by Baird et al.
-almost a decade ago \cite{baird_toward_2011}.
+\cite{baird_toward_2011} almost a decade ago.
 By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS) providers of invertebrate trait data could connect their traits to such ontologies \cite{schneider_towards_2019}.
@@
 
-%%% No section on codings?
-% Besides semantic heterogeneity between traits and grouping features, codings used to describe traits differ between trait databases.
-% We showed that fuzzy coded and binary coded could be used together but a lot of assumptions have been made here?
-%%% Section to different codings -> what is an appropriate question?
-% Maybe this section is not necessary and just one or two sentences to various codings is sufficient
-% The European and Australian trait databases use several codings for their traits (fuzzy, binary and continuous) while the North American databases only use binary coding and the New Zealand database only fuzzy coding.
-% due to a lack of species trait information.
-% Differences in fuzzy coding:
-% freshecol: 
-% It is based on the average distributions, occurrences or behaviours of a taxon within the environmental gradient or organismic flexibility under consideration.
-The ten point assignment system was first introduced by Zelinka and Marvan (1961) for the classification of saprobic valences and was extended by Moog (1995) to other parameters, such as stream zonation preferences and feeding types.
-Within freshwaterecology.info the ten point assignment system was used for coding the majority of those parameters, which comprise several categories.
-% Example for the parameter "stream zonation preference": If 70% of a species’ records are observed in spring brooks and 30% in the upper trout region, 7 out of 10 points will be allocated to the category "hypocrenal" (spring brook) and 3 points to "epirhithral" (upper trout region) to describe the expected occurrence of this species within the longitudinal zonation of a river.
-For all other categories "0" will be used.
-% Tachet: 0 - 5: Thereby, the relevant features of a taxon were described by the relative distribution of the information among the categories of each trait.
-This procedure was a pertinent and simple way to "translate" the available knowledge about species traits of organisms into numerical values.
-It also avoided the obligate assignment of a taxon to a single category, which can lead to inaccurate characterisation of biological or ecological trait profiles
-% Can be converted so that they can be used together 
-% As already stated fuzzy coding is used to express uncertainty in traits, for variability in traits within taxononomic groups above species-level or for variation in traits during the development of an organism.
-So it's not really clear for fuzzy coded taxa on family-level what uncertainty is expressed
-% Fuzzy coding captures uncertainty. Nice way but has also drawbacks -> correlated variables, needs specific statistic methods, cannot be used in bayesian priors etc.
-% Binary coding is, transformed to 0 and 1, and thus converted just a "variant" of fuzzy coding?
-% Problems fuzzy coding: Which uncertainty do they cover?
-% Stay focused!
-Schneide nicht zu viele Themen an - Du musst nicht jedes einzelne Thema diskutieren.
-Generell kann die Diskussion so 3-4 Abschnitte haben, die jeweils die wichtigsten Resultate oder Aspekte diskutieren.
-Eine generelle Diskussion der Fuzzy Coding und intra-species variation wäre aus meiner Sicht eher ein eigener, wenn auch nicht allzulanger Abschnit
-% \textit{\color{blue} Ideas for concluding this section:
-% \begin{itemize}
-%   \item The uncertainty of trait information should be taken into account when aggregating traits and appropriate measures to capture this uncertainty should be established.
-%   \item Are other measures of uncertainty thinkable, e.g. based on SD or Variance 
-% \end{itemize}
-% }
-
-%%%%%%% Section on taxonomic levels and data coverage
-%? What's the problem with the state of data coverage
-Our analysis aimed to use most of the available trait information for different regions to establish harmonised grouping feature datasets.
-Although many taxa are coverd in the trait databases, the availability of trait information varies strongly across grouping features and taxonomic resolution differs between databases.
-% freshwaterecolgy.info on species-level, Australia mainy taxa on genus and family-level
-% Pointing to the problem of how accurate information on levels with lower taxonomic precision is 
-% For some groups, species and genus-level identification important since information varies considerably in these groups; see Serra Paper!
-% Erwähnen? Obtaining trait information on species-level is challenging
-% How would this change our results?
+% What's the problem with the state of data coverage
+Our analysis aimed to use most of the available invertebrate trait information for different regions to establish harmonised grouping feature datasets.
+Although many taxa are covered in the trait databases from which we extracted our trait datasets, the availability of trait information varies strongly across grouping features and taxonomic resolution differs between databases.
+While trait information from Europe and New Zealand was mainly on species-level, considerable portions of trait data from North America and Australia were on genus or family-level (Table \ref{tab:tax_coverage}).
+Assigned traits on family-level might not reflect the real trait diversity within a taxon, for example for Chironomidae \cite{serra_synthesising_2016}.
+However, species identification can be complicated and time-consuming \cite{marshall_taxonomic_2006, resh_which_2008}, and therefore trait information on family-level has been widley used e.g.
+in bioassessment \cite{beketov_spear_2009}.
+% How would obtaining information on species level change our results?
 
@@
 % Why is it important to investigate trait aggregation methods? And trait harmonisation?
-
-% R: Man könnte das ggf.
-auch an den Anfang ziehen.
-Also einleitend: Warum ist die Frage wichtig, was haben wir überhaupt gemacht - und dann eben erst mal sagen, dass die Analysen zwischen aggregated und assigned traits jetzt nicht die ultimative Wahrheit sind.
-Gleichwohl unsere Ergebnisse anzeigen können, welche Methoden überhaupt und unter welchen Umständen zu unterschiedlichen Ergebnissen führen, so dass die Leser dort entsprechend vorsichtig sein müssten
-
-As outlined in the introduction, various trait aggregation methods are used by researchers when trait data are on more precise taxonomic levels than observational data.
+In the case when trait values are only available at species-level and observational data are on less precise taxonomic levels various trait aggregation methods have been used by researchers.
 We aggregated traits from an Australian and North American trait dataset to family-level using 5 different aggregation methods and compared the results to traits assigned at family-level for these regions.
@@
 The number of differing cases and the mean absolute differences to the assigned traits were similar within the mean aggregation and within the median aggregation methods, which confirms our second finding, the small influence of weighting on the aggregation methods.
-Furthermore, the distributions of absolute trait affinity differences to assigned traits obtained were relatively similar for the mean aggregation methods and the median aggregation methods in both tested datasets (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
+Furthermore, the distributions of absolute trait affinity differences to assigned traits obtained were relatively similar for the mean aggregation methods and the median aggregation methods in both tested datasets respectively (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
 The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species entries.
@@
 
-% R: Allgemein in Trait data sets - ja geht in die Richtung, wobei du ja hier nicht noch analysen für alle möglichen Tiere und traits machen kannst, aber zumindest aufzeigen unter welchen Umständen es bedeutsam ist - und was dann gemacht werden sollte.
-Der Leser will ja aus der Diskussion etwas mitnehmen, ggf.
-auch was er tun soll
-\textit{\color{blue} Maybe include: How often does such a taxonomic data occur in the trait datasets?}
-% Das liest sich wie einer erweiterte Resultate Sectioin - das ist nicht Sinn der Diskussion.
-Du sollst da nicht neue Ergebnisse vorstellen sondern dann eher auf eine Abbildung verweisen und in der Regel in 2-3 Sätzen die Ergebnissen in einfachen Sätzen nennen und diskutieren d.h.
-in Kontext anderer Studien stellen - oder wenn es diese nicht gibt, was auch gesagt werden müsste, dann sagen, was daraus folgt.
-
 % R: Misses a starting sentence, Why did we conduct this analysis?
-In the re-analysis where we investigated how using harmonised and aggregated traits might change the results of trait-environment relationships we found similar results compared the original study.
-Traits that responded only in the original analysis but were non-response in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits.
+% Mention that comparison to other studies not possible since they don't exist?
+In the re-analysis where we investigated how using harmonised and aggregated traits might change the results of trait-environment relationships we found only slightly different results compared to the original study.
+Some of the traits that responded in the original analysis did not respond in the re-analysis.
+Those traits that responded only in the original analysis but were non-response in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits.
+A reason for their non-responsiveness was likely the harmonisation procedure.
 For example, during harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder).
 As a result, the trait affinities in the original dataset have a higher mean and standard deviation than in the aggregated and harmonized datasets (Table S\ref{tab:SI_resp_traits_summary_stats}).
-Hence, the signal in the original data for the trait shredder has presumably been weakened by the harmonization, which might be the reason that shredders showed a less strong reaction to the salinity gradient.
+Hence, the signal in the original data for the trait shredder has presumably been weakened by the harmonisation, which might be the reason that shredders showed a less strong reaction to the salinity gradient in the re-analysis.
+The fact that the family-level aggregated traits showed similar results compared to the original analysis is in line with the findings of others that family-level traits can be sensitive enough to detect environmental impacts \cite{beketov_spear_2009}, although species-level traits are expected to result in more precise results when investigating trait-environment relationships.
+% Cite Schmidt Kloiber?
+Cite another paper that uses family-level trait data
 
@@
 
-% What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
-% quality evaluation of traits als Thema..
+\section*{Conclusion}
+
+% What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? 
+% Quality evaluation of traits als Thema..
+% What do we learned: 
+Comprehensive invertebrate trait databases have been developed over the last years in freshwater ecology.
+We showed that trait definitions are distinct across these databases.
+By providing an overview of definition discrepancies we hope to provide a starting point for the development of standardized trait definitions through which trait databases can be linked.
+Standardized terminolgy will facilitate comparable trait analysis across large scales.
+% - Variation in taxonomic coverage 
+If trait aggregation is necessary we showed that using the median is often in conclusion with expert assignments. 
+% Different weighting approaches did
+Which method is objectively the a better measure cannot be answered, but traits with high variance should be treated carefully and taxa where a few genera have a disproportional high number of species trait information.
+If researchers need to aggregate traits, a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
+
+% Efforts in creating trait ontologies etc etc
+% Technology improvement, e.g. Deep learning for species identification
 

### 2020-12-08 Paper/Draft_harmonization_paper.tex
08.12: Update Discussion/Conclusion

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % 1. Trait Database 
@@
 %- Andere Studien zur Trait Harmonisierung usw.
+
+\subsection*{Trait definition discrepancies and taxonomic resolution}
 
@@
 Although, others have noted the lack of standardized trait terminology in freshwater ecology \cite{baird_toward_2011, brink_traits-based_2011} we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
-To resolve definition discrepancies and facilitate data synthesis terminological standards are needed.
-Harmonised definitions and concepts of traits have been developed in the past, e.g.
+To resolve definition discrepancies and facilitate data synthesis in the future terminological standards are needed.
+Harmonised definitions and concepts of traits have been developed in the past for other organisms, e.g.
 for plants with the \textit{Thesaurus Of Plant characteristics} (TOP) initiative \cite{garnier_towards_2017}.
 The core of this harmonisation initiative is to provide standardized trait definitions and to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field.
-Such initiatives could be a role model for freshwater science to establish unambiguous terminologies for invertebrate traits.
-The existing freshwater invertebrate trait databases could then be linked through standardised terminologies or ontologies, as suggested by Baird et al.
+Such initiatives could be a role model for freshwater ecologists to establish unambiguous terminologies for invertebrate traits.
+The existing freshwater invertebrate trait databases could be linked through standardised terminologies or ontologies, as suggested by Baird et al.
 \cite{baird_toward_2011} almost a decade ago.
 By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS) providers of invertebrate trait data could connect their traits to such ontologies \cite{schneider_towards_2019}.
-Once standardised trait definitions are established, these will improve trait data sharing, trait data processing when working with multiple trait databases, and ultimately improve interpretation of derived results.
+Once standardised trait definitions are established, these will improve trait data sharing, trait data processing when working with multiple trait databases, and ultimately interpretation of the derived results.
 % What is not mentioned here is how traits are measured, for which measurement protocols exist I believe.
@@
 
-% What's the problem with the state of data coverage
+% ?What's the problem with the state of data coverage
 Our analysis aimed to use most of the available invertebrate trait information for different regions to establish harmonised grouping feature datasets.
@@
 Assigned traits on family-level might not reflect the real trait diversity within a taxon, for example for Chironomidae \cite{serra_synthesising_2016}.
-However, species identification can be complicated and time-consuming \cite{marshall_taxonomic_2006, resh_which_2008}, and therefore trait information on family-level has been widley used e.g.
+However, species identification can be complicated and time-consuming \cite{marshall_taxonomic_2006, resh_which_2008}, and therefore trait information on family-level has been widely used, e.g.
 in bioassessment \cite{beketov_spear_2009}.
@@
 
+\subsection*{Trait aggregation and grouping feature harmonisation}
+
 % Why is it important to investigate trait aggregation methods? And trait harmonisation?
@@
 Some traits can vary strongly on more precise taxonomic levels than the family-level.
-For example, Monaghan and Soares found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}.
+For example, Monaghan and Soares \cite{monaghan_improving_2013} found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction.
 Furthermore, studies focusing on the lability of traits, i.e.
@@
 The 5 aggregation methods we tested use either the mean or the median and different weightings.
-Our results indicated that 1) aggregation of traits using \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{mean}} (median aggregation methods) compared to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_mean} (mean aggregation methods) is often closer to the assigned traits at family-level and 2) that the different weightings tested exerted a minor impact on the aggregated trait affinities.
+Our results indicated that 1) the aggregation methods \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{mean}} (median aggregation methods) compared to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_mean} (mean aggregation methods) were often closer to the assigned traits at family-level and 2) that the different weightings tested exerted a minor impact on the aggregated trait affinities.
 We obtained for both datasets more differing cases for mean aggregation methods, irrespective of the weighting.
@@
 In the North American dataset, mean aggregation methods yielded in 47 \% of the cases a difference to the assigned traits, much higher in comparison to the median aggregation methods (between 15 and 18 \%, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
-However, when there were differences between median aggregation methods and assigned traits, these differences were greater compared to the mean aggregation methods, particularly for the North American trait dataset.
+When differences occurred between median aggregation methods and assigned traits, these differences were greater compared to the mean aggregation methods, particularly for the North American dataset.
 The mean absolute differences for the median aggregations was twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
-The differences can be explained by the binary coding used in the North American trait dataset and in the assigned traits for North America.
+The differences can be explained by the binary coding used in the North American trait dataset and in the assigned traits.
 As a result, traits have affinities of either 1 or 0.
@@
 Using the median to aggregate binary coded taxa will often result in a value of 0 or 1, while using the mean will often result in values between 0 and 1.
-Thus, using the median led for the North American dataset in many cases either to agreement with the assigned traits or the difference between median aggregated traits and assigned traits was often 1.
+% Was folgt daraus?
+%Thus, using the median led for the North American dataset in many cases to agreement with the assigned traits.
+However, when differences were found the difference between median aggregated traits and assigned traits was often 1.
 % except for traits were binary coding was not mutually exclusive and when same number of 0 and 1
-% Binary coding also explains the amount of differing cases, median often right for binary data, must be cautious when a lot of traits are unknown?
-The number of differing cases and the mean absolute differences to the assigned traits were similar within the mean aggregation and within the median aggregation methods, which confirms our second finding, the small influence of weighting on the aggregation methods.
-Furthermore, the distributions of absolute trait affinity differences to assigned traits obtained were relatively similar for the mean aggregation methods and the median aggregation methods in both tested datasets respectively (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
+
+The weightings explored in this analysis should lead to different aggregated trait affinities in cases where several genera within a family have different numbers of species.
+In fact, the simulation results indicated that for a particular family where one genus has a much larger number of species compared to other genera within this family , especially for traits with a higher variance.
+However, in the comparison of the trait aggregation methods to assigned traits the number of differing cases and the mean absolute differences in trait affinities were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the tested weightings on the aggregation methods.
+Also, the distributions of absolute trait affinity differences to assigned traits were relatively similar for the mean aggregation methods and the median aggregation methods respectively (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
 The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species entries.
-From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 14 \% were resolved on family-level and 62 \% were resolved on genus-level.
+From the taxa that were compared from the North American trait dataset, 14 \% were resolved on family-level and 62 \% were resolved on genus-level.
 52 \% had 5 or less genera and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
-In the Australian dataset 21 \% of the taxa were resolved on family-level, 40 \% were resolved on genus level, and 39 \% were resolved on species-level.
+In the Australian dataset, 21 \% of the taxa were resolved on family-level, 40 \% were resolved on genus level, and 39 \% were resolved on species-level.
 68 \% of the taxa contain 5 or less genera and 40 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}).
+% Results might change when trait information is all on species level
 
-Although the simulation results showed only small differences between the results of the aggregation methods the choice of the aggregation method for small numbers of genera per family can be important when one genus has a much larger number of species compared to other genera within a particular family.
-% R: Das Argument ist schwer greifbar für den Leser - es wäre einfacher zu folgen, wenn Du schreiben würdest, wann man denn mit unterschieden rechnen würde und warum - und dann deine Daten beschreiben.
-Also wenn es sehr viele Genera und diese mit sehr unterschiedlicher Anzahl an Arten wären usw.
-.
-Die Diskussion sollte vor allen Dingen allgemeiner verständniclih sein und nicht technisch die Resultate fortsetzen.
+In our second analysis we explored how using harmonised grouping features and aggregated traits might change the results of trait-environment relationships.
+We are not aware of other studies that compared trait-environment relationships using harmonised and not harmonised data.
+The re-analysis yielded only slightly different results compared to the original study, i.e.
+some of the traits that responded in the original analysis did not respond in the re-analysis.
+Those traits that were non-responsive in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see method section), namely feeding mode shredder, respiration gills, and life cycle duration traits.
+Feeding mode shredder was the only trait that was non-responsive when using harmonised (but not aggregated) as well as when using aggregated data.
+One reason for the non-responsiveness of shredders in the re-analysis was likely the harmonisation procedure.
+For example, during harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder).
+As a result, the trait affinities in the original data have a higher mean and standard deviation than in the aggregated and harmonized data (Table \ref{tab:SI_resp_traits_summary_stats}) suggesting that the signal in the original data has presumably been weakened by the harmonisation.
+This might be the reason that shredders showed a less strong reaction to the salinity gradient in the re-analysis.
+These findings show that if harmonisation is necessary, harmonised and non-harmonised data should be compared and possible averaging effects should be considered in further analysis.
 
-% R: Misses a starting sentence, Why did we conduct this analysis?
-% Mention that comparison to other studies not possible since they don't exist?
-In the re-analysis where we investigated how using harmonised and aggregated traits might change the results of trait-environment relationships we found only slightly different results compared to the original study.
-Some of the traits that responded in the original analysis did not respond in the re-analysis.
-Those traits that responded only in the original analysis but were non-response in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits.
-A reason for their non-responsiveness was likely the harmonisation procedure.
-For example, during harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder).
-As a result, the trait affinities in the original dataset have a higher mean and standard deviation than in the aggregated and harmonized datasets (Table S\ref{tab:SI_resp_traits_summary_stats}).
-Hence, the signal in the original data for the trait shredder has presumably been weakened by the harmonisation, which might be the reason that shredders showed a less strong reaction to the salinity gradient in the re-analysis.
-The fact that the family-level aggregated traits showed similar results compared to the original analysis is in line with the findings of others that family-level traits can be sensitive enough to detect environmental impacts \cite{beketov_spear_2009}, although species-level traits are expected to result in more precise results when investigating trait-environment relationships.
+The fact that the family-level aggregated traits used in the re-analysis showed only slightly different results compared to the original analysis is in line with the findings of others that family-level traits can be sensitive enough to detect environmental impacts \cite{beketov_spear_2009}.
+% Although species-level traits are expected to result in more precise results when investigating trait-environment relationships.
 % Cite Schmidt Kloiber?
@@
 % Quality evaluation of traits als Thema..
-% What do we learned: 
-Comprehensive invertebrate trait databases have been developed over the last years in freshwater ecology.
-We showed that trait definitions are distinct across these databases.
-By providing an overview of definition discrepancies we hope to provide a starting point for the development of standardized trait definitions through which trait databases can be linked.
-Standardized terminolgy will facilitate comparable trait analysis across large scales.
+Although comprehensive invertebrate trait databases have been developed for several regions in the past, data synthesis is difficult due to discrepancies in trait definitions.
+By providing an overview of definition discrepancies we hope to set a starting point for the development of standardized trait definitions through which trait databases can be linked.
+Standardized terminology will facilitate comparable trait analysis across large scales.
 % - Variation in taxonomic coverage 
-If trait aggregation is necessary we showed that using the median is often in conclusion with expert assignments. 
-% Different weighting approaches did
-Which method is objectively the a better measure cannot be answered, but traits with high variance should be treated carefully and taxa where a few genera have a disproportional high number of species trait information.
+We showed that trait aggregation is often in conclusion with expert assignments and specifically approaches using the median.
+...
+weighting trait information based on the taxa present in the trait databases exerts a minor influence on the aggregated trait affinities.
+Which method the objectively better measure is cannot be answered, but when trait aggregation is necessary we showed 1) that highly variable traits should be treated carefully, 2) coding of traits should be considered, and 3) taxa where a few genera have a disproportional high number of species trait information ....
 If researchers need to aggregate traits, a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
-
+% Question for future research?
+% Fuzzy coding and uncertainty?
 % Efforts in creating trait ontologies etc etc

### 2020-12-09 Paper/Draft_harmonization_paper.tex
09.12: Final edits before send to Ralf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{DRAFT: Harmonized and trait aggregation paper }
+\title{DRAFT: Harmonisation and trait aggregation paper }
 \author{}%Stefan Kunz 
@@
 To our knowledge, only Brown et al.
-\cite{brown_functional_2018} harmonized grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
+\cite{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
 We suspect that the heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents.
 To harmonize grouping features from different regions, first commonly accepted and unambiguous trait definitions are required \cite{schneider_towards_2019}.
-In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonized using standardized terminology.
-However, a lack of standardized terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology \cite{baird_toward_2011, kissling_towards_2018}.
+In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonised using standardised terminology.
+However, a lack of standardised terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology \cite{baird_toward_2011, kissling_towards_2018}.
 Secondly, consistent coding of traits facilitates the compatibility of trait data from different databases.
@@
 European and New Zealand databases fuzzy coding, North American database binary coding).
-A centralized database with standardized and unambiguous traits and a consistent coding of traits would minimize the data processing effort.
+Databases with standardised and unambiguous traits and a consistent coding of traits would minimize the data processing effort.
 Discrepancies in the taxonomic resolutions (e.g.
@@
 (3) we re-analysed data on the effect of anthropogenic salinisation on biological traits by Szöcs et al.
-\cite{szocs_effects_2014} using trait data from the established harmonized European trait datasets and aggregated traits.
-By comparison with the original analysis, we investigated how harmonizing and aggregating trait data can modify the outcome of trait-environment relationships.
+\cite{szocs_effects_2014} using trait data from the established harmonised European trait datasets and aggregated traits.
+By comparison with the original analysis, we investigated how harmonising and aggregating trait data can modify the outcome of trait-environment relationships.
 
@@
 
-We extracted information from 6 trait databases from Europe, North America, Australia, and New Zealand and harmonized 7 grouping features.
+We extracted information from 6 trait databases from Europe, North America, Australia, and New Zealand and harmonised 7 grouping features.
 Trait information for Europe was obtained from the freshwaterecology.info database \cite{schmidt-kloiber_www.freshwaterecology.info_2015} and the Tachet database \cite{usseglio-polatera_biomonitoring_2000}.
@@
 temperature preference) because these traits are missing in the New Zealand trait database.
-The grouping features were differently classified across the databases, we therefore harmonized them into 26 traits (Table \ref{tab:traits_harmonization}).
-Harmonization was undertaken by amalgamating similar traits into one trait (e.g.
+The grouping features were differently classified across the databases, we therefore harmonised them into 26 traits (Table \ref{tab:traits_harmonization}).
+Harmonisation was undertaken by amalgamating similar traits into one trait (e.g.
 crawlers and sprawlers into crawlers).
@@
 
-We used fuzzy coding for establishing our harmonized datasets unless data quality prohibited.
+We used fuzzy coding for establishing our harmonised datasets unless data quality prohibited.
 In the latter case we used binary traits, i.e.
@@
 freshwaterecology.info 0 to 10, Tachet database 0 to 3 or 0 to 5).
-We standardized these to a range between 0 and 1 and converted trait affinities to percentages.
+We standardised these to a range between 0 and 1 and converted trait affinities to percentages.
 Thus, fuzzy coded and binary traits were in the same range.
 
-Prior to harmonization we consolidated duplicate taxa on species, genus or family-level if present within a dataset, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
+Prior to harmonisation we consolidated duplicate taxa on species, genus or family-level if present within a dataset, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
 We omitted taxa with a lower taxonomic precision than family-level.
@@
 \centering
-\caption{Traits of the harmonized grouping features. The last column indicates traits that were amalgamated for harmonization (no amalgamation needed if empty).}
+\caption{Traits of the harmonised grouping features. The last column indicates traits that were amalgamated for harmonisation (no amalgamation needed if empty).}
 \label{tab:traits_harmonization}
@@
 
-Traits of the harmonized grouping feature datasets were aggregated to family-level using three approaches.
+Traits of the harmonised grouping feature datasets were aggregated to family-level using three approaches.
 I) Direct aggregation of taxa to family-level giving equal weight to every taxon using the mean or median, denoted \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively.
@@
 The sampling was repeated 100 times for each standard deviation.
-Hence, in total 100 datasets for each level of trait variability were simulated, resulting in 12500 simulated trait affinities for each scenario ($25$ species per family $* 5$ levels of trait variability $* 100$ replicates).
-All trait aggregation methods were applied to each simulated dataset resulting in 500 aggregated trait values per scenario.
-The results were compared based on the produced range of aggregated trait affinities between levels of trait variability and hypothetical taxonomic hierarchies.
+Hence, in total 100 datasets for each level of trait variability were simulated, resulting in 12500 simulated trait affinities for each simulated trait ($25$ species per family $* 5$ levels of trait variability $* 100$ replicates).
+These 12500 simulated affinities per trait were assigned to each scenario.
+The above mentioned trait aggregation methods were applied to each simulated dataset.
+% ...resulting in 2500 aggregated affinities per trait and scenario ($12500$ trait affinities per trait divided by $25$, the number of species and multiplied by $5$, the number of aggregation methods).
+The results were compared based on the produced range of aggregated trait affinities between levels of trait variability and scenario.
 We also compared for each simulated dataset the differences in trait affinities obtained by each aggregation method.
@@
 \cite{szocs_effects_2014} who studied the effect of anthropogenic salinization on invertebrates in the River Werra in Germany.
-For the re-analysis we used the established harmonized grouping features for Europe and additionally aggregated traits using the aforementioned aggregation methods.
+For the re-analysis we used the established harmonised grouping features for Europe and additionally aggregated traits using the aforementioned aggregation methods.
 
@@
 
-We substituted 6 of the grouping features from the original data with harmonized grouping features from the European trait dataset.
-We compared the results of the redundancy analysis (RDA) from the original study to the case when using harmonized grouping features.
+We substituted 6 of the grouping features from the original data with harmonised grouping features from the European trait dataset.
+We compared the results of the redundancy analysis (RDA) from the original study to the case when using harmonised grouping features.
 Specifically, the trait composition expressed as community weighted mean (CWM) traits was ordinated along an electric conductivity gradient.
@@
 \cite{szocs_effects_2014} used.
-The 6 harmonized grouping features used were \textit{Size, Feeding mode, Locomotion, Oviposition, Respiration}, and \textit{Voltinism}.
+The 6 harmonised grouping features used were \textit{Size, Feeding mode, Locomotion, Oviposition, Respiration}, and \textit{Voltinism}.
 Additionally, for testing the effect of aggregated traits we assigned to each taxon in Szöcs et al.
@@
 
-\subsection*{Taxonomic coverage of the harmonized trait datasets}
+\subsection*{Taxonomic coverage of the harmonised trait datasets}
 
@@
     \centering
-    \caption{Number of taxa per harmonized dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percentage.} 
+    \caption{Number of taxa per harmonised dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percentage.} 
     \label{tab:tax_coverage}
@@
 
-The amount of entries with available information for the selected grouping features varied strongly for the preprocessed European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
+The amount of entries with available information for the selected grouping features varied strongly for the established European, North American, and Australian trait datasets (Table \ref{tab:trait_coverage}).
 By contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
@@
 
-Comparing the aggregated trait affinities, in total 15000 ($500$ aggregated traits $*10$ unique comparisons of trait affinities and $3$ scenarios) for each simulated dataset showed that in most simulated datasets the differences between the aggregated traits were small.
-Only 1.42 \% (213 out of 15.000) of all comparisons showed a difference equal or greater than an absolute trait affinity of 0.1.
+Each trait aggregation method yielded one aggregated affinity for every simulated dataset, in total 15000 ($100$ replicates $*$ 5 levels of trait variability $* 10$ unique comparisons of trait aggregation methods $* 3$ scenarios).
+Overall, differences between the results of the aggregation methods for each simulated dataset increased with increasing trait variability.
+However, in most simulated datasets the different aggregation methods often resulted in similar trait affinities.
+Only 1.42 \% (213 out of 15.000) of all aggregated affinities showed a difference equal or greater than an absolute trait affinity of 0.1.
 Most of these differences occurred for the \textit{sim\_extreme} scenario (83.5 \%).
@@
 % Differences were rather small, largest difference 0.265 for sim_extreme (stepwise_median vs weighted_agg)
-
-Overall, differences between the results of the aggregation methods for each simulated dataset increased with increasing trait variability.
-According to the simulation results, the different aggregation methods often result in similar trait affinities.
-If differences occurred, than mostly between aggregation methods using the median and aggregation methods using the mean.
 
@@
 
-\subsection*{Re-analysis of Szöcs et al. using harmonized and aggregated grouping features}
+\subsection*{Re-analysis of Szöcs et al. using harmonised and aggregated grouping features}
 
@@
 
-Using harmonized grouping features resulted in less traits that distinguish upstream and downstream sites in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+Using harmonised grouping features resulted in less traits that distinguish upstream and downstream sites in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
 According to the RDA of the trait composition, downstream sites were characterised by taxa with the traits multivoltinism, ovoviviparity and long life cycle duration.
 Upstream sites were characterised by univoltine taxa with a short life cycle duration that lay their eggs in an aquatic environment (aquatic eggs).
-The trait aquatic eggs of the harmonized grouping feature oviposition has been derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonization}).
+The trait aquatic eggs of the harmonised grouping feature oviposition has been derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonization}).
 The traits shredder and gill respiration did not characterise sites with high salinisation.
 
-Using at family-level aggregated traits from the harmonized dataset showed also results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+Using at family-level aggregated traits from the harmonised dataset showed also results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
 The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg}
@@
     \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
-    \caption{Species scores obtained by RDA from the original analysis \cite{szocs_effects_2014}, using harmonized grouping features, and using harmonized grouping features with traits aggregated to family-level.
+    \caption{Species scores obtained by RDA from the original analysis \cite{szocs_effects_2014}, using harmonised grouping features, and using harmonised grouping features with traits aggregated to family-level.
 The dots represent the individual species scores for each analysed trait along the conductivity axis.
@@
 the trait piercer in the Tachet database, Table \ref{tab:traits_harmonization}).
-Although, others have noted the lack of standardized trait terminology in freshwater ecology \cite{baird_toward_2011, brink_traits-based_2011} we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
+Although, others have noted the lack of standardised trait terminology in freshwater ecology \cite{baird_toward_2011, brink_traits-based_2011} we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
+%In addition we provide harmonised grouping feature trait datasets that can be used for other studies
 To resolve definition discrepancies and facilitate data synthesis in the future terminological standards are needed.
-Harmonised definitions and concepts of traits have been developed in the past for other organisms, e.g.
+Harmonised definitions and concepts of traits have been developed in the past for other organism groups, e.g.
 for plants with the \textit{Thesaurus Of Plant characteristics} (TOP) initiative \cite{garnier_towards_2017}.
-The core of this harmonisation initiative is to provide standardized trait definitions and to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field.
+The core of this harmonisation initiative is to provide standardised trait definitions and to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field.
 Such initiatives could be a role model for freshwater ecologists to establish unambiguous terminologies for invertebrate traits.
@@
 
-\subsection*{Trait aggregation and grouping feature harmonisation}
+\subsection*{Trait aggregation}
 
 % Why is it important to investigate trait aggregation methods? And trait harmonisation?
-In the case when trait values are only available at species-level and observational data are on less precise taxonomic levels various trait aggregation methods have been used by researchers.
+When trait values are only available at species-level and observational data are on less precise taxonomic levels various trait aggregation methods have been used by researchers.
 We aggregated traits from an Australian and North American trait dataset to family-level using 5 different aggregation methods and compared the results to traits assigned at family-level for these regions.
@@
 When differences occurred between median aggregation methods and assigned traits, these differences were greater compared to the mean aggregation methods, particularly for the North American dataset.
-The mean absolute differences for the median aggregations was twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
+There, the mean absolute differences for the median aggregations was twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
 The differences can be explained by the binary coding used in the North American trait dataset and in the assigned traits.
@@
 
-The weightings explored in this analysis should lead to different aggregated trait affinities in cases where several genera within a family have different numbers of species.
-In fact, the simulation results indicated that for a particular family where one genus has a much larger number of species compared to other genera within this family , especially for traits with a higher variance.
-However, in the comparison of the trait aggregation methods to assigned traits the number of differing cases and the mean absolute differences in trait affinities were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the tested weightings on the aggregation methods.
+The weightings explored in this analysis should lead to different aggregated trait affinities in cases where genera within a family have different numbers of species.
+In fact, the simulation results indicated that for a particular family where one genus has a much larger number of species compared to the other genera, weighting the number of taxa can lead to different aggregated trait affinities, sspecially for traits with higher levels of variance (Figure \ref{fig:sim_indv_runs}.
+However, in the comparison of the trait aggregation methods to assigned traits the number of differing cases and the mean absolute differences in trait affinities were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weightings on the aggregation methods.
 Also, the distributions of absolute trait affinity differences to assigned traits were relatively similar for the mean aggregation methods and the median aggregation methods respectively (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
@@
 68 \% of the taxa contain 5 or less genera and 40 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}).
-% Results might change when trait information is all on species level
+Hence, these results are expected to change when trait information is all on species level
 
-In our second analysis we explored how using harmonised grouping features and aggregated traits might change the results of trait-environment relationships.
+\subsection*{Grouping feature harmonisation}
+
+We explored how using harmonised grouping features and aggregated traits might change the results of trait-environment relationships.
 We are not aware of other studies that compared trait-environment relationships using harmonised and not harmonised data.
@@
 For example, during harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder).
-As a result, the trait affinities in the original data have a higher mean and standard deviation than in the aggregated and harmonized data (Table \ref{tab:SI_resp_traits_summary_stats}) suggesting that the signal in the original data has presumably been weakened by the harmonisation.
+As a result, the trait affinities in the original data have a higher mean and standard deviation than in the aggregated and harmonised data (Table \ref{tab:SI_resp_traits_summary_stats}) suggesting that the signal in the original data has presumably been weakened by the harmonisation.
 This might be the reason that shredders showed a less strong reaction to the salinity gradient in the re-analysis.
-These findings show that if harmonisation is necessary, harmonised and non-harmonised data should be compared and possible averaging effects should be considered in further analysis.
-
+These findings show that if harmonisation is necessary, harmonised and non-harmonised data, if available, should be compared and possible averaging effects should be considered in further analysis.
 The fact that the family-level aggregated traits used in the re-analysis showed only slightly different results compared to the original analysis is in line with the findings of others that family-level traits can be sensitive enough to detect environmental impacts \cite{beketov_spear_2009}.
@@
 % Keep it simple!
-% Resp gills: Original data has a lot of zeros, which are not present in the harmonized \& aggregated datasets (see % In the analysis with the harmonized dataset resp gills is not responding to the salinity gradient
-% Aggregated data look similar to the harmonized ones, but resp gills is here one of the traits responding to conductivity!
+% Resp gills: Original data has a lot of zeros, which are not present in the harmonised \& aggregated datasets (see % In the analysis with the harmonised dataset resp gills is not responding to the salinity gradient
+% Aggregated data look similar to the harmonised ones, but resp gills is here one of the traits responding to conductivity!
 % Why did some aggregated datasets promote life cycle duration traits and others not
@@
 
-% What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? 
-% Quality evaluation of traits als Thema..
 Although comprehensive invertebrate trait databases have been developed for several regions in the past, data synthesis is difficult due to discrepancies in trait definitions.
-By providing an overview of definition discrepancies we hope to set a starting point for the development of standardized trait definitions through which trait databases can be linked.
-Standardized terminology will facilitate comparable trait analysis across large scales.
-% - Variation in taxonomic coverage 
-We showed that trait aggregation is often in conclusion with expert assignments and specifically approaches using the median.
-...
-weighting trait information based on the taxa present in the trait databases exerts a minor influence on the aggregated trait affinities.
-Which method the objectively better measure is cannot be answered, but when trait aggregation is necessary we showed 1) that highly variable traits should be treated carefully, 2) coding of traits should be considered, and 3) taxa where a few genera have a disproportional high number of species trait information ....
-If researchers need to aggregate traits, a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
-% Question for future research?
-% Fuzzy coding and uncertainty?
-% Efforts in creating trait ontologies etc etc
-% Technology improvement, e.g. Deep learning for species identification
+By providing an overview of these definition discrepancies we hope to set a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
+A consent on standard terminology and the subsequent development of ontologies are the next steps to facilitate trait-based analysis on large scales.
+As our analysis showed, some grouping features might need to be reclassified to fit into such a standardised terminology.
+We could show that trait affinities resulting from fuzzy coding and binary coding can be used together, but a uniform coding of traits is another problem that should be addressed in the course of trait standardisation.
 
-% Where does the classification come from? Few sources used in NOA also used in AUS:
+With the increasing use of computer vision in ecology, species identification could become easier and more automated, and trait aggregation might be less needed \cite{milosevic_application_2020}.
+However, if traits need to be aggregated we showed that trait aggregation is often in conclusion with expert assignments, specifically aggregation approaches using the median.
+Which aggregation method the objectively better measure is cannot be answered, but when trait aggregation is necessary 1) highly variable traits and taxa where a few genera have a high number of species should be treated carefully, 2) coding of traits should be considered, and 3) weighting trait information based on the taxa present in the used trait database does not seem to have much influence.
+No matter which aggregation approach is chosen, for future studies in which researchers must aggregate traits, a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
+
+% Ideas for this section:
+% ?What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? 
+% ?Where does the classification come from? Few sources used in NOA also used in AUS:
 % AUS: Merrit \& Cummins 1978/1984 for feeding mode for a few genera and families 
@@
 Trophic Relations of Aquatic Insects" was used for feeding mode
+% Uncertainty captured by fuzzy codes?
 

### 2020-12-09 Paper/Flowchart/Flowchart_methods.tex
16.10: Paper Update, first implm. of Co-Authors
09.12: Final edits before send to Ralf

@@
       %% Nodes
-      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Allocating duplicate taxa \\ NOA \& AUS DB};
+      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Consolidating duplicate \\ taxa in  EU, NOA, AUS \& \\ NZ DBs};
       \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{AUS traits standardized to [0-1] \\ because multiple codings used \\ throughout this database};
-      \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Omitted taxa lower \\ family-level};
+      \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Taxa more precise than \\ family-level};
 
@@
 
-      \node(harmonization)[mainnode, align = center, xshift = -5cm, yshift = -2.5cm]{Harmonization};
+      \node(harmonisation)[mainnode, align = center, xshift = -5cm, yshift = -2.5cm]{Harmonisation};
 
@@
 
-      \node(frameHarmAggr) [frame, fit = (harmonization) (traitAgg)] {};
+      \node(frameHarmAggr) [frame, fit = (harmonisation) (traitAgg)] {};
 
@@
       \draw[->] (normalAUS.east) -- (omission.west);
-      \draw[->] (harmonization.east) -- (conversionPerc.west);
+      \draw[->] (harmonisation.east) -- (conversionPerc.west);
       \draw[->] (conversionPerc.east) -- (traitAgg.west);

### 2020-12-10 Paper/Draft_harmonization_paper.tex
10.12: Discussion draft finished

@@
 
-\subsection*{Selection of traits and harmonization of trait databases}
+\subsection*{Selection of traits and harmonisation of trait databases}
 
@@
 temperature preference) because these traits are missing in the New Zealand trait database.
-The grouping features were differently classified across the databases, we therefore harmonised them into 26 traits (Table \ref{tab:traits_harmonization}).
+The grouping features were differently classified across the databases, we therefore harmonised them into 26 traits (Table \ref{tab:traits_harmonisation}).
 Harmonisation was undertaken by amalgamating similar traits into one trait (e.g.
@@
 \caption{Traits of the harmonised grouping features. The last column indicates traits that were amalgamated for harmonisation (no amalgamation needed if empty).}
-\label{tab:traits_harmonization}
+\label{tab:traits_harmonisation}
 \begin{tabular}{lll}
@@
 This method weights the genera according to the number of their species in the trait datasets regardless if for every used grouping feature information was available (Figure \ref{fig:data_proc_overview}).
+When we refer to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg} together we denote these methods as mean aggregation methods and when we refer to \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}} together, we denote these methods as median aggregation methods.
 
@@
 
-\subsection*{Analysis of the effect of harmonization and trait aggregation on trait-environment relationships}
+\subsection*{Analysis of the effect of harmonisation and trait aggregation on trait-environment relationships}
 
@@
 \cite{szocs_effects_2014} who studied the effect of anthropogenic salinization on invertebrates in the River Werra in Germany.
-For the re-analysis we used the established harmonised grouping features for Europe and additionally aggregated traits using the aforementioned aggregation methods.
+For the re-analysis we used the established harmonised grouping feature dataset for Europe and additionally aggregated traits using the aforementioned aggregation methods.
 
@@
 Following the original study, we identified traits associated with high or low salinity based on their distance to the ordination axis median using the mahalanobis distance.
-Traits with a mahalanobis distance greater than the $97.5 \%$ -quantile of the Chi-square distribution (5.02) were regarded as traits responding to either low or high salinity.
+CWM traits with a mahalanobis distance greater than the $97.5 \%$ -quantile of the Chi-square distribution (5.02) were regarded as traits responding to either low or high salinity.
 For our analysis, we used the same 21 grouping features that Szöcs et al.
@@
 The data processing and aforementioned analyses were carried out using R (Version 3.6.1).
-Raw data and the R code for data processing and grouping feature harmonization is located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
+Raw data and the R code for data processing and grouping feature harmonisation is located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
 Scripts and data to reproduce the trait aggregation and analysis with aggregated traits are located in the Github repository \url{https://github.com/KunzstLD/Trait-aggregation}.
@@
 
-The trait aggregation methods \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}} and \textit{weighted\_agg} yielded similar ranges of aggregated trait affinities within each level of trait variability for the \textit{sim\_base} scenario.
-The \textit(stepwise\_agg \textsubscript{median}) and \textit(direct\_agg \textsubscript{median}) yielded mostly greater ranges of aggregated trait affinities for the \textit{sim\_base} scenario.
-As expected with increasing trait variability the produced range of trait affinities increased (Figure \ref{fig:overview_sim_results}).
+As expected with increasing trait variability the produced range of trait affinities increased for all aggregation methods (Figure \ref{fig:overview_sim_results}).
+The mean aggregation methods yielded similar ranges of aggregated trait affinities within each level of trait variability for the \textit{sim\_base} scenario.
+The median aggregation methods yielded mostly greater ranges of aggregated trait affinities for the \textit{sim\_base} scenario.
 By contrast, the ranges of trait affinities slightly differed for all aggregation methods for the simulation scenarios \textit{sim\_extreme} and \textit{sim\_variation}.
@@
 
-Each trait aggregation method yielded one aggregated affinity for every simulated dataset, in total 15000 ($100$ replicates $*$ 5 levels of trait variability $* 10$ unique comparisons of trait aggregation methods $* 3$ scenarios).
+Each trait aggregation method yielded one aggregated affinity for every simulated dataset, in total 15000 comparisons ($100$ replicates $*$ 5 levels of trait variability $* 10$ unique comparisons of trait aggregation methods $* 3$ scenarios).
 Overall, differences between the results of the aggregation methods for each simulated dataset increased with increasing trait variability.
 However, in most simulated datasets the different aggregation methods often resulted in similar trait affinities.
-Only 1.42 \% (213 out of 15.000) of all aggregated affinities showed a difference equal or greater than an absolute trait affinity of 0.1.
+Only 1.42 \% (213 out of 15.000) of all comparisons showed a difference equal or greater than an absolute trait affinity of 0.1.
 Most of these differences occurred for the \textit{sim\_extreme} scenario (83.5 \%).
@@
 For the North American dataset, comparison of the trait aggregation methods to trait affinities assigned at family-level yielded between 15.3 \% and 47 \% differing cases (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
-In general, trait aggregation methods using the median yielded fewer cases with differences compared to approaches using the mean.
-However, aggregation methods using the median produced greater differences for both datasets.
+In general, median aggregation methods yielded fewer cases with differences compared to mean aggregation methods.
+However, median aggregation methods produced greater differences for both datasets.
 Standard deviations of absolute differences were similar for all tested aggregation methods.
@@
 % Is that necessary?
-A comparison of the aggregation methods with each other for the 4 datasets revealed that differences in aggregated trait affinities were largest between the \textit{stepwise\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{median}} (Figure \ref{fig:comp_aggr_methods}).
+% A comparison of the aggregation methods with each other for the 4 datasets revealed that differences in aggregated trait affinities were largest between the \textit{stepwise\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{median}} (Figure \ref{fig:comp_aggr_methods}).
 
@@
   \centering
-  \caption{Amount of differing cases, the minimum and maximum, and means and standard deviations of absolute differences between trait affinities assigned at family-level and aggregated trait affinities.}
+  \caption{Amount of differing cases, minimum, maximum, means, and standard deviations of absolute differences between trait affinities assigned at family-level and aggregated trait affinities.}
   \label{tab:summary_stat_aggr_vs_fam_assigned}
@@
 Upstream sites were characterised by univoltine taxa with a short life cycle duration that lay their eggs in an aquatic environment (aquatic eggs).
-The trait aquatic eggs of the harmonised grouping feature oviposition has been derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonization}).
+The trait aquatic eggs of the harmonised grouping feature oviposition has been derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonisation}).
 The traits shredder and gill respiration did not characterise sites with high salinisation.
@@
 
-% 1. Allgemeiner Satz zum Thema, der auf eine offene Frage o.ä. hinweist
-% 2. Was haben wir herausgefunden?
-% 3. Was haben andere schon herausgefunden
-% 4. Was bedeutet das für zukünftige Studien?
-
-% 1. Trait Database 
-%- Unterschiede zwischen Regionen und Trait Genauigkeit
-%- Was kann man machen
-%- Andere Studien zur Trait Harmonisierung usw.
-
 \subsection*{Trait definition discrepancies and taxonomic resolution}
 
-% Why do we need trait-based analysis, especially across regions?
 Synthesizing trait information from multiple trait databases is crucial to unfold the full potential of trait-based approaches, e.g.
@@
 In addition, the same traits are sometimes defined differently in the investigated databases, requiring expert knowledge to reclassify these traits (e.g.
-the trait piercer in the Tachet database, Table \ref{tab:traits_harmonization}).
+the trait piercer in the Tachet database, Table \ref{tab:traits_harmonisation}).
 Although, others have noted the lack of standardised trait terminology in freshwater ecology \cite{baird_toward_2011, brink_traits-based_2011} we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
@@
 % What is not mentioned here is how traits are measured, for which measurement protocols exist I believe.
-I think this is an separate issue.
+I think this is a separate issue.
 
-% ?What's the problem with the state of data coverage
 Our analysis aimed to use most of the available invertebrate trait information for different regions to establish harmonised grouping feature datasets.
 Although many taxa are covered in the trait databases from which we extracted our trait datasets, the availability of trait information varies strongly across grouping features and taxonomic resolution differs between databases.
+Much information is available for grouping features that are often used in trait-environment studies, such as feeding mode and respiration.
+Surprisingly, there is little information on body form, a trait that is relatively easy to determine.
+
 While trait information from Europe and New Zealand was mainly on species-level, considerable portions of trait data from North America and Australia were on genus or family-level (Table \ref{tab:tax_coverage}).
@@
 in bioassessment \cite{beketov_spear_2009}.
-% How would obtaining information on species level change our results?
 
-% Include Ben's point?
+% Include Ben's point? Discussion on evolutionary history?
 % Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 2.
-+ 3.
-die aktuellen Abschnitte (obwohl sie auch etwas ähnliche Themen beinhalten - geht ja immer um was ähnliches - wie gut sind die Aggregationsmethoden - könnte man vielleicht auch zusammenfassen
+
 % Hier: Überschrift mit genereller Aussage?
-
 \subsection*{Trait aggregation}
 
-% Why is it important to investigate trait aggregation methods? And trait harmonisation?
 When trait values are only available at species-level and observational data are on less precise taxonomic levels various trait aggregation methods have been used by researchers.
@@
 The 5 aggregation methods we tested use either the mean or the median and different weightings.
-Our results indicated that 1) the aggregation methods \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{mean}} (median aggregation methods) compared to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_mean} (mean aggregation methods) were often closer to the assigned traits at family-level and 2) that the different weightings tested exerted a minor impact on the aggregated trait affinities.
+Our results indicated that 1) the median aggregation methods compared to mean aggregation methods were often closer to the assigned traits at family-level and 2) that the different weightings tested exerted a minor impact on the aggregated trait affinities.
 We obtained for both datasets more differing cases for mean aggregation methods, irrespective of the weighting.
@@
 When differences occurred between median aggregation methods and assigned traits, these differences were greater compared to the mean aggregation methods, particularly for the North American dataset.
-There, the mean absolute differences for the median aggregations was twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
+There, the mean absolute differences for the median aggregations were twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
 The differences can be explained by the binary coding used in the North American trait dataset and in the assigned traits.
@@
 Using the median to aggregate binary coded taxa will often result in a value of 0 or 1, while using the mean will often result in values between 0 and 1.
-% Was folgt daraus?
-%Thus, using the median led for the North American dataset in many cases to agreement with the assigned traits.
-However, when differences were found the difference between median aggregated traits and assigned traits was often 1.
-% except for traits were binary coding was not mutually exclusive and when same number of 0 and 1
+Thus, using the median led for the North American dataset either to agreement with the assigned traits or to higher differences compared to the mean aggregation methods.
 
 The weightings explored in this analysis should lead to different aggregated trait affinities in cases where genera within a family have different numbers of species.
-In fact, the simulation results indicated that for a particular family where one genus has a much larger number of species compared to the other genera, weighting the number of taxa can lead to different aggregated trait affinities, sspecially for traits with higher levels of variance (Figure \ref{fig:sim_indv_runs}.
+In fact, the simulation results indicated that for a particular family where one genus has a much larger number of species compared to the other genera, weighting the number of taxa can lead to different aggregated trait affinities, especially for traits with higher levels of variance (Figure \ref{fig:sim_indv_runs}.
 However, in the comparison of the trait aggregation methods to assigned traits the number of differing cases and the mean absolute differences in trait affinities were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weightings on the aggregation methods.
@@
 68 \% of the taxa contain 5 or less genera and 40 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}).
-Hence, these results are expected to change when trait information is all on species level
+Hence, these results might change when more trait information on species-level becomes available.
 
@@
 One reason for the non-responsiveness of shredders in the re-analysis was likely the harmonisation procedure.
-For example, during harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder).
+During harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder).
 As a result, the trait affinities in the original data have a higher mean and standard deviation than in the aggregated and harmonised data (Table \ref{tab:SI_resp_traits_summary_stats}) suggesting that the signal in the original data has presumably been weakened by the harmonisation.
@@
 The fact that the family-level aggregated traits used in the re-analysis showed only slightly different results compared to the original analysis is in line with the findings of others that family-level traits can be sensitive enough to detect environmental impacts \cite{beketov_spear_2009}.
-% Although species-level traits are expected to result in more precise results when investigating trait-environment relationships.
-% Cite Schmidt Kloiber?
-Cite another paper that uses family-level trait data
-
-% Keep it simple!
-% Resp gills: Original data has a lot of zeros, which are not present in the harmonised \& aggregated datasets (see % In the analysis with the harmonised dataset resp gills is not responding to the salinity gradient
-% Aggregated data look similar to the harmonised ones, but resp gills is here one of the traits responding to conductivity!
-% Why did some aggregated datasets promote life cycle duration traits and others not
-% Results using trait data obtained when aggregating with stepwise\_agg (median) and stepwise\_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites.
-% Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites
-% However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets (see Table S2). 
-% Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?
+% Cite another paper that uses family-level trait data
+% Although species-level traits are expected to result in more precise results when investigating trait-environment relationships. % Cite Schmidt Kloiber?
 
@@
 A consent on standard terminology and the subsequent development of ontologies are the next steps to facilitate trait-based analysis on large scales.
-As our analysis showed, some grouping features might need to be reclassified to fit into such a standardised terminology.
+As our analysis showed, some grouping features might need to be re-classified to fit into such a standardised terminology.
 We could show that trait affinities resulting from fuzzy coding and binary coding can be used together, but a uniform coding of traits is another problem that should be addressed in the course of trait standardisation.
@@
 
-% Ideas for this section:
-% ?What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? 
-% ?Where does the classification come from? Few sources used in NOA also used in AUS:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Further ideas for the discussion:
+% - What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? 
+% - Where does the classification come from? Few sources used in NOA also used in AUS:
 % AUS: Merrit \& Cummins 1978/1984 for feeding mode for a few genera and families 
@@
 Trophic Relations of Aquatic Insects" was used for feeding mode
-% Uncertainty captured by fuzzy codes?
+% - Discussion on fuzzy coding -> Uncertainty captured by fuzzy codes? 
+% - Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?
+% - Traits that responded differently after harmonisation:
+% Resp gills: Original data has a lot of zeros, which are not present in the harmonised \& aggregated datasets.
+In the analysis with the harmonised dataset resp gills is not responding to the salinity gradient.
+Aggregated data look similar to the harmonised ones, but resp gills is here one of the traits responding to conductivity!
+% Why did some aggregated datasets promote life cycle duration traits and others not?
+Results using trait data obtained when aggregating with stepwise\_agg (median) and stepwise\_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites.
+% Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites
+% However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets (see Table S2).
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \printbibliography
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supporting information %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supporting information %%%%%%%%%%%%%%%%%%%%%%%%
 \setcounter{table}{0}

### 2020-12-17 Paper/Draft_harmonization_paper.tex
17.12: Minor Edits Ralf

@@
 the trait piercer in the Tachet database, Table \ref{tab:traits_harmonisation}).
-Although, others have noted the lack of standardised trait terminology in freshwater ecology \cite{baird_toward_2011, brink_traits-based_2011} we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
+Although, others have noted the lack of standardised trait terminology in freshwater ecology \cite{baird_toward_2011, brink_traits-based_2011}, we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
 %In addition we provide harmonised grouping feature trait datasets that can be used for other studies
-To resolve definition discrepancies and facilitate data synthesis in the future terminological standards are needed.
+To resolve definition discrepancies and facilitate data synthesis in the future,  terminological standards are needed.
 Harmonised definitions and concepts of traits have been developed in the past for other organism groups, e.g.
@@
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
-Aggregation of trait information on species or genus-level to a point estimate on family-level suggests a precision which is not necessarily present, especially not for traits with a high variability or if trait information on species-level is missing.
+Aggregation of trait information on species or genus-level to a point estimate on family-level suggests a precision that is not necessarily present, especially not for traits with a high variability or if trait information on species-level is missing.
 Some traits can vary strongly on more precise taxonomic levels than the family-level.
@@
 The weightings explored in this analysis should lead to different aggregated trait affinities in cases where genera within a family have different numbers of species.
-In fact, the simulation results indicated that for a particular family where one genus has a much larger number of species compared to the other genera, weighting the number of taxa can lead to different aggregated trait affinities, especially for traits with higher levels of variance (Figure \ref{fig:sim_indv_runs}.
+In fact, the simulation results indicated that for a particular family where one genus has a much larger number of species compared to the other genera, weighting the number of taxa can lead to different aggregated trait affinities, especially for traits with higher levels of variance (Figure \ref{fig:sim_indv_runs}).
 However, in the comparison of the trait aggregation methods to assigned traits the number of differing cases and the mean absolute differences in trait affinities were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weightings on the aggregation methods.
-Also, the distributions of absolute trait affinity differences to assigned traits were relatively similar for the mean aggregation methods and the median aggregation methods respectively (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
+Also, the distributions of absolute trait affinity differences to assigned traits were relatively similar for the mean aggregation methods and the median aggregation methods, respectively (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
 The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species entries.
@@
 We explored how using harmonised grouping features and aggregated traits might change the results of trait-environment relationships.
-We are not aware of other studies that compared trait-environment relationships using harmonised and not harmonised data.
+We are not aware of other studies that compared trait-environment relationships using harmonised and non harmonised data.
 The re-analysis yielded only slightly different results compared to the original study, i.e.
 some of the traits that responded in the original analysis did not respond in the re-analysis.
-Those traits that were non-responsive in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see method section), namely feeding mode shredder, respiration gills, and life cycle duration traits.
+Those traits that were non-responsive in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (Mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see method section), namely feeding mode shredder, respiration gills, and life cycle duration traits.
 Feeding mode shredder was the only trait that was non-responsive when using harmonised (but not aggregated) as well as when using aggregated data.
 One reason for the non-responsiveness of shredders in the re-analysis was likely the harmonisation procedure.
-During harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder).
+During harmonisation the trait shredder has been amalgamated based on three traits (miner, xylophagus, and shredder).
 As a result, the trait affinities in the original data have a higher mean and standard deviation than in the aggregated and harmonised data (Table \ref{tab:SI_resp_traits_summary_stats}) suggesting that the signal in the original data has presumably been weakened by the harmonisation.
@@
 
-With the increasing use of computer vision in ecology, species identification could become easier and more automated, and trait aggregation might be less needed \cite{milosevic_application_2020}.
+With the increasing use of computer vision in ecology, both species identification and trait quantification could be automated \cite{milosevic_application_2020, hoye_deep_2020}.
+This might result in more observational data and trait data on species-level in the future.
 However, if traits need to be aggregated we showed that trait aggregation is often in conclusion with expert assignments, specifically aggregation approaches using the median.
-Which aggregation method the objectively better measure is cannot be answered, but when trait aggregation is necessary 1) highly variable traits and taxa where a few genera have a high number of species should be treated carefully, 2) coding of traits should be considered, and 3) weighting trait information based on the taxa present in the used trait database does not seem to have much influence.
+Which aggregation method the objectively better measure is cannot be answered, but when trait aggregation is necessary 1) median aggregation seems to be favorable, 2) highly variable traits and taxa where a few genera have a high number of species should be treated carefully, 3) coding of traits should be considered, and 4) weighting trait information based on the taxa present in the used trait database does not seem to have much influence.
 No matter which aggregation approach is chosen, for future studies in which researchers must aggregate traits, a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.

### 2020-12-18 Paper/Draft_harmonization_paper.tex
18.12: Abstract draft and figure correction

@@
 
+\section*{Summary}
+
+% FROM FRESHWATER BIOLOGY Website:
+% All papers should include a summary, in short numbered paragraphs, limited to about 3% of the length of the text, and in any case to not more than 500 words.
+This should provide a concise statement of the scope of the work and its principal findings and be fully intelligible without reference to the main text.
+It is helpful to structure your abstract as follows: point 1 = background to and reason for the study and the aims; point 2 = brief description of methods used; point 3 = main project results (address the aims); point 4 = conclusions of your study; point 5 = the contribution that your results make to the field / why your study is useful to an international audience.
+Referring to abstracts in recently published issues may help with structuring an abstract.
+
+1.
+Invertebrate traits are increasingly used in ecological studies because they provide a mechanistic understanding of species-environment relationships and are suitable for large scale analysis due to their consistent response to environmental gradients.
+The development of invertebrate trait databases for different continents in recent years should have created impetus for trait-based research, especially on large scales.
+However, a number of data-related problems hamper the work with trait-based approaches.
+For example, standardised trait definitions are lacking and coding of traits varies across trait databases impeding trait data synthesis.
+Another issue is different taxonomic resolution between observational taxonomic data and trait databases, leading to the need to aggregate traits.
+% Aim of our study?
+
+2.
+In this study, we describe discrepancies in trait definitions of trait databases from Europe, North America, New Zealand and Australia for traits frequently used in ecological studies.
+Based on these databases we established 4 novel trait datasets by harmonising 7 commonly used grouping features.
+Two of these datasets were used to evaluate different trait aggregation methods by comparing aggregated traits with assigned traits by experts at family-level.
+Furthermore, we explored the effect of grouping feature harmonisation and trait aggregation by re-analysing a study on the effect of anthropogenic salinisation on biological traits using harmonised grouping features and aggregated traits.
+
+3.
+We found that investigated trait databases are distinct with regard to how grouping features are differentiated into traits, the scope of the grouping feature definitions, how traits are defined, and the coding to describe traits.
+Comparison of aggregated and assigned traits showed that aggregated traits are generally in conclusion with expert assignments, especially approaches using the median.
+Grouping feature harmonisation and trait aggregation had a minor impact in the re-analysis, although averaging effects can occur due to harmonisation diminishing the signal of a trait.
+
+4.
+By outlining discrepancies in trait definitions we hope to motivate the development of a standardized terminology for invertebrate traits.
+When trait aggregation is needed, our results provide guidance under which circumstances the choice of a trait aggregation method becomes important.
+
 \section*{Introduction}
@@
 
-In this study, we follow the terminology proposed by Schmera et al., where a grouping feature is defined as a general property (e.g.
-feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species" \cite{schmera_proposed_2015}.
+In this study, we follow the terminology proposed by Schmera et al.
+\cite{schmera_proposed_2015}, where a grouping feature is defined as a general property (e.g.
+feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species".
 Thus, we use the term grouping feature in place of which many studies use the term "trait", and the term trait instead of "trait state", "modality" or "trait category".
@@
 
-\begin{sidewaysfigure}
-  \label{fig:boxplots_scores_on_constrained_axis}
-  \centering
-  \includegraphics[width= 22cm, height=12cm]{Scores_on_constrained_axis_combined.pdf}
-  \caption{RDA of traits constrained by electric conductivity for the tested methods and the original study.
+% \begin{sidewaysfigure}
+%   \label{fig:boxplots_scores_on_constrained_axis}
+%   \centering
+%   \includegraphics[width= 22cm, height=12cm]{Scores_on_constrained_axis_combined.pdf}
+%   \caption{RDA of traits constrained by electric conductivity for the tested methods and the original study.
 Shown are boxplots of the site scores along the conductivity axis.
@@
 Only traits with a mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.}
-\end{sidewaysfigure}
+% \end{sidewaysfigure}
+
+\begin{figure}[H]
+  \label{}
+  \centering
+  \includegraphics[width=16.5cm, height=25cm]{Scores_on_constrained_axis_comb_ALT.pdf}
+  \caption{}
+\end{figure}
 
@@
 However, if traits need to be aggregated we showed that trait aggregation is often in conclusion with expert assignments, specifically aggregation approaches using the median.
-Which aggregation method the objectively better measure is cannot be answered, but when trait aggregation is necessary 1) median aggregation seems to be favorable, 2) highly variable traits and taxa where a few genera have a high number of species should be treated carefully, 3) coding of traits should be considered, and 4) weighting trait information based on the taxa present in the used trait database does not seem to have much influence.
+Which aggregation method the objectively better measure is cannot be answered, but when trait aggregation is necessary 1) median aggregation seems to be favourable, 2) highly variable traits and taxa where a few genera have a high number of species should be treated carefully, 3) coding of traits should be considered, and 4) weighting trait information based on the taxa present in the used trait database does not seem to have much influence.
 No matter which aggregation approach is chosen, for future studies in which researchers must aggregate traits, a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.

### 2020-12-19 Paper/Draft_harmonization_paper.tex
19.12.: Started fixing references, fixed figure 7

@@
 \usepackage{rotating}
+\usepackage{caption}
 % \graphicspath{{/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures/}}
@@
 backend = biber,
-style = ieee,
-citestyle = numeric-comp,
-maxbibnames=99,
-sorting = none % sort by name year title
+style = apa,
+citestyle = authoryear,
+maxcitenames = 2, 
+maxbibnames = 99 % ,
+%sorting = none % sort by name year title
 ]{biblatex}
 \addbibresource{Ref_invertebrate_DB.bib}
+
+% From freshwater biology:
+% List all sources in the reference list alphabetically by name.
+In text citations should follow the author-date method.
+This means that the author's last name and the year of publication for the source should appear in the text, for example, (Jones, 1998), and a complete reference should appear in the reference list at the end of the paper.
+
+% References are styled according to the sixth edition of the Publication Manual of the American Psychological Association.
+A sample of the most common entries in reference lists appears below.
+Please note that for journal articles, issue numbers are not included unless each issue in the volume begins with page one.
+
+% Article: 
+% One author: Fawcett, T. (2006). An introduction to ROC analysis. Pattern Recognition Letters, 27(8), 861–874. DOI: 10.1016/j.patrec.2005.10.010.
+
+% 2 to 7 authors: Daley, C. E., & Nagle, R. J. (1996). Relevance of WISC-III Indicators for assessment of learning disabilities. Journal of Psychoeducational Assessment, 14 (4), 320–333.
+
+% More than 7 authors: Rutter, M., Caspi, A., Fergusson, D., Horwood, L.
+J., Goodman, R., Maughan, B., … Carroll, J.
+(2004).
+Sex differences in developmental reading disability: New findings from 4 epidemiological studies.
+Journal of the American Medical Association, 291(16), 2007–2012.
+DOI: 10.1001/jama.291.16.2007
+
+% In press or forthcoming: van Bergen, E., de Jong, P.
+F., Maassen, B., Krikhaar, E., Plakas, A., & van der Leij, A.
+(in press).
+IQ of four-year-olds who go on to develop dyslexia.
+Journal of Learning Disabilities.
+DOI: 10.1177/0022219413479673
 
@@
 
+\newpage
+
 \section*{Introduction}
@@
 Explaining and predicting how communities are shaped by environmental factors is one of the main goals of ecology.
-Species traits, defined as measurable properties of an organism \cite{mcgill_rebuilding_2006}, might be beneficial in achieving this goal \cite{heino_jani_macroecological_2013}.
-Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism or a population and its environment \cite{southwood_habitat_1977, verberk_delivering_2013}.
-Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than in taxonomic responses \cite{bonada_taxonomic_2007, baird_toward_2011}.
+Species traits, defined as measurable properties of an organism (\cite{mcgill_rebuilding_2006}), might be beneficial in achieving this goal (\cite{heino_jani_macroecological_2013}).
+Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
+Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than in taxonomic responses (\cite{bonada_taxonomic_2007, baird_toward_2011}).
 Traits of freshwater invertebrate individuals are difficult to determine because - unlike plant traits - they often can not be measured directly.
-For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community \cite{moog_comprehensive_nodate}.
+For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community (\cite{moog_comprehensive_nodate}).
 Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
-by relating macroinvertebrate trait composition to environmental factors and as trait metrics in biomonitoring \cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}.
+by relating macroinvertebrate trait composition to environmental factors and as trait metrics in biomonitoring (\cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}).
 
-In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases for various continents \cite{usseglio-polatera_biomonitoring_2000, schmidt-kloiber_www.freshwaterecology.info_2015, vieira_database_nodate, Philips_and_Smith_NZ_DB_2018, kefford_integrated_2020, tomanova_trophic_2006}.
+In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases for various continents (\cite{usseglio-polatera_biomonitoring_2000, schmidt-kloiber_www.freshwaterecology.info_2015, vieira_database_nodate, Philips_and_Smith_NZ_DB_2018, kefford_integrated_2020, tomanova_trophic_2006}).
 The availability of invertebrate trait data from different continents enables comparisons of trait variation and analyses of their relation to environmental factors across large scales.
@@
 For example, Bonada et al.
-\cite{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from Usseglio-Polatera et al.
-\cite{usseglio-polatera_biomonitoring_2000}(typically referred to as Tachet database); Poff et al.
+(\cite{bonada_taxonomic_2007}) compared trait composition for Mediterranean and temperate regions in Europe using traits from Usseglio-Polatera et al.
+(\cite{usseglio-polatera_biomonitoring_2000}, typically referred to as Tachet database); Poff et al.
 \cite{poff_developing_2010} characterized trait composition across sites in the Western US using traits from Poff et al.
-\cite{poff_functional_2006}, and Botwe et al.
+(\cite{poff_functional_2006}), and Botwe et al.
 \cite{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from Poff et al.
-\cite{poff_functional_2006} and Schäfer et al.
-\cite{schafer_trait_2011}.
+(\cite{poff_functional_2006}) and Schäfer et al.
+(\cite{schafer_trait_2011}).
 Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different continents are rare.
@@
 In this study, we follow the terminology proposed by Schmera et al.
-\cite{schmera_proposed_2015}, where a grouping feature is defined as a general property (e.g.
+(\cite{schmera_proposed_2015}), where a grouping feature is defined as a general property (e.g.
 feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species".
@@
 To our knowledge, only Brown et al.
-\cite{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
+(\cite{brown_functional_2018}) harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
 We suspect that the heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents.
-To harmonize grouping features from different regions, first commonly accepted and unambiguous trait definitions are required \cite{schneider_towards_2019}.
+To harmonize grouping features from different regions, first commonly accepted and unambiguous trait definitions are required (\cite{schneider_towards_2019}).
 In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonised using standardised terminology.
-However, a lack of standardised terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology \cite{baird_toward_2011, kissling_towards_2018}.
+However, a lack of standardised terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology (\cite{baird_toward_2011, kissling_towards_2018}).
 Secondly, consistent coding of traits facilitates the compatibility of trait data from different databases.
@@
 
-However, invertebrate trait databases are heterogeneous regarding the coding they use for their traits \cite{culp_incorporating_2011}.
+However, invertebrate trait databases are heterogeneous regarding the coding they use for their traits (\cite{culp_incorporating_2011}).
 For example, in the study from Brown et al.
-\cite{brown_functional_2018} the authors needed to reclassify traits using expert knowledge given that the individual databases employed different coding approaches (i.e.
+(\cite{brown_functional_2018}) the authors needed to reclassify traits using expert knowledge given that the individual databases employed different coding approaches (i.e.
 European and New Zealand databases fuzzy coding, North American database binary coding).
@@
 \cite{szocs_effects_2014, vos_taxonomic_2017}).
-Conversely, if trait information is only available on more precise taxonomic levels than the observed taxa, traits are aggregated to a less precise taxonomic level, e.g.
-\cite{poff_functional_2006, szocs_effects_2014, piliere_a._f._h._importance_2016, aspin_extreme_2019}.
+Conversely, if trait information is only available on more precise taxonomic levels than the observed taxa, traits are aggregated to a less precise taxonomic level (e.g.
+\cite{poff_functional_2006, szocs_effects_2014, piliere_a._f._h._importance_2016, aspin_extreme_2019}).
 Studies have used different methods of trait aggregation, e.g.
-the mean \cite{magliozzi_functional_2019}, median \cite{szocs_effects_2014} or the mode \cite{piliere_a._f._h._importance_2016}.
+the mean (\cite{magliozzi_functional_2019}), median (\cite{szocs_effects_2014}) or the mode (\cite{piliere_a._f._h._importance_2016}).
 Up to now, studies on how and to which extent different trait aggregation methods influence trait-based analysis are missing.
@@
 (3) we re-analysed data on the effect of anthropogenic salinisation on biological traits by Szöcs et al.
-\cite{szocs_effects_2014} using trait data from the established harmonised European trait datasets and aggregated traits.
+(\cite{szocs_effects_2014}) using trait data from the established harmonised European trait datasets and aggregated traits.
 By comparison with the original analysis, we investigated how harmonising and aggregating trait data can modify the outcome of trait-environment relationships.
@@
 
-Using harmonised grouping features resulted in less traits that distinguish upstream and downstream sites in comparison to the original analysis (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+Using harmonised grouping features resulted in less traits that distinguish upstream and downstream sites in comparison to the original analysis (Figure \ref{fig:violin_plot_species_sc} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
 According to the RDA of the trait composition, downstream sites were characterised by taxa with the traits multivoltinism, ovoviviparity and long life cycle duration.
@@
 
-Using at family-level aggregated traits from the harmonised dataset showed also results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figure \ref{fig:rda_species_scores} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+Using at family-level aggregated traits from the harmonised dataset showed also results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figure \ref{fig:violin_plot_species_sc} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
 The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg}
@@
 \begin{figure}[H]
-    \label{fig:rda_species_scores}
     \centering
@@
 Gray vertical lines indicate the median of the obtained species scores.}
+    \label{fig:violin_plot_species_sc}
 \end{figure}
 
+% Old figure:
 % \begin{sidewaysfigure}
@@
 \begin{figure}[H]
-  \label{}
   \centering
   \includegraphics[width=16.5cm, height=25cm]{Scores_on_constrained_axis_comb_ALT.pdf}
-  \caption{}
 \end{figure}
+\clearpage % insert a page break
+\captionof{figure}{RDA of traits constrained by electric conductivity for the tested methods and the original study.
+Shown are boxplots of the site scores along the conductivity axis.
+The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
+Only traits with a mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
+For better comparability, species scores of the original analysis were multiplied by -1.}
+\label{fig:boxplots_scores_on_constrained_axis}
 
@@
 
+% From Freshwater biology: 
+% This should highlight the significance of the results and place them in the context of other work.
+It should not include references to figures or tables cited in the Results – check that all of your Results are presented in the Results section.
+Figures (e.g.
+photographs, conceptual diagrams) or tables presented specifically as part of the Discussion are welcome and may be cited there.
+
 \subsection*{Trait definition discrepancies and taxonomic resolution}
@@
 In addition, the same traits are sometimes defined differently in the investigated databases, requiring expert knowledge to reclassify these traits (e.g.
-the trait piercer in the Tachet database, Table \ref{tab:traits_harmonisation}).
+the trait piercer in the Tachet database).
 Although, others have noted the lack of standardised trait terminology in freshwater ecology \cite{baird_toward_2011, brink_traits-based_2011}, we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
@@
 Once standardised trait definitions are established, these will improve trait data sharing, trait data processing when working with multiple trait databases, and ultimately interpretation of the derived results.
-% What is not mentioned here is how traits are measured, for which measurement protocols exist I believe.
-I think this is a separate issue.
 
@@
 In the Australian dataset, the amount of differing cases was slightly higher for the mean aggregation methods (23 \%) than for median aggregation methods (16 to 18 \% differing cases).
-In the North American dataset, mean aggregation methods yielded in 47 \% of the cases a difference to the assigned traits, much higher in comparison to the median aggregation methods (between 15 and 18 \%, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
+In the North American dataset, mean aggregation methods yielded in 47 \% of the cases a difference to the assigned traits, much higher in comparison to the median aggregation methods (between 15 and 18 \%).
 When differences occurred between median aggregation methods and assigned traits, these differences were greater compared to the mean aggregation methods, particularly for the North American dataset.
-There, the mean absolute differences for the median aggregations were twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31, Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
+There, the mean absolute differences for the median aggregations were twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31).
 The differences can be explained by the binary coding used in the North American trait dataset and in the assigned traits.
@@
 The weightings explored in this analysis should lead to different aggregated trait affinities in cases where genera within a family have different numbers of species.
-In fact, the simulation results indicated that for a particular family where one genus has a much larger number of species compared to the other genera, weighting the number of taxa can lead to different aggregated trait affinities, especially for traits with higher levels of variance (Figure \ref{fig:sim_indv_runs}).
+In fact, the simulation results indicated that for a particular family where one genus has a much larger number of species compared to the other genera, weighting the number of taxa can lead to different aggregated trait affinities, especially for traits with higher levels of variance.
 However, in the comparison of the trait aggregation methods to assigned traits the number of differing cases and the mean absolute differences in trait affinities were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weightings on the aggregation methods.
-Also, the distributions of absolute trait affinity differences to assigned traits were relatively similar for the mean aggregation methods and the median aggregation methods, respectively (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
+Also, the distributions of absolute trait affinity differences to assigned traits were relatively similar for the mean aggregation methods and the median aggregation methods, respectively.
 The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species entries.
@@
 % Cite another paper that uses family-level trait data
-% Although species-level traits are expected to result in more precise results when investigating trait-environment relationships. % Cite Schmidt Kloiber?
+% Although species-level traits are expected to result in more precise results when investigating trait-environment relationships.
 
@@
 
-\section*{Conclusion}
+\subsection*{Outlook}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \printbibliography

### 2020-12-21 Paper/Draft_harmonization_paper.tex
21.12: Edits Summary and References

@@
 
+% Alternative start: Invertebrate traits are increasingly used in ecological studies because they provide a mechanistic understanding of species-environment relationships and are suitable for large scale analysis due to their consistent response to environmental gradients.
+
 1.
-Invertebrate traits are increasingly used in ecological studies because they provide a mechanistic understanding of species-environment relationships and are suitable for large scale analysis due to their consistent response to environmental gradients.
-The development of invertebrate trait databases for different continents in recent years should have created impetus for trait-based research, especially on large scales.
-However, a number of data-related problems hamper the work with trait-based approaches.
+In recent years, comprehensive invertebrate trait databases have been established for different continents.
+The wide availability of invertebrate trait data should have created an impetus for trait-based studies, especially on large scales.
+However, a number of data-related problems hamper the work with trait data.
 For example, standardised trait definitions are lacking and coding of traits varies across trait databases impeding trait data synthesis.
-Another issue is different taxonomic resolution between observational taxonomic data and trait databases, leading to the need to aggregate traits.
-% Aim of our study?
+Another issue is different taxonomic resolutions between observational taxonomic data and trait databases, leading to the need to aggregate traits.
+% The aim of our study was to investigate discrepancies in trait definitions, to evaluate different trait aggregation methods and
 
 2.
-In this study, we describe discrepancies in trait definitions of trait databases from Europe, North America, New Zealand and Australia for traits frequently used in ecological studies.
-Based on these databases we established 4 novel trait datasets by harmonising 7 commonly used grouping features.
+In this study, we describe discrepancies in trait definitions of trait databases from Europe, North America, New Zealand, and Australia for traits frequently used in ecological studies.
+Based on these trait databases we established 4 novel trait datasets by harmonising 7 commonly used grouping features.
 Two of these datasets were used to evaluate different trait aggregation methods by comparing aggregated traits with assigned traits by experts at family-level.
@@
 4.
-By outlining discrepancies in trait definitions we hope to motivate the development of a standardized terminology for invertebrate traits.
+By outlining discrepancies in trait definitions we hope to motivate the development of standardised terminology for invertebrate traits.
 When trait aggregation is needed, our results provide guidance under which circumstances the choice of a trait aggregation method becomes important.
@@
 (\cite{usseglio-polatera_biomonitoring_2000}, typically referred to as Tachet database); Poff et al.
-\cite{poff_developing_2010} characterized trait composition across sites in the Western US using traits from Poff et al.
+(\cite{poff_developing_2010}) characterized trait composition across sites in the Western US using traits from Poff et al.
 (\cite{poff_functional_2006}), and Botwe et al.
-\cite{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from Poff et al.
+(\cite{botwe_effects_2018}) investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from Poff et al.
 (\cite{poff_functional_2006}) and Schäfer et al.
@@
 We extracted information from 6 trait databases from Europe, North America, Australia, and New Zealand and harmonised 7 grouping features.
-Trait information for Europe was obtained from the freshwaterecology.info database \cite{schmidt-kloiber_www.freshwaterecology.info_2015} and the Tachet database \cite{usseglio-polatera_biomonitoring_2000}.
+Trait information for Europe was obtained from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}) and the Tachet database (\cite{usseglio-polatera_biomonitoring_2000}).
 The freshwaterecology.info contains taxa on species-level, while taxa recorded in the Tachet database are on species, genus and family-level.
 Trait information for North America was obtained from Twardochleb et al.
-\cite{twardochleb_trait_data_2020} and complemented by Vieira et al.
-\cite{vieira_database_nodate}.
-Data on body form for European and North American taxa was based on expert knowledge \cite{polatera_personal_information_2020}.
+(\cite{twardochleb_trait_data_2020}) and complemented by Vieira et al.
+(\cite{vieira_database_nodate}).
+Data on body form for European and North American taxa was based on expert knowledge (\cite{polatera_personal_information_2020}).
 For Australia and New Zealand, we used trait databases from Kefford et al.
-\cite{kefford_integrated_2020} and Philips and Smith respectively \cite{Philips_and_Smith_NZ_DB_2018}.
+(\cite{kefford_integrated_2020}) and Philips and Smith respectively (\cite{Philips_and_Smith_NZ_DB_2018}).
 To increase readability we refer to the databases as well as the datasets we extracted from them by the name of the continent they originate from, except for European databases, which we refer to by their commonly used names (freshwaterecology.info and Tachet database).
@@
 \begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-    \textit{a} The trait "bluff (blocky)" occurred in the Vieira et al.
-\cite{vieira_database_nodate} database and was newly classified by expert knowledge into cylindrical and flattened \cite{polatera_personal_information_2020}.
+    \textit{a} The trait "bluff (blocky)" occurred in the North America (Vieira et al.) database and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}).
 \\
     \textit{b} Reflects the different size classifications by the North American trait databases and the other trait databases. \\
-    \textit{c} The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases \cite{usseglio-polatera_biomonitoring_2000}.
-Taxa exhibiting this trait have been assigned to predators or herbivores based on expert knowledge \cite{polatera_personal_information_piercer_2020}.
+    \textit{c} The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases (\cite{usseglio-polatera_biomonitoring_2000}).
+Taxa exhibiting this trait have been assigned to predators or herbivores based on expert knowledge (\cite{polatera_personal_information_piercer_2020}).
 }
@@
 For the Australian dataset, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman et al.
-\cite{chessman_dissolved-oxygen_2018}.
+(\cite{chessman_dissolved-oxygen_2018}).
 In Chessman et al.
-\cite{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the Australian dataset except that the trait parasite is missing.
+(\cite{chessman_dissolved-oxygen_2018}) feeding mode is classified similarly as in the Australian dataset except that the trait parasite is missing.
 We conducted the comparison for the 220 families available in Chessman et al.
-\cite{chessman_dissolved-oxygen_2018}.
+(\cite{chessman_dissolved-oxygen_2018}).
 Considering each factor combination of family and trait (in total 8) this amounts to 1760 cases.
@@
 For the North American dataset, we compared aggregated trait affinities with assigned trait affinities on family-level for the grouping features feeding mode, respiration, size, voltinism, and locomotion.
-The assigned trait affinities at family-level are part of the North American database (Twardochleb et al.) \cite{twardochleb_trait_data_2020} and originate from expert knowledge.
+The assigned trait affinities at family-level are part of the North American database (Twardochleb) and originate from expert knowledge.
 Trait information was available for 94 families of which all were present in the North American dataset (total number of cases 1598).
@@
 We repeated the analysis of Szöcs et al.
-\cite{szocs_effects_2014} who studied the effect of anthropogenic salinization on invertebrates in the River Werra in Germany.
+(\cite{szocs_effects_2014}) who studied the effect of anthropogenic salinization on invertebrates in the River Werra in Germany.
 For the re-analysis we used the established harmonised grouping feature dataset for Europe and additionally aggregated traits using the aforementioned aggregation methods.
 
-The river Werra has been subject to effluents from the potash industry since the mid of the 20th century and allows to study responses of invertebrates and their trait compositions to salinization \cite{bathe_biological_2011}.
+The river Werra has been subject to effluents from the potash industry since the mid of the 20th century and allows to study responses of invertebrates and their trait compositions to salinization (\cite{bathe_biological_2011}).
 Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition.
 Further details can be found in Szöcs et al.
-\cite{szocs_effects_2014}.
+(\cite{szocs_effects_2014}).
 
@@
 For our analysis, we used the same 21 grouping features that Szöcs et al.
-\cite{szocs_effects_2014} used.
+(\cite{szocs_effects_2014}) used.
 The 6 harmonised grouping features used were \textit{Size, Feeding mode, Locomotion, Oviposition, Respiration}, and \textit{Voltinism}.
 Additionally, for testing the effect of aggregated traits we assigned to each taxon in Szöcs et al.
-\cite{szocs_effects_2014} the aggregated trait value for its corresponding family and repeated the RDA.
+(\cite{szocs_effects_2014}) the aggregated trait value for its corresponding family and repeated the RDA.
 
@@
 The freshwaterecology.info database, the Tachet database and the North American database (Twardochleb et al.) provided more detailed descriptions of their trait information compared to the North American (Vieira et al.) and New Zealand database.
-An exception is the Australian trait database which is a collection of seven specific trait datasets \cite{kefford_integrated_2020}.
+An exception is the Australian trait database which is a collection of seven specific trait datasets (\cite{kefford_integrated_2020}).
 Thus, grouping features occur multiple times with varying differentiation into traits.
@@
 \begin{landscape}
-  \begin{longtable}{m{2.5cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
+  \begin{longtable}{m{2.9cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
   \caption{Number of traits per grouping feature and type of coding of the traits for the respective grouping feature per database.}
@@
   \hline
-  \multirow{2}{*}{\specialcell{North America \\ (Twardochleb)}} & 
+  \multirow{2}{*}{\specialcell{North America \\ (Twardochleb et al.)}} & 
   6 & 
@@
   \hline
-  \multirow{2}{*}{\specialcell{North America \\ (Vieira)}} & 
+  \multirow{2}{*}{\specialcell{North America \\ (Vieira et al.)}} & 
   8 & 
@@
       \newline
-      \textit{b} Many traits were rather comments than traits in the original database and were not considered.
+      \textit{b} Not all traits were considered because trait information was partly presented as comments to describe other traits or due to incomplete information.
   \end{minipage}
@@
 The original RDA in Szöcs et al.
-\cite{szocs_effects_2014} indicated that downstream sites (high salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle duration ($> 1$ year), and gill respiration and upstream sites (low salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
+(\cite{szocs_effects_2014}) indicated that downstream sites (high salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle duration ($> 1$ year), and gill respiration and upstream sites (low salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
 
@@
     \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
-    \caption{Species scores obtained by RDA from the original analysis \cite{szocs_effects_2014}, using harmonised grouping features, and using harmonised grouping features with traits aggregated to family-level.
+    \caption{Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonised grouping features, and using harmonised grouping features with traits aggregated to family-level.
 The dots represent the individual species scores for each analysed trait along the conductivity axis.
@@
 the trait piercer in the Tachet database).
-Although, others have noted the lack of standardised trait terminology in freshwater ecology \cite{baird_toward_2011, brink_traits-based_2011}, we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
-%In addition we provide harmonised grouping feature trait datasets that can be used for other studies
+Although, others have noted the lack of standardised trait terminology in freshwater ecology (\cite{baird_toward_2011, brink_traits-based_2011}), we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
 To resolve definition discrepancies and facilitate data synthesis in the future, terminological standards are needed.
 Harmonised definitions and concepts of traits have been developed in the past for other organism groups, e.g.
-for plants with the \textit{Thesaurus Of Plant characteristics} (TOP) initiative \cite{garnier_towards_2017}.
+for plants with the \textit{Thesaurus Of Plant characteristics} (TOP) initiative (\cite{garnier_towards_2017}).
 The core of this harmonisation initiative is to provide standardised trait definitions and to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field.
@@
 The existing freshwater invertebrate trait databases could be linked through standardised terminologies or ontologies, as suggested by Baird et al.
-\cite{baird_toward_2011} almost a decade ago.
-By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS) providers of invertebrate trait data could connect their traits to such ontologies \cite{schneider_towards_2019}.
+(\cite{baird_toward_2011}) almost a decade ago.
+By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS) providers of invertebrate trait data could connect their traits to such ontologies (\cite{schneider_towards_2019}).
 Once standardised trait definitions are established, these will improve trait data sharing, trait data processing when working with multiple trait databases, and ultimately interpretation of the derived results.
@@
 While trait information from Europe and New Zealand was mainly on species-level, considerable portions of trait data from North America and Australia were on genus or family-level (Table \ref{tab:tax_coverage}).
-Assigned traits on family-level might not reflect the real trait diversity within a taxon, for example for Chironomidae \cite{serra_synthesising_2016}.
-However, species identification can be complicated and time-consuming \cite{marshall_taxonomic_2006, resh_which_2008}, and therefore trait information on family-level has been widely used, e.g.
-in bioassessment \cite{beketov_spear_2009}.
-
-% Include Ben's point? Discussion on evolutionary history?
-% Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
-I wonder if this indicates that Family richness is really higher in Australia.
-Perhaps it might be as Australia has a wider range of evolutionary histories.
-This would be worth considering in the discussion
+Assigned traits on family-level might not reflect the real trait diversity within a taxon, for example for Chironomidae (\cite{serra_synthesising_2016}).
+However, species identification can be complicated and time-consuming (\cite{marshall_taxonomic_2006, resh_which_2008}), and therefore trait information on family-level has been widely used, e.g.
+in bioassessment (\cite{beketov_spear_2009}).
 
@@
 
-% Hier: Überschrift mit genereller Aussage?
 \subsection*{Trait aggregation}
@@
 Some traits can vary strongly on more precise taxonomic levels than the family-level.
-For example, Monaghan and Soares \cite{monaghan_improving_2013} found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction.
+For example, Monaghan and Soares (\cite{monaghan_improving_2013}) found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction.
 Furthermore, studies focusing on the lability of traits, i.e.
 how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g.
-thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}.
+thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable (\cite{poff_functional_2006, wilkes_traitbased_2020}).
 However, if trait aggregation is necessary our study can give guidance, under which circumstances the choice of aggregation method might be important.
@@
 These findings show that if harmonisation is necessary, harmonised and non-harmonised data, if available, should be compared and possible averaging effects should be considered in further analysis.
-The fact that the family-level aggregated traits used in the re-analysis showed only slightly different results compared to the original analysis is in line with the findings of others that family-level traits can be sensitive enough to detect environmental impacts \cite{beketov_spear_2009}.
+The fact that the family-level aggregated traits used in the re-analysis showed only slightly different results compared to the original analysis is in line with the findings of others that family-level traits can be sensitive enough to detect environmental impacts (\cite{beketov_spear_2009}).
 % Cite another paper that uses family-level trait data
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 4. Ausblick und offene Fragen für zukünftige Studien
 
@@
 
-With the increasing use of computer vision in ecology, both species identification and trait quantification could be automated \cite{milosevic_application_2020, hoye_deep_2020}.
+With the increasing use of computer vision in ecology, both species identification and trait quantification could be automated (\cite{milosevic_application_2020, hoye_deep_2020}).
 This might result in more observational data and trait data on species-level in the future.
@@
 % However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets (see Table S2). 
+% Include Ben's point? Discussion on evolutionary history?
+% Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
+I wonder if this indicates that Family richness is really higher in Australia.
+Perhaps it might be as Australia has a wider range of evolutionary histories.
+This would be worth considering in the discussion
 

### 2020-12-21 Paper/Results/SI.tex
21.12: Edits Summary and References

@@
 Hence, differences for reproduction have been described in the paper.
-Body form traits are not different between databases, except that the North America (Vieira) database contains the trait Bluff (blocky) which does not appear in the other databases.}
+Body form traits are not different between databases, except that the North America (Vieira et al.) database contains the trait Bluff (blocky) which does not appear in the other databases.}
         \label{stab:trait_definitions}
@@
         \toprule[.1em]
-        Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & \specialcell{North America \\ (Twardochleb)} & 
-        North America (Vieira) & Australia & New Zealand \\
+        Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & \specialcell{North America \\ (Twardochleb et al.)} & 
+        North America (Vieira et al.) & Australia & New Zealand \\
         \toprule[.1em]
@@
 
-\subsection*{Differences in trait affinities obtained by trait aggregation methods com-pared to traits assigned at family-level}
+% \subsection*{Differences in trait affinities obtained by trait aggregation methods com-pared to traits assigned at family-level}
 
-\subsubsection*{Comparison of the trait aggregation methods with each other}
-\label{sec:compa_aggr_methods}
+% \subsubsection*{Comparison of the trait aggregation methods with each other}
+% \label{sec:compa_aggr_methods}
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{Comparison_trait_agg_methods.png}
-    \caption{Comparison of trait aggregation methods when aggregating over all traits for all datasets.
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=16.5cm, height=10cm]{Comparison_trait_agg_methods.png}
+%     \caption{Comparison of trait aggregation methods when aggregating over all traits for all datasets.
 Displayed are means of absolute differences in trait affinities with standard deviations (truncated at 0).
@@
 Total number of cases: Australia 2223, Europe 3352, New Zealand 777, and North America 4080.}
-    \label{fig:comp_aggr_methods}
-\end{figure}
+%     \label{fig:comp_aggr_methods}
+% \end{figure}
 

### 2020-12-21 Paper/Draft_harmonization_paper.tex
21.12: Edits Ralf Abstract and References

@@
 
-\section*{Summary}
+\section*{Abstract}
 
@@
 1.
-In recent years, comprehensive invertebrate trait databases have been established for different continents.
-The wide availability of invertebrate trait data should have created an impetus for trait-based studies, especially on large scales.
+Invertebrate traits are expected to be suitable for large-scale analysis in freshwater ecology due to their consistent response to environmental gradients.
+In recent years, comprehensive invertebrate trait databases have been established at different scales (e.g.
+regions, continents).
+The wide availability of invertebrate trait data supports trait-based studies, especially on large scales.
 However, a number of data-related problems hamper the work with trait data.
-For example, standardised trait definitions are lacking and coding of traits varies across trait databases impeding trait data synthesis.
-Another issue is different taxonomic resolutions between observational taxonomic data and trait databases, leading to the need to aggregate traits.
-% The aim of our study was to investigate discrepancies in trait definitions, to evaluate different trait aggregation methods and
+For example, for freshwater invertebrate traits standardised definitions are lacking and coding of traits varies across trait databases impeding trait data synthesis.
+Moreover, uncertainty remains how harmonising grouping features from different trait databases can influence trait-environment relationships.
+Another issue is that if the taxonomic resolution of observational taxonomic data is less precise than of trait databases, the traits in databases require aggregation before they can be linked to the observational data.
+% Here: Describe aims of the study or redundant with part 2? Something like this: The aim of our study is to investigate these data-related issues by synthesizing trait data from different databases.
 
 2.
-In this study, we describe discrepancies in trait definitions of trait databases from Europe, North America, New Zealand, and Australia for traits frequently used in ecological studies.
-Based on these trait databases we established 4 novel trait datasets by harmonising 7 commonly used grouping features.
+We describe discrepancies in trait definitions of trait databases from Europe, North America, New Zealand, and Australia for traits frequently used in ecological studies.
+Based on these trait databases, we established 4 novel trait datasets by harmonising 7 commonly used grouping features.
 Two of these datasets were used to evaluate different trait aggregation methods by comparing aggregated traits with assigned traits by experts at family-level.
-Furthermore, we explored the effect of grouping feature harmonisation and trait aggregation by re-analysing a study on the effect of anthropogenic salinisation on biological traits using harmonised grouping features and aggregated traits.
+We tested trait aggregation based on the mean and based on the median, each with different weightings.
+Furthermore, we explored the effect of grouping feature harmonisation and trait aggregation by re-analysing data from a case study.
 
 3.
-We found that investigated trait databases are distinct with regard to how grouping features are differentiated into traits, the scope of the grouping feature definitions, how traits are defined, and the coding to describe traits.
-Comparison of aggregated and assigned traits showed that aggregated traits are generally in conclusion with expert assignments, especially approaches using the median.
-Grouping feature harmonisation and trait aggregation had a minor impact in the re-analysis, although averaging effects can occur due to harmonisation diminishing the signal of a trait.
+Between the trait databases, grouping features varied in terms of their classification into traits, the scope of the grouping feature definitions, how traits are defined, and the coding to describe traits.
+Aggregated and assigned traits based on expert knowledge displayed a good match, specially approaches using the median.
+Grouping feature harmonisation and trait aggregation only slightly changed the results in the re-analysis compared to the original study, although averaging effects can occur due to harmonisation.
 
@@
 Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
-Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large scale analysis because the variability in trait responses is lower than in taxonomic responses (\cite{bonada_taxonomic_2007, baird_toward_2011}).
+Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large-scale analysis because the variability in trait responses is lower than in taxonomic responses (\cite{bonada_taxonomic_2007, baird_toward_2011}).
 Traits of freshwater invertebrate individuals are difficult to determine because - unlike plant traits - they often can not be measured directly.

### 2020-12-22 Paper/Draft_harmonization_paper.tex
22.12: Fixing references

@@
 backend = biber,
+natbib,
 style = apa,
@@
 maxcitenames = 2, 
-maxbibnames = 99 % ,
+maxbibnames = 99, 
+uniquename=false,
+uniquelist=false
 %sorting = none % sort by name year title
@@
 However, such analyses have been carried out mostly within continents, using information from one or two trait databases.
-For example, Bonada et al.
-(\cite{bonada_taxonomic_2007}) compared trait composition for Mediterranean and temperate regions in Europe using traits from Usseglio-Polatera et al.
-(\cite{usseglio-polatera_biomonitoring_2000}, typically referred to as Tachet database); Poff et al.
-(\cite{poff_developing_2010}) characterized trait composition across sites in the Western US using traits from Poff et al.
-(\cite{poff_functional_2006}), and Botwe et al.
-(\cite{botwe_effects_2018}) investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from Poff et al.
-(\cite{poff_functional_2006}) and Schäfer et al.
-(\cite{schafer_trait_2011}).
+For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from \citet{usseglio-polatera_biomonitoring_2000} (typically referred to as Tachet database); \citet{poff_developing_2010}) characterized trait composition across sites in the Western US using traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from \citet{poff_functional_2006}) and \citet{schafer_trait_2011}.
 Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different continents are rare.
 
-In this study, we follow the terminology proposed by Schmera et al.
-(\cite{schmera_proposed_2015}), where a grouping feature is defined as a general property (e.g.
+In this study, we follow the terminology proposed by \citet{schmera_proposed_2015}, where a grouping feature is defined as a general property (e.g.
 feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species".
@@
 
-To our knowledge, only Brown et al.
-(\cite{brown_functional_2018}) harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
+To our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
 We suspect that the heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents.
@@
 However, invertebrate trait databases are heterogeneous regarding the coding they use for their traits (\cite{culp_incorporating_2011}).
-For example, in the study from Brown et al.
-(\cite{brown_functional_2018}) the authors needed to reclassify traits using expert knowledge given that the individual databases employed different coding approaches (i.e.
+For example, in the study from \citet{brown_functional_2018} the authors needed to reclassify traits using expert knowledge given that the individual databases employed different coding approaches (i.e.
 European and New Zealand databases fuzzy coding, North American database binary coding).
@@
 We evaluate different trait aggregation methods by (2) comparing aggregated traits with assigned traits by experts at family-level for two of the established trait datasets.
-(3) we re-analysed data on the effect of anthropogenic salinisation on biological traits by Szöcs et al.
-(\cite{szocs_effects_2014}) using trait data from the established harmonised European trait datasets and aggregated traits.
+(3) we re-analysed data on the effect of anthropogenic salinisation on biological traits by \citet{szocs_effects_2014} using trait data from the established harmonised European trait datasets and aggregated traits.
 By comparison with the original analysis, we investigated how harmonising and aggregating trait data can modify the outcome of trait-environment relationships.
@@
 The freshwaterecology.info contains taxa on species-level, while taxa recorded in the Tachet database are on species, genus and family-level.
-Trait information for North America was obtained from Twardochleb et al.
-(\cite{twardochleb_trait_data_2020}) and complemented by Vieira et al.
-(\cite{vieira_database_nodate}).
+Trait information for North America was obtained from \citet{twardochleb_trait_data_2020} and complemented by \citet{vieira_database_nodate}.
 Data on body form for European and North American taxa was based on expert knowledge (\cite{polatera_personal_information_2020}).
@@
 Aggregated trait affinities of the five trait aggregation methods (\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg}) were compared to trait affinities assigned at family-level by experts, which were available for Australia and North America for a subset of grouping features and taxa.
-For the Australian dataset, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from Chessman et al.
-(\cite{chessman_dissolved-oxygen_2018}).
-In Chessman et al.
-(\cite{chessman_dissolved-oxygen_2018}) feeding mode is classified similarly as in the Australian dataset except that the trait parasite is missing.
-We conducted the comparison for the 220 families available in Chessman et al.
-(\cite{chessman_dissolved-oxygen_2018}).
+For the Australian dataset, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from \citet{chessman_dissolved-oxygen_2018}.
+In \citet{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the Australian dataset except that the trait parasite is missing.
+We conducted the comparison for the 220 families available in \citet{chessman_dissolved-oxygen_2018}.
 Considering each factor combination of family and trait (in total 8) this amounts to 1760 cases.
@@
 For the North American dataset, we compared aggregated trait affinities with assigned trait affinities on family-level for the grouping features feeding mode, respiration, size, voltinism, and locomotion.
-The assigned trait affinities at family-level are part of the North American database (Twardochleb) and originate from expert knowledge.
+The assigned trait affinities at family-level are part of the North American database (Twardochleb et al.) and originate from expert knowledge.
 Trait information was available for 94 families of which all were present in the North American dataset (total number of cases 1598).
@@
 
-We repeated the analysis of Szöcs et al.
-(\cite{szocs_effects_2014}) who studied the effect of anthropogenic salinization on invertebrates in the River Werra in Germany.
+We repeated the analysis of \citet{szocs_effects_2014} who studied the effect of anthropogenic salinization on invertebrates in the River Werra in Germany.
 For the re-analysis we used the established harmonised grouping feature dataset for Europe and additionally aggregated traits using the aforementioned aggregation methods.
@@
 Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition.
-Further details can be found in Szöcs et al.
-(\cite{szocs_effects_2014}).
+Further details can be found in \citet{szocs_effects_2014}.
 
@@
 CWM traits with a mahalanobis distance greater than the $97.5 \%$ -quantile of the Chi-square distribution (5.02) were regarded as traits responding to either low or high salinity.
-For our analysis, we used the same 21 grouping features that Szöcs et al.
-(\cite{szocs_effects_2014}) used.
+For our analysis, we used the same 21 grouping features that \citet{szocs_effects_2014} used.
 The 6 harmonised grouping features used were \textit{Size, Feeding mode, Locomotion, Oviposition, Respiration}, and \textit{Voltinism}.
-Additionally, for testing the effect of aggregated traits we assigned to each taxon in Szöcs et al.
-(\cite{szocs_effects_2014}) the aggregated trait value for its corresponding family and repeated the RDA.
+Additionally, for testing the effect of aggregated traits we assigned to each taxon in \citet{szocs_effects_2014} the aggregated trait value for its corresponding family and repeated the RDA.
 
@@
 
-The original RDA in Szöcs et al.
-(\cite{szocs_effects_2014}) indicated that downstream sites (high salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle duration ($> 1$ year), and gill respiration and upstream sites (low salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
+The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (high salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle duration ($> 1$ year), and gill respiration and upstream sites (low salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
 
@@
 Such initiatives could be a role model for freshwater ecologists to establish unambiguous terminologies for invertebrate traits.
-The existing freshwater invertebrate trait databases could be linked through standardised terminologies or ontologies, as suggested by Baird et al.
-(\cite{baird_toward_2011}) almost a decade ago.
+The existing freshwater invertebrate trait databases could be linked through standardised terminologies or ontologies, as suggested by \citet{baird_toward_2011} almost a decade ago.
 By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS) providers of invertebrate trait data could connect their traits to such ontologies (\cite{schneider_towards_2019}).
@@
 Some traits can vary strongly on more precise taxonomic levels than the family-level.
-For example, Monaghan and Soares (\cite{monaghan_improving_2013}) found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction.
+For example, \citet{monaghan_improving_2013} found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction.
 Furthermore, studies focusing on the lability of traits, i.e.
@@
 With the increasing use of computer vision in ecology, both species identification and trait quantification could be automated (\cite{milosevic_application_2020, hoye_deep_2020}).
-This might result in more observational data and trait data on species-level in the future.
+This development might result in more observational data and trait data on species-level in the future.
 However, if traits need to be aggregated we showed that trait aggregation is often in conclusion with expert assignments, specifically aggregation approaches using the median.

### 2020-12-22 Paper/Draft_harmonization_paper.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{DRAFT: Harmonisation and trait aggregation paper }
+\title{Tackling discrepancies in freshwater invertebrate trait databases and taxonomic resolution: Harmonising across continents and trait aggregation}
 \author{}%Stefan Kunz 
@@
 However, a number of data-related problems hamper the work with trait data.
-For example, for freshwater invertebrate traits standardised definitions are lacking and coding of traits varies across trait databases impeding trait data synthesis.
+For example, for freshwater invertebrate traits standardised definitions are lacking impeding trait data synthesis.
 Moreover, uncertainty remains how harmonising grouping features from different trait databases can influence trait-environment relationships.
-Another issue is that if the taxonomic resolution of observational taxonomic data is less precise than of trait databases, the traits in databases require aggregation before they can be linked to the observational data.
+Another issue is that if the taxonomic resolution of observational taxonomic data is less precise than in trait databases, the traits in databases require aggregation before they can be linked to the observational data.
 % Here: Describe aims of the study or redundant with part 2? Something like this: The aim of our study is to investigate these data-related issues by synthesizing trait data from different databases.
@@
 3.
-Between the trait databases, grouping features varied in terms of their classification into traits, the scope of the grouping feature definitions, how traits are defined, and the coding to describe traits.
+Between the trait databases, grouping features differed in terms of their classification into traits and their scope leading to discrepancies how traits are defined.
+Also, the coding to describe traits varied between databases.
 Aggregated and assigned traits based on expert knowledge displayed a good match, specially approaches using the median.
@@
 However, such analyses have been carried out mostly within continents, using information from one or two trait databases.
-For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from \citet{usseglio-polatera_biomonitoring_2000} (typically referred to as Tachet database); \citet{poff_developing_2010}) characterized trait composition across sites in the Western US using traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from \citet{poff_functional_2006}) and \citet{schafer_trait_2011}.
+For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from \citet{usseglio-polatera_biomonitoring_2000} (typically referred to as Tachet database); \citet{poff_developing_2010} characterized trait composition across sites in the Western US using traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from \citet{poff_functional_2006}) and \citet{schafer_trait_2011}.
 Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different continents are rare.

### 2020-12-22 Paper/Draft_harmonization_paper.tex
22.12: Minor Edits

@@
 However, such analyses have been carried out mostly within continents, using information from one or two trait databases.
-For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from \citet{usseglio-polatera_biomonitoring_2000} (typically referred to as Tachet database); \citet{poff_developing_2010} characterized trait composition across sites in the Western US using traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from \citet{poff_functional_2006}) and \citet{schafer_trait_2011}.
+For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from \citet{usseglio-polatera_biomonitoring_2000} (typically referred to as Tachet database); \citet{poff_developing_2010} characterized trait composition across sites in the Western US using traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from \citet{poff_functional_2006} and \citet{schafer_trait_2011}.
 Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different continents are rare.

### 2021-01-20 Paper/Draft_harmonization_paper.tex
20.01: Added and started implementing comments from PUP and BK

@@
 Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large-scale analysis because the variability in trait responses is lower than in taxonomic responses (\cite{bonada_taxonomic_2007, baird_toward_2011}).
-Traits of freshwater invertebrate individuals are difficult to determine because - unlike plant traits - they often can not be measured directly.
+Traits of individual freshwater invertebrate are difficult to determine because - unlike plant traits - they are often difficult to measure directly.
 For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community (\cite{moog_comprehensive_nodate}).
 Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
-by relating macroinvertebrate trait composition to environmental factors and as trait metrics in biomonitoring (\cite{poff_developing_2010, szocs_effects_2014, bhowmik_large_2015, menezes_beyond_2010}).
+by relating macroinvertebrate trait composition to environmental factors and as trait metrics in biomonitoring (\cite{bhowmik_large_2015, menezes_beyond_2010, poff_developing_2010, szocs_effects_2014}).
 
@@
 The availability of invertebrate trait data from different continents enables comparisons of trait variation and analyses of their relation to environmental factors across large scales.
-However, such analyses have been carried out mostly within continents, using information from one or two trait databases.
-For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from \citet{usseglio-polatera_biomonitoring_2000} (typically referred to as Tachet database); \citet{poff_developing_2010} characterized trait composition across sites in the Western US using traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from \citet{poff_functional_2006} and \citet{schafer_trait_2011}.
+To date, such analyses have been carried out mostly within continents, using information from one or two trait databases.
+For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from \citet{ussegliopolatera_biological_2000} (typically referred to as Tachet database); \citet{poff_developing_2010} characterized trait composition across sites in the Western US using traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from \citet{poff_functional_2006} and \citet{schafer_trait_2011}.
 Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different continents are rare.
+
+% Ben suggests: 
+% Need something here like: One challenge in comparing traits of freshwater invertebrates across many continents are difference in the recording of trait information in the various continental trait databases.
+For example, ......,
 
@@
 Thus, we use the term grouping feature in place of which many studies use the term "trait", and the term trait instead of "trait state", "modality" or "trait category".
+% Ben suggest here: For  example  e.g., predator, shredder, etc. Are traits of the grouping feature ..... and removing predator, shredder, etc. from the sentence above.
 Traits can be described using different codings (binary, fuzzy) that represent the prevalence of a characteristic in an organism.
@@
 Conversely, if trait information is only available on more precise taxonomic levels than the observed taxa, traits are aggregated to a less precise taxonomic level (e.g.
-\cite{poff_functional_2006, szocs_effects_2014, piliere_a._f._h._importance_2016, aspin_extreme_2019}).
+\cite{aspin_extreme_2019, piliere_a._f._h._importance_2016, poff_functional_2006, szocs_effects_2014}).
 Studies have used different methods of trait aggregation, e.g.
 the mean (\cite{magliozzi_functional_2019}), median (\cite{szocs_effects_2014}) or the mode (\cite{piliere_a._f._h._importance_2016}).
-Up to now, studies on how and to which extent different trait aggregation methods influence trait-based analysis are missing.
+Studies on how and to which extent different trait aggregation methods influence trait-based analysis are missing.
 However, related knowledge would inform future studies regarding the choice of the aggregation method.
@@
 We extracted information from 6 trait databases from Europe, North America, Australia, and New Zealand and harmonised 7 grouping features.
-Trait information for Europe was obtained from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}) and the Tachet database (\cite{usseglio-polatera_biomonitoring_2000}).
+Trait information for Europe was obtained from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}) and the Tachet database (\cite{ussegliopolatera_biological_2000}).
 The freshwaterecology.info contains taxa on species-level, while taxa recorded in the Tachet database are on species, genus and family-level.
@@
 crawlers and sprawlers into crawlers).
-Thereby, for a particular taxa the highest trait affinity score among the amalgamated traits was taken.
+Thereby, for a particular taxon the highest trait affinity score among the amalgamated traits was taken.
 
@@
 the coordinates of the tips of the vectors representing the CWM traits in the bi- or triplots.
-Following the original study, we identified traits associated with high or low salinity based on their distance to the ordination axis median using the mahalanobis distance.
-CWM traits with a mahalanobis distance greater than the $97.5 \%$ -quantile of the Chi-square distribution (5.02) were regarded as traits responding to either low or high salinity.
+Following the original study, we identified traits associated with high or low salinity based on their distance to the ordination axis median using the Mahalanobis distance.
+CWM traits with a Mahalanobis distance greater than the $97.5 \%$ -quantile of the Chi-square distribution (5.02) were regarded as traits responding to either low or high salinity.
 For our analysis, we used the same 21 grouping features that \citet{szocs_effects_2014} used.
@@
     \toprule[.1em]
-    Database & Nr. of taxa & Species & Genus & Family & Nr. aquatic insects \\ 
+    Dataset & Nr. of taxa & Species & Genus & Family & Nr. aquatic insects \\ 
     \toprule[.1em]
@@
     \toprule[.1em]
-    Database & Body form & Oviposition & Voltinism & Locomotion & Size & Respiration & Feeding mode \\ 
+    Dataset & Body form & Oviposition & Voltinism & Locomotion & Size & Respiration & Feeding mode \\ 
     \toprule[.1em]
@@
 The freshwaterecology.info database, the Tachet database and the North American database (Twardochleb et al.) provided more detailed descriptions of their trait information compared to the North American (Vieira et al.) and New Zealand database.
-An exception is the Australian trait database which is a collection of seven specific trait datasets (\cite{kefford_integrated_2020}).
+An exception is the Australian trait database (\cite{kefford_integrated_2020}) which is a collection of seven specific trait datasets.
 Thus, grouping features occur multiple times with varying differentiation into traits.
@@
 
-As expected with increasing trait variability the produced range of trait affinities increased for all aggregation methods (Figure \ref{fig:overview_sim_results}).
+As expected with increasing trait variability the produced range of trait affinities increased for all aggregation methods (Figure \ref{fig:overview_sim_results}).% Ben would add: 
+ % as indicated by the increasing range of the boxes and wiskers with increasing standard deviation.
+
+ % Ben further suggests: When each genus has the same number of species (sim base) ......
+.
+In contrast with most species in one genus and fewer in the other genera (sim_extreme) ....
+.
+While with variable number of species per genera () .....
+.
+
 The mean aggregation methods yielded similar ranges of aggregated trait affinities within each level of trait variability for the \textit{sim\_base} scenario.
@@
 
-The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (high salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle duration ($> 1$ year), and gill respiration and upstream sites (low salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
+The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (higher salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle duration ($> 1$ year), and gill respiration and upstream sites (lower salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
+
+%BEN: Suggest start with some overall main message.
+The main message I get from Fig 6 is: „The original analysis in Szocs et al.
+(2014) and all agrigration methods produced very similar distributions of RDA species scores (Figure 6).“ I suggest start with this sentence (or something like this), then  draw out any details but only if necessary (i.e.
+do not feel compelled to say more if there is not really much more to say).
 
@@
 
-Using at family-level aggregated traits from the harmonised dataset showed also results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figure \ref{fig:violin_plot_species_sc} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+Using family-level aggregated traits from the harmonised dataset showed also results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figure \ref{fig:violin_plot_species_sc} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
 The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg}
@@
 
-Although comprehensive invertebrate trait databases have been developed for several regions in the past, data synthesis is difficult due to discrepancies in trait definitions.
+Although comprehensive invertebrate trait databases have been developed for several regions, data synthesis is difficult due to discrepancies in trait definitions.
 By providing an overview of these definition discrepancies we hope to set a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
@@
 
-With the increasing use of computer vision in ecology, both species identification and trait quantification could be automated (\cite{milosevic_application_2020, hoye_deep_2020}).
+With the increasing use of computer vision in ecology, both species identification and trait quantification could be automated (\cite{hoye_deep_2020, milosevic_application_2020}).
 This development might result in more observational data and trait data on species-level in the future.

### 2021-01-20 Paper/Draft_harmonization_paper.tex
21.01.: Small changes in Paper

--- 2020-12-22 Paper/Draft_harmonization_paper.tex
@@
 We evaluate different trait aggregation methods by (2) comparing aggregated traits with assigned traits by experts at family-level for two of the established trait datasets.
-(3) we re-analysed data on the effect of anthropogenic salinisation on biological traits by \citet{szocs_effects_2014} using trait data from the established harmonised European trait datasets and aggregated traits.
+(3) we re-analysed data on the effect of anthropogenic salinisation on biological traits by \citet{szocs_effects_2014} using trait data from the established harmonised European trait dataset and aggregated traits.
 By comparison with the original analysis, we investigated how harmonising and aggregating trait data can modify the outcome of trait-environment relationships.
@@
 In total every family consisted of 25 species.
-To each hypothetical taxonomic hierarchy a hypothetical grouping feature with 3 traits was assigned.
+To each scenario a hypothetical grouping feature with 3 traits was assigned.
 The 25 affinities for each trait were simulated by sampling from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviations (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability.
@@
 
-We evaluate the simulation results based on the produced range of aggregated trait affinities and by comparing results of every simulated dataset.
+We evaluated the simulation results based on the produced range of aggregated trait affinities and by comparing results of every simulated dataset.
 
@@
 
-While trait information from Europe and New Zealand was mainly on species-level, considerable portions of trait data from North America and Australia were on genus or family-level (Table \ref{tab:tax_coverage}).
+While trait information from Europe and New Zealand was mainly on species-level, considerable portions of trait data from North America and Australia were on genus or family-level.
 Assigned traits on family-level might not reflect the real trait diversity within a taxon, for example for Chironomidae (\cite{serra_synthesising_2016}).

### 2021-01-22 Paper/Draft_harmonization_paper.tex
22.01: Added (final) comments and corrections from Co-Authors

--- 2021-01-20 Paper/Draft_harmonization_paper.tex
@@
 1.
-Invertebrate traits are expected to be suitable for large-scale analysis in freshwater ecology due to their consistent response to environmental gradients.
+Use of invertebrate traits rather than species composition is expected  expected to facilitate large-scale comparisons of community structure and responses to disturbance in freshwater ecology because the same traits can potentially occur everywhere.
+% OLD: because of their consistent response to environmental gradients
 In recent years, comprehensive invertebrate trait databases have been established at different scales (e.g.
 regions, continents).
-The wide availability of invertebrate trait data supports trait-based studies, especially on large scales.
+The wide availability of invertebrate trait data supports trait-based studies, especially at large scales.
 However, a number of data-related problems hamper the work with trait data.
-For example, for freshwater invertebrate traits standardised definitions are lacking impeding trait data synthesis.
-Moreover, uncertainty remains how harmonising grouping features from different trait databases can influence trait-environment relationships.
+For example, for freshwater invertebrate traits standardised definitions are lacking, impeding comparisons across regions.
+Moreover, it is uncertain how standardising grouping features from different databases might influence trait-environment relationships.
 Another issue is that if the taxonomic resolution of observational taxonomic data is less precise than in trait databases, the traits in databases require aggregation before they can be linked to the observational data.
@@
 2.
-We describe discrepancies in trait definitions of trait databases from Europe, North America, New Zealand, and Australia for traits frequently used in ecological studies.
-Based on these trait databases, we established 4 novel trait datasets by harmonising 7 commonly used grouping features.
-Two of these datasets were used to evaluate different trait aggregation methods by comparing aggregated traits with assigned traits by experts at family-level.
+We describe discrepancies in the definitions of traits used to create freshwater invertebrate trait databases in Europe, North America, New Zealand, and Australia.
+Based on our comparisons of these trait databases, we established 4 novel trait datasets by harmonising 7 commonly used grouping features.
+Two of these datasets were used to compare aggregated traits obtained by different aggregation methods with traits assigned by experts at family-level.
 We tested trait aggregation based on the mean and based on the median, each with different weightings.
@@
 Also, the coding to describe traits varied between databases.
-Aggregated and assigned traits based on expert knowledge displayed a good match, specially approaches using the median.
+Aggregated and assigned traits based on expert knowledge displayed a good match, especially approaches using the median.
 Grouping feature harmonisation and trait aggregation only slightly changed the results in the re-analysis compared to the original study, although averaging effects can occur due to harmonisation.
@@
 Explaining and predicting how communities are shaped by environmental factors is one of the main goals of ecology.
-Species traits, defined as measurable properties of an organism (\cite{mcgill_rebuilding_2006}), might be beneficial in achieving this goal (\cite{heino_jani_macroecological_2013}).
-Traits evolve through adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and indicate direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
-Besides providing a mechanistic explanation of species-environment relationships, trait-based approaches might be suitable for large-scale analysis because the variability in trait responses is lower than in taxonomic responses (\cite{bonada_taxonomic_2007, baird_toward_2011}).
+Species traits are measurable properties of an organism (\cite{mcgill_rebuilding_2006}), and comparing communities based on the traits possessed by species may facilitate testing of a range of ecological hypotheses (\cite{heino_jani_macroecological_2013}).
+Traits are assumed to be adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and represent direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
+Besides providing more mechanistic-based expressions of species-environment relationships, trait-based approaches might be suitable for large-scale analysis because the variability in trait responses is lower than in taxonomic responses (\cite{baird_toward_2011, bonada_taxonomic_2007}).
+
 Traits of individual freshwater invertebrate are difficult to determine because - unlike plant traits - they are often difficult to measure directly.
-For example, to gain knowledge on feeding habits requires evaluating mouthpart morphology, consumed food, and the organisms function within its community (\cite{moog_comprehensive_nodate}).
+For example, to describe feeding habits requires that we understand both mouthpart morphology and the specific food that is consumed, and the organisms function within its community (\cite{moog_comprehensive_nodate}).
 Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
@@
 
-In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases for various continents (\cite{usseglio-polatera_biomonitoring_2000, schmidt-kloiber_www.freshwaterecology.info_2015, vieira_database_nodate, Philips_and_Smith_NZ_DB_2018, kefford_integrated_2020, tomanova_trophic_2006}).
-The availability of invertebrate trait data from different continents enables comparisons of trait variation and analyses of their relation to environmental factors across large scales.
+In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases for various continents (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate}).
+The availability of invertebrate trait data from different continents arguably enables comparisons of trait variation and testing if variation in trait structure is consistently related to environmental factors across both small and large spatial extents.
 To date, such analyses have been carried out mostly within continents, using information from one or two trait databases.
-For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe using traits from \citet{ussegliopolatera_biological_2000} (typically referred to as Tachet database); \citet{poff_developing_2010} characterized trait composition across sites in the Western US using traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} investigated the effect of salinity on invertebrate traits in different sites in South Australia using trait data from \citet{poff_functional_2006} and \citet{schafer_trait_2011}.
+For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe based on traits from \citet{ussegliopolatera_biological_2000} (typically referred to as the Tachet database), \citet{poff_developing_2010} characterized trait composition across sites in the Western USA based on traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} used trait definitions from \citet{poff_functional_2006} and \citet{schafer_trait_2011} to test for effects of salinity on invertebrate traits across different sites in South Australia.
 Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different continents are rare.
@@
 
-Traits can be described in a binary fashion, or with multiple categories, ignoring uncertainty how the trait is expressed in any particular organism (e.g.
+Traits can be described in a binary fashion, or with multiple categories, ignoring uncertainty in how traits are expressed in any particular organism (e.g.
 adult terrestrial stage, presence of gills) or continuous (e.g.
@@
 Discrepancies in the taxonomic resolutions (e.g.
-species, genus or family) when linking observational taxonomic data to trait database represents another challenge.
-When observations are on a more precise taxonomic level than data available in the trait databases (e.g.
-observations on species-level, trait data on genus-level) trait information of the less precise taxonomic level is often assigned (e.g.
+species, genus or family) when linking observational taxonomic data to trait databases represents another challenge.
+When observations are at a more precise taxonomic level than data available in the trait databases (e.g.
+observations at species-level, trait data at genus-level) trait information of the less precise taxonomic level is often assigned (e.g.
 \cite{szocs_effects_2014, vos_taxonomic_2017}).
-Conversely, if trait information is only available on more precise taxonomic levels than the observed taxa, traits are aggregated to a less precise taxonomic level (e.g.
+Conversely, if trait information is only available at more precise taxonomic levels than the observed taxa, traits are aggregated to a less precise taxonomic level (e.g.
 \cite{aspin_extreme_2019, piliere_a._f._h._importance_2016, poff_functional_2006, szocs_effects_2014}).
-Studies have used different methods of trait aggregation, e.g.
+To data, studies have used different methods of trait aggregation, e.g.
 the mean (\cite{magliozzi_functional_2019}), median (\cite{szocs_effects_2014}) or the mode (\cite{piliere_a._f._h._importance_2016}).
@@
 
-The outlined difficulties when working with or synthesizing trait data motivated us to (1) investigate discrepancies in trait definition between trait databases from Europe, North America, Australia, and New Zealand.
-As a basis for further evaluating different trait aggregation methods and how harmonising definition discrepancies between grouping features can influence trait-environment relationships, we established 4 novel invertebrate trait datasets from these trait databases by harmonising 7 grouping features.
-We evaluate different trait aggregation methods by (2) comparing aggregated traits with assigned traits by experts at family-level for two of the established trait datasets.
-(3) we re-analysed data on the effect of anthropogenic salinisation on biological traits by \citet{szocs_effects_2014} using trait data from the established harmonised European trait datasets and aggregated traits.
-By comparison with the original analysis, we investigated how harmonising and aggregating trait data can modify the outcome of trait-environment relationships.
+These challenges when working with or synthesizing trait data motivated us to (1) investigate discrepancies in trait definition between trait databases from Europe, North America, Australia, and New Zealand.
+As a basis for further evaluating different trait aggregation methods and how harmonising definition discrepancies between grouping features can influence trait-environment relationships, we developed 4 novel invertebrate trait datasets from these existing trait databases by harmonising 7 grouping features.
+(2) We then evaluated different trait aggregation methods by comparing aggregated traits with traits assigned by experts at family-level for two of the established trait datasets.
+(3) Finally, we re-analysed data from a study of salinisation effects on biological traits (\cite{szocs_effects_2014}) using data from the newly established harmonised European trait dataset and aggregated traits.
+By comparing the re-analysis's findings with those of \citet{szocs_effects_2014}, we investigated how harmonising and aggregating trait data can modify the outcome of trait-environment relationships.
 
@@
 Data on body form for European and North American taxa was based on expert knowledge (\cite{polatera_personal_information_2020}).
-For Australia and New Zealand, we used trait databases from Kefford et al.
-(\cite{kefford_integrated_2020}) and Philips and Smith respectively (\cite{Philips_and_Smith_NZ_DB_2018}).
+For Australia and New Zealand, we used trait databases from \citet{kefford_integrated_2020} and \citet{Philips_and_Smith_NZ_DB_2018} respectively.
 To increase readability we refer to the databases as well as the datasets we extracted from them by the name of the continent they originate from, except for European databases, which we refer to by their commonly used names (freshwaterecology.info and Tachet database).
@@
 temperature preference) because these traits are missing in the New Zealand trait database.
-The grouping features were differently classified across the databases, we therefore harmonised them into 26 traits (Table \ref{tab:traits_harmonisation}).
+Because grouping features were differently classified across the databases, we harmonised them into 26 traits (Table \ref{tab:traits_harmonisation}).
 Harmonisation was undertaken by amalgamating similar traits into one trait (e.g.
 crawlers and sprawlers into crawlers).
-Thereby, for a particular taxon the highest trait affinity score among the amalgamated traits was taken.
+When doing so, for each taxon the highest trait affinity score among the amalgamated traits was taken.
 
-We used fuzzy coding for establishing our harmonised datasets unless data quality prohibited.
-In the latter case we used binary traits, i.e.
+We used fuzzy coding for establishing our harmonised datasets unless data quality prohibited this.
+In the latter case, we used binary traits, i.e.
 categorical and continuous traits were converted into binary traits.
@@
 Hence, entries such as "arctic" or "boreal" in the voltinism traits were substituted with a value of 1.
-Implicitly, we assumed for binary traits that a value of 1 and 0 corresponds to the highest and no affinity for a particular trait.
+Implicitly, we assumed for binary traits that a value of 1 and 0 corresponded to the highest and no affinity for a particular trait.
 Fuzzy codes are reported with different ranges in the trait databases (e.g.
@@
 
-Prior to harmonisation we consolidated duplicate taxa on species, genus or family-level if present within a dataset, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
-We omitted taxa with a lower taxonomic precision than family-level.
+Prior to harmonisation, we consolidated duplicate taxa at the species, genus or family-level if present within a dataset, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
+We also omitted all taxa with a lower taxonomic precision than family-level.
 
@@
 \begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-    \textit{a} The trait "bluff (blocky)" occurred in the North America (Vieira et al.) database and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}).
+    \textit{a} The trait "bluff (blocky)" occurred in the North America database (Vieira et al.) and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}).
 \\
@@
 We conducted the comparison for the 220 families available in \citet{chessman_dissolved-oxygen_2018}.
-Considering each factor combination of family and trait (in total 8) this amounts to 1760 cases.
+Considering each factor combination of family and trait (in total 8) this amounted to 1760 cases.
 
@@
 
-\subsection*{Analysis of the effect of harmonisation and trait aggregation on trait-environment relationships}
+\subsection*{Effects of harmonisation and trait aggregation on trait-environment relationships}
 
 We repeated the analysis of \citet{szocs_effects_2014} who studied the effect of anthropogenic salinization on invertebrates in the River Werra in Germany.
-For the re-analysis we used the established harmonised grouping feature dataset for Europe and additionally aggregated traits using the aforementioned aggregation methods.
+For this re-analysis we used the established harmonised grouping feature dataset for Europe and additionally aggregated traits using the aforementioned aggregation methods.
 
-The river Werra has been subject to effluents from the potash industry since the mid of the 20th century and allows to study responses of invertebrates and their trait compositions to salinization (\cite{bathe_biological_2011}).
+The River Werra has been subject to effluents from the potash industry since the mid- 20th century and allows to study responses of invertebrates and their trait compositions to salinization (\cite{bathe_biological_2011}).
 Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition.
@@
 CWM traits with a Mahalanobis distance greater than the $97.5 \%$ -quantile of the Chi-square distribution (5.02) were regarded as traits responding to either low or high salinity.
-For our analysis, we used the same 21 grouping features that \citet{szocs_effects_2014} used.
+For our analysis, we used the same 21 grouping features as in \citet{szocs_effects_2014}.
 The 6 harmonised grouping features used were \textit{Size, Feeding mode, Locomotion, Oviposition, Respiration}, and \textit{Voltinism}.
@@
 The data processing and aforementioned analyses were carried out using R (Version 3.6.1).
-Raw data and the R code for data processing and grouping feature harmonisation is located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
+Raw data and the R code for data processing and grouping feature harmonisation are located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
 Scripts and data to reproduce the trait aggregation and analysis with aggregated traits are located in the Github repository \url{https://github.com/KunzstLD/Trait-aggregation}.
@@
 
-Regarding the taxonomic coverage, the New Zealand dataset has the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
-By contrast, the European trait dataset has the largest taxon pool with 4601 taxa followed by the North American trait dataset that contained trait information on 3753 taxa.
+Regarding taxonomic coverage, the New Zealand dataset has the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
+By contrast, the European trait dataset has the largest taxon pool with 4601 taxa followed by the North American dataset that contains trait information on 3753 taxa.
 The Australian dataset contains 1402 taxa.
-The European, New Zealand, and North American datasets have most taxa on the species-level whereas the Australian dataset has a similar number of taxa on species and genus-level.
+The European, New Zealand, and North American datasets contain most taxa at the species-level whereas the Australian dataset comprises a similar number of taxa at species and genus-level.
 
@@
     \centering
-    \caption{Number of taxa per harmonised dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percentage.} 
+    \caption{Number of taxa per harmonised dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percent.} 
     \label{tab:tax_coverage}
@@
 
-The amount of entries with available information for the selected grouping features varied strongly for the established European, North American, and Australian trait datasets (Table \ref{tab:trait_coverage}).
+The amount of entries with available information for the selected grouping features varied strongly for the developed European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
 By contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
@@
     \centering
-    \caption{Rounded percentage of entries that have 
+    \caption{Rounded percentage of entries that include 
     information for the individual grouping features
@@
 
-\subsection*{Discrepancies of invertebrate trait definitions}
+\subsection*{Discrepancies in invertebrate trait definitions across databases}
 
@@
 The freshwaterecology.info database, the Tachet database and the North American database (Twardochleb et al.) provided more detailed descriptions of their trait information compared to the North American (Vieira et al.) and New Zealand database.
-An exception is the Australian trait database (\cite{kefford_integrated_2020}) which is a collection of seven specific trait datasets.
+The Australian trait database (\cite{kefford_integrated_2020}) is a collection of seven specific trait datasets.
 Thus, grouping features occur multiple times with varying differentiation into traits.
@@
 Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the North American (Vieira et al.) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb et al.) database includes not only the way of movement, but also the location of movement.
-Similarly, regarding the reproduction traits, databases differ in their scope.
+Similarly, regarding reproduction traits, databases differ in their scope.
 Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases.
@@
 binary, fuzzy, continuous).
-The freshwaterecology.info and Australian use different codings in their databases.
-Tachet and the New Zealand database exclusively use fuzzy coding.
+The freshwaterecology.info and Australian databases use different codings, while the Tachet and the New Zealand database exclusively use fuzzy coding.
 Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
@@
 
-We evaluate the simulation results based on the produced range of aggregated trait affinities and by comparing results of every simulated dataset.
+We evaluated the simulation results based on the produced range of aggregated trait affinities and by comparing results of every simulated dataset.
 
-As expected with increasing trait variability the produced range of trait affinities increased for all aggregation methods (Figure \ref{fig:overview_sim_results}).% Ben would add: 
+As expected the produced range of trait affinities increased for all aggregation methods with increasing trait variability (Figure \ref{fig:overview_sim_results}).% Ben would add: 
  % as indicated by the increasing range of the boxes and wiskers with increasing standard deviation.
@@
 
-The mean aggregation methods yielded similar ranges of aggregated trait affinities within each level of trait variability for the \textit{sim\_base} scenario.
-The median aggregation methods yielded mostly greater ranges of aggregated trait affinities for the \textit{sim\_base} scenario.
+For the \textit{sim\_base} scenario, the mean aggregation methods yielded similar ranges of aggregated trait affinities within each level of trait variability whereas the median aggregation methods produced mostly greater ranges of aggregated trait affinities.
 By contrast, the ranges of trait affinities slightly differed for all aggregation methods for the simulation scenarios \textit{sim\_extreme} and \textit{sim\_variation}.
@@
   \centering
-  \caption{Amount of differing cases, minimum, maximum, means, and standard deviations of absolute differences between trait affinities assigned at family-level and aggregated trait affinities.}
+  \caption{Frequency of differing cases, minimum, maximum, means, and standard deviations of absolute differences between trait affinities assigned at family-level and aggregated trait affinities.}
   \label{tab:summary_stat_aggr_vs_fam_assigned}
@@
   \toprule[.1em]
-  \multirow{4}{*}{\specialcell{Australia \\ (Chessman)}} & \specialcell{direct\_agg (median)} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
+  \multirow{4}{*}{\specialcell{Australia}} & \specialcell{direct\_agg (median)} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
   & \specialcell{direct\_agg (mean)} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
@@
 Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
-Absolute differences in trait affinities are depicted as gray dots.
-N denotes the number of cases per comparison where differences occurred.
-The blue dot indicates the mean of absolute differences and the error bars the standard deviation.
-The gray vertical lines show the 25th, 50th and 75th quantile of the density estimate.}
+For more details see Figure \ref{fig:diff_aggr_traits_chessman}}
   \label{fig:diff_aggr_traits_pyne}
@@
 
-The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (higher salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle duration ($> 1$ year), and gill respiration and upstream sites (lower salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
+The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (higher salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle duration ($> 1$ year), and gill respiration, whereas upstream sites (lower salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
 
@@
 
-Using harmonised grouping features resulted in less traits that distinguish upstream and downstream sites in comparison to the original analysis (Figure \ref{fig:violin_plot_species_sc} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+Using harmonised grouping features resulted in less traits that distinguish upstream and downstream sites in comparison to the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
 According to the RDA of the trait composition, downstream sites were characterised by taxa with the traits multivoltinism, ovoviviparity and long life cycle duration.
@@
 
-Using family-level aggregated traits from the harmonised dataset showed also results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figure \ref{fig:violin_plot_species_sc} and Figure \ref{fig:boxplots_scores_on_constrained_axis}).
+Using traits aggregated at family-level from the harmonised dataset also showed results similar to the original analysis, but with fewer traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
 The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg}
@@
 The same results were obtained when re-analysing the data with traits aggregated by the \textit{stepwise\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, with the exception that none of the life cycle traits characterised upstream or downstream sites.
-Thus, in our comparison aggregating by \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg} yielded to the least change in interpretation of the RDA results compared to the original results.
+Thus, in our comparison aggregating by \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg} yielded the least change in interpretation of the RDA results compared to the original findings.
 
@@
 
-Synthesizing trait information from multiple trait databases is crucial to unfold the full potential of trait-based approaches, e.g.
+Synthesizing trait information from multiple trait databases is crucial for developing the full potential of trait-based approaches, e.g.
 for studying community trait responses to environmental gradients worldwide.
-Our attempt of harmonising invertebrate trait information from trait databases of different regions showed that grouping feature harmonisation is labour-intensive because grouping features are differentiated differently into traits between trait databases and various codings are used to describe traits.
+Our attempt at harmonising invertebrate trait information from trait databases of different regions showed that grouping feature harmonisation was labour-intensive because grouping features are differentiated differently into traits between trait databases and various codings are used to describe traits.
 In addition, the same traits are sometimes defined differently in the investigated databases, requiring expert knowledge to reclassify these traits (e.g.
@@
 Such initiatives could be a role model for freshwater ecologists to establish unambiguous terminologies for invertebrate traits.
-The existing freshwater invertebrate trait databases could be linked through standardised terminologies or ontologies, as suggested by \citet{baird_toward_2011} almost a decade ago.
-By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS) providers of invertebrate trait data could connect their traits to such ontologies (\cite{schneider_towards_2019}).
+The existing freshwater invertebrate trait databases could be linked through standardised terminologies or ontologies, as suggested by \citet{baird_toward_2011} a decade ago.
+By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS), providers of invertebrate trait data could connect their traits to such ontologies (\cite{schneider_towards_2019}).
 Once standardised trait definitions are established, these will improve trait data sharing, trait data processing when working with multiple trait databases, and ultimately interpretation of the derived results.
@@
 Our analysis aimed to use most of the available invertebrate trait information for different regions to establish harmonised grouping feature datasets.
-Although many taxa are covered in the trait databases from which we extracted our trait datasets, the availability of trait information varies strongly across grouping features and taxonomic resolution differs between databases.
+Although many taxa are covered in the trait databases from which we extracted our datasets, the availability of trait information varies strongly across grouping features and taxonomic resolution differs between databases.
 Much information is available for grouping features that are often used in trait-environment studies, such as feeding mode and respiration.
@@
 
-While trait information from Europe and New Zealand was mainly on species-level, considerable portions of trait data from North America and Australia were on genus or family-level (Table \ref{tab:tax_coverage}).
-Assigned traits on family-level might not reflect the real trait diversity within a taxon, for example for Chironomidae (\cite{serra_synthesising_2016}).
-However, species identification can be complicated and time-consuming (\cite{marshall_taxonomic_2006, resh_which_2008}), and therefore trait information on family-level has been widely used, e.g.
-in bioassessment (\cite{beketov_spear_2009}).
+While trait information from Europe and New Zealand was mainly at species-level, considerable portions of trait data from North America and Australia were at genus or family-level.
+Assigned traits at family-level may not reflect the real trait diversity within a taxon, for example for the large, ecologically diverse family Chironomidae (\cite{serra_synthesising_2016}).
+However, species-level identification can be complicated, time-consuming and expensive (\cite{marshall_taxonomic_2006, resh_which_2008}).
+Consequently, trait information at family-level has been widely used by freshwater ecologists, for example in bioassessment (\cite{beketov_spear_2009}).
 
@@
 
-When trait values are only available at species-level and observational data are on less precise taxonomic levels various trait aggregation methods have been used by researchers.
-We aggregated traits from an Australian and North American trait dataset to family-level using 5 different aggregation methods and compared the results to traits assigned at family-level for these regions.
+When trait values are only available at species-level and observational data are at less precise taxonomic levels, various trait aggregation methods have been used by researchers.
+We aggregated traits from an Australian and a North American trait dataset to family-level using 5 different aggregation methods and compared the results to traits assigned at family-level for these regions.
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
-Aggregation of trait information on species or genus-level to a point estimate on family-level suggests a precision that is not necessarily present, especially not for traits with a high variability or if trait information on species-level is missing.
-Some traits can vary strongly on more precise taxonomic levels than the family-level.
+Aggregation of trait information at species or genus-level to a point estimate at family-level suggests a precision that is not necessarily present, especially not for traits with a high variability or if trait information at species-level is missing.
+Some traits can vary strongly at more precise taxonomic levels than the family-level.
 For example, \citet{monaghan_improving_2013} found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction.
-Furthermore, studies focusing on the lability of traits, i.e.
+Further, studies focusing on the lability of traits, i.e.
 how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g.
 thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable (\cite{poff_functional_2006, wilkes_traitbased_2020}).
-However, if trait aggregation is necessary our study can give guidance, under which circumstances the choice of aggregation method might be important.
+If trait aggregation is necessary, however, our study can give guidance, under which circumstances the choice of aggregation method may be important.
 The 5 aggregation methods we tested use either the mean or the median and different weightings.
-Our results indicated that 1) the median aggregation methods compared to mean aggregation methods were often closer to the assigned traits at family-level and 2) that the different weightings tested exerted a minor impact on the aggregated trait affinities.
-We obtained for both datasets more differing cases for mean aggregation methods, irrespective of the weighting.
+Our results indicated that 1) the median aggregation methods compared to mean aggregation methods were often closer to the assigned traits at family-level and 2) the different weightings tested exerted a minor impact on the aggregated trait affinities.
+We obtained for both datasets more strongly differing cases for mean aggregation methods, irrespective of the weighting.
 In the Australian dataset, the amount of differing cases was slightly higher for the mean aggregation methods (23 \%) than for median aggregation methods (16 to 18 \% differing cases).
@@
 There, the mean absolute differences for the median aggregations were twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31).
-The differences can be explained by the binary coding used in the North American trait dataset and in the assigned traits.
+These differences can be explained by the binary coding used in the North American trait dataset and in the assigned traits.
 As a result, traits have affinities of either 1 or 0.
-Therefore, traits of a particular grouping feature have in most cases a higher difference in trait affinities to each other than if they were fuzzy coded.
-Using the median to aggregate binary coded taxa will often result in a value of 0 or 1, while using the mean will often result in values between 0 and 1.
+Therefore, traits of a particular grouping feature showed in most cases a higher difference in trait affinities to each other than if they were fuzzy coded.
+Using the median to aggregate binary coded taxa often resulted in a value of 0 or 1, while using the mean yielded values between 0 and 1.
 Thus, using the median led for the North American dataset either to agreement with the assigned traits or to higher differences compared to the mean aggregation methods.
@@
 The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species entries.
-From the taxa that were compared from the North American trait dataset, 14 \% were resolved on family-level and 62 \% were resolved on genus-level.
-52 \% had 5 or less genera and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
-In the Australian dataset, 21 \% of the taxa were resolved on family-level, 40 \% were resolved on genus level, and 39 \% were resolved on species-level.
-68 \% of the taxa contain 5 or less genera and 40 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}).
-Hence, these results might change when more trait information on species-level becomes available.
+Of the taxa that were compared from the North American trait dataset, 14 \% were identified at family and 62 \% at genus-level, 52 \% comprised 5 or fewer genera, and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
+In the Australian dataset, 21 \% of the compared taxa were identified at family, 40 \% at genus, and 39 \% at species-level, 68 \% of the taxa contained 5 or fewer genera, and 40 \% just one genus (Figure \ref{fig:tax_hierarchy_AUS}).
+Hence, these results could change when more trait information at species-level becomes available.
 
@@
 We are not aware of other studies that compared trait-environment relationships using harmonised and non harmonised data.
-The re-analysis yielded only slightly different results compared to the original study, i.e.
-some of the traits that responded in the original analysis did not respond in the re-analysis.
-Those traits that were non-responsive in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (Mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see method section), namely feeding mode shredder, respiration gills, and life cycle duration traits.
+The re-analysis of the data on salinisation effects on biological traits from \citet{szocs_effects_2014} yielded only slightly different results compared to the original study, i.e.
+some of the traits that had responded in the original analysis did not respond in the re-analysis.
+These non-responsive traits were those closest to the criterion that defined when a trait was associated with either high or low salinity (Mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see method section), namely feeding mode shredder, respiration gills, and life cycle duration traits.
 Feeding mode shredder was the only trait that was non-responsive when using harmonised (but not aggregated) as well as when using aggregated data.
-One reason for the non-responsiveness of shredders in the re-analysis was likely the harmonisation procedure.
-During harmonisation the trait shredder has been amalgamated based on three traits (miner, xylophagus, and shredder).
-As a result, the trait affinities in the original data have a higher mean and standard deviation than in the aggregated and harmonised data (Table \ref{tab:SI_resp_traits_summary_stats}) suggesting that the signal in the original data has presumably been weakened by the harmonisation.
-This might be the reason that shredders showed a less strong reaction to the salinity gradient in the re-analysis.
-These findings show that if harmonisation is necessary, harmonised and non-harmonised data, if available, should be compared and possible averaging effects should be considered in further analysis.
-The fact that the family-level aggregated traits used in the re-analysis showed only slightly different results compared to the original analysis is in line with the findings of others that family-level traits can be sensitive enough to detect environmental impacts (\cite{beketov_spear_2009}).
+This result was likely due to the harmonisation procedure, when this trait was amalgamated based on three traits (miner, xylophagus, and shredder).
+Consequently, the trait affinities in the original data had a higher mean and standard deviation than in the aggregated and harmonised data (Table \ref{tab:SI_resp_traits_summary_stats}), suggesting that the signal in the original data was weakened by the harmonisation.
+%This might be the reason that shredders showed a less strong reaction to the salinity gradient in the re-analysis.
+-> Kicked out by CM
+These findings show that if harmonisation is necessary, harmonised and non-harmonised data, if available, should be compared and possible averaging effects should be considered in further analyses.
+The fact that the family-level aggregated traits used in the re-analysis showed similar results compared to the original analysis agrees with previous findings that family-level traits can be sensitive enough to detect environmental impacts (\cite{beketov_spear_2009}).
 % Cite another paper that uses family-level trait data
@@
 
-Although comprehensive invertebrate trait databases have been developed for several regions, data synthesis is difficult due to discrepancies in trait definitions.
+Although comprehensive freshwater invertebrate trait databases have been developed for several regions in the past, data synthesis is difficult due to discrepancies in trait definitions.
 By providing an overview of these definition discrepancies we hope to set a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
-A consent on standard terminology and the subsequent development of ontologies are the next steps to facilitate trait-based analysis on large scales.
+A consent on standard terminology and the subsequent development of ontologies are the next steps to facilitate trait-based analysis at large geographical scales.
 As our analysis showed, some grouping features might need to be re-classified to fit into such a standardised terminology.
-We could show that trait affinities resulting from fuzzy coding and binary coding can be used together, but a uniform coding of traits is another problem that should be addressed in the course of trait standardisation.
+We could show that trait affinities resulting from fuzzy coding and binary coding can be used together, but a uniform coding of traits is another problem that should be addressed during trait standardisation.
 
 With the increasing use of computer vision in ecology, both species identification and trait quantification could be automated (\cite{hoye_deep_2020, milosevic_application_2020}).
-This development might result in more observational data and trait data on species-level in the future.
-However, if traits need to be aggregated we showed that trait aggregation is often in conclusion with expert assignments, specifically aggregation approaches using the median.
-Which aggregation method the objectively better measure is cannot be answered, but when trait aggregation is necessary 1) median aggregation seems to be favourable, 2) highly variable traits and taxa where a few genera have a high number of species should be treated carefully, 3) coding of traits should be considered, and 4) weighting trait information based on the taxa present in the used trait database does not seem to have much influence.
-No matter which aggregation approach is chosen, for future studies in which researchers must aggregate traits, a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
+This development might result in more observational data and trait data at species-level in the future.
+However, if traits need to be aggregated we showed that trait aggregation is often in agreement with expert assignments, especially aggregation approaches using the median.
+Ultimately, the question which aggregation method is the objectively best measure cannot be answered.
+Nevertheless, we make the following recommendations for situations when trait aggregation is necessary 1) median aggregation seems to be favourable, 2) highly variable traits and taxa where a few genera have a high number of species should be treated carefully, 3) coding of traits should be considered, 4) weighting trait information based on the taxa present in the database used does not seem to have much influence and 5) a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
+% OLD: No matter which aggregation approach is chosen, for future studies in which researchers must aggregate traits,....
 

### 2021-01-25 Paper/Draft_harmonization_paper.tex
25.01.: Minor comments added from ASK

@@
 1.
-Use of invertebrate traits rather than species composition is expected  expected to facilitate large-scale comparisons of community structure and responses to disturbance in freshwater ecology because the same traits can potentially occur everywhere.
+Use of invertebrate traits rather than species composition is expected to facilitate large-scale comparisons of community structure and responses to disturbance in freshwater ecology because the same traits can potentially occur everywhere.
 % OLD: because of their consistent response to environmental gradients
@@
 The wide availability of invertebrate trait data supports trait-based studies, especially at large scales.
-However, a number of data-related problems hamper the work with trait data.
+However, a number of data-related issues complicate the use of invertebrate traits for ecological studies.
 For example, for freshwater invertebrate traits standardised definitions are lacking, impeding comparisons across regions.
-Moreover, it is uncertain how standardising grouping features from different databases might influence trait-environment relationships.
+Moreover, it is uncertain how harmonising varying trait definitions between databases from different databases might influence trait-environment relationships.
 Another issue is that if the taxonomic resolution of observational taxonomic data is less precise than in trait databases, the traits in databases require aggregation before they can be linked to the observational data.
-% Here: Describe aims of the study or redundant with part 2? Something like this: The aim of our study is to investigate these data-related issues by synthesizing trait data from different databases.
+% Alternative from Co-Authors: Another issue is that we do not know how taxonomic resolution affects the characterization of traits and hence the comparability of different datasets.
+% Another issue is that if aggregation of traits is necessary, i.e.
+when observational taxonomic data is less precise than available trait data, no guidance exists which method under which circumstances can
 
@@
 We describe discrepancies in the definitions of traits used to create freshwater invertebrate trait databases in Europe, North America, New Zealand, and Australia.
-Based on our comparisons of these trait databases, we established 4 novel trait datasets by harmonising 7 commonly used grouping features.
+Based on our comparisons of these trait databases, we established 4 novel trait datasets by harmonising trait definitions of commonly used traits.
 Two of these datasets were used to compare aggregated traits obtained by different aggregation methods with traits assigned by experts at family-level.
-We tested trait aggregation based on the mean and based on the median, each with different weightings.
-Furthermore, we explored the effect of grouping feature harmonisation and trait aggregation by re-analysing data from a case study.
+We compared trait aggregation that were based on the mean and the median respectively, each with different weightings.
+Furthermore, we explored the effect of harmonisation and trait aggregation by re-analysing data from a case study.
 
@@
 Also, the coding to describe traits varied between databases.
-Aggregated and assigned traits based on expert knowledge displayed a good match, especially approaches using the median.
-Grouping feature harmonisation and trait aggregation only slightly changed the results in the re-analysis compared to the original study, although averaging effects can occur due to harmonisation.
+Aggregated and assigned traits based on expert knowledge displayed a good match, especially approaches using the median to aggregate from species to family-level.
+Grouping feature harmonisation and trait aggregation only slightly changed the results in the re-analysis compared to the original study, although averaging effects did occur in some cases because of harmonisation.
 
@@
   \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_chessman.png}
-  \caption{Display of the cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family-level.
+  \caption{Cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family-level.
 Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the Australian dataset for the grouping features feeding mode and body size.
@@
   \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_pyne.png}
-  \caption{Display of the cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family-level.
+  \caption{Cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family-level.
 Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
@@
 Upstream sites were characterised by univoltine taxa with a short life cycle duration that lay their eggs in an aquatic environment (aquatic eggs).
-The trait aquatic eggs of the harmonised grouping feature oviposition has been derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonisation}).
+The trait aquatic eggs of the harmonised grouping feature oviposition was derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonisation}).
 The traits shredder and gill respiration did not characterise sites with high salinisation.
@@
 for studying community trait responses to environmental gradients worldwide.
-Our attempt at harmonising invertebrate trait information from trait databases of different regions showed that grouping feature harmonisation was labour-intensive because grouping features are differentiated differently into traits between trait databases and various codings are used to describe traits.
-In addition, the same traits are sometimes defined differently in the investigated databases, requiring expert knowledge to reclassify these traits (e.g.
+Our attempt at harmonising invertebrate trait information from trait databases of different regions showed that harmonisation was labour-intensive because grouping features are differentiated differently into traits and various codings are used to describe traits in the various databases.
+In addition, the same traits are sometimes defined differently, requiring expert knowledge to reclassify these traits (e.g.
 the trait piercer in the Tachet database).
@@
 When trait values are only available at species-level and observational data are at less precise taxonomic levels, various trait aggregation methods have been used by researchers.
-We aggregated traits from an Australian and a North American trait dataset to family-level using 5 different aggregation methods and compared the results to traits assigned at family-level for these regions.
+We aggregated traits from an Australian and a North American trait dataset to family-level using 5 different aggregation methods and compared the results to traits originally assigned at family-level for these regions.
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
@@
 In the Australian dataset, the amount of differing cases was slightly higher for the mean aggregation methods (23 \%) than for median aggregation methods (16 to 18 \% differing cases).
-In the North American dataset, mean aggregation methods yielded in 47 \% of the cases a difference to the assigned traits, much higher in comparison to the median aggregation methods (between 15 and 18 \%).
+In the North American dataset, mean aggregation methods yielded 47 \% cases being different to the assigned traits, a value much higher in comparison to the median aggregation methods (between 15 and 18 \%).
 When differences occurred between median aggregation methods and assigned traits, these differences were greater compared to the mean aggregation methods, particularly for the North American dataset.
 There, the mean absolute differences for the median aggregations were twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31).
-These differences can be explained by the binary coding used in the North American trait dataset and in the assigned traits.
+These differences can be explained by the binary coding used in the North American trait dataset and by the assigned traits.
 As a result, traits have affinities of either 1 or 0.
@@
 Also, the distributions of absolute trait affinity differences to assigned traits were relatively similar for the mean aggregation methods and the median aggregation methods, respectively.
-The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species entries.
+The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species.
 Of the taxa that were compared from the North American trait dataset, 14 \% were identified at family and 62 \% at genus-level, 52 \% comprised 5 or fewer genera, and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
@@
 some of the traits that had responded in the original analysis did not respond in the re-analysis.
-These non-responsive traits were those closest to the criterion that defined when a trait was associated with either high or low salinity (Mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see method section), namely feeding mode shredder, respiration gills, and life cycle duration traits.
+These non-responsive traits were those closest to the criterion that defined when a trait was associated with either higher or lower salinity (Mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see method section), namely feeding mode shredder, respiration gills, and life cycle duration traits.
 Feeding mode shredder was the only trait that was non-responsive when using harmonised (but not aggregated) as well as when using aggregated data.

### 2021-01-26 Paper/Draft_harmonization_paper.tex

@@
 For example, for freshwater invertebrate traits standardised definitions are lacking, impeding comparisons across regions.
-Moreover, it is uncertain how harmonising varying trait definitions between databases from different databases might influence trait-environment relationships.
-Another issue is that if the taxonomic resolution of observational taxonomic data is less precise than in trait databases, the traits in databases require aggregation before they can be linked to the observational data.
+Moreover, it is uncertain how harmonising varying trait definitions between databases might influence trait-environment relationships.
+Another issue is that if aggregation of traits is necessary, i.e.
+when observational taxonomic data is less precise than available trait data, no guidance exists which method under which circumstances can
 % Alternative from Co-Authors: Another issue is that we do not know how taxonomic resolution affects the characterization of traits and hence the comparability of different datasets.
-% Another issue is that if aggregation of traits is necessary, i.e.
-when observational taxonomic data is less precise than available trait data, no guidance exists which method under which circumstances can
 
@@
 3.
-Between the trait databases, grouping features differed in terms of their classification into traits and their scope leading to discrepancies how traits are defined.
+Between the trait databases, grouping features differed in terms of their classification into traits and their focus leading to discrepancies how traits are defined.
 Also, the coding to describe traits varied between databases.
 Aggregated and assigned traits based on expert knowledge displayed a good match, especially approaches using the median to aggregate from species to family-level.
-Grouping feature harmonisation and trait aggregation only slightly changed the results in the re-analysis compared to the original study, although averaging effects did occur in some cases because of harmonisation.
+Harmonisation and trait aggregation only slightly changed the results in the re-analysis compared to the original study, although averaging effects did occur in some cases because of harmonisation.
 
@@
 Traits are assumed to be adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and represent direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
-Besides providing more mechanistic-based expressions of species-environment relationships, trait-based approaches might be suitable for large-scale analysis because the variability in trait responses is lower than in taxonomic responses (\cite{baird_toward_2011, bonada_taxonomic_2007}).
+Besides providing more mechanistic-based expressions of species-environment relationships, trait-based approaches might be suitable for large-scale analysis because trait responses are less constrained by biogeographic boundaries and taxon distributional areas (\cite{baird_toward_2011, bonada_taxonomic_2007}).
 
 Traits of individual freshwater invertebrate are difficult to determine because - unlike plant traits - they are often difficult to measure directly.
-For example, to describe feeding habits requires that we understand both mouthpart morphology and the specific food that is consumed, and the organisms function within its community (\cite{moog_comprehensive_nodate}).
+For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behavior, and the specific food that is consumed(\cite{moog_comprehensive_nodate}).
 Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
-by relating macroinvertebrate trait composition to environmental factors and as trait metrics in biomonitoring (\cite{bhowmik_large_2015, menezes_beyond_2010, poff_developing_2010, szocs_effects_2014}).
+by relating macroinvertebrate trait composition to environmental factors (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}).
 
@@
 For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe based on traits from \citet{ussegliopolatera_biological_2000} (typically referred to as the Tachet database), \citet{poff_developing_2010} characterized trait composition across sites in the Western USA based on traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} used trait definitions from \citet{poff_functional_2006} and \citet{schafer_trait_2011} to test for effects of salinity on invertebrate traits across different sites in South Australia.
-Analyses of invertebrate traits that synthesize information on invertebrate grouping features from more than two different continents are rare.
+Analyses that synthesize invertebrate trait information from more than two different continents are rare, but see \citet{brown_functional_2018} and \citet{statzner_reproductive_1997}.
 
@@
 % Ben suggest here: For  example  e.g., predator, shredder, etc. Are traits of the grouping feature ..... and removing predator, shredder, etc. from the sentence above.
-Traits can be described using different codings (binary, fuzzy) that represent the prevalence of a characteristic in an organism.
+Traits can be described using different codings (binary, fuzzy) that represent the expression of a characteristic in an organism.
 
@@
 
-These challenges when working with or synthesizing trait data motivated us to (1) investigate discrepancies in trait definition between trait databases from Europe, North America, Australia, and New Zealand.
+These challenges when working with or synthesizing trait data motivated us to (1) investi<gate discrepancies in trait definition between trait databases from Europe, North America, Australia, and New Zealand.
 As a basis for further evaluating different trait aggregation methods and how harmonising definition discrepancies between grouping features can influence trait-environment relationships, we developed 4 novel invertebrate trait datasets from these existing trait databases by harmonising 7 grouping features.

### 2021-01-26 Paper/Draft_harmonization_paper.tex
26.01: Fixed references error
26.01.: Final fixes before send to Brooke Pt.1

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % From freshwater biology:
@@
 DOI: 10.1177/0022219413479673
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Two of these datasets were used to compare aggregated traits obtained by different aggregation methods with traits assigned by experts at family-level.
-We compared trait aggregation that were based on the mean and the median respectively, each with different weightings.
+We compared trait aggregation methods that use either the mean or the median and different weightings.
 Furthermore, we explored the effect of harmonisation and trait aggregation by re-analysing data from a case study.
@@
 
-We extracted information from 6 trait databases from Europe, North America, Australia, and New Zealand and harmonised 7 grouping features.
+We established in total 4 trait datasets for the regions Europe, North America, Australia, and New Zealand by harmonising 7 grouping features from 6 trait databases.
 Trait information for Europe was obtained from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}) and the Tachet database (\cite{ussegliopolatera_biological_2000}).
-The freshwaterecology.info contains taxa on species-level, while taxa recorded in the Tachet database are on species, genus and family-level.
-Trait information for North America was obtained from \citet{twardochleb_trait_data_2020} and complemented by \citet{vieira_database_nodate}.
+We refer to both databases by their commonly used names (freshwaterecology.info database and Tachet database).
+The freshwaterecology.info database contains taxa on species-level, while taxa recorded in the Tachet database are on species, genus and family-level.
+Trait information for North America was obtained from \citet{twardochleb_freshwater_nodate} and complemented by \citet{vieira_database_nodate}.
+We refer to the former as the CONUS database and the latter as the Vieira database.
 Data on body form for European and North American taxa was based on expert knowledge (\cite{polatera_personal_information_2020}).
 For Australia and New Zealand, we used trait databases from \citet{kefford_integrated_2020} and \citet{Philips_and_Smith_NZ_DB_2018} respectively.
-To increase readability we refer to the databases as well as the datasets we extracted from them by the name of the continent they originate from, except for European databases, which we refer to by their commonly used names (freshwaterecology.info and Tachet database).
+We refer to both as the Australian and New Zealand database.
+To increase readability we refer to the datasets we extracted from the trait databases by the name of the continent they originate from.
 
@@
 \begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-    \textit{a} The trait "bluff (blocky)" occurred in the North America database (Vieira et al.) and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}).
-\\
-    \textit{b} Reflects the different size classifications by the North American trait databases and the other trait databases. \\
+    \textit{a} The trait "bluff (blocky)" occurred in the Vieira database and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}). \\  
+    \textit{b} Reflects the different size classifications by the Vieiera and the CONUS databases and the other trait databases. \\
     \textit{c} The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases (\cite{usseglio-polatera_biomonitoring_2000}).
@@
 
+\subsubsection*{Simulation of varying taxonomic hierarchies}
+
 To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we created three hypothetical examples of different taxonomic hierarchies (scenarios).
@@
 In total every family consisted of 25 species.
-To each scenario a hypothetical grouping feature with 3 traits was assigned.
+To each scenario a hypothetical grouping feature with 3 traits was assigned (denotes as T1, T2, and T3).
 The 25 affinities for each trait were simulated by sampling from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviations (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability.
@@
 
-\subsection*{Comparison of family-level aggregated traits with family-level assigned traits}
+\subsubsection*{Comparison of family-level aggregated traits with family-level assigned traits}
 
@@
 For the North American dataset, we compared aggregated trait affinities with assigned trait affinities on family-level for the grouping features feeding mode, respiration, size, voltinism, and locomotion.
-The assigned trait affinities at family-level are part of the North American database (Twardochleb et al.) and originate from expert knowledge.
+The assigned trait affinities at family-level are part of the CONUS database and originate from expert knowledge.
 Trait information was available for 94 families of which all were present in the North American dataset (total number of cases 1598).
@@
 Definitions of grouping features and traits varied in their level of detail in the investigated trait databases.
-The freshwaterecology.info database, the Tachet database and the North American database (Twardochleb et al.) provided more detailed descriptions of their trait information compared to the North American (Vieira et al.) and New Zealand database.
+The freshwaterecology.info database, the Tachet database and the CONUS database provided more detailed descriptions of their trait information compared to the Vieira database and New Zealand database.
 The Australian trait database (\cite{kefford_integrated_2020}) is a collection of seven specific trait datasets.
@@
 
-The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope.
+The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their focus.
 We provide a summary of discrepancies in trait definitions in the appendix (Table \ref{stab:trait_definitions}).
@@
 The Tachet database defines predators as carvers, engulfers and swallowers.
-By contrast, in the North American (Twardochleb et al.) database predators are defined as engulfers and carnivorous piercers.
+By contrast, in the CONUS database predators are defined as engulfers and carnivorous piercers.
 In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers.
-Furthermore, the scope in the freshwaterecology.info database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition.
+Furthermore, the focus in the freshwaterecology.info database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition.
 Therefore, the freshwaterecology.info database defines e.g.
@@
 Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table \ref{stab:trait_definitions}).
-Locomotion definitions differ also in scope between databases.
-Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the North American (Vieira et al.) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb et al.) database includes not only the way of movement, but also the location of movement.
-Similarly, regarding reproduction traits, databases differ in their scope.
+Locomotion definitions differ also in focus between databases.
+Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the Vieira as how organisms deal with flow, Australia as attachment, and the CONUS database includes not only the way of movement, but also the location of movement.
+Similarly, regarding reproduction traits, databases differ in their focus.
 Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases.
-North America (Vieira et al.) provides information on the oviposition location but not on reproductive behavior.
+The Vieira database provides information on the oviposition location but not on reproductive behavior.
 The Australian database report traits for reproductive behavior but also on oviposition site.
@@
 The freshwaterecology.info and Australian databases use different codings, while the Tachet and the New Zealand database exclusively use fuzzy coding.
-Both North American trait databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
+The Vieira and CONUS databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
 
 \begin{landscape}
-  \begin{longtable}{m{2.9cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
+  \begin{longtable}{m{2.2cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
   \caption{Number of traits per grouping feature and type of coding of the traits for the respective grouping feature per database.}
@@
   \hline
-  \multirow{2}{*}{\specialcell{North America \\ (Twardochleb et al.)}} & 
+  \multirow{2}{*}{\specialcell{CONUS}} & 
   6 & 
@@
   \hline
-  \multirow{2}{*}{\specialcell{North America \\ (Vieira et al.)}} & 
+  \multirow{2}{*}{\specialcell{Vieira}} & 
   8 & 
@@
   \specialcell{binary; \\ continuous; \\ fuzzy $[0 - 3]$} & 
-  fuzzy codes $[0-3]$
+  fuzzy $[0-3]$
   \\
@@
   \begin{minipage}{\linewidth}\small
-      \textit{a} Some of the traits were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
+      \textit{a} Some of the feeding mode traits used in the Australian database were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
       \newline
@@
 Each trait aggregation method yielded one aggregated affinity for every simulated dataset, in total 15000 comparisons ($100$ replicates $*$ 5 levels of trait variability $* 10$ unique comparisons of trait aggregation methods $* 3$ scenarios).
-Overall, differences between the results of the aggregation methods for each simulated dataset increased with increasing trait variability.
-However, in most simulated datasets the different aggregation methods often resulted in similar trait affinities.
+In most simulated datasets the different aggregation methods often resulted in similar trait affinities.
 Only 1.42 \% (213 out of 15.000) of all comparisons showed a difference equal or greater than an absolute trait affinity of 0.1.
@@
 for studying community trait responses to environmental gradients worldwide.
-Our attempt at harmonising invertebrate trait information from trait databases of different regions showed that harmonisation was labour-intensive because grouping features are differentiated differently into traits and various codings are used to describe traits in the various databases.
+Our attempt at harmonising invertebrate trait information from trait databases of different regions showed that harmonisation was labour-intensive because grouping features are resolved differently into traits and various codings are used to describe traits in the various databases.
 In addition, the same traits are sometimes defined differently, requiring expert knowledge to reclassify these traits (e.g.
@@
 Further, studies focusing on the lability of traits, i.e.
-how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g.
+how much traits are constrained by phylogeny, found that traits of ecological preferences (e.g.
 thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable (\cite{poff_functional_2006, wilkes_traitbased_2020}).
@@
 some of the traits that had responded in the original analysis did not respond in the re-analysis.
-These non-responsive traits were those closest to the criterion that defined when a trait was associated with either higher or lower salinity (Mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see method section), namely feeding mode shredder, respiration gills, and life cycle duration traits.
+These non-responsive traits were those closest to the criterion that defined when a trait was associated with either higher or lower salinity, namely feeding mode shredder, respiration gills, and life cycle duration traits.
 Feeding mode shredder was the only trait that was non-responsive when using harmonised (but not aggregated) as well as when using aggregated data.
@@
 Although comprehensive freshwater invertebrate trait databases have been developed for several regions in the past, data synthesis is difficult due to discrepancies in trait definitions.
-By providing an overview of these definition discrepancies we hope to set a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
+By providing an overview of these definition discrepancies we provide a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
 A consent on standard terminology and the subsequent development of ontologies are the next steps to facilitate trait-based analysis at large geographical scales.
@@
 
-With the increasing use of computer vision in ecology, both species identification and trait quantification could be automated (\cite{hoye_deep_2020, milosevic_application_2020}).
-This development might result in more observational data and trait data at species-level in the future.
+As ecological knowledge increases in the future, and with the aid of new  methods such as computer vision for species and trait identification (\cite{hoye_deep_2020}), more observational and trait data at species-level may become available in the future, reducing the need for trait aggregation.
 However, if traits need to be aggregated we showed that trait aggregation is often in agreement with expert assignments, especially aggregation approaches using the median.
 Ultimately, the question which aggregation method is the objectively best measure cannot be answered.
-Nevertheless, we make the following recommendations for situations when trait aggregation is necessary 1) median aggregation seems to be favourable, 2) highly variable traits and taxa where a few genera have a high number of species should be treated carefully, 3) coding of traits should be considered, 4) weighting trait information based on the taxa present in the database used does not seem to have much influence and 5) a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
+Nevertheless, we make the following recommendations for situations when trait aggregation is necessary 1) median aggregation seems to be favourable, 2) highly variable traits and taxa where a few genera have a high number of species should be treated carefully, 3) description of traits (binary, fuzzy) should be considered, 4) weighting trait information based on the taxa present in the database used does not seem to have much influence and 5) a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
 % OLD: No matter which aggregation approach is chosen, for future studies in which researchers must aggregate traits,....

### 2021-01-27 Paper/Draft_harmonization_paper.tex
27.01: Minor fixes before send to Brooke

@@
 Moreover, it is uncertain how harmonising varying trait definitions between databases might influence trait-environment relationships.
-Another issue is that if aggregation of traits is necessary, i.e.
-when observational taxonomic data is less precise than available trait data, no guidance exists which method under which circumstances can
+Another issue is that taxonomic resolution between observational taxonomic data and trait data can differ, making aggregation of traits necessary.
+So far, comparisons of different aggregation approaches to expert assessments are lacking.
 % Alternative from Co-Authors: Another issue is that we do not know how taxonomic resolution affects the characterization of traits and hence the comparability of different datasets.
@@
 We compared trait aggregation methods that use either the mean or the median and different weightings.
+Thereby, we simulated how taxonomic resolution and trait variability can change the result of different aggregation approaches.
 Furthermore, we explored the effect of harmonisation and trait aggregation by re-analysing data from a case study.
 
+% Intial: Between the trait databases, grouping features differed in terms of their classification into traits and their focus leading to discrepancies how traits are defined
 3.
-Between the trait databases, grouping features differed in terms of their classification into traits and their focus leading to discrepancies how traits are defined.
-Also, the coding to describe traits varied between databases.
+We found that between trait databases, trait definitions are often different because varying numbers of traits are used to describe groups of related traits (e.g.
+respiration traits).
+Also the focus to describe groups of related traits varies between databases, e.g.
+for feeding mode some focus on the food source, while others on mouthpart morphology.
+Also, the coding to describe traits (binary, fuzzy) varied between databases.
 Aggregated and assigned traits based on expert knowledge displayed a good match, especially approaches using the median to aggregate from species to family-level.
-Harmonisation and trait aggregation only slightly changed the results in the re-analysis compared to the original study, although averaging effects did occur in some cases because of harmonisation.
+The comparison with the case study showed that harmonisation and trait aggregation only slightly changed results.
 
@@
 However, a lack of standardised terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology (\cite{baird_toward_2011, kissling_towards_2018}).
-Secondly, consistent coding of traits facilitates the compatibility of trait data from different databases.
+Secondly, consistent coding of traits facilitates the comparability of trait data from different databases.
 
@@
 
-However, invertebrate trait databases are heterogeneous regarding the coding they use for their traits (\cite{culp_incorporating_2011}).
+However, invertebrate trait databases are heterogeneous with respect to the coding that is used for traits (\cite{culp_incorporating_2011}).
 For example, in the study from \citet{brown_functional_2018} the authors needed to reclassify traits using expert knowledge given that the individual databases employed different coding approaches (i.e.
@@
 
-These challenges when working with or synthesizing trait data motivated us to (1) investi<gate discrepancies in trait definition between trait databases from Europe, North America, Australia, and New Zealand.
+These challenges when working with or synthesizing trait data motivated us to (1) investigate discrepancies in trait definition between trait databases from Europe, North America, Australia, and New Zealand.
 As a basis for further evaluating different trait aggregation methods and how harmonising definition discrepancies between grouping features can influence trait-environment relationships, we developed 4 novel invertebrate trait datasets from these existing trait databases by harmonising 7 grouping features.
@@
 
-We repeated the analysis of \citet{szocs_effects_2014} who studied the effect of anthropogenic salinization on invertebrates in the River Werra in Germany.
+We repeated the analysis of \citet{szocs_effects_2014} who studied the effect of anthropogenic salinisation on invertebrates in the River Werra in Germany.
 For this re-analysis we used the established harmonised grouping feature dataset for Europe and additionally aggregated traits using the aforementioned aggregation methods.
 
-The River Werra has been subject to effluents from the potash industry since the mid- 20th century and allows to study responses of invertebrates and their trait compositions to salinization (\cite{bathe_biological_2011}).
+The River Werra has been subject to effluents from the potash industry since the mid- 20th century and allows to study responses of invertebrates and their trait compositions to salinisation (\cite{bathe_biological_2011}).
 Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition.
@@
 the coordinates of the tips of the vectors representing the CWM traits in the bi- or triplots.
-Following the original study, we identified traits associated with high or low salinity based on their distance to the ordination axis median using the Mahalanobis distance.
-CWM traits with a Mahalanobis distance greater than the $97.5 \%$ -quantile of the Chi-square distribution (5.02) were regarded as traits responding to either low or high salinity.
+Following the original study, we identified traits associated with higher or lower salinity based on their distance to the ordination axis median using the Mahalanobis distance.
+CWM traits with a Mahalanobis distance greater than the $97.5 \%$ -quantile of the Chi-square distribution (5.02) were regarded as traits responding to either lower or higher salinity.
 For our analysis, we used the same 21 grouping features as in \citet{szocs_effects_2014}.
@@
 We provide a summary of discrepancies in trait definitions in the appendix (Table \ref{stab:trait_definitions}).
-Both, differences in differentiation and scope can lead to discrepancies in trait definitions.
+Both, differences in differentiation and focus can lead to discrepancies in trait definitions.
 For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways.
@@
 
-%BEN: Suggest start with some overall main message.
-The main message I get from Fig 6 is: „The original analysis in Szocs et al.
-(2014) and all agrigration methods produced very similar distributions of RDA species scores (Figure 6).“ I suggest start with this sentence (or something like this), then  draw out any details but only if necessary (i.e.
-do not feel compelled to say more if there is not really much more to say).
-
+Overall, harmonised trait data and all aggregation methods produced similar distributions of RDA species scores (Figures \ref{fig:violin_plot_species_sc}) compared to the original analysis in \citet{szocs_effects_2014}.
 Using harmonised grouping features resulted in less traits that distinguish upstream and downstream sites in comparison to the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
@@
 The trait aquatic eggs of the harmonised grouping feature oviposition was derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonisation}).
-The traits shredder and gill respiration did not characterise sites with high salinisation.
+The traits shredder and gill respiration did not characterise sites with higher salinisation.
 
-Using traits aggregated at family-level from the harmonised dataset also showed results similar to the original analysis, but with fewer traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
+Using traits aggregated at family-level from the harmonised dataset also showed results similar to the original analysis, but with less traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
 The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg}
@@
 
-Although comprehensive freshwater invertebrate trait databases have been developed for several regions in the past, data synthesis is difficult due to discrepancies in trait definitions.
-By providing an overview of these definition discrepancies we provide a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
+Although comprehensive freshwater invertebrate trait databases have been developed for several regions in the past, data synthesis is difficult because of discrepancies in trait definitions.
+By providing an overview of these definition discrepancies we have set a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
 A consent on standard terminology and the subsequent development of ontologies are the next steps to facilitate trait-based analysis at large geographical scales.
@@
 Ultimately, the question which aggregation method is the objectively best measure cannot be answered.
-Nevertheless, we make the following recommendations for situations when trait aggregation is necessary 1) median aggregation seems to be favourable, 2) highly variable traits and taxa where a few genera have a high number of species should be treated carefully, 3) description of traits (binary, fuzzy) should be considered, 4) weighting trait information based on the taxa present in the database used does not seem to have much influence and 5) a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
+Nevertheless, we make the following recommendations for situations when trait aggregation is necessary.
+1) The aggregation method will tend to have little effect except for highly variable traits and taxa where a few genera have a high number of species.
+2) The coding used to describe traits (binary, fuzzy) should be considered, because median and mean aggregations can yield very different results for binary coded traits.
+3) Weighting trait information based on the taxa present in the database used does not seem to have much influence except for families with few genera that have a high number of species.
+4) A measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
 % OLD: No matter which aggregation approach is chosen, for future studies in which researchers must aggregate traits,....

### 2021-01-27 Paper/Results/SI.tex
22.12: Slight changes in SI to avoid merging conflict
27.01: Minor fixes before send to Brooke

@@
 \begin{landscape}
-    \begin{longtable}{m{1.8cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}}
+    \begin{longtable}{m{1.8cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3.2cm}|m{3cm}}
         \caption{Comparison of trait definitions between invertebrate trait databases.
@@
 Hence, differences for reproduction have been described in the paper.
-Body form traits are not different between databases, except that the North America (Vieira et al.) database contains the trait Bluff (blocky) which does not appear in the other databases.}
+Body form traits are not different between databases, except that the Vieira database contains the trait Bluff (blocky) which does not appear in the other databases.}
         \label{stab:trait_definitions}
@@
         \toprule[.1em]
-        Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & \specialcell{North America \\ (Twardochleb et al.)} & 
-        North America (Vieira et al.) & Australia & New Zealand \\
+        Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & CONUS & Vieira & Australia & New Zealand \\
         \toprule[.1em]
@@
     \centering
-    \caption{Mean, median and standard deviation of trait affinities that were responsive to the salinity gradient in the original study but not when re-analysis with the harmonized dataset trait dataset.}
+    \caption{Mean, median and standard deviation of the affinities of traits that were responsive to the salinity gradient in the original study but not in the re-analysis using the harmonised European trait dataset.}
     \label{tab:SI_resp_traits_summary_stats}
-    \begin{tabular}{llccc}
+    \begin{tabular}{llccc|c}
     \toprule[.1em]
-    Dataset & Trait & Mean & Median & SD \\ 
+    Type & Trait & Mean & Median & SD & Responsive? \\ 
     \toprule[.1em]
-    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 \\ 
-      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 \\ 
-      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 \\ 
-      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 \\ 
-      Weighted & Shredder & 0.19 & 0.14 & 0.22 \\ 
-      Harmonized; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 \\ 
-      Original & Shredder & 0.25 & 0.14 & 0.32 \\ 
-      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 \\ 
-      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 \\ 
-      Direct\_median & Gills & 0.30 & 0.30 & 0.32 \\ 
-      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 \\ 
-      Weighted & Gills & 0.30 & 0.30 & 0.32 \\ 
-      Harmonized; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 \\ 
-      Original & Gills & 0.28 & 0.00 & 0.33 \\ 
-      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 \\ 
-      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 \\ 
-      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 \\ 
-      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
-      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
-      Harmonized; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
-      Original & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
-      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 \\ 
-      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 \\ 
-      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 \\ 
-      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
-      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
-      Harmonized; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
-      Original & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
+    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 & No \\ 
+      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 & No\\ 
+      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 & No\\ 
+      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 & No\\ 
+      Weighted & Shredder & 0.19 & 0.14 & 0.22 & No \\ 
+      Harmonised; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 & No \\ 
+      Original & Shredder & 0.25 & 0.14 & 0.32 & Yes\\ 
+      \midrule
+      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 & Yes\\ 
+      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 & Yes\\ 
+      Direct\_median & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
+      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
+      Weighted & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
+      Harmonised; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 & No \\ 
+      Original & Gills & 0.28 & 0.00 & 0.33 & Yes \\ 
+      \midrule
+      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 & No \\ 
+      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 & No \\ 
+      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 & Yes \\ 
+      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 & Yes \\ 
+      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 & Yes\\ 
+      Harmonised; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 & Yes \\ 
+      Original & Short life cycle & 0.64 & 0.75 & 0.40 & Yes \\ 
+      \midrule
+      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 & No \\ 
+      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 & No \\
+      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 & Yes\\ 
+      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 & Yes \\ 
+      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 & Yes \\ 
+      Harmonised; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 & Yes \\ 
+      Original & Long life cylce & 0.36 & 0.25 & 0.40 & Yes\\ 
     \bottomrule

### 2021-01-27 Paper/Draft_harmonization_paper.tex
27.01.: Final edits upon sending to editor

@@
 
-% Intial: Between the trait databases, grouping features differed in terms of their classification into traits and their focus leading to discrepancies how traits are defined
+% Initial: Between the trait databases, grouping features differed in terms of their classification into traits and their focus leading to discrepancies how traits are defined
 3.
@@
 Traits of individual freshwater invertebrate are difficult to determine because - unlike plant traits - they are often difficult to measure directly.
-For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behavior, and the specific food that is consumed(\cite{moog_comprehensive_nodate}).
+For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behaviour, and the specific food that is consumed (\cite{moog_comprehensive_nodate}).
 Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
@@
 
+\newpage
+
 \subsubsection*{Comparison of family-level aggregated traits with family-level assigned traits}
@@
 Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases.
-The Vieira database provides information on the oviposition location but not on reproductive behavior.
-The Australian database report traits for reproductive behavior but also on oviposition site.
+The Vieira database provides information on the oviposition location but not on reproductive behaviour.
+The Australian database report traits for reproductive behaviour but also on oviposition site.
 The New Zealand database distinguishes three grouping features related to reproduction: reproductive technique, oviposition site (e.g.
@@
 
-\subsection*{Differences in trait affinities obtained by trait aggregation methods compared to traits assigned at family-level}
+\subsection*{Comparison of family-level aggregated traits with family-level assigned traits}
 \label{sec:diff_trait_agg_chessman}
@@
 Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
-For more details see Figure \ref{fig:diff_aggr_traits_chessman}}
+For more details see Figure \ref{fig:diff_aggr_traits_chessman}.}
   \label{fig:diff_aggr_traits_pyne}
@@
 
-\subsection*{Re-analysis of Szöcs et al. using harmonised and aggregated grouping features}
+\subsection*{Effects of harmonisation and trait aggregation on trait-environment relationships}
 
@@
 The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
-Only traits with a mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
+Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
 For better comparability, species scores of the original analysis were multiplied by -1.}

### 2021-02-08 Paper/Draft_harmonization_paper.tex
08.02: First part edits from Brooke

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Tackling discrepancies in freshwater invertebrate trait databases and taxonomic resolution: Harmonising across continents and trait aggregation}
+\title{Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
 \author{}%Stefan Kunz 
@@
 1.
-Use of invertebrate traits rather than species composition is expected to facilitate large-scale comparisons of community structure and responses to disturbance in freshwater ecology because the same traits can potentially occur everywhere.
-% OLD: because of their consistent response to environmental gradients
+Use of invertebrate traits rather than species composition may facilitate large-scale comparisons of community structure and responses to disturbance in freshwater ecology because the same traits can potentially occur everywhere.
 In recent years, comprehensive invertebrate trait databases have been established at different scales (e.g.
@@
 However, a number of data-related issues complicate the use of invertebrate traits for ecological studies.
-For example, for freshwater invertebrate traits standardised definitions are lacking, impeding comparisons across regions.
-Moreover, it is uncertain how harmonising varying trait definitions between databases might influence trait-environment relationships.
-Another issue is that taxonomic resolution between observational taxonomic data and trait data can differ, making aggregation of traits necessary.
-So far, comparisons of different aggregation approaches to expert assessments are lacking.
-% Alternative from Co-Authors: Another issue is that we do not know how taxonomic resolution affects the characterization of traits and hence the comparability of different datasets.
+For example, standardised definitions for for freshwater invertebrate traits are lacking, which impedes comparisons across regions.
+Moreover, it is uncertain how harmonising varying trait definitions among databases might influence identification of trait-environment relationships.
+In addition, is that taxonomic resolution between observational taxonomic data and trait data can differ, making aggregation of traits necessary.
+At present, it is unknown how different trait aggregation approaches compare with expert-assigned trait affinities.
+In this study we aimed to identify discrepancies in trait definitions across freshwater invertebrate databases and to compare trait aggregation methods to identify how taxonomic hierarchy structure and trait variability influence results from different aggregation approaches.
 
@@
 We describe discrepancies in the definitions of traits used to create freshwater invertebrate trait databases in Europe, North America, New Zealand, and Australia.
-Based on our comparisons of these trait databases, we established 4 novel trait datasets by harmonising trait definitions of commonly used traits.
-Two of these datasets were used to compare aggregated traits obtained by different aggregation methods with traits assigned by experts at family-level.
-We compared trait aggregation methods that use either the mean or the median and different weightings.
-Thereby, we simulated how taxonomic resolution and trait variability can change the result of different aggregation approaches.
-Furthermore, we explored the effect of harmonisation and trait aggregation by re-analysing data from a case study.
+Based on our comparisons of these trait databases, we established four novel trait datasets by harmonising trait definitions of commonly used traits.
+Next, we used two of these datasets to compare aggregated traits obtained by different aggregation methods with traits assigned by experts, both at the family level.
+The trait aggregation methods we compared used either the mean or the median and different weightings.
+%Thereby, we simulated how taxonomic resolution and trait variability can change the result of different aggregation approaches.
+We further explored the effects of harmonisation and trait aggregation by re-analysing data from a case study.
 
-% Initial: Between the trait databases, grouping features differed in terms of their classification into traits and their focus leading to discrepancies how traits are defined
 3.
-We found that between trait databases, trait definitions are often different because varying numbers of traits are used to describe groups of related traits (e.g.
-respiration traits).
-Also the focus to describe groups of related traits varies between databases, e.g.
-for feeding mode some focus on the food source, while others on mouthpart morphology.
-Also, the coding to describe traits (binary, fuzzy) varied between databases.
-Aggregated and assigned traits based on expert knowledge displayed a good match, especially approaches using the median to aggregate from species to family-level.
-The comparison with the case study showed that harmonisation and trait aggregation only slightly changed results.
+We found that among trait databases, trait definitions often differed because varying numbers of traits were used to describe groups of related traits (e.g., respiration traits) and the focus of descriptions for groups of related traits also varied (e.g., for feeding mode some databases focused on the food source, whereas others focused on mouthpart morphology).
+The coding to describe traits (binary, fuzzy) also varied among databases.
+Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially from approaches using the median, and that trait coding method, uneven taxonomic hierarchical structure, and high trait variability can influence aggregated trait affinities.
+We further showed that harmonised and aggregated data performed similarly to observational data in identifying trait–environment relationships.
 
@@
 By outlining discrepancies in trait definitions we hope to motivate the development of standardised terminology for invertebrate traits.
-When trait aggregation is needed, our results provide guidance under which circumstances the choice of a trait aggregation method becomes important.
+Our results also illustrate the usefulness of harmonised datasets for ecological study and provide guidance for the circumstances under which the choice of trait aggregation method is important.
 
@@
 
-Explaining and predicting how communities are shaped by environmental factors is one of the main goals of ecology.
+Explaining and predicting how communities are shaped by environmental factors is a primary main goal of ecology.
 Species traits are measurable properties of an organism (\cite{mcgill_rebuilding_2006}), and comparing communities based on the traits possessed by species may facilitate testing of a range of ecological hypotheses (\cite{heino_jani_macroecological_2013}).
-Traits are assumed to be adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and represent direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
-Besides providing more mechanistic-based expressions of species-environment relationships, trait-based approaches might be suitable for large-scale analysis because trait responses are less constrained by biogeographic boundaries and taxon distributional areas (\cite{baird_toward_2011, bonada_taxonomic_2007}).
+Traits are assumed to be adaptations (e.g., physiological, behavioural) of organisms to their environment and to indicate direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
+In addition to providing local-scale mechanistic-based expressions of species-environment relationships, trait-based approaches might be suitable for large-scale analyses because trait responses are less constrained by biogeographic boundaries and taxon distributional areas than taxonomic responses (\cite{baird_toward_2011, bonada_taxonomic_2007}).
 
-Traits of individual freshwater invertebrate are difficult to determine because - unlike plant traits - they are often difficult to measure directly.
-For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behaviour, and the specific food that is consumed (\cite{moog_comprehensive_nodate}).
-Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
+Invertebrate traits have been increasingly used in freshwater ecology, e.g.
 by relating macroinvertebrate trait composition to environmental factors (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}).
-
-In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases for various continents (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate}).
-The availability of invertebrate trait data from different continents arguably enables comparisons of trait variation and testing if variation in trait structure is consistently related to environmental factors across both small and large spatial extents.
+In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases, which typically include data for a single region or continent (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate}).
+The availability of invertebrate trait data from different continents enables comparisons of regional trait variation and allows for testing the consistency of trait structure–environmental factor relationships across both small and large spatial extents.
 To date, such analyses have been carried out mostly within continents, using information from one or two trait databases.
@@
 
-% Ben suggests: 
-% Need something here like: One challenge in comparing traits of freshwater invertebrates across many continents are difference in the recording of trait information in the various continental trait databases.
-For example, ......,
-
+The heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents.
+There are several challenges presented by using invertebrate trait data from multiple established databases in ecological studies.
+One such challenge is inconsistency in terminology.
 In this study, we follow the terminology proposed by \citet{schmera_proposed_2015}, where a grouping feature is defined as a general property (e.g.
 feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species".
-Thus, we use the term grouping feature in place of which many studies use the term "trait", and the term trait instead of "trait state", "modality" or "trait category".
+Thus, we use the term grouping feature in place of the term trait, and the term trait instead of trait state, modality or trait category.
 % Ben suggest here: For  example  e.g., predator, shredder, etc. Are traits of the grouping feature ..... and removing predator, shredder, etc. from the sentence above.
-Traits can be described using different codings (binary, fuzzy) that represent the expression of a characteristic in an organism.
 
-To our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
-We suspect that the heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents.
-To harmonize grouping features from different regions, first commonly accepted and unambiguous trait definitions are required (\cite{schneider_towards_2019}).
-In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonised using standardised terminology.
-However, a lack of standardised terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology (\cite{baird_toward_2011, kissling_towards_2018}).
-Secondly, consistent coding of traits facilitates the comparability of trait data from different databases.
+Another challenge to using data from multiple continents is that invertebrate trait databases include different grouping features and related traits.
+To harmonize grouping features from different regions, or to structure them in such a way as to facilitate cross-database comparison, commonly accepted and unambiguous trait definitions are required (\cite{schneider_towards_2019}).
+Ideally, the same traits and grouping features would be reported across databases or standardised terminology would exist to easily harmonise them; however, there is a lack of standardised terminology of trait definitions and poor metadata quality in many trait databases, making grouping-feature harmonisation difficult (\cite{baird_toward_2011, kissling_towards_2018}).
+To our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and invertebrate assemblages.
 
-Traits can be described in a binary fashion, or with multiple categories, ignoring uncertainty in how traits are expressed in any particular organism (e.g.
-adult terrestrial stage, presence of gills) or continuous (e.g.
-tolerance of pollution, body size).
-One approach for dealing with uncertainty is the use of fuzzy coding, where the traits are assigned probabilistic values.
-Fuzzy codes are used to account for plasticity in traits, variability in traits within taxonomic groups above species, and incomplete knowledge and are usually converted to proportions.
-In this study we denote the probabilistic values (0-1) of traits as affinities or affinity scores.
+A third challenge to comparing across invertebrate trait databases is inconsistent coding of trait data (\cite{culp_incorporating_2011}), or assigning affinities (aka affinity scores).
+Traits of individual freshwater invertebrates can be difficult to quantify because, unlike plant traits, they are often difficult to measure directly.
+For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behaviour, and specific food sources (\cite{moog_comprehensive_nodate}).
+Some traits can be described as binary or categorical, which ignores uncertainty in how traits are expressed in any particular organism (e.g., adult terrestrial stage, presence of gills).
+Other traits are better suited to being described as continuous (e.g., tolerance of pollution, body size).
+One approach for dealing with uncertainty is the use of fuzzy coding, where traits are assigned probabilistic values.
+Fuzzy codes, which are usually converted to proportions, are used to account for plasticity in traits, variability in traits within taxonomic groups above the species level, and incomplete knowledge.
+A challenge is presented by the use of different types of coding for trait affinities in different databases.
+For example, in the study from \citet{brown_functional_2018} the authors needed to reclassify trait affinities because the individual databases employed different coding approaches (i.e., European and New Zealand databases used fuzzy coding, North American database used binary coding).
 
-However, invertebrate trait databases are heterogeneous with respect to the coding that is used for traits (\cite{culp_incorporating_2011}).
-For example, in the study from \citet{brown_functional_2018} the authors needed to reclassify traits using expert knowledge given that the individual databases employed different coding approaches (i.e.
-European and New Zealand databases fuzzy coding, North American database binary coding).
-Databases with standardised and unambiguous traits and a consistent coding of traits would minimize the data processing effort.
-Discrepancies in the taxonomic resolutions (e.g.
-species, genus or family) when linking observational taxonomic data to trait databases represents another challenge.
-When observations are at a more precise taxonomic level than data available in the trait databases (e.g.
-observations at species-level, trait data at genus-level) trait information of the less precise taxonomic level is often assigned (e.g.
+Finally, discrepancies in the taxonomic resolutions (e.g., species, genus, or family) when comparing among trait databases, or when linking observational taxonomic data to trait databases, presents another challenge.
+When observations or data in one trait database are at a more precise taxonomic level than other data (e.g.
+observations at species-level and trait data at genus-level) trait information of the less precise taxonomic level is often assigned (e.g.
 \cite{szocs_effects_2014, vos_taxonomic_2017}).
-Conversely, if trait information is only available at more precise taxonomic levels than the observed taxa, traits are aggregated to a less precise taxonomic level (e.g.
+Conversely, if trait information is only available at more precise taxonomic levels than observed taxa, traits are aggregated to a less precise taxonomic level (e.g.
 \cite{aspin_extreme_2019, piliere_a._f._h._importance_2016, poff_functional_2006, szocs_effects_2014}).
-To data, studies have used different methods of trait aggregation, e.g.
-the mean (\cite{magliozzi_functional_2019}), median (\cite{szocs_effects_2014}) or the mode (\cite{piliere_a._f._h._importance_2016}).
-Studies on how and to which extent different trait aggregation methods influence trait-based analysis are missing.
-However, related knowledge would inform future studies regarding the choice of the aggregation method.
+To date, studies have used different methods of trait aggregation, e.g.
+the mean (\cite{magliozzi_functional_2019}), median (\cite{szocs_effects_2014}) or mode (\cite{piliere_a._f._h._importance_2016}), but studies on how and to what extent different trait aggregation methods influence trait-based analyses are missing.
+%However, related knowledge would inform future studies regarding the choice of the aggregation method.
 
-These challenges when working with or synthesizing trait data motivated us to (1) investigate discrepancies in trait definition between trait databases from Europe, North America, Australia, and New Zealand.
-As a basis for further evaluating different trait aggregation methods and how harmonising definition discrepancies between grouping features can influence trait-environment relationships, we developed 4 novel invertebrate trait datasets from these existing trait databases by harmonising 7 grouping features.
-(2) We then evaluated different trait aggregation methods by comparing aggregated traits with traits assigned by experts at family-level for two of the established trait datasets.
-(3) Finally, we re-analysed data from a study of salinisation effects on biological traits (\cite{szocs_effects_2014}) using data from the newly established harmonised European trait dataset and aggregated traits.
-By comparing the re-analysis's findings with those of \citet{szocs_effects_2014}, we investigated how harmonising and aggregating trait data can modify the outcome of trait-environment relationships.
+These challenges when working with or synthesizing trait data motivated us to assess the characteristics and comparability of freshwater invertebrate trait data contained in disparate databases.
+We aimed to explore methods of improving the comparability of trait data across databases, despite differences in trait definitions and the taxonomic level of data in three ways: (1) by investigating and describing discrepancies in trait definitions between trait databases from Europe, North America, Australia, and New Zealand; (2) by harmonising trait definitions across databases to provide consistent trait grouping features for comparison across geographic locations; and (3) by comparing the influence of different trait aggregation methods and grouping-feature harmonisation on the identification of trait–environment relationships.
 
@@
 
+To address our study objectives, we took a multi-prong approach to describing, combining, and assessing multiple sources of freshwater invertebrate data that differed in trait grouping-feature definitions and taxonomic resolution.
+%Version from Brooke: As a basis for evaluating the comparability of freshwater invertebrate databases, we developed four novel invertebrate trait datasets by harmonising seven grouping features from existing trait databases.
+We then evaluated the influence of different...
+Identified trait definitions discrepancies served as a starting point to develop four novel invertebrate trait datasets by harmonising seven grouping features from existing trait databases.
+The harmonised trait datasets were used to evaluate the influence of different trait aggregation approaches on the identification of trait–environment relationships, our third study objective, in two ways by (1) comparing family-level aggregated trait affinities with family-level trait affinities assigned by experts for two of the established trait datasets where such data were available and (2) comparing the influence of taxonomic hierarchy and trait variability on the outcomes of the different trait aggregation approaches for simulated data.
+Finally, to further investigate how harmonising and aggregating trait data can modify the outcomes of trait–environment relationship characterisation, we used data from one of the newly established datasets with harmonised and aggregated traits to repeat an analysis of salinisation effects on biological traits (\cite{szocs_effects_2014}) and compared our results with those of the original study.
+
 \subsection*{Selection of traits and harmonisation of trait databases}
 
-We established in total 4 trait datasets for the regions Europe, North America, Australia, and New Zealand by harmonising 7 grouping features from 6 trait databases.
-Trait information for Europe was obtained from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}) and the Tachet database (\cite{ussegliopolatera_biological_2000}).
-We refer to both databases by their commonly used names (freshwaterecology.info database and Tachet database).
-The freshwaterecology.info database contains taxa on species-level, while taxa recorded in the Tachet database are on species, genus and family-level.
-Trait information for North America was obtained from \citet{twardochleb_freshwater_nodate} and complemented by \citet{vieira_database_nodate}.
-We refer to the former as the CONUS database and the latter as the Vieira database.
-Data on body form for European and North American taxa was based on expert knowledge (\cite{polatera_personal_information_2020}).
-For Australia and New Zealand, we used trait databases from \citet{kefford_integrated_2020} and \citet{Philips_and_Smith_NZ_DB_2018} respectively.
-We refer to both as the Australian and New Zealand database.
-To increase readability we refer to the datasets we extracted from the trait databases by the name of the continent they originate from.
+To explore the characteristics and comparability of freshwater invertebrate trait data with differing grouping-feature definitions and taxonomic resolution, we obtained invertebrate trait data from six trait databases for four regions: Europe, North America, Australia, and New Zealand.
+For Europe we obtained trait information from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}), which contains taxa at the species level, and the Tachet database (\cite{ussegliopolatera_biological_2000}), which contains taxa at species, genus, and family levels.
+For North America we primarily obtained trait information from \citet{twardochleb_freshwater_nodate} (hereafter referred to as the CONUS database) and where taxa were missing from that database, we obtained data from \citet{vieira_database_nodate} (hereafter referred to as the Vieira database).
+Both databases contain taxa at species, genus and family levels.
+Data on body form for European and North American taxa were based on expert knowledge (\cite{polatera_personal_information_2020}).
+For Australia and New Zealand, we used trait databases from \citet{kefford_integrated_2020} (hereafter referred to as the Australian database) and \citet{Philips_and_Smith_NZ_DB_2018} (hereafter referred to as the New Zealand database) respectively.
+These databases contain taxa at species, genus, family, and less precise taxonomic levels.
 
-We selected traits of seven grouping features that were available in all databases, are commonly applied in trait-based ecological studies, and describe different parts of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
+We established four datasets, one for each of the four geographic regions, by harmonising the traits of seven grouping features from the trait databases.
+We selected traits that were available in all databases, are commonly applied in trait-based ecological studies, and describe different parts of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
 We omitted ecological traits that describe habitat preferences (e.g.
 temperature preference) because these traits are missing in the New Zealand trait database.
-Because grouping features were differently classified across the databases, we harmonised them into 26 traits (Table \ref{tab:traits_harmonisation}).
-Harmonisation was undertaken by amalgamating similar traits into one trait (e.g.
-crawlers and sprawlers into crawlers).
-When doing so, for each taxon the highest trait affinity score among the amalgamated traits was taken.
+Grouping features were  classified differently across the databases, so we harmonised them into 26 traits (Table \ref{tab:traits_harmonisation}).
+To do so we combined  similar traits into one trait (e.g.
+crawlers and sprawlers into crawlers) and assigned the highest trait affinity score among the combined traits for each taxon.
 
-We used fuzzy coding for establishing our harmonised datasets unless data quality prohibited this.
-In the latter case, we used binary traits, i.e.
-categorical and continuous traits were converted into binary traits.
-For example, in the  freshwaterecology.info database, the classification of the trait voltinism accounts for different faunistic regions.
-Hence, entries such as "arctic" or "boreal" in the voltinism traits were substituted with a value of 1.
-Implicitly, we assumed for binary traits that a value of 1 and 0 corresponded to the highest and no affinity for a particular trait.
-Fuzzy codes are reported with different ranges in the trait databases (e.g.
-freshwaterecology.info 0 to 10, Tachet database 0 to 3 or 0 to 5).
-We standardised these to a range between 0 and 1 and converted trait affinities to percentages.
-Thus, fuzzy coded and binary traits were in the same range.
-
-Prior to harmonisation, we consolidated duplicate taxa at the species, genus or family-level if present within a dataset, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
-We also omitted all taxa with a lower taxonomic precision than family-level.
+Next, we selected taxa for inclusion in our datasets and normalised the trait affinity scores for each taxon.
+We first omitted all taxa with a lower taxonomic precision than family level and consolidated duplicate taxa that appeared within a database, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
+We then established our harmonised datasets by using either fuzzy coding or, when unavailable, binary coding.
+Fuzzy codes are reported with different ranges in the trait databases (e.g., freshwaterecology.info: 0–10, Tachet database: 0–3 or 0–5).
+We normalised these to a range between 0 and 1 and converted trait affinities to proportions.
+In cases where binary coding was needed, we converted categorical and continuous traits into binary traits with values of 1 and 0, which, thus, corresponded with the range of fuzzy coded traits.
+For example, in the  freshwaterecology.info database, the classification of the grouping feature voltinism accounts for different faunistic regions and we substituted a value of 1 for entries such as “arctic” or “boreal”.
+We assumed that values of 1 and 0 for binary traits corresponded to the highest and no affinity for a particular trait.
 
@@
 \centering
-\caption{Traits of the harmonised grouping features. The last column indicates traits that were amalgamated for harmonisation (no amalgamation needed if empty).}
+\caption{Traits of harmonised grouping features from six invertebrate trait databases and four geographic regions.
+The last column indicates traits that were combined for harmonisation (no combining needed if empty).}
 \label{tab:traits_harmonisation}
@@
 \toprule[.1em]
-Grouping feature & Trait & Amalgamated traits\\
+Grouping feature & Trait & Combined traits\\
 \toprule[.1em]
@@
 \midrule
-Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattenend, dorsoventrally flattened \textsuperscript{\textit{a}}\\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
+Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattenend, dorsoventrally flattened$^{\dagger}$ \\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
 \midrule
-Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm, \textless 10 mm \textsuperscript{\textit{b}}\\ 9 - 16 mm, 10 - 20 mm\\ \textgreater 16 mm, \textgreater 20 mm\end{tabular}                                                                                                                \\
+Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm, \textless 10 mm$^{\ddagger}$ \\ 9 - 16 mm, 10 - 20 mm\\ \textgreater 16 mm, \textgreater 20 mm\end{tabular}                                                                                                                \\
 \midrule
-Respiration  & \begin{tabular}[c]{@{}l@{}}Gills\\ Plastron/Spiracle\\ \\ \\ \\ Tegument\end{tabular}                             & \begin{tabular}[c]{@{}l@{}} Tracheal gills, gills\\ Temporary air store, Spiracular gills, \\ atmospheric breathers, plant breathers, \\ functional spiracles, air (plants), aerial, \\ plastron/spiracle\\ Cutaneous, tegument \end{tabular}                                                                         \\
+Respiration  & \begin{tabular}[c]{@{}l@{}}Gills\\ Plastron/Spiracle\\ \\ \\ \\ Tegument\end{tabular}                             & \begin{tabular}[c]{@{}l@{}} Tracheal gills, gills\\ Temporary air store, spiracular gills, \\ atmospheric breathers, plant breathers, \\ functional spiracles, air (plants), aerial, \\ plastron/spiracle\\ Cutaneous, tegument \end{tabular}                                                                         \\
 \midrule
@@
 \midrule
-Feeding mode & \begin{tabular}[c]{@{}l@{}}Filterer\\ \\ Gatherer\\ \\ Herbivore\\ \\ Parasite\\ Predator\\ Shredder \\ \\ \end{tabular} & \begin{tabular}[c]{@{}l@{}}Active/passive filterer, absorber, \\ filter-feeder, collector-filterer, filterer\\ Deposit-feeder, collector-gatherer, \\ detrivore, gatherer\\ Grazer, scraper, piercer herbivore, \\ herbivore, algal piercer, piercer (plants)\textsuperscript{\textit{c}}\\ \\ Piercer (animals)\textsuperscript{\textit{c}}, predator \\ Miner, xylophagus, shredder, \\ shredder detrivore\end{tabular} \\
+Feeding mode & \begin{tabular}[c]{@{}l@{}}Filterer\\ \\ Gatherer\\ \\ Herbivore\\ \\ Parasite\\ Predator\\ Shredder \\ \\ \end{tabular} & \begin{tabular}[c]{@{}l@{}}Active/passive filterer, absorber, \\ filter-feeder, collector-filterer, filterer\\ Deposit-feeder, collector-gatherer, \\ detrivore, gatherer\\ Grazer, scraper, piercer herbivore, \\ herbivore, algal piercer, piercer (plants)$^{\mathsection}$\\ \\ Piercer (animals)$^{\mathsection}$, predator \\ Miner, xylophagus, shredder, \\ shredder detrivore\end{tabular} \\
 \hline
@@
 \begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-    \textit{a} The trait "bluff (blocky)" occurred in the Vieira database and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}). \\  
-    \textit{b} Reflects the different size classifications by the Vieiera and the CONUS databases and the other trait databases. \\
-    \textit{c} The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases (\cite{usseglio-polatera_biomonitoring_2000}).
+    $\dagger$ The trait "bluff (blocky)" occurred in the Vieira database and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}). \\  
+    $\ddagger$ Reflects the different size classifications by the Vieira and CONUS databases from the other trait databases. \\
+    $\mathsection$ The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases (\cite{usseglio-polatera_biomonitoring_2000}).
 Taxa exhibiting this trait have been assigned to predators or herbivores based on expert knowledge (\cite{polatera_personal_information_piercer_2020}).
@@
 
-\subsection*{Trait aggregation}
+\subsection*{Comparing trait aggregation methods}
 
-Traits of the harmonised grouping feature datasets were aggregated to family-level using three approaches.
-I) Direct aggregation of taxa to family-level giving equal weight to every taxon using the mean or median, denoted \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively.
-II) Stepwise aggregation, i.e.
-first to the genus-level and subsequently to the family-level using the mean or median.
+For our study aim of comparing the effects of different aggregation methods on trait–environment relationship inference, we aggregated the traits of two of the harmonised datasets to the family level.
+We used three different aggregation approaches: (1) direct aggregation of taxa to family level with either the mean or median, giving equal weight to every taxon.
+We denote these aggregation methods as \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively; (2) stepwise aggregation, first to the genus level and subsequently to the family level with either the mean or median.
 This approach gives equal weights to each genus.
-Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{mean}} or \textit{stepwise\_agg\textsubscript{median}}, respectively.
-III) Aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
-This method weights the genera according to the number of their species in the trait datasets regardless if for every used grouping feature information was available (Figure \ref{fig:data_proc_overview}).
+Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{mean}} or \textit{stepwise\_agg\textsubscript{median}}, respectively; and (3) aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
+This method weights each genus according to its number of species in the trait datasets, regardless of whether information was available for every used grouping feature (Figure \ref{fig:data_proc_overview}).
 When we refer to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg} together we denote these methods as mean aggregation methods and when we refer to \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}} together, we denote these methods as median aggregation methods.
 
-\subsubsection*{Simulation of varying taxonomic hierarchies}
+\subsubsection*{Comparison of family-level aggregated traits with family-level assigned traits}
 
-To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we created three hypothetical examples of different taxonomic hierarchies (scenarios).
-1) A family with an equal number of genera and species (5 genera each with 5 species respectively), denoted as \textit{sim\_base}.
-2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively), denoted as \textit{sim\_extreme}. 
-3) A family where all genera have a different number of species (8, 2, 7, 3, 5), denoted as \textit{sim\_variation}.
-In total every family consisted of 25 species.
-To each scenario a hypothetical grouping feature with 3 traits was assigned (denotes as T1, T2, and T3).
-The 25 affinities for each trait were simulated by sampling from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviations (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability.
-The truncated normal distribution was bound to 0 and 1.
-Simulated trait affinities were converted to percentages, similar to the data processing of the trait databases.
-The sampling was repeated 100 times for each standard deviation.
-Hence, in total 100 datasets for each level of trait variability were simulated, resulting in 12500 simulated trait affinities for each simulated trait ($25$ species per family $* 5$ levels of trait variability $* 100$ replicates).
-These 12500 simulated affinities per trait were assigned to each scenario.
-The above mentioned trait aggregation methods were applied to each simulated dataset.
-% ...resulting in 2500 aggregated affinities per trait and scenario ($12500$ trait affinities per trait divided by $25$, the number of species and multiplied by $5$, the number of aggregation methods).
-The results were compared based on the produced range of aggregated trait affinities between levels of trait variability and scenario.
-We also compared for each simulated dataset the differences in trait affinities obtained by each aggregation method.
+To evaluate the effect of the five trait aggregation methods
+(\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, 
+\textit{stepwise\_agg\textsubscript{median}},
+\textit{stepwise\_agg\textsubscript{mean}},
+\textit{weighted\_agg}) on the assignment of trait affinity scores, we compared our aggregated affinities with trait affinities assigned at family level by experts.
+Expert-assigned trait data were available for a subset of grouping features and taxa for Australia (\cite{chessman_dissolved-oxygen_2018}) and North America (CONUS database), so we conducted this comparison only for these two datasets.
+For the Australian dataset, we used the grouping features feeding mode (all traits listed in Table 1 except parasite) and size (220 families $*$ 8 family–trait combinations = 1760 comparisons).
+For the North American dataset, we used the grouping features feeding mode, respiration, size, voltinism, and locomotion (94 families $*$ 17 family–trait combinations = 1598 comparisons).
+Assigned traits from North America were on a categorical scale, and we converted them to binary prior to comparing them with aggregated trait affinities.
+Size was assigned as continuous variable for Australia, thus, we converted size into three traits (small, medium, and large) with a binary coding.
+Because trait affinities ranged from 0 to 1, the maximum difference possible in trait affinity was 1 to –1, either which corresponds to 100 \%.
+For convenience and to improve interpretation, we calculated absolute trait differences.
+
+\subsubsection*{Effect of taxonomic hierarchy and trait variability on aggregation outcomes}
+
+To examine the influence of taxonomic hierarchy and trait variability on the outcomes of the different trait aggregation methods, we created three hypothetical scenarios.
+We simulated three different families, each composed of 25 total species but with different taxonomic hierarchical structures.
+The three families consisted of (1) a family with an equal number of genera and species (five genera each with five species each), denoted as \textit{sim\_base}; (2) a family in which one genus had a much larger number of species than the other four genera (1 genus with 13 species, 4 genera with 3 species each), denoted as \textit{sim\_extreme}; (3) a family in which all genera had a different number of species (8, 2, 7, 3, 5), denoted as \textit{sim\_variation}.
+We assigned a hypothetical grouping feature with three traits (T1, T2, and T3) to each scenario.
+We then simulated the 25 affinities, one per species, for each trait by sampling from a truncated normal distribution bound by 0 and 1 and with a mean value of 0.5.
+To simulate different levels of trait variability, we repeated the sampling 100 times for each of the 5 levels of standard deviations (0.2, 0.4, 0.6, 0.8, and 1), resulting in 12,500 simulated trait affinities for each simulated trait ($25$ species per family $*$ 5 levels of trait variability $*$ 100 replicates).
+We converted simulated trait affinities to proportions, as was done during trait database processing, and assigned the 12,500 simulated affinities per trait to each of the three family scenarios.
+We then applied the five trait aggregation methods described above to each simulated dataset.
+We compared the resulting ranges of aggregated trait affinities between levels of trait variability and taxonomic hierarchical scenario as well as the differences in trait affinities obtained by each aggregation method.
 
@@
 Intermediate (gray) and main (orange) steps of data preparation are depicted.
-The dashed bottom box illustrates the different trait aggregation methods using a small made-up example (data in the upper left corner).
-The aggregation methods (blue) and intermediate steps of the aggregation methods (purple) are displayed.
-Abbreviations: EU: Europe, NOA: North America, AUS: Australia, NZ: New Zealand, DB: Database.}
+The dashed bottom box illustrates the different trait aggregation methods (hypothetical data in the upper left corner).
+The aggregation methods (purple) and intermediate steps of the aggregation methods (pink) are displayed.
+Abbreviations: EU, Europe; NOA, North America; AUS, Australia; NZ, New Zealand.}
   \label{fig:data_proc_overview}

### 2021-02-08 Paper/Draft_harmonization_paper.tex
08.02: Brooke Edits Part 2

@@
 
-\subsection*{Effects of harmonisation and trait aggregation on trait-environment relationships}
+\subsection*{Effects of harmonisation and trait aggregation on trait-environment relationship inferences}
 
-We repeated the analysis of \citet{szocs_effects_2014} who studied the effect of anthropogenic salinisation on invertebrates in the River Werra in Germany.
-For this re-analysis we used the established harmonised grouping feature dataset for Europe and additionally aggregated traits using the aforementioned aggregation methods.
+To further evaluate the effects of grouping-feature harmonisation and trait aggregation on characterisation of trait–environment relationships, we repeated the analysis of \citet{szocs_effects_2014}, who studied the effects of anthropogenic salinisation on invertebrates in the River Werra in Germany.
+The River Werra has been subject to effluents from the potash industry since the mid- 20th century, which makes it a useful system for studying the responses of invertebrates and their trait compositions to salinisation (\cite{bathe_biological_2011}).
+\citet{szocs_effects_2014}  used redundancy analysis (RDA) to compare trait compositions among sites downstream, upstream, and close to salt discharge (transition).
+Further details about the original study can be found in \citet{szocs_effects_2014}.
 
-The River Werra has been subject to effluents from the potash industry since the mid- 20th century and allows to study responses of invertebrates and their trait compositions to salinisation (\cite{bathe_biological_2011}).
-Sites downstream, upstream, and close to the salt discharge (transition) were compared regarding their trait composition.
-Further details can be found in \citet{szocs_effects_2014}.
-
-We substituted 6 of the grouping features from the original data with harmonised grouping features from the European trait dataset.
-We compared the results of the redundancy analysis (RDA) from the original study to the case when using harmonised grouping features.
-Specifically, the trait composition expressed as community weighted mean (CWM) traits was ordinated along an electric conductivity gradient.
-We compared the species scores obtained from the RDA, i.e.
-the coordinates of the tips of the vectors representing the CWM traits in the bi- or triplots.
-Following the original study, we identified traits associated with higher or lower salinity based on their distance to the ordination axis median using the Mahalanobis distance.
-CWM traits with a Mahalanobis distance greater than the $97.5 \%$ -quantile of the Chi-square distribution (5.02) were regarded as traits responding to either lower or higher salinity.
-For our analysis, we used the same 21 grouping features as in \citet{szocs_effects_2014}.
-The 6 harmonised grouping features used were \textit{Size, Feeding mode, Locomotion, Oviposition, Respiration}, and \textit{Voltinism}.
-Additionally, for testing the effect of aggregated traits we assigned to each taxon in \citet{szocs_effects_2014} the aggregated trait value for its corresponding family and repeated the RDA.
+We re-analysed the \citet{szocs_effects_2014} study by performing a RDA with harmonised grouping features from the dataset for Europe and additionally with traits that we aggregated to family level with the five aggregation methods described above.
+We used all 21 grouping features from the original study, but replaced 6 with harmonised grouping features from our European trait dataset, namely: size, feeding mode, locomotion, oviposition, respiration, and voltinism.
+We compared the results of the original study’s RDA with the results of the RDA from the harmonised grouping features.
+Specifically, the trait composition, expressed as community weighted mean (CWM) traits, was ordinated along an electric conductivity gradient.
+We compared the species scores obtained from the RDA (i.e., the coordinates of the tips of the vectors representing the CWM traits in the bi- or triplots).
+Following the original study, we used the Mahalanobis distance measure and identified traits associated with higher or lower salinity based on their distance to the ordination axis median.
+We considered CWM traits with a Mahalanobis distance greater than the 97.5 \%-quantile of the Chi-square distribution (5.02) to have responded to either lower or higher salinity.
+Additionally, for testing the effect of different aggregation methods on inference about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
 
@@
 
-The data processing and aforementioned analyses were carried out using R (Version 3.6.1).
+All data processing and RDA analyses were carried out using R (\cite{cite_R}).
+RDA was computed using the vegan package (\cite{cite_vegan}).
 Raw data and the R code for data processing and grouping feature harmonisation are located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
-Scripts and data to reproduce the trait aggregation and analysis with aggregated traits are located in the Github repository \url{https://github.com/KunzstLD/Trait-aggregation}.
+Scripts and data to reproduce the trait aggregation, comparison of aggregated and assigned traits, and the RDA analysis are located in the Github repository \url{https://github.com/KunzstLD/Trait-aggregation}.
 
@@
 
+\subsection*{Harmonised trait datasets}
+
 \subsection*{Taxonomic coverage of the harmonised trait datasets}
 
-Regarding taxonomic coverage, the New Zealand dataset has the smallest taxon pool (478 taxa, Table \ref{tab:tax_coverage}).
-By contrast, the European trait dataset has the largest taxon pool with 4601 taxa followed by the North American dataset that contains trait information on 3753 taxa.
-The Australian dataset contains 1402 taxa.
-The European, New Zealand, and North American datasets contain most taxa at the species-level whereas the Australian dataset comprises a similar number of taxa at species and genus-level.
+The harmonised European, North American, Australian, and New Zealand trait datasets differed in terms of their taxonomic coverage.
+The European trait dataset had the largest taxon pool with 4601 taxa (Table \ref{tab:tax_coverage}) followed by the North American dataset (3753 taxa), the Australian dataset (1402 taxa), and the New Zealand dataset with the smallest taxon pool (478 taxa).
+The European, New Zealand, and North American datasets contained most taxa at the species level, whereas the Australian dataset comprised a similar number of taxa at species and genus level.
 
@@
     \centering
-    \caption{Number of taxa per harmonised dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percent.} 
+    \caption{Number (Nr.) of taxa per harmonised dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percent.} 
     \label{tab:tax_coverage}
@@
     \toprule[.1em]
-    Dataset & Nr. of taxa & Species & Genus & Family & Nr. aquatic insects \\ 
+    Dataset & Taxa (Nr.) & Aquatic insects (Nr.) & Species & Genus & Family \\ 
     \toprule[.1em]
-    EU & 4601 & 3739 (81) & 704 (15) & 158 (3) & 3942 (86) \\ 
-    NOA & 3753 & 2414 (64) & 1163 (31) & 176 (5) & 3305 (88) \\ 
-    AUS & 1402 & 564 (40) & 578 (41) & 260 (19) & 1016 (72) \\ 
-    NZ & 478 & 404 (85) & 47 (10) & 27 (6) & 443 (93) \\ 
+    EU & 4601 & 3942 (86) & 3739 (81) & 704 (15) & 158 (3) \\ 
+    NOA & 3753 & 3305 (88) & 2414 (64) & 1163 (31) & 176 (5)  \\ 
+    AUS & 1402 & 1016 (72) & 564 (40) & 578 (41) & 260 (19) \\ 
+    NZ & 478 & 443 (93) & 404 (85) & 47 (10) & 27 (6) \\ 
     \bottomrule
@@
 \end{table}
+\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
+\centering
+Abbreviations: EU, European; NOA, North American; AUS, Australian; NZ, New Zealand.
+\end{minipage}
 
@@
 \subsection*{Completeness of trait information}
+
+The numbers of entries with available information for the selected grouping features varied considerably within the harmonised European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
+By contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (94–100\%).
 

### 2021-02-09 Paper/Draft_harmonization_paper.tex
09.02: Brook Edits part 3

@@
 For our study aim of comparing the effects of different aggregation methods on trait–environment relationship inference, we aggregated the traits of two of the harmonised datasets to the family level.
-We used three different aggregation approaches: (1) direct aggregation of taxa to family level with either the mean or median, giving equal weight to every taxon.
-We denote these aggregation methods as \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively; (2) stepwise aggregation, first to the genus level and subsequently to the family level with either the mean or median.
+We used three different aggregation approaches: (1) direct aggregation of taxa to family level with either the median or mean, giving equal weight to every taxon.
+We denote these aggregation methods as \textit{direct\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{mean}}, respectively; (2) stepwise aggregation, first to the genus level and subsequently to the family level with either the median or mean.
 This approach gives equal weights to each genus.
-Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{mean}} or \textit{stepwise\_agg\textsubscript{median}}, respectively; and (3) aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
+Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{median}} or \textit{stepwise\_agg\textsubscript{mean}}, respectively; and (3) aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
 This method weights each genus according to its number of species in the trait datasets, regardless of whether information was available for every used grouping feature (Figure \ref{fig:data_proc_overview}).
-When we refer to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg} together we denote these methods as mean aggregation methods and when we refer to \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}} together, we denote these methods as median aggregation methods.
 
@@
 Definitions of grouping features and traits varied in their level of detail in the investigated trait databases.
-The freshwaterecology.info database, the Tachet database and the CONUS database provided more detailed descriptions of their trait information compared to the Vieira database and New Zealand database.
-The Australian trait database (\cite{kefford_integrated_2020}) is a collection of seven specific trait datasets.
-Thus, grouping features occur multiple times with varying differentiation into traits.
-Depending on the dataset trait information is described with more or less detail.
+The freshwaterecology.info, Tachet, and CONUS databases provided more detailed descriptions of trait information than the Vieira and New Zealand databases provided.
+The Australian trait database (\cite{kefford_integrated_2020}) was a collection of seven specific trait datasets; thus, grouping features occurred multiple times with varying differentiation into traits.
+Depending on the dataset, trait information was described with more or less detail.
 
-The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their focus.
+The definitions of grouping features also varied across databases in their differentiation into traits and in their focus, both which can lead to discrepancies in trait definitions.
 We provide a summary of discrepancies in trait definitions in the appendix (Table \ref{stab:trait_definitions}).
-Both, differences in differentiation and focus can lead to discrepancies in trait definitions.
-For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways.
-The Tachet database defines predators as carvers, engulfers and swallowers.
-By contrast, in the CONUS database predators are defined as engulfers and carnivorous piercers.
-In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers.
-Furthermore, the focus in the freshwaterecology.info database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition.
-Therefore, the freshwaterecology.info database defines e.g.
-predator as "eating from prey", while the other databases use the mouthpart morphology as basis of their definition.
-The Tachet database captures the food source in an additional grouping feature.
-Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table \ref{stab:trait_definitions}).
-Locomotion definitions differ also in focus between databases.
-Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the Vieira as how organisms deal with flow, Australia as attachment, and the CONUS database includes not only the way of movement, but also the location of movement.
-Similarly, regarding reproduction traits, databases differ in their focus.
-Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases.
-The Vieira database provides information on the oviposition location but not on reproductive behaviour.
-The Australian database report traits for reproductive behaviour but also on oviposition site.
-The New Zealand database distinguishes three grouping features related to reproduction: reproductive technique, oviposition site (e.g.
+Varying levels of differentiation among the trait databases were present in all investigated grouping features (Table \ref{tab:trait_databases_coding_differentiation} and Table \ref{stab:trait_definitions}).
+
+For example, for the grouping feature feeding mode, discrepancies arose because traits were assigned in different ways.
+The Tachet database defined predators as carvers, engulfers, and swallowers.
+By contrast, the CONUS database defined predators as engulfers and carnivorous piercers.
+In turn, the Tachet database defined piercers as a separate trait encompassing both herbivorous and carnivorous piercers.
+Furthermore, the focus in the freshwaterecology.info database for feeding mode was primarily on the food source of a species (except for filterers), whereas the other databases focused on the strategies of food acquisition.
+For example, the freshwaterecology.info database defined predator as "eating from prey", and the other databases used the mouthpart morphology as basis for their definitions.
+The Tachet database captured the food source in an additional grouping feature.
+Locomotion definitions also differed in focus among databases.
+The New Zealand and freshwaterecology.info databases described locomotion as an organism’s way of movement, Tachet as substrate relation and locomotion, Vieira as how organisms deal with flow, Australia as attachment, and CONUS included not only the method of movement but also the location of movement.
+Similarly, databases differed in their focus for reproduction traits.
+In the freshwaterecology.info and Tachet databases, reproduction was captured in one grouping feature and was defined as location of oviposit clutches and mode of reproduction.
+The Vieira database provided information on the oviposition location but not on reproductive behaviour.
+The Australian database reported grouping features for reproductive behaviour but also on oviposition location separately.
+The New Zealand database distinguished three grouping features related to reproduction: reproductive technique, oviposition location (e.g.
 water surface, terrestrial), and egg/egg mass (e.g.
@@
 
-Various codings to describe traits are used throughout the databases (e.g.
-binary, fuzzy, continuous).
-The freshwaterecology.info and Australian databases use different codings, while the Tachet and the New Zealand database exclusively use fuzzy coding.
-The Vieira and CONUS databases contain categorical grouping features that can be converted into traits using a binary coding (Table \ref{tab:trait_databases_coding_differentiation}).
+Trait affinity scores also varied among the databases and were described by varying coding methods (e.g., binary, fuzzy, continuous).
+In the freshwaterecology.info and Australian databases a combination of coding methods is used, whereas in the Tachet and New Zealand databases exclusively fuzzy coding is used.
+The Vieira and CONUS databases contained categorical grouping features that can be converted into binary trait affinities (Table \ref{tab:trait_databases_coding_differentiation}).
 
 \begin{landscape}
-  \begin{longtable}{m{2.2cm}|m{1.8cm}|m{2.3cm}|m{1.8cm}|m{3cm}|m{2cm}|m{2cm}|m{1.8cm}}
-  \caption{Number of traits per grouping feature and type of coding of the traits for the respective grouping feature per database.}
+\begin{longtable}{m{2.3cm}|m{3cm}|m{1.8cm}|m{1.4cm}|m{1.4cm}|m{4.1cm}|m{2cm}}
+\caption{Number of traits per grouping feature and type of coding of the traits for the grouping features used in this study per database. Oviposition location was used for the New Zealand database.}
 \endfirsthead
@@
 \label{tab:trait_databases_coding_differentiation}
-  Database & Feeding Mode & Voltinism & Locomotion & Respiration & Reproduction & Size & Body Form \\ 
+\specialcell{Grouping \\ feature} & \specialcell{freshwater- \\ ecology.info} & Tachet & CONUS & Vieira & Australia & New Zealand \\
 \toprule[.1em]
-  \multirow{2}{*}[-5mm]{ \specialcell{Freshwater- \\ ecology.info}} & 
-  10 & 
-  6 &
-  6 & 
-  7 & 
-  9 & 
-  - & 
-  - 
-  \\
-  \cline{2-8} & 
-  \specialcell{10 point \\ assignment \\ system} &
-  \specialcell{single category \\ assignment \\ system} &
-  \specialcell{10 point \\ assignment \\ system} &
-  \multicolumn{2}{c |}{\specialcell{binary}} &
-  - & 
-  - \\
-  \hline
-  \hline
-  \multirow{2}{*}{Tachet} & 
-  7 & 
-  3 &
-  8 & 
-  5 & 
-  8 & 
-  7 & 
-  - 
-  \\
-  \cline{2-8} &
-  \multicolumn{2}{c |}{fuzzy $[0-3]$} &
-  fuzzy $[0-5]$ & 
-  \multicolumn{3}{c |}{fuzzy $[0-3]$} & 
-  -
-  \\
-  \hline
-  \hline
-  \multirow{2}{*}{\specialcell{CONUS}} & 
-  6 & 
-  3 &
-  10 & 
-  3 & 
-  10 & 
-  3 & 
-  - 
-  \\
-  \cline{2-8} &
-  \multicolumn{6}{c |}{binary} &
-  -
-  \\
-  \hline
-  \hline
-  \multirow{2}{*}{\specialcell{Vieira}} & 
-  8 & 
-  3 &
-  9 & 
-  8 & 
-  10 & 
-  3 & 
-  5 
-  \\
-  \cline{2-8} &
-  \multicolumn{7}{c }{binary}
-  \\
-  \hline
-  \hline
-  \multirow{2}{*}[-4mm]{Australia} & 
-  16 \textsuperscript{\textit{a}} & 
-  7 &
-  9 & 
-  10 &
-  13 \textsuperscript{\textit{b}} & 
-  9 & 
-  4
-  \\
-  \cline{2-8} & 
-  \multicolumn{2}{c |}{\specialcell{binary; proportional $[0 - 1]$; \\ fuzzy $[0 - 3]$}} & 
-  binary; fuzzy $[0 - 3]$ & 
-  \specialcell{binary; proportional \\ scale $[0 - 1]$; \\ fuzzy $[0 - 3]$} & 
-  categorical & 
-  \specialcell{binary; \\ continuous; \\ fuzzy $[0 - 3]$} & 
-  fuzzy $[0-3]$
-  \\
-  \hline
-  \hline
-  \multirow{2}{*}{New Zealand} & 
-  6 & 
-  3 & 
-  4 & 
-  4 & 
-  4 & 
-  5 & 
-  4
-  \\
-  \cline{2-8} & 
-  \multicolumn{7}{c }{fuzzy $[0-3]$}
-  \\
+Feeding Mode & \begin{tabular}[c]{@{}l@{}}10 traits; \\ 10 point assginment \\ system\end{tabular}       & \begin{tabular}[c]{@{}l@{}}7 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}6 traits; \\ binary\end{tabular}   & \begin{tabular}[c]{@{}l@{}}8 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}16 traits$^{\dagger}$; \\ binary, proportional {[}0 - 1{]}, \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}6 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+Voltinism                                                           & \begin{tabular}[c]{@{}l@{}}6 traits; \\ single category \\ assignment system\end{tabular} & \begin{tabular}[c]{@{}l@{}}3 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}3 traits;\\ binary\end{tabular}    & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}7 traits; \\ binary, proportional {[}0 - 1{]}, \\ fuzzy {[}0 - 3{]}\end{tabular}  & \begin{tabular}[c]{@{}l@{}}3 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+Locomotion                                                          & \begin{tabular}[c]{@{}l@{}}6 traits; \\ 10 point assignment \\ system\end{tabular}        & \begin{tabular}[c]{@{}l@{}}8 traits; \\ fuzzy {[}0 - 5{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}10 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary, fuzzy  {[}0 - 3{]}\end{tabular}                              & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+Respiration                                                         & \begin{tabular}[c]{@{}l@{}}7 traits; \\ binary\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}5 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}3 traits;  \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}8 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}10 traits; \\ binary, proportional {[}0 - 1{]}, \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+\begin{tabular}[c]{@{}l@{}}Reproduction/\\ Oviposition\end{tabular} & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}8 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}10 traits;  \\ binary\end{tabular} & \begin{tabular}[c]{@{}l@{}}10 traits; \\ binary\end{tabular} & \begin{tabular}[c]{@{}l@{}}13 traits$^{\ddagger}$; \\ binary\end{tabular}                                                 & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+Size                                                                & -                                                                                         & \begin{tabular}[c]{@{}l@{}}7 traits;\\ fuzzy {[}0 - 3{]}\end{tabular}  & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}   & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary, continuous, \\ \\ fuzzy {[}0 - 3{]}\end{tabular}             & \begin{tabular}[c]{@{}l@{}}5 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+Body Form                                                           & -                                                                                         & -                                                                      & -                                                             & \begin{tabular}[c]{@{}l@{}}4 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular}                                       & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
 \bottomrule
@@
 \begin{minipage}{\linewidth}\small
-      \textit{a} Some of the feeding mode traits used in the Australian database were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
+      $\dagger$ Some of the feeding mode traits used in the Australian database were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
       \newline
-      \textit{b} Not all traits were considered because trait information was partly presented as comments to describe other traits or due to incomplete information.
+      $\ddagger$ Not all traits were considered because trait information was partly presented as comments to describe other traits or due to incomplete information.
   \end{minipage}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Comparing aggregation methods}
+
+\subsection*{Comparison of family-level aggregated traits with family-level assigned traits}
+\label{sec:diff_trait_agg_chessman}
+
+The comparison of family-level aggregated trait affinities with those assigned by experts for the Australian and North American databases showed that aggregation method (median or mean) had a greater effect than overall approach (direct, stepwise, or weighted) in whether trait affinities differed from those assigned by experts.
+
+The percentage of differing cases of aggregated versus assigned trait affinities varied by method between 16.2 and 22.9 \% for the Australian dataset and between 15.3 and 47 \% for the North American dataset (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
+In general, median aggregation methods yielded fewer cases with differences compared with mean and weighted aggregation methods.
+However, median aggregation methods produced, on average, greater absolute differences for both datasets.
+Standard deviations of absolute differences were similar for all tested aggregation methods.
+Maximum differences of 1 (i.e., the maximum possible difference) occurred for all investigated grouping features in both datasets (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
+
+\begin{table}[H]
+  \centering
+  \caption{Percentage of differing cases, minimum, maximum, mean, and standard deviation of absolute differences between trait affinities assigned at family level by experts and aggregated trait affinities from five different aggregation methods.}
+  \label{tab:summary_stat_aggr_vs_fam_assigned}
+  \begin{tabular}{ll|ccccc}
+  \toprule[.1em]
+  Database & \specialcell{Comparison to\\ traits at family level} & \specialcell{Differing \\ cases [\%]} & \specialcell{Min.
+\\ differences} & \specialcell{Max.
+\\ differences} & \specialcell{Mean abs.
+\\ differences} & \specialcell{SD abs.
+\\ differences} \\
+  \toprule[.1em]
+  \multirow{4}{*}{\specialcell{Australia}} & \specialcell{\textit{direct\_agg (median)}} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
+  & \specialcell{\textit{direct\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
+  & \specialcell{\textit{stepwise\_agg (median)}} & 17.90 & 0.01 & 1.00 & 0.42 & 0.26 \\ 
+  & \specialcell{\textit{stepwise\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
+  & \specialcell{\textit{weighted\_agg}} & 23.24 & $< 0.01$ & 1.00 & 0.34 & 0.24 \\ 
+  \midrule
+  \multirow{4}{*}{\specialcell{North America}} & \specialcell{\textit{direct\_agg (median)}} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
+  & \specialcell{\textit{direct\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
+  & \specialcell{\textit{stepwise\_agg (median)}} & 18.00 & 0.08 & 1.00 & 0.63 & 0.28 \\ 
+  & \specialcell{\textit{stepwise\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.27 \\ 
+  & \specialcell{\textit{weighted\_agg}} & 47.00 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
+  \bottomrule
+  \end{tabular}
+\end{table}
+
+\newpage
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_chessman.png}
+  \caption{Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the Australian dataset for the grouping features feeding mode and body size.
+Violin plots - mirrored density plots - show
+  the density of the absolute trait affinity differences.
+Absolute differences in trait affinities are depicted as grey dots.
+\textit{n} denotes the number of cases per comparison where differences occurred.
+The blue dot indicates the mean of absolute differences, and the error bars show the standard deviation.
+The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.}
+  \label{fig:diff_aggr_traits_chessman}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_pyne.png}
+  \caption{Cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family-level.
+Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
+For more details see Figure \ref{fig:diff_aggr_traits_chessman}.}
+  \label{fig:diff_aggr_traits_pyne}
+\end{figure}
+
+\newpage
 
@@
   \label{fig:sim_indv_runs}
-\end{figure}
-
-\newpage
-
-\subsection*{Comparison of family-level aggregated traits with family-level assigned traits}
-\label{sec:diff_trait_agg_chessman}
-
-The percentage of differing cases of trait affinities obtained by the trait aggregation methods compared to trait affinities originally assigned at family-level varied between 16.2 \% and 22.9 \% for the Australian dataset.
-For the North American dataset, comparison of the trait aggregation methods to trait affinities assigned at family-level yielded between 15.3 \% and 47 \% differing cases (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
-In general, median aggregation methods yielded fewer cases with differences compared to mean aggregation methods.
-However, median aggregation methods produced greater differences for both datasets.
-Standard deviations of absolute differences were similar for all tested aggregation methods.
-For both datasets maximum differences of 1 occurred for all investigated grouping features (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
-
-% Is that necessary?
-% A comparison of the aggregation methods with each other for the 4 datasets revealed that differences in aggregated trait affinities were largest between the \textit{stepwise\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{median}} (Figure \ref{fig:comp_aggr_methods}).
-
-\begin{table}[H]
-  \centering
-  \caption{Frequency of differing cases, minimum, maximum, means, and standard deviations of absolute differences between trait affinities assigned at family-level and aggregated trait affinities.}
-  \label{tab:summary_stat_aggr_vs_fam_assigned}
-  \begin{tabular}{ll|ccccc}
-  \toprule[.1em]
-  Database & \specialcell{Comparison to\\ traits at fam.-lvl.} & \specialcell{Differing \\ cases [\%]} & \specialcell{Min.
-\\ differences} & \specialcell{Max.
-\\ differences} & \specialcell{Mean abs.
-\\ differences} & \specialcell{SD abs.
-\\ differences} \\
-  \toprule[.1em]
-  \multirow{4}{*}{\specialcell{Australia}} & \specialcell{direct\_agg (median)} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
-  & \specialcell{direct\_agg (mean)} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
-  & \specialcell{stepwise\_agg (median)} & 17.90 & 0.01 & 1.00 & 0.42 & 0.26 \\ 
-  & \specialcell{stepwise\_agg (mean)} & 23.24 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
-  & \specialcell{weighted\_agg} & 23.24 & $< 0.01$ & 1.00 & 0.34 & 0.24 \\ 
-  \midrule
-  \multirow{4}{*}{\specialcell{North America}} & \specialcell{direct\_agg (median)} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
-  & \specialcell{direct\_agg (mean)} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
-  & \specialcell{stepwise\_agg (median)} & 18.00 & 0.08 & 1.00 & 0.63 & 0.28 \\ 
-  & \specialcell{stepwise\_agg (mean)} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.27 \\ 
-  & \specialcell{weighted\_agg} & 47.00 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
-  \bottomrule
-  \end{tabular}
-\end{table}
-
-\newpage
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_chessman.png}
-  \caption{Cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family-level.
-Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the Australian dataset for the grouping features feeding mode and body size.
-Absolute differences in trait affinities are depicted as gray dots.
-N denotes the number of cases per comparison where differences occurred.
-The blue dot indicates the mean of absolute differences and the error bars the standard deviation.
-The gray vertical lines show the 25th, 50th and 75th quantile of the density estimate.}
-  \label{fig:diff_aggr_traits_chessman}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_pyne.png}
-  \caption{Cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family-level.
-Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
-For more details see Figure \ref{fig:diff_aggr_traits_chessman}.}
-  \label{fig:diff_aggr_traits_pyne}
 \end{figure}

### 2021-02-09 Paper/Draft_harmonization_paper.tex
09.02.: Local update paper

--- 2021-02-08 Paper/Draft_harmonization_paper.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
+\title{Tackling discrepancies in freshwater invertebrate trait databases and taxonomic resolution: Harmonising across continents and trait aggregation}
 \author{}%Stefan Kunz 
@@
 1.
-Use of invertebrate traits rather than species composition may facilitate large-scale comparisons of community structure and responses to disturbance in freshwater ecology because the same traits can potentially occur everywhere.
+Use of invertebrate traits rather than species composition is expected to facilitate large-scale comparisons of community structure and responses to disturbance in freshwater ecology because the same traits can potentially occur everywhere.
+% OLD: because of their consistent response to environmental gradients
 In recent years, comprehensive invertebrate trait databases have been established at different scales (e.g.
@@
 However, a number of data-related issues complicate the use of invertebrate traits for ecological studies.
-For example, standardised definitions for for freshwater invertebrate traits are lacking, which impedes comparisons across regions.
-Moreover, it is uncertain how harmonising varying trait definitions among databases might influence identification of trait-environment relationships.
-In addition, is that taxonomic resolution between observational taxonomic data and trait data can differ, making aggregation of traits necessary.
-At present, it is unknown how different trait aggregation approaches compare with expert-assigned trait affinities.
-In this study we aimed to identify discrepancies in trait definitions across freshwater invertebrate databases and to compare trait aggregation methods to identify how taxonomic hierarchy structure and trait variability influence results from different aggregation approaches.
+For example, for freshwater invertebrate traits standardised definitions are lacking, impeding comparisons across regions.
+Moreover, it is uncertain how harmonising varying trait definitions between databases might influence trait-environment relationships.
+Another issue is that taxonomic resolution between observational taxonomic data and trait data can differ, making aggregation of traits necessary.
+So far, comparisons of different aggregation approaches to expert assessments are lacking.
+% Alternative from Co-Authors: Another issue is that we do not know how taxonomic resolution affects the characterization of traits and hence the comparability of different datasets.
 
@@
 We describe discrepancies in the definitions of traits used to create freshwater invertebrate trait databases in Europe, North America, New Zealand, and Australia.
-Based on our comparisons of these trait databases, we established four novel trait datasets by harmonising trait definitions of commonly used traits.
-Next, we used two of these datasets to compare aggregated traits obtained by different aggregation methods with traits assigned by experts, both at the family level.
-The trait aggregation methods we compared used either the mean or the median and different weightings.
-%Thereby, we simulated how taxonomic resolution and trait variability can change the result of different aggregation approaches.
-We further explored the effects of harmonisation and trait aggregation by re-analysing data from a case study.
+Based on our comparisons of these trait databases, we established 4 novel trait datasets by harmonising trait definitions of commonly used traits.
+Two of these datasets were used to compare aggregated traits obtained by different aggregation methods with traits assigned by experts at family-level.
+We compared trait aggregation methods that use either the mean or the median and different weightings.
+Thereby, we simulated how taxonomic resolution and trait variability can change the result of different aggregation approaches.
+Furthermore, we explored the effect of harmonisation and trait aggregation by re-analysing data from a case study.
 
+% Initial: Between the trait databases, grouping features differed in terms of their classification into traits and their focus leading to discrepancies how traits are defined
 3.
-We found that among trait databases, trait definitions often differed because varying numbers of traits were used to describe groups of related traits (e.g., respiration traits) and the focus of descriptions for groups of related traits also varied (e.g., for feeding mode some databases focused on the food source, whereas others focused on mouthpart morphology).
-The coding to describe traits (binary, fuzzy) also varied among databases.
-Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially from approaches using the median, and that trait coding method, uneven taxonomic hierarchical structure, and high trait variability can influence aggregated trait affinities.
-We further showed that harmonised and aggregated data performed similarly to observational data in identifying trait–environment relationships.
+We found that between trait databases, trait definitions are often different because varying numbers of traits are used to describe groups of related traits (e.g.
+respiration traits).
+Also the focus to describe groups of related traits varies between databases, e.g.
+for feeding mode some focus on the food source, while others on mouthpart morphology.
+Also, the coding to describe traits (binary, fuzzy) varied between databases.
+Aggregated and assigned traits based on expert knowledge displayed a good match, especially approaches using the median to aggregate from species to family-level.
+The comparison with the case study showed that harmonisation and trait aggregation only slightly changed results.
 
@@
 By outlining discrepancies in trait definitions we hope to motivate the development of standardised terminology for invertebrate traits.
-Our results also illustrate the usefulness of harmonised datasets for ecological study and provide guidance for the circumstances under which the choice of trait aggregation method is important.
+When trait aggregation is needed, our results provide guidance under which circumstances the choice of a trait aggregation method becomes important.
 
@@
 
-Explaining and predicting how communities are shaped by environmental factors is a primary main goal of ecology.
+Explaining and predicting how communities are shaped by environmental factors is one of the main goals of ecology.
 Species traits are measurable properties of an organism (\cite{mcgill_rebuilding_2006}), and comparing communities based on the traits possessed by species may facilitate testing of a range of ecological hypotheses (\cite{heino_jani_macroecological_2013}).
-Traits are assumed to be adaptations (e.g., physiological, behavioural) of organisms to their environment and to indicate direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
-In addition to providing local-scale mechanistic-based expressions of species-environment relationships, trait-based approaches might be suitable for large-scale analyses because trait responses are less constrained by biogeographic boundaries and taxon distributional areas than taxonomic responses (\cite{baird_toward_2011, bonada_taxonomic_2007}).
+Traits are assumed to be adaptations (e.g., physiological, behavioural, etc.) of organisms to their environment and represent direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
+Besides providing more mechanistic-based expressions of species-environment relationships, trait-based approaches might be suitable for large-scale analysis because trait responses are less constrained by biogeographic boundaries and taxon distributional areas (\cite{baird_toward_2011, bonada_taxonomic_2007}).
 
-Invertebrate traits have been increasingly used in freshwater ecology, e.g.
+Traits of individual freshwater invertebrate are difficult to determine because - unlike plant traits - they are often difficult to measure directly.
+For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behaviour, and the specific food that is consumed (\cite{moog_comprehensive_nodate}).
+Nevertheless, invertebrate traits have been increasingly used in freshwater ecology, e.g.
 by relating macroinvertebrate trait composition to environmental factors (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}).
-In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases, which typically include data for a single region or continent (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate}).
-The availability of invertebrate trait data from different continents enables comparisons of regional trait variation and allows for testing the consistency of trait structure–environmental factor relationships across both small and large spatial extents.
+
+In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases for various continents (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate}).
+The availability of invertebrate trait data from different continents arguably enables comparisons of trait variation and testing if variation in trait structure is consistently related to environmental factors across both small and large spatial extents.
 To date, such analyses have been carried out mostly within continents, using information from one or two trait databases.
@@
 
-The heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents.
-There are several challenges presented by using invertebrate trait data from multiple established databases in ecological studies.
-One such challenge is inconsistency in terminology.
+% Ben suggests: 
+% Need something here like: One challenge in comparing traits of freshwater invertebrates across many continents are difference in the recording of trait information in the various continental trait databases.
+For example, ......,
+
 In this study, we follow the terminology proposed by \citet{schmera_proposed_2015}, where a grouping feature is defined as a general property (e.g.
 feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species".
-Thus, we use the term grouping feature in place of the term trait, and the term trait instead of trait state, modality or trait category.
+Thus, we use the term grouping feature in place of which many studies use the term "trait", and the term trait instead of "trait state", "modality" or "trait category".
 % Ben suggest here: For  example  e.g., predator, shredder, etc. Are traits of the grouping feature ..... and removing predator, shredder, etc. from the sentence above.
+Traits can be described using different codings (binary, fuzzy) that represent the expression of a characteristic in an organism.
 
-Another challenge to using data from multiple continents is that invertebrate trait databases include different grouping features and related traits.
-To harmonize grouping features from different regions, or to structure them in such a way as to facilitate cross-database comparison, commonly accepted and unambiguous trait definitions are required (\cite{schneider_towards_2019}).
-Ideally, the same traits and grouping features would be reported across databases or standardised terminology would exist to easily harmonise them; however, there is a lack of standardised terminology of trait definitions and poor metadata quality in many trait databases, making grouping-feature harmonisation difficult (\cite{baird_toward_2011, kissling_towards_2018}).
-To our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and invertebrate assemblages.
+To our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and community assembly of invertebrates.
+We suspect that the heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents.
+To harmonize grouping features from different regions, first commonly accepted and unambiguous trait definitions are required (\cite{schneider_towards_2019}).
+In the best case, grouping features would be classified into the same traits across databases or they could easily be harmonised using standardised terminology.
+However, a lack of standardised terminology of trait definitions and poor metadata quality in many trait databases are common issues throughout the field of trait-based ecology (\cite{baird_toward_2011, kissling_towards_2018}).
+Secondly, consistent coding of traits facilitates the comparability of trait data from different databases.
 
-A third challenge to comparing across invertebrate trait databases is inconsistent coding of trait data (\cite{culp_incorporating_2011}), or assigning affinities (aka affinity scores).
-Traits of individual freshwater invertebrates can be difficult to quantify because, unlike plant traits, they are often difficult to measure directly.
-For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behaviour, and specific food sources (\cite{moog_comprehensive_nodate}).
-Some traits can be described as binary or categorical, which ignores uncertainty in how traits are expressed in any particular organism (e.g., adult terrestrial stage, presence of gills).
-Other traits are better suited to being described as continuous (e.g., tolerance of pollution, body size).
-One approach for dealing with uncertainty is the use of fuzzy coding, where traits are assigned probabilistic values.
-Fuzzy codes, which are usually converted to proportions, are used to account for plasticity in traits, variability in traits within taxonomic groups above the species level, and incomplete knowledge.
-A challenge is presented by the use of different types of coding for trait affinities in different databases.
-For example, in the study from \citet{brown_functional_2018} the authors needed to reclassify trait affinities because the individual databases employed different coding approaches (i.e., European and New Zealand databases used fuzzy coding, North American database used binary coding).
+Traits can be described in a binary fashion, or with multiple categories, ignoring uncertainty in how traits are expressed in any particular organism (e.g.
+adult terrestrial stage, presence of gills) or continuous (e.g.
+tolerance of pollution, body size).
+One approach for dealing with uncertainty is the use of fuzzy coding, where the traits are assigned probabilistic values.
+Fuzzy codes are used to account for plasticity in traits, variability in traits within taxonomic groups above species, and incomplete knowledge and are usually converted to proportions.
+In this study we denote the probabilistic values (0-1) of traits as affinities or affinity scores.
 
-Finally, discrepancies in the taxonomic resolutions (e.g., species, genus, or family) when comparing among trait databases, or when linking observational taxonomic data to trait databases, presents another challenge.
-When observations or data in one trait database are at a more precise taxonomic level than other data (e.g.
-observations at species-level and trait data at genus-level) trait information of the less precise taxonomic level is often assigned (e.g.
+However, invertebrate trait databases are heterogeneous with respect to the coding that is used for traits (\cite{culp_incorporating_2011}).
+For example, in the study from \citet{brown_functional_2018} the authors needed to reclassify traits using expert knowledge given that the individual databases employed different coding approaches (i.e.
+European and New Zealand databases fuzzy coding, North American database binary coding).
+Databases with standardised and unambiguous traits and a consistent coding of traits would minimize the data processing effort.
+Discrepancies in the taxonomic resolutions (e.g.
+species, genus or family) when linking observational taxonomic data to trait databases represents another challenge.
+When observations are at a more precise taxonomic level than data available in the trait databases (e.g.
+observations at species-level, trait data at genus-level) trait information of the less precise taxonomic level is often assigned (e.g.
 \cite{szocs_effects_2014, vos_taxonomic_2017}).
-Conversely, if trait information is only available at more precise taxonomic levels than observed taxa, traits are aggregated to a less precise taxonomic level (e.g.
+Conversely, if trait information is only available at more precise taxonomic levels than the observed taxa, traits are aggregated to a less precise taxonomic level (e.g.
 \cite{aspin_extreme_2019, piliere_a._f._h._importance_2016, poff_functional_2006, szocs_effects_2014}).
-To date, studies have used different methods of trait aggregation, e.g.
-the mean (\cite{magliozzi_functional_2019}), median (\cite{szocs_effects_2014}) or mode (\cite{piliere_a._f._h._importance_2016}), but studies on how and to what extent different trait aggregation methods influence trait-based analyses are missing.
-%However, related knowledge would inform future studies regarding the choice of the aggregation method.
+To data, studies have used different methods of trait aggregation, e.g.
+the mean (\cite{magliozzi_functional_2019}), median (\cite{szocs_effects_2014}) or the mode (\cite{piliere_a._f._h._importance_2016}).
+Studies on how and to which extent different trait aggregation methods influence trait-based analysis are missing.
+However, related knowledge would inform future studies regarding the choice of the aggregation method.
 
-These challenges when working with or synthesizing trait data motivated us to assess the characteristics and comparability of freshwater invertebrate trait data contained in disparate databases.
-We aimed to explore methods of improving the comparability of trait data across databases, despite differences in trait definitions and the taxonomic level of data in three ways: (1) by investigating and describing discrepancies in trait definitions between trait databases from Europe, North America, Australia, and New Zealand; (2) by harmonising trait definitions across databases to provide consistent trait grouping features for comparison across geographic locations; and (3) by comparing the influence of different trait aggregation methods and grouping-feature harmonisation on the identification of trait–environment relationships.
+These challenges when working with or synthesizing trait data motivated us to (1) investigate discrepancies in trait definition between trait databases from Europe, North America, Australia, and New Zealand.
+As a basis for further evaluating different trait aggregation methods and how harmonising definition discrepancies between grouping features can influence trait-environment relationships, we developed 4 novel invertebrate trait datasets from these existing trait databases by harmonising 7 grouping features.
+(2) We then evaluated different trait aggregation methods by comparing aggregated traits with traits assigned by experts at family-level for two of the established trait datasets.
+(3) Finally, we re-analysed data from a study of salinisation effects on biological traits (\cite{szocs_effects_2014}) using data from the newly established harmonised European trait dataset and aggregated traits.
+By comparing the re-analysis's findings with those of \citet{szocs_effects_2014}, we investigated how harmonising and aggregating trait data can modify the outcome of trait-environment relationships.
 
@@
 
-To address our study objectives, we took a multi-prong approach to describing, combining, and assessing multiple sources of freshwater invertebrate data that differed in trait grouping-feature definitions and taxonomic resolution.
-%Version from Brooke: As a basis for evaluating the comparability of freshwater invertebrate databases, we developed four novel invertebrate trait datasets by harmonising seven grouping features from existing trait databases.
-We then evaluated the influence of different...
-Identified trait definitions discrepancies served as a starting point to develop four novel invertebrate trait datasets by harmonising seven grouping features from existing trait databases.
-The harmonised trait datasets were used to evaluate the influence of different trait aggregation approaches on the identification of trait–environment relationships, our third study objective, in two ways by (1) comparing family-level aggregated trait affinities with family-level trait affinities assigned by experts for two of the established trait datasets where such data were available and (2) comparing the influence of taxonomic hierarchy and trait variability on the outcomes of the different trait aggregation approaches for simulated data.
-Finally, to further investigate how harmonising and aggregating trait data can modify the outcomes of trait–environment relationship characterisation, we used data from one of the newly established datasets with harmonised and aggregated traits to repeat an analysis of salinisation effects on biological traits (\cite{szocs_effects_2014}) and compared our results with those of the original study.
-
 \subsection*{Selection of traits and harmonisation of trait databases}
 
-To explore the characteristics and comparability of freshwater invertebrate trait data with differing grouping-feature definitions and taxonomic resolution, we obtained invertebrate trait data from six trait databases for four regions: Europe, North America, Australia, and New Zealand.
-For Europe we obtained trait information from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}), which contains taxa at the species level, and the Tachet database (\cite{ussegliopolatera_biological_2000}), which contains taxa at species, genus, and family levels.
-For North America we primarily obtained trait information from \citet{twardochleb_freshwater_nodate} (hereafter referred to as the CONUS database) and where taxa were missing from that database, we obtained data from \citet{vieira_database_nodate} (hereafter referred to as the Vieira database).
-Both databases contain taxa at species, genus and family levels.
-Data on body form for European and North American taxa were based on expert knowledge (\cite{polatera_personal_information_2020}).
-For Australia and New Zealand, we used trait databases from \citet{kefford_integrated_2020} (hereafter referred to as the Australian database) and \citet{Philips_and_Smith_NZ_DB_2018} (hereafter referred to as the New Zealand database) respectively.
-These databases contain taxa at species, genus, family, and less precise taxonomic levels.
+We established in total 4 trait datasets for the regions Europe, North America, Australia, and New Zealand by harmonising 7 grouping features from 6 trait databases.
+Trait information for Europe was obtained from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}) and the Tachet database (\cite{ussegliopolatera_biological_2000}).
+We refer to both databases by their commonly used names (freshwaterecology.info database and Tachet database).
+The freshwaterecology.info database contains taxa on species-level, while taxa recorded in the Tachet database are on species, genus and family-level.
+Trait information for North America was obtained from \citet{twardochleb_freshwater_nodate} and complemented by \citet{vieira_database_nodate}.
+We refer to the former as the CONUS database and the latter as the Vieira database.
+Data on body form for European and North American taxa was based on expert knowledge (\cite{polatera_personal_information_2020}).
+For Australia and New Zealand, we used trait databases from \citet{kefford_integrated_2020} and \citet{Philips_and_Smith_NZ_DB_2018} respectively.
+We refer to both as the Australian and New Zealand database.
+To increase readability we refer to the datasets we extracted from the trait databases by the name of the continent they originate from.
 
-We established four datasets, one for each of the four geographic regions, by harmonising the traits of seven grouping features from the trait databases.
-We selected traits that were available in all databases, are commonly applied in trait-based ecological studies, and describe different parts of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
+We selected traits of seven grouping features that were available in all databases, are commonly applied in trait-based ecological studies, and describe different parts of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
 We omitted ecological traits that describe habitat preferences (e.g.
 temperature preference) because these traits are missing in the New Zealand trait database.
-Grouping features were  classified differently across the databases, so we harmonised them into 26 traits (Table \ref{tab:traits_harmonisation}).
-To do so we combined  similar traits into one trait (e.g.
-crawlers and sprawlers into crawlers) and assigned the highest trait affinity score among the combined traits for each taxon.
+Because grouping features were differently classified across the databases, we harmonised them into 26 traits (Table \ref{tab:traits_harmonisation}).
+Harmonisation was undertaken by amalgamating similar traits into one trait (e.g.
+crawlers and sprawlers into crawlers).
+When doing so, for each taxon the highest trait affinity score among the amalgamated traits was taken.
 
-Next, we selected taxa for inclusion in our datasets and normalised the trait affinity scores for each taxon.
-We first omitted all taxa with a lower taxonomic precision than family level and consolidated duplicate taxa that appeared within a database, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
-We then established our harmonised datasets by using either fuzzy coding or, when unavailable, binary coding.
-Fuzzy codes are reported with different ranges in the trait databases (e.g., freshwaterecology.info: 0–10, Tachet database: 0–3 or 0–5).
-We normalised these to a range between 0 and 1 and converted trait affinities to proportions.
-In cases where binary coding was needed, we converted categorical and continuous traits into binary traits with values of 1 and 0, which, thus, corresponded with the range of fuzzy coded traits.
-For example, in the  freshwaterecology.info database, the classification of the grouping feature voltinism accounts for different faunistic regions and we substituted a value of 1 for entries such as “arctic” or “boreal”.
-We assumed that values of 1 and 0 for binary traits corresponded to the highest and no affinity for a particular trait.
+We used fuzzy coding for establishing our harmonised datasets unless data quality prohibited this.
+In the latter case, we used binary traits, i.e.
+categorical and continuous traits were converted into binary traits.
+For example, in the  freshwaterecology.info database, the classification of the trait voltinism accounts for different faunistic regions.
+Hence, entries such as "arctic" or "boreal" in the voltinism traits were substituted with a value of 1.
+Implicitly, we assumed for binary traits that a value of 1 and 0 corresponded to the highest and no affinity for a particular trait.
+Fuzzy codes are reported with different ranges in the trait databases (e.g.
+freshwaterecology.info 0 to 10, Tachet database 0 to 3 or 0 to 5).
+We standardised these to a range between 0 and 1 and converted trait affinities to percentages.
+Thus, fuzzy coded and binary traits were in the same range.
+
+Prior to harmonisation, we consolidated duplicate taxa at the species, genus or family-level if present within a dataset, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
+We also omitted all taxa with a lower taxonomic precision than family-level.
 
@@
 \centering
-\caption{Traits of harmonised grouping features from six invertebrate trait databases and four geographic regions.
-The last column indicates traits that were combined for harmonisation (no combining needed if empty).}
+\caption{Traits of the harmonised grouping features. The last column indicates traits that were amalgamated for harmonisation (no amalgamation needed if empty).}
 \label{tab:traits_harmonisation}
@@
 \toprule[.1em]
-Grouping feature & Trait & Combined traits\\
+Grouping feature & Trait & Amalgamated traits\\
 \toprule[.1em]
@@
 \midrule
-Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattenend, dorsoventrally flattened$^{\dagger}$ \\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
+Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattenend, dorsoventrally flattened \textsuperscript{\textit{a}}\\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
 \midrule
-Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm, \textless 10 mm$^{\ddagger}$ \\ 9 - 16 mm, 10 - 20 mm\\ \textgreater 16 mm, \textgreater 20 mm\end{tabular}                                                                                                                \\
+Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm, \textless 10 mm \textsuperscript{\textit{b}}\\ 9 - 16 mm, 10 - 20 mm\\ \textgreater 16 mm, \textgreater 20 mm\end{tabular}                                                                                                                \\
 \midrule
-Respiration  & \begin{tabular}[c]{@{}l@{}}Gills\\ Plastron/Spiracle\\ \\ \\ \\ Tegument\end{tabular}                             & \begin{tabular}[c]{@{}l@{}} Tracheal gills, gills\\ Temporary air store, spiracular gills, \\ atmospheric breathers, plant breathers, \\ functional spiracles, air (plants), aerial, \\ plastron/spiracle\\ Cutaneous, tegument \end{tabular}                                                                         \\
+Respiration  & \begin{tabular}[c]{@{}l@{}}Gills\\ Plastron/Spiracle\\ \\ \\ \\ Tegument\end{tabular}                             & \begin{tabular}[c]{@{}l@{}} Tracheal gills, gills\\ Temporary air store, Spiracular gills, \\ atmospheric breathers, plant breathers, \\ functional spiracles, air (plants), aerial, \\ plastron/spiracle\\ Cutaneous, tegument \end{tabular}                                                                         \\
 \midrule
@@
 \midrule
-Feeding mode & \begin{tabular}[c]{@{}l@{}}Filterer\\ \\ Gatherer\\ \\ Herbivore\\ \\ Parasite\\ Predator\\ Shredder \\ \\ \end{tabular} & \begin{tabular}[c]{@{}l@{}}Active/passive filterer, absorber, \\ filter-feeder, collector-filterer, filterer\\ Deposit-feeder, collector-gatherer, \\ detrivore, gatherer\\ Grazer, scraper, piercer herbivore, \\ herbivore, algal piercer, piercer (plants)$^{\mathsection}$\\ \\ Piercer (animals)$^{\mathsection}$, predator \\ Miner, xylophagus, shredder, \\ shredder detrivore\end{tabular} \\
+Feeding mode & \begin{tabular}[c]{@{}l@{}}Filterer\\ \\ Gatherer\\ \\ Herbivore\\ \\ Parasite\\ Predator\\ Shredder \\ \\ \end{tabular} & \begin{tabular}[c]{@{}l@{}}Active/passive filterer, absorber, \\ filter-feeder, collector-filterer, filterer\\ Deposit-feeder, collector-gatherer, \\ detrivore, gatherer\\ Grazer, scraper, piercer herbivore, \\ herbivore, algal piercer, piercer (plants)\textsuperscript{\textit{c}}\\ \\ Piercer (animals)\textsuperscript{\textit{c}}, predator \\ Miner, xylophagus, shredder, \\ shredder detrivore\end{tabular} \\
 \hline
@@
 \begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-    $\dagger$ The trait "bluff (blocky)" occurred in the Vieira database and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}). \\  
-    $\ddagger$ Reflects the different size classifications by the Vieira and CONUS databases from the other trait databases. \\
-    $\mathsection$ The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases (\cite{usseglio-polatera_biomonitoring_2000}).
+    \textit{a} The trait "bluff (blocky)" occurred in the Vieira database and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}). \\  
+    \textit{b} Reflects the different size classifications by the Vieiera and the CONUS databases and the other trait databases. \\
+    \textit{c} The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases (\cite{usseglio-polatera_biomonitoring_2000}).
 Taxa exhibiting this trait have been assigned to predators or herbivores based on expert knowledge (\cite{polatera_personal_information_piercer_2020}).
@@
 
-\subsection*{Comparing trait aggregation methods}
+\subsection*{Trait aggregation}
 
-For our study aim of comparing the effects of different aggregation methods on trait–environment relationship inference, we aggregated the traits of two of the harmonised datasets to the family level.
-We used three different aggregation approaches: (1) direct aggregation of taxa to family level with either the mean or median, giving equal weight to every taxon.
-We denote these aggregation methods as \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively; (2) stepwise aggregation, first to the genus level and subsequently to the family level with either the mean or median.
+Traits of the harmonised grouping feature datasets were aggregated to family-level using three approaches.
+I) Direct aggregation of taxa to family-level giving equal weight to every taxon using the mean or median, denoted \textit{direct\_agg\textsubscript{mean}} and \textit{direct\_agg\textsubscript{median}}, respectively.
+II) Stepwise aggregation, i.e.
+first to the genus-level and subsequently to the family-level using the mean or median.
 This approach gives equal weights to each genus.
-Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{mean}} or \textit{stepwise\_agg\textsubscript{median}}, respectively; and (3) aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
-This method weights each genus according to its number of species in the trait datasets, regardless of whether information was available for every used grouping feature (Figure \ref{fig:data_proc_overview}).
+Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{mean}} or \textit{stepwise\_agg\textsubscript{median}}, respectively.
+III) Aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
+This method weights the genera according to the number of their species in the trait datasets regardless if for every used grouping feature information was available (Figure \ref{fig:data_proc_overview}).
 When we refer to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg} together we denote these methods as mean aggregation methods and when we refer to \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}} together, we denote these methods as median aggregation methods.
 
-\subsubsection*{Comparison of family-level aggregated traits with family-level assigned traits}
+\subsubsection*{Simulation of varying taxonomic hierarchies}
 
-To evaluate the effect of the five trait aggregation methods
-(\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, 
-\textit{stepwise\_agg\textsubscript{median}},
-\textit{stepwise\_agg\textsubscript{mean}},
-\textit{weighted\_agg}) on the assignment of trait affinity scores, we compared our aggregated affinities with trait affinities assigned at family level by experts.
-Expert-assigned trait data were available for a subset of grouping features and taxa for Australia (\cite{chessman_dissolved-oxygen_2018}) and North America (CONUS database), so we conducted this comparison only for these two datasets.
-For the Australian dataset, we used the grouping features feeding mode (all traits listed in Table 1 except parasite) and size (220 families $*$ 8 family–trait combinations = 1760 comparisons).
-For the North American dataset, we used the grouping features feeding mode, respiration, size, voltinism, and locomotion (94 families $*$ 17 family–trait combinations = 1598 comparisons).
-Assigned traits from North America were on a categorical scale, and we converted them to binary prior to comparing them with aggregated trait affinities.
-Size was assigned as continuous variable for Australia, thus, we converted size into three traits (small, medium, and large) with a binary coding.
-Because trait affinities ranged from 0 to 1, the maximum difference possible in trait affinity was 1 to –1, either which corresponds to 100 \%.
-For convenience and to improve interpretation, we calculated absolute trait differences.
-
-\subsubsection*{Effect of taxonomic hierarchy and trait variability on aggregation outcomes}
-
-To examine the influence of taxonomic hierarchy and trait variability on the outcomes of the different trait aggregation methods, we created three hypothetical scenarios.
-We simulated three different families, each composed of 25 total species but with different taxonomic hierarchical structures.
-The three families consisted of (1) a family with an equal number of genera and species (five genera each with five species each), denoted as \textit{sim\_base}; (2) a family in which one genus had a much larger number of species than the other four genera (1 genus with 13 species, 4 genera with 3 species each), denoted as \textit{sim\_extreme}; (3) a family in which all genera had a different number of species (8, 2, 7, 3, 5), denoted as \textit{sim\_variation}.
-We assigned a hypothetical grouping feature with three traits (T1, T2, and T3) to each scenario.
-We then simulated the 25 affinities, one per species, for each trait by sampling from a truncated normal distribution bound by 0 and 1 and with a mean value of 0.5.
-To simulate different levels of trait variability, we repeated the sampling 100 times for each of the 5 levels of standard deviations (0.2, 0.4, 0.6, 0.8, and 1), resulting in 12,500 simulated trait affinities for each simulated trait ($25$ species per family $*$ 5 levels of trait variability $*$ 100 replicates).
-We converted simulated trait affinities to proportions, as was done during trait database processing, and assigned the 12,500 simulated affinities per trait to each of the three family scenarios.
-We then applied the five trait aggregation methods described above to each simulated dataset.
-We compared the resulting ranges of aggregated trait affinities between levels of trait variability and taxonomic hierarchical scenario as well as the differences in trait affinities obtained by each aggregation method.
+To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we created three hypothetical examples of different taxonomic hierarchies (scenarios).
+1) A family with an equal number of genera and species (5 genera each with 5 species respectively), denoted as \textit{sim\_base}.
+2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively), denoted as \textit{sim\_extreme}. 
+3) A family where all genera have a different number of species (8, 2, 7, 3, 5), denoted as \textit{sim\_variation}.
+In total every family consisted of 25 species.
+To each scenario a hypothetical grouping feature with 3 traits was assigned (denotes as T1, T2, and T3).
+The 25 affinities for each trait were simulated by sampling from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviations (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability.
+The truncated normal distribution was bound to 0 and 1.
+Simulated trait affinities were converted to percentages, similar to the data processing of the trait databases.
+The sampling was repeated 100 times for each standard deviation.
+Hence, in total 100 datasets for each level of trait variability were simulated, resulting in 12500 simulated trait affinities for each simulated trait ($25$ species per family $* 5$ levels of trait variability $* 100$ replicates).
+These 12500 simulated affinities per trait were assigned to each scenario.
+The above mentioned trait aggregation methods were applied to each simulated dataset.
+% ...resulting in 2500 aggregated affinities per trait and scenario ($12500$ trait affinities per trait divided by $25$, the number of species and multiplied by $5$, the number of aggregation methods).
+The results were compared based on the produced range of aggregated trait affinities between levels of trait variability and scenario.
+We also compared for each simulated dataset the differences in trait affinities obtained by each aggregation method.
 
@@
 Intermediate (gray) and main (orange) steps of data preparation are depicted.
-The dashed bottom box illustrates the different trait aggregation methods (hypothetical data in the upper left corner).
-The aggregation methods (purple) and intermediate steps of the aggregation methods (pink) are displayed.
-Abbreviations: EU, Europe; NOA, North America; AUS, Australia; NZ, New Zealand.}
+The dashed bottom box illustrates the different trait aggregation methods using a small made-up example (data in the upper left corner).
+The aggregation methods (blue) and intermediate steps of the aggregation methods (purple) are displayed.
+Abbreviations: EU: Europe, NOA: North America, AUS: Australia, NZ: New Zealand, DB: Database.}
   \label{fig:data_proc_overview}

### 2021-02-09 Paper/Flowchart/Flowchart_methods.tex

@@
                 matrix,
-                shapes.geometric}
+                shapes.geometric,
+                decorations.pathreplacing, 
+                angles,
+                quotes}
 
@@
       %% Nodes
-      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Consolidating duplicate \\ taxa in  EU, NOA, AUS \& \\ NZ DBs};
-      \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{AUS traits standardized to [0-1] \\ because multiple codings used \\ throughout this database};
-      \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Taxa more precise than \\ family-level};
+      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Consolidating duplicate \\ taxa in  EU, NOA, AUS \& \\ NZ databases};
+      \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{AUS traits standardised to [0 - 1] \\ because multiple codings used \\ throughout this database};
+      \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Omitted taxa less \\ precise than family-level};
 
@@
 
-      \node(conversionPerc)[intstepsnode, align = center, xshift = 0cm, yshift = -2.5cm]{Traits converted to percentages \\ and normalized to [0-1]};
+      \node(conversionPerc)[intstepsnode, align = center, xshift = 0cm, yshift = -2.5cm]{Traits converted to proportions \\ and normalised to [0 - 1]};
 
@@
       \draw[->] (conversionPerc.east) -- (traitAgg.west);
-      \draw[arrow1] (traitAgg.south) -- (frameExample.north);
+      \draw[arrow1] (traitAgg.south) to [out=200,in=40] (frameExample.north);
+      \draw[arrow1] (traitAgg.south) to [out=360,in=80] (frameExample.east);
       \draw[->] (directAgg.south) -- (tab_direct_agg.north);

### 2021-02-09 Paper/Draft_harmonization_paper.tex
09.02: Brooke Edits Pt. 4

--- 2021-02-09 Paper/Draft_harmonization_paper.tex
@@
   \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_pyne.png}
-  \caption{Cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family-level.
-Violin plots - a mirrored density plot - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
+  \caption{Cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family level.
+Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
 For more details see Figure \ref{fig:diff_aggr_traits_chessman}.}
@@
 
-\subsection*{Simulation of varying taxonomic hierarchies}
+\subsection*{Comparison of aggregation methods with varying taxonomic hierarchies and trait variability}
 
-We evaluated the simulation results based on the produced range of aggregated trait affinities and by comparing results of every simulated dataset.
-
-As expected the produced range of trait affinities increased for all aggregation methods with increasing trait variability (Figure \ref{fig:overview_sim_results}).% Ben would add: 
+Our simulation results showed that both taxonomic hierarchical structure and trait variability affected aggregated trait affinities and that aggregation method mattered in terms of the ranges of trait affinities produced over simulation replicates.
+The effect of taxonomic hierarchy differed across aggregation methods, but, as we expected, the produced range of trait affinities increased with increasing trait variability for all aggregation methods (Figure \ref{fig:overview_sim_results}).
+% Ben would add:
  % as indicated by the increasing range of the boxes and wiskers with increasing standard deviation.
 
- % Ben further suggests: When each genus has the same number of species (sim base) ......
-.
-In contrast with most species in one genus and fewer in the other genera (sim_extreme) ....
-.
-While with variable number of species per genera () .....
-.
+Taxonomic hierarchical structure appeared to influence the outcomes of the different aggregation methods.
+For the \textit{sim\_base} scenario (equal numbers of genera and species), the mean and weighted aggregation methods yielded similar ranges of aggregated trait affinities within each level of trait variability, and the median aggregation methods consistently produced greater ranges of aggregated trait affinities than the other methods.
+The largest ranges were produced by the \textit{stepwise\_agg \textsubscript{median}} method.
+For the more complex taxonomic hierarchical structures, \textit{sim\_extreme} (one genus with a much larger number of species than the other four) and \textit{sim\_variation} (all genera with a different number of species), the \textit{stepwise\_agg \textsubscript{median}} method still produced the largest ranges of trait affinities for most levels of trait variability (and \textit{direct\_agg\textsubscript{mean}} produced the narrowest ranges for most levels of trait variability), but there was much less consistency in the ranges of trait affinities for all aggregation methods (i.e., the ranges were different among all aggregation methods).
 
-For the \textit{sim\_base} scenario, the mean aggregation methods yielded similar ranges of aggregated trait affinities within each level of trait variability whereas the median aggregation methods produced mostly greater ranges of aggregated trait affinities.
-By contrast, the ranges of trait affinities slightly differed for all aggregation methods for the simulation scenarios \textit{sim\_extreme} and \textit{sim\_variation}.
-\textit{Weighted\_agg} and \textit{stepwise\_agg\textsubscript{mean}} produced a wider range of trait affinities than the \textit{direct\_agg\textsubscript{mean}} in the \textit{sim\_extreme} scenario.
-For most levels of trait variability the \textit{stepwise\_agg \textsubscript{median}} resulted in the largest range of trait affinities in the \textit{sim\_extreme} and \textit{sim\_variation} scenarios.
-
-Each trait aggregation method yielded one aggregated affinity for every simulated dataset, in total 15000 comparisons ($100$ replicates $*$ 5 levels of trait variability $* 10$ unique comparisons of trait aggregation methods $* 3$ scenarios).
-In most simulated datasets the different aggregation methods often resulted in similar trait affinities.
-Only 1.42 \% (213 out of 15.000) of all comparisons showed a difference equal or greater than an absolute trait affinity of 0.1.
-Most of these differences occurred for the \textit{sim\_extreme} scenario (83.5 \%).
-The majority of the differences equal or above 0.1 were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure \ref{fig:sim_indv_runs}).
-% Differences were rather small, largest difference 0.265 for sim_extreme (stepwise_median vs weighted_agg)
+Although trait aggregation methods were affected by taxonomic hierarchical structure and trait variability to some degree, in most simulated datasets, the different aggregation methods resulted in similar trait affinities.
+Only 1.42 \%, or 213 out of 15.000 total comparisons (3 scenarios $*$ 5 levels of trait variability $*$ 10 unique comparisons of trait aggregation methods $*$ 100 replicates) showed a difference equal or greater than an absolute trait affinity of 0.1.
+Most  (83.5 \%) of these differences occurred in the \textit{sim\_extreme} scenario and were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure \ref{fig:sim_indv_runs}).
 
@@
   \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
-Boxplots depict results for each trait aggregation method of 100 simulations.
-T1, T2, and T3 are the simulated traits.}
+Boxplots depict results for 100 replicated simulations of each trait aggregation method.
+The boxplot depicts the median and encompasses the 25\textsuperscript{th} and 75\textsuperscript{th} percentile.
+Horizontal black lines depict the median.
+Whiskers extend to the largest and smallest value respectively no further than 1.5 $*$ of the inter-quartile range.
+Outliers beyond the end of the whiskers are plotted as grey dots.}
   \label{fig:overview_sim_results}
@@
   \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
-  \caption{Comparison of the aggregated trait affinities produced by the different trait aggregation methods for every simulated dataset across all 3 simulated traits.
+  \caption{Comparison between the aggregated trait affinities produced by the different trait aggregation methods for every simulated dataset across all 3 simulated traits (5,000 comparisons per taxonomic hierarchy scenario).
+Results are shown for different levels of trait variability which is represented by the standard deviation (SD) of the simulated traits.
 Dots depict comparisons where absolute differences between aggregated trait affinities were greater than 0.1.
+Overall, there are 10 possible unique comparisons of which 7 produced absolute differences greater than 0.1.
 \newline
-  Comparison: \newline
-  1) Direct\_agg (median) - Stepwise\_agg (mean) \newline
-  2) Direct\_agg (median) - Weighted\_agg, \newline
-  3) Stepwise\_agg (mean) - Stepwise\_agg (median), \newline
-  4) Stepwise\_agg (mean) - Weighted\_agg, \newline  
-  5) Direct\_agg (mean) - Stepwise\_agg (median), \newline
-  6) Direct\_agg (median) - Stepwise\_agg (median), \newline
-  7) Stepwise\_agg (median) - Weighted\_agg \newline
+  Comparisons: \newline
+  1) \textit{direct\_agg (median)} - \textit{Stepwise\_agg (mean)} \newline
+  2) \textit{Direct\_agg (median)} - \textit{Weighted\_agg} \newline
+  3) \textit{Stepwise\_agg (mean)} - \textit{Stepwise\_agg (median)} \newline
+  4) \textit{Stepwise\_agg (mean)} - \textit{Weighted\_agg} \newline  
+  5) \textit{Direct\_agg (mean)} - \textit{Stepwise\_agg (median)} \newline
+  6) \textit{Direct\_agg (median)} - \textit{Stepwise\_agg (median)} \newline
+  7) \textit{Stepwise\_agg (median)} - \textit{Weighted\_agg} \newline
   }
@@
 
-The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (higher salinity) were characterised by the traits shredder, ovoviviparity, multivoltinism, long life cycle duration ($> 1$ year), and gill respiration, whereas upstream sites (lower salinity) were characterized by univoltinism, oviposition in clutches and short life cycle duration ($< 1$ year).
+Our re-analysis of the \citet{szocs_effects_2014} study on the effects of salinisation on invertebrate traits showed that the use of harmonised and aggregated trait data may be useful for ecological studies on trait–environment relationships.
+Overall, harmonised trait data and all aggregation methods produced similar distributions of RDA species scores (\ref{fig:violin_plot_species_sc}) compared with the original analysis, and they resulted in similar, but fewer, traits that distinguished upstream and downstream sites than the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
 
-Overall, harmonised trait data and all aggregation methods produced similar distributions of RDA species scores (Figures \ref{fig:violin_plot_species_sc}) compared to the original analysis in \citet{szocs_effects_2014}.
-Using harmonised grouping features resulted in less traits that distinguish upstream and downstream sites in comparison to the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
-According to the RDA of the trait composition, downstream sites were characterised by taxa with the traits multivoltinism, ovoviviparity and long life cycle duration.
-Upstream sites were characterised by univoltine taxa with a short life cycle duration that lay their eggs in an aquatic environment (aquatic eggs).
-The trait aquatic eggs of the harmonised grouping feature oviposition was derived by amalgamating the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonisation}).
-The traits shredder and gill respiration did not characterise sites with higher salinisation.
+RDA using harmonised, but not aggregated, grouping features identified some, but not all, of the same traits that were identified by the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
+The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (higher salinity) were characterised by the traits: ovoviviparity, multivoltinism, long life-cycle duration ($> 1$ year), shredder, and gill respiration, whereas RDA with the harmonised data identified the first three traits but did not include shredder or gill respiration traits.
+The original RDA indicated that upstream sites (lower salinity) were characterised by the traits: univoltinism, oviposition in clutches, and short life-cycle duration ($< 1$ year), and RDA with the harmonised data characterised upstream sites by univoltine taxa with short life-cycle durations that lay their eggs in an aquatic environment (aquatic eggs).
+This difference in oviposition trait is not substantial because the trait aquatic eggs of the harmonised grouping feature oviposition was derived by combining the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonisation}).
 
-Using traits aggregated at family-level from the harmonised dataset also showed results similar to the original analysis, but with less traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
-The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg}
-characterised the downstream sites with the same traits as the original analysis except that downstream sites were not characterised by the trait shredder.
-Upstream sites were characterised by the traits univoltinism, aquatic eggs and short life cycle duration.
-The same results were obtained when re-analysing the data with traits aggregated by the \textit{stepwise\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, with the exception that none of the life cycle traits characterised upstream or downstream sites.
-Thus, in our comparison aggregating by \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg} yielded the least change in interpretation of the RDA results compared to the original findings.
+RDA using harmonised traits that were aggregated to family level also produced results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
+The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg} characterised the downstream sites with the same traits as the original analysis except the trait shredder.
+As for the RDA with harmonised but not aggregated data, RDA with these three aggregation methods characterised upstream sites by the traits univoltinism, short life-cycle duration, and aquatic eggs.
+The \textit{stepwise\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}} methods produced the same results except that none of the life-cycle traits characterised upstream or downstream sites.
+Thus, compared with the original study’s findings, aggregating by the direct and weighted methods yielded less change than the stepwise methods in interpretation of the RDA results.
 
@@
     \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
-    \caption{Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonised grouping features, and using harmonised grouping features with traits aggregated to family-level.
+    \caption{Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonised grouping features, and using harmonised grouping features with traits aggregated to family level with five different aggregation methods.
 The dots represent the individual species scores for each analysed trait along the conductivity axis.
 The violin plot shows the density estimate of the species scores.
-Gray vertical lines indicate the median of the obtained species scores.}
+Grey vertical lines indicate the median of the obtained species scores.}
     \label{fig:violin_plot_species_sc}

### 2021-02-09 Paper/Draft_harmonization_paper.tex
09.02.: Brooke edits Pt.5

@@
   \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
+Shown are the results only for one simulated trait (T1).
+Similar results were obtained for the other simulated traits (see appendix).
 Boxplots depict results for 100 replicated simulations of each trait aggregation method.
@@
 Horizontal black lines depict the median.
-Whiskers extend to the largest and smallest value respectively no further than 1.5 $*$ of the inter-quartile range.
+Whiskers extend to the largest and smallest value respectively no further than 1.5 $*$ the inter-quartile range.
 Outliers beyond the end of the whiskers are plotted as grey dots.}
@@
 
-\subsection*{Trait definition discrepancies and taxonomic resolution}
+Freshwater invertebrate trait databases are a valuable source of data that are freely available to researchers and that can offer opportunities for large-scale, cross-regional ecological study without the need for time-consuming and expensive field work.
+However, a lack of consistency among regional and continent-wide databases in trait definitions, trait affinity coding, and taxonomic resolution presents challenges to the use of multiple databases for a single study.
+We explored the effects of harmonising grouping features and aggregating trait affinities at different taxonomic levels from databases from four different continents on the outcomes of trait affinities and on analysis of trait–environment relationships.
+We found that despite discrepancies in trait definitions and taxonomic resolution across databases, harmonised and aggregated data were useful in identifying trait–environmental relationships, as evidenced by similar results from RDA as were found using observational data.
+Our results have implications for future multi-regional ecological studies that may benefit from the use of existing databases and provide insight into methods for harmonising traits with differing trait definitions and selecting aggregation methods that minimize either cases or ranges of differences in trait affinity scores when aggregating from higher to lower taxonomic precision.
 
-Synthesizing trait information from multiple trait databases is crucial for developing the full potential of trait-based approaches, e.g.
-for studying community trait responses to environmental gradients worldwide.
-Our attempt at harmonising invertebrate trait information from trait databases of different regions showed that harmonisation was labour-intensive because grouping features are resolved differently into traits and various codings are used to describe traits in the various databases.
-In addition, the same traits are sometimes defined differently, requiring expert knowledge to reclassify these traits (e.g.
-the trait piercer in the Tachet database).
-Although, others have noted the lack of standardised trait terminology in freshwater ecology (\cite{baird_toward_2011, brink_traits-based_2011}), we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
+\subsection{Harmonising trait databases}
+
+Synthesizing trait information from multiple trait databases is crucial for developing the full potential of trait-based approaches, such as for studying community trait responses to environmental gradients across geographic regions.
+Others have noted the lack of standardised trait terminology in freshwater ecology (\cite{baird_toward_2011, brink_traits-based_2011}), but we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
+Our experience can offer some insight into the need for, and process of, harmonising invertebrate trait information from trait databases of different regions.
+Some of the challenges we found were that grouping features were resolved differently into traits in different databases and that various codings (fuzzy, categorical, binary) were used to describe traits.
+In addition, the same traits were sometimes defined differently, requiring expert knowledge to reclassify these traits (e.g.
+the trait piercer).
+Missing information was another challenge.
+We aimed to use most of the available invertebrate trait information for different regions to establish harmonised grouping feature datasets, but the availability of trait information varied strongly across grouping features and databases.
+For instance, there was extensive information available for grouping features that are often used in trait–environment studies, such as feeding mode and respiration, but there was surprisingly little information on body form, a trait that is relatively easy to determine.
+
 To resolve definition discrepancies and facilitate data synthesis in the future, terminological standards are needed.
-Harmonised definitions and concepts of traits have been developed in the past for other organism groups, e.g.
-for plants with the \textit{Thesaurus Of Plant characteristics} (TOP) initiative (\cite{garnier_towards_2017}).
+Harmonised definitions and concepts of traits have been developed in the past for other organism groups, such as for plants with the \textit{Thesaurus of Plant Characteristics} (TOP) initiative (\cite{garnier_towards_2017}).
 The core of this harmonisation initiative is to provide standardised trait definitions and to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field.
 Such initiatives could be a role model for freshwater ecologists to establish unambiguous terminologies for invertebrate traits.
-The existing freshwater invertebrate trait databases could be linked through standardised terminologies or ontologies, as suggested by \citet{baird_toward_2011} a decade ago.
+The existing freshwater invertebrate trait databases could be linked through standardised terminologies or ontologies, as suggested by \citet{baird_toward_2011}.
 By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS), providers of invertebrate trait data could connect their traits to such ontologies (\cite{schneider_towards_2019}).
-Once standardised trait definitions are established, these will improve trait data sharing, trait data processing when working with multiple trait databases, and ultimately interpretation of the derived results.
-
-Our analysis aimed to use most of the available invertebrate trait information for different regions to establish harmonised grouping feature datasets.
-Although many taxa are covered in the trait databases from which we extracted our datasets, the availability of trait information varies strongly across grouping features and taxonomic resolution differs between databases.
-Much information is available for grouping features that are often used in trait-environment studies, such as feeding mode and respiration.
-Surprisingly, there is little information on body form, a trait that is relatively easy to determine.
-
-While trait information from Europe and New Zealand was mainly at species-level, considerable portions of trait data from North America and Australia were at genus or family-level.
-Assigned traits at family-level may not reflect the real trait diversity within a taxon, for example for the large, ecologically diverse family Chironomidae (\cite{serra_synthesising_2016}).
-However, species-level identification can be complicated, time-consuming and expensive (\cite{marshall_taxonomic_2006, resh_which_2008}).
-Consequently, trait information at family-level has been widely used by freshwater ecologists, for example in bioassessment (\cite{beketov_spear_2009}).
+Once standardised trait definitions are established, these will improve trait data sharing, trait data processing when working with multiple trait databases, and, ultimately, interpretation of the derived results.
 
@@
 
-\subsection*{Trait aggregation}
+\subsection*{Trait aggregation method selection}
 
-When trait values are only available at species-level and observational data are at less precise taxonomic levels, various trait aggregation methods have been used by researchers.
-We aggregated traits from an Australian and a North American trait dataset to family-level using 5 different aggregation methods and compared the results to traits originally assigned at family-level for these regions.
-Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is.
-Aggregation of trait information at species or genus-level to a point estimate at family-level suggests a precision that is not necessarily present, especially not for traits with a high variability or if trait information at species-level is missing.
-Some traits can vary strongly at more precise taxonomic levels than the family-level.
+Trait data for freshwater invertebrates is often resolved to a variety of taxonomic levels because species-level identification can be complicated, time-consuming, and expensive (\cite{marshall_taxonomic_2006, resh_which_2008}).
+Consequently, trait information at family level has been widely used by freshwater ecologists, for example in bioassessment (\cite{beketov_spear_2009}).
+However, assigned traits at family level may not reflect the real trait diversity within, for example, a taxon in the large, ecologically diverse family Chironomidae (\cite{serra_synthesising_2016}).
+Additionally, various trait aggregation methods have been used by researchers to allow comparison among traits at different taxonomic levels.
+Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait is for a particular family.
+Aggregation of trait information at species or genus level to a point estimate at family level suggests a precision that is not necessarily present, especially not for traits with high variability or if trait information at species level is missing.
+Indeed, some traits can vary strongly at more precise taxonomic levels than the family level.
 For example, \citet{monaghan_improving_2013} found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction.
-Further, studies focusing on the lability of traits, i.e.
-how much traits are constrained by phylogeny, found that traits of ecological preferences (e.g.
-thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable (\cite{poff_functional_2006, wilkes_traitbased_2020}).
-If trait aggregation is necessary, however, our study can give guidance, under which circumstances the choice of aggregation method may be important.
-The 5 aggregation methods we tested use either the mean or the median and different weightings.
-Our results indicated that 1) the median aggregation methods compared to mean aggregation methods were often closer to the assigned traits at family-level and 2) the different weightings tested exerted a minor impact on the aggregated trait affinities.
-We obtained for both datasets more strongly differing cases for mean aggregation methods, irrespective of the weighting.
-In the Australian dataset, the amount of differing cases was slightly higher for the mean aggregation methods (23 \%) than for median aggregation methods (16 to 18 \% differing cases).
-In the North American dataset, mean aggregation methods yielded 47 \% cases being different to the assigned traits, a value much higher in comparison to the median aggregation methods (between 15 and 18 \%).
-When differences occurred between median aggregation methods and assigned traits, these differences were greater compared to the mean aggregation methods, particularly for the North American dataset.
-There, the mean absolute differences for the median aggregations were twice as high (0.63 - 0.7) compared to the mean aggregations (0.3 - 0.31).
-These differences can be explained by the binary coding used in the North American trait dataset and by the assigned traits.
-As a result, traits have affinities of either 1 or 0.
-Therefore, traits of a particular grouping feature showed in most cases a higher difference in trait affinities to each other than if they were fuzzy coded.
-Using the median to aggregate binary coded taxa often resulted in a value of 0 or 1, while using the mean yielded values between 0 and 1.
+Further, studies focusing on the lability of traits, (i.e.
+how much traits are constrained by phylogeny), found that traits of ecological preferences (e.g.
+thermal preference), body size, resistance forms, and, to a lesser extent, feeding mode are labile, and thus possibly highly variable (\cite{poff_functional_2006, wilkes_traitbased_2020}).
+
+If trait aggregation is necessary, however, our study can offer insight about the circumstances under which the choice of aggregation method may be important.
+The 5 aggregation methods we tested used either the mean or the median and different weightings to assign family-level affinities.
+Our results indicated that for both the Australian and North American datasets (1) the median aggregation methods provided affinities that were often closer to the assigned traits than were those provided by the mean aggregation methods and (2) the different weighting approaches exerted only a minor influence on the aggregated trait affinities.
+However, when differences occurred between median aggregation methods and assigned traits, these differences were greater in absolute value compared with the mean aggregation methods, particularly for the North American dataset where mean absolute differences for median aggregations were twice as high as for mean aggregations.
+This pattern of greater differences for median than mean aggregations can, in large part, be explained by the binary coding used in the North American trait dataset and by the assigned traits.
+Binary coded traits have affinities of either 1 or 0; therefore, traits of a particular grouping feature showed, in most cases, a higher difference in trait affinities to each other than if they were fuzzy coded.
+Median-aggregated binary-coded taxa often resulted in a value of 0 or 1, whereas mean aggregation often yielded values between 0 and 1.
 Thus, using the median led for the North American dataset either to agreement with the assigned traits or to higher differences compared to the mean aggregation methods.
+This pattern inherent in using median-aggregation methods to aggregate binary-coded data should be considered when researchers choose methods to resolve affinities at different taxonomic levels.
 
-The weightings explored in this analysis should lead to different aggregated trait affinities in cases where genera within a family have different numbers of species.
-In fact, the simulation results indicated that for a particular family where one genus has a much larger number of species compared to the other genera, weighting the number of taxa can lead to different aggregated trait affinities, especially for traits with higher levels of variance.
-However, in the comparison of the trait aggregation methods to assigned traits the number of differing cases and the mean absolute differences in trait affinities were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weightings on the aggregation methods.
-Also, the distributions of absolute trait affinity differences to assigned traits were relatively similar for the mean aggregation methods and the median aggregation methods, respectively.
-The minor impact on trait aggregation of the weightings may be explained by the fact that a considerable portion of taxa had low numbers of genera or species.
-Of the taxa that were compared from the North American trait dataset, 14 \% were identified at family and 62 \% at genus-level, 52 \% comprised 5 or fewer genera, and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
-In the Australian dataset, 21 \% of the compared taxa were identified at family, 40 \% at genus, and 39 \% at species-level, 68 \% of the taxa contained 5 or fewer genera, and 40 \% just one genus (Figure \ref{fig:tax_hierarchy_AUS}).
-Hence, these results could change when more trait information at species-level becomes available.
+We expected that, in addition to averaging measure, different weighting approaches to aggregation (i.e., equal weight to each taxon, equal weight to each genus, or weighted by number of species) would affect affinities for families with varying taxonomic hierarchical structure.
+However, we found that although taxonomic structural unevenness appeared to produce variation in affinities among weighting approaches, especially for a family where one genus had a much larger number of species than its other genera, trait variability had a greater effect on the range of affinities (i.e., greater ranges of affinities at higher levels of variance) and on the differences in affinities between weighting methods.
+Also, the number of differing cases and the mean absolute differences in trait affinities, as well as the distributions of absolute trait affinity differences to assigned traits, were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weighting approach on the aggregation outcomes.
+The minor impact of the weighting approaches on trait aggregation may be explained by the fact that a considerable portion of taxa had low numbers of genera or species.
+Of the taxa that were compared from the North American trait dataset, 14 \% were identified at family and 62 \% at genus level, 52 \% comprised five or fewer genera, and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
+In the Australian dataset, 21 \% of the compared taxa were identified at family, 40 \% at genus, and 39 \% at species level, 68 \% of the taxa contained five or fewer genera, and 40 \% just one genus (Figure \ref{fig:tax_hierarchy_AUS}).
+Hence, these results could change when more species-level trait information becomes available.
+Our findings show that the choice of aggregation method may matter less when taxonomic hierarchical structure is fairly even and traits are less variable, but the \textit{stepwise\_agg\textsubscript{median}} method tended to produce the widest range in affinities, especially with high taxonomic unevenness and high trait variability.
 

### 2021-02-10 Paper/Results/SI.tex
10.02.: Brook Edits Pt.6

@@
 
-\subsubsection*{Taxonomic hierarchy in the trait datasets used for comparisons with assigned traits at family-level}
+\subsubsection*{Taxonomic hierarchy in the trait datasets used for comparisons with assigned traits at family level}
 \label{sec:taxonomic_hierarchy}
@@
     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NOA.png}
-    \caption{Number of genera per family and species per genus for those families of the North American trait dataset that have been compared to assigned traits at family level.
+    \caption{Number of genera per family and species per genus for those families of the North American trait dataset that have been compared with assigned traits at family level.
 For better visual display only families with more than 15 genera are displayed.}

### 2021-02-10 Paper/Draft_harmonization_paper.tex
09.02: Slight edit

@@
 
-\subsection{Harmonising trait databases}
+\subsection*{Harmonising trait databases}
 
@@
 
-\subsection*{Trait aggregation method selection}
+\subsection*{Trait aggregation method choice}
 
-Trait data for freshwater invertebrates is often resolved to a variety of taxonomic levels because species-level identification can be complicated, time-consuming, and expensive (\cite{marshall_taxonomic_2006, resh_which_2008}).
+Observational data for freshwater invertebrates are often resolved to a variety of taxonomic levels because species-level identification can be complicated, time-consuming, and expensive (\cite{marshall_taxonomic_2006, resh_which_2008}).
 Consequently, trait information at family level has been widely used by freshwater ecologists, for example in bioassessment (\cite{beketov_spear_2009}).
@@
 
-\subsection*{Grouping feature harmonisation}
+\subsection*{Using harmonised and aggregated datasets for ecological research}
 
-We explored how using harmonised grouping features and aggregated traits might change the results of trait-environment relationships.
-We are not aware of other studies that compared trait-environment relationships using harmonised and non harmonised data.
-The re-analysis of the data on salinisation effects on biological traits from \citet{szocs_effects_2014} yielded only slightly different results compared to the original study, i.e.
-some of the traits that had responded in the original analysis did not respond in the re-analysis.
-These non-responsive traits were those closest to the criterion that defined when a trait was associated with either higher or lower salinity, namely feeding mode shredder, respiration gills, and life cycle duration traits.
-Feeding mode shredder was the only trait that was non-responsive when using harmonised (but not aggregated) as well as when using aggregated data.
-This result was likely due to the harmonisation procedure, when this trait was amalgamated based on three traits (miner, xylophagus, and shredder).
-Consequently, the trait affinities in the original data had a higher mean and standard deviation than in the aggregated and harmonised data (Table \ref{tab:SI_resp_traits_summary_stats}), suggesting that the signal in the original data was weakened by the harmonisation.
-%This might be the reason that shredders showed a less strong reaction to the salinity gradient in the re-analysis.
--> Kicked out by CM
-These findings show that if harmonisation is necessary, harmonised and non-harmonised data, if available, should be compared and possible averaging effects should be considered in further analyses.
-The fact that the family-level aggregated traits used in the re-analysis showed similar results compared to the original analysis agrees with previous findings that family-level traits can be sensitive enough to detect environmental impacts (\cite{beketov_spear_2009}).
-% Cite another paper that uses family-level trait data
-% Although species-level traits are expected to result in more precise results when investigating trait-environment relationships.
+By reanalysing trait–environment relationships identified in \citet{szocs_effects_2014} with our harmonised and family-level aggregated datasets, we have illustrated the potential for the use of harmonised and aggregated data in ecological research.
+As far as we are aware, ours is the first study to compare trait–environment relationships using harmonised and non-harmonised data.
+Our re-analysis of the data on salinisation effects on biological traits yielded only slightly different results compared with the original study, which agrees with previous findings that family-level traits can be sensitive enough to detect environmental impacts (\cite{beketov_spear_2009}).
+However, some of the traits that had responded in the original analysis did not respond in the re-analysis: feeding mode shredder, respiration gills, and life-cycle duration traits.
+There are several possible reasons for these discrepancies.
+The non-responsive traits were those closest to the threshold for association with either higher or lower salinity, and so the precision lost through trait harmonisation may have decreased our ability to detect a relatively weak association.
+Feeding mode shredder was the only trait that was non-responsive when using harmonised (but not aggregated) data as well as when using aggregated data.
+This result was likely because of the harmonisation procedure, when this trait was combined based on three traits (miner, xylophagus, and shredder).
+Consequently, the trait affinities in the original data had a higher mean and standard deviation than in the harmonised and aggregated data (Table \ref{tab:SI_resp_traits_summary_stats}), suggesting that the signal in the original data was weakened by harmonisation.
+Following this result, we suggest that if harmonisation is necessary, harmonised and non-harmonised data, if available, should be compared, and possible averaging effects should be considered in further analyses.
+However, our results illustrate that where site-level data are not available, harmonised and aggregated datasets may be useful in identifying at least the strongest associations between traits and environmental conditions.
 
@@
 
-Although comprehensive freshwater invertebrate trait databases have been developed for several regions in the past, data synthesis is difficult because of discrepancies in trait definitions.
-By providing an overview of these definition discrepancies we have set a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
-A consent on standard terminology and the subsequent development of ontologies are the next steps to facilitate trait-based analysis at large geographical scales.
+Although comprehensive freshwater invertebrate trait databases have been developed for several regions in the past, data synthesis presents challenges because of discrepancies in trait definitions, coding of trait affinities, and taxonomic resolution.
+By providing an overview of definition discrepancies, we have set a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
+Agreement on standard terminology and the subsequent development of ontologies are the next steps to facilitate trait-based analysis at large geographical scales.
 As our analysis showed, some grouping features might need to be re-classified to fit into such a standardised terminology.
-We could show that trait affinities resulting from fuzzy coding and binary coding can be used together, but a uniform coding of traits is another problem that should be addressed during trait standardisation.
+Although we showed that trait affinities from fuzzy and binary coding can be used together, we also recommend that a uniform coding of traits should be addressed during trait standardisation.
 
-As ecological knowledge increases in the future, and with the aid of new  methods such as computer vision for species and trait identification (\cite{hoye_deep_2020}), more observational and trait data at species-level may become available in the future, reducing the need for trait aggregation.
-However, if traits need to be aggregated we showed that trait aggregation is often in agreement with expert assignments, especially aggregation approaches using the median.
-Ultimately, the question which aggregation method is the objectively best measure cannot be answered.
-Nevertheless, we make the following recommendations for situations when trait aggregation is necessary.
-1) The aggregation method will tend to have little effect except for highly variable traits and taxa where a few genera have a high number of species.
-2) The coding used to describe traits (binary, fuzzy) should be considered, because median and mean aggregations can yield very different results for binary coded traits.
-3) Weighting trait information based on the taxa present in the database used does not seem to have much influence except for families with few genera that have a high number of species.
-4) A measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
-% OLD: No matter which aggregation approach is chosen, for future studies in which researchers must aggregate traits,....
+As ecological knowledge increases, and with the aid of new  methods such as computer vision for species and trait identification (\cite{hoye_deep_2020}), more observational and species-level trait data at may become available in the future, reducing the need for trait aggregation.
+However, we showed that trait aggregation is often in agreement with expert assignments, especially through aggregation approaches that use the median.
+
+No aggregation method is objectively best, and except for cases where traits are highly variable and taxonomic hierarchical structure is highly uneven, choice of aggregation method does not appear to be influential on the outcome.
+Weighting trait information based on the taxa present in the database used does not seem to have much influence except .
+However, we recommend that the type of coding used to describe traits (binary, fuzzy) should be considered, because median and mean aggregations can yield very different results for binary-coded traits.
+We also suggest that a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
+Through the use of carefully synthesised data from freshwater invertebrate trait databases, while acknowledging the limitations inherent in harmonised and aggregated data, the ability to investigate a wide range of large-scale ecological questions is enhanced.
 

### 2021-02-10 Paper/Draft_harmonization_paper.tex
10.02: Brookes Edits finished

@@
 Moreover, it is uncertain how harmonising varying trait definitions among databases might influence identification of trait-environment relationships.
-In addition, is that taxonomic resolution between observational taxonomic data and trait data can differ, making aggregation of traits necessary.
+In addition, taxonomic resolution between observational taxonomic data and trait data can differ, making aggregation of traits necessary.
 At present, it is unknown how different trait aggregation approaches compare with expert-assigned trait affinities.
@@
 Thus, we use the term grouping feature in place of the term trait, and the term trait instead of trait state, modality or trait category.
-% Ben suggest here: For  example  e.g., predator, shredder, etc. Are traits of the grouping feature ..... and removing predator, shredder, etc. from the sentence above.
 
@@
 
+% Other alternative from Brooke: These challenges when working with or synthesizing trait data motivated us to assess the characteristics and comparability of freshwater invertebrate trait data contained in disparate databases.
+We aimed to explore methods of improving the comparability of trait data across databases, despite differences in trait grouping-feature definitions, affinity score coding, and taxonomic level of data, through two study objectives: (1) to investigate the plausibility of comparing across databases from different geographic regions by providing harmonised datasets from Europe, North America, Australia, and New Zealand; and (2) to compare the influence of different trait aggregation methods on the characterisation of trait–environment relationships.
+
 \newpage
@@
 
-To address our study objectives, we took a multi-prong approach to describing, combining, and assessing multiple sources of freshwater invertebrate data that differed in trait grouping-feature definitions and taxonomic resolution.
+To address our study objectives, we took a multi-prong approach to describing, combining, and assessing multiple sources of freshwater invertebrate data that differed in grouping-feature definitions and taxonomic resolution.
 %Version from Brooke: As a basis for evaluating the comparability of freshwater invertebrate databases, we developed four novel invertebrate trait datasets by harmonising seven grouping features from existing trait databases.
@@
 Abbreviations: EU, European; NOA, North American; AUS, Australian; NZ, New Zealand.
+}
 \end{minipage}
@@
 
-The comparison of family-level aggregated trait affinities with those assigned by experts for the Australian and North American databases showed that aggregation method (median or mean) had a greater effect than overall approach (direct, stepwise, or weighted) in whether trait affinities differed from those assigned by experts.
+The comparison of family-level aggregated trait affinities with those assigned by experts for the Australian and North American databases showed that aggregation method (median or mean) had a greater effect than the overall approach (direct, stepwise, or weighted by the number of species) in whether trait affinities differed from those assigned by experts.
 
@@
 
-Our simulation results showed that both taxonomic hierarchical structure and trait variability affected aggregated trait affinities and that aggregation method mattered in terms of the ranges of trait affinities produced over simulation replicates.
+Our simulation results showed that both taxonomic hierarchical structure and trait variability affected aggregated trait affinities, although only to a small degree, and that aggregation method mattered in terms of the ranges of trait affinities produced over simulation replicates.
 The effect of taxonomic hierarchy differed across aggregation methods, but, as we expected, the produced range of trait affinities increased with increasing trait variability for all aggregation methods (Figure \ref{fig:overview_sim_results}).
@@
   Comparisons: \newline
-  1) \textit{direct\_agg (median)} - \textit{Stepwise\_agg (mean)} \newline
-  2) \textit{Direct\_agg (median)} - \textit{Weighted\_agg} \newline
-  3) \textit{Stepwise\_agg (mean)} - \textit{Stepwise\_agg (median)} \newline
-  4) \textit{Stepwise\_agg (mean)} - \textit{Weighted\_agg} \newline  
-  5) \textit{Direct\_agg (mean)} - \textit{Stepwise\_agg (median)} \newline
-  6) \textit{Direct\_agg (median)} - \textit{Stepwise\_agg (median)} \newline
-  7) \textit{Stepwise\_agg (median)} - \textit{Weighted\_agg} \newline
+  1) \textit{direct\_agg (median)} - \textit{stepwise\_agg (mean)} \newline
+  2) \textit{direct\_agg (median)} - \textit{weighted\_agg} \newline
+  3) \textit{stepwise\_agg (mean)} - \textit{stepwise\_agg (median)} \newline
+  4) \textit{stepwise\_agg (mean)} - \textit{weighted\_agg} \newline  
+  5) \textit{direct\_agg (mean)} - \textit{stepwise\_agg (median)} \newline
+  6) \textit{direct\_agg (median)} - \textit{stepwise\_agg (median)} \newline
+  7) \textit{stepwise\_agg (median)} - \textit{weighted\_agg} \newline
   }
@@
 We expected that, in addition to averaging measure, different weighting approaches to aggregation (i.e., equal weight to each taxon, equal weight to each genus, or weighted by number of species) would affect affinities for families with varying taxonomic hierarchical structure.
-However, we found that although taxonomic structural unevenness appeared to produce variation in affinities among weighting approaches, especially for a family where one genus had a much larger number of species than its other genera, trait variability had a greater effect on the range of affinities (i.e., greater ranges of affinities at higher levels of variance) and on the differences in affinities between weighting methods.
+However, we found through simulations that although taxonomic structural unevenness appeared to produce variation in affinities among weighting approaches, especially for a family where one genus had a much larger number of species than its other genera, trait variability had a greater effect on the range of affinities (i.e., greater ranges of affinities at higher levels of variance) and on the differences in affinities between weighting methods.
 Also, the number of differing cases and the mean absolute differences in trait affinities, as well as the distributions of absolute trait affinity differences to assigned traits, were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weighting approach on the aggregation outcomes.
@@
 No aggregation method is objectively best, and except for cases where traits are highly variable and taxonomic hierarchical structure is highly uneven, choice of aggregation method does not appear to be influential on the outcome.
-Weighting trait information based on the taxa present in the database used does not seem to have much influence except .
+Weighting trait information based on the taxa present in the database used does not seem to have much influence except when the taxonomic hierarchical structure is highly uneven.
 However, we recommend that the type of coding used to describe traits (binary, fuzzy) should be considered, because median and mean aggregations can yield very different results for binary-coded traits.

### 2021-02-10 Paper/Draft_harmonization_paper.tex
10.02.: Small changes

@@
 
-To address our study objectives, we took a multi-prong approach to describing, combining, and assessing multiple sources of freshwater invertebrate data that differed in grouping-feature definitions and taxonomic resolution.
 %Version from Brooke: As a basis for evaluating the comparability of freshwater invertebrate databases, we developed four novel invertebrate trait datasets by harmonising seven grouping features from existing trait databases.
 We then evaluated the influence of different...
+
+To address our study objectives, we took a multi-prong approach to describing, combining, and assessing multiple sources of freshwater invertebrate data that differed in grouping-feature definitions and taxonomic resolution.
 Identified trait definitions discrepancies served as a starting point to develop four novel invertebrate trait datasets by harmonising seven grouping features from existing trait databases.
@@
 
+\newpage
+
 \subsubsection*{Effect of taxonomic hierarchy and trait variability on aggregation outcomes}
@@
   \caption{Data processing steps of the selected traits.
-Intermediate (gray) and main (orange) steps of data preparation are depicted.
+Intermediate (grey) and main (orange) steps of data preparation are depicted.
 The dashed bottom box illustrates the different trait aggregation methods (hypothetical data in the upper left corner).
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \newpage
-
-\subsubsection*{Comparison of family-level aggregated traits with family-level assigned traits}
-
-Aggregated trait affinities of the five trait aggregation methods (\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg}) were compared to trait affinities assigned at family-level by experts, which were available for Australia and North America for a subset of grouping features and taxa.
-For the Australian dataset, we compared aggregated trait affinities with assigned trait affinities resolved at family-level for the grouping features feeding mode and size using data from \citet{chessman_dissolved-oxygen_2018}.
-In \citet{chessman_dissolved-oxygen_2018} feeding mode is classified similarly as in the Australian dataset except that the trait parasite is missing.
-We conducted the comparison for the 220 families available in \citet{chessman_dissolved-oxygen_2018}.
-Considering each factor combination of family and trait (in total 8) this amounted to 1760 cases.
-
-For the North American dataset, we compared aggregated trait affinities with assigned trait affinities on family-level for the grouping features feeding mode, respiration, size, voltinism, and locomotion.
-The assigned trait affinities at family-level are part of the CONUS database and originate from expert knowledge.
-Trait information was available for 94 families of which all were present in the North American dataset (total number of cases 1598).
-The traits were on the categorical scale and were converted to binary traits prior to the comparison with aggregated trait affinities.
-
-As mentioned above, trait affinities ranged from 0 to 1.
-Hence, the maximum difference possible in trait affinities is 1 or -1 (corresponds to 100 \%).
-For convenience and to improve interpretation, we report absolute trait differences.
 
@@
 Scripts and data to reproduce the trait aggregation, comparison of aggregated and assigned traits, and the RDA analysis are located in the Github repository \url{https://github.com/KunzstLD/Trait-aggregation}.
+
+\newpage
 
@@
 However, we showed that trait aggregation is often in agreement with expert assignments, especially through aggregation approaches that use the median.
-
 No aggregation method is objectively best, and except for cases where traits are highly variable and taxonomic hierarchical structure is highly uneven, choice of aggregation method does not appear to be influential on the outcome.

### 2021-02-11 Paper/Draft_harmonization_paper.tex
11.02.: Updates on figures

@@
 
-\subsection*{Taxonomic coverage of the harmonised trait datasets}
+\subsubsection*{Taxonomic coverage of the harmonised trait datasets}
 
@@
 
-\subsection*{Completeness of trait information}
+\subsubsection*{Completeness of trait information}
 
@@
 
-\subsection*{Discrepancies in invertebrate trait definitions across databases}
+\subsubsection*{Discrepancies in invertebrate trait definitions across databases}
 
@@
 
-\subsection*{Comparison of family-level aggregated traits with family-level assigned traits}
+\subsubsection*{Comparison of family-level aggregated traits with family-level assigned traits}
 \label{sec:diff_trait_agg_chessman}
@@
 Standard deviations of absolute differences were similar for all tested aggregation methods.
-Maximum differences of 1 (i.e., the maximum possible difference) occurred for all investigated grouping features in both datasets (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
+Maximum differences of 1 (i.e., the maximum possible difference) occurred for all investigated grouping features in both datasets (Figure \ref{fig:diff_aggr_traits_combined}).
 
@@
   \centering
-  \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_chessman.png}
-  \caption{Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the Australian dataset for the grouping features feeding mode and body size.
-Violin plots - mirrored density plots - show
-  the density of the absolute trait affinity differences.
+  \includegraphics[width=16.5cm, height=12cm]{Deviances_trait_agg_combined.png}
+  \caption{Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the Australian and North American dataset.
+Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the grouping features feeding mode and body size.
+Results for the North American dataset for the grouping features locomotion, respiration, and voltinism are shown in the supporting information (Figure \ref{fig:diff_aggr_traits_pyne}).
 Absolute differences in trait affinities are depicted as grey dots.
@@
 The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.}
-  \label{fig:diff_aggr_traits_chessman}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_pyne.png}
-  \caption{Cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family level.
-Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
-For more details see Figure \ref{fig:diff_aggr_traits_chessman}.}
-  \label{fig:diff_aggr_traits_pyne}
+  \label{fig:diff_aggr_traits_combined}
 \end{figure}
@@
 
-\subsection*{Comparison of aggregation methods with varying taxonomic hierarchies and trait variability}
+\subsubsection*{Comparison of aggregation methods with varying taxonomic hierarchies and trait variability}
 
@@
 The effect of taxonomic hierarchy differed across aggregation methods, but, as we expected, the produced range of trait affinities increased with increasing trait variability for all aggregation methods (Figure \ref{fig:overview_sim_results}).
-% Ben would add:
- % as indicated by the increasing range of the boxes and wiskers with increasing standard deviation.
+% Ben would add: % as indicated by the increasing range of the boxes and wiskers with increasing standard deviation.
 
@@
 Shown are the results only for one simulated trait (T1).
-Similar results were obtained for the other simulated traits (see appendix).
+Similar results were obtained for the other simulated traits (Figure \ref{fig:overview_sim_results_T2_T3}).
 Boxplots depict results for 100 replicated simulations of each trait aggregation method.
@@
 Whiskers extend to the largest and smallest value respectively no further than 1.5 $*$ the inter-quartile range.
-Outliers beyond the end of the whiskers are plotted as grey dots.}
+Outliers beyond the end of the whiskers are plotted as grey dots.
+Trait aggregation methods are in order of least to greatest produced ranges to improve visual inspection.}
   \label{fig:overview_sim_results}
@@
 
-% Old figure:
-% \begin{sidewaysfigure}
-%   \label{fig:boxplots_scores_on_constrained_axis}
-%   \centering
-%   \includegraphics[width= 22cm, height=12cm]{Scores_on_constrained_axis_combined.pdf}
-%   \caption{RDA of traits constrained by electric conductivity for the tested methods and the original study.
-Shown are boxplots of the site scores along the conductivity axis.
-The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
-Only traits with a mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.}
-% \end{sidewaysfigure}
-
 \begin{figure}[H]
   \centering
-  \includegraphics[width=16.5cm, height=25cm]{Scores_on_constrained_axis_comb_ALT.pdf}
-\end{figure}
-\clearpage % insert a page break
-\captionof{figure}{RDA of traits constrained by electric conductivity for the tested methods and the original study.
+  \includegraphics[width=17cm, height=14.5cm]{boxplot_scores_combined.png}
+  \caption{RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{median}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
 Shown are boxplots of the site scores along the conductivity axis.
@@
 Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
-For better comparability, species scores of the original analysis were multiplied by -1.}
-\label{fig:boxplots_scores_on_constrained_axis}
+For better comparability, species scores of the original analysis were multiplied by -1.
+Results for the other aggregated methods are shown in the supporting information.
+lcd, life cycle duration; nr.cy, potential number of cycles per year}
+\end{figure}
 

### 2021-02-11 Paper/Results/SI.tex
11.02.: Updates on figures

@@
 
-\subsection*{Discrepancies in trait definitions}
+\subsection*{Harmonised trait datasets}
+
+\subsubsection*{Discrepancies in trait definitions}
 
@@
 
-% \subsection*{Differences in trait affinities obtained by trait aggregation methods com-pared to traits assigned at family-level}
+\newpage
 
-% \subsubsection*{Comparison of the trait aggregation methods with each other}
-% \label{sec:compa_aggr_methods}
+\subsection*{Comparing aggregation methods}
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Comparison_trait_agg_methods.png}
-%     \caption{Comparison of trait aggregation methods when aggregating over all traits for all datasets.
-Displayed are means of absolute differences in trait affinities with standard deviations (truncated at 0).
-Compared aggregation methods are displayed on the y-axis.
-N indicates the number of cases where differences occurred.
-Total number of cases: Australia 2223, Europe 3352, New Zealand 777, and North America 4080.}
-%     \label{fig:comp_aggr_methods}
-% \end{figure}
+\subsubsection*{Comparison of family-level aggregated traits with family-level assigned traits}
 
-%\subsubsection*{Simulation of varying taxonomic hierarchies}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=12cm]{Deviances_trait_agg_pyne.png}
+    \caption{Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the North American dataset.
+Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the grouping features locomotion, respiration, and body size.
+For more details see Figure \ref{fig:diff_aggr_traits_combined}.}
+    \label{fig:diff_aggr_traits_pyne}
+  \end{figure}
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
-%     \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
-Boxplots depict results for each trait aggregation method of 100 simulations.
-T1 to T3 are the simulated traits.}
-%     \label{fig:overview_sim_results}
-% \end{figure}
+\subsubsection*{Comparison of aggregation methods with varying taxonomic hierarchies and trait variability}
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
-%     \caption{Comparison of the results of the trait aggregation methods for every simulated dataset.
-Simulated datasets where absolute differences between aggregated trait affinities were greater than 0.1 are depicted.
-Only the comparisons are shown were differences greater than 0.1 occurred.}
-%     \label{fig:sim_indv_runs}
-% \end{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results_T2_T3.png}
+    \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
+Shown are the results for the simulated traits T2 and T3.
+Boxplots depict results for 100 replicated simulations of each trait aggregation method.
+Trait aggregation methods are in order of least to greatest produced ranges to improve visual inspection.
+For more details see Figure \ref{fig:overview_sim_results}.}
+    \label{fig:overview_sim_results_T2_T3}
+  \end{figure}
 
@@
 \label{sec:taxonomic_hierarchy}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_EU.png}
-%     \caption{Number of genera per family and species per genus for the European trait dataset. For better visual display only families with more than 10 genera are displayed.}
-%     \label{fig:tax_hierarchy_EU}
-% \end{figure}
 
@@
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{taxonomic_hierarchy_NZ.png}
-%     \caption{Number of genera per family and species per genus for the New Zealand trait dataset. For better visual display only families with more than 5 genera are displayed.}
-%     \label{fig:tax_hierarchy_NZ}
-% \end{figure}
-
-\newpage
-
-\subsection*{Re-analysis of Szöcs et al. using harmonised and aggregated grouping features}
+\subsection*{Effects of harmonisation and trait aggregation on trait-environment relationships}
 
@@
 
-%\subsection*{Re-analysis of Szöcs et al. using harmonized grouping features.}
-%\label{subsec:SI_szoecs_reanalysis}
-
-% \subsubsection*{RDA of trait composition}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{RDA_traits_harmonized.png}
-%     \caption{RDA of traits constrained by electric conductivity using harmonized grouping features.
-Boxplot of site scores along the conductivity axis ($31.44 \%$ explained variance, p = 0.001, 1000 permutations).
-Rug on the right indicates trait scores on the conductivity axis.
-Only traits with a mahalanobis distance greater than 5.02 were labeled in accordance to the procedure in Szöcs et al.
-\cite{szocs_effects_2014}.
-%     } 
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{RDA_traits_Szoecs_2014.png}
-%     \caption{RDA of traits constrained by electric conductivity.
-Boxplot of site scores along the conductivity axis ($30.09 \%$ explained variance, p = 0.001, 1000 permutations).
-Rug on the right indicates trait scores on the conductivity axis.
-Only traits with a mahalanobis distance greater than 5.02 were labeled.
-%     } 
-% \end{figure}
-
-% Not sure if the next two sections are really needed
-% Need also to run analysis again
-%\subsubsection*{Trait distribution along first RDA axis}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_harmonized.png}
-%     \caption{Trait scores on the first RDA axis for harmonized traits and traits of the grouping feature \textit{life cycle duration}.
-%     } 
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=17.5cm, height=10cm]{Trait_distrb_Szoecs_2014.png}
-%     \caption{Trait scores on the first RDA axis for the traits responding to high salinity in Szöcs et al. \cite{szocs_effects_2014}
-%     .
-%     }
-% \end{figure}
-
-\newpage
-% \subsubsection*{Linear models of trait proportions}
-
-% \textit{Linear models of trait proportions with harmonized traits:}
-% \begin{table}[ht]
-%     \centering
-%     \caption{Results of linear models for the four selected harmonized traits and life cycle duration $>$ 1 year.
-Trait proportions were logit transformed prior model building, estimates are on the logit scale.
-Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation.
-Bold values indicate statistically significant effects (p $<$ 0.05).}
-%     \label{stab:linear_models_new}
-%     \begin{tabular}{l|ccccc}
-%     \toprule[.1em]
-%     & \specialcell{Feeding mode:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell{Voltinism:\\ bi- or multivoltine} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
-%     \toprule[.1em]
-%     Intercept ($=$ upstream) & \textbf{-1.041} & \textbf{-0.486} & 0.375* & \textbf{-0.823} & 0.092\\ 
-%     Downstream & \textbf{0.926} & \textbf{0.605} & \textbf{1.376} & \textbf{1.684} & \textbf{0.854}\\ 
-%     Downstream x 2008 & -0.117 & 0.106 & -0.235 & -0.088 & -0.317\\ 
-%     Downstream x 2009 & 0.030 & -0.056 & 0.001 & 0.245 & 0.180\\ 
-%     Year 2008 & -0.167 & -0.115 & 0.033 & -0.182 & -0.151\\ 
-%     Year 2009 & 0.175 & 0.086 & -0.088 & 0.246 & 0.141\\ 
-%     \bottomrule
-%     \end{tabular}
-%     \textit{* p.value = 0.055}
-% \end{table}
-% \newline
-% \newline
-% \newline
-% \textit{Linear models of trait proportions Szöcs et al. :}
-% \begin{table}[ht]
-%     \centering
-%     \caption{Results of linear models for the five selected traits for Szöcs et al.
-\cite{szocs_effects_2014}.
-Trait proportions were logit transformed prior model building, estimates are on the logit scale.
-%     Although years were statistically not significant we kept this factor in the model to avoid temporal autocorrelation. Bold values indicate statistically
-%     significant effects (p $<$ 0.05).}
-%     \label{stab:linear_models_edi}
-%     \begin{tabular}{l|ccccc}
-%     \toprule[.1em]
-%     & \specialcell{Feeding habits:\\ shredder} & \specialcell{Life cycle duration:\\ $>$ 1 year} & \specialcell {Cycles per year:\\ $>$ 1} & \specialcell{Reproduction:\\ ovoviviparity} & \specialcell{Respiration:\\ gills} \\
-%     \toprule[.1em]
-%     Intercept ($=$ upstream) & \textbf{-0.853} & \textbf{-0.478} & \textbf{0.603} & \textbf{-0.838} & 0.111 \\ 
-%     Downstream & \textbf{0.819} & \textbf{0.594} & \textbf{1.297} & \textbf{1.679} & \textbf{0.839} \\ 
-%     Downstream x 2008 & -0.155 & 0.102 & -0.227 & -0.070 & -0.314 \\ 
-%     Downstream x 2009 & 0.073 & -0.053 & -0.020 & 0.248 & 0.176 \\ 
-%     Year 2008 & -0.122 & -0.112 & 0.026 & -0.192 & -0.154 \\ 
-%     Year 2009 & 0.167 & 0.084 & -0.104 & 0.250 & 0.139 \\ 
-%     \bottomrule
-%     \end{tabular} 
-% \end{table}
-
-% \subsubsection*{Trait proportions over time}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_harmonized.png}
-%     \caption{Proportions for the four harmonized traits that have been promoted by salinization and life cycle duration $>$ 1 year for down- and upstream sites.
-%     } 
-% \end{figure}
-
-% % Trait proportions over time
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=16.5cm, height=10cm]{Trait_proportion_Szoecs_2014.png}
-%     \caption{Proportions for five selected traits for down- and upstream sites (traits that have been promoted by salinization) from Szöcs et al. \cite{szocs_effects_2014}.} 
-% \end{figure}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=16.5cm, height=25cm]{Scores_on_constrained_axis_comb_ALT.pdf}
+\end{figure}
+  \clearpage % insert a page break
+  \captionof{figure}{RDA of traits constrained by electric conductivity for the tested methods and the original study.
+Shown are boxplots of the site scores along the conductivity axis.
+The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
+Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
+For better comparability, species scores of the original analysis were multiplied by -1.}
+\label{fig:boxplots_scores_on_constrained_axis}
 

### 2021-02-13 Paper/Draft_harmonization_paper.tex
13.02: Figure & SI update

@@
 \usepackage{longtable}
-%\usepackage[sort&compress,square,comma,authoryear]{natbib}
 \usepackage{booktabs}
@@
 \usepackage{caption}
-% \graphicspath{{/home/kunz/Dokumente/Projects/Trait_DB/Invertebrate_traits/Paper/Figures/}}
+\usepackage{authblk}
 \graphicspath{{Figures/}}
@@
 \title{Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
-\author{}%Stefan Kunz 
+\author[1]{Stefan Kunz}
+\author[2]{Ben J. Kefford}
+\author[3]{Leon Metzeling}
+\author[4]{Astrid Schmidt-Kloiber}
+\author[4]{Wolfram Graf}
+\author[5]{Philippe Usseglio-Polatera}
+\author[6]{Christoph D. Matthaei}
+\author[7]{Charles P. Hawkins}
+\author[8]{N. LeRoy Poff}
+\author[9]{Laura Twardochleb}
+\author[1]{Ralf B. Schäfer}
+\affil[1]{Institute for Environmental Sciences, University of Koblenz-Landau, Landau, Germany}
+\affil[2]{Centre for Applied Water Science, Institute for Applied Ecology, University of Canberra, Canberra, Australia}
+\affil[3]{Environment Protection Authority Victoria, Applied Sciences Division, Macleod, Australia}
+\affil[4]{Institute of Hydrobiology and Aquatic Ecosystem Management, University of Natural Resources and Life Sciences Vienna (BOKU), Vienna, Austria}
+\affil[5]{University of Lorraine, CNRS, LIEC, Metz, France}
+\affil[6]{Department of Zoology, University of Otago, Dunedin, New Zealand}
+\affil[7]{Department of Watershed Sciences and the Ecology Center, Utah State University, Logan, USA}
+\affil[8]{Department of Biology, Colorado State University, Fort Collins, USA}
+\affil[9]{Department of Fisheries and Wildlife, Michigan State University, East Lansing, USA}
 \date{}
@@
 \maketitle
+
+\newpage
 
@@
 The trait aggregation methods we compared used either the mean or the median and different weightings.
-%Thereby, we simulated how taxonomic resolution and trait variability can change the result of different aggregation approaches.
 We further explored the effects of harmonisation and trait aggregation by re-analysing data from a case study.
@@
 This method weights each genus according to its number of species in the trait datasets, regardless of whether information was available for every used grouping feature (Figure \ref{fig:data_proc_overview}).
+When we refer to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg} together we denote these methods as mean aggregation methods and when we refer to \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}} together, we denote these methods as median aggregation methods.
 
@@
 To evaluate the effect of the five trait aggregation methods
-(\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, 
-\textit{stepwise\_agg\textsubscript{median}},
-\textit{stepwise\_agg\textsubscript{mean}},
-\textit{weighted\_agg}) on the assignment of trait affinity scores, we compared our aggregated affinities with trait affinities assigned at family level by experts.
+(\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, \textit{weighted\_agg}) on the assignment of trait affinity scores, we compared our aggregated affinities with trait affinities assigned at family level by experts.
 Expert-assigned trait data were available for a subset of grouping features and taxa for Australia (\cite{chessman_dissolved-oxygen_2018}) and North America (CONUS database), so we conducted this comparison only for these two datasets.
@@
 
-We re-analysed the \citet{szocs_effects_2014} study by performing a RDA with harmonised grouping features from the dataset for Europe and additionally with traits that we aggregated to family level with the five aggregation methods described above.
+We re-analysed the \citet{szocs_effects_2014} study by performing a RDA with harmonised grouping features from the dataset for Europe and with traits that we aggregated to family level with the five aggregation methods described above.
 We used all 21 grouping features from the original study, but replaced 6 with harmonised grouping features from our European trait dataset, namely: size, feeding mode, locomotion, oviposition, respiration, and voltinism.
@@
 The percentage of differing cases of aggregated versus assigned trait affinities varied by method between 16.2 and 22.9 \% for the Australian dataset and between 15.3 and 47 \% for the North American dataset (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
-In general, median aggregation methods yielded fewer cases with differences compared with mean and weighted aggregation methods.
+In general, median aggregation methods yielded fewer cases with differences compared with mean aggregation methods.
 However, median aggregation methods produced, on average, greater absolute differences for both datasets.
@@
 Our re-analysis of the \citet{szocs_effects_2014} study on the effects of salinisation on invertebrate traits showed that the use of harmonised and aggregated trait data may be useful for ecological studies on trait–environment relationships.
-Overall, harmonised trait data and all aggregation methods produced similar distributions of RDA species scores (\ref{fig:violin_plot_species_sc}) compared with the original analysis, and they resulted in similar, but fewer, traits that distinguished upstream and downstream sites than the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
+Overall, harmonised trait data and all aggregation methods produced similar distributions of RDA species scores (\ref{fig:violin_plot_species_sc}) compared with the original analysis, and they resulted in similar, but fewer, traits that distinguished upstream and downstream sites than the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
 
-RDA using harmonised, but not aggregated, grouping features identified some, but not all, of the same traits that were identified by the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
+RDA using harmonised, but not aggregated, grouping features identified some, but not all, of the same traits that were identified by the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
 The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (higher salinity) were characterised by the traits: ovoviviparity, multivoltinism, long life-cycle duration ($> 1$ year), shredder, and gill respiration, whereas RDA with the harmonised data identified the first three traits but did not include shredder or gill respiration traits.
@@
 
-RDA using harmonised traits that were aggregated to family level also produced results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplots_scores_on_constrained_axis}).
+RDA using harmonised traits that were aggregated to family level also produced results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
 The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg} characterised the downstream sites with the same traits as the original analysis except the trait shredder.
@@
 For better comparability, species scores of the original analysis were multiplied by -1.
-Results for the other aggregated methods are shown in the supporting information.
+Results for the other aggregated methods are shown in the supporting information (Figure \ref{fig:boxplots_scores_on_constrained_axis_REMAIN}).
 lcd, life cycle duration; nr.cy, potential number of cycles per year}
+  \label{fig:boxplot_scores_on_constrained_axis}
 \end{figure}
@@
 
-As ecological knowledge increases, and with the aid of new  methods such as computer vision for species and trait identification (\cite{hoye_deep_2020}), more observational and species-level trait data at may become available in the future, reducing the need for trait aggregation.
+As ecological knowledge increases, and with the aid of new  methods such as computer vision for species and trait identification (\cite{hoye_deep_2020}), more observational and species-level trait data may become available in the future, reducing the need for trait aggregation.
 However, we showed that trait aggregation is often in agreement with expert assignments, especially through aggregation approaches that use the median.
-No aggregation method is objectively best, and except for cases where traits are highly variable and taxonomic hierarchical structure is highly uneven, choice of aggregation method does not appear to be influential on the outcome.
+No aggregation method is objectively the best, and except for cases where traits are highly variable and taxonomic hierarchical structure is highly uneven, choice of aggregation method does not appear to be influential on the outcome.
 Weighting trait information based on the taxa present in the database used does not seem to have much influence except when the taxonomic hierarchical structure is highly uneven.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Data availability statement}
+
+Harmonised invertebrate trait datasets for Australia, Europe, North America and New Zealand are deposited \textit{Zenondo/Github?}
+
+\section*{Acknowledgments}
+
+% Verena Schreiner body form traits?
+Stefan Kunz acknowledges that this paper was part of his PhD thesis. The project is funded by the German research society (DFG \textit{insert project number}).
+
+\section*{Conflict of interest}
+
+The authors declare no conflict of interest.
+
 \newpage

### 2021-02-13 Paper/Draft_harmonization_paper.tex
13.02: 2nd Update Paper & figures

@@
   \centering
+  % \includegraphics[width=22cm, height=28cm]{Flowchart_methods.pdf}
   \subfile{Flowchart/Flowchart_methods.tex}
@@
 \end{table}
+\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
+  \centering
+  Abbreviations: Min., Minimum; Max., Maximum; abs., absolute; SD, Standard deviation.
+  }
+  \end{minipage}
 
@@
 The blue dot indicates the mean of absolute differences, and the error bars show the standard deviation.
-The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.}
+The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.
+Abbreviations: AUS, Australia; NOA, North America.}
   \label{fig:diff_aggr_traits_combined}
@@
 Results for the other aggregated methods are shown in the supporting information (Figure \ref{fig:boxplots_scores_on_constrained_axis_REMAIN}).
-lcd, life cycle duration; nr.cy, potential number of cycles per year}
+Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.}
   \label{fig:boxplot_scores_on_constrained_axis}
@@
 % Verena Schreiner body form traits?
-Stefan Kunz acknowledges that this paper was part of his PhD thesis. The project is funded by the German research society (DFG \textit{insert project number}).
+We thank Brooke Cassell for technical editing of the manuscript. The project is funded by the German research society (DFG \textit{insert project number}).
 

### 2021-02-13 Paper/Flowchart/Flowchart_methods.tex
13.02: 2nd Update Paper & figures

@@
                 decorations.pathreplacing,
+                %calligraphy,
                 angles,
@@
       \draw[->] (conversionPerc.east) -- (traitAgg.west);
-      \draw[arrow1] (traitAgg.south) to [out=200,in=40] (frameExample.north);
-      \draw[arrow1] (traitAgg.south) to [out=360,in=80] (frameExample.east);
+      %\draw[arrow1] (traitAgg.south) to [out=200,in=40] (frameExample.north);
+      %\draw[arrow1] (traitAgg.south) to [out=360,in=80] (frameExample.east);
+      \draw [decorate,decoration={brace, amplitude=20pt}, line width = 2pt](2.9, -4) -- (7.1, -4);
       \draw[->] (directAgg.south) -- (tab_direct_agg.north);

### 2021-02-13 Paper/Draft_harmonization_paper.tex
Updates from Overleaf

--- 2021-02-11 Paper/Draft_harmonization_paper.tex
@@
 
-\subsubsection*{Taxonomic coverage of the harmonised trait datasets}
+\subsection*{Taxonomic coverage of the harmonised trait datasets}
 
@@
 
-\subsubsection*{Completeness of trait information}
+\subsection*{Completeness of trait information}
 
@@
 
-\subsubsection*{Discrepancies in invertebrate trait definitions across databases}
+\subsection*{Discrepancies in invertebrate trait definitions across databases}
 
@@
 
-\subsubsection*{Comparison of family-level aggregated traits with family-level assigned traits}
+\subsection*{Comparison of family-level aggregated traits with family-level assigned traits}
 \label{sec:diff_trait_agg_chessman}
@@
 Standard deviations of absolute differences were similar for all tested aggregation methods.
-Maximum differences of 1 (i.e., the maximum possible difference) occurred for all investigated grouping features in both datasets (Figure \ref{fig:diff_aggr_traits_combined}).
+Maximum differences of 1 (i.e., the maximum possible difference) occurred for all investigated grouping features in both datasets (Figure \ref{fig:diff_aggr_traits_chessman} and Figure \ref{fig:diff_aggr_traits_pyne}).
 
@@
   \centering
-  \includegraphics[width=16.5cm, height=12cm]{Deviances_trait_agg_combined.png}
-  \caption{Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the Australian and North American dataset.
-Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the grouping features feeding mode and body size.
-Results for the North American dataset for the grouping features locomotion, respiration, and voltinism are shown in the supporting information (Figure \ref{fig:diff_aggr_traits_pyne}).
+  \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_chessman.png}
+  \caption{Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the Australian dataset for the grouping features feeding mode and body size.
+Violin plots - mirrored density plots - show
+  the density of the absolute trait affinity differences.
 Absolute differences in trait affinities are depicted as grey dots.
@@
 The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.}
-  \label{fig:diff_aggr_traits_combined}
+  \label{fig:diff_aggr_traits_chessman}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=16.5cm, height=10cm]{Deviances_trait_agg_pyne.png}
+  \caption{Cases (factor combination investigated families and traits) where differences occurred between aggregated traits and traits assigned at family level.
+Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the North America dataset for the grouping features feeding mode, locomotion, respiration, body size and voltinism.
+For more details see Figure \ref{fig:diff_aggr_traits_chessman}.}
+  \label{fig:diff_aggr_traits_pyne}
 \end{figure}
@@
 
-\subsubsection*{Comparison of aggregation methods with varying taxonomic hierarchies and trait variability}
+\subsection*{Comparison of aggregation methods with varying taxonomic hierarchies and trait variability}
 
@@
 The effect of taxonomic hierarchy differed across aggregation methods, but, as we expected, the produced range of trait affinities increased with increasing trait variability for all aggregation methods (Figure \ref{fig:overview_sim_results}).
-% Ben would add: % as indicated by the increasing range of the boxes and wiskers with increasing standard deviation.
+% Ben would add:
+ % as indicated by the increasing range of the boxes and wiskers with increasing standard deviation.
 
@@
 Shown are the results only for one simulated trait (T1).
-Similar results were obtained for the other simulated traits (Figure \ref{fig:overview_sim_results_T2_T3}).
+Similar results were obtained for the other simulated traits (see appendix).
 Boxplots depict results for 100 replicated simulations of each trait aggregation method.
@@
 Whiskers extend to the largest and smallest value respectively no further than 1.5 $*$ the inter-quartile range.
-Outliers beyond the end of the whiskers are plotted as grey dots.
-Trait aggregation methods are in order of least to greatest produced ranges to improve visual inspection.}
+Outliers beyond the end of the whiskers are plotted as grey dots.}
   \label{fig:overview_sim_results}
@@
 
+% Old figure:
+% \begin{sidewaysfigure}
+%   \label{fig:boxplots_scores_on_constrained_axis}
+%   \centering
+%   \includegraphics[width= 22cm, height=12cm]{Scores_on_constrained_axis_combined.pdf}
+%   \caption{RDA of traits constrained by electric conductivity for the tested methods and the original study.
+Shown are boxplots of the site scores along the conductivity axis.
+The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
+Only traits with a mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.}
+% \end{sidewaysfigure}
+
 \begin{figure}[H]
   \centering
-  \includegraphics[width=17cm, height=14.5cm]{boxplot_scores_combined.png}
-  \caption{RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{median}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
+  \includegraphics[width=16.5cm, height=25cm]{Scores_on_constrained_axis_comb_ALT.pdf}
+\end{figure}
+\clearpage % insert a page break
+\captionof{figure}{RDA of traits constrained by electric conductivity for the tested methods and the original study.
 Shown are boxplots of the site scores along the conductivity axis.
@@
 Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
-For better comparability, species scores of the original analysis were multiplied by -1.
-Results for the other aggregated methods are shown in the supporting information.
-lcd, life cycle duration; nr.cy, potential number of cycles per year}
-\end{figure}
+For better comparability, species scores of the original analysis were multiplied by -1.}
+\label{fig:boxplots_scores_on_constrained_axis}
 

### 2021-02-13 Paper/Results/SI.tex

@@
         \begin{itemize}
-            \item Detrivore \textsuperscript{\textit{a}}
+            \item Detrivore$^{\dagger}$
             \item Trait herbivore includes among others the trait shredder
@@
         Multivoltine & 
-        "\textit{Three} or more generations per year" \textsuperscript{\textit{b}}& 
+        "\textit{Three} or more generations per year"$^{\ddagger}$ & 
         "Able to complete \textit{at least} two successive generations per year" &
@@
         - &
-        \multirow{3}{*}{\specialcell{Multiple size \\ classifications \textsuperscript{\textit{d}}}} & 
+        \multirow{3}{*}{\specialcell{Multiple size \\ classifications$^{\P}$}} & 
         $<$ 9 mm & 
         $<$ 9 mm & 
-        $<$ 9 mm \textsuperscript{\textit{a;c}} &
-        \multirow{3}{*}{\specialcell{Multiple size \\ classifications \textsuperscript{\textit{e}}}}
+        $<$ 9 mm $^{\dagger \mathsection}$ &
+        \multirow{3}{*}{\specialcell{Multiple size \\ classifications$^{\star}$}}  
         \\
@@
     \begin{minipage}{\linewidth}\small
-        \textit{a} Traits from Botwe et al.
+        $\dagger$ Traits from Botwe et al.
         \newline
-        \textit{b} Contains also bivoltine (two generations per year), trivoltine (three generations per year) and flexible.
+        $\ddagger$ Contains also bivoltine (two generations per year), trivoltine (three generations per year) and flexible.
         \newline
-        \textit{c} Contains a size trait with numeric size values. Contains also traits classifying size like Tachet and like the North American trait databases. 
+        $\mathsection$ Contains a size trait with numeric size values. Contains also traits classifying size like Tachet and like the North American trait databases. 
         \newline
-        \textit{d} Size classifications: \textit{$<=0.25$ cm, $> 0.25-0.5$ cm, $0.5-1$ cm, $1-2$ cm, $2-4$ cm, $4-8$ cm, $> 8$ cm}. No distinction into small, medium and large.
+        $\P$ Size classifications: \textit{$<=0.25$ cm, $> 0.25-0.5$ cm, $0.5-1$ cm, $1-2$ cm, $2-4$ cm, $4-8$ cm, $> 8$ cm}. No distinction into small, medium and large.
         \newline
-        \textit{e} Size classifications: \textit{$> 0.25-0.5$ cm, $0.5-1$ cm, $1-2$ cm, $2-4$ cm, $4-8$ cm}. No distinction into small, medium and large.
+        $\star$ Size classifications: \textit{$> 0.25-0.5$ cm, $0.5-1$ cm, $1-2$ cm, $2-4$ cm, $4-8$ cm}. No distinction into small, medium and large.
     \end{minipage}
@@
     \centering
-    \includegraphics[width=16.5cm, height=25cm]{Scores_on_constrained_axis_comb_ALT.pdf}
+    \includegraphics[width=18.5cm, height=16cm]{boxplot_scores_combined_REMAIN_SI.png}
+    \caption{RDA of traits constrained by electric conductivity for the data aggregated with \textit{direct\_agg \textsubscript{mean}}, \textit{stepwise\_agg \textsubscript{mean}}, and \textit{weighted\_agg}.
+Shown are boxplots of the site scores along the conductivity axis.
+The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
+For more details see Figure \ref{fig:boxplot_scores_on_constrained_axis}.
+lcd, life cycle duration; nr.cy, potential number of cycles per year.}
+    \label{fig:boxplots_scores_on_constrained_axis_REMAIN}
 \end{figure}
-  \clearpage % insert a page break
-  \captionof{figure}{RDA of traits constrained by electric conductivity for the tested methods and the original study.
+%   \clearpage % insert a page break
+%   \captionof{figure}{RDA of traits constrained by electric conductivity for the tested methods and the original study.
 Shown are boxplots of the site scores along the conductivity axis.
@@
 For better comparability, species scores of the original analysis were multiplied by -1.}
-\label{fig:boxplots_scores_on_constrained_axis}
 

### 2021-02-15 Paper/Draft_harmonization_paper.tex
15.02: Small citation change

--- 2021-02-13 Paper/Draft_harmonization_paper.tex
@@
 Explaining and predicting how communities are shaped by environmental factors is a primary main goal of ecology.
-Species traits are measurable properties of an organism (\cite{mcgill_rebuilding_2006}), and comparing communities based on the traits possessed by species may facilitate testing of a range of ecological hypotheses (\cite{heino_jani_macroecological_2013}).
+Species traits are measurable properties of an organism (\cite{mcgill_rebuilding_2006}), and comparing communities based on the traits possessed by species may facilitate testing of a range of ecological hypotheses (\cite{statzner_perspectives_2001}).
 Traits are assumed to be adaptations (e.g., physiological, behavioural) of organisms to their environment and to indicate direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).

### 2021-02-15 Paper/Draft_harmonization_paper.tex
15.02.: Small edits

@@
 natbib,
-style = apa,
+bibstyle = apa,
 citestyle = authoryear,
@@
 % Verena Schreiner body form traits?
-We thank Brooke Cassell for technical editing of the manuscript. The project is funded by the German research society (DFG \textit{insert project number}).
+We thank Brooke Cassell for technical editing of the manuscript. The project, in which this study was conducted, is funded by the German research society (DFG \textit{insert project number}).
 

### 2021-02-15 Paper/Draft_harmonization_paper.tex
15.02: Added author contributions and keywords

--- 2021-02-15 Paper/Draft_harmonization_paper.tex
@@
 DOI: 10.1177/0022219413479673
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%% New Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \newcommand{\specialcell}[2][c]{%
@@
 \renewcommand*{\thefootnote}{\alph{footnote}}
+
+% Keywords command
+\providecommand{\keywords}[1]
+{
+  \small	
+  \textbf{\textit{Keywords---}} #1
+}
 
@@
 \author[2]{Ben J. Kefford}
-\author[3]{Leon Metzeling}
-\author[4]{Astrid Schmidt-Kloiber}
+\author[3]{Astrid Schmidt-Kloiber}
+\author[4]{Christoph D. Matthaei}
+\author[5]{Philippe Usseglio-Polatera}
 \author[4]{Wolfram Graf}
-\author[5]{Philippe Usseglio-Polatera}
-\author[6]{Christoph D. Matthaei}
-\author[7]{Charles P. Hawkins}
-\author[8]{N. LeRoy Poff}
-\author[9]{Laura Twardochleb}
+\author[6]{N. LeRoy Poff}
+\author[7]{Leon Metzeling}
+\author[8]{Laura Twardochleb}
+\author[9]{Charles P. Hawkins}
 \author[1]{Ralf B. Schäfer}
@@
 \affil[2]{Centre for Applied Water Science, Institute for Applied Ecology, University of Canberra, Canberra, Australia}
-\affil[3]{Environment Protection Authority Victoria, Applied Sciences Division, Macleod, Australia}
-\affil[4]{Institute of Hydrobiology and Aquatic Ecosystem Management, University of Natural Resources and Life Sciences Vienna (BOKU), Vienna, Austria}
+\affil[3]{Institute of Hydrobiology and Aquatic Ecosystem Management, University of Natural Resources and Life Sciences Vienna (BOKU), Vienna, Austria}
+\affil[4]{Department of Zoology, University of Otago, Dunedin, New Zealand}
 \affil[5]{University of Lorraine, CNRS, LIEC, Metz, France}
-\affil[6]{Department of Zoology, University of Otago, Dunedin, New Zealand}
-\affil[7]{Department of Watershed Sciences and the Ecology Center, Utah State University, Logan, USA}
-\affil[8]{Department of Biology, Colorado State University, Fort Collins, USA}
-\affil[9]{Department of Fisheries and Wildlife, Michigan State University, East Lansing, USA}
+\affil[6]{Department of Biology, Colorado State University, Fort Collins, USA}
+\affil[7]{Environment Protection Authority Victoria, Applied Sciences Division, Macleod, Australia}
+\affil[8]{Department of Fisheries and Wildlife, Michigan State University, East Lansing, USA}
+\affil[9]{Department of Watershed Sciences and the Ecology Center, Utah State University, Logan, USA}
 \date{}
@@
 Our results also illustrate the usefulness of harmonised datasets for ecological study and provide guidance for the circumstances under which the choice of trait aggregation method is important.
+\\
+\\
+\keywords{trait definitions, trait aggregation, data synthesis}
 
@@
 In this study, we follow the terminology proposed by \citet{schmera_proposed_2015}, where a grouping feature is defined as a general property (e.g.
-feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species".
-Thus, we use the term grouping feature in place of the term trait, and the term trait instead of trait state, modality or trait category.
+feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species" (page number 825).
+Thus, to use consistent terminology in this study, we use the term grouping feature in place of the term trait, and the term trait instead of trait state, modality or trait category.
 
@@
 the mean (\cite{magliozzi_functional_2019}), median (\cite{szocs_effects_2014}) or mode (\cite{piliere_a._f._h._importance_2016}), but studies on how and to what extent different trait aggregation methods influence trait-based analyses are missing.
-%However, related knowledge would inform future studies regarding the choice of the aggregation method.
 
@@
 
-Harmonised invertebrate trait datasets for Australia, Europe, North America and New Zealand are deposited \textit{Zenondo/Github?}
+Harmonised invertebrate trait datasets for Australia, Europe, North America and New Zealand are deposited on Github. % Add link
 
@@
 % Verena Schreiner body form traits?
-We thank Brooke Cassell for technical editing of the manuscript. The project is funded by the German research society (DFG \textit{insert project number}).
+We thank Brooke Cassell for technical editing of the manuscript. The project, in which this study was conducted, is funded by the German research society (DFG, project number 338785727).
 
@@
 The authors declare no conflict of interest.
+
+\section*{Author contribution}
+R.B.S.
+and S.K.
+designed the study; B.J.K.
+and L.M.
+provided trait data for Australia; P.U-P.
+provided trait data from the Tachet database; C.P.H., N.L.P., and L.T.
+provided trait data for North America; C.D.M.
+provided trait data for New Zealand;
+B.J.K., A.S-K., C.D.M, W.G., N.L.P., L.M., and C.P.H.
+provided in depth information on trait data and discussed procedure of analysis; S.K.
+conducted data processing and the statistical analyses.; S.K.
+wrote the manuscript; B.J.K, A-S.K., C.D.M, P.U-P., C.P.H., and R.B.S.
+discussed the results and provided suggestions on the manuscript.
 

### 2021-02-18 Paper/Draft_harmonization_paper.tex
18.02: Formatting fixes

@@
-\documentclass{article}
+\documentclass[12pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{authblk}
+\usepackage{csquotes}
 \graphicspath{{Figures/}}
+\usepackage{setspace}
 \usepackage{rotating}
@@
 natbib,
-style = apa,
+style = apa6,
 citestyle = authoryear,
@@
 
-% functions and definitions
+%%%% Functions and definitions %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \definecolor{Gray}{gray}{0.9}
@@
 
-%%%%% New Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%% New Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%% Formatting options %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\onehalfspacing
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \author[5]{Philippe Usseglio-Polatera}
-\author[4]{Wolfram Graf}
+\author[3]{Wolfram Graf}
 \author[6]{N. LeRoy Poff}
@@
 
-\begin{table}[H]
-\centering
+\newpage
+
+\begin{longtable}{m{2.5cm}|m{4cm}|m{7cm}}
 \caption{Traits of harmonised grouping features from six invertebrate trait databases and four geographic regions.
 The last column indicates traits that were combined for harmonisation (no combining needed if empty).}
+\endfirsthead
+\toprule[.1em]
 \label{tab:traits_harmonisation}
-\begin{tabular}{lll}
-\toprule[.1em]
-Grouping feature & Trait & Combined traits\\
+%\begin{tabular}
+\specialcell{Grouping \\ feature} & Trait & Combined traits\\
 \toprule[.1em]
@@
 \bottomrule[.1em]
-\end{tabular}
-\end{table}
+%\end{tabular}
+\end{longtable}
 \begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
@@
 
+\newpage
+
 \subsection*{Comparing trait aggregation methods}
 
-For our study aim of comparing the effects of different aggregation methods on trait–environment relationship inference, we aggregated the traits of two of the harmonised datasets to the family level.
+For our study aim of comparing the effects of different aggregation methods on trait\-environment relationship inference, we aggregated the traits of two of the harmonised datasets to the family level.
 We used three different aggregation approaches: (1) direct aggregation of taxa to family level with either the median or mean, giving equal weight to every taxon.
@@
 
-\subsection*{Effects of harmonisation and trait aggregation on trait-environment relationship inferences}
+\subsection*{Effects of harmonisation and trait aggregation on trait-environ\-ment relationship inferences}
 
@@
 The River Werra has been subject to effluents from the potash industry since the mid- 20th century, which makes it a useful system for studying the responses of invertebrates and their trait compositions to salinisation (\cite{bathe_biological_2011}).
-\citet{szocs_effects_2014}  used redundancy analysis (RDA) to compare trait compositions among sites downstream, upstream, and close to salt discharge (transition).
+\citet{szocs_effects_2014}  used redundancy analysis (RDA) to compare trait compositions among sites downstream and upstream to the salt discharge.
 Further details about the original study can be found in \citet{szocs_effects_2014}.
@@
     \label{tab:tax_coverage}
-    \begin{tabular}{lccccc}
+    \begin{tabular}{l|c|c|c|c|c}
     \toprule[.1em]
@@
 
-\begin{table}[ht]
+\begin{table}[H]
     \centering
@@
     \label{tab:trait_coverage}
-    \begin{tabular}{lccccccc}
+    \begin{tabular}{l|c|c|c|c|c|c|c}
     \toprule[.1em]
-    Dataset & Body form & Oviposition & Voltinism & Locomotion & Size & Respiration & Feeding mode \\ 
+    Dataset & \specialcell{Body \\ form} & Oviposition & Voltinism & Locomotion & Size & Respiration & \specialcell{Feeding \\ mode} \\ 
     \toprule[.1em]
@@
 \end{longtable}
-\begin{minipage}{\linewidth}\small
+\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
       $\dagger$ Some of the feeding mode traits used in the Australian database were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
@@
       $\ddagger$ Not all traits were considered because trait information was partly presented as comments to describe other traits or due to incomplete information.
+      }
   \end{minipage}
@@
 
+\begin{landscape}
 \begin{table}[H]
@@
  \end{minipage}
+\end{landscape}
 
@@
 
-\subsection*{Effects of harmonisation and trait aggregation on trait-environment relationships}
+\subsection*{Effects of harmonisation and trait aggregation on trait-environ\-ment relationships}
 
@@
 provided trait data for Australia; P.U-P.
-provided trait data from the Tachet database; C.P.H., N.L.P., and L.T.
+provided body form trait data for European and North American invertebrates; C.P.H., N.L.P., and L.T.
 provided trait data for North America; C.D.M.
@@
 B.J.K., A.S-K., C.D.M, W.G., N.L.P., L.M., and C.P.H.
-provided in depth information on trait data and discussed procedure of analysis; S.K.
+provided in depth information on trait data and discussed the procedure of analysis; S.K.
 conducted data processing and the statistical analyses.; S.K.

### 2021-02-18 Paper/Flowchart/Flowchart_methods.tex
18.02: Formatting fixes

@@
       \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Consolidating duplicate \\ taxa in  EU, NOA, AUS \& \\ NZ databases};
-      \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{AUS traits standardised to [0 - 1] \\ because multiple codings used \\ throughout this database};
+      \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{ Normalised AUS \\ traits ([0 - 1]) to work \\ with multiple codings};
       \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Omitted taxa less \\ precise than family-level};
@@
 
-      \node(tab_aggregation)[xshift = -3cm, yshift = -6.6cm]{
+      \node(tab_aggregation)[xshift = -3cm, yshift = -7.2cm]{
         \begin{tabular}{ccc|ccc}
@@
 
-      \node(directAgg)[aggrtypesnode, align = center, xshift = 4cm, yshift = -5cm]{Direct aggregation};
+      \node(directAgg)[aggrtypesnode, align = center, xshift = 4.2cm, yshift = -5cm]{Direct aggregation};
 
-      \node(tab_direct_agg)[xshift = 4cm, yshift = -7.5cm]{
+      \node(tab_direct_agg)[xshift = 4.2cm, yshift = -8.2cm]{
         \begin{tabular}{c|ccc}
@@
 
-      \node(stepwiseAgg)[aggrtypesnode, align = center, xshift = -3.5cm, yshift = -10.3cm]{Stepwise aggregation};
+      \node(stepwiseAgg)[aggrtypesnode, align = center, xshift = -3.5cm, yshift = -11.3cm]{Stepwise aggregation};
 
-      \node(tab_stepwise_agg)[xshift = -3.5cm, yshift = -12.5cm]{
+      \node(tab_stepwise_agg)[xshift = -3.5cm, yshift = -13.6cm]{
         \begin{tabular}{cc|ccc}
@@
 
-      \node(stepwiseAgg2)[aggrstepsnode, align = center, xshift = -3.5cm, yshift = -14.7cm]{ $A\_h_1 = mean(0.4167, 0.125, 0.25)$ \\ $ = 0.26$};
+      \node(stepwiseAgg2)[aggrstepsnode, align = center, xshift = -3.5cm, yshift = -16cm]{ $A\_h_1 = mean(0.4167, 0.125, 0.25)$ \\ $ = 0.26$};
 
-      \node(weightedAgg)[aggrtypesnode, xshift = 4cm, yshift = -10.3cm]{Weighted aggregation};
+      \node(weightedAgg)[aggrtypesnode, xshift = 4.2cm, yshift = -11.3cm]{Weighted aggregation};
 
-      \node(weights)[aggrstepsnode, align = center, xshift = 4cm, yshift = -12.7cm]{Weights based on \\ species per genera: \\
+      \node(weights)[aggrstepsnode, align = center, xshift = 4.2cm, yshift = -13.4cm]{Weights based on \\ species per genera: \\
       $3$ for $G_1$, $1$ for $G_2$, \\
@@
 
-      \node(weights2)[aggrstepsnode, align = center, xshift = 4cm, yshift = -15.1cm]{$A\_h_1 = \frac{0.25*3+0.5*3+...+ 0.25*1}{3+3...+1}$ \\ \\ $ = 0.35$};
+      \node(weights2)[aggrstepsnode, align = center, xshift = 4.2cm, yshift = -16cm]{$A\_h_1 = \frac{0.25*3+0.5*3+...+ 0.25*1}{3+3...+1}$ \\ \\ $ = 0.35$};
 

### 2021-02-18 Paper/Results/SI.tex
15.02.: Small edits
18.02: Formatting fixes

@@
 \begin{landscape}
-    \begin{longtable}{m{1.8cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3.2cm}|m{3cm}}
+    \begin{longtable}{m{1.9cm}|m{3.3cm}|m{3.3cm}|m{2.7cm}|m{3cm}|m{3.2cm}|m{2.5cm}}
         \caption{Comparison of trait definitions between invertebrate trait databases.
@@
         \midrule
-        Multivoltine & 
+        Multi\-voltine & 
         "\textit{Three} or more generations per year"$^{\ddagger}$ & 
@@
     \end{longtable}
-    \begin{minipage}{\linewidth}\small
+    \begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
         $\dagger$ Traits from Botwe et al.
@@
         $\star$ Size classifications: \textit{$> 0.25-0.5$ cm, $0.5-1$ cm, $1-2$ cm, $2-4$ cm, $4-8$ cm}. No distinction into small, medium and large.
+        }
     \end{minipage}
@@
     \label{tab:SI_resp_traits_summary_stats}
-    \begin{tabular}{llccc|c}
+    \begin{tabular}{l|l|c|c|c|c}
     \toprule[.1em]
@@
 For more details see Figure \ref{fig:boxplot_scores_on_constrained_axis}.
-lcd, life cycle duration; nr.cy, potential number of cycles per year.}
+Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.}
     \label{fig:boxplots_scores_on_constrained_axis_REMAIN}
 \end{figure}
-%   \clearpage % insert a page break
-%   \captionof{figure}{RDA of traits constrained by electric conductivity for the tested methods and the original study.
-Shown are boxplots of the site scores along the conductivity axis.
-The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
-Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
-For better comparability, species scores of the original analysis were multiplied by -1.}
 

### 2021-02-19 Paper/Draft_harmonization_paper.tex
19.02: Suggestions Chuck

@@
 \usepackage{caption}
+\usepackage{ccaption}
 \usepackage{authblk}
@@
 \affil[8]{Department of Fisheries and Wildlife, Michigan State University, East Lansing, USA}
-\affil[9]{Department of Watershed Sciences and the Ecology Center, Utah State University, Logan, USA}
+\affil[9]{Department of Watershed Sciences, National Aquatic Monitoring Center, and the Ecology Center, Utah State University, Logan, USA}
 \date{}
@@
 However, a number of data-related issues complicate the use of invertebrate traits for ecological studies.
-For example, standardised definitions for for freshwater invertebrate traits are lacking, which impedes comparisons across regions.
+For example, standardised definitions for freshwater invertebrate traits are lacking, which impedes comparisons across regions.
 Moreover, it is uncertain how harmonising varying trait definitions among databases might influence identification of trait-environment relationships.
-In addition, taxonomic resolution between observational taxonomic data and trait data can differ, making aggregation of traits necessary.
+In addition, taxonomic resolution between taxonomic composition data and trait data can differ, making aggregation of traits necessary.
 At present, it is unknown how different trait aggregation approaches compare with expert-assigned trait affinities.
@@
 The coding to describe traits (binary, fuzzy) also varied among databases.
-Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially from approaches using the median, and that trait coding method, uneven taxonomic hierarchical structure, and high trait variability can influence aggregated trait affinities.
-We further showed that harmonised and aggregated data performed similarly to observational data in identifying trait–environment relationships.
+Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially when aggregation was based on the median, and that trait coding method, uneven taxonomic hierarchical structure, and high trait variability can influence aggregated trait affinities.
+We further showed that harmonised and aggregated data performed similarly to not aggregated and harmonised data from the case study in identifying trait–environment relationships.
 
 4.
-By outlining discrepancies in trait definitions we hope to motivate the development of standardised terminology for invertebrate traits.
+By identifying discrepancies in trait definitions we hope to motivate the development of standardised terminology for invertebrate traits.
 Our results also illustrate the usefulness of harmonised datasets for ecological study and provide guidance for the circumstances under which the choice of trait aggregation method is important.
@@
 
-Explaining and predicting how communities are shaped by environmental factors is a primary main goal of ecology.
+Explaining and predicting how communities are shaped by environmental factors is a primary goal of ecology.
 Species traits are measurable properties of an organism (\cite{mcgill_rebuilding_2006}), and comparing communities based on the traits possessed by species may facilitate testing of a range of ecological hypotheses (\cite{statzner_perspectives_2001}).
-Traits are assumed to be adaptations (e.g., physiological, behavioural) of organisms to their environment and to indicate direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
-In addition to providing local-scale mechanistic-based expressions of species-environment relationships, trait-based approaches might be suitable for large-scale analyses because trait responses are less constrained by biogeographic boundaries and taxon distributional areas than taxonomic responses (\cite{baird_toward_2011, bonada_taxonomic_2007}).
+Traits are assumed to be adaptations (e.g., physiological, behavioural) of organisms to their environment, which represent either direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
+In addition to providing local-scale mechanistic-based expressions of species-environment relationships, trait-based approaches might be suitable for large-scale analyses of environmental risks to communities because the occurrence and distribution of traits are less constrained by biogeographic boundaries than that of taxa (\cite{baird_toward_2011, bonada_taxonomic_2007}).
 
 Invertebrate traits have been increasingly used in freshwater ecology, e.g.
-by relating macroinvertebrate trait composition to environmental factors (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}).
+by relating macroinvertebrate trait composition to environmental factors such as climate change or salinisation (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}).
 In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases, which typically include data for a single region or continent (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate}).
@@
 
-The heterogeneity of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of studies across continents.
-There are several challenges presented by using invertebrate trait data from multiple established databases in ecological studies.
-One such challenge is inconsistency in terminology.
-In this study, we follow the terminology proposed by \citet{schmera_proposed_2015}, where a grouping feature is defined as a general property (e.g.
-feeding mode) that comprises a "group of related traits (e.g., predator, shredder, etc.) that vary among species or among individuals within a species" (page number 825).
+The variability and inconsistencies of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of comparisons across continents.
+Several challenges currently prevent use of invertebrate trait data from different established databases in ecological studies.
+One challenge is inconsistency in terminology.
+In this study, we follow the terminology proposed by \citet{schmera_proposed_2015}, in which a grouping feature (e.g.
+feeding mode) refers to a set of related organismal traits (e.g.
+predator, shredder, etc.) that together define an ecological property that is shared among individuals or species.
 Thus, to use consistent terminology in this study, we use the term grouping feature in place of the term trait, and the term trait instead of trait state, modality or trait category.
@@
 Another challenge to using data from multiple continents is that invertebrate trait databases include different grouping features and related traits.
-To harmonize grouping features from different regions, or to structure them in such a way as to facilitate cross-database comparison, commonly accepted and unambiguous trait definitions are required (\cite{schneider_towards_2019}).
-Ideally, the same traits and grouping features would be reported across databases or standardised terminology would exist to easily harmonise them; however, there is a lack of standardised terminology of trait definitions and poor metadata quality in many trait databases, making grouping-feature harmonisation difficult (\cite{baird_toward_2011, kissling_towards_2018}).
-To our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on functional diversity and invertebrate assemblages.
+To harmonise grouping features from different regions, or to structure them in such a way as to facilitate cross-database comparison, commonly accepted and unambiguous trait definitions are required (\cite{schneider_towards_2019}).
+Ideally, the same traits and grouping features would be reported across databases or standardised terminology would exist to easily harmonise them; however, standardised terminology of trait definitions is lacking and poor metadata quality in many trait databases make, harmonisation of grouping features difficult (\cite{baird_toward_2011, kissling_towards_2018}).
+To our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on the functional diversity of invertebrate assemblages.
 
-A third challenge to comparing across invertebrate trait databases is inconsistent coding of trait data (\cite{culp_incorporating_2011}), or assigning affinities (aka affinity scores).
+A third challenge to comparing across invertebrate trait databases is inconsistent coding of trait data (\cite{culp_incorporating_2011}).
+Coding of trait data is usually done by assigning an affinity (aka affinity score) of an invertebrate taxon to express a particular trait %, either using a binary classification (0/1), continuous or fuzzy classification (0 - 1 or 0 - 100 \%).
 Traits of individual freshwater invertebrates can be difficult to quantify because, unlike plant traits, they are often difficult to measure directly.
-For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behaviour, and specific food sources (\cite{moog_comprehensive_nodate}).
-Some traits can be described as binary or categorical, which ignores uncertainty in how traits are expressed in any particular organism (e.g., adult terrestrial stage, presence of gills).
+For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behaviour, and what is being eaten (\cite{moog_comprehensive_nodate}).
+Some traits can be described in categorical terms, which ignores uncertainty in how traits are expressed in any particular organism (e.g., adult terrestrial stage, presence of gills).
 Other traits are better suited to being described as continuous (e.g., tolerance of pollution, body size).
@@
 Fuzzy codes, which are usually converted to proportions, are used to account for plasticity in traits, variability in traits within taxonomic groups above the species level, and incomplete knowledge.
-A challenge is presented by the use of different types of coding for trait affinities in different databases.
-For example, in the study from \citet{brown_functional_2018} the authors needed to reclassify trait affinities because the individual databases employed different coding approaches (i.e., European and New Zealand databases used fuzzy coding, North American database used binary coding).
+The use of different types of coding for trait affinities in different databases limits comparisons.
+For example, in the study from \citet{brown_functional_2018} the authors needed to reclassify trait affinities because the individual databases employed different coding approaches (i.e., European and New Zealand databases used fuzzy coding whereas the North American database used binary coding).
 
-Finally, discrepancies in the taxonomic resolutions (e.g., species, genus, or family) when comparing among trait databases, or when linking observational taxonomic data to trait databases, presents another challenge.
-When observations or data in one trait database are at a more precise taxonomic level than other data (e.g.
+Finally, discrepancies in the taxonomic resolutions (e.g., species, genus, or family) used when comparing among trait databases, or when linking counted taxonomic data to trait databases, presents another challenge.
+When taxonomic composition or data in on trait database are at a more precise taxonomic level than other trait data (e.g.
 observations at species-level and trait data at genus-level) trait information of the less precise taxonomic level is often assigned (e.g.
 \cite{szocs_effects_2014, vos_taxonomic_2017}).
-Conversely, if trait information is only available at more precise taxonomic levels than observed taxa, traits are aggregated to a less precise taxonomic level (e.g.
+If trait information is only available at more precise taxonomic levels than for taxonomic composition, traits are aggregated to a less precise taxonomic level (e.g.
 \cite{aspin_extreme_2019, piliere_a._f._h._importance_2016, poff_functional_2006, szocs_effects_2014}).
@@
 
-These challenges when working with or synthesizing trait data motivated us to assess the characteristics and comparability of freshwater invertebrate trait data contained in disparate databases.
-We aimed to explore methods of improving the comparability of trait data across databases, despite differences in trait definitions and the taxonomic level of data in three ways: (1) by investigating and describing discrepancies in trait definitions between trait databases from Europe, North America, Australia, and New Zealand; (2) by harmonising trait definitions across databases to provide consistent trait grouping features for comparison across geographic locations; and (3) by comparing the influence of different trait aggregation methods and grouping-feature harmonisation on the identification of trait–environment relationships.
+These challenges motivated us to assess the characteristics and comparability of different freshwater invertebrate trait databases with the goal of facilitating future syntheses.
+We aimed to identify methods of improving the comparability of trait data across databases, despite differences in trait definitions and the taxonomic level of data in three ways: (1) by describing discrepancies in trait definitions between trait databases from Europe, North America, Australia, and New Zealand; (2) by harmonising trait definitions across databases to provide consistent trait grouping features for comparison across geographic locations; and (3) by comparing the influence of different trait aggregation methods and grouping-feature harmonisation on the detection of trait–environment relationships.
 
@@
 
-%Version from Brooke: As a basis for evaluating the comparability of freshwater invertebrate databases, we developed four novel invertebrate trait datasets by harmonising seven grouping features from existing trait databases.
-We then evaluated the influence of different...
-
 To address our study objectives, we took a multi-prong approach to describing, combining, and assessing multiple sources of freshwater invertebrate data that differed in grouping-feature definitions and taxonomic resolution.
-Identified trait definitions discrepancies served as a starting point to develop four novel invertebrate trait datasets by harmonising seven grouping features from existing trait databases.
+Discrepancies in trait definitions served as a starting point to develop four novel invertebrate trait datasets by harmonising seven grouping features present in the existing trait databases.
 The harmonised trait datasets were used to evaluate the influence of different trait aggregation approaches on the identification of trait–environment relationships, our third study objective, in two ways by (1) comparing family-level aggregated trait affinities with family-level trait affinities assigned by experts for two of the established trait datasets where such data were available and (2) comparing the influence of taxonomic hierarchy and trait variability on the outcomes of the different trait aggregation approaches for simulated data.
@@
 
-To explore the characteristics and comparability of freshwater invertebrate trait data with differing grouping-feature definitions and taxonomic resolution, we obtained invertebrate trait data from six trait databases for four regions: Europe, North America, Australia, and New Zealand.
-For Europe we obtained trait information from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}), which contains taxa at the species level, and the Tachet database (\cite{ussegliopolatera_biological_2000}), which contains taxa at species, genus, and family levels.
+We assessed how six databases differed in how they assigned and described traits of freshwater invertebrates.
+These databases (from Europe, North America, Australia, and New Zealand) differed in how grouping features were defined and the taxonomic resolution used to assign traits.
+For Europe we obtained trait information from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}), which assigns traits at the species level, and the Tachet database (\cite{ussegliopolatera_biological_2000}), which assigns traits at species, genus, and family levels.
 For North America we primarily obtained trait information from \citet{twardochleb_freshwater_nodate} (hereafter referred to as the CONUS database) and where taxa were missing from that database, we obtained data from \citet{vieira_database_nodate} (hereafter referred to as the Vieira database).
@@
 Data on body form for European and North American taxa were based on expert knowledge (\cite{polatera_personal_information_2020}).
-For Australia and New Zealand, we used trait databases from \citet{kefford_integrated_2020} (hereafter referred to as the Australian database) and \citet{Philips_and_Smith_NZ_DB_2018} (hereafter referred to as the New Zealand database) respectively.
-These databases contain taxa at species, genus, family, and less precise taxonomic levels.
+For Australia and New Zealand, we used trait databases from \citet{kefford_integrated_2020} (hereafter referred to as the Australian database) and \citet{Philips_and_Smith_NZ_DB_2018} (hereafter referred to as the New Zealand database).
+These databases assigned traits at species, genus, family, and coarser taxonomic levels.
 
 We established four datasets, one for each of the four geographic regions, by harmonising the traits of seven grouping features from the trait databases.
-We selected traits that were available in all databases, are commonly applied in trait-based ecological studies, and describe different parts of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
+We selected traits that were available in all databases, are commonly applied in trait-based ecological studies, and describe different aspects of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
 We omitted ecological traits that describe habitat preferences (e.g.
 temperature preference) because these traits are missing in the New Zealand trait database.
-Grouping features were  classified differently across the databases, so we harmonised them into 26 traits (Table \ref{tab:traits_harmonisation}).
+Grouping features were classified differently across the databases, so we harmonised 7 grouping features that collectively included 26 traits (Table \ref{tab:traits_harmonisation}).
 To do so we combined similar traits into one trait (e.g.
-crawlers and sprawlers into crawlers) and assigned the highest trait affinity score among the combined traits for each taxon.
-
+crawlers and sprawlers into crawlers) and for each taxon we assigned for the new combined trait the highest affinity score of those originally assigned to the subsequently combined traits.
+% and assigned the highest trait affinity score among the combined traits for each taxon.  
 Next, we selected taxa for inclusion in our datasets and normalised the trait affinity scores for each taxon.
 We first omitted all taxa with a lower taxonomic precision than family level and consolidated duplicate taxa that appeared within a database, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
-We then established our harmonised datasets by using either fuzzy coding or, when unavailable, binary coding.
+We then used either fuzzy coding or, when unavailable, binary coding to create the final harmonised datasets.
 Fuzzy codes are reported with different ranges in the trait databases (e.g., freshwaterecology.info: 0–10, Tachet database: 0–3 or 0–5).
 We normalised these to a range between 0 and 1 and converted trait affinities to proportions.
-In cases where binary coding was needed, we converted categorical and continuous traits into binary traits with values of 1 and 0, which, thus, corresponded with the range of fuzzy coded traits.
-For example, in the  freshwaterecology.info database, the classification of the grouping feature voltinism accounts for different faunistic regions and we substituted a value of 1 for entries such as “arctic” or “boreal”.
-We assumed that values of 1 and 0 for binary traits corresponded to the highest and no affinity for a particular trait.
+In cases where binary coding was needed, we converted categorical and continuous traits into binary traits with values of 1 and 0, which, therefore, had the same range as fuzzy coded traits.
+For example, in the  freshwaterecology.info database, voltinism traits are associated with different faunistic regions, and we substituted a value of 1 for entries such as “arctic” or “boreal” % and 0 if no region was given.
+We assumed that values of 1 and 0 for binary traits corresponded to the highest and lowest affinity for a particular trait.
 
@@
 
-For our study aim of comparing the effects of different aggregation methods on trait\-environment relationship inference, we aggregated the traits of two of the harmonised datasets to the family level.
-We used three different aggregation approaches: (1) direct aggregation of taxa to family level with either the median or mean, giving equal weight to every taxon.
-We denote these aggregation methods as \textit{direct\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{mean}}, respectively; (2) stepwise aggregation, first to the genus level and subsequently to the family level with either the median or mean.
+To compare the effects of different aggregation methods on trait\-environment relationship inferences, we aggregated the traits of two of the harmonised datasets to the family level.
+We used three different aggregation approaches: (1) direct aggregation of taxa to family level, in which we aggregated either trait affinities by the median or mean for species and genera within a family, giving equal weight to every taxon.
+We denote these aggregation methods as \textit{direct\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{mean}}, respectively; and (2) stepwise aggregation, first to the genus level and subsequently to the family level with either the median or mean.
 This approach gives equal weights to each genus.
@@
 Expert-assigned trait data were available for a subset of grouping features and taxa for Australia (\cite{chessman_dissolved-oxygen_2018}) and North America (CONUS database), so we conducted this comparison only for these two datasets.
-For the Australian dataset, we used the grouping features feeding mode (all traits listed in Table 1 except parasite) and size (220 families $*$ 8 family–trait combinations = 1760 comparisons).
-For the North American dataset, we used the grouping features feeding mode, respiration, size, voltinism, and locomotion (94 families $*$ 17 family–trait combinations = 1598 comparisons).
+For the Australian dataset, we used the grouping features feeding mode (all traits listed in Table 1 except parasite) and size (220 families $\times$ 8 family–trait combinations = 1760 comparisons).
+For the North American dataset, we used the grouping features feeding mode, respiration, size, voltinism, and locomotion (94 families $\times$ 17 family–trait combinations = 1598 comparisons).
 Assigned traits from North America were on a categorical scale, and we converted them to binary prior to comparing them with aggregated trait affinities.
-Size was assigned as continuous variable for Australia, thus, we converted size into three traits (small, medium, and large) with a binary coding.
-Because trait affinities ranged from 0 to 1, the maximum difference possible in trait affinity was 1 to –1, either which corresponds to 100 \%.
-For convenience and to improve interpretation, we calculated absolute trait differences.
+Size is a continuous variable in the Australian database, so, we converted size into three traits (small, medium, and large) each with a binary coding.
+Because trait affinities ranged from 0 to 1, the maximum difference possible in trait affinity was 1 to –1, both of which corresponds to 100 \%.
+For convenience and to improve interpretation, we calculated absolute values of the trait differences, i.e.
+a difference of -1 was converted to 1.
 
@@
 
-\subsubsection*{Effect of taxonomic hierarchy and trait variability on aggregation outcomes}
+\subsubsection*{Effect of phylogeny and trait variability on aggregation outcomes}
 
-To examine the influence of taxonomic hierarchy and trait variability on the outcomes of the different trait aggregation methods, we created three hypothetical scenarios.
-We simulated three different families, each composed of 25 total species but with different taxonomic hierarchical structures.
+To examine the influence of phylogeny and trait variability on the outcomes of the different trait aggregation methods, we created three hypothetical scenarios.
+We simulated three different families, each containing 25 total species but with different phylogenetic structures.
 The three families consisted of (1) a family with an equal number of genera and species (five genera each with five species each), denoted as \textit{sim\_base}; (2) a family in which one genus had a much larger number of species than the other four genera (1 genus with 13 species, 4 genera with 3 species each), denoted as \textit{sim\_extreme}; (3) a family in which all genera had a different number of species (8, 2, 7, 3, 5), denoted as \textit{sim\_variation}.
 We assigned a hypothetical grouping feature with three traits (T1, T2, and T3) to each scenario.
-We then simulated the 25 affinities, one per species, for each trait by sampling from a truncated normal distribution bound by 0 and 1 and with a mean value of 0.5.
-To simulate different levels of trait variability, we repeated the sampling 100 times for each of the 5 levels of standard deviations (0.2, 0.4, 0.6, 0.8, and 1), resulting in 12,500 simulated trait affinities for each simulated trait ($25$ species per family $*$ 5 levels of trait variability $*$ 100 replicates).
+We then simulated the 25 affinities, one per species, for each trait, by sampling from a truncated normal distribution bound by 0 and 1 and with a mean value of 0.5.
+To simulate different levels of trait variability, we repeated the sampling 100 times for each of the 5 standard deviations (0.2, 0.4, 0.6, 0.8, and 1), resulting in 12,500 simulated trait affinities for each simulated trait ($25$ species per family $\times$ 5 levels of trait variability $\times$ 100 replicates).
 We converted simulated trait affinities to proportions, as was done during trait database processing, and assigned the 12,500 simulated affinities per trait to each of the three family scenarios.
@@
 
+% TODO Figure caption next page?
 \begin{figure}
@@
   \subfile{Flowchart/Flowchart_methods.tex}
-  \caption{Data processing steps of the selected traits.
+  \label{fig:data_proc_overview}
+\end{figure}
+\newpage
+\begin{center}
+\captionof{figure}{Data processing steps of the selected traits.
 Intermediate (grey) and main (orange) steps of data preparation are depicted.
@@
 \label{fig:data_proc_overview}
-\end{figure}
+\end{center}
 
@@
 
-\subsection*{Effects of harmonisation and trait aggregation on trait-environ\-ment relationship inferences}
+\subsection*{Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships}
 
@@
 \citet{szocs_effects_2014}  used redundancy analysis (RDA) to compare trait compositions among sites downstream and upstream to the salt discharge.
-Further details about the original study can be found in \citet{szocs_effects_2014}.
+Details about the original study can be found in \citet{szocs_effects_2014}.
 
-We re-analysed the \citet{szocs_effects_2014} study by performing a RDA with harmonised grouping features from the dataset for Europe and with traits that we aggregated to family level with the five aggregation methods described above.
-We used all 21 grouping features from the original study, but replaced 6 with harmonised grouping features from our European trait dataset, namely: size, feeding mode, locomotion, oviposition, respiration, and voltinism.
+We re-analysed the \citet{szocs_effects_2014} data by performing a RDA with harmonised grouping features from the dataset for Europe and with traits that we aggregated to family level with the five aggregation methods described above.
+We used all 21 grouping features from the original study, but replaced 6 with harmonised grouping features from the established European trait dataset, namely size, feeding mode, locomotion, oviposition, respiration, and voltinism.
 We compared the results of the original study’s RDA with the results of the RDA from the harmonised grouping features.
-Specifically, the trait composition, expressed as community weighted mean (CWM) traits, was ordinated along an electric conductivity gradient.
+Specifically, trait composition, expressed as community weighted mean (CWM) traits, was ordinated along an electrical conductivity gradient.
 We compared the species scores obtained from the RDA (i.e., the coordinates of the tips of the vectors representing the CWM traits in the bi- or triplots).
@@
 We considered CWM traits with a Mahalanobis distance greater than the 97.5 \%-quantile of the Chi-square distribution (5.02) to have responded to either lower or higher salinity.
-Additionally, for testing the effect of different aggregation methods on inference about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
+Additionally, to test fo the effect of different aggregation methods on inferences about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
 
@@
 
-\subsection*{Data analysis}
+\subsection*{Software used in data analyses}
 
@@
 The European trait dataset had the largest taxon pool with 4601 taxa (Table \ref{tab:tax_coverage}) followed by the North American dataset (3753 taxa), the Australian dataset (1402 taxa), and the New Zealand dataset with the smallest taxon pool (478 taxa).
-The European, New Zealand, and North American datasets contained most taxa at the species level, whereas the Australian dataset comprised a similar number of taxa at species and genus level.
+The European, North American, and New Zealand datasets contained the most taxa at the species level, whereas the Australian dataset comprised a similar number of taxa at species and genus level.
 
@@
     \toprule[.1em]
-    EU & 4601 & 3942 (86) & 3739 (81) & 704 (15) & 158 (3) \\ 
-    NOA & 3753 & 3305 (88) & 2414 (64) & 1163 (31) & 176 (5)  \\ 
+    EUR & 4601 & 3942 (86) & 3739 (81) & 704 (15) & 158 (3) \\ 
+    NA & 3753 & 3305 (88) & 2414 (64) & 1163 (31) & 176 (5)  \\ 
     AUS & 1402 & 1016 (72) & 564 (40) & 578 (41) & 260 (19) \\ 
@@
 \centering
-Abbreviations: EU, European; NOA, North American; AUS, Australian; NZ, New Zealand.
+Abbreviations: EUR, Europe; NOA, North America; AUS, Australia; NZ, New Zealand.
 }
@@
 
-The amount of entries with available information for the selected grouping features varied strongly for the developed European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
-By contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
+The number of entries with available information for the selected grouping features varied strongly across the established European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
+In contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
 
@@
     \toprule[.1em]
-    EU & 8 & 15 & 23 & 36 & 11 & 57 & 76 \\ 
-    NOA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
+    EUR & 8 & 15 & 23 & 36 & 11 & 57 & 76 \\ 
+    NA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
     AUS & 4 & 46 & 49 & 39 & 75 & 68 & 99 \\ 
@@
 \centering
-Abbreviations: EU, European; NOA, North American; AUS, Australian; NZ, New Zealand.
+Abbreviations: EUR, Europe; NA, North America; AUS, Australia; NZ, New Zealand.
 }
@@
 
-Definitions of grouping features and traits varied in their level of detail in the investigated trait databases.
+Definitions of grouping features and traits varied in their level of detail in the six trait databases.
 The freshwaterecology.info, Tachet, and CONUS databases provided more detailed descriptions of trait information than the Vieira and New Zealand databases provided.
@@
 
-The definitions of grouping features also varied across databases in their differentiation into traits and in their focus, both which can lead to discrepancies in trait definitions.
-We provide a summary of discrepancies in trait definitions in the appendix (Table \ref{stab:trait_definitions}).
+The definitions of grouping features also varied across databases in their differentiation into traits and in their focus, both which can lead to discrepancies in trait definitions (see Table \ref{stab:trait_definitions} for a summary of discrepancies in trait definitions).
 Varying levels of differentiation among the trait databases were present in all investigated grouping features (Table \ref{tab:trait_databases_coding_differentiation} and Table \ref{stab:trait_definitions}).
@@
 In turn, the Tachet database defined piercers as a separate trait encompassing both herbivorous and carnivorous piercers.
-Furthermore, the focus in the freshwaterecology.info database for feeding mode was primarily on the food source of a species (except for filterers), whereas the other databases focused on the strategies of food acquisition.
-For example, the freshwaterecology.info database defined predator as "eating from prey", and the other databases used the mouthpart morphology as basis for their definitions.
-The Tachet database captured the food source in an additional grouping feature.
+Furthermore, the feeding mode in the freshwaterecology.info database was primarily described in terms of type of food (except for filterers), whereas the other databases described feeding mode in terms of strategies of food acquisition.
+For example, the freshwaterecology.info database defined predator as "eating from prey", and the other databases used the mouthpart morphology as the basis for their definitions.
+The Tachet database captured the food source in a separate grouping feature.
 Locomotion definitions also differed in focus among databases.
-The New Zealand and freshwaterecology.info databases described locomotion as an organism’s way of movement, Tachet as substrate relation and locomotion, Vieira as how organisms deal with flow, Australia as attachment, and CONUS included not only the method of movement but also the location of movement.
-Similarly, databases differed in their focus for reproduction traits.
+The New Zealand and freshwaterecology.info databases described locomotion as an organism’s way of movement, the Tachet database as substrate relation and locomotion, the Vieira database as how organisms deal with flow, the Australia database as attachment, and the CONUS database as not only the method of movement but also the location of movement.
+Similarly, databases differed in the way they characterise reproduction traits.
 In the freshwaterecology.info and Tachet databases, reproduction was captured in one grouping feature and was defined as location of oviposit clutches and mode of reproduction.
@@
   \toprule[.1em]
-  Database & \specialcell{Comparison to\\ traits at family level} & \specialcell{Differing \\ cases [\%]} & \specialcell{Min.
+  \specialcell{Data \\ origin} & \specialcell{Comparison to\\ traits at family level} & \specialcell{Differing \\ cases [\%]} & \specialcell{Min.
 \\ differences} & \specialcell{Max.
@@
   \toprule[.1em]
-  \multirow{4}{*}{\specialcell{Australia}} & \specialcell{\textit{direct\_agg (median)}} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
+  \multirow{4}{*}{\specialcell{AUS}} & \specialcell{\textit{direct\_agg (median)}} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
   & \specialcell{\textit{direct\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
@@
   \midrule
-  \multirow{4}{*}{\specialcell{North America}} & \specialcell{\textit{direct\_agg (median)}} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
+  \multirow{4}{*}{\specialcell{NA}} & \specialcell{\textit{direct\_agg (median)}} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
   & \specialcell{\textit{direct\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
@@
   \centering
-  Abbreviations: Min., Minimum; Max., Maximum; abs., absolute; SD, Standard deviation.
+  Abbreviations: Min., Minimum; Max., Maximum; abs., absolute; SD, Standard deviation; AUS, Australia; NA, North America.
   }
@@
 
-\subsubsection*{Comparison of aggregation methods with varying taxonomic hierarchies and trait variability}
+\subsubsection*{Comparison of aggregation methods with varying phylogenies and trait variability}
 
-Our simulation results showed that both taxonomic hierarchical structure and trait variability affected aggregated trait affinities, although only to a small degree, and that aggregation method mattered in terms of the ranges of trait affinities produced over simulation replicates.
-The effect of taxonomic hierarchy differed across aggregation methods, but, as we expected, the produced range of trait affinities increased with increasing trait variability for all aggregation methods (Figure \ref{fig:overview_sim_results}).
+The simulations showed that both phylogenetic structure and trait variability affected aggregated trait affinities, although only to a small degree, and that aggregation method mattered in terms of the ranges of trait affinities produced over simulation replicates.
+The effect of phylogenetic structure differed across aggregation methods, but, as we expected, the range of trait affinities increased with increasing trait variability for all aggregation methods (Figure \ref{fig:overview_sim_results}).
 % Ben would add: % as indicated by the increasing range of the boxes and wiskers with increasing standard deviation.
 
-Taxonomic hierarchical structure appeared to influence the outcomes of the different aggregation methods.
+Phylogenetic structure appeared to influence the outcomes of the different aggregation methods.
 For the \textit{sim\_base} scenario (equal numbers of genera and species), the mean and weighted aggregation methods yielded similar ranges of aggregated trait affinities within each level of trait variability, and the median aggregation methods consistently produced greater ranges of aggregated trait affinities than the other methods.
 The largest ranges were produced by the \textit{stepwise\_agg \textsubscript{median}} method.
-For the more complex taxonomic hierarchical structures, \textit{sim\_extreme} (one genus with a much larger number of species than the other four) and \textit{sim\_variation} (all genera with a different number of species), the \textit{stepwise\_agg \textsubscript{median}} method still produced the largest ranges of trait affinities for most levels of trait variability (and \textit{direct\_agg\textsubscript{mean}} produced the narrowest ranges for most levels of trait variability), but there was much less consistency in the ranges of trait affinities for all aggregation methods (i.e., the ranges were different among all aggregation methods).
+For the more complex phylogenetic structures, \textit{sim\_extreme} (one genus with a much larger number of species than the other four) and \textit{sim\_variation} (all genera with a different number of species), the \textit{stepwise\_agg \textsubscript{median}} method still produced the largest ranges of trait affinities for most levels of trait variability (and \textit{direct\_agg\textsubscript{mean}} produced the narrowest ranges for most levels of trait variability), but there was much less consistency in the ranges of trait affinities for all aggregation methods (i.e., the ranges were different among all aggregation methods).
 
-Although trait aggregation methods were affected by taxonomic hierarchical structure and trait variability to some degree, in most simulated datasets, the different aggregation methods resulted in similar trait affinities.
-Only 1.42 \%, or 213 out of 15.000 total comparisons (3 scenarios $*$ 5 levels of trait variability $*$ 10 unique comparisons of trait aggregation methods $*$ 100 replicates) showed a difference equal or greater than an absolute trait affinity of 0.1.
+Although trait aggregation methods were affected by phylogenetic structure and trait variability to some degree, in most simulated datasets, the different aggregation methods resulted in similar trait affinities.
+Only 1.4 \%, or 213 out of 15.000 total comparisons (3 scenarios $\times$ 5 levels of trait variability $\times$ 10 unique comparisons of trait aggregation methods $\times$ 100 replicates) showed a difference equal or greater than an absolute trait affinity of 0.1.
 Most  (83.5 \%) of these differences occurred in the \textit{sim\_extreme} scenario and were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure \ref{fig:sim_indv_runs}).
@@
 
-\subsection*{Effects of harmonisation and trait aggregation on trait-environ\-ment relationships}
+\subsection*{Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships}
 
@@
 The original RDA indicated that upstream sites (lower salinity) were characterised by the traits: univoltinism, oviposition in clutches, and short life-cycle duration ($< 1$ year), and RDA with the harmonised data characterised upstream sites by univoltine taxa with short life-cycle durations that lay their eggs in an aquatic environment (aquatic eggs).
-This difference in oviposition trait is not substantial because the trait aquatic eggs of the harmonised grouping feature oviposition was derived by combining the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonisation}).
+This difference in the oviposition trait is not substantial because the trait aquatic eggs of the harmonised grouping feature oviposition was derived by combining the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonisation}).
 
-RDA using harmonised traits that were aggregated to family level also produced results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
+RDA based on harmonised traits that were aggregated to family level also produced results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
 The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg} characterised the downstream sites with the same traits as the original analysis except the trait shredder.
@@
 Freshwater invertebrate trait databases are a valuable source of data that are freely available to researchers and that can offer opportunities for large-scale, cross-regional ecological study without the need for time-consuming and expensive field work.
-However, a lack of consistency among regional and continent-wide databases in trait definitions, trait affinity coding, and taxonomic resolution presents challenges to the use of multiple databases for a single study.
+However, a lack of consistency among regional and continent-wide databases in trait definitions, trait affinity coding, and taxonomic resolution can greatly limit the use of combined databases.
 We explored the effects of harmonising grouping features and aggregating trait affinities at different taxonomic levels from databases from four different continents on the outcomes of trait affinities and on analysis of trait–environment relationships.
-We found that despite discrepancies in trait definitions and taxonomic resolution across databases, harmonised and aggregated data were useful in identifying trait–environmental relationships, as evidenced by similar results from RDA as were found using observational data.
+We found that despite discrepancies in trait definitions and taxonomic resolution across databases, harmonised and aggregated data were generally effective in identifying trait–environmental relationships, as evidenced by similar results from RDA as were found using observational data.
 Our results have implications for future multi-regional ecological studies that may benefit from the use of existing databases and provide insight into methods for harmonising traits with differing trait definitions and selecting aggregation methods that minimize either cases or ranges of differences in trait affinity scores when aggregating from higher to lower taxonomic precision.
@@
 Synthesizing trait information from multiple trait databases is crucial for developing the full potential of trait-based approaches, such as for studying community trait responses to environmental gradients across geographic regions.
-Others have noted the lack of standardised trait terminology in freshwater ecology (\cite{baird_toward_2011, brink_traits-based_2011}), but we are the first to describe invertebrate trait definition discrepancies for some commonly used grouping features.
-Our experience can offer some insight into the need for, and process of, harmonising invertebrate trait information from trait databases of different regions.
+Others have noted the lack of standardised trait terminology in freshwater ecology (\cite{baird_toward_2011, brink_traits-based_2011}), but in this study we show for the first time the discrepancies that exist across some commonly used grouping features.
+Furthermore, we offer insight into the need for, and process of, harmonising invertebrate trait information from trait databases of different regions.
 Some of the challenges we found were that grouping features were resolved differently into traits in different databases and that various codings (fuzzy, categorical, binary) were used to describe traits.
@@
 We aimed to use most of the available invertebrate trait information for different regions to establish harmonised grouping feature datasets, but the availability of trait information varied strongly across grouping features and databases.
-For instance, there was extensive information available for grouping features that are often used in trait–environment studies, such as feeding mode and respiration, but there was surprisingly little information on body form, a trait that is relatively easy to determine.
+For instance, extensive information was available for grouping features that are often used in trait–environment studies, such as feeding mode and respiration, but there was surprisingly little information on body form, a trait that is relatively easy to characterise.
 
@@
 The core of this harmonisation initiative is to provide standardised trait definitions and to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field.
-Such initiatives could be a role model for freshwater ecologists to establish unambiguous terminologies for invertebrate traits.
+Such initiatives should encourage freshwater ecologists to establish unambiguous terminologies for invertebrate traits.
 The existing freshwater invertebrate trait databases could be linked through standardised terminologies or ontologies, as suggested by \citet{baird_toward_2011}.
 By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS), providers of invertebrate trait data could connect their traits to such ontologies (\cite{schneider_towards_2019}).
-Once standardised trait definitions are established, these will improve trait data sharing, trait data processing when working with multiple trait databases, and, ultimately, interpretation of the derived results.
+Once standardised trait definitions are established, they will improve trait data sharing, trait data processing when working with multiple trait databases, and, ultimately, interpretation of the derived results.
 
@@
 
-Observational data for freshwater invertebrates are often resolved to a variety of taxonomic levels because species-level identification can be complicated, time-consuming, and expensive (\cite{marshall_taxonomic_2006, resh_which_2008}).
-Consequently, trait information at family level has been widely used by freshwater ecologists, for example in bioassessment (\cite{beketov_spear_2009}).
-However, assigned traits at family level may not reflect the real trait diversity within, for example, a taxon in the large, ecologically diverse family Chironomidae (\cite{serra_synthesising_2016}).
-Additionally, various trait aggregation methods have been used by researchers to allow comparison among traits at different taxonomic levels.
+The taxonomic resolution used to describe the occurrence and abundance of freshwater invertebrates can be highly variable because species-level identifications require specialists and are also often time-consuming and expensive (\cite{marshall_taxonomic_2006, resh_which_2008}).
+Consequently, trait information at the family level has been widely used by freshwater ecologists, for example in bioassessment (\cite{beketov_spear_2009}).
+However, traits assigned at the family level may not reflect the full trait diversity that exists within, for example, large, ecologically diverse families such as Chironomidae (\cite{serra_synthesising_2016}).
+Additionally, various trait aggregation methods have been used by researchers to compare trait profiles based on different taxonomic levels.
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait is for a particular family.
-Aggregation of trait information at species or genus level to a point estimate at family level suggests a precision that is not necessarily present, especially not for traits with high variability or if trait information at species level is missing.
-Indeed, some traits can vary strongly at more precise taxonomic levels than the family level.
-For example, \citet{monaghan_improving_2013} found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction.
-Further, studies focusing on the lability of traits, (i.e.
+Aggregation of trait information at the species or genus level to a single estimate at the family level implies a precision that is not necessarily present, especially not for traits with high variability or if trait information at species level is missing.
+Indeed, some traits can vary strongly at more resolved taxonomic levels than the family level.
+For example, \citet{monaghan_improving_2013} found high intra-family trait dispersion in the Tachet database for traits within the grouping features body size, flow preference, and reproduction.
+Furthermore, studies focusing on the lability of traits, (i.e.
 how much traits are constrained by phylogeny), found that traits of ecological preferences (e.g.
@@
 
-If trait aggregation is necessary, however, our study can offer insight about the circumstances under which the choice of aggregation method may be important.
+If trait aggregation is necessary, however, our study offers insights about the circumstances under which the choice of aggregation method may be important.
 The 5 aggregation methods we tested used either the mean or the median and different weightings to assign family-level affinities.
@@
 However, when differences occurred between median aggregation methods and assigned traits, these differences were greater in absolute value compared with the mean aggregation methods, particularly for the North American dataset where mean absolute differences for median aggregations were twice as high as for mean aggregations.
-This pattern of greater differences for median than mean aggregations can, in large part, be explained by the binary coding used in the North American trait dataset and by the assigned traits.
+This pattern of greater differences for median than mean aggregations is probably caused by the use of binary coding in the North American trait dataset and by the assigned traits.
 Binary coded traits have affinities of either 1 or 0; therefore, traits of a particular grouping feature showed, in most cases, a higher difference in trait affinities to each other than if they were fuzzy coded.
 Median-aggregated binary-coded taxa often resulted in a value of 0 or 1, whereas mean aggregation often yielded values between 0 and 1.
-Thus, using the median led for the North American dataset either to agreement with the assigned traits or to higher differences compared to the mean aggregation methods.
+Thus, using the median resulted in the North American dataset either to agreement with the assigned traits or to more substantial differences compared to the use of mean aggregation methods.
 This pattern inherent in using median-aggregation methods to aggregate binary-coded data should be considered when researchers choose methods to resolve affinities at different taxonomic levels.
 
-We expected that, in addition to averaging measure, different weighting approaches to aggregation (i.e., equal weight to each taxon, equal weight to each genus, or weighted by number of species) would affect affinities for families with varying taxonomic hierarchical structure.
-However, we found through simulations that although taxonomic structural unevenness appeared to produce variation in affinities among weighting approaches, especially for a family where one genus had a much larger number of species than its other genera, trait variability had a greater effect on the range of affinities (i.e., greater ranges of affinities at higher levels of variance) and on the differences in affinities between weighting methods.
-Also, the number of differing cases and the mean absolute differences in trait affinities, as well as the distributions of absolute trait affinity differences to assigned traits, were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weighting approach on the aggregation outcomes.
-The minor impact of the weighting approaches on trait aggregation may be explained by the fact that a considerable portion of taxa had low numbers of genera or species.
+We expected that, in addition to averaging measures, different weighting approaches to aggregation (i.e., equal weight to each taxon, equal weight to each genus, or weighted by number of species) would affect affinities for families with varying phylogenetic structure.
+However, we found through simulations that trait variability had a greater effect on the range of affinities (i.e., greater ranges of affinities at higher levels of variance) and on the differences in affinities between weighting approaches.
+In the simulation, taxonomic structural unevenness appeared to produce some variation in affinities among weighting approaches, especially for a family where one genus had a much larger number of species than its other genera.
+The comparison between aggregated and assigned traits showed, that the number of differing cases and the mean absolute differences in trait affinities, as well as the distributions of absolute trait affinity differences to assigned traits, were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weighting approach on the aggregation outcomes.
+The minor impact of the weighting approaches on trait aggregation might be explained by the fact that a considerable portion of taxa had low numbers of genera or species.
 Of the taxa that were compared from the North American trait dataset, 14 \% were identified at family and 62 \% at genus level, 52 \% comprised five or fewer genera, and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
@@
 
-By reanalysing trait–environment relationships identified in \citet{szocs_effects_2014} with our harmonised and family-level aggregated datasets, we have illustrated the potential for the use of harmonised and aggregated data in ecological research.
-As far as we are aware, ours is the first study to compare trait–environment relationships using harmonised and non-harmonised data.
+By reanalysing trait–environment relationships identified in \citet{szocs_effects_2014} with our harmonised and family-level aggregated datasets, we illustrated the potential for the use of harmonised and aggregated data in ecological research.
+As far as we are aware, ours is the first study to compare inferences regarding trait–environment relationships based on harmonised and non-harmonised data.
 Our re-analysis of the data on salinisation effects on biological traits yielded only slightly different results compared with the original study, which agrees with previous findings that family-level traits can be sensitive enough to detect environmental impacts (\cite{beketov_spear_2009}).
-However, some of the traits that had responded in the original analysis did not respond in the re-analysis: feeding mode shredder, respiration gills, and life-cycle duration traits.
+However, some of the traits that had responded in the original analysis did not respond in the re-analysis, specifically feeding mode shredder, respiration gills, and life-cycle duration traits.
 There are several possible reasons for these discrepancies.
 The non-responsive traits were those closest to the threshold for association with either higher or lower salinity, and so the precision lost through trait harmonisation may have decreased our ability to detect a relatively weak association.
-Feeding mode shredder was the only trait that was non-responsive when using harmonised (but not aggregated) data as well as when using aggregated data.
-This result was likely because of the harmonisation procedure, when this trait was combined based on three traits (miner, xylophagus, and shredder).
+The shredder feeding mode was the only trait that was non-responsive when using harmonised (but not aggregated) data as well as when using aggregated data.
+This result was likely because of the harmonisation procedure, in which this trait was combined based on three traits (miner, xylophagus, and shredder) used in the original databases.
 Consequently, the trait affinities in the original data had a higher mean and standard deviation than in the harmonised and aggregated data (Table \ref{tab:SI_resp_traits_summary_stats}), suggesting that the signal in the original data was weakened by harmonisation.
-Following this result, we suggest that if harmonisation is necessary, harmonised and non-harmonised data, if available, should be compared, and possible averaging effects should be considered in further analyses.
-However, our results illustrate that where site-level data are not available, harmonised and aggregated datasets may be useful in identifying at least the strongest associations between traits and environmental conditions.
+Given this result, we suggest that if harmonisation is necessary, harmonised and non-harmonised data, if available, should be compared, and possible averaging effects should be considered in further analyses.
+However, our results also illustrate that where site-level data are not available, harmonised and aggregated datasets may be useful in identifying at least the strongest associations between traits and environmental conditions.
 
@@
 
-As ecological knowledge increases, and with the aid of new  methods such as computer vision for species and trait identification (\cite{hoye_deep_2020}), more observational and species-level trait data may become available in the future, reducing the need for trait aggregation.
+As ecological knowledge increases, and with the help of new methods such as computer vision for species and trait identification (\cite{hoye_deep_2020}), more observed taxa will be identified to the species level and trait data will be available at the species level in the future, reducing the need for trait aggregation.
 However, we showed that trait aggregation is often in agreement with expert assignments, especially through aggregation approaches that use the median.
-No aggregation method is objectively the best, and except for cases where traits are highly variable and taxonomic hierarchical structure is highly uneven, choice of aggregation method does not appear to be influential on the outcome.
+Based on this analysis, we cannot claim that a specific aggregation method is objectively the best, and except for cases where traits are highly variable and phylogenetic structure is highly uneven, the choice of aggregation method does not appear to be influential to the outcome.
 Weighting trait information based on the taxa present in the database used does not seem to have much influence except when the taxonomic hierarchical structure is highly uneven.
@@
 We also suggest that a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
-Through the use of carefully synthesised data from freshwater invertebrate trait databases, while acknowledging the limitations inherent in harmonised and aggregated data, the ability to investigate a wide range of large-scale ecological questions is enhanced.
+Use of carefully harmonised and integrated trait data as described here should  enhance our ability to study a wide range of large-scale ecological questions with greater rigor than currently exists.
 

### 2021-02-19 Paper/Draft_harmonization_paper.tex
19.02: Minor fixes figures NA

@@
 \usepackage{caption}
-\usepackage{ccaption}
 \usepackage{authblk}
@@
 natbib,
-style = apa6,
+style = apa,
 citestyle = authoryear,
@@
 \affil[9]{Department of Watershed Sciences, National Aquatic Monitoring Center, and the Ecology Center, Utah State University, Logan, USA}
-\date{}
 
@@
 \section*{Abstract}
-
-% FROM FRESHWATER BIOLOGY Website:
-% All papers should include a summary, in short numbered paragraphs, limited to about 3% of the length of the text, and in any case to not more than 500 words.
-This should provide a concise statement of the scope of the work and its principal findings and be fully intelligible without reference to the main text.
-It is helpful to structure your abstract as follows: point 1 = background to and reason for the study and the aims; point 2 = brief description of methods used; point 3 = main project results (address the aims); point 4 = conclusions of your study; point 5 = the contribution that your results make to the field / why your study is useful to an international audience.
-Referring to abstracts in recently published issues may help with structuring an abstract.
-
-% Alternative start: Invertebrate traits are increasingly used in ecological studies because they provide a mechanistic understanding of species-environment relationships and are suitable for large scale analysis due to their consistent response to environmental gradients.
 
@@
 At present, it is unknown how different trait aggregation approaches compare with expert-assigned trait affinities.
-In this study we aimed to identify discrepancies in trait definitions across freshwater invertebrate databases and to compare trait aggregation methods to identify how taxonomic hierarchy structure and trait variability influence results from different aggregation approaches.
+In this study we aimed to identify discrepancies in trait definitions across freshwater invertebrate databases and to compare trait aggregation methods to identify how phylogenetic structure and trait variability influence results from different aggregation approaches.
 
@@
 A third challenge to comparing across invertebrate trait databases is inconsistent coding of trait data (\cite{culp_incorporating_2011}).
-Coding of trait data is usually done by assigning an affinity (aka affinity score) of an invertebrate taxon to express a particular trait %, either using a binary classification (0/1), continuous or fuzzy classification (0 - 1 or 0 - 100 \%).
+Coding of trait data is usually done by assigning an affinity (aka affinity score) of an invertebrate taxon to express a particular trait.
 Traits of individual freshwater invertebrates can be difficult to quantify because, unlike plant traits, they are often difficult to measure directly.
@@
 
-% Other alternative from Brooke: These challenges when working with or synthesizing trait data motivated us to assess the characteristics and comparability of freshwater invertebrate trait data contained in disparate databases.
-We aimed to explore methods of improving the comparability of trait data across databases, despite differences in trait grouping-feature definitions, affinity score coding, and taxonomic level of data, through two study objectives: (1) to investigate the plausibility of comparing across databases from different geographic regions by providing harmonised datasets from Europe, North America, Australia, and New Zealand; and (2) to compare the influence of different trait aggregation methods on the characterisation of trait–environment relationships.
-
 \newpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Discrepancies in trait definitions served as a starting point to develop four novel invertebrate trait datasets by harmonising seven grouping features present in the existing trait databases.
-The harmonised trait datasets were used to evaluate the influence of different trait aggregation approaches on the identification of trait–environment relationships, our third study objective, in two ways by (1) comparing family-level aggregated trait affinities with family-level trait affinities assigned by experts for two of the established trait datasets where such data were available and (2) comparing the influence of taxonomic hierarchy and trait variability on the outcomes of the different trait aggregation approaches for simulated data.
+The harmonised trait datasets were used to evaluate the influence of different trait aggregation approaches on the identification of trait–environment relationships, our third study objective, in two ways by (1) comparing family-level aggregated trait affinities with family-level trait affinities assigned by experts for two of the established trait datasets where such data were available and (2) comparing the influence of taxonomic phylogeny and trait variability on the outcomes of the different trait aggregation approaches for simulated data.
 Finally, to further investigate how harmonising and aggregating trait data can modify the outcomes of trait–environment relationship characterisation, we used data from one of the newly established datasets with harmonised and aggregated traits to repeat an analysis of salinisation effects on biological traits (\cite{szocs_effects_2014}) and compared our results with those of the original study.
@@
 
-% TODO Figure caption next page?
 \begin{figure}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.
-Abbreviations: AUS, Australia; NOA, North America.}
+Abbreviations: AUS, Australia; NA, North America.}
   \label{fig:diff_aggr_traits_combined}
@@
 The effect of phylogenetic structure differed across aggregation methods, but, as we expected, the range of trait affinities increased with increasing trait variability for all aggregation methods (Figure \ref{fig:overview_sim_results}).
-% Ben would add: % as indicated by the increasing range of the boxes and wiskers with increasing standard deviation.
 
@@
   \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
-  \caption{Comparison between the aggregated trait affinities produced by the different trait aggregation methods for every simulated dataset across all 3 simulated traits (5,000 comparisons per taxonomic hierarchy scenario).
+  \caption{Comparison between the aggregated trait affinities produced by the different trait aggregation methods for every simulated dataset across all 3 simulated traits (5,000 comparisons per scenario).
 Results are shown for different levels of trait variability which is represented by the standard deviation (SD) of the simulated traits.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-02-19 Paper/Draft_harmonization_paper.tex
19.02: Fixes font size

@@
 \usepackage{longtable}
+\usepackage{etoolbox}
 \usepackage{hhline}
@@
 \onehalfspacing
+
+\captionsetup{font=small}
+
+\AtBeginEnvironment{tabular}{\small}
+\AtBeginEnvironment{longtable}{\small}
 
@@
 A third challenge to comparing across invertebrate trait databases is inconsistent coding of trait data (\cite{culp_incorporating_2011}).
-Coding of trait data is usually done by assigning an affinity (aka affinity score) of an invertebrate taxon to express a particular trait.
 Traits of individual freshwater invertebrates can be difficult to quantify because, unlike plant traits, they are often difficult to measure directly.
@@
 Fuzzy codes, which are usually converted to proportions, are used to account for plasticity in traits, variability in traits within taxonomic groups above the species level, and incomplete knowledge.
+The values derived from the different coding approaches represent affinities (aka affinity scores) that indicate how strongly a taxon expresses a particular trait.
 The use of different types of coding for trait affinities in different databases limits comparisons.
@@
 \begin{landscape}
-\begin{longtable}{m{2.3cm}|m{3cm}|m{1.8cm}|m{1.4cm}|m{1.4cm}|m{4.1cm}|m{2cm}}
+\begin{longtable}{m{2.3cm}|m{3.3cm}|m{1.8cm}|m{1.4cm}|m{1.4cm}|m{4.4cm}|m{2cm}}
 \caption{Number of traits per grouping feature and type of coding of the traits for the grouping features used in this study per database. Oviposition location was used for the New Zealand database.}
@@
 \midrule
-Size                                                                & -                                                                                         & \begin{tabular}[c]{@{}l@{}}7 traits;\\ fuzzy {[}0 - 3{]}\end{tabular}  & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}   & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary, continuous, \\ \\ fuzzy {[}0 - 3{]}\end{tabular}             & \begin{tabular}[c]{@{}l@{}}5 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+Size                                                                & -                                                                                         & \begin{tabular}[c]{@{}l@{}}7 traits;\\ fuzzy {[}0 - 3{]}\end{tabular}  & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}   & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary, continuous, \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}5 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
 \midrule

### 2021-02-19 Paper/Results/SI.tex
19.02: Minor fixes figures NA
19.02: Fixes font size

@@
     \centering
-    \includegraphics[width=16.5cm, height=12cm]{Deviances_trait_agg_pyne.png}
+    \includegraphics[width=15cm, height=12cm]{Deviances_trait_agg_pyne.png}
     \caption{Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the North American dataset.
@@
 
-\subsection*{Effects of harmonisation and trait aggregation on trait-environment relationships}
+\newpage
+
+\subsection*{Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships}
 

### 2021-02-20 Paper/Draft_harmonization_paper.tex
19.02: Small fixes graphs
20.02: Final fixes

@@
 \usepackage{lmodern}
+% \usepackage[style = apa]{biblatex}
 \usepackage[
@@
 natbib,
-style = apa,
 citestyle = authoryear,
+bibstyle = apa6,
 maxcitenames = 2, 
@@
 
+% raplace "and" in authoryear in-text citations with "&" 
+\renewcommand*{\finalnamedelim}{%
+  \ifnumgreater{\value{liststop}}{2}{\finalandcomma}{}%
+  \addspace\&\space}
+
 % Keywords command
@@
 {
-  \small	
+  {\small	
   \textbf{\textit{Keywords---}} #1
-}
+}}
 
@@
 
-\captionsetup{font=small}
-
-\AtBeginEnvironment{tabular}{\small}
-\AtBeginEnvironment{longtable}{\small}
+\listfiles
 
@@
 \affil[9]{Department of Watershed Sciences, National Aquatic Monitoring Center, and the Ecology Center, Utah State University, Logan, USA}
+\date{}
 
@@
 Our results also illustrate the usefulness of harmonised datasets for ecological study and provide guidance for the circumstances under which the choice of trait aggregation method is important.
-\\
 \\
@@
 To do so we combined similar traits into one trait (e.g.
-crawlers and sprawlers into crawlers) and for each taxon we assigned for the new combined trait the highest affinity score of those originally assigned to the subsequently combined traits.
-% and assigned the highest trait affinity score among the combined traits for each taxon.  
+crawlers and sprawlers into crawlers) by assigning for each taxon for the new combined trait the highest affinity score of those originally assigned.
 Next, we selected taxa for inclusion in our datasets and normalised the trait affinity scores for each taxon.
@@
 We assumed that values of 1 and 0 for binary traits corresponded to the highest and lowest affinity for a particular trait.
-
-\newpage
 
@@
 Because trait affinities ranged from 0 to 1, the maximum difference possible in trait affinity was 1 to –1, both of which corresponds to 100 \%.
-For convenience and to improve interpretation, we calculated absolute values of the trait differences, i.e.
+For convenience and to improve interpretation, we calculated absolute values of the trait differences, e.g.
 a difference of -1 was converted to 1.
-
-\newpage
 
@@
   \subfile{Flowchart/Flowchart_methods.tex}
-  \label{fig:data_proc_overview}
+  % \label{fig:data_proc_overview}
 \end{figure}
@@
 
-\newpage
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-All data processing and RDA analyses were carried out using R (\cite{cite_R}).
+All data processing and RDA analyses were carried out using R version 3.6.1 (\cite{cite_R}).
 RDA was computed using the vegan package (\cite{cite_vegan}).
@@
   \includegraphics[width=17cm, height=14.5cm]{boxplot_scores_combined.png}
-  \caption{RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{median}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
+\end{figure}
+\begin{center}
+\captionof{figure}{RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{median}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
 Shown are boxplots of the site scores along the conductivity axis.
@@
 \label{fig:boxplot_scores_on_constrained_axis}
-\end{figure}
+\end{center}
 

### 2021-02-20 Paper/Submission/Main_Document_Latex.tex
20.02.: Created submission files

--- 2021-02-20 Paper/Draft_harmonization_paper.tex
@@
 \usepackage{lmodern}
-% \usepackage[style = apa]{biblatex}
 \usepackage[
@@
 \addbibresource{Ref_invertebrate_DB.bib}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% From freshwater biology:
-% List all sources in the reference list alphabetically by name.
-In text citations should follow the author-date method.
-This means that the author's last name and the year of publication for the source should appear in the text, for example, (Jones, 1998), and a complete reference should appear in the reference list at the end of the paper.
-
-% References are styled according to the sixth edition of the Publication Manual of the American Psychological Association.
-A sample of the most common entries in reference lists appears below.
-Please note that for journal articles, issue numbers are not included unless each issue in the volume begins with page one.
-
-% Article: 
-% One author: Fawcett, T. (2006). An introduction to ROC analysis. Pattern Recognition Letters, 27(8), 861–874. DOI: 10.1016/j.patrec.2005.10.010.
-
-% 2 to 7 authors: Daley, C. E., & Nagle, R. J. (1996). Relevance of WISC-III Indicators for assessment of learning disabilities. Journal of Psychoeducational Assessment, 14 (4), 320–333.
-
-% More than 7 authors: Rutter, M., Caspi, A., Fergusson, D., Horwood, L.
-J., Goodman, R., Maughan, B., … Carroll, J.
-(2004).
-Sex differences in developmental reading disability: New findings from 4 epidemiological studies.
-Journal of the American Medical Association, 291(16), 2007–2012.
-DOI: 10.1001/jama.291.16.2007
-
-% In press or forthcoming: van Bergen, E., de Jong, P.
-F., Maassen, B., Krikhaar, E., Plakas, A., & van der Leij, A.
-(in press).
-IQ of four-year-olds who go on to develop dyslexia.
-Journal of Learning Disabilities.
-DOI: 10.1177/0022219413479673
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 At present, it is unknown how different trait aggregation approaches compare with expert-assigned trait affinities.
-In this study we aimed to identify discrepancies in trait definitions across freshwater invertebrate databases and to compare trait aggregation methods to identify how phylogenetic structure and trait variability influence results from different aggregation approaches.
+In this study we aimed to identify discrepancies in trait definitions across freshwater invertebrate databases and to compare trait aggregation methods to identify how phylogenetic structure and trait variability influence results from different aggregation methods.
 
@@
 The coding to describe traits (binary, fuzzy) also varied among databases.
-Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially when aggregation was based on the median, and that trait coding method, uneven taxonomic hierarchical structure, and high trait variability can influence aggregated trait affinities.
+Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially when aggregation was based on the median, and that trait coding method, uneven phylogenetic structure, and high trait variability can influence aggregated trait affinities.
 We further showed that harmonised and aggregated data performed similarly to not aggregated and harmonised data from the case study in identifying trait–environment relationships.
@@
 To date, such analyses have been carried out mostly within continents, using information from one or two trait databases.
-For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe based on traits from \citet{ussegliopolatera_biological_2000} (typically referred to as the Tachet database), \citet{poff_developing_2010} characterized trait composition across sites in the Western USA based on traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} used trait definitions from \citet{poff_functional_2006} and \citet{schafer_trait_2011} to test for effects of salinity on invertebrate traits across different sites in South Australia.
-Analyses that synthesize invertebrate trait information from more than two different continents are rare, but see \citet{brown_functional_2018} and \citet{statzner_reproductive_1997}.
+For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe based on traits from \citet{ussegliopolatera_biological_2000} (typically referred to as the Tachet database), \citet{poff_developing_2010} characterised trait composition across sites in the Western USA based on traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} used trait definitions from \citet{poff_functional_2006} and \citet{schafer_trait_2011} to test for effects of salinity on invertebrate traits across different sites in South Australia.
+Analyses that synthesise invertebrate trait information from more than two different continents are rare, but see \citet{brown_functional_2018} and \citet{statzner_reproductive_1997}.
 
 The variability and inconsistencies of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of comparisons across continents.
-Several challenges currently prevent use of invertebrate trait data from different established databases in ecological studies.
+Several challenges currently prevent the use of invertebrate trait data from different established databases in ecological studies.
 One challenge is inconsistency in terminology.
 In this study, we follow the terminology proposed by \citet{schmera_proposed_2015}, in which a grouping feature (e.g.
-feeding mode) refers to a set of related organismal traits (e.g.
+feeding mode) refers to a set of related traits (e.g.
 predator, shredder, etc.) that together define an ecological property that is shared among individuals or species.
@@
 To harmonise grouping features from different regions, or to structure them in such a way as to facilitate cross-database comparison, commonly accepted and unambiguous trait definitions are required (\cite{schneider_towards_2019}).
-Ideally, the same traits and grouping features would be reported across databases or standardised terminology would exist to easily harmonise them; however, standardised terminology of trait definitions is lacking and poor metadata quality in many trait databases make, harmonisation of grouping features difficult (\cite{baird_toward_2011, kissling_towards_2018}).
+Ideally, the same traits and grouping features would be reported across databases or standardised terminology would exist to easily harmonise them; however, standardised terminology of trait definitions is lacking and poor metadata quality in many trait databases make harmonisation of grouping features difficult (\cite{baird_toward_2011, kissling_towards_2018}).
 To our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on the functional diversity of invertebrate assemblages.
@@
 
-Finally, discrepancies in the taxonomic resolutions (e.g., species, genus, or family) used when comparing among trait databases, or when linking counted taxonomic data to trait databases, presents another challenge.
+Finally, discrepancies in the taxonomic resolutions (e.g., species, genus, or family) used when comparing among trait databases, or when linking observed taxonomic data to trait databases, presents another challenge.
 When taxonomic composition or data in on trait database are at a more precise taxonomic level than other trait data (e.g.
@@
 These challenges motivated us to assess the characteristics and comparability of different freshwater invertebrate trait databases with the goal of facilitating future syntheses.
-We aimed to identify methods of improving the comparability of trait data across databases, despite differences in trait definitions and the taxonomic level of data in three ways: (1) by describing discrepancies in trait definitions between trait databases from Europe, North America, Australia, and New Zealand; (2) by harmonising trait definitions across databases to provide consistent trait grouping features for comparison across geographic locations; and (3) by comparing the influence of different trait aggregation methods and grouping-feature harmonisation on the detection of trait–environment relationships.
+We aimed to identify methods of improving the comparability of trait data across databases, despite differences in trait definitions and the taxonomic level of data in three ways: (1) by describing discrepancies in trait definitions between trait databases from Europe, North America, Australia, and New Zealand; (2) by harmonising trait definitions across databases to provide consistent grouping features for comparison across geographic locations; and (3) by comparing the influence of different trait aggregation methods and grouping-feature harmonisation on the detection of trait–environment relationships.
 
@@
 Discrepancies in trait definitions served as a starting point to develop four novel invertebrate trait datasets by harmonising seven grouping features present in the existing trait databases.
-The harmonised trait datasets were used to evaluate the influence of different trait aggregation approaches on the identification of trait–environment relationships, our third study objective, in two ways by (1) comparing family-level aggregated trait affinities with family-level trait affinities assigned by experts for two of the established trait datasets where such data were available and (2) comparing the influence of taxonomic phylogeny and trait variability on the outcomes of the different trait aggregation approaches for simulated data.
+The harmonised trait datasets were used to evaluate the influence of different trait aggregation methods on the identification of trait–environment relationships, our third study objective, in two ways by (1) comparing family-level aggregated trait affinities with family-level trait affinities assigned by experts for two of the established trait datasets where such data were available and (2) comparing the influence of phylogenetic structure and trait variability on the outcomes of the different trait aggregation approaches for simulated data.
 Finally, to further investigate how harmonising and aggregating trait data can modify the outcomes of trait–environment relationship characterisation, we used data from one of the newly established datasets with harmonised and aggregated traits to repeat an analysis of salinisation effects on biological traits (\cite{szocs_effects_2014}) and compared our results with those of the original study.
@@
 In cases where binary coding was needed, we converted categorical and continuous traits into binary traits with values of 1 and 0, which, therefore, had the same range as fuzzy coded traits.
-For example, in the  freshwaterecology.info database, voltinism traits are associated with different faunistic regions, and we substituted a value of 1 for entries such as “arctic” or “boreal” % and 0 if no region was given.
+For example, in the  freshwaterecology.info database, voltinism traits are associated with different faunistic regions, and we substituted a value of 1 for entries such as “arctic” or “boreal”.
 We assumed that values of 1 and 0 for binary traits corresponded to the highest and lowest affinity for a particular trait.
 
-\begin{longtable}{m{2.5cm}|m{4cm}|m{7cm}}
+\begin{longtable}{m{2.5cm}|m{4cm}|m{7.5cm}}
 \caption{Traits of harmonised grouping features from six invertebrate trait databases and four geographic regions.
@@
 We then applied the five trait aggregation methods described above to each simulated dataset.
-We compared the resulting ranges of aggregated trait affinities between levels of trait variability and taxonomic hierarchical scenario as well as the differences in trait affinities obtained by each aggregation method.
+We compared the resulting ranges of aggregated trait affinities between levels of trait variability and phylogenetic scenario as well as the differences in trait affinities obtained by each aggregation method.
 
@@
   \centering
-  % \includegraphics[width=22cm, height=28cm]{Flowchart_methods.pdf}
   \subfile{Flowchart/Flowchart_methods.tex}
-  % \label{fig:data_proc_overview}
 \end{figure}
@@
 We considered CWM traits with a Mahalanobis distance greater than the 97.5 \%-quantile of the Chi-square distribution (5.02) to have responded to either lower or higher salinity.
-Additionally, to test fo the effect of different aggregation methods on inferences about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
+Additionally, to test for the effect of different aggregation methods on inferences about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
 
@@
 Raw data and the R code for data processing and grouping feature harmonisation are located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
-Scripts and data to reproduce the trait aggregation, comparison of aggregated and assigned traits, and the RDA analysis are located in the Github repository \url{https://github.com/KunzstLD/Trait-aggregation}.
+Scripts and data to reproduce the trait aggregation, comparison of aggregated and assigned traits, and the RDA analysis are located in the Github repository: \url{https://github.com/KunzstLD/Trait-aggregation}.
 
@@
 \begin{landscape}
-\begin{longtable}{m{2.3cm}|m{3.3cm}|m{1.8cm}|m{1.4cm}|m{1.4cm}|m{4.4cm}|m{2cm}}
+\begin{longtable}{m{2.5cm}|m{3.5cm}|m{2cm}|m{1.5cm}|m{1.5cm}|m{4.8cm}|m{2cm}}
 \caption{Number of traits per grouping feature and type of coding of the traits for the grouping features used in this study per database. Oviposition location was used for the New Zealand database.}
@@
 Horizontal black lines depict the median.
-Whiskers extend to the largest and smallest value respectively no further than 1.5 $*$ the inter-quartile range.
+Whiskers extend to the largest and smallest value respectively no further than 1.5 $\times$ the inter-quartile range.
 Outliers beyond the end of the whiskers are plotted as grey dots.
@@
 
-% From Freshwater biology: 
-% This should highlight the significance of the results and place them in the context of other work.
-It should not include references to figures or tables cited in the Results – check that all of your Results are presented in the Results section.
-Figures (e.g.
-photographs, conceptual diagrams) or tables presented specifically as part of the Discussion are welcome and may be cited there.
-
 Freshwater invertebrate trait databases are a valuable source of data that are freely available to researchers and that can offer opportunities for large-scale, cross-regional ecological study without the need for time-consuming and expensive field work.
@@
 
-Synthesizing trait information from multiple trait databases is crucial for developing the full potential of trait-based approaches, such as for studying community trait responses to environmental gradients across geographic regions.
+Synthesising trait information from multiple trait databases is crucial for developing the full potential of trait-based approaches, such as for studying community trait responses to environmental gradients across geographic regions.
 Others have noted the lack of standardised trait terminology in freshwater ecology (\cite{baird_toward_2011, brink_traits-based_2011}), but in this study we show for the first time the discrepancies that exist across some commonly used grouping features.
@@
 Hence, these results could change when more species-level trait information becomes available.
-Our findings show that the choice of aggregation method may matter less when taxonomic hierarchical structure is fairly even and traits are less variable, but the \textit{stepwise\_agg\textsubscript{median}} method tended to produce the widest range in affinities, especially with high taxonomic unevenness and high trait variability.
+Our findings show that the choice of aggregation method may matter less when phylogenetic structure is fairly even and traits are less variable, but the \textit{stepwise\_agg\textsubscript{median}} method tended to produce the widest range in affinities, especially with high taxonomic unevenness and high trait variability.
 
@@
 Based on this analysis, we cannot claim that a specific aggregation method is objectively the best, and except for cases where traits are highly variable and phylogenetic structure is highly uneven, the choice of aggregation method does not appear to be influential to the outcome.
-Weighting trait information based on the taxa present in the database used does not seem to have much influence except when the taxonomic hierarchical structure is highly uneven.
+Weighting trait information based on the taxa present in the database used does not seem to have much influence except when the phylogenetic structure is highly uneven.
 However, we recommend that the type of coding used to describe traits (binary, fuzzy) should be considered, because median and mean aggregations can yield very different results for binary-coded traits.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Further ideas for the discussion:
-% - What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? 
-% - Where does the classification come from? Few sources used in NOA also used in AUS:
-% AUS: Merrit \& Cummins 1978/1984 for feeding mode for a few genera and families 
-% NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait description "Cummins, K.
-W.
-Trophic Relations of Aquatic Insects" was used for feeding mode
-% - Discussion on fuzzy coding -> Uncertainty captured by fuzzy codes? 
-% - Extrapolate to "large" scale studies, i.e. studies with a stronger gradient?
-% - Traits that responded differently after harmonisation:
-% Resp gills: Original data has a lot of zeros, which are not present in the harmonised \& aggregated datasets.
-In the analysis with the harmonised dataset resp gills is not responding to the salinity gradient.
-Aggregated data look similar to the harmonised ones, but resp gills is here one of the traits responding to conductivity!
-% Why did some aggregated datasets promote life cycle duration traits and others not?
-Results using trait data obtained when aggregating with stepwise\_agg (median) and stepwise\_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites.
-% Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites
-% However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets (see Table S2). 
-% Include Ben's point? Discussion on evolutionary history?
-% Discussion point BK: It is intersting that Australia has fewer species and genus than NOA and EU (not suprisngly since the datasets in Oz were mostly delveoped at family level) but more families than these other regions.
-I wonder if this indicates that Family richness is really higher in Australia.
-Perhaps it might be as Australia has a wider range of evolutionary histories.
-This would be worth considering in the discussion
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgments}
+
+We thank Brooke Cassell for technical editing of the manuscript. The project, in which this study was conducted, is funded by the German research society (DFG, project number 338785727).
 
@@
 
-Harmonised invertebrate trait datasets for Australia, Europe, North America and New Zealand are deposited on Github. % Add link
-
-\section*{Acknowledgments}
-
-% Verena Schreiner body form traits?
-We thank Brooke Cassell for technical editing of the manuscript. The project, in which this study was conducted, is funded by the German research society (DFG, project number 338785727).
+Harmonised invertebrate trait datasets for Australia, Europe, North America and New Zealand are deposited in the Github repository: \url{https://github.com/KunzstLD/Trait-aggregation}.
 
@@
 
-\subfile{Results/SI}
+\subfile{SI}
 

### 2021-02-21 Paper/Submission_new/Main_doc.tex
21.02: Submission files try again

--- 2021-02-20 Paper/Submission/Main_Document_Latex.tex
@@
 \usepackage[utf8]{inputenc}
+\usepackage{xr-hyper}
 \usepackage{hyperref}
@@
 
+\makeatletter
+\newcommand*{\addFileDependency}[1]{% argument=file name and extension
+  \typeout{(#1)}
+  \@addtofilelist{#1}
+  \IfFileExists{#1}{}{\typeout{No file #1.}}
+}
+\makeatother
+
+\newcommand*{\myexternaldocument}[1]{%
+    \externaldocument{#1}%
+    \addFileDependency{#1.tex}%
+    \addFileDependency{#1.aux}%
+}
+
 \newcommand{\specialcell}[2][c]{%
@@
 \listfiles
+
+\myexternaldocument{SI_test}
 
@@
 
-\newpage
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{longtable}{m{2.5cm}|m{4cm}|m{7.5cm}}
-\caption{Traits of harmonised grouping features from six invertebrate trait databases and four geographic regions.
-The last column indicates traits that were combined for harmonisation (no combining needed if empty).}
-\endfirsthead
-\toprule[.1em]
-\label{tab:traits_harmonisation}
-%\begin{tabular}
-\specialcell{Grouping \\ feature} & Trait & Combined traits\\
-\toprule[.1em]
-Voltinism    & \begin{tabular}[c]{@{}l@{}}Semivoltine\\ Univoltine\\ Bi/multivoltine\end{tabular}                                & \begin{tabular}[c]{@{}l@{}}\textless 1 generation per year\\ 1 generation per year\\ \textgreater 1 generation per year\end{tabular}                                                                                                                                            \\
-\midrule
-Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattenend, dorsoventrally flattened$^{\dagger}$ \\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
-\midrule
-Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm, \textless 10 mm$^{\ddagger}$ \\ 9 - 16 mm, 10 - 20 mm\\ \textgreater 16 mm, \textgreater 20 mm\end{tabular}                                                                                                                \\
-\midrule
-Respiration  & \begin{tabular}[c]{@{}l@{}}Gills\\ Plastron/Spiracle\\ \\ \\ \\ Tegument\end{tabular}                             & \begin{tabular}[c]{@{}l@{}} Tracheal gills, gills\\ Temporary air store, spiracular gills, \\ atmospheric breathers, plant breathers, \\ functional spiracles, air (plants), aerial, \\ plastron/spiracle\\ Cutaneous, tegument \end{tabular}                                                                         \\
-\midrule
-Locomotion   & \begin{tabular}[c]{@{}l@{}}Burrower\\ Crawler\\ Sessile\\ Swimmer \end{tabular}                                     & \begin{tabular}[c]{@{}l@{}}Interstitial, boring, burrowing\\ Sprawler, walking, climber, clinger, crawler\\ Attached, sessile\\ Skating, diving, planctonic, swimming\end{tabular}                                                                                                                 \\
-\midrule
-Feeding mode & \begin{tabular}[c]{@{}l@{}}Filterer\\ \\ Gatherer\\ \\ Herbivore\\ \\ Parasite\\ Predator\\ Shredder \\ \\ \end{tabular} & \begin{tabular}[c]{@{}l@{}}Active/passive filterer, absorber, \\ filter-feeder, collector-filterer, filterer\\ Deposit-feeder, collector-gatherer, \\ detrivore, gatherer\\ Grazer, scraper, piercer herbivore, \\ herbivore, algal piercer, piercer (plants)$^{\mathsection}$\\ \\ Piercer (animals)$^{\mathsection}$, predator \\ Miner, xylophagus, shredder, \\ shredder detrivore\end{tabular} \\
-\hline
-Oviposition  & \begin{tabular}[c]{@{}l@{}}Aquatic eggs\\ \\ Ovoviviparity\\ Terrestrial eggs\end{tabular}                            & \begin{tabular}[c]{@{}l@{}}Eggs attached to substrate/plants/stones,\\ free/fixed eggs/clutches\\ \\ Terrestrial clutches, terrestrial \end{tabular}     \\
-\bottomrule[.1em]
-%\end{tabular}
-\end{longtable}
-\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-    $\dagger$ The trait "bluff (blocky)" occurred in the Vieira database and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}). \\  
-    $\ddagger$ Reflects the different size classifications by the Vieira and CONUS databases from the other trait databases. \\
-    $\mathsection$ The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases (\cite{usseglio-polatera_biomonitoring_2000}).
-Taxa exhibiting this trait have been assigned to predators or herbivores based on expert knowledge (\cite{polatera_personal_information_piercer_2020}).
-}
-\end{minipage}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
 
@@
 
-\begin{table}[ht]
-    \centering
-    \caption{Number (Nr.) of taxa per harmonised dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percent.} 
-    \label{tab:tax_coverage}
-    \begin{tabular}{l|c|c|c|c|c}
-    \toprule[.1em]
-    Dataset & Taxa (Nr.) & Aquatic insects (Nr.) & Species & Genus & Family \\ 
-    \toprule[.1em]
-    EUR & 4601 & 3942 (86) & 3739 (81) & 704 (15) & 158 (3) \\ 
-    NA & 3753 & 3305 (88) & 2414 (64) & 1163 (31) & 176 (5)  \\ 
-    AUS & 1402 & 1016 (72) & 564 (40) & 578 (41) & 260 (19) \\ 
-    NZ & 478 & 443 (93) & 404 (85) & 47 (10) & 27 (6) \\ 
-    \bottomrule
-    \end{tabular}
-\end{table}
-\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-\centering
-Abbreviations: EUR, Europe; NOA, North America; AUS, Australia; NZ, New Zealand.
-}
-\end{minipage}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 In contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
-
-\begin{table}[H]
-    \centering
-    \caption{Rounded percentage of entries that include 
-    information for the individual grouping features
-    shown per trait dataset.} 
-    \label{tab:trait_coverage}
-    \begin{tabular}{l|c|c|c|c|c|c|c}
-    \toprule[.1em]
-    Dataset & \specialcell{Body \\ form} & Oviposition & Voltinism & Locomotion & Size & Respiration & \specialcell{Feeding \\ mode} \\ 
-    \toprule[.1em]
-    EUR & 8 & 15 & 23 & 36 & 11 & 57 & 76 \\ 
-    NA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
-    AUS & 4 & 46 & 49 & 39 & 75 & 68 & 99 \\ 
-    NZ & 100 & 94 & 100 & 99 & 100 & 100 & 99 \\ 
-    \bottomrule
-    \end{tabular}
-\end{table}
-\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-\centering
-Abbreviations: EUR, Europe; NA, North America; AUS, Australia; NZ, New Zealand.
-}
-\end{minipage}
-
-\newpage
 
@@
 
-\begin{landscape}
-\begin{longtable}{m{2.5cm}|m{3.5cm}|m{2cm}|m{1.5cm}|m{1.5cm}|m{4.8cm}|m{2cm}}
-\caption{Number of traits per grouping feature and type of coding of the traits for the grouping features used in this study per database. Oviposition location was used for the New Zealand database.}
-\endfirsthead
-\toprule[.1em]
-\label{tab:trait_databases_coding_differentiation}
-\specialcell{Grouping \\ feature} & \specialcell{freshwater- \\ ecology.info} & Tachet & CONUS & Vieira & Australia & New Zealand \\
-\toprule[.1em]
-Feeding Mode & \begin{tabular}[c]{@{}l@{}}10 traits; \\ 10 point assginment \\ system\end{tabular}       & \begin{tabular}[c]{@{}l@{}}7 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}6 traits; \\ binary\end{tabular}   & \begin{tabular}[c]{@{}l@{}}8 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}16 traits$^{\dagger}$; \\ binary, proportional {[}0 - 1{]}, \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}6 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
-\midrule
-Voltinism                                                           & \begin{tabular}[c]{@{}l@{}}6 traits; \\ single category \\ assignment system\end{tabular} & \begin{tabular}[c]{@{}l@{}}3 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}3 traits;\\ binary\end{tabular}    & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}7 traits; \\ binary, proportional {[}0 - 1{]}, \\ fuzzy {[}0 - 3{]}\end{tabular}  & \begin{tabular}[c]{@{}l@{}}3 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
-\midrule
-Locomotion                                                          & \begin{tabular}[c]{@{}l@{}}6 traits; \\ 10 point assignment \\ system\end{tabular}        & \begin{tabular}[c]{@{}l@{}}8 traits; \\ fuzzy {[}0 - 5{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}10 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary, fuzzy  {[}0 - 3{]}\end{tabular}                              & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
-\midrule
-Respiration                                                         & \begin{tabular}[c]{@{}l@{}}7 traits; \\ binary\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}5 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}3 traits;  \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}8 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}10 traits; \\ binary, proportional {[}0 - 1{]}, \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
-\midrule
-\begin{tabular}[c]{@{}l@{}}Reproduction/\\ Oviposition\end{tabular} & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}8 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}10 traits;  \\ binary\end{tabular} & \begin{tabular}[c]{@{}l@{}}10 traits; \\ binary\end{tabular} & \begin{tabular}[c]{@{}l@{}}13 traits$^{\ddagger}$; \\ binary\end{tabular}                                                 & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
-\midrule
-Size                                                                & -                                                                                         & \begin{tabular}[c]{@{}l@{}}7 traits;\\ fuzzy {[}0 - 3{]}\end{tabular}  & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}   & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary, continuous, \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}5 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
-\midrule
-Body Form & - & - & -                                                             & \begin{tabular}[c]{@{}l@{}}4 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
-\bottomrule
-\end{longtable}
-\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-      $\dagger$ Some of the feeding mode traits used in the Australian database were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
-      \newline
-      $\ddagger$ Not all traits were considered because trait information was partly presented as comments to describe other traits or due to incomplete information.
-      }
-  \end{minipage}
-\end{landscape}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Maximum differences of 1 (i.e., the maximum possible difference) occurred for all investigated grouping features in both datasets (Figure \ref{fig:diff_aggr_traits_combined}).
-
-\begin{landscape}
-\begin{table}[H]
-  \centering
-  \caption{Percentage of differing cases, minimum, maximum, mean, and standard deviation of absolute differences between trait affinities assigned at family level by experts and aggregated trait affinities from five different aggregation methods.}
-  \label{tab:summary_stat_aggr_vs_fam_assigned}
-  \begin{tabular}{ll|ccccc}
-  \toprule[.1em]
-  \specialcell{Data \\ origin} & \specialcell{Comparison to\\ traits at family level} & \specialcell{Differing \\ cases [\%]} & \specialcell{Min.
-\\ differences} & \specialcell{Max.
-\\ differences} & \specialcell{Mean abs.
-\\ differences} & \specialcell{SD abs.
-\\ differences} \\
-  \toprule[.1em]
-  \multirow{4}{*}{\specialcell{AUS}} & \specialcell{\textit{direct\_agg (median)}} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
-  & \specialcell{\textit{direct\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
-  & \specialcell{\textit{stepwise\_agg (median)}} & 17.90 & 0.01 & 1.00 & 0.42 & 0.26 \\ 
-  & \specialcell{\textit{stepwise\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
-  & \specialcell{\textit{weighted\_agg}} & 23.24 & $< 0.01$ & 1.00 & 0.34 & 0.24 \\ 
-  \midrule
-  \multirow{4}{*}{\specialcell{NA}} & \specialcell{\textit{direct\_agg (median)}} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
-  & \specialcell{\textit{direct\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
-  & \specialcell{\textit{stepwise\_agg (median)}} & 18.00 & 0.08 & 1.00 & 0.63 & 0.28 \\ 
-  & \specialcell{\textit{stepwise\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.27 \\ 
-  & \specialcell{\textit{weighted\_agg}} & 47.00 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
-  \bottomrule
-  \end{tabular}
-\end{table}
-\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-  \centering
-  Abbreviations: Min., Minimum; Max., Maximum; abs., absolute; SD, Standard deviation; AUS, Australia; NA, North America.
-  }
- \end{minipage}
-\end{landscape}
-
-\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \printbibliography
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supporting information %%%%%%%%%%%%%%%%%%%%%%%%
-\setcounter{table}{0}
-\setcounter{figure}{0}
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\thefigure}{S\arabic{figure}}
+%%%%%%%%%%%%%%%%%%%% Tables %%%%%%%%%%%%%%%%%%%%%%%
 
-\subfile{SI}
+\section*{Tables}
+
+% Table 1
+\begin{longtable}{m{2.5cm}|m{4cm}|m{7.5cm}}
+\caption{Traits of harmonised grouping features from six invertebrate trait databases and four geographic regions.
+The last column indicates traits that were combined for harmonisation (no combining needed if empty).}
+\endfirsthead
+\toprule[.1em]
+\label{tab:traits_harmonisation}
+%\begin{tabular}
+\specialcell{Grouping \\ feature} & Trait & Combined traits\\
+\toprule[.1em]
+Voltinism    & \begin{tabular}[c]{@{}l@{}}Semivoltine\\ Univoltine\\ Bi/multivoltine\end{tabular}                                & \begin{tabular}[c]{@{}l@{}}\textless 1 generation per year\\ 1 generation per year\\ \textgreater 1 generation per year\end{tabular}                                                                                                                                            \\
+\midrule
+Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattenend, dorsoventrally flattened$^{\dagger}$ \\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
+\midrule
+Size         & \begin{tabular}[c]{@{}l@{}}Small \\ Medium \\ Large\end{tabular}                                                  & \begin{tabular}[c]{@{}l@{}}\textless 9 mm, \textless 10 mm$^{\ddagger}$ \\ 9 - 16 mm, 10 - 20 mm\\ \textgreater 16 mm, \textgreater 20 mm\end{tabular}                                                                                                                \\
+\midrule
+Respiration  & \begin{tabular}[c]{@{}l@{}}Gills\\ Plastron/Spiracle\\ \\ \\ \\ Tegument\end{tabular}                             & \begin{tabular}[c]{@{}l@{}} Tracheal gills, gills\\ Temporary air store, spiracular gills, \\ atmospheric breathers, plant breathers, \\ functional spiracles, air (plants), aerial, \\ plastron/spiracle\\ Cutaneous, tegument \end{tabular}                                                                         \\
+\midrule
+Locomotion   & \begin{tabular}[c]{@{}l@{}}Burrower\\ Crawler\\ Sessile\\ Swimmer \end{tabular}                                     & \begin{tabular}[c]{@{}l@{}}Interstitial, boring, burrowing\\ Sprawler, walking, climber, clinger, crawler\\ Attached, sessile\\ Skating, diving, planctonic, swimming\end{tabular}                                                                                                                 \\
+\midrule
+Feeding mode & \begin{tabular}[c]{@{}l@{}}Filterer\\ \\ Gatherer\\ \\ Herbivore\\ \\ Parasite\\ Predator\\ Shredder \\ \\ \end{tabular} & \begin{tabular}[c]{@{}l@{}}Active/passive filterer, absorber, \\ filter-feeder, collector-filterer, filterer\\ Deposit-feeder, collector-gatherer, \\ detrivore, gatherer\\ Grazer, scraper, piercer herbivore, \\ herbivore, algal piercer, piercer (plants)$^{\mathsection}$\\ \\ Piercer (animals)$^{\mathsection}$, predator \\ Miner, xylophagus, shredder, \\ shredder detrivore\end{tabular} \\
+\hline
+Oviposition  & \begin{tabular}[c]{@{}l@{}}Aquatic eggs\\ \\ Ovoviviparity\\ Terrestrial eggs\end{tabular}                            & \begin{tabular}[c]{@{}l@{}}Eggs attached to substrate/plants/stones,\\ free/fixed eggs/clutches\\ \\ Terrestrial clutches, terrestrial \end{tabular}     \\
+\bottomrule[.1em]
+%\end{tabular}
+\end{longtable}
+\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
+    $\dagger$ The trait "bluff (blocky)" occurred in the Vieira database and was newly classified by expert knowledge into cylindrical and flattened (\cite{polatera_personal_information_2020}). \\  
+    $\ddagger$ Reflects the different size classifications by the Vieira and CONUS databases from the other trait databases. \\
+    $\mathsection$ The trait piercer was defined in the Tachet database for piercing plants and animals, in contrast to the other databases (\cite{usseglio-polatera_biomonitoring_2000}).
+Taxa exhibiting this trait have been assigned to predators or herbivores based on expert knowledge (\cite{polatera_personal_information_piercer_2020}).
+}
+\end{minipage}
+
+\newpage
+% Table 2 (Start Results)
+\begin{table}[ht]
+    \centering
+    \caption{Number (Nr.) of taxa per harmonised dataset and per taxonomic level. Numbers in parenthesis show rounded relative frequencies in percent.} 
+    \label{tab:tax_coverage}
+    \begin{tabular}{l|c|c|c|c|c}
+    \toprule[.1em]
+    Dataset & Taxa (Nr.) & Aquatic insects (Nr.) & Species & Genus & Family \\ 
+    \toprule[.1em]
+    EUR & 4601 & 3942 (86) & 3739 (81) & 704 (15) & 158 (3) \\ 
+    NA & 3753 & 3305 (88) & 2414 (64) & 1163 (31) & 176 (5)  \\ 
+    AUS & 1402 & 1016 (72) & 564 (40) & 578 (41) & 260 (19) \\ 
+    NZ & 478 & 443 (93) & 404 (85) & 47 (10) & 27 (6) \\ 
+    \bottomrule
+    \end{tabular}
+\end{table}
+\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
+\centering
+Abbreviations: EUR, Europe; NOA, North America; AUS, Australia; NZ, New Zealand.
+}
+\end{minipage}
+
+% Table 3
+\begin{table}[H]
+    \centering
+    \caption{Rounded percentage of entries that include 
+    information for the individual grouping features
+    shown per trait dataset.} 
+    \label{tab:trait_coverage}
+    \begin{tabular}{l|c|c|c|c|c|c|c}
+    \toprule[.1em]
+    Dataset & \specialcell{Body \\ form} & Oviposition & Voltinism & Locomotion & Size & Respiration & \specialcell{Feeding \\ mode} \\ 
+    \toprule[.1em]
+    EUR & 8 & 15 & 23 & 36 & 11 & 57 & 76 \\ 
+    NA & 28 & 13 & 47 & 52 & 73 & 44 & 63 \\ 
+    AUS & 4 & 46 & 49 & 39 & 75 & 68 & 99 \\ 
+    NZ & 100 & 94 & 100 & 99 & 100 & 100 & 99 \\ 
+    \bottomrule
+    \end{tabular}
+\end{table}
+\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
+\centering
+Abbreviations: EUR, Europe; NA, North America; AUS, Australia; NZ, New Zealand.
+}
+\end{minipage}
+
+% Table 4
+\begin{landscape}
+\begin{longtable}{m{2.5cm}|m{3.5cm}|m{2cm}|m{1.5cm}|m{1.5cm}|m{4.8cm}|m{2cm}}
+\caption{Number of traits per grouping feature and type of coding of the traits for the grouping features used in this study per database. Oviposition location was used for the New Zealand database.}
+\endfirsthead
+\toprule[.1em]
+\label{tab:trait_databases_coding_differentiation}
+\specialcell{Grouping \\ feature} & \specialcell{freshwater- \\ ecology.info} & Tachet & CONUS & Vieira & Australia & New Zealand \\
+\toprule[.1em]
+Feeding Mode & \begin{tabular}[c]{@{}l@{}}10 traits; \\ 10 point assginment \\ system\end{tabular}       & \begin{tabular}[c]{@{}l@{}}7 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}6 traits; \\ binary\end{tabular}   & \begin{tabular}[c]{@{}l@{}}8 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}16 traits$^{\dagger}$; \\ binary, proportional {[}0 - 1{]}, \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}6 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+Voltinism                                                           & \begin{tabular}[c]{@{}l@{}}6 traits; \\ single category \\ assignment system\end{tabular} & \begin{tabular}[c]{@{}l@{}}3 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}3 traits;\\ binary\end{tabular}    & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}7 traits; \\ binary, proportional {[}0 - 1{]}, \\ fuzzy {[}0 - 3{]}\end{tabular}  & \begin{tabular}[c]{@{}l@{}}3 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+Locomotion                                                          & \begin{tabular}[c]{@{}l@{}}6 traits; \\ 10 point assignment \\ system\end{tabular}        & \begin{tabular}[c]{@{}l@{}}8 traits; \\ fuzzy {[}0 - 5{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}10 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary, fuzzy  {[}0 - 3{]}\end{tabular}                              & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+Respiration                                                         & \begin{tabular}[c]{@{}l@{}}7 traits; \\ binary\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}5 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}3 traits;  \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}8 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}10 traits; \\ binary, proportional {[}0 - 1{]}, \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+\begin{tabular}[c]{@{}l@{}}Reproduction/\\ Oviposition\end{tabular} & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}8 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}10 traits;  \\ binary\end{tabular} & \begin{tabular}[c]{@{}l@{}}10 traits; \\ binary\end{tabular} & \begin{tabular}[c]{@{}l@{}}13 traits$^{\ddagger}$; \\ binary\end{tabular}                                                 & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+Size                                                                & -                                                                                         & \begin{tabular}[c]{@{}l@{}}7 traits;\\ fuzzy {[}0 - 3{]}\end{tabular}  & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}   & \begin{tabular}[c]{@{}l@{}}3 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}9 traits; \\ binary, continuous, \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}5 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\midrule
+Body Form & - & - & -                                                             & \begin{tabular}[c]{@{}l@{}}4 traits; \\ binary\end{tabular}  & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}4 traits; \\ fuzzy {[}0 - 3{]}\end{tabular} \\
+\bottomrule
+\end{longtable}
+\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
+      $\dagger$ Some of the feeding mode traits used in the Australian database were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
+      \newline
+      $\ddagger$ Not all traits were considered because trait information was partly presented as comments to describe other traits or due to incomplete information.
+      }
+  \end{minipage}
+\end{landscape}
+
+% Table 5
+\begin{landscape}
+\begin{table}[H]
+  \centering
+  \caption{Percentage of differing cases, minimum, maximum, mean, and standard deviation of absolute differences between trait affinities assigned at family level by experts and aggregated trait affinities from five different aggregation methods.}
+  \label{tab:summary_stat_aggr_vs_fam_assigned}
+  \begin{tabular}{ll|ccccc}
+  \toprule[.1em]
+  \specialcell{Data \\ origin} & \specialcell{Comparison to\\ traits at family level} & \specialcell{Differing \\ cases [\%]} & \specialcell{Min.
+\\ differences} & \specialcell{Max.
+\\ differences} & \specialcell{Mean abs.
+\\ differences} & \specialcell{SD abs.
+\\ differences} \\
+  \toprule[.1em]
+  \multirow{4}{*}{\specialcell{AUS}} & \specialcell{\textit{direct\_agg (median)}} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
+  & \specialcell{\textit{direct\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
+  & \specialcell{\textit{stepwise\_agg (median)}} & 17.90 & 0.01 & 1.00 & 0.42 & 0.26 \\ 
+  & \specialcell{\textit{stepwise\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
+  & \specialcell{\textit{weighted\_agg}} & 23.24 & $< 0.01$ & 1.00 & 0.34 & 0.24 \\ 
+  \midrule
+  \multirow{4}{*}{\specialcell{NA}} & \specialcell{\textit{direct\_agg (median)}} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
+  & \specialcell{\textit{direct\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
+  & \specialcell{\textit{stepwise\_agg (median)}} & 18.00 & 0.08 & 1.00 & 0.63 & 0.28 \\ 
+  & \specialcell{\textit{stepwise\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.27 \\ 
+  & \specialcell{\textit{weighted\_agg}} & 47.00 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
+  \bottomrule
+  \end{tabular}
+\end{table}
+\begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
+  \centering
+  Abbreviations: Min., Minimum; Max., Maximum; abs., absolute; SD, Standard deviation; AUS, Australia; NA, North America.
+  }
+ \end{minipage}
+\end{landscape}
+
+\section*{Figure captions}
+
+\textbf{Figure caption 1:}
+
+Data processing steps of the selected traits.
+Intermediate (grey) and main (orange) steps of data preparation are depicted.
+The dashed bottom box illustrates the different trait aggregation methods (hypothetical data in the upper left corner).
+The aggregation methods (purple) and intermediate steps of the aggregation methods (pink) are displayed.
+Abbreviations: EU, Europe; NOA, North America; AUS, Australia; NZ, New Zealand.
+\\
+
+\noindent{\textbf{Figure caption 2:}}
+
+Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the Australian and North American dataset.
+Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the grouping features feeding mode and body size.
+Results for the North American dataset for the grouping features locomotion, respiration, and voltinism are shown in the supporting information (Figure \ref{fig:diff_aggr_traits_pyne}).
+Absolute differences in trait affinities are depicted as grey dots.
+\textit{n} denotes the number of cases per comparison where differences occurred.
+The blue dot indicates the mean of absolute differences, and the error bars show the standard deviation.
+The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.
+Abbreviations: AUS, Australia; NA, North America.
+\\
+
+\noindent{\textbf{Figure caption 3:}}
+
+Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
+Shown are the results only for one simulated trait (T1).
+Similar results were obtained for the other simulated traits (Figure \ref{fig:overview_sim_results_T2_T3}).
+Boxplots depict results for 100 replicated simulations of each trait aggregation method.
+The boxplot depicts the median and encompasses the 25\textsuperscript{th} and 75\textsuperscript{th} percentile.
+Horizontal black lines depict the median.
+Whiskers extend to the largest and smallest value respectively no further than 1.5 $\times$ the inter-quartile range.
+Outliers beyond the end of the whiskers are plotted as grey dots.
+Trait aggregation methods are in order of least to greatest produced ranges to improve visual inspection.
+
+\noindent{\textbf{Figure caption 4:}}
+
+Comparison between the aggregated trait affinities produced by the different trait aggregation methods for every simulated dataset across all 3 simulated traits (5,000 comparisons per scenario).
+Results are shown for different levels of trait variability which is represented by the standard deviation (SD) of the simulated traits.
+Dots depict comparisons where absolute differences between aggregated trait affinities were greater than 0.1.
+Overall, there are 10 possible unique comparisons of which 7 produced absolute differences greater than 0.1.
+\newline
+  Comparisons: \newline
+  1) \textit{direct\_agg (median)} - \textit{stepwise\_agg (mean)} \newline
+  2) \textit{direct\_agg (median)} - \textit{weighted\_agg} \newline
+  3) \textit{stepwise\_agg (mean)} - \textit{stepwise\_agg (median)} \newline
+  4) \textit{stepwise\_agg (mean)} - \textit{weighted\_agg} \newline  
+  5) \textit{direct\_agg (mean)} - \textit{stepwise\_agg (median)} \newline
+  6) \textit{direct\_agg (median)} - \textit{stepwise\_agg (median)} \newline
+  7) \textit{stepwise\_agg (median)} - \textit{weighted\_agg} \newline
+
+\noindent{\textbf{Figure caption 5:}}
+
+Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonised grouping features, and using harmonised grouping features with traits aggregated to family level with five different aggregation methods.
+The dots represent the individual species scores for each analysed trait along the conductivity axis.
+The violin plot shows the density estimate of the species scores.
+Grey vertical lines indicate the median of the obtained species scores.
+\\
+
+\noindent{\textbf{Figure caption 6:}}
+
+RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{median}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
+Shown are boxplots of the site scores along the conductivity axis.
+The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
+Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
+For better comparability, species scores of the original analysis were multiplied by -1.
+Results for the other aggregated methods are shown in the supporting information (Figure \ref{fig:boxplots_scores_on_constrained_axis_REMAIN}).
+Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.
 

### 2021-02-21 Paper/Submission_new/Latex_Supplementary_File.tex
21.02: Finalised files for submission

--- 2021-02-19 Paper/Results/SI.tex
@@
-\documentclass[../Draft_harmonization_paper.tex]{subfiles}
+\documentclass[12pt]{article}
+\usepackage[utf8]{inputenc}
+\usepackage{hyperref}
+\usepackage{float}
+\usepackage[table,xcdraw]{xcolor}
+\usepackage{color, colortbl}
+\usepackage{longtable}
+\usepackage{booktabs}
+\usepackage{graphicx}
+\usepackage{multirow}
+\usepackage{tikz}
+\usepackage{rotating}
+\usepackage{caption}
+\usepackage{authblk}
+\usepackage{csquotes}
+\graphicspath{{Figures/}}
+\usepackage{setspace}
+\usepackage{rotating}
+\usepackage{geometry}
+\usepackage{array}
+\usepackage{lscape}
+\usepackage{longtable}
+\usepackage{etoolbox}
+\usepackage{hhline}
+\usepackage{lmodern}
+
+%%%% Functions and definitions %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\definecolor{Gray}{gray}{0.9}
+
+%% horizontal space between two columns
+\setlength{\tabcolsep}{2mm}
+
+%%%%%% New Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\specialcell}[2][c]{%
+  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
+
+% \renewcommand*{\thefootnote}{\alph{footnote}}
+
+%%%%% Formatting options %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\onehalfspacing
+
+%%%%%% Options for tables and figure counts %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+
+% \listfiles
+
+\title{Supporting Information - Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
+\author[1]{Stefan Kunz}
+\author[2]{Ben J. Kefford}
+\author[3]{Astrid Schmidt-Kloiber}
+\author[4]{Christoph D. Matthaei}
+\author[5]{Philippe Usseglio-Polatera}
+\author[3]{Wolfram Graf}
+\author[6]{N. LeRoy Poff}
+\author[7]{Leon Metzeling}
+\author[8]{Laura Twardochleb}
+\author[9]{Charles P. Hawkins}
+\author[1]{Ralf B. Schäfer}
+\affil[1]{Institute for Environmental Sciences, University of Koblenz-Landau, Landau, Germany}
+\affil[2]{Centre for Applied Water Science, Institute for Applied Ecology, University of Canberra, Canberra, Australia}
+\affil[3]{Institute of Hydrobiology and Aquatic Ecosystem Management, University of Natural Resources and Life Sciences Vienna (BOKU), Vienna, Austria}
+\affil[4]{Department of Zoology, University of Otago, Dunedin, New Zealand}
+\affil[5]{University of Lorraine, CNRS, LIEC, Metz, France}
+\affil[6]{Department of Biology, Colorado State University, Fort Collins, USA}
+\affil[7]{Environment Protection Authority Victoria, Applied Sciences Division, Macleod, Australia}
+\affil[8]{Department of Fisheries and Wildlife, Michigan State University, East Lansing, USA}
+\affil[9]{Department of Watershed Sciences, National Aquatic Monitoring Center, and the Ecology Center, Utah State University, Logan, USA}
+\date{}
 
 \begin{document}
-
-\section*{Supporting Information}
-\label{sec:SI}
-
-\subsection*{Harmonised trait datasets}
-
-\subsubsection*{Discrepancies in trait definitions}
+\maketitle
 
@@
 Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the grouping features locomotion, respiration, and body size.
-For more details see Figure \ref{fig:diff_aggr_traits_combined}.}
+For more details see Figure 2.}%\ref{fig:diff_aggr_traits_combined}
     \label{fig:diff_aggr_traits_pyne}
@@
 Trait aggregation methods are in order of least to greatest produced ranges to improve visual inspection.
-For more details see Figure \ref{fig:overview_sim_results}.}
+For more details see Figure 3.}%\ref{fig:overview_sim_results}
     \label{fig:overview_sim_results_T2_T3}
@@
 The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
-For more details see Figure \ref{fig:boxplot_scores_on_constrained_axis}.
+For more details see Figure 6.
+%\ref{fig:boxplot_scores_on_constrained_axis}.
     Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.}

### 2021-06-28 Paper/Submission_new/Flowchart/Flowchart_methods.tex
21.02: Submission files try again
28.06.2021: Update paper revisions

--- 2021-02-18 Paper/Flowchart/Flowchart_methods.tex
@@
-\documentclass[../Draft_harmonization_paper.tex]{subfiles}
+\documentclass[../Main_Document-Latex.tex]{subfiles}
 \usetikzlibrary{trees,
@@
       %% Nodes
-      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Consolidating duplicate \\ taxa in  EU, NOA, AUS \& \\ NZ databases};
-      \node(normalAUS)[intstepsnode, align = center, xshift = 0cm, yshift = 0cm]{ Normalised AUS \\ traits ([0 - 1]) to work \\ with multiple codings};
+      \node(duplTaxa)[intstepsnode, align = center] at (-5cm,0cm){Consolidating duplicate \\ taxa in  EU, NA, AUS \& \\ NZ databases};
+      \node(normalAUS)[intstepsnode, align = center, xshift = 0.1cm, yshift = 0cm]{ Normalised AUS \\ traits ([0 - 1]) to work \\ with multiple codings};
       \node(omission)[intstepsnode, align = center, xshift = 5cm, yshift = 0cm]{Omitted taxa less \\ precise than family-level};

### 2021-06-28 Paper/Submission_new/Latex_Supplementary_File.tex
28.06.2021: Update paper revisions

@@
 \usepackage{lmodern}
+
+\usepackage{subfiles} % Best loaded last in the preamble
 
@@
 \begin{landscape}
-    \begin{longtable}{m{1.9cm}|m{3.3cm}|m{3.3cm}|m{2.7cm}|m{3cm}|m{3.2cm}|m{2.5cm}}
+    \begin{longtable}{m{1.9cm}|m{3.4cm}|m{3.3cm}|m{2.7cm}|m{3cm}|m{3.6cm}|m{2.5cm}}
         \caption{Comparison of trait definitions between invertebrate trait databases.
@@
         \toprule[.1em]
-        Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & CONUS & Vieira & Australia & New Zealand \\
+        Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & CONUS & Vieira & Australia & \specialcell{New \\ Zealand} \\
         \toprule[.1em]
@@
 
-\subsubsection*{Comparison of aggregation methods with varying taxonomic hierarchies and trait variability}
+\subsubsection*{Effect of phylogeny and trait variability on aggregation outcomes}
+
+To examine the influence of phylogeny and trait variability on the outcomes of the different trait aggregation methods, we created three hypothetical scenarios.
+We simulated three different families, each containing 25 total species but with different phylogenetic structures.
+The three families consisted of (1) a family with an equal number of genera and species (five genera each with five species each), denoted as \textit{sim\_base}; (2) a family in which one genus had a much larger number of species than the other four genera (1 genus with 13 species, 4 genera with 3 species each), denoted as \textit{sim\_extreme}; (3) a family in which all genera had a different number of species (8, 2, 7, 3, 5), denoted as \textit{sim\_variation}.
+We assigned a hypothetical grouping feature with three traits (T1, T2, and T3) to each scenario.
+We then simulated the 25 affinities, one per species, for each trait, by sampling from a truncated normal distribution bound by 0 and 1 and with a mean value of 0.5.
+To simulate different levels of trait variability, we repeated the sampling 100 times for each of the 5 standard deviations (0.2, 0.4, 0.6, 0.8, and 1), resulting in 12,500 simulated trait affinities for each simulated trait ($25$ species per family $\times$ 5 levels of trait variability $\times$ 100 replicates).
+We converted simulated trait affinities to proportions, as was done during trait database processing, and assigned the 12,500 simulated affinities per trait to each of the three family scenarios.
+We then applied the five trait aggregation methods described above to each simulated dataset.
+We compared the resulting ranges of aggregated trait affinities between levels of trait variability and phylogenetic scenario as well as the differences in trait affinities obtained by each aggregation method.
+
+\paragraph*{Results: Comparison of aggregation methods with varying phylogenies and trait variability}
+\hfill
+\\
+
+The simulations showed that both phylogenetic structure and trait variability affected aggregated trait affinities, although only to a small degree, and that aggregation method mattered in terms of the ranges of trait affinities produced over simulation replicates.
+The effect of phylogenetic structure differed across aggregation methods, but, as we expected, the range of trait affinities increased with increasing trait variability for all aggregation methods (Figure \ref{fig:overview_sim_results}).
+
+Phylogenetic structure appeared to influence the outcomes of the different aggregation methods.
+For the \textit{sim\_base} scenario (equal numbers of genera and species), the mean aggregation methods yielded similar ranges of aggregated trait affinities within each level of trait variability, and the median aggregation methods consistently produced greater ranges of aggregated trait affinities than the other methods.
+The largest ranges were produced by the \textit{stepwise\_agg \textsubscript{median}} method.
+For the more complex phylogenetic structures, \textit{sim\_extreme} (one genus with a much larger number of species than the other four) and \textit{sim\_variation} (all genera with a different number of species), the \textit{stepwise\_agg \textsubscript{median}} method still produced the largest ranges of trait affinities for most levels of trait variability (and \textit{direct\_agg\textsubscript{mean}} produced the narrowest ranges for most levels of trait variability), but there was much less consistency in the ranges of trait affinities for all aggregation methods (i.e., the ranges were different among all aggregation methods).
+
+Although trait aggregation methods were affected by phylogenetic structure and trait variability to some degree, in most simulated datasets, the different aggregation methods resulted in similar trait affinities.
+Only 1.4 \%, or 213 out of 15.000 total comparisons (3 scenarios $\times$ 5 levels of trait variability $\times$ 10 unique comparisons of trait aggregation methods $\times$ 100 replicates) showed a difference equal or greater than an absolute trait affinity of 0.1.
+Most  (83.5 \%) of these differences occurred in the \textit{sim\_extreme} scenario and were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure \ref{fig:sim_indv_runs}).
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
+    \caption{Ranges of aggregated trait affinities for the three examples of phylogenetic structures and simulated levels of trait variability.
+Shown are the results only for one simulated trait (T1).
+Similar results were obtained for the other simulated traits (Figure \ref{fig:overview_sim_results_T2_T3}).
+Boxplots depict results for 100 replicated simulations of each trait aggregation method.
+The boxplot depicts the median and encompasses the 25\textsuperscript{th} and 75\textsuperscript{th} percentile.
+Horizontal black lines depict the median.
+Whiskers extend to the largest and smallest value respectively no further than 1.5 $\times$ the inter-quartile range.
+Outliers beyond the end of the whiskers are plotted as grey dots.
+Trait aggregation methods are in order of least to greatest produced ranges to improve visual inspection.}
+    \label{fig:overview_sim_results}
+  \end{figure}
 
@@
     \label{fig:overview_sim_results_T2_T3}
+  \end{figure}
+
+  \begin{figure}[H]
+    \centering
+    \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
+    \caption{Comparison between the aggregated trait affinities produced by the different trait aggregation methods for every simulated dataset across all 3 simulated traits (5,000 comparisons per scenario).
+Results are shown for different levels of trait variability which is represented by the standard deviation (SD) of the simulated traits.
+Dots depict comparisons where absolute differences between aggregated trait affinities were greater than 0.1.
+Overall, there are 10 possible unique comparisons of which 7 produced absolute differences greater than 0.1.
+\newline
+    Comparisons: \newline
+    1) \textit{direct\_agg\textsubscript{median}} - \textit{stepwise\_agg\textsubscript{mean}} \newline
+    2) \textit{direct\_agg\textsubscript{median}} - \textit{weighted\_agg} \newline
+    3) \textit{stepwise\_agg\textsubscript{mean}} - \textit{stepwise\_agg\textsubscript{median}} \newline
+    4) \textit{stepwise\_agg\textsubscript{mean}} - \textit{weighted\_agg} \newline  
+    5) \textit{direct\_agg\textsubscript{mean}} - \textit{stepwise\_agg\textsubscript{median}} \newline
+    6) \textit{direct\_agg\textsubscript{median}} - \textit{stepwise\_agg\textsubscript{median}} \newline
+    7) \textit{stepwise\_agg\textsubscript{median}} - \textit{weighted\_agg} \newline
+    }
+    \label{fig:sim_indv_runs}
   \end{figure}

### 2021-06-28 Paper/Submission_new/Main_Document-Latex.tex
21.02: Finalised files for submission
28.06.2021: Update paper revisions

--- 2021-02-21 Paper/Submission_new/Main_doc.tex
@@
 citestyle = authoryear,
-bibstyle = apa6,
+bibstyle = apa,
 maxcitenames = 2, 
@@
 
-\myexternaldocument{SI_test}
+\myexternaldocument{Latex_Supplementary_File}
 
@@
 \\
-\keywords{trait definitions, trait aggregation, data synthesis}
+\keywords{trait definitions, trait aggregation, data synthesis, trait-environment relationships, large-scale comparisons}
 
@@
 Invertebrate traits have been increasingly used in freshwater ecology, e.g.
-by relating macroinvertebrate trait composition to environmental factors such as climate change or salinisation (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}).
-In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases, which typically include data for a single region or continent (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate}).
+by relating macroinvertebrate trait composition to environmental factors such as climate change or salinisation (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}), for predicting changes in ecosystem functioning and trophic dynamics (\cite{vos_taxonomic_2017, gutierrez-canovasPopulationsHighvaluePredators2021}), or for developing indices for biomonitoring (\cite{beketov_spear_2009}).
+In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases, which typically include data for a single region or continent (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate, gayraudInvertebrateTraitsBiomonitoring2003, statznerConservationTaxonomicBiological2007}).
 The availability of invertebrate trait data from different continents enables comparisons of regional trait variation and allows for testing the consistency of trait structure–environmental factor relationships across both small and large spatial extents.
@@
 Other traits are better suited to being described as continuous (e.g., tolerance of pollution, body size).
-One approach for dealing with uncertainty is the use of fuzzy coding, where traits are assigned probabilistic values.
+One approach for dealing with uncertainty is the use of fuzzy coding, where traits are assigned probabilistic values (\cite{chevenet_francois_fuzzy_1994}).
 Fuzzy codes, which are usually converted to proportions, are used to account for plasticity in traits, variability in traits within taxonomic groups above the species level, and incomplete knowledge.
@@
 We established four datasets, one for each of the four geographic regions, by harmonising the traits of seven grouping features from the trait databases.
-We selected traits that were available in all databases, are commonly applied in trait-based ecological studies, and describe different aspects of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
-We omitted ecological traits that describe habitat preferences (e.g.
+We selected traits that are commonly applied in trait-based ecological studies and describe different aspects of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
+The selected traits also relate to how taxa cope with disturbances (e.g.
+reproduction traits like ovoviviparity or number of life cycles) and to ecosystem functions such as organic matter breakdown and nutrient cycling (e.g.
+trait shredder).
+A criterion for trait selection was that the traits occurred in all databases, to enable us to show trait definitions differences and the influence of grouping-feature harmonisation on trait-environment relationships.
+Thus, we omitted ecological traits that describe habitat preferences (e.g.
 temperature preference) because these traits are missing in the New Zealand trait database.
+% OLD:
+% We selected traits that were available in all databases, are commonly applied in trait-based ecological studies, and describe different aspects of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
+
 Grouping features were classified differently across the databases, so we harmonised 7 grouping features that collectively included 26 traits (Table \ref{tab:traits_harmonisation}).
@@
 
-To compare the effects of different aggregation methods on trait\-environment relationship inferences, we aggregated the traits of two of the harmonised datasets to the family level.
+To compare the effects of different aggregation methods on trait-environment relationship inferences, we aggregated the traits of two of the harmonised datasets to the family level.
 We used three different aggregation approaches: (1) direct aggregation of taxa to family level, in which we aggregated either trait affinities by the median or mean for species and genera within a family, giving equal weight to every taxon.
@@
 
-\subsubsection*{Effect of phylogeny and trait variability on aggregation outcomes}
-
-To examine the influence of phylogeny and trait variability on the outcomes of the different trait aggregation methods, we created three hypothetical scenarios.
-We simulated three different families, each containing 25 total species but with different phylogenetic structures.
-The three families consisted of (1) a family with an equal number of genera and species (five genera each with five species each), denoted as \textit{sim\_base}; (2) a family in which one genus had a much larger number of species than the other four genera (1 genus with 13 species, 4 genera with 3 species each), denoted as \textit{sim\_extreme}; (3) a family in which all genera had a different number of species (8, 2, 7, 3, 5), denoted as \textit{sim\_variation}.
-We assigned a hypothetical grouping feature with three traits (T1, T2, and T3) to each scenario.
-We then simulated the 25 affinities, one per species, for each trait, by sampling from a truncated normal distribution bound by 0 and 1 and with a mean value of 0.5.
-To simulate different levels of trait variability, we repeated the sampling 100 times for each of the 5 standard deviations (0.2, 0.4, 0.6, 0.8, and 1), resulting in 12,500 simulated trait affinities for each simulated trait ($25$ species per family $\times$ 5 levels of trait variability $\times$ 100 replicates).
-We converted simulated trait affinities to proportions, as was done during trait database processing, and assigned the 12,500 simulated affinities per trait to each of the three family scenarios.
-We then applied the five trait aggregation methods described above to each simulated dataset.
-We compared the resulting ranges of aggregated trait affinities between levels of trait variability and phylogenetic scenario as well as the differences in trait affinities obtained by each aggregation method.
+Further, we examined the influence of phylogeny and trait variability on the outcomes of the different trait aggregation methods by simulating families with different phylogenetic structures and different levels of trait variability.
+The simulation showed that both phylogenetic structure and trait variability can affect aggregated trait affinities, but mostly only to a small degree.
+As expected, the range of trait affinities increasing trait variability for all trait aggregation methods.
+Therefore, we provide details of the simulation and the results in the supplementary materials.
 
@@
 Additionally, to test for the effect of different aggregation methods on inferences about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
+% Add change in functional diversity
 
@@
 
-The definitions of grouping features also varied across databases in their differentiation into traits and in their focus, both which can lead to discrepancies in trait definitions (see Table \ref{stab:trait_definitions} for a summary of discrepancies in trait definitions).
-Varying levels of differentiation among the trait databases were present in all investigated grouping features (Table \ref{tab:trait_databases_coding_differentiation} and Table \ref{stab:trait_definitions}).
+The definitions of grouping features also varied across databases in their differentiation into traits and in their focus, both which can lead to discrepancies in trait definitions (see Table \ref{tab:trait_definitions} and Table \ref{stab:trait_definitions} for a summary of discrepancies in trait definitions).
+Varying levels of differentiation among the trait databases were present in all investigated grouping features (Table \ref{tab:trait_databases_coding_differentiation}, Table \ref{tab:trait_definitions}, and Table \ref{stab:trait_definitions}).
 
@@
   \label{fig:diff_aggr_traits_combined}
-\end{figure}
-
-\newpage
-
-\subsubsection*{Comparison of aggregation methods with varying phylogenies and trait variability}
-
-The simulations showed that both phylogenetic structure and trait variability affected aggregated trait affinities, although only to a small degree, and that aggregation method mattered in terms of the ranges of trait affinities produced over simulation replicates.
-The effect of phylogenetic structure differed across aggregation methods, but, as we expected, the range of trait affinities increased with increasing trait variability for all aggregation methods (Figure \ref{fig:overview_sim_results}).
-
-Phylogenetic structure appeared to influence the outcomes of the different aggregation methods.
-For the \textit{sim\_base} scenario (equal numbers of genera and species), the mean and weighted aggregation methods yielded similar ranges of aggregated trait affinities within each level of trait variability, and the median aggregation methods consistently produced greater ranges of aggregated trait affinities than the other methods.
-The largest ranges were produced by the \textit{stepwise\_agg \textsubscript{median}} method.
-For the more complex phylogenetic structures, \textit{sim\_extreme} (one genus with a much larger number of species than the other four) and \textit{sim\_variation} (all genera with a different number of species), the \textit{stepwise\_agg \textsubscript{median}} method still produced the largest ranges of trait affinities for most levels of trait variability (and \textit{direct\_agg\textsubscript{mean}} produced the narrowest ranges for most levels of trait variability), but there was much less consistency in the ranges of trait affinities for all aggregation methods (i.e., the ranges were different among all aggregation methods).
-
-Although trait aggregation methods were affected by phylogenetic structure and trait variability to some degree, in most simulated datasets, the different aggregation methods resulted in similar trait affinities.
-Only 1.4 \%, or 213 out of 15.000 total comparisons (3 scenarios $\times$ 5 levels of trait variability $\times$ 10 unique comparisons of trait aggregation methods $\times$ 100 replicates) showed a difference equal or greater than an absolute trait affinity of 0.1.
-Most  (83.5 \%) of these differences occurred in the \textit{sim\_extreme} scenario and were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure \ref{fig:sim_indv_runs}).
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
-  \caption{Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
-Shown are the results only for one simulated trait (T1).
-Similar results were obtained for the other simulated traits (Figure \ref{fig:overview_sim_results_T2_T3}).
-Boxplots depict results for 100 replicated simulations of each trait aggregation method.
-The boxplot depicts the median and encompasses the 25\textsuperscript{th} and 75\textsuperscript{th} percentile.
-Horizontal black lines depict the median.
-Whiskers extend to the largest and smallest value respectively no further than 1.5 $\times$ the inter-quartile range.
-Outliers beyond the end of the whiskers are plotted as grey dots.
-Trait aggregation methods are in order of least to greatest produced ranges to improve visual inspection.}
-  \label{fig:overview_sim_results}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=16.5cm, height=10cm]{Diffs_indiv_runs_sim.png}
-  \caption{Comparison between the aggregated trait affinities produced by the different trait aggregation methods for every simulated dataset across all 3 simulated traits (5,000 comparisons per scenario).
-Results are shown for different levels of trait variability which is represented by the standard deviation (SD) of the simulated traits.
-Dots depict comparisons where absolute differences between aggregated trait affinities were greater than 0.1.
-Overall, there are 10 possible unique comparisons of which 7 produced absolute differences greater than 0.1.
-\newline
-  Comparisons: \newline
-  1) \textit{direct\_agg (median)} - \textit{stepwise\_agg (mean)} \newline
-  2) \textit{direct\_agg (median)} - \textit{weighted\_agg} \newline
-  3) \textit{stepwise\_agg (mean)} - \textit{stepwise\_agg (median)} \newline
-  4) \textit{stepwise\_agg (mean)} - \textit{weighted\_agg} \newline  
-  5) \textit{direct\_agg (mean)} - \textit{stepwise\_agg (median)} \newline
-  6) \textit{direct\_agg (median)} - \textit{stepwise\_agg (median)} \newline
-  7) \textit{stepwise\_agg (median)} - \textit{weighted\_agg} \newline
-  }
-  \label{fig:sim_indv_runs}
 \end{figure}
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 
@@
 % Table 1
+\begin{landscape}
+  \begin{longtable}{m{2.0cm}|m{4.0cm}|m{4.2cm}|m{4.2cm}|m{1.7cm}|m{2cm}|m{2.2cm}}
+      \caption{Excerpt of the comparison of trait definitions between invertebrate trait databases for the traits predator and swimming.
+The definition is quoted if it enables differences to be identified, otherwise the differences are described.
+The full version and further information can be found in the supporting information Table \ref{stab:trait_definitions}.}
+      \label{tab:trait_definitions}
+      \endfirsthead
+      \toprule[.1em]
+      Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & CONUS & Vieira & Australia & \specialcell{New \\ Zealand} \\
+      \toprule[.1em]
+      Feeding predator & 
+        "Eating from prey" & 
+        \begin{itemize}
+            \item Carvers, engulfers \& swallowers
+            \item Piercers (plants \& animals) are an additional trait
+        \end{itemize} & % Notes: Tachet -> Piercer (plants & animals)
+        Engulfers ("ingest prey whole or in parts") \& 
+        piercers ("prey tissues and suck fluids") & 
+        Predator &
+        Piercer \& engulfer &
+        Predator
+        \\ 
+        \midrule
+        Locomotion swimming & 
+        \begin{itemize}
+            \item Passive movement like floating or drifting (trait swimming/scating)
+            \item Active movement (trait swimming/diving)
+        \end{itemize}. &
+        \begin{itemize}
+            \item Surface swimmers (over and under the water surface)
+            \item Full water swimmers (e.g. Baetidae).
+        \end{itemize} & 
+        "Adapted for "fishlike" swimming" & 
+        Swimmer & 
+        Traits swimmer and skater & 
+        Swimmers (water column)
+        \\
+      \bottomrule
+  \end{longtable}
+\end{landscape}
+
+% Table 2
 \begin{longtable}{m{2.5cm}|m{4cm}|m{7.5cm}}
@@
     \toprule[.1em]
-  \multirow{4}{*}{\specialcell{AUS}} & \specialcell{\textit{direct\_agg (median)}} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
-  & \specialcell{\textit{direct\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
-  & \specialcell{\textit{stepwise\_agg (median)}} & 17.90 & 0.01 & 1.00 & 0.42 & 0.26 \\ 
-  & \specialcell{\textit{stepwise\_agg (mean)}} & 23.24 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
+    \multirow{4}{*}{\specialcell{AUS}} & \specialcell{\textit{direct\_agg\textsubscript{median}}} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
+    & \specialcell{\textit{direct\_agg\textsubscript{mean}}} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{median}}} & 17.90 & 0.01 & 1.00 & 0.42 & 0.26 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{mean}}} & 23.24 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
     & \specialcell{\textit{weighted\_agg}} & 23.24 & $< 0.01$ & 1.00 & 0.34 & 0.24 \\ 
     \midrule
-  \multirow{4}{*}{\specialcell{NA}} & \specialcell{\textit{direct\_agg (median)}} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
-  & \specialcell{\textit{direct\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
-  & \specialcell{\textit{stepwise\_agg (median)}} & 18.00 & 0.08 & 1.00 & 0.63 & 0.28 \\ 
-  & \specialcell{\textit{stepwise\_agg (mean)}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.27 \\ 
+    \multirow{4}{*}{\specialcell{NA}} & \specialcell{\textit{direct\_agg\textsubscript{median}}} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
+    & \specialcell{\textit{direct\_agg\textsubscript{mean}}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{median}}} & 18.00 & 0.08 & 1.00 & 0.63 & 0.28 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{mean}}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.27 \\ 
     & \specialcell{\textit{weighted\_agg}} & 47.00 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
@@
 
-Ranges of aggregated trait affinities for the three examples of taxonomic hierarchies and simulated levels of trait variability.
+Ranges of aggregated trait affinities for the three examples of phylogenetic structures and simulated levels of trait variability.
 Shown are the results only for one simulated trait (T1).
@@
 Trait aggregation methods are in order of least to greatest produced ranges to improve visual inspection.
+\\
 
@@
   Comparisons: \newline
-  1) \textit{direct\_agg (median)} - \textit{stepwise\_agg (mean)} \newline
-  2) \textit{direct\_agg (median)} - \textit{weighted\_agg} \newline
-  3) \textit{stepwise\_agg (mean)} - \textit{stepwise\_agg (median)} \newline
-  4) \textit{stepwise\_agg (mean)} - \textit{weighted\_agg} \newline  
-  5) \textit{direct\_agg (mean)} - \textit{stepwise\_agg (median)} \newline
-  6) \textit{direct\_agg (median)} - \textit{stepwise\_agg (median)} \newline
-  7) \textit{stepwise\_agg (median)} - \textit{weighted\_agg} \newline
+  1) \textit{direct\_agg\textsubscript{median}} - \textit{stepwise\_agg\textsubscript{mean}} \newline
+  2) \textit{direct\_agg\textsubscript{median}} - \textit{weighted\_agg} \newline
+  3) \textit{stepwise\_agg\textsubscript{mean}} - \textit{stepwise\_agg\textsubscript{median}} \newline
+  4) \textit{stepwise\_agg\textsubscript{mean}} - \textit{weighted\_agg} \newline  
+  5) \textit{direct\_agg\textsubscript{mean}} - \textit{stepwise\_agg\textsubscript{median}} \newline
+  6) \textit{direct\_agg\textsubscript{median}} - \textit{stepwise\_agg\textsubscript{median}} \newline
+  7) \textit{stepwise\_agg\textsubscript{median}} - \textit{weighted\_agg}
+\\
 

### 2021-06-28 Paper/Submission_new/Tables.tex
28.06.2021: Update paper revisions

--- 2021-06-28 Paper/Submission_new/Main_Document-Latex.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
-\author[1]{Stefan Kunz}
-\author[2]{Ben J. Kefford}
-\author[3]{Astrid Schmidt-Kloiber}
-\author[4]{Christoph D. Matthaei}
-\author[5]{Philippe Usseglio-Polatera}
-\author[3]{Wolfram Graf}
-\author[6]{N. LeRoy Poff}
-\author[7]{Leon Metzeling}
-\author[8]{Laura Twardochleb}
-\author[9]{Charles P. Hawkins}
-\author[1]{Ralf B. Schäfer}
-\affil[1]{Institute for Environmental Sciences, University of Koblenz-Landau, Landau, Germany}
-\affil[2]{Centre for Applied Water Science, Institute for Applied Ecology, University of Canberra, Canberra, Australia}
-\affil[3]{Institute of Hydrobiology and Aquatic Ecosystem Management, University of Natural Resources and Life Sciences Vienna (BOKU), Vienna, Austria}
-\affil[4]{Department of Zoology, University of Otago, Dunedin, New Zealand}
-\affil[5]{University of Lorraine, CNRS, LIEC, Metz, France}
-\affil[6]{Department of Biology, Colorado State University, Fort Collins, USA}
-\affil[7]{Environment Protection Authority Victoria, Applied Sciences Division, Macleod, Australia}
-\affil[8]{Department of Fisheries and Wildlife, Michigan State University, East Lansing, USA}
-\affil[9]{Department of Watershed Sciences, National Aquatic Monitoring Center, and the Ecology Center, Utah State University, Logan, USA}
+\title{Tables - Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
+\author{}
 \date{}
@@
 
-\newpage
-
-\section*{Abstract}
-
-1.
-Use of invertebrate traits rather than species composition may facilitate large-scale comparisons of community structure and responses to disturbance in freshwater ecology because the same traits can potentially occur everywhere.
-In recent years, comprehensive invertebrate trait databases have been established at different scales (e.g.
-regions, continents).
-The wide availability of invertebrate trait data supports trait-based studies, especially at large scales.
-However, a number of data-related issues complicate the use of invertebrate traits for ecological studies.
-For example, standardised definitions for freshwater invertebrate traits are lacking, which impedes comparisons across regions.
-Moreover, it is uncertain how harmonising varying trait definitions among databases might influence identification of trait-environment relationships.
-In addition, taxonomic resolution between taxonomic composition data and trait data can differ, making aggregation of traits necessary.
-At present, it is unknown how different trait aggregation approaches compare with expert-assigned trait affinities.
-In this study we aimed to identify discrepancies in trait definitions across freshwater invertebrate databases and to compare trait aggregation methods to identify how phylogenetic structure and trait variability influence results from different aggregation methods.
-
-2.
-We describe discrepancies in the definitions of traits used to create freshwater invertebrate trait databases in Europe, North America, New Zealand, and Australia.
-Based on our comparisons of these trait databases, we established four novel trait datasets by harmonising trait definitions of commonly used traits.
-Next, we used two of these datasets to compare aggregated traits obtained by different aggregation methods with traits assigned by experts, both at the family level.
-The trait aggregation methods we compared used either the mean or the median and different weightings.
-We further explored the effects of harmonisation and trait aggregation by re-analysing data from a case study.
-
-3.
-We found that among trait databases, trait definitions often differed because varying numbers of traits were used to describe groups of related traits (e.g., respiration traits) and the focus of descriptions for groups of related traits also varied (e.g., for feeding mode some databases focused on the food source, whereas others focused on mouthpart morphology).
-The coding to describe traits (binary, fuzzy) also varied among databases.
-Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially when aggregation was based on the median, and that trait coding method, uneven phylogenetic structure, and high trait variability can influence aggregated trait affinities.
-We further showed that harmonised and aggregated data performed similarly to not aggregated and harmonised data from the case study in identifying trait–environment relationships.
-
-4.
-By identifying discrepancies in trait definitions we hope to motivate the development of standardised terminology for invertebrate traits.
-Our results also illustrate the usefulness of harmonised datasets for ecological study and provide guidance for the circumstances under which the choice of trait aggregation method is important.
-\\
-\keywords{trait definitions, trait aggregation, data synthesis, trait-environment relationships, large-scale comparisons}
-
-\newpage
-
-\section*{Introduction}
-
-Explaining and predicting how communities are shaped by environmental factors is a primary goal of ecology.
-Species traits are measurable properties of an organism (\cite{mcgill_rebuilding_2006}), and comparing communities based on the traits possessed by species may facilitate testing of a range of ecological hypotheses (\cite{statzner_perspectives_2001}).
-Traits are assumed to be adaptations (e.g., physiological, behavioural) of organisms to their environment, which represent either direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
-In addition to providing local-scale mechanistic-based expressions of species-environment relationships, trait-based approaches might be suitable for large-scale analyses of environmental risks to communities because the occurrence and distribution of traits are less constrained by biogeographic boundaries than that of taxa (\cite{baird_toward_2011, bonada_taxonomic_2007}).
-
-Invertebrate traits have been increasingly used in freshwater ecology, e.g.
-by relating macroinvertebrate trait composition to environmental factors such as climate change or salinisation (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}), for predicting changes in ecosystem functioning and trophic dynamics (\cite{vos_taxonomic_2017, gutierrez-canovasPopulationsHighvaluePredators2021}), or for developing indices for biomonitoring (\cite{beketov_spear_2009}).
-In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases, which typically include data for a single region or continent (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate, gayraudInvertebrateTraitsBiomonitoring2003, statznerConservationTaxonomicBiological2007}).
-The availability of invertebrate trait data from different continents enables comparisons of regional trait variation and allows for testing the consistency of trait structure–environmental factor relationships across both small and large spatial extents.
-To date, such analyses have been carried out mostly within continents, using information from one or two trait databases.
-For example, \citet{bonada_taxonomic_2007} compared trait composition for Mediterranean and temperate regions in Europe based on traits from \citet{ussegliopolatera_biological_2000} (typically referred to as the Tachet database), \citet{poff_developing_2010} characterised trait composition across sites in the Western USA based on traits from \citet{poff_functional_2006}, and \citet{botwe_effects_2018} used trait definitions from \citet{poff_functional_2006} and \citet{schafer_trait_2011} to test for effects of salinity on invertebrate traits across different sites in South Australia.
-Analyses that synthesise invertebrate trait information from more than two different continents are rare, but see \citet{brown_functional_2018} and \citet{statzner_reproductive_1997}.
-
-The variability and inconsistencies of information in freshwater invertebrate trait databases, besides the diversity of taxa across regions, is likely a major reason for the lack of comparisons across continents.
-Several challenges currently prevent the use of invertebrate trait data from different established databases in ecological studies.
-One challenge is inconsistency in terminology.
-In this study, we follow the terminology proposed by \citet{schmera_proposed_2015}, in which a grouping feature (e.g.
-feeding mode) refers to a set of related traits (e.g.
-predator, shredder, etc.) that together define an ecological property that is shared among individuals or species.
-Thus, to use consistent terminology in this study, we use the term grouping feature in place of the term trait, and the term trait instead of trait state, modality or trait category.
-
-Another challenge to using data from multiple continents is that invertebrate trait databases include different grouping features and related traits.
-To harmonise grouping features from different regions, or to structure them in such a way as to facilitate cross-database comparison, commonly accepted and unambiguous trait definitions are required (\cite{schneider_towards_2019}).
-Ideally, the same traits and grouping features would be reported across databases or standardised terminology would exist to easily harmonise them; however, standardised terminology of trait definitions is lacking and poor metadata quality in many trait databases make harmonisation of grouping features difficult (\cite{baird_toward_2011, kissling_towards_2018}).
-To our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on the functional diversity of invertebrate assemblages.
-
-A third challenge to comparing across invertebrate trait databases is inconsistent coding of trait data (\cite{culp_incorporating_2011}).
-Traits of individual freshwater invertebrates can be difficult to quantify because, unlike plant traits, they are often difficult to measure directly.
-For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behaviour, and what is being eaten (\cite{moog_comprehensive_nodate}).
-Some traits can be described in categorical terms, which ignores uncertainty in how traits are expressed in any particular organism (e.g., adult terrestrial stage, presence of gills).
-Other traits are better suited to being described as continuous (e.g., tolerance of pollution, body size).
-One approach for dealing with uncertainty is the use of fuzzy coding, where traits are assigned probabilistic values (\cite{chevenet_francois_fuzzy_1994}).
-Fuzzy codes, which are usually converted to proportions, are used to account for plasticity in traits, variability in traits within taxonomic groups above the species level, and incomplete knowledge.
-The values derived from the different coding approaches represent affinities (aka affinity scores) that indicate how strongly a taxon expresses a particular trait.
-The use of different types of coding for trait affinities in different databases limits comparisons.
-For example, in the study from \citet{brown_functional_2018} the authors needed to reclassify trait affinities because the individual databases employed different coding approaches (i.e., European and New Zealand databases used fuzzy coding whereas the North American database used binary coding).
-
-Finally, discrepancies in the taxonomic resolutions (e.g., species, genus, or family) used when comparing among trait databases, or when linking observed taxonomic data to trait databases, presents another challenge.
-When taxonomic composition or data in on trait database are at a more precise taxonomic level than other trait data (e.g.
-observations at species-level and trait data at genus-level) trait information of the less precise taxonomic level is often assigned (e.g.
-\cite{szocs_effects_2014, vos_taxonomic_2017}).
-If trait information is only available at more precise taxonomic levels than for taxonomic composition, traits are aggregated to a less precise taxonomic level (e.g.
-\cite{aspin_extreme_2019, piliere_a._f._h._importance_2016, poff_functional_2006, szocs_effects_2014}).
-To date, studies have used different methods of trait aggregation, e.g.
-the mean (\cite{magliozzi_functional_2019}), median (\cite{szocs_effects_2014}) or mode (\cite{piliere_a._f._h._importance_2016}), but studies on how and to what extent different trait aggregation methods influence trait-based analyses are missing.
-
-These challenges motivated us to assess the characteristics and comparability of different freshwater invertebrate trait databases with the goal of facilitating future syntheses.
-We aimed to identify methods of improving the comparability of trait data across databases, despite differences in trait definitions and the taxonomic level of data in three ways: (1) by describing discrepancies in trait definitions between trait databases from Europe, North America, Australia, and New Zealand; (2) by harmonising trait definitions across databases to provide consistent grouping features for comparison across geographic locations; and (3) by comparing the influence of different trait aggregation methods and grouping-feature harmonisation on the detection of trait–environment relationships.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Methods}
-
-To address our study objectives, we took a multi-prong approach to describing, combining, and assessing multiple sources of freshwater invertebrate data that differed in grouping-feature definitions and taxonomic resolution.
-Discrepancies in trait definitions served as a starting point to develop four novel invertebrate trait datasets by harmonising seven grouping features present in the existing trait databases.
-The harmonised trait datasets were used to evaluate the influence of different trait aggregation methods on the identification of trait–environment relationships, our third study objective, in two ways by (1) comparing family-level aggregated trait affinities with family-level trait affinities assigned by experts for two of the established trait datasets where such data were available and (2) comparing the influence of phylogenetic structure and trait variability on the outcomes of the different trait aggregation approaches for simulated data.
-Finally, to further investigate how harmonising and aggregating trait data can modify the outcomes of trait–environment relationship characterisation, we used data from one of the newly established datasets with harmonised and aggregated traits to repeat an analysis of salinisation effects on biological traits (\cite{szocs_effects_2014}) and compared our results with those of the original study.
-
-\subsection*{Selection of traits and harmonisation of trait databases}
-
-We assessed how six databases differed in how they assigned and described traits of freshwater invertebrates.
-These databases (from Europe, North America, Australia, and New Zealand) differed in how grouping features were defined and the taxonomic resolution used to assign traits.
-For Europe we obtained trait information from the freshwaterecology.info database (\cite{schmidt-kloiber_www.freshwaterecology.info_2015}), which assigns traits at the species level, and the Tachet database (\cite{ussegliopolatera_biological_2000}), which assigns traits at species, genus, and family levels.
-For North America we primarily obtained trait information from \citet{twardochleb_freshwater_nodate} (hereafter referred to as the CONUS database) and where taxa were missing from that database, we obtained data from \citet{vieira_database_nodate} (hereafter referred to as the Vieira database).
-Both databases contain taxa at species, genus and family levels.
-Data on body form for European and North American taxa were based on expert knowledge (\cite{polatera_personal_information_2020}).
-For Australia and New Zealand, we used trait databases from \citet{kefford_integrated_2020} (hereafter referred to as the Australian database) and \citet{Philips_and_Smith_NZ_DB_2018} (hereafter referred to as the New Zealand database).
-These databases assigned traits at species, genus, family, and coarser taxonomic levels.
-
-We established four datasets, one for each of the four geographic regions, by harmonising the traits of seven grouping features from the trait databases.
-We selected traits that are commonly applied in trait-based ecological studies and describe different aspects of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
-The selected traits also relate to how taxa cope with disturbances (e.g.
-reproduction traits like ovoviviparity or number of life cycles) and to ecosystem functions such as organic matter breakdown and nutrient cycling (e.g.
-trait shredder).
-A criterion for trait selection was that the traits occurred in all databases, to enable us to show trait definitions differences and the influence of grouping-feature harmonisation on trait-environment relationships.
-Thus, we omitted ecological traits that describe habitat preferences (e.g.
-temperature preference) because these traits are missing in the New Zealand trait database.
-% OLD:
-% We selected traits that were available in all databases, are commonly applied in trait-based ecological studies, and describe different aspects of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
-
-Grouping features were classified differently across the databases, so we harmonised 7 grouping features that collectively included 26 traits (Table \ref{tab:traits_harmonisation}).
-To do so we combined similar traits into one trait (e.g.
-crawlers and sprawlers into crawlers) by assigning for each taxon for the new combined trait the highest affinity score of those originally assigned.
-Next, we selected taxa for inclusion in our datasets and normalised the trait affinity scores for each taxon.
-We first omitted all taxa with a lower taxonomic precision than family level and consolidated duplicate taxa that appeared within a database, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
-We then used either fuzzy coding or, when unavailable, binary coding to create the final harmonised datasets.
-Fuzzy codes are reported with different ranges in the trait databases (e.g., freshwaterecology.info: 0–10, Tachet database: 0–3 or 0–5).
-We normalised these to a range between 0 and 1 and converted trait affinities to proportions.
-In cases where binary coding was needed, we converted categorical and continuous traits into binary traits with values of 1 and 0, which, therefore, had the same range as fuzzy coded traits.
-For example, in the  freshwaterecology.info database, voltinism traits are associated with different faunistic regions, and we substituted a value of 1 for entries such as “arctic” or “boreal”.
-We assumed that values of 1 and 0 for binary traits corresponded to the highest and lowest affinity for a particular trait.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Comparing trait aggregation methods}
-
-To compare the effects of different aggregation methods on trait-environment relationship inferences, we aggregated the traits of two of the harmonised datasets to the family level.
-We used three different aggregation approaches: (1) direct aggregation of taxa to family level, in which we aggregated either trait affinities by the median or mean for species and genera within a family, giving equal weight to every taxon.
-We denote these aggregation methods as \textit{direct\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{mean}}, respectively; and (2) stepwise aggregation, first to the genus level and subsequently to the family level with either the median or mean.
-This approach gives equal weights to each genus.
-Hereafter, we denote this aggregation type as \textit{stepwise\_agg\textsubscript{median}} or \textit{stepwise\_agg\textsubscript{mean}}, respectively; and (3) aggregation using a weighted mean approach, denoted as \textit{weighted\_agg}.
-This method weights each genus according to its number of species in the trait datasets, regardless of whether information was available for every used grouping feature (Figure \ref{fig:data_proc_overview}).
-When we refer to \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg} together we denote these methods as mean aggregation methods and when we refer to \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}} together, we denote these methods as median aggregation methods.
-
-\subsubsection*{Comparison of family-level aggregated traits with family-level assigned traits}
-
-To evaluate the effect of the five trait aggregation methods
-(\textit{direct\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, \textit{weighted\_agg}) on the assignment of trait affinity scores, we compared our aggregated affinities with trait affinities assigned at family level by experts.
-Expert-assigned trait data were available for a subset of grouping features and taxa for Australia (\cite{chessman_dissolved-oxygen_2018}) and North America (CONUS database), so we conducted this comparison only for these two datasets.
-For the Australian dataset, we used the grouping features feeding mode (all traits listed in Table 1 except parasite) and size (220 families $\times$ 8 family–trait combinations = 1760 comparisons).
-For the North American dataset, we used the grouping features feeding mode, respiration, size, voltinism, and locomotion (94 families $\times$ 17 family–trait combinations = 1598 comparisons).
-Assigned traits from North America were on a categorical scale, and we converted them to binary prior to comparing them with aggregated trait affinities.
-Size is a continuous variable in the Australian database, so, we converted size into three traits (small, medium, and large) each with a binary coding.
-Because trait affinities ranged from 0 to 1, the maximum difference possible in trait affinity was 1 to –1, both of which corresponds to 100 \%.
-For convenience and to improve interpretation, we calculated absolute values of the trait differences, e.g.
-a difference of -1 was converted to 1.
-
-Further, we examined the influence of phylogeny and trait variability on the outcomes of the different trait aggregation methods by simulating families with different phylogenetic structures and different levels of trait variability.
-The simulation showed that both phylogenetic structure and trait variability can affect aggregated trait affinities, but mostly only to a small degree.
-As expected, the range of trait affinities increasing trait variability for all trait aggregation methods.
-Therefore, we provide details of the simulation and the results in the supplementary materials.
-
-\begin{figure}
-  \centering
-  \subfile{Flowchart/Flowchart_methods.tex}
-\end{figure}
-\newpage
-\begin{center}
-\captionof{figure}{Data processing steps of the selected traits.
-Intermediate (grey) and main (orange) steps of data preparation are depicted.
-The dashed bottom box illustrates the different trait aggregation methods (hypothetical data in the upper left corner).
-The aggregation methods (purple) and intermediate steps of the aggregation methods (pink) are displayed.
-Abbreviations: EU, Europe; NOA, North America; AUS, Australia; NZ, New Zealand.}
-\label{fig:data_proc_overview}
-\end{center}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships}
-
-To further evaluate the effects of grouping-feature harmonisation and trait aggregation on characterisation of trait–environment relationships, we repeated the analysis of \citet{szocs_effects_2014}, who studied the effects of anthropogenic salinisation on invertebrates in the River Werra in Germany.
-The River Werra has been subject to effluents from the potash industry since the mid- 20th century, which makes it a useful system for studying the responses of invertebrates and their trait compositions to salinisation (\cite{bathe_biological_2011}).
-\citet{szocs_effects_2014} used redundancy analysis (RDA) to compare trait compositions among sites downstream and upstream to the salt discharge.
-Details about the original study can be found in \citet{szocs_effects_2014}.
-
-We re-analysed the \citet{szocs_effects_2014} data by performing a RDA with harmonised grouping features from the dataset for Europe and with traits that we aggregated to family level with the five aggregation methods described above.
-We used all 21 grouping features from the original study, but replaced 6 with harmonised grouping features from the established European trait dataset, namely size, feeding mode, locomotion, oviposition, respiration, and voltinism.
-We compared the results of the original study’s RDA with the results of the RDA from the harmonised grouping features.
-Specifically, trait composition, expressed as community weighted mean (CWM) traits, was ordinated along an electrical conductivity gradient.
-We compared the species scores obtained from the RDA (i.e., the coordinates of the tips of the vectors representing the CWM traits in the bi- or triplots).
-Following the original study, we used the Mahalanobis distance measure and identified traits associated with higher or lower salinity based on their distance to the ordination axis median.
-We considered CWM traits with a Mahalanobis distance greater than the 97.5 \%-quantile of the Chi-square distribution (5.02) to have responded to either lower or higher salinity.
-Additionally, to test for the effect of different aggregation methods on inferences about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
-% Add change in functional diversity
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Software used in data analyses}
-
-All data processing and RDA analyses were carried out using R version 3.6.1 (\cite{cite_R}).
-RDA was computed using the vegan package (\cite{cite_vegan}).
-Raw data and the R code for data processing and grouping feature harmonisation are located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
-Scripts and data to reproduce the trait aggregation, comparison of aggregated and assigned traits, and the RDA analysis are located in the Github repository: \url{https://github.com/KunzstLD/Trait-aggregation}.
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Results}
-
-\subsection*{Harmonised trait datasets}
-
-\subsubsection*{Taxonomic coverage of the harmonised trait datasets}
-
-The harmonised European, North American, Australian, and New Zealand trait datasets differed in terms of their taxonomic coverage.
-The European trait dataset had the largest taxon pool with 4601 taxa (Table \ref{tab:tax_coverage}) followed by the North American dataset (3753 taxa), the Australian dataset (1402 taxa), and the New Zealand dataset with the smallest taxon pool (478 taxa).
-The European, North American, and New Zealand datasets contained the most taxa at the species level, whereas the Australian dataset comprised a similar number of taxa at species and genus level.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection*{Completeness of trait information}
-
-The numbers of entries with available information for the selected grouping features varied considerably within the harmonised European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
-By contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (94–100\%).
-
-The number of entries with available information for the selected grouping features varied strongly across the established European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
-In contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection*{Discrepancies in invertebrate trait definitions across databases}
-
-Definitions of grouping features and traits varied in their level of detail in the six trait databases.
-The freshwaterecology.info, Tachet, and CONUS databases provided more detailed descriptions of trait information than the Vieira and New Zealand databases provided.
-The Australian trait database (\cite{kefford_integrated_2020}) was a collection of seven specific trait datasets; thus, grouping features occurred multiple times with varying differentiation into traits.
-Depending on the dataset, trait information was described with more or less detail.
-
-The definitions of grouping features also varied across databases in their differentiation into traits and in their focus, both which can lead to discrepancies in trait definitions (see Table \ref{tab:trait_definitions} and Table \ref{stab:trait_definitions} for a summary of discrepancies in trait definitions).
-Varying levels of differentiation among the trait databases were present in all investigated grouping features (Table \ref{tab:trait_databases_coding_differentiation}, Table \ref{tab:trait_definitions}, and Table \ref{stab:trait_definitions}).
-
-For example, for the grouping feature feeding mode, discrepancies arose because traits were assigned in different ways.
-The Tachet database defined predators as carvers, engulfers, and swallowers.
-By contrast, the CONUS database defined predators as engulfers and carnivorous piercers.
-In turn, the Tachet database defined piercers as a separate trait encompassing both herbivorous and carnivorous piercers.
-Furthermore, the feeding mode in the freshwaterecology.info database was primarily described in terms of type of food (except for filterers), whereas the other databases described feeding mode in terms of strategies of food acquisition.
-For example, the freshwaterecology.info database defined predator as "eating from prey", and the other databases used the mouthpart morphology as the basis for their definitions.
-The Tachet database captured the food source in a separate grouping feature.
-Locomotion definitions also differed in focus among databases.
-The New Zealand and freshwaterecology.info databases described locomotion as an organism’s way of movement, the Tachet database as substrate relation and locomotion, the Vieira database as how organisms deal with flow, the Australia database as attachment, and the CONUS database as not only the method of movement but also the location of movement.
-Similarly, databases differed in the way they characterise reproduction traits.
-In the freshwaterecology.info and Tachet databases, reproduction was captured in one grouping feature and was defined as location of oviposit clutches and mode of reproduction.
-The Vieira database provided information on the oviposition location but not on reproductive behaviour.
-The Australian database reported grouping features for reproductive behaviour but also on oviposition location separately.
-The New Zealand database distinguished three grouping features related to reproduction: reproductive technique, oviposition location (e.g.
-water surface, terrestrial), and egg/egg mass (e.g.
-free, cemented).
-
-Trait affinity scores also varied among the databases and were described by varying coding methods (e.g., binary, fuzzy, continuous).
-In the freshwaterecology.info and Australian databases a combination of coding methods is used, whereas in the Tachet and New Zealand databases exclusively fuzzy coding is used.
-The Vieira and CONUS databases contained categorical grouping features that can be converted into binary trait affinities (Table \ref{tab:trait_databases_coding_differentiation}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Comparing aggregation methods}
-
-\subsubsection*{Comparison of family-level aggregated traits with family-level assigned traits}
-\label{sec:diff_trait_agg_chessman}
-
-The comparison of family-level aggregated trait affinities with those assigned by experts for the Australian and North American databases showed that aggregation method (median or mean) had a greater effect than the overall approach (direct, stepwise, or weighted by the number of species) in whether trait affinities differed from those assigned by experts.
-
-The percentage of differing cases of aggregated versus assigned trait affinities varied by method between 16.2 and 22.9 \% for the Australian dataset and between 15.3 and 47 \% for the North American dataset (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
-In general, median aggregation methods yielded fewer cases with differences compared with mean aggregation methods.
-However, median aggregation methods produced, on average, greater absolute differences for both datasets.
-Standard deviations of absolute differences were similar for all tested aggregation methods.
-Maximum differences of 1 (i.e., the maximum possible difference) occurred for all investigated grouping features in both datasets (Figure \ref{fig:diff_aggr_traits_combined}).
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=16.5cm, height=12cm]{Deviances_trait_agg_combined.png}
-  \caption{Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the Australian and North American dataset.
-Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the grouping features feeding mode and body size.
-Results for the North American dataset for the grouping features locomotion, respiration, and voltinism are shown in the supporting information (Figure \ref{fig:diff_aggr_traits_pyne}).
-Absolute differences in trait affinities are depicted as grey dots.
-\textit{n} denotes the number of cases per comparison where differences occurred.
-The blue dot indicates the mean of absolute differences, and the error bars show the standard deviation.
-The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.
-Abbreviations: AUS, Australia; NA, North America.}
-  \label{fig:diff_aggr_traits_combined}
-\end{figure}
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships}
-
-Our re-analysis of the \citet{szocs_effects_2014} study on the effects of salinisation on invertebrate traits showed that the use of harmonised and aggregated trait data may be useful for ecological studies on trait–environment relationships.
-Overall, harmonised trait data and all aggregation methods produced similar distributions of RDA species scores (\ref{fig:violin_plot_species_sc}) compared with the original analysis, and they resulted in similar, but fewer, traits that distinguished upstream and downstream sites than the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
-
-RDA using harmonised, but not aggregated, grouping features identified some, but not all, of the same traits that were identified by the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
-The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (higher salinity) were characterised by the traits: ovoviviparity, multivoltinism, long life-cycle duration ($> 1$ year), shredder, and gill respiration, whereas RDA with the harmonised data identified the first three traits but did not include shredder or gill respiration traits.
-The original RDA indicated that upstream sites (lower salinity) were characterised by the traits: univoltinism, oviposition in clutches, and short life-cycle duration ($< 1$ year), and RDA with the harmonised data characterised upstream sites by univoltine taxa with short life-cycle durations that lay their eggs in an aquatic environment (aquatic eggs).
-This difference in the oviposition trait is not substantial because the trait aquatic eggs of the harmonised grouping feature oviposition was derived by combining the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonisation}).
-
-RDA based on harmonised traits that were aggregated to family level also produced results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
-The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg} characterised the downstream sites with the same traits as the original analysis except the trait shredder.
-As for the RDA with harmonised but not aggregated data, RDA with these three aggregation methods characterised upstream sites by the traits univoltinism, short life-cycle duration, and aquatic eggs.
-The \textit{stepwise\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}} methods produced the same results except that none of the life-cycle traits characterised upstream or downstream sites.
-Thus, compared with the original study’s findings, aggregating by the direct and weighted methods yielded less change than the stepwise methods in interpretation of the RDA results.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
-    \caption{Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonised grouping features, and using harmonised grouping features with traits aggregated to family level with five different aggregation methods.
-The dots represent the individual species scores for each analysed trait along the conductivity axis.
-The violin plot shows the density estimate of the species scores.
-Grey vertical lines indicate the median of the obtained species scores.}
-    \label{fig:violin_plot_species_sc}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=17cm, height=14.5cm]{boxplot_scores_combined.png}
-\end{figure}
-\begin{center}
-\captionof{figure}{RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{median}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
-Shown are boxplots of the site scores along the conductivity axis.
-The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
-Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
-For better comparability, species scores of the original analysis were multiplied by -1.
-Results for the other aggregated methods are shown in the supporting information (Figure \ref{fig:boxplots_scores_on_constrained_axis_REMAIN}).
-Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.}
-\label{fig:boxplot_scores_on_constrained_axis}
-\end{center}
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Discussion}
-
-Freshwater invertebrate trait databases are a valuable source of data that are freely available to researchers and that can offer opportunities for large-scale, cross-regional ecological study without the need for time-consuming and expensive field work.
-However, a lack of consistency among regional and continent-wide databases in trait definitions, trait affinity coding, and taxonomic resolution can greatly limit the use of combined databases.
-We explored the effects of harmonising grouping features and aggregating trait affinities at different taxonomic levels from databases from four different continents on the outcomes of trait affinities and on analysis of trait–environment relationships.
-We found that despite discrepancies in trait definitions and taxonomic resolution across databases, harmonised and aggregated data were generally effective in identifying trait–environmental relationships, as evidenced by similar results from RDA as were found using observational data.
-Our results have implications for future multi-regional ecological studies that may benefit from the use of existing databases and provide insight into methods for harmonising traits with differing trait definitions and selecting aggregation methods that minimize either cases or ranges of differences in trait affinity scores when aggregating from higher to lower taxonomic precision.
-
-\subsection*{Harmonising trait databases}
-
-Synthesising trait information from multiple trait databases is crucial for developing the full potential of trait-based approaches, such as for studying community trait responses to environmental gradients across geographic regions.
-Others have noted the lack of standardised trait terminology in freshwater ecology (\cite{baird_toward_2011, brink_traits-based_2011}), but in this study we show for the first time the discrepancies that exist across some commonly used grouping features.
-Furthermore, we offer insight into the need for, and process of, harmonising invertebrate trait information from trait databases of different regions.
-Some of the challenges we found were that grouping features were resolved differently into traits in different databases and that various codings (fuzzy, categorical, binary) were used to describe traits.
-In addition, the same traits were sometimes defined differently, requiring expert knowledge to reclassify these traits (e.g.
-the trait piercer).
-Missing information was another challenge.
-We aimed to use most of the available invertebrate trait information for different regions to establish harmonised grouping feature datasets, but the availability of trait information varied strongly across grouping features and databases.
-For instance, extensive information was available for grouping features that are often used in trait–environment studies, such as feeding mode and respiration, but there was surprisingly little information on body form, a trait that is relatively easy to characterise.
-
-To resolve definition discrepancies and facilitate data synthesis in the future, terminological standards are needed.
-Harmonised definitions and concepts of traits have been developed in the past for other organism groups, such as for plants with the \textit{Thesaurus of Plant Characteristics} (TOP) initiative (\cite{garnier_towards_2017}).
-The core of this harmonisation initiative is to provide standardised trait definitions and to draw connections to synonyms, related terms, and surrounding concepts by linking to other controlled vocabularies or ontologies in the field.
-Such initiatives should encourage freshwater ecologists to establish unambiguous terminologies for invertebrate traits.
-The existing freshwater invertebrate trait databases could be linked through standardised terminologies or ontologies, as suggested by \citet{baird_toward_2011}.
-By following the recently proposed \textit{Ecological Trait-data Standard Vocabulary} (ETS), providers of invertebrate trait data could connect their traits to such ontologies (\cite{schneider_towards_2019}).
-Once standardised trait definitions are established, they will improve trait data sharing, trait data processing when working with multiple trait databases, and, ultimately, interpretation of the derived results.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Trait aggregation method choice}
-
-The taxonomic resolution used to describe the occurrence and abundance of freshwater invertebrates can be highly variable because species-level identifications require specialists and are also often time-consuming and expensive (\cite{marshall_taxonomic_2006, resh_which_2008}).
-Consequently, trait information at the family level has been widely used by freshwater ecologists, for example in bioassessment (\cite{beketov_spear_2009}).
-However, traits assigned at the family level may not reflect the full trait diversity that exists within, for example, large, ecologically diverse families such as Chironomidae (\cite{serra_synthesising_2016}).
-Additionally, various trait aggregation methods have been used by researchers to compare trait profiles based on different taxonomic levels.
-Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait is for a particular family.
-Aggregation of trait information at the species or genus level to a single estimate at the family level implies a precision that is not necessarily present, especially not for traits with high variability or if trait information at species level is missing.
-Indeed, some traits can vary strongly at more resolved taxonomic levels than the family level.
-For example, \citet{monaghan_improving_2013} found high intra-family trait dispersion in the Tachet database for traits within the grouping features body size, flow preference, and reproduction.
-Furthermore, studies focusing on the lability of traits, (i.e.
-how much traits are constrained by phylogeny), found that traits of ecological preferences (e.g.
-thermal preference), body size, resistance forms, and, to a lesser extent, feeding mode are labile, and thus possibly highly variable (\cite{poff_functional_2006, wilkes_traitbased_2020}).
-
-If trait aggregation is necessary, however, our study offers insights about the circumstances under which the choice of aggregation method may be important.
-The 5 aggregation methods we tested used either the mean or the median and different weightings to assign family-level affinities.
-Our results indicated that for both the Australian and North American datasets (1) the median aggregation methods provided affinities that were often closer to the assigned traits than were those provided by the mean aggregation methods and (2) the different weighting approaches exerted only a minor influence on the aggregated trait affinities.
-However, when differences occurred between median aggregation methods and assigned traits, these differences were greater in absolute value compared with the mean aggregation methods, particularly for the North American dataset where mean absolute differences for median aggregations were twice as high as for mean aggregations.
-This pattern of greater differences for median than mean aggregations is probably caused by the use of binary coding in the North American trait dataset and by the assigned traits.
-Binary coded traits have affinities of either 1 or 0; therefore, traits of a particular grouping feature showed, in most cases, a higher difference in trait affinities to each other than if they were fuzzy coded.
-Median-aggregated binary-coded taxa often resulted in a value of 0 or 1, whereas mean aggregation often yielded values between 0 and 1.
-Thus, using the median resulted in the North American dataset either to agreement with the assigned traits or to more substantial differences compared to the use of mean aggregation methods.
-This pattern inherent in using median-aggregation methods to aggregate binary-coded data should be considered when researchers choose methods to resolve affinities at different taxonomic levels.
-
-We expected that, in addition to averaging measures, different weighting approaches to aggregation (i.e., equal weight to each taxon, equal weight to each genus, or weighted by number of species) would affect affinities for families with varying phylogenetic structure.
-However, we found through simulations that trait variability had a greater effect on the range of affinities (i.e., greater ranges of affinities at higher levels of variance) and on the differences in affinities between weighting approaches.
-In the simulation, taxonomic structural unevenness appeared to produce some variation in affinities among weighting approaches, especially for a family where one genus had a much larger number of species than its other genera.
-The comparison between aggregated and assigned traits showed, that the number of differing cases and the mean absolute differences in trait affinities, as well as the distributions of absolute trait affinity differences to assigned traits, were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weighting approach on the aggregation outcomes.
-The minor impact of the weighting approaches on trait aggregation might be explained by the fact that a considerable portion of taxa had low numbers of genera or species.
-Of the taxa that were compared from the North American trait dataset, 14 \% were identified at family and 62 \% at genus level, 52 \% comprised five or fewer genera, and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
-In the Australian dataset, 21 \% of the compared taxa were identified at family, 40 \% at genus, and 39 \% at species level, 68 \% of the taxa contained five or fewer genera, and 40 \% just one genus (Figure \ref{fig:tax_hierarchy_AUS}).
-Hence, these results could change when more species-level trait information becomes available.
-Our findings show that the choice of aggregation method may matter less when phylogenetic structure is fairly even and traits are less variable, but the \textit{stepwise\_agg\textsubscript{median}} method tended to produce the widest range in affinities, especially with high taxonomic unevenness and high trait variability.
-
-\subsection*{Using harmonised and aggregated datasets for ecological research}
-
-By reanalysing trait–environment relationships identified in \citet{szocs_effects_2014} with our harmonised and family-level aggregated datasets, we illustrated the potential for the use of harmonised and aggregated data in ecological research.
-As far as we are aware, ours is the first study to compare inferences regarding trait–environment relationships based on harmonised and non-harmonised data.
-Our re-analysis of the data on salinisation effects on biological traits yielded only slightly different results compared with the original study, which agrees with previous findings that family-level traits can be sensitive enough to detect environmental impacts (\cite{beketov_spear_2009}).
-However, some of the traits that had responded in the original analysis did not respond in the re-analysis, specifically feeding mode shredder, respiration gills, and life-cycle duration traits.
-There are several possible reasons for these discrepancies.
-The non-responsive traits were those closest to the threshold for association with either higher or lower salinity, and so the precision lost through trait harmonisation may have decreased our ability to detect a relatively weak association.
-The shredder feeding mode was the only trait that was non-responsive when using harmonised (but not aggregated) data as well as when using aggregated data.
-This result was likely because of the harmonisation procedure, in which this trait was combined based on three traits (miner, xylophagus, and shredder) used in the original databases.
-Consequently, the trait affinities in the original data had a higher mean and standard deviation than in the harmonised and aggregated data (Table \ref{tab:SI_resp_traits_summary_stats}), suggesting that the signal in the original data was weakened by harmonisation.
-Given this result, we suggest that if harmonisation is necessary, harmonised and non-harmonised data, if available, should be compared, and possible averaging effects should be considered in further analyses.
-However, our results also illustrate that where site-level data are not available, harmonised and aggregated datasets may be useful in identifying at least the strongest associations between traits and environmental conditions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Outlook}
-
-Although comprehensive freshwater invertebrate trait databases have been developed for several regions in the past, data synthesis presents challenges because of discrepancies in trait definitions, coding of trait affinities, and taxonomic resolution.
-By providing an overview of definition discrepancies, we have set a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
-Agreement on standard terminology and the subsequent development of ontologies are the next steps to facilitate trait-based analysis at large geographical scales.
-As our analysis showed, some grouping features might need to be re-classified to fit into such a standardised terminology.
-Although we showed that trait affinities from fuzzy and binary coding can be used together, we also recommend that a uniform coding of traits should be addressed during trait standardisation.
-
-As ecological knowledge increases, and with the help of new methods such as computer vision for species and trait identification (\cite{hoye_deep_2020}), more observed taxa will be identified to the species level and trait data will be available at the species level in the future, reducing the need for trait aggregation.
-However, we showed that trait aggregation is often in agreement with expert assignments, especially through aggregation approaches that use the median.
-Based on this analysis, we cannot claim that a specific aggregation method is objectively the best, and except for cases where traits are highly variable and phylogenetic structure is highly uneven, the choice of aggregation method does not appear to be influential to the outcome.
-Weighting trait information based on the taxa present in the database used does not seem to have much influence except when the phylogenetic structure is highly uneven.
-However, we recommend that the type of coding used to describe traits (binary, fuzzy) should be considered, because median and mean aggregations can yield very different results for binary-coded traits.
-We also suggest that a measure of trait dispersion should be reported to indicate the uncertainty of the aggregated estimate.
-Use of carefully harmonised and integrated trait data as described here should enhance our ability to study a wide range of large-scale ecological questions with greater rigor than currently exists.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Acknowledgements}
-
-We thank Brooke Cassell for technical editing of the manuscript. The project, in which this study was conducted, is funded by the German research society (DFG, project number 338785727).
-
-\section*{Data availability statement}
-
-Harmonised invertebrate trait datasets for Australia, Europe, North America and New Zealand are deposited in the Github repository: \url{https://github.com/KunzstLD/Trait-aggregation}.
-
-\section*{Conflict of interest}
-
-The authors declare no conflict of interest.
-
-\section*{Author contribution}
-R.B.S.
-and S.K.
-designed the study; B.J.K.
-and L.M.
-provided trait data for Australia; P.U-P.
-provided body form trait data for European and North American invertebrates; C.P.H., N.L.P., and L.T.
-provided trait data for North America; C.D.M.
-provided trait data for New Zealand;
-B.J.K., A.S-K., C.D.M, W.G., N.L.P., L.M., and C.P.H.
-provided in depth information on trait data and discussed the procedure of analysis; S.K.
-conducted data processing and the statistical analyses.; S.K.
-wrote the manuscript; B.J.K, A-S.K., C.D.M, P.U-P., C.P.H., and R.B.S.
-discussed the results and provided suggestions on the manuscript.
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\printbibliography
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%% Tables %%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Tables}
-
-% Table 1
+% Table 1:Excerpt from differences in trait definitions
 \begin{landscape}
-  \begin{longtable}{m{2.0cm}|m{4.0cm}|m{4.2cm}|m{4.2cm}|m{1.7cm}|m{2cm}|m{2.2cm}}
+  \begin{longtable}{m{2.0cm}|m{3.5cm}|m{3.4cm}|m{4.2cm}|m{1.7cm}|m{2.5cm}|m{2.2cm}}
       \caption{Excerpt of the comparison of trait definitions between invertebrate trait databases for the traits predator and swimming.
 The definition is quoted if it enables differences to be identified, otherwise the differences are described.
-The full version and further information can be found in the supporting information Table \ref{stab:trait_definitions}.}
-      \label{tab:trait_definitions}
+The full version and further information can be found in the supporting information Table S\ref{stab:trait_definitions}.}
+      \label{stab:trait_definitions}
       \endfirsthead
@@
         \\ 
-        \midrule
+        \toprule[.1em]
         Locomotion swimming & 
@@
         Swimmer & 
-        Traits swimmer and skater & 
+        Distinguishes swimmer and skater & 
         Swimmers (water column)
@@
 
-\section*{Figure captions}
-
-\textbf{Figure caption 1:}
-
-Data processing steps of the selected traits.
-Intermediate (grey) and main (orange) steps of data preparation are depicted.
-The dashed bottom box illustrates the different trait aggregation methods (hypothetical data in the upper left corner).
-The aggregation methods (purple) and intermediate steps of the aggregation methods (pink) are displayed.
-Abbreviations: EU, Europe; NOA, North America; AUS, Australia; NZ, New Zealand.
-\\
-
-\noindent{\textbf{Figure caption 2:}}
-
-Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the Australian and North American dataset.
-Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the grouping features feeding mode and body size.
-Results for the North American dataset for the grouping features locomotion, respiration, and voltinism are shown in the supporting information (Figure \ref{fig:diff_aggr_traits_pyne}).
-Absolute differences in trait affinities are depicted as grey dots.
-\textit{n} denotes the number of cases per comparison where differences occurred.
-The blue dot indicates the mean of absolute differences, and the error bars show the standard deviation.
-The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.
-Abbreviations: AUS, Australia; NA, North America.
-\\
-
-\noindent{\textbf{Figure caption 3:}}
-
-Ranges of aggregated trait affinities for the three examples of phylogenetic structures and simulated levels of trait variability.
-Shown are the results only for one simulated trait (T1).
-Similar results were obtained for the other simulated traits (Figure \ref{fig:overview_sim_results_T2_T3}).
-Boxplots depict results for 100 replicated simulations of each trait aggregation method.
-The boxplot depicts the median and encompasses the 25\textsuperscript{th} and 75\textsuperscript{th} percentile.
-Horizontal black lines depict the median.
-Whiskers extend to the largest and smallest value respectively no further than 1.5 $\times$ the inter-quartile range.
-Outliers beyond the end of the whiskers are plotted as grey dots.
-Trait aggregation methods are in order of least to greatest produced ranges to improve visual inspection.
-\\
-
-\noindent{\textbf{Figure caption 4:}}
-
-Comparison between the aggregated trait affinities produced by the different trait aggregation methods for every simulated dataset across all 3 simulated traits (5,000 comparisons per scenario).
-Results are shown for different levels of trait variability which is represented by the standard deviation (SD) of the simulated traits.
-Dots depict comparisons where absolute differences between aggregated trait affinities were greater than 0.1.
-Overall, there are 10 possible unique comparisons of which 7 produced absolute differences greater than 0.1.
-\newline
-  Comparisons: \newline
-  1) \textit{direct\_agg\textsubscript{median}} - \textit{stepwise\_agg\textsubscript{mean}} \newline
-  2) \textit{direct\_agg\textsubscript{median}} - \textit{weighted\_agg} \newline
-  3) \textit{stepwise\_agg\textsubscript{mean}} - \textit{stepwise\_agg\textsubscript{median}} \newline
-  4) \textit{stepwise\_agg\textsubscript{mean}} - \textit{weighted\_agg} \newline  
-  5) \textit{direct\_agg\textsubscript{mean}} - \textit{stepwise\_agg\textsubscript{median}} \newline
-  6) \textit{direct\_agg\textsubscript{median}} - \textit{stepwise\_agg\textsubscript{median}} \newline
-  7) \textit{stepwise\_agg\textsubscript{median}} - \textit{weighted\_agg}
-\\
-
-\noindent{\textbf{Figure caption 5:}}
-
-Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonised grouping features, and using harmonised grouping features with traits aggregated to family level with five different aggregation methods.
-The dots represent the individual species scores for each analysed trait along the conductivity axis.
-The violin plot shows the density estimate of the species scores.
-Grey vertical lines indicate the median of the obtained species scores.
-\\
-
-\noindent{\textbf{Figure caption 6:}}
-
-RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{median}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
-Shown are boxplots of the site scores along the conductivity axis.
-The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
-Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
-For better comparability, species scores of the original analysis were multiplied by -1.
-Results for the other aggregated methods are shown in the supporting information (Figure \ref{fig:boxplots_scores_on_constrained_axis_REMAIN}).
-Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.
-
 \end{document}

### 2021-06-28 R/01_EU_preprocess_new.R
28.06.2021: Update r scripts28.06.2021: Update r scripts

@@ -10,10 +10,11 @@ trait_EU <- readRDS(
     "Trait_freshecol_2020_pp.rds"
   )
 )
+names(trait_EU)
 
 # Subset to relevant traits
 trait_EU <- trait_EU[, .SD,
-  .SDcols = names(trait_EU) %like% "^order$|^family$|genus|species|taxon.*|feed|loco|resp|volt|rep|size|ID.*"
+  .SDcols = names(trait_EU) %like% "^order$|^family$|genus|species|taxon.*|feed|loco|resp|volt|rep|size|temp|ID.*"
 ]
 
 # Voltinism trait contains thermal conditions, change every string to 1
@@ -44,17 +45,16 @@ no_info <- trait_EU[, apply(.SD, 1, function(y) {
 pos <- no_info == ncol(trait_EU[, ..col])
 trait_EU <- trait_EU[!pos, ]
 
-# __________________________________
+# __________________________________________________________________________________________________
 #### Consolidate duplicate taxa ####
 # only for family-level
-# species and genus duplicates have been introduced in the past
-# by rm e.g. "new Gen. sp." from some species
+# species and genus duplicates have been introduced by rm e.g. "new Gen. sp." from some species
 # has not been done now
-# __________________________________
+# __________________________________________________________________________________________________
 
 # binary columns -> aggr via max
 # fuzzy coded columns -> aggr via median
-cols_bin <- grep("(?=volt.*|resp.*)(?!.*tachet)",
+cols_bin <- grep("(?=volt.*|resp.*|temp.*)(?!.*tachet)",
                  names(trait_EU),
                  value = TRUE,
                  perl = TRUE
@@ -127,7 +127,7 @@ trait_EU[is.na(species) & is.na(genus) & family %in% dupl_families,
 # were on subfamily-tribe level which will be used later 
 # in the re-analysis of Szöcs et al. 2014
 # code to remove:
-# rm_dupl <- trait_EU[is.na(species) & is.na(genus) & !is.na(family), ] %>% 
+# rm_dupl <- trait_EU[is.na(species) & is.na(genus) & !is.na(family), ] %>%
 # .[duplicated(family), taxon_cp]
 # trait_EU <- trait_EU[!(taxon_cp %in% rm_dupl),]
 

### 2021-06-28 R/02_EU_harmonize_new.R

@@ -405,7 +405,6 @@ Trait_EU <- Trait_EU[is.na(feed_other) | feed_other < 0.5, ]
 Trait_EU[feed_other > 0, feed_other := 0]
 Trait_EU[, "feed_other" := NULL]
 
-
 # _________________________________________________________________________
 #### Locomotion ####
 # locm_swim:  swimmer, scater (active & passive)
@@ -609,18 +608,30 @@ Trait_EU[, c(
 
 # _________________________________________________________________________
 #### Temperature ####
-# temp very cold (< 6 °C)
-# temp cold (< 10 °C)
-# temp moderate (< 18 °C)
-# temp warm (>= 18 °C)
+# temp_coldsteno: cold stenotherm (cos); preference for a small cold temperature range (below 10°C)
+# temp_warmsteno: warm stenotherm	(was);	preference for a small warm temperature range (above 18°C)
+# temp_euryt: eurytherm	(eut)	no specific preference, wide temperature range
 # temp eurytherm (no specific preference)
+# psychrophilic (< 15 °C)
+# thermophilic (> 15 °C)
+# -> temp_eury, temp_cold, temp_warm (themophilic & stenotherm)
 # _________________________________________________________________________
-# Trait_EU[, temp_cold := apply(.SD, 1, max),
-#   .SDcols = c("temp_cold", "temp_moderate", "temp_very_cold")
-# ]
-# Trait_EU[, c("temp_moderate", "temp_very_cold") := NULL]
-
-
+Trait_EU[, temp_eury := apply(.SD, 1, max, na.rm = TRUE),
+         .SDcols = c("temp_euryt",
+                     "temp_euryt_tachet")]
+Trait_EU[, temp_cold := apply(.SD, 1, max, na.rm = TRUE),
+         .SDcols = c("temp_coldsteno",
+                     "temp_psychrophil_tachet")]
+Trait_EU[, temp_warm := apply(.SD, 1, max, na.rm = TRUE),
+         .SDcols = c("temp_warmsteno", "temp_thermophil_tachet")
+]
+Trait_EU[, c("temp_euryt", 
+             "temp_euryt_tachet",
+             "temp_coldsteno",
+             "temp_psychrophil_tachet",
+             "temp_warmsteno", 
+             "temp_thermophil_tachet"
+             ) := NULL]
 # _________________________________________________________________________
 #### Body form ####
[…]

### 2021-06-28 R/02_NOA_preprocessing.R

@@ -9,14 +9,14 @@ Trait_Noa <- readRDS(file = file.path(data_cleaned,
                                       "North_America",
                                       "Traits_US_taxa_pp.rds"))
 
-# subset to relevant traits:
+# Subset to relevant traits:
 cols <- "Resp_late|Ovipos_behav_prim|stages|Habit_prim|Thermal_pref|Larval_disp|Feed_mode_prim|Voltinism|size|Body\\_shape|Order|Family|Genus|Species"
 Trait_Noa <- Trait_Noa[, .SD, .SDcols = names(Trait_Noa) %like% cols]
 
 # Add ID col as unique identifier
 Trait_Noa[, unique_id := 1:nrow(Trait_Noa)]
 
-# taxonomical corrections
+# Taxonomical corrections
 # Parapoynx & Petrophilia
 Trait_Noa[Genus %in% c("Parapoynx",
                        "Petrophila"), Family := "Crambidae"]
@@ -32,6 +32,7 @@ Trait_Noa[Family == "Corbiculidae", Order := "Venerida"]
 
 #__________________________________________________________________________
 #### Create two DB versions with different codings ####
+# NOTE: "Fuzzy coded" version not used
 #__________________________________________________________________________
 
 # transform categories to columns!

### 2021-06-28 R/03_AUS_aggregate_traits.R

@@ -102,3 +102,5 @@ Trait_AUS_agg <- normalize_by_rowSum(Trait_AUS_agg,
 # save
 saveRDS(object = Trait_AUS_agg,
         file = file.path(data_out, "Trait_AUS_agg.rds"))
+saveRDS(object = Trait_AUS_agg, 
+        file = "/home/kunzst/Dokumente/Projects/Trait_DB/Convergence-trait-profiles/Data/Trait_AUS_agg.rds")

### 2021-06-28 R/03_EU_aggregate_traits.R

@@ -5,7 +5,9 @@
 # read in harmonized, preprocessed & already normalized EU Trait DB
 # data are already normalized!
 Trait_EU <-
-  readRDS(file = file.path(data_cleaned, "EU", "Trait_EU_pp_harmonized.rds"))
+  readRDS(file = file.path(data_cleaned, 
+                           "EU",
+                           "Trait_freshecol_2020_pp_harmonized.rds"))
 
 # check completeness of trait data
 completeness_trait_data(x = Trait_EU,
@@ -31,7 +33,6 @@ Trait_EU <- Trait_EU[, .SD,
     "Neuroptera"
   ),]
 
-
 # trait aggregation to family-lvl
 Trait_EU_agg <- direct_agg(
   trait_data = Trait_EU,
@@ -50,7 +51,6 @@ Trait_EU_agg <- normalize_by_rowSum(x = Trait_EU_agg,
           cols = names(.[, -c("family",
                               "order")]))
 
-  
 # TODO: BF information, check that again!
 # family information in tachet not completely covered in agg. freshwaterecol
 # BF information missing for few families
@@ -69,5 +69,8 @@ Trait_EU_agg <- normalize_by_rowSum(x = Trait_EU_agg,
 #   "Diptera"
 # ), ]
 
-# cache as RDS object
+# Save as RDS object
 saveRDS(object = Trait_EU_agg, file = file.path(data_out, "Trait_EU_agg.rds"))
+# For TPG analysis
+saveRDS(object = Trait_EU_agg, 
+        file = "/home/kunzst/Dokumente/Projects/Trait_DB/Convergence-trait-profiles/Data/Trait_EU_agg.rds")

### 2021-06-28 R/03_NZ_aggregate_traits.R

@@ -67,7 +67,7 @@ Trait_NZ_agg <-
           cols = names(.[, -c("family",
                               "order")]))
 
-# dim(Trait_NZ_agg)
-
 # save
 saveRDS(object = Trait_NZ_agg, file = file.path(data_out, "Trait_NZ_agg.rds"))
+saveRDS(object = Trait_NZ_agg, 
+        file = "/home/kunzst/Dokumente/Projects/Trait_DB/Convergence-trait-profiles/Data/Trait_NZ_agg.rds")

### 2021-06-28 R/04_NOA_NEW_preprocessing.R

@@ -21,7 +21,6 @@ cols <-
     "Voltinism_abbrev"
   )
 Trait_Noa_new <- Trait_Noa_new[, .SD, .SDcols = cols]
-
 Trait_Noa_new[which(Trait_Noa_new$Habit_prim == "Other (specify in comments)"),]
 
 # create species column
@@ -160,6 +159,9 @@ Trait_Noa_new[!is.na(Species) &
 dupl_unique_id <- Trait_Noa_new[duplicated(Species) & !is.na(Species), unique_id]
 Trait_Noa_new <- Trait_Noa_new[!unique_id %in% dupl_unique_id, ]
 
+
+Trait_Noa_new[Species == "Ephemerella subvaria", ]
+
 # genus-level:
 Trait_Noa_new[is.na(Species) & !is.na(Genus) &
                 (duplicated(Genus) |
@@ -187,9 +189,6 @@ Trait_Noa_new <- Trait_Noa_new[!unique_id %in% dupl_unique_id, ]
 setnames(Trait_Noa_new, 
          old = c("Species", "Genus", "Family", "Order"), 
          new = c("species", "genus", "family", "order"))
-
-Trait_Noa_new[family == "Corbiculidae", ]
-# order := "Venerida"
 
 # save
 saveRDS(object = Trait_Noa_new, 

### 2021-06-28 R/06_NOA_NEW_aggregate_traits.R

@@ -57,7 +57,10 @@ Trait_Noa_new_agg <- normalize_by_rowSum(x = Trait_Noa_new_agg,
           cols = names(.[, -c("family",
                               "order")]))
   
-  
+dim(Trait_Noa_new_agg)  
+
 # save
 saveRDS(object = Trait_Noa_new_agg,
-        file = file.path(data_out, "Trait_Noa_agg.rds"))
+        file = file.path(data_out, "Trait_NOA_agg.rds"))
+saveRDS(object = Trait_Noa_new_agg,
+        file = "/home/kunzst/Dokumente/Projects/Trait_DB/Convergence-trait-profiles/Data/Trait_NOA_agg.rds")

### 2021-06-28 R/Checking_references.R

@@ -1,0 +1,64 @@
+
+# reference cols
+ref_cols <- grep("(?i)ref.+", names(Trait_AUS), value = TRUE)
+
+# search terms 
+search <- c("Merrit.+Cummins.+1986" = 70,
+            "Merrit.+Cummins.+1978" = 236,
+            "Poff.+2006" = 261)
+
+# create lf of reference data from AUS trait dataset
+Trait_AUS <-
+  fread(file.path(data_in,
+                  "Australia",
+                  "Australian_macroinv_trait_database_final.csv"))
+
+ref_data <- melt(Trait_AUS[, c("Species", "Genus", "Family", "Order", ref_cols), with = FALSE], 
+     measure.vars = ref_cols)
+
+#### Feeding mode ####
+
+# References in search are used in NOA dataset
+# check if these families were used in the NOA dataset for trait aggregations
+# than compare 
+ref_data[value %in% search, ]
+
+# Trait NOA table
+Trait_Noa_new <- fread(file.path(data_in, "North_America", "Trait_table_LauraT.csv"))
+cols <- c("Accepted_Name", "Genus", "Family", "Order", "Study_Citation_abbrev", "Study_Citation")
+
+refs_Noa <- Trait_Noa_new[, ..cols]
+
+# might use the same source for feeding, but not really sure (according to the trait
+# table description Trophic Relations of Aquatic Insects is used in Noa)
+Trait_Noa_new[Study_Citation_abbrev %like% "Merrit.+Cummins" & !is.na(Feed_prim_abbrev), ]
+
+
+#### Body size ####
+# Check body size data, as these look very similar between NOA and AUS!
+# basically, almost all references in the AUS DB availabile for size are
+# assigned at family-level
+# TODO few references need to be fixed!
+body_size_refs <- ref_data[variable %like% "size", unique(value)] %>% 
+  strsplit(. , ";|,") %>% 
+  unlist() %>% 
+  as.numeric() %>% 
+  table()
+
+body_size_refs[order(-body_size_refs)]
+
+# most frequent references: 2, 36, 22, 16
+ref_data[variable %like% "size" & value %like% "22|16" & !is.na(Family), ]
+
+ref_data[variable %like% "size" & !is.na(value) & !is.na(Genus), ]
+
+# could still check if these occur in NOA (which is rather unlikely)
+# 2 - Williams W. D. (1980). Australian Freshwater Life. (MacMillan Books: Melbourne.)
[…]

### 2021-06-28 R/Overview_NOA_trait_data.R

@@ -1,0 +1,115 @@
+# __________________________________________________________________________________________________
+# Harmonized trait DB
+# __________________________________________________________________________________________________
+Trait_Noa_new <- readRDS(file = file.path(data_cleaned,
+                                          "North_America",
+                                          "Traits_US_LauraT_pp_harmonized.rds"))
+names(Trait_Noa_new)
+# feeding mode
+# locomotion (crawler, burrower, clinger, ...)
+# size
+# respiration 
+# voltinism
+# oviposition
+# body form
+
+# Check completeness of trait data
+# just return rows where for each trait there is an observation 
+# oviposition is clearly the bottleneck!
+completeness_trait_data(x = Trait_Noa_new,
+                        non_trait_cols = c("unique_id",
+                                           "species",
+                                           "genus",
+                                           "family",
+                                           "order"))
+
+# Information on species-level: 2414
+Trait_Noa_new[!is.na(species), ]
+# Information on genus-level: 1163
+Trait_Noa_new[is.na(species) & !is.na(genus), ]
+# Information on family-level: 176
+Trait_Noa_new[is.na(species) & is.na(genus) & !is.na(family), ]
+
+# How many taxa per order?
+Trait_Noa_new[, .N, by = order] %>% 
+  ggplot(., aes(x = as.factor(order),
+                              y = N)) +
+  geom_pointrange(aes(ymin = 0,
+                      ymax = N)) +
+  #scale_y_continuous(trans = 'log10') +
+  labs(x = "Order", y = "Number of taxa per order") +
+  ggtitle("Overview taxa harmonized NA trait database") +
+  theme_bw() +
+  theme(
+    axis.title = element_text(size = 16),
+    axis.text.x = element_text(
+      family = "Roboto Mono",
+      size = 14,
+      angle = 90,
+      hjust = 1,
+      vjust = 0.4
+    ),
+    axis.text.y = element_text(family = "Roboto Mono",
+                               size = 14),
+    legend.title = element_text(family = "Roboto Mono",
+                                size = 16),
+    legend.text = element_text(family = "Roboto Mono",
+                               size = 14),
+    strip.text = element_text(family = "Roboto Mono",
+                              size = 14),
+    panel.grid = element_blank()
+  )
+
+# __________________________________________________________________________________________________
+# Twardochleb DB
+# see Paper: https://onlinelibrary.wiley.com/doi/10.1111/geb.13257
[…]

### 2021-06-28 R/Preprocessing_raw/01_preprocess_new_freshecol_2020.R

@@ -1,4 +1,6 @@
-#### read taxaexports ####
+# --------------------------------------------------------------------------------------------------
+#### Lead taxaexports from fwecol ####
+# --------------------------------------------------------------------------------------------------
 filelinks <- list.files(
   path = data_raw,
   pattern = "taxadbexport",
@@ -24,7 +26,10 @@ for (i in seq_along(filelinks)) {
   output_db[[i]] <- db
 }
 
-#### data processing ####
+# --------------------------------------------------------------------------------------------------
+#### Data processing ####
+# --------------------------------------------------------------------------------------------------
+
 # delete summary statistics (not part of DB)
 output_db <- lapply(
   output_db,
@@ -35,7 +40,7 @@ output_db <- lapply(
 lapply(
   output_db[2:length(output_db)],
   function(y) {
-    y[, c("V1", "EU") := NULL]
+    y[, c("V1", "EU", "ID-AQEM (ID-fwe)") := NULL]
   }
 )
 
@@ -62,10 +67,18 @@ setnames(aqem, "V1", "taxon")
 # merge ID
 freshwaterecol[aqem, ID_AQEM := `i.ID-AQEM (ID-fwe)`, on = "taxon"]
 
+# --------------------------------------------------------------------------------------------------
+#### Trait preparation ####
+# Some columns have the same colname 
+# that's because sometimes the same traits are named the same way, although they originate
+# from different databases. From these duplicate colnames, the second duplicate always 
+# originates from the tachet database.
+# --------------------------------------------------------------------------------------------------
 
-# trait preparation ----
-
-# pH preference
+#### pH preference ####
+# Explanation:  ph_acidic:      acidic - pH < 7
+#               ph_neutral_alk: neutral to alkaline - ph = 7
+#               ph_ind:         indifferent - no specific preference
 setnames(
   freshwaterecol, c(
     "aci",
@@ -97,26 +110,25 @@ setnames(
   ), 
   "_tachet")
 )
-# Explanation:  ph_acidic:      acidic - pH < 7
-#               ph_neutral_alk: neutral to alkaline - ph = 7
-#               ph_ind:         indifferent - no specific preference
 
-
-# Temperature preference
+#### Temperature preference ####
+# Explanation:  
+#             temp_coldsteno: cold stenotherm (cos); preference for a small cold temperature range (below 10°C)
[…]

### 2021-06-28 Paper/Submission_new/Main_Document-Latex.tex
28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Update Paper and Supp28.06: Updat

@@
 Additionally, to test for the effect of different aggregation methods on inferences about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
-% Add change in functional diversity
+
+Finally, we assessed how functional diversity (FD) changed when harmonised and aggregated trait data are used.
+Harmonisation of grouping features reduces the number of traits per grouping feature and thus likely influences FD metrics, e.g.
+for the freshwaterecology.info database ten feeding mode traits were combined to six traits.
+We calculated functional richness (FRic), functional evenness (FEve), and functional divergence (FDiv) following \citet{villegerNewMultidimensionalFunctional2008a} with the traits from \citet{szocs_effects_2014}, harmonised grouping features from the European trait dataset, and with family-level aggregated trait values.
+For FEve and FDiv invertebrate abundance data were used from \citet{szocs_effects_2014}.
+To account for temporal autocorrelation (sampling was done over a time period of three years) we regressed each FD metric with year and extracted the residuals.
+The residuals of the original study were compared with the residuals of the harmonised and aggregated datasets through regression for each FD metric.
+% R2!
 
@@
 \end{center}
+
+Calculating FD metrics for the original, harmonised (not aggregated), and aggregated datasets showed that the use of harmonised trait data results in similar FRic and FDiv values compared to the original dataset ($R2 = 0.96$ and $0.86$, respectively).
+Generally, aggregated trait data yielded lower, but moderate to good, correlations to the original for FRic and FDiv than the harmonised (Figure \ref{fig:FRic} and \ref{fig:FDiv}).
+By contrast, FEve calculated with harmonised and aggregated trait data seemed to substantially differ from the original dataset (all correlations below $< 0.1$), except for \textit{stepwise\_agg \textsubscript{median}}, which had an $R2$ of 0.48 (Figure \ref{fig:FEve}).
+
+% Evaluated by R2
 

### 2021-07-13 Paper/Submission_new/Latex_Supplementary_File.tex
13.07: Update revisions

@@
 \usepackage{lmodern}
+\usepackage[
+backend = biber,
+natbib,
+citestyle = authoryear,
+bibstyle = apa,
+maxcitenames = 2, 
+maxbibnames = 99, 
+uniquename=false,
+uniquelist=false
+%sorting = none % sort by name year title
+]{biblatex}
+\addbibresource{Ref_invertebrate_DB.bib}
 
@@
 \begin{landscape}
-    \begin{longtable}{m{1.9cm}|m{3.4cm}|m{3.3cm}|m{2.7cm}|m{3cm}|m{3.6cm}|m{2.5cm}}
-        \caption{Comparison of trait definitions between invertebrate trait databases.
+    \begin{longtable}{m{2cm}|m{3.25cm}|m{3.2cm}|m{3.1cm}|m{2.9cm}|m{3.4cm}|m{2.4cm}}
+        \caption{Comparison of trait definition differences between invertebrate trait databases.
 Only traits that are differently described across databases are listed.
 The definition is quoted if it enables differences to be identified, otherwise the differences are described.
+Bullet points indicate when several traits have been used to describe a morphological or behavioural property.
 The hyphen indicates a missing trait.
@@
         Feeding filter-feeder & 
-        Distinguishes between active and passive &
+        \begin{itemize}
+            \item Active filter feeders
+            \item Passive filter feeders
+        \end{itemize} &
         No distinction between active and passive &
@@
             \item 1-2 generations per year
-            \item bi/multivoltine
+            \item bi - or multivoltine
             \item up to 5 generations per year
@@
         Swimmer & 
-        Distinguishes swimmer and skater & 
+        \begin{itemize}
+            \item Swimmer
+            \item Skater
+        \end{itemize} & 
         Swimmers (water column)
@@
             \item Burrowing "within the first centimeters of the benthic fine sediment"
-            \item Differentiates also the trait interstitial (endobenthic)
+            \item Interstitial (endobenthic)
         \end{itemize} & 
@@
         - & 
-        Database contains traits crawler, 
-        sprawler, climber and clinger. &
+        \begin{itemize}
+            \item Crawler
+            \item Sprawler
+            \item Climber
+            \item Clinger
+        \end{itemize} &
         Crawlers (epibenthic) \\
@@
         Does not distinguish temporarily and permanently attached & 
-        Distinguishes temporarily and permanently attached & 
+        \begin{itemize}
+            \item Temporarily attached
+            \item Permanently attached
+        \end{itemize} & 
         Does not distinguish temporarily and permanently attached & 
         Does not distinguish temporarily and permanently attached & 
-        Distinguishes temporarily and permanently attached & 
+        \begin{itemize}
+            \item Temporarily attached
+            \item Permanently attached
+        \end{itemize} & 
         Does not distinguish temporarily and permanently attached \\
@@
         Plastron and spiracle combined into one trait & 
-        Distinguishes spiracular gills, plastron, atmospheric breathers and plant breathers &
-        Plastron and spiracle (termed aerial) occur as separate and combined traits. Contains also traits: air (plants), atmospheric, and functional spiracles &
-        Distinguishes plastron and spiracle (termed aerial) \\
+        \begin{itemize}
+            \item Spiracular gills
+            \item Plastron
+            \item Atmosph. breathers
+            \item Plant breathers
+        \end{itemize} &
+        \begin{itemize}
+            \item Plastron and spiracle (termed aerial) occur as separate and combined traits
+            \item Air (plants)
+            \item Atmospheric
+            \item Functional spiracles
+        \end{itemize} &
+        \begin{itemize}
+            \item Plastron
+            \item Spiracle (termed aerial)
+        \end{itemize} 
+        \\
         \toprule[.1em]
@@
 
+\paragraph*{Discussion: Comparison of aggregation methods with varying phylogenies and trait variability}
+\hfill
+\\
+
+We expected that, in addition to averaging measures, different weighting approaches to aggregation (i.e., equal weight to each taxon, equal weight to each genus, or weighted by number of species) would affect affinities for families with varying phylogenetic structure.
+However, we found through simulations that trait variability had a greater effect on the range of affinities (i.e., greater ranges of affinities at higher levels of variance) and on the differences in affinities between weighting approaches.
+In the simulation, taxonomic structural unevenness appeared to produce some variation in affinities among weighting approaches, especially for a family where one genus had a much larger number of species than its other genera.
+The comparison between aggregated and assigned traits showed, that the number of differing cases and the mean absolute differences in trait affinities, as well as the distributions of absolute trait affinity differences to assigned traits, were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weighting approach on the aggregation outcomes.
+The minor impact of the weighting approaches on trait aggregation might be explained by the fact that a considerable portion of taxa had low numbers of genera or species.
+Of the taxa that were compared from the North American trait dataset, 14 \% were identified at family and 62 \% at genus level, 52 \% comprised five or fewer genera, and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
+In the Australian dataset, 21 \% of the compared taxa were identified at family, 40 \% at genus, and 39 \% at species level, 68 \% of the taxa contained five or fewer genera, and 40 \% just one genus (Figure \ref{fig:tax_hierarchy_AUS}).
+Hence, these results could change when more species-level trait information becomes available.
+Our findings show that the choice of aggregation method may matter less when phylogenetic structure is fairly even and traits are less variable, but the \textit{stepwise\_agg\textsubscript{median}} method tended to produce the widest range in affinities, especially with high taxonomic unevenness and high trait variability.
+
 \subsubsection*{Taxonomic hierarchy in the trait datasets used for comparisons with assigned traits at family level}
@@
 
-\begin{figure}[ht]
+\begin{figure}[H]
     \centering
@@
 
+\subsubsection*{Fourth corner analysis}
+
+We selected the ecologically relevant traits identified by \citet{szocs_effects_2014} that increased (shredder, life cycle duration $ > 1 $ year, gills, bi/multivoltine, ovoviviparity) or decreased (univoltine, eggs in clutches/cemented or fixed, life cycle duration $ <= 1$ year) with increasing salinity and used these in the fourth corner analysis.
+The selected traits have also reacted to salinity in other studies (but see the discussion in \citet{szocs_effects_2014}).
+For some sites, environmental and abundance data have been sampled multiple times per year.
+\citet{szocs_effects_2014} used the full data and did not consider repeated sampling.
+We applied two analysis: one where we did not consider multiple samplings.
+And second where we selected, for the sites with multiple samplings, only those sampling events with the highest macroinvertebrate abundances per year and accordingly only used the conductivity data for these sampling events (this was not done for the RDA approach).Fourth corner analysis was carried out in R with the \textit{fourthcorner()} function from the ade4 package.
+With the fourth corner analysis fewer trait-conductivity relationships than with the RDA approach were detected.
+With the original dataset significant relationships to conductivity were found for the traits shredder and ovoviviparity.
+In three out of the six aggregated and harmonised datasets (\textit{direct\_agg\textsubscript{mean}}, \textit{weighted\_agg}, harmonised (not aggregated)) four to five significant relationships (for the traits shredder, univoltinism, bi/multivoltine, ovoviviparity, and aquatic oviposition) were detected.
+In the remaining three datasets (\textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{direct\_agg\textsubscript{median}}) two significant relationships for the traits univoltinism and bi/multivoltinism were detected.
+Results were only slightly different when not considering multiple samplings (original dataset: one significant trait-conductivity relationship, others three to four).
+For the significant trait-conductivity relationships, the classification into characteristic traits for downstream and upstream sites was consistent with the results of the RDA analysis.
+
+\subsection*{Effect of harmonisation and trait aggregation on functional diversity metrics}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=17cm, height=12cm]{Correlation_fd_metrics_FRic.png}
+    \caption{Fitted regressions between residuals of FRic with traits used in the original study and with harmonised and aggregated traits.
+Dots refer to each site-year combination.
+Sites have been sampled maximum three times in three years.
+For further details please refer to sections "Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships" and the original study.}
+    \label{fig:FRic}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=17cm, height=12cm]{Correlation_fd_metrics_FDiv.png}
+    \caption{Fitted regressions between residuals of FDiv with traits used in the original study and with harmonised and aggregated traits.
+Dots refer to each site-year combination site-year combination.
+Sites have been sampled maximum three times in three years.
+Some sites were sampled multiple times within a year.
+In that case the highest sampling event with the highest total invertebrate abundance was taken (this explains the discrepancy to the original study, that did not consider multiple samplings).
+For further details please refer to sections "Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships" and the original study.}
+    \label{fig:FDiv}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=17cm, height=12cm]{Correlation_fd_metrics_FEve.png}
+    \caption{Fitted regressions between residuals of FEve with traits used in the original study and with harmonised and aggregated traits.
+Dots refer to each site-year combination site-year combination.
+Sites have been sampled maximum three times in three years.
+Some sites were sampled multiple times within a year.
+In that case the highest sampling event with the highest total invertebrate abundance was taken (this explains the discrepancy to the original study, that did not consider multiple samplings).
+For further details please refer to sections "Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships" and the original study.}
+    \label{fig:FEve}
+\end{figure}
+
 \end{document}

### 2021-07-13 Paper/Submission_new/Main_Document-Latex.tex
13.07: Update revisions

--- 2021-06-28 Paper/Submission_new/Main_Document-Latex.tex
@@
 Invertebrate traits have been increasingly used in freshwater ecology, e.g.
-by relating macroinvertebrate trait composition to environmental factors such as climate change or salinisation (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}), for predicting changes in ecosystem functioning and trophic dynamics (\cite{vos_taxonomic_2017, gutierrez-canovasPopulationsHighvaluePredators2021}), or for developing indices for biomonitoring (\cite{beketov_spear_2009}).
+by relating macroinvertebrate trait composition to environmental factors such as climate change or salinisation (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}), for predicting changes in ecosystem functioning and trophic dynamics (\cite{vos_taxonomic_2017, gutierrez-canovasPopulationsHighvaluePredators2021}), or for developing indices for biomonitoring (\cite{doledecInvertebrateTraitsBiomonitoring2008a, beketov_spear_2009}), but see also \citet{hamiltonLimitationsTraitbasedApproaches2020} for a critical perspective.
 In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases, which typically include data for a single region or continent (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate, gayraudInvertebrateTraitsBiomonitoring2003, statznerConservationTaxonomicBiological2007}).
 The availability of invertebrate trait data from different continents enables comparisons of regional trait variation and allows for testing the consistency of trait structure–environmental factor relationships across both small and large spatial extents.
+% Traits provide adaptations to the environmental variability of a habitat which may explain species distributions and early work focused on the link between habitat utilization and traits which lead to one of the first collections of trait information on aquatic invertebrates
+% See theoretical habitat templets (Polatera & Tachet 1994)
+
 To date, such analyses have been carried out mostly within continents, using information from one or two trait databases.
@@
 feeding mode) refers to a set of related traits (e.g.
-predator, shredder, etc.) that together define an ecological property that is shared among individuals or species.
+predator, shredder, etc.) that together define a general property (e.g.
+respiration) that is shared among individuals or species.
 Thus, to use consistent terminology in this study, we use the term grouping feature in place of the term trait, and the term trait instead of trait state, modality or trait category.
@@
 Ideally, the same traits and grouping features would be reported across databases or standardised terminology would exist to easily harmonise them; however, standardised terminology of trait definitions is lacking and poor metadata quality in many trait databases make harmonisation of grouping features difficult (\cite{baird_toward_2011, kissling_towards_2018}).
-To our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on the functional diversity of invertebrate assemblages.
+\citet{maasriGlobalUnifiedTrait2019} advocated for a globally harmonised invertebrate trait database, but to our knowledge, only \citet{brown_functional_2018} harmonised grouping features from more than two geographically distant invertebrate trait databases, for a limited set of grouping features (8) and taxa (112), in a study on the influence of decreasing glacier cover on the functional diversity of invertebrate assemblages.
 
@@
 
-Finally, discrepancies in the taxonomic resolutions (e.g., species, genus, or family) used when comparing among trait databases, or when linking observed taxonomic data to trait databases, presents another challenge.
-When taxonomic composition or data in on trait database are at a more precise taxonomic level than other trait data (e.g.
+Finally, discrepancies in the taxonomic resolutions (e.g., species, genus, or family) used when comparing among trait databases, or when linking observed taxonomic data to trait databases, presents another challenge (\cite{gayraudInvertebrateTraitsBiomonitoring2003, doledecAccurateDescriptionAbundance2000}).
+When taxonomic composition or data in a trait database are at a more precise taxonomic level than other trait data (e.g.
 observations at species-level and trait data at genus-level) trait information of the less precise taxonomic level is often assigned (e.g.
@@
 We established four datasets, one for each of the four geographic regions, by harmonising the traits of seven grouping features from the trait databases.
-We selected traits that are commonly applied in trait-based ecological studies and describe different aspects of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
-The selected traits also relate to how taxa cope with disturbances (e.g.
-reproduction traits like ovoviviparity or number of life cycles) and to ecosystem functions such as organic matter breakdown and nutrient cycling (e.g.
-trait shredder).
+We selected grouping feautres that are commonly applied in trait-based ecological studies and describe different aspects of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode), and reproduction (Oviposition).
 A criterion for trait selection was that the traits occurred in all databases, to enable us to show trait definitions differences and the influence of grouping-feature harmonisation on trait-environment relationships.
-Thus, we omitted ecological traits that describe habitat preferences (e.g.
+Thus, we only used biological traits and omitted ecological traits that describe habitat preferences (e.g.
 temperature preference) because these traits are missing in the New Zealand trait database.
-% OLD:
-% We selected traits that were available in all databases, are commonly applied in trait-based ecological studies, and describe different aspects of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode) and reproduction (Oviposition).
+Also, traits from the selected grouping features may consistently respond to certain environmental stressors across large scales and thus be suitable for intercontinental comparisons of trait-environment relationships.
+For example, traits like body size small, multiple life cycles per year, or swimming are related to resilience and resistance to flow disturbances or retreating glacier cover and may consistently respond to certain environmental stressors across regions (\cite{bonada_taxonomic_2007, brown_functional_2018}).
 
@@
 The simulation showed that both phylogenetic structure and trait variability can affect aggregated trait affinities, but mostly only to a small degree.
-As expected, the range of trait affinities increasing trait variability for all trait aggregation methods.
+As expected, the range of trait affinities increased with higher trait variability for all trait aggregation methods.
 Therefore, we provide details of the simulation and the results in the supplementary materials.
@@
 
-We re-analysed the \citet{szocs_effects_2014} data by performing a RDA with harmonised grouping features from the dataset for Europe and with traits that we aggregated to family level with the five aggregation methods described above.
+We re-analysed the \citet{szocs_effects_2014} data by performing a RDA with a mixture of harmonised grouping features from the dataset for Europe and non-harmonised grouping features, and with traits that we aggregated to family level with the five aggregation methods described above.
 We used all 21 grouping features from the original study, but replaced 6 with harmonised grouping features from the established European trait dataset, namely size, feeding mode, locomotion, oviposition, respiration, and voltinism.
@@
 Additionally, to test for the effect of different aggregation methods on inferences about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
-% Add change in functional diversity
+We used the RDA approach for consistency with \citet{szocs_effects_2014} but are aware of the criticism that regressing CWM traits against environmental gradients has received (but see \cite{peres-netoLinkingTraitVariation2017, millerFunctionalTraitsCommunity2019}).
+% because CWM trait values are treated as independent while they in fact are non-independent which can lead to inflated Type 1 errors
+
+Finally, we assessed how functional diversity (FD) changed when harmonised and aggregated trait data are used.
+Harmonisation of grouping features reduces the number of traits per grouping feature, e.g.
+for the freshwaterecology.info database ten feeding mode traits were combined to six traits, and thus likely influences FD metrics.
+We calculated functional richness (FRic), functional evenness (FEve), and functional divergence (FDiv) following \citet{villegerNewMultidimensionalFunctional2008a} with the traits from \citet{szocs_effects_2014}, harmonised grouping features from the European trait dataset, and with family-level aggregated trait values.
+For FEve and FDiv invertebrate abundance data were used from \citet{szocs_effects_2014}.
+To account for temporal autocorrelation (sampling was done over a time period of three years) we regressed each FD metric with year and extracted the residuals.
+The residuals of the original study were compared with the residuals of the harmonised and aggregated datasets through regression and evaluation of the coefficient of determination ($R^2$).
 
@@
 
-The number of entries with available information for the selected grouping features varied strongly across the established European, North American, and Australian datasets (Table \ref{tab:trait_coverage}).
-In contrast, the New Zealand dataset contained complete trait information for most of the investigated grouping features (between 94 \% and 100 \%).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The definitions of grouping features also varied across databases in their differentiation into traits and in their focus, both which can lead to discrepancies in trait definitions (see Table \ref{tab:trait_definitions} and Table \ref{stab:trait_definitions} for a summary of discrepancies in trait definitions).
-Varying levels of differentiation among the trait databases were present in all investigated grouping features (Table \ref{tab:trait_databases_coding_differentiation}, Table \ref{tab:trait_definitions}, and Table \ref{stab:trait_definitions}).
+Varying levels of differentiation among the trait databases were present in all investigated grouping features (Table \ref{tab:trait_definitions}, Table \ref{tab:trait_databases_coding_differentiation}, and Table \ref{stab:trait_definitions}).
 
@@
 Our re-analysis of the \citet{szocs_effects_2014} study on the effects of salinisation on invertebrate traits showed that the use of harmonised and aggregated trait data may be useful for ecological studies on trait–environment relationships.
-Overall, harmonised trait data and all aggregation methods produced similar distributions of RDA species scores (\ref{fig:violin_plot_species_sc}) compared with the original analysis, and they resulted in similar, but fewer, traits that distinguished upstream and downstream sites than the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
+Overall, harmonised trait data and all aggregation methods produced similar distributions of RDA species scores (Figure \ref{fig:violin_plot_species_sc}) compared with the original analysis, and they resulted in similar, but fewer, traits that distinguished upstream and downstream sites than the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
 
@@
 Thus, compared with the original study’s findings, aggregating by the direct and weighted methods yielded less change than the stepwise methods in interpretation of the RDA results.
+To demonstrate a different approach to detecting relationships between traits and conductivity we used fourth corner analysis with the original, harmonised, and aggregated trait datasets (methods and results in  ).
 
@@
 \end{center}
+
+The calculation of FD metrics for the original, harmonised (not aggregated), and aggregated datasets suggested that harmonising trait data preserves FRic and FDiv values, while aggregated trait data only preserved FRic values.
+The FRic and FDiv values calculated from harmonised trait data correlated highly to FRic and FDiv values from the original dataset ($R^2 = 0.96$ and $0.86$, respectively).
+FRic and FDiv calculated for aggregated trait data showed moderate to good correlations to the FRic and FDiv values calculated with the original dataset (FRic: $0.78 <= R^2 <= 0.85$ , FDiv: $0.47 <= R^2 <= 0.55$, Figure \ref{fig:FRic} and \ref{fig:FDiv}).
+By contrast, FEve values calculated with harmonised and aggregated trait data were unrelated to the FEve values calculated with the original dataset (all $R^2 < 0.1$), except for \textit{stepwise\_agg \textsubscript{median}}, which showed a moderate correlation to FEve values calculated from the original dataset ($R^2  = 0.48$, Figure \ref{fig:FEve}).
 
@@
 Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait is for a particular family.
-Aggregation of trait information at the species or genus level to a single estimate at the family level implies a precision that is not necessarily present, especially not for traits with high variability or if trait information at species level is missing.
+Aggregation of trait values always represents a loss of information.
+Especially for traits with high variability or if trait information at species level is missing, a single aggregated family-level trait value implies a precision that is not necessarily present.
 Indeed, some traits can vary strongly at more resolved taxonomic levels than the family level.
@@
 
-We expected that, in addition to averaging measures, different weighting approaches to aggregation (i.e., equal weight to each taxon, equal weight to each genus, or weighted by number of species) would affect affinities for families with varying phylogenetic structure.
-However, we found through simulations that trait variability had a greater effect on the range of affinities (i.e., greater ranges of affinities at higher levels of variance) and on the differences in affinities between weighting approaches.
-In the simulation, taxonomic structural unevenness appeared to produce some variation in affinities among weighting approaches, especially for a family where one genus had a much larger number of species than its other genera.
-The comparison between aggregated and assigned traits showed, that the number of differing cases and the mean absolute differences in trait affinities, as well as the distributions of absolute trait affinity differences to assigned traits, were similar across the mean aggregation and across the median aggregation methods, which suggests a small influence of the weighting approach on the aggregation outcomes.
-The minor impact of the weighting approaches on trait aggregation might be explained by the fact that a considerable portion of taxa had low numbers of genera or species.
-Of the taxa that were compared from the North American trait dataset, 14 \% were identified at family and 62 \% at genus level, 52 \% comprised five or fewer genera, and 13 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}).
-In the Australian dataset, 21 \% of the compared taxa were identified at family, 40 \% at genus, and 39 \% at species level, 68 \% of the taxa contained five or fewer genera, and 40 \% just one genus (Figure \ref{fig:tax_hierarchy_AUS}).
-Hence, these results could change when more species-level trait information becomes available.
-Our findings show that the choice of aggregation method may matter less when phylogenetic structure is fairly even and traits are less variable, but the \textit{stepwise\_agg\textsubscript{median}} method tended to produce the widest range in affinities, especially with high taxonomic unevenness and high trait variability.
-
 \subsection*{Using harmonised and aggregated datasets for ecological research}
@@
 However, our results also illustrate that where site-level data are not available, harmonised and aggregated datasets may be useful in identifying at least the strongest associations between traits and environmental conditions.
+
+FD analysis is an important trait-based application to quantify the variability of traits that influence ecosystem functions.
+We found through correlation that harmonised trait data may be used to calculate FRic and FDiv values, and that aggregated trait data can at least be used to calculate FRic values.
+This does not apply to FEve, as the use of harmonised and aggregated trait data yielded completely different FEve values than with the trait data from \citet{szocs_effects_2014}.
+FRic represents the trait space spanned by the community (also termed the convex hull volume) and is only dependent on the trait data used.
+Our results show that harmonisation preserves the trait space the best, i.e.
+the most extreme trait values of the original study, and that aggregation only slightly changes the trait space.
+It follows that FDiv, which describes how abundances are distributed within the volume of the trait space, is best preserved by harmonised trait data preserved and to a lesser extent with aggregated trait data.
+FEve describes how regular the trait space is filled by taxa.
+We found that harmonised and aggregated trait change the evenness of the abundance distribution in the trait space, which is likely because during the calculation of FEve only the nearest neighbours in the trait space are considered.
+This leads to the undesirable property that even small community changes result in large changes in the FEve index, a behaviour that has been shown by \citet{botta-dukatTestingAbilityFunctional2016} through simulation.
 
@@
   \begin{longtable}{m{2.0cm}|m{4.0cm}|m{4.2cm}|m{4.2cm}|m{1.7cm}|m{2cm}|m{2.2cm}}
-      \caption{Excerpt of the comparison of trait definitions between invertebrate trait databases for the traits predator and swimming.
+      \caption{Excerpt of the comparison of trait definition differences between invertebrate trait databases for the traits predator and swimming.
 The definition is quoted if it enables differences to be identified, otherwise the differences are described.
+Bullet points indicate when several traits have been used to describe a morphological or behavioural property.
 The full version and further information can be found in the supporting information Table \ref{stab:trait_definitions}.}

### 2021-07-14 Paper/Submission_new/Latex_Supplementary_File.tex
14.07: Revisions change in harm. first part

@@
 The selected traits have also reacted to salinity in other studies (but see the discussion in \citet{szocs_effects_2014}).
+
 For some sites, environmental and abundance data have been sampled multiple times per year.
@@
 And second where we selected, for the sites with multiple samplings, only those sampling events with the highest macroinvertebrate abundances per year and accordingly only used the conductivity data for these sampling events (this was not done for the RDA approach).Fourth corner analysis was carried out in R with the \textit{fourthcorner()} function from the ade4 package.
-With the fourth corner analysis fewer trait-conductivity relationships than with the RDA approach were detected.
+
+Fourth corner analysis detected fewer trait-conductivity relationships than the RDA approach.
 With the original dataset significant relationships to conductivity were found for the traits shredder and ovoviviparity.
-In three out of the six aggregated and harmonised datasets (\textit{direct\_agg\textsubscript{mean}}, \textit{weighted\_agg}, harmonised (not aggregated)) four to five significant relationships (for the traits shredder, univoltinism, bi/multivoltine, ovoviviparity, and aquatic oviposition) were detected.
-In the remaining three datasets (\textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{direct\_agg\textsubscript{median}}) two significant relationships for the traits univoltinism and bi/multivoltinism were detected.
-Results were only slightly different when not considering multiple samplings (original dataset: one significant trait-conductivity relationship, others three to four).
-For the significant trait-conductivity relationships, the classification into characteristic traits for downstream and upstream sites was consistent with the results of the RDA analysis.
+In three out of the six aggregated and harmonised datasets (\textit{direct\_agg\textsubscript{mean}}, \textit{weighted\_agg}, \textit{direct\_agg\textsubscript{median}}) four significant relationships (for the traits univoltinism, bi/multivoltine, ovoviviparity, and aquatic oviposition) were detected.
+In the remaining three datasets (\textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and harmonised (not aggregated)) two significant relationships for the traits univoltinism and bi/multivoltinism were detected (Table \ref{stab:fc_selected_reduced}).
+Results were only slightly different when not considering multiple samplings (original dataset: two significant trait-conductivity relationship (bi-multivoltine, ovoviviparity), other datasets two to four, Table \ref{stab:fc_selected_full}).
+For all significant trait-conductivity relationships, the classification into characteristic traits for downstream and upstream sites was consistent with the results of the RDA analysis.
+
+\begin{longtable}[H]{m{2.6cm}|m{7.3cm}|m{1cm}|m{1.4cm}|m{1.5cm}|m{1.5cm}}
+    \caption{Results of the fourth corner analysis, after accounting for multiple samplings per year, with the original dataset, harmonised, and aggregated trait datasets.}
+    \label{stab:fc_selected_reduced}
+    \endfirsthead
+    \toprule[.1em]
+    Dataset & Test & Obs & Std.Obs & Pvalue & Pvalue.adj \\ 
+    \toprule[.1em]
+       stepw\_median & cond / feed\_shredder & 0.45 & 1.86  & 0.04 & 0.16 \\ 
+       stepw\_median & cond / resp\_gil & 0.47 & 1.87  & 0.05 & 0.16 \\ 
+       stepw\_median & cond / volt\_uni & -0.57 & -2.29  & 0.00 & 0.03 \\ 
+       stepw\_median & cond / volt\_bi\_multi & 0.58 & 2.35  & 0.00 & 0.02 \\ 
+       stepw\_median & cond / ovip\_aqu & -0.53 & -2.14  & 0.01 & 0.06 \\ 
+       stepw\_median & cond / ovip\_ovo & 0.54 & 2.15  & 0.01 & 0.06 \\ 
+       stepw\_median & cond / Life cycle duration $<=$ 1 year & -0.32 & -1.27  & 0.24 & 0.49 \\ 
+       stepw\_median & cond / Life cycle duration $>$ 1 year & 0.32 & 1.27  & 0.24 & 0.49 \\ 
+       stepw\_mean & cond / feed\_shredder & 0.46 & 1.96  & 0.03 & 0.11 \\ 
+       stepw\_mean & cond / resp\_gil & 0.47 & 1.75  & 0.06 & 0.18 \\ 
+       stepw\_mean & cond / volt\_uni & -0.58 & -2.45  & 0.01 & 0.04 \\ 
+       stepw\_mean & cond / volt\_bi\_multi & 0.59 & 2.50  & 0.00 & 0.03 \\ 
+       stepw\_mean & cond / ovip\_aqu & -0.52 & -2.23  & 0.01 & 0.06 \\ 
+       stepw\_mean & cond / ovip\_ovo & 0.52 & 2.23  & 0.01 & 0.06 \\ 
+       stepw\_mean & cond / Life cycle duration $<=$ 1 year & -0.33 & -1.30  & 0.23 & 0.47 \\ 
+       stepw\_mean & cond / Life cycle duration $>$ 1 year & 0.33 & 1.30  & 0.23 & 0.47 \\ 
+       direct\_median & cond / feed\_shredder & 0.45 & 1.89  & 0.04 & 0.15 \\ 
+       direct\_median & cond / resp\_gil & 0.47 & 1.88  & 0.04 & 0.15 \\ 
+       direct\_median & cond / volt\_uni & -0.58 & -2.24  & 0.00 & 0.02 \\ 
+       direct\_median & cond / volt\_bi\_multi & 0.58 & 2.33  & 0.00 & 0.02 \\ 
+       direct\_median & cond / ovip\_aqu & -0.53 & -2.14  & 0.01 & 0.05 \\ 
+       direct\_median & cond / ovip\_ovo & 0.54 & 2.15  & 0.01 & 0.05 \\ 
+       direct\_median & cond / Life cycle duration $<=$ 1 year & -0.34 & -1.35  & 0.21 & 0.43 \\ 
+       direct\_median & cond / Life cycle duration $>$ 1 year & 0.34 & 1.35  & 0.21 & 0.43 \\ 
+       direct\_mean & cond / feed\_shredder & 0.46 & 1.83  & 0.05 & 0.19 \\ 
+       direct\_mean & cond / resp\_gil & 0.47 & 1.82  & 0.05 & 0.19 \\ 
+       direct\_mean & cond / volt\_uni & -0.58 & -2.49  & 0.00 & 0.02 \\ 
+       direct\_mean & cond / volt\_bi\_multi & 0.59 & 2.54  & 0.00 & 0.02 \\ 
+       direct\_mean & cond / ovip\_aqu & -0.52 & -2.26  & 0.01 & 0.05 \\ 
+       direct\_mean & cond / ovip\_ovo & 0.52 & 2.43  & 0.01 & 0.05 \\ 
+       direct\_mean & cond / Life cycle duration $<=$ 1 year & -0.34 & -1.37  & 0.18 & 0.37 \\ 
+       direct\_mean & cond / Life cycle duration $>$ 1 year & 0.34 & 1.37  & 0.18 & 0.37 \\ 
+       weighted & cond / feed\_shredder & 0.46 & 1.97  & 0.03 & 0.11 \\ 
+       weighted & cond / resp\_gil & 0.47 & 1.92  & 0.04 & 0.11 \\ 
+       weighted & cond / volt\_uni & -0.58 & -2.51  & 0.00 & 0.02 \\ 
+       weighted & cond / volt\_bi\_multi & 0.59 & 2.56  & 0.00 & 0.02 \\ 
+       weighted & cond / ovip\_aqu & -0.52 & -2.13  & 0.01 & 0.04 \\ 
+       weighted & cond / ovip\_ovo & 0.52 & 2.35  & 0.01 & 0.04 \\ 
+       weighted & cond / Life cycle duration $<=$ 1 year & -0.34 & -1.38  & 0.20 & 0.41 \\ 
+       weighted & cond / Life cycle duration $>$ 1 year & 0.34 & 1.38  & 0.20 & 0.41 \\ 
+       not\_aggregated & cond / feed\_shredder & 0.51 & 2.08  & 0.01 & 0.08 \\ 
+       not\_aggregated & cond / resp\_gil & 0.46 & 1.72  & 0.08 & 0.40 \\ 
+       not\_aggregated & cond / volt\_uni & -0.64 & -2.76  & 0.00 & 0.02 \\ 
+       not\_aggregated & cond / volt\_bi\_multi & 0.65 & 2.81  & 0.00 & 0.02 \\ 
+       not\_aggregated & cond / ovip\_aqu & -0.26 & -1.22  & 0.27 & 0.80 \\ 
+       not\_aggregated & cond / ovip\_ovo & 0.27 & 1.39  & 0.20 & 0.80 \\ 
+       not\_aggregated & cond / Life cycle duration $<=$ 1 year & -0.33 & -1.26   & 0.24 & 0.80 \\ 
+       not\_aggregated & cond / Life cycle duration $>$ 1 year & 0.33 & 1.26  & 0.24 & 0.80 \\ 
+       original & cond / Life cycle duration $<=$ 1 year & -0.33 & -1.31  & 0.22 & 0.65 \\ 
+       original & cond / Life cycle duration $>$ 1 year & 0.33 & 1.31  & 0.22 & 0.65 \\ 
+       original & cond / Potential number of cycles per year $1$ & -0.48 & -1.91  & 0.04 & 0.18 \\ 
+       original & cond / Potential number of cycles per year $> 1$  & 0.49 & 1.95  & 0.03 & 0.16 \\ 
+       original & cond / Reproduction ovoviviparity & 0.58 & 2.43  & 0.01 & 0.04 \\ 
+       original & cond / Reproduction clutches, cemented or fixed & -0.33 & -1.27  & 0.24 & 0.65 \\ 
+       original & cond / Respiration gill & 0.47 & 1.87  & 0.04 & 0.18 \\ 
+       original & cond / Feeding habits shredder & 0.54 & 2.51  & 0.01 & 0.04 \\ 
+      \bottomrule
+\end{longtable}
+
+\begin{longtable}[H]{m{2.6cm}|m{7.3cm}|m{1cm}|m{1.4cm}|m{1.5cm}|m{1.5cm}}
+    \caption{Results of the fourth corner analysis without accounting for multiple samplings per year, with the original dataset, harmonised, and aggregated trait datasets.}
+    \label{stab:fc_selected_full}
+    \endfirsthead
+    \toprule[.1em]
+    Dataset & Test & Obs & Std.Obs & Pvalue & Pvalue.adj \\ 
+    \toprule[.1em]
+    stepw\_median & cond / feed\_shredder & 0.38 & 1.86 & 0.05 & 0.19 \\ 
+      stepw\_median & cond / resp\_gil & 0.38 & 1.80 & 0.06 & 0.19 \\ 
+      stepw\_median & cond / volt\_uni & -0.54 & -2.43 & 0.00 & 0.03 \\ 
+      stepw\_median & cond / volt\_bi\_multi & 0.54 & 2.50 & 0.00 & 0.02 \\ 
+      stepw\_median & cond / ovip\_aqu & -0.46 & -2.34 & 0.01 & 0.04 \\ 
+      stepw\_median & cond / ovip\_ovo & 0.46 & 2.57 & 0.01 & 0.04 \\ 
+      stepw\_median & cond / Life cycle duration $<=$ 1 year & -0.28 & -1.29 & 0.22 & 0.45 \\ 
+      stepw\_median & cond / Life cycle duration $>$ 1 year & 0.28 & 1.29 & 0.22 & 0.45 \\ 
+      stepw\_mean & cond / feed\_shredder & 0.39 & 1.93 & 0.03 & 0.12 \\ 
+      stepw\_mean & cond / resp\_gil & 0.39 & 1.81 & 0.06 & 0.17 \\ 
+      stepw\_mean & cond / volt\_uni & -0.54 & -3.65 & 0.00 & 0.01 \\ 
+      stepw\_mean & cond / volt\_bi\_multi & 0.55 & 3.71 & 0.00 & 0.01 \\ 
+      stepw\_mean & cond / ovip\_aqu & -0.44 & -2.26 & 0.01 & 0.05 \\ 
+      stepw\_mean & cond / ovip\_ovo & 0.45 & 2.50 & 0.00 & 0.02 \\ 
+      stepw\_mean & cond / Life cycle duration $<=$ 1 year & -0.28 & -1.34 & 0.20 & 0.39 \\ 
+      stepw\_mean & cond / Life cycle duration $>$ 1 year & 0.28 & 1.34 & 0.20 & 0.39 \\ 
+      direct\_median & cond / feed\_shredder & 0.37 & 1.89 & 0.03 & 0.13 \\ 
+      direct\_median & cond / resp\_gil & 0.38 & 1.82 & 0.05 & 0.16 \\ 
+      direct\_median & cond / volt\_uni & -0.54 & -3.79 & 0.00 & 0.01 \\ 
+      direct\_median & cond / volt\_bi\_multi & 0.55 & 3.85 & 0.00 & 0.01 \\ 
+      direct\_median & cond / ovip\_aqu & -0.46 & -2.37 & 0.01 & 0.05 \\ 
+      direct\_median & cond / ovip\_ovo & 0.46 & 2.56 & 0.01 & 0.05 \\ 
+      direct\_median & cond / Life cycle duration $<=$ 1 year & -0.30 & -1.41 & 0.18 & 0.35 \\ 
+      direct\_median & cond / Life cycle duration $>$ 1 year & 0.30 & 1.41 & 0.18 & 0.35 \\ 
+      direct\_mean & cond / feed\_shredder & 0.39 & 1.94 & 0.03 & 0.11 \\ 
+      direct\_mean & cond / resp\_gil & 0.38 & 1.79 & 0.06 & 0.17 \\ 
+      direct\_mean & cond / volt\_uni & -0.55 & -3.54 & 0.00 & 0.01 \\ 
+      direct\_mean & cond / volt\_bi\_multi & 0.55 & 3.60 & 0.00 & 0.01 \\ 
+      direct\_mean & cond / ovip\_aqu & -0.44 & -2.25 & 0.01 & 0.03 \\ 
+      direct\_mean & cond / ovip\_ovo & 0.45 & 2.52 & 0.00 & 0.02 \\ 
+      direct\_mean & cond / Life cycle duration $<=$ 1 year & -0.30 & -1.49 & 0.15 & 0.30 \\ 
+      direct\_mean & cond / Life cycle duration $>$ 1 year & 0.30 & 1.49 & 0.15 & 0.30 \\ 
+      weighted & cond / feed\_shredder & 0.39 & 1.84 & 0.05 & 0.19 \\ 
+      weighted & cond / resp\_gil & 0.38 & 1.81 & 0.06 & 0.19 \\ 
+      weighted & cond / volt\_uni & -0.55 & -3.43 & 0.00 & 0.01 \\ 
+      weighted & cond / volt\_bi\_multi & 0.55 & 3.49 & 0.00 & 0.01 \\ 
+      weighted & cond / ovip\_aqu & -0.44 & -2.24 & 0.01 & 0.05 \\ 
+      weighted & cond / ovip\_ovo & 0.45 & 2.44 & 0.01 & 0.05 \\ 
+      weighted & cond / Life cycle duration $<=$ 1 year & -0.30 & -1.42 & 0.17 & 0.34 \\ 
+      weighted & cond / Life cycle duration $>$ 1 year & 0.30 & 1.42 & 0.17 & 0.34 \\ 
+      not\_aggregated & cond / feed\_shredder & 0.43 & 2.07 & 0.01 & 0.09 \\ 
+      not\_aggregated & cond / resp\_gil & 0.38 & 1.77 & 0.06 & 0.30 \\ 
+      not\_aggregated & cond / volt\_uni & -0.57 & -3.90 & 0.00 & 0.01 \\ 
+      not\_aggregated & cond / volt\_bi\_multi & 0.58 & 3.96 & 0.00 & 0.01 \\ 
+      not\_aggregated & cond / ovip\_aqu & -0.25 & -1.28 & 0.22 & 0.62 \\ 
+      not\_aggregated & cond / ovip\_ovo & 0.25 & 1.50 & 0.15 & 0.62 \\ 
+      not\_aggregated & cond / Life cycle duration $<=$ 1 year & -0.29 & -1.37 & 0.18 & 0.62 \\ 
+      not\_aggregated & cond / Life cycle duration $>$ 1 year & 0.29 & 1.37 & 0.18 & 0.62 \\ 
+      original & cond / Life cycle duration $<=$ 1 year & -0.29 & -1.42 & 0.17 & 0.50 \\ 
+      original & cond / Life cycle duration $>$ 1 year & 0.29 & 1.42 & 0.17 & 0.50 \\ 
+      original & cond / Potential number of cycles per year $1$ & -0.47 & -2.11 & 0.02 & 0.10 \\ 
+      original & cond / Potential number of cycles per year $> 1$ 1 & 0.47 & 2.19 & 0.01 & 0.05 \\ 
+      original & cond / Reproduction ovoviviparity & 0.51 & 3.06 & 0.00 & 0.01 \\ 
+      original & cond / Reproduction clutches, cemented or fixed & -0.34 & -1.49 & 0.17 & 0.50 \\ 
+      original & cond / Respiration gill & 0.38 & 1.80 & 0.06 & 0.25 \\ 
+      original & cond / Feeding habits shredder & 0.45 & 2.19 & 0.01 & 0.06 \\ 
+     \bottomrule
+\end{longtable}
+
+\newpage
 

### 2021-07-14 Paper/Submission_new/Main_Document-Latex.tex
14.07: Revisions change in harm. first part

@@
 The FRic and FDiv values calculated from harmonised trait data correlated highly to FRic and FDiv values from the original dataset ($R^2 = 0.96$ and $0.86$, respectively).
-FRic and FDiv calculated for aggregated trait data showed moderate to good correlations to the FRic and FDiv values calculated with the original dataset (FRic: $0.78 <= R^2 <= 0.85$ , FDiv: $0.47 <= R^2 <= 0.55$, Figure \ref{fig:FRic} and \ref{fig:FDiv}).
+FRic and FDiv calculated for aggregated trait data showed moderate to good correlations to the FRic and FDiv values calculated with the original dataset (FRic: $0.78 <= R^2 <= 0.84$ , FDiv: $0.42 <= R^2 <= 0.62$, Figure \ref{fig:FRic} and \ref{fig:FDiv}).
 By contrast, FEve values calculated with harmonised and aggregated trait data were unrelated to the FEve values calculated with the original dataset (all $R^2 < 0.1$), except for \textit{stepwise\_agg \textsubscript{median}}, which showed a moderate correlation to FEve values calculated from the original dataset ($R^2  = 0.48$, Figure \ref{fig:FEve}).
@@
 the most extreme trait values of the original study, and that aggregation only slightly changes the trait space.
-It follows that FDiv, which describes how abundances are distributed within the volume of the trait space, is best preserved by harmonised trait data preserved and to a lesser extent with aggregated trait data.
+It follows that FDiv, which describes how abundances are distributed within the volume of the trait space, is best preserved by harmonised trait data and to a lesser extent with aggregated trait data.
 FEve describes how regular the trait space is filled by taxa.

### 2021-07-15 R/01_AUS_preprocessing.R
15.07: Changed harmonisation to sum

@@ -5,18 +5,21 @@
 
 # load raw Trait database
 Trait_AUS <-
-  fread(file.path(data_in,
-                  "Australia",
-                  "Australian_macroinv_trait_database_final.csv"))
+  fread(file.path(
+    data_in,
+    "Australia",
+    "Australian_macroinv_trait_database_final.csv"
+  ))
 
 # delete entries with "Adult"
-Trait_AUS <- Trait_AUS[!grepl("(?i)Adult", Species), ]
+Trait_AUS <- Trait_AUS[!grepl("(?i)Adult", Species),]
 
 # remove reference columns
 Trait_AUS[, grep("(?i)ref.+", names(Trait_AUS), value = TRUE) := NULL]
 
 # subset with comments
-Comments_AUS <- Trait_AUS[, .SD, .SDcols = names(Trait_AUS) %like% "Comment|unique_ID"]
+Comments_AUS <-
+  Trait_AUS[, .SD, .SDcols = names(Trait_AUS) %like% "Comment|unique_ID"]
 Trait_AUS[, grep("(?i)comment.+", names(Trait_AUS), value = TRUE) := NULL]
 
 # feeding mode: adjust col names Marchant
@@ -26,7 +29,7 @@ setnames(
   new = paste0("feeding_", grep("Marchant", names(Trait_AUS), value = TRUE))
 )
 
-# Change names for Maxwell 
+# Change names for Maxwell
 # Botwe for feeding mode
 setnames(
   Trait_AUS,
@@ -127,10 +130,10 @@ Trait_AUS <- Trait_AUS[, c(
 , with = FALSE]
 
 # ________________________________________________________________________
-#### Trait preprocessing categorical traits #### 
+#### Trait preprocessing categorical traits ####
 # Trait_AUS[, lapply(.SD, max, na.rm =TRUE),
 #           .SDcols = -c("unique_id", "Species", "Genus", "Family", "Order")]
-# Each trait category is transformed into a column with an indication 
+# Each trait category is transformed into a column with an indication
 # of present or not present (one or zero/ 100 % or 0 %)
 # ________________________________________________________________________
 
@@ -140,7 +143,7 @@ Trait_AUS <- Trait_AUS[, c(
 # resp_gil: gills
 # resp_spi: spiracle
 # resp_pls: plastron
-# resp_atm: atmospheric breathers 
[…]

### 2021-07-15 R/01_EU_preprocess_new.R

@@ -106,7 +106,7 @@ cols_fuzzy <- grep("(?=volt.*|resp.*|species|genus|family|order|taxon.*|ID.*)(?!
 # trait_EU <- trait_EU[!(taxon_cp %in% rm_dupl), ]
 
 
-# aggr. duplicated families
+# combine duplicated families
 dupl_families <- trait_EU[is.na(species) & is.na(genus) & !is.na(family), ] %>%
   .[duplicated(family) | duplicated(family, fromLast = TRUE), family] %>%
   .[!duplicated(.)]

### 2021-07-15 R/02_AUS_harmonize_traits.R

@@ -19,25 +19,42 @@ Trait_AUS <- readRDS(
 # volt_uni
 # volt_bi_multi
 # _________________________________________________________________________ 
-Trait_AUS[, volt_semi := apply(.SD, 1, max),
+Trait_AUS[, volt_semi := apply(.SD, 1, max, na.rm = TRUE),
           .SDcols = c("Voltinism_less_than_1_VicEPA",
                       "Volt1_botwe",
                       "volt1_Maxwell",
                       "Less_than_one_generation_per_year_Schaefer",
                       "Less_than_one_generation_per_year_bugs_gbr")]
-Trait_AUS[, volt_uni := apply(.SD, 1, max),
+Trait_AUS[, volt_uni := apply(.SD, 1, max, na.rm = TRUE),
           .SDcols = c("Voltinism_1_VicEPA",
                       "Volt2_botwe",
                       "One_generation_per_year_bugs_gbr", 
                       "One_generation_per_year_Schaefer")]
-Trait_AUS[, volt_bi_multi := apply(.SD, 1, max),
+# Trait_AUS[, volt_bi_multi := apply(.SD, 1, max),
+#           .SDcols = c("Voltinism_2_VicEPA",
+#                       "Volt3_botwe",
+#                       "volt2_Maxwell",
+#                       "volt3_Maxwell",
+#                       "volt4_Maxwell",
+#                       "More_than_two_generations_per_year_bugs_gbr", 
+#                       "More_than_two_generations_per_year_Schaefer")]
+Trait_AUS[, volt_bi_multi_maxwell := apply(.SD, 1, sum, na.rm = TRUE),
+          .SDcols = c("volt2_Maxwell",
+                      "volt3_Maxwell",
+                      "volt4_Maxwell")]
+Trait_AUS[, volt_bi_multi_schaefer := apply(.SD, 1, sum, na.rm = TRUE),
+          .SDcols = c("Two_generations_per_year_Schaefer",
+                      "More_than_two_generations_per_year_Schaefer")]
+Trait_AUS[, volt_bi_multi_gbr := apply(.SD, 1, sum, na.rm = TRUE),
+          .SDcols = c("Two_generations_per_year_bugs_gbr",
+                      "More_than_two_generations_per_year_bugs_gbr")]
+Trait_AUS[, volt_bi_multi := apply(.SD, 1, max, na.rm = TRUE),
           .SDcols = c("Voltinism_2_VicEPA",
                       "Volt3_botwe",
[…]

### 2021-07-15 R/02_EU_harmonize_new.R

@@ -1,5 +1,7 @@
 # _________________________________________________________________________
 #### Harmonize EU Traits ####
+# For traits from different databases, the maximum value is taken
+# For traits that are combined from one db, the sum is taken
 # _________________________________________________________________________
 
 # read in RDS
@@ -43,16 +45,27 @@ Trait_EU[, volt_uni := apply(.SD, 1, max, na.rm = TRUE),
     "voltinism_uni_tachet"
   )
 ]
-Trait_EU[, volt_bi_multi := apply(.SD, 1, max, na.rm = TRUE),
-  .SDcols = c(
-    "voltinism_bi",
-    "voltinism_tri",
-    "voltinism_multi",
-    "voltinism_multi_tachet",
-    "voltinism_flex"
-  )
-]
 
+# Trait_EU[, volt_bi_multi := apply(.SD, 1, max, na.rm = TRUE),
+#   .SDcols = c(
+#     "voltinism_bi",
+#     "voltinism_tri",
+#     "voltinism_multi",
+#     "voltinism_multi_tachet",
+#     "voltinism_flex"
+#   )
+# ]
+Trait_EU[, volt_bi_multi := apply(.SD, 1, sum, na.rm = TRUE),
+         .SDcols = c(
+           "voltinism_bi",
+           "voltinism_tri",
+           "voltinism_multi",
+           "voltinism_flex"
+         )
+]
+Trait_EU[, volt_bi_multi := apply(.SD, 1, max, na.rm = TRUE),
+         .SDcols = c("volt_bi_multi",
+                     "voltinism_multi_tachet")] 
 Trait_EU[, c(
   "voltinism_semi",
   "voltinism_semi_tachet",
@@ -64,6 +77,7 @@ Trait_EU[, c(
   "voltinism_multi_tachet",
   "voltinism_flex"
 ) := NULL]
+
 # _________________________________________________________________________
 # TODO
 #### aquatic stages ####
@@ -329,22 +343,41 @@ Trait_EU[
   feed_other := 0
 ]
 
+# Trait_EU[, feed_shredder := apply(.SD, 1, max, na.rm = TRUE),
+#   .SDcols = c(
+#     "feed_shredder",
+#     "feed_shredder_tachet",
+#     "feed_miner",
+#     "feed_xylo"
+#   )
+# ]
[…]

### 2021-07-15 R/02_NOA_preprocessing.R

@@ -12,6 +12,7 @@ Trait_Noa <- readRDS(file = file.path(data_cleaned,
 # Subset to relevant traits:
 cols <- "Resp_late|Ovipos_behav_prim|stages|Habit_prim|Thermal_pref|Larval_disp|Feed_mode_prim|Voltinism|size|Body\\_shape|Order|Family|Genus|Species"
 Trait_Noa <- Trait_Noa[, .SD, .SDcols = names(Trait_Noa) %like% cols]
+Trait_Noa[, Body_shape_case := NULL]
 
 # Add ID col as unique identifier
 Trait_Noa[, unique_id := 1:nrow(Trait_Noa)]
@@ -137,6 +138,16 @@ Trait_Noa[is.na(Species) & is.na(Genus) & !is.na(Family),
 dupl_unique_id <- Trait_Noa[is.na(Species) & is.na(Genus) & !is.na(Family), ] %>% 
   .[(duplicated(Family)), unique_id]
 Trait_Noa <- Trait_Noa[!unique_id %in% dupl_unique_id, ]
+
+# ___________________________________________________________________________
+#### Normalization ####
+# ___________________________________________________________________________
+normalize_by_rowSum(x = Trait_Noa, 
+                    non_trait_cols = c("unique_id",
+                                       "Species", 
+                                       "Genus",
+                                       "Family",
+                                       "Order"))
 
 # save
 saveRDS(object = Trait_Noa, 

### 2021-07-15 R/03_NOA_harmonize_traits.R

@@ -1,6 +1,6 @@
 # _________________________________________________________________________ 
 #### Harmonize NOA Traits ####
-# Includes also normalization
+# 
 # _________________________________________________________________________
 
 # read in
@@ -90,9 +90,10 @@ setnames(
     "feed_shredder"
   )
 )
-Trait_Noa[, feed_herbivore := apply(.SD, 1. , max),
+Trait_Noa[, feed_herbivore := apply(.SD, 1. , sum, na.rm = TRUE),
           .SDcols = c("Feed_mode_prim_Scraper/grazer",
                       "Feed_mode_prim_Piercer herbivore")]
+
 Trait_Noa[, c("Feed_mode_prim_Scraper/grazer",
               "Feed_mode_prim_Piercer herbivore") := NULL]
 
@@ -227,17 +228,9 @@ Trait_Noa[Trait_EU[is.na(species) & is.na(genus) &
           ),
           on = c(Taxa = "family")]
 
-# A few of the taxa can also be found in the 
-# load NOA_new
-# TODO: check as well
-# load Trait_Noa_new
-# taxa_other_feed_mode[is.na(Species) & !is.na(Genus) , Genus] %in% Trait_Noa_new[, unique(genus)]
-
-
-# del feed mode others
-# still 187 taxa
-# Trait_Noa[`Feed_mode_prim_Other (specify in comments)` > 0, .SD, .SDcols = names(Trait_Noa) %like% "(?i)Feed|Species|Genus|Family"] %>% View()
+# Del remaining 
 Trait_Noa[, `Feed_mode_prim_Other (specify in comments)` := NULL]
+
 
 # _________________________________________________________________________
 #### Locomotion ####
@@ -250,12 +243,14 @@ Trait_Noa[, `Feed_mode_prim_Other (specify in comments)` := NULL]
 setnames(Trait_Noa, 
          old = c("Habit_prim_Attached/fixed", "Habit_prim_Burrower"), 
          new = c("locom_sessil", "locom_burrow"))
-Trait_Noa[, locom_swim := apply(.SD, 1, max),
+Trait_Noa[, locom_swim := apply(.SD, 1, sum, na.rm = TRUE),
           .SDcols = c("Habit_prim_Swimmer",
                       "Habit_prim_Planktonic",
                       "Habit_prim_Skater")]
-Trait_Noa[, locom_crawl := apply(.SD, 1, max),
-          .SDcols = c("Habit_prim_Sprawler", "Habit_prim_Climber", "Habit_prim_Clinger")]
[…]

### 2021-07-15 R/04_NOA_NEW_preprocessing.R

@@ -12,10 +12,8 @@ cols <-
     "Genus",
     "Family",
     "Order",
-    "Feed_mode_sec",
     "Feed_prim_abbrev",
     "Habit_prim",
-    "Habit_sec",
     "Max_body_size_abbrev",
     "Resp_abbrev",
     "Voltinism_abbrev"
@@ -139,9 +137,8 @@ Trait_Noa_new <- data.table::dcast(
 #### Handle duplicates ####
 # _________________________________________________________________________
 
-
-# condense duplicate entries
-# species-level:
+# Condense duplicate entries
+# - species-level:
 # Just zero & ones -> take maximum per duplicate for each trait state
 trait_col <- grep("unique_id|Species|Genus|Family|Order",
                   names(Trait_Noa_new),
@@ -162,18 +159,19 @@ Trait_Noa_new <- Trait_Noa_new[!unique_id %in% dupl_unique_id, ]
 
 Trait_Noa_new[Species == "Ephemerella subvaria", ]
 
-# genus-level:
+# - genus-level:
 Trait_Noa_new[is.na(Species) & !is.na(Genus) &
                 (duplicated(Genus) |
                    duplicated(Genus, fromLast = TRUE)),
               (trait_col) := lapply(.SD, max),
               .SDcols = trait_col,
               by = .(Genus)]
+
 # rm duplicate species entries
 dupl_unique_id <- Trait_Noa_new[is.na(Species) & !is.na(Genus) & duplicated(Genus), unique_id]
 Trait_Noa_new <- Trait_Noa_new[!unique_id %in% dupl_unique_id, ]
 
-# family-level:
+# - family-level:
 Trait_Noa_new[is.na(Species) & is.na(Genus) & !is.na(Family) &
                 (duplicated(Family) |
                    duplicated(Family, fromLast = TRUE)),
@@ -189,6 +187,19 @@ Trait_Noa_new <- Trait_Noa_new[!unique_id %in% dupl_unique_id, ]
 setnames(Trait_Noa_new, 
          old = c("Species", "Genus", "Family", "Order"), 
          new = c("species", "genus", "family", "order"))
+
+# _________________________________________________________________________
+#### Normalization ####
+# Normalizing of the trait values to a range of [0 - 1] by
+# dividing for a given trait each value for each trait state by the sum of all 
+# trait states 
+# _________________________________________________________________________
+normalize_by_rowSum(Trait_Noa_new,
+                    non_trait_cols = c("unique_id",
+                                       "species",
[…]

### 2021-07-15 R/05_NOA_NEW_harmonize_traits.R

@@ -55,16 +55,28 @@ setnames(Trait_Noa_new,
          new = c("locom_sessil",
                  "locom_burrow"))
 # Swimmer
-Trait_Noa_new[, locom_swim := apply(.SD, 1, max),
+Trait_Noa_new[, locom_swim := apply(.SD, 1, sum, na.rm = TRUE),
           .SDcols = c("Habit_prim_Swimmer",
                       "Habit_prim_Planktonic",
                       "Habit_prim_Skater")]
+
 # Crawler 
-Trait_Noa_new[, locom_crawl := apply(.SD, 1, max),
+Trait_Noa_new[, locom_crawl := apply(.SD, 1, sum, na.rm = TRUE),
           .SDcols = c("Habit_prim_Crawler",
                       "Habit_prim_Sprawler",
                       "Habit_prim_Climber",
                       "Habit_prim_Clinger")]
+
+Trait_Noa_new[, c(
+  "Habit_prim_Swimmer",
+  "Habit_prim_Planktonic",
+  "Habit_prim_Skater",
+  "Habit_prim_Crawler",
+  "Habit_prim_Sprawler",
+  "Habit_prim_Climber",
+  "Habit_prim_Clinger"
+) := NULL]
+
 # _________________________________________________________________________
 #### Size ####
 # specifically: Maximum body size
@@ -117,21 +129,6 @@ setnames(
   new = c("volt_uni", 
           "volt_semi",
           "volt_bi_multi")
-)
-
-# _________________________________________________________________________
-#### Normalize Noa New trait data ####
-# Normalizing of the trait values to a range of [0 - 1] by
-# dividing for a given trait each value for each trait state by the sum of all 
-# trait states 
-# _________________________________________________________________________
-Trait_Noa_new <- normalize_by_rowSum(
-  x = Trait_Noa_new,
-  non_trait_cols = c("unique_id",
-                     "species",
-                     "genus",
-                     "family",
-                     "order")
 )
 
 # _________________________________________________________________________
@@ -335,7 +332,7 @@ for (i in name_vec) {
 Trait_Noa_new <- final
 
 
-#### merge information from taxa that are only in old Noa DB ####
+#### Merge information from taxa that are only in old Noa DB ####
 # species level
 Trait_Noa_new <-
   rbind(Trait_Noa_new, Trait_Noa[!is.na(species), ] %>%

### 2021-07-15 R/functions_used_TDB.R

@@ -201,6 +201,7 @@ create_pattern_ind <- function(x, non_trait_cols) {
 #### Normalization of trait scores ####
 # All trait states of one trait are divided by their row sum
 # Hence, trait affinities are represented as "%" or ratios
+# this works for traits named: "groupingfeature_trait"
 normalize_by_rowSum <- function(x, 
                                 non_trait_cols, 
                                 na.rm = TRUE) {
@@ -220,7 +221,7 @@ normalize_by_rowSum <- function(x,
     # divide values for each trait state by
     # the sum of trait state values
     x[, (col_name) := lapply(.SD, function(y) {
-      round(y / rowSum, digits = 2)
+      y / rowSum
     }),
     .SDcols = names(x) %like% cols]
   }

### 2021-08-04 Paper/Submission_new/Latex_Supplementary_File.tex
04.08: Revisions first round completed

@@
 \subsection*{Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships}
+\label{sec:effects_harmonisation_trait_env_rel}
 
@@
 We selected the ecologically relevant traits identified by \citet{szocs_effects_2014} that increased (shredder, life cycle duration $ > 1 $ year, gills, bi/multivoltine, ovoviviparity) or decreased (univoltine, eggs in clutches/cemented or fixed, life cycle duration $ <= 1$ year) with increasing salinity and used these in the fourth corner analysis.
-The selected traits have also reacted to salinity in other studies (but see the discussion in \citet{szocs_effects_2014}).
+The selected traits also responded to salinity in other studies (but see \cite{szocs_effects_2014}).
 
-For some sites, environmental and abundance data have been sampled multiple times per year.
-\citet{szocs_effects_2014} used the full data and did not consider repeated sampling.
-We applied two analysis: one where we did not consider multiple samplings.
-And second where we selected, for the sites with multiple samplings, only those sampling events with the highest macroinvertebrate abundances per year and accordingly only used the conductivity data for these sampling events (this was not done for the RDA approach).Fourth corner analysis was carried out in R with the \textit{fourthcorner()} function from the ade4 package.
+Environmental and abundance data have been sampled multiple times per year in 12 of 15 sites.
+\citet{szocs_effects_2014} used the full data and ignored repeated sampling.
+To avoid temporal pseudoreplication, we selected, for all sites with multiple samplings only the sampling event with the highest macroinvertebrate abundance of each year and the corresponding conductivity data.
+Fourth corner analysis was carried out in R with the \textit{fourthcorner()} function from the ade4 package.
 
-Fourth corner analysis detected fewer trait-conductivity relationships than the RDA approach.
-With the original dataset significant relationships to conductivity were found for the traits shredder and ovoviviparity.
+As expected, the fourth corner analysis detected fewer trait-conductivity relationships than the RDA approach.
+With the original dataset, significant relationships to conductivity were found for the traits shredder and ovoviviparity.
 In three out of the six aggregated and harmonised datasets (\textit{direct\_agg\textsubscript{mean}}, \textit{weighted\_agg}, \textit{direct\_agg\textsubscript{median}}) four significant relationships (for the traits univoltinism, bi/multivoltine, ovoviviparity, and aquatic oviposition) were detected.
-In the remaining three datasets (\textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and harmonised (not aggregated)) two significant relationships for the traits univoltinism and bi/multivoltinism were detected (Table \ref{stab:fc_selected_reduced}).
-Results were only slightly different when not considering multiple samplings (original dataset: two significant trait-conductivity relationship (bi-multivoltine, ovoviviparity), other datasets two to four, Table \ref{stab:fc_selected_full}).
+In the remaining three datasets (\textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and harmonised (not aggregated)), two significant relationships for the traits univoltinism and bi/multivoltinism were detected (Table \ref{stab:fc_selected_reduced}).
+The results were only slightly different when multiple samplings were ignored (original dataset: two significant trait-conductivity relationship (bi-multivoltine, ovoviviparity), other datasets two to four, Table \ref{stab:fc_selected_full}).
 For all significant trait-conductivity relationships, the classification into characteristic traits for downstream and upstream sites was consistent with the results of the RDA analysis.
+
+\newpage
 

### 2021-08-04 Paper/Submission_new/Main_Document-Latex.tex
04.08: Revisions first round completed

@@
 In addition, taxonomic resolution between taxonomic composition data and trait data can differ, making aggregation of traits necessary.
-At present, it is unknown how different trait aggregation approaches compare with expert-assigned trait affinities.
-In this study we aimed to identify discrepancies in trait definitions across freshwater invertebrate databases and to compare trait aggregation methods to identify how phylogenetic structure and trait variability influence results from different aggregation methods.
+However, at present, it is unknown how different trait aggregation approaches compare with expert-assigned trait affinities.
+% In this study we aimed to identify discrepancies in trait definitions across freshwater invertebrate databases and to compare trait aggregation methods to identify how phylogenetic structure and trait variability influence results from different aggregation methods.
 
@@
 The coding to describe traits (binary, fuzzy) also varied among databases.
-Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially when aggregation was based on the median, and that trait coding method, uneven phylogenetic structure, and high trait variability can influence aggregated trait affinities.
-We further showed that harmonised and aggregated data performed similarly to not aggregated and harmonised data from the case study in identifying trait–environment relationships.
+Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially when aggregation was based on the median.
+% ,and that trait coding method, uneven phylogenetic structure, and high trait variability can influence aggregated trait affinities. 
+We further showed that harmonised and aggregated data performed similarly to non-aggregated and harmonised data from the case study in identifying trait–environment relationships, but were only partially able to yield similar values for functional diversity metrics in the case study.
 
 4.
-By identifying discrepancies in trait definitions we hope to motivate the development of standardised terminology for invertebrate traits.
+By identifying discrepancies in trait definitions we hope to motivate the development of standardised definitions for invertebrate traits.
 Our results also illustrate the usefulness of harmonised datasets for ecological study and provide guidance for the circumstances under which the choice of trait aggregation method is important.
@@
 Invertebrate traits have been increasingly used in freshwater ecology, e.g.
-by relating macroinvertebrate trait composition to environmental factors such as climate change or salinisation (\cite{bhowmik_large_2015, poff_developing_2010, szocs_effects_2014}), for predicting changes in ecosystem functioning and trophic dynamics (\cite{vos_taxonomic_2017, gutierrez-canovasPopulationsHighvaluePredators2021}), or for developing indices for biomonitoring (\cite{doledecInvertebrateTraitsBiomonitoring2008a, beketov_spear_2009}), but see also \citet{hamiltonLimitationsTraitbasedApproaches2020} for a critical perspective.
-In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases, which typically include data for a single region or continent (\cite{kefford_integrated_2020, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate, gayraudInvertebrateTraitsBiomonitoring2003, statznerConservationTaxonomicBiological2007}).
+by relating macroinvertebrate trait composition to environmental factors such as climate change or salinisation (\cite{bhowmik_large_2015, contiTraitbasedApproachAssess2014, poff_developing_2010, szocs_effects_2014}), for predicting changes in ecosystem functioning and trophic dynamics (\cite{gutierrez-canovasPopulationsHighvaluePredators2021, vos_taxonomic_2017}), for developing indices or diagnostic tools for biomonitoring (\cite{beketov_spear_2009, doledecInvertebrateTraitsBiomonitoring2008a, mondyUsingConditionalTree2013}), but see also \citet{hamiltonLimitationsTraitbasedApproaches2020} for a critical perspective.
+In the last decades, freshwater ecologists have compiled comprehensive invertebrate trait databases, which typically include data for a single region or continent (\cite{gayraudInvertebrateTraitsBiomonitoring2003, keffordIntegratedDatabaseStream2020a, Philips_and_Smith_NZ_DB_2018, schmidt-kloiber_www.freshwaterecology.info_2015,
+statznerConservationTaxonomicBiological2007, tomanova_trophic_2006, ussegliopolatera_biological_2000, vieira_database_nodate}).
 The availability of invertebrate trait data from different continents enables comparisons of regional trait variation and allows for testing the consistency of trait structure–environmental factor relationships across both small and large spatial extents.
-% Traits provide adaptations to the environmental variability of a habitat which may explain species distributions and early work focused on the link between habitat utilization and traits which lead to one of the first collections of trait information on aquatic invertebrates
-% See theoretical habitat templets (Polatera & Tachet 1994)
-
+In fact, the first studies on the link between habitat utilization and traits in the Upper Rhône river initiated the compilation of aquatic invertebrate trait information (\cite{bournaudApproachSynthesisQualitative1992,usseglio-polateraTheoreticalHabitatTemplets1994}).
+At large scales, consistent responses of traits to environmental stressors have been reported, e.g.
+traits like small body size, multiple life cycles per year, or swimming have been related to resilience and resistance to flow disturbances or retreating glacier cover (\cite{bonada_taxonomic_2007, brown_functional_2018}).
 To date, such analyses have been carried out mostly within continents, using information from one or two trait databases.
@@
 feeding mode) refers to a set of related traits (e.g.
-predator, shredder, etc.) that together define a general property (e.g.
-respiration) that is shared among individuals or species.
+predator, shredder, etc.) that together define a general property that is shared among individuals or species.
 Thus, to use consistent terminology in this study, we use the term grouping feature in place of the term trait, and the term trait instead of trait state, modality or trait category.
@@
 Traits of individual freshwater invertebrates can be difficult to quantify because, unlike plant traits, they are often difficult to measure directly.
-For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behaviour, and what is being eaten (\cite{moog_comprehensive_nodate}).
+For example, to describe feeding habits requires that we understand mouthpart morphology, feeding behaviour, and what is being eaten (\cite{moogFaunaAquaticaAustriaca2017}).
 Some traits can be described in categorical terms, which ignores uncertainty in how traits are expressed in any particular organism (e.g., adult terrestrial stage, presence of gills).
@@
 Data on body form for European and North American taxa were based on expert knowledge (\cite{polatera_personal_information_2020}).
-For Australia and New Zealand, we used trait databases from \citet{kefford_integrated_2020} (hereafter referred to as the Australian database) and \citet{Philips_and_Smith_NZ_DB_2018} (hereafter referred to as the New Zealand database).
+For Australia and New Zealand, we used trait databases from \citet{keffordIntegratedDatabaseStream2020a} (hereafter referred to as the Australian database) and \citet{Philips_and_Smith_NZ_DB_2018} (hereafter referred to as the New Zealand database).
 These databases assigned traits at species, genus, family, and coarser taxonomic levels.
@@
 We established four datasets, one for each of the four geographic regions, by harmonising the traits of seven grouping features from the trait databases.
-We selected grouping feautres that are commonly applied in trait-based ecological studies and describe different aspects of the biology of a species: life history (Voltinism), morphology (Respiration, Body form, Size), ecology (Locomotion, Feeding mode), and reproduction (Oviposition).
-A criterion for trait selection was that the traits occurred in all databases, to enable us to show trait definitions differences and the influence of grouping-feature harmonisation on trait-environment relationships.
+We selected grouping features that are commonly applied in trait-based ecological studies and describe different aspects of the biology of a species: life history (Voltinism), morphology (Body form, Size), physiology (Feeding mode, Respiration), mobility (Locomotion), and reproduction (Oviposition).
+A criterion for trait selection was that the traits occurred in all databases, to allow for an analysis of potential differences in trait definitions and of the influence of grouping-feature harmonisation on trait-environment relationships.
 Thus, we only used biological traits and omitted ecological traits that describe habitat preferences (e.g.
 temperature preference) because these traits are missing in the New Zealand trait database.
-Also, traits from the selected grouping features may consistently respond to certain environmental stressors across large scales and thus be suitable for intercontinental comparisons of trait-environment relationships.
-For example, traits like body size small, multiple life cycles per year, or swimming are related to resilience and resistance to flow disturbances or retreating glacier cover and may consistently respond to certain environmental stressors across regions (\cite{bonada_taxonomic_2007, brown_functional_2018}).
 
 Grouping features were classified differently across the databases, so we harmonised 7 grouping features that collectively included 26 traits (Table \ref{tab:traits_harmonisation}).
-To do so we combined similar traits into one trait (e.g.
-crawlers and sprawlers into crawlers) by assigning for each taxon for the new combined trait the highest affinity score of those originally assigned.
-Next, we selected taxa for inclusion in our datasets and normalised the trait affinity scores for each taxon.
+To do so we normalised trait affinity scores and combined similar traits into one trait (e.g.
+crawlers and sprawlers into crawlers) by summing for each taxon for the new combined trait the affinity scores of those originally assigned.
+If similar traits from multiple databases were combined (e.g.
+in the Australian trait database) we assigned the highest affinity score.
+Next, we selected taxa for inclusion in our datasets and normalised the trait affinity scores for each taxon again.
 We first omitted all taxa with a lower taxonomic precision than family level and consolidated duplicate taxa that appeared within a database, by either applying the median for fuzzy coded traits, or the maximum for binary traits.
@@
 As expected, the range of trait affinities increased with higher trait variability for all trait aggregation methods.
-Therefore, we provide details of the simulation and the results in the supplementary materials.
+We provide details of the simulation and the results in the Supplementary Materials.
 
@@
 Additionally, to test for the effect of different aggregation methods on inferences about CWM trait–salinisation relationships, we repeated the RDA five times, each with family-level aggregated trait values assigned to corresponding taxa from \citet{szocs_effects_2014}.
-We used the RDA approach for consistency with \citet{szocs_effects_2014} but are aware of the criticism that regressing CWM traits against environmental gradients has received (but see \cite{peres-netoLinkingTraitVariation2017, millerFunctionalTraitsCommunity2019}).
+We used the RDA approach for consistency with \citet{szocs_effects_2014}, though it is under debate (see \citet{peres-netoLinkingTraitVariation2017, millerFunctionalTraitsCommunity2019}).
 % because CWM trait values are treated as independent while they in fact are non-independent which can lead to inflated Type 1 errors
@@
 Finally, we assessed how functional diversity (FD) changed when harmonised and aggregated trait data are used.
-Harmonisation of grouping features reduces the number of traits per grouping feature, e.g.
-for the freshwaterecology.info database ten feeding mode traits were combined to six traits, and thus likely influences FD metrics.
+Harmonisation of grouping features reduces the number of traits per grouping feature and thus likely influences FD metrics, e.g.
+for the freshwaterecology.info database ten feeding mode traits were combined to six traits.
 We calculated functional richness (FRic), functional evenness (FEve), and functional divergence (FDiv) following \citet{villegerNewMultidimensionalFunctional2008a} with the traits from \citet{szocs_effects_2014}, harmonised grouping features from the European trait dataset, and with family-level aggregated trait values.
 For FEve and FDiv invertebrate abundance data were used from \citet{szocs_effects_2014}.
-To account for temporal autocorrelation (sampling was done over a time period of three years) we regressed each FD metric with year and extracted the residuals.
-The residuals of the original study were compared with the residuals of the harmonised and aggregated datasets through regression and evaluation of the coefficient of determination ($R^2$).
+To account for temporal autocorrelation (sampling was done over a time period of three years), we partialled out the effect of year from all datasets.
+The datasets were compared through regression with the coefficient of determination ($R^2$).
 
@@
 The freshwaterecology.info, Tachet, and CONUS databases provided more detailed descriptions of trait information than the Vieira and New Zealand databases provided.
-The Australian trait database (\cite{kefford_integrated_2020}) was a collection of seven specific trait datasets; thus, grouping features occurred multiple times with varying differentiation into traits.
+The Australian trait database (\cite{keffordIntegratedDatabaseStream2020a}) was a collection of seven specific trait datasets; thus, grouping features occurred multiple times with varying differentiation into traits.
 Depending on the dataset, trait information was described with more or less detail.
@@
 
-The percentage of differing cases of aggregated versus assigned trait affinities varied by method between 16.2 and 22.9 \% for the Australian dataset and between 15.3 and 47 \% for the North American dataset (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
+The percentage of differing cases of aggregated versus assigned trait affinities varied by method between 21.9 and 27.6 \% for the Australian dataset and between 15.5 and 44.8 \% for the North American dataset (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
 In general, median aggregation methods yielded fewer cases with differences compared with mean aggregation methods.
@@
 Thus, compared with the original study’s findings, aggregating by the direct and weighted methods yielded less change than the stepwise methods in interpretation of the RDA results.
-To demonstrate a different approach to detecting relationships between traits and conductivity we used fourth corner analysis with the original, harmonised, and aggregated trait datasets (methods and results in  ).
+Given the criticism of approaches relying on CWM traits we also applied fourth corner analysis with the original, harmonised, and aggregated trait datasets to detect relationships between traits and conductivity (methods and results in the supporting information \ref{sec:effects_harmonisation_trait_env_rel}).
 
@@
 
-The calculation of FD metrics for the original, harmonised (not aggregated), and aggregated datasets suggested that harmonising trait data preserves FRic and FDiv values, while aggregated trait data only preserved FRic values.
+The calculation of FD metrics for the original, harmonised (not aggregated), and aggregated datasets suggested that harmonising trait data preserves FRic and FDiv values, whereas aggregated trait data only preserved FRic values.
 The FRic and FDiv values calculated from harmonised trait data correlated highly to FRic and FDiv values from the original dataset ($R^2 = 0.96$ and $0.86$, respectively).
-FRic and FDiv calculated for aggregated trait data showed moderate to good correlations to the FRic and FDiv values calculated with the original dataset (FRic: $0.78 <= R^2 <= 0.84$ , FDiv: $0.42 <= R^2 <= 0.62$, Figure \ref{fig:FRic} and \ref{fig:FDiv}).
+FRic and FDiv calculated for aggregated trait data showed moderate to high correlations to the FRic and FDiv values calculated with the original dataset (FRic: $0.78 <= R^2 <= 0.84$ , FDiv: $0.42 <= R^2 <= 0.62$, Figure \ref{fig:FRic} and \ref{fig:FDiv}).
 By contrast, FEve values calculated with harmonised and aggregated trait data were unrelated to the FEve values calculated with the original dataset (all $R^2 < 0.1$), except for \textit{stepwise\_agg \textsubscript{median}}, which showed a moderate correlation to FEve values calculated from the original dataset ($R^2  = 0.48$, Figure \ref{fig:FEve}).
@@
 
-FD analysis is an important trait-based application to quantify the variability of traits that influence ecosystem functions.
-We found through correlation that harmonised trait data may be used to calculate FRic and FDiv values, and that aggregated trait data can at least be used to calculate FRic values.
-This does not apply to FEve, as the use of harmonised and aggregated trait data yielded completely different FEve values than with the trait data from \citet{szocs_effects_2014}.
+FD analysis quantifies the variability of traits that influence ecosystem functions.
+We found that harmonised trait data was well-suited for calculating FRic and FDiv values, and that aggregated trait data was well-suited for calculating FRic values.
+By contrast, the use of harmonised and aggregated trait data yielded completely different FEve values than with the trait data from \citet{szocs_effects_2014}.
 FRic represents the trait space spanned by the community (also termed the convex hull volume) and is only dependent on the trait data used.
-Our results show that harmonisation preserves the trait space the best, i.e.
-the most extreme trait values of the original study, and that aggregation only slightly changes the trait space.
-It follows that FDiv, which describes how abundances are distributed within the volume of the trait space, is best preserved by harmonised trait data and to a lesser extent with aggregated trait data.
+Our results show that harmonisation preserved the trait space and that aggregation only slightly changed the trait space.
+FDiv, which describes how abundances are distributed within the volume of the trait space, was preserved by harmonised trait data and to a lesser extent by aggregated trait data.
 FEve describes how regular the trait space is filled by taxa.
-We found that harmonised and aggregated trait change the evenness of the abundance distribution in the trait space, which is likely because during the calculation of FEve only the nearest neighbours in the trait space are considered.
-This leads to the undesirable property that even small community changes result in large changes in the FEve index, a behaviour that has been shown by \citet{botta-dukatTestingAbilityFunctional2016} through simulation.
+We found that harmonised and aggregated trait changed the evenness of the abundance distribution in the trait space, which is likely because during the calculation of FEve only the nearest neighbours in the trait space are considered.
+This leads to the undesirable property that even small community changes result in large changes in FEve (\cite{botta-dukatTestingAbilityFunctional2016}).
 
@@
 Although comprehensive freshwater invertebrate trait databases have been developed for several regions in the past, data synthesis presents challenges because of discrepancies in trait definitions, coding of trait affinities, and taxonomic resolution.
-By providing an overview of definition discrepancies, we have set a starting point for the development of standardised trait terminology through which invertebrate trait databases can be linked.
-Agreement on standard terminology and the subsequent development of ontologies are the next steps to facilitate trait-based analysis at large geographical scales.
-As our analysis showed, some grouping features might need to be re-classified to fit into such a standardised terminology.
+By providing an overview of discrepancies in definitions, we have set a starting point for the development of standardised trait definitions through which invertebrate trait databases can be linked.
+Agreement on standard trait definitions and the subsequent development of ontologies are the next steps to facilitate trait-based analysis at large geographical scales.
+As our analysis showed, some grouping features might need to be re-classified to fit into such a controlled vocabulary.
 Although we showed that trait affinities from fuzzy and binary coding can be used together, we also recommend that a uniform coding of traits should be addressed during trait standardisation.
@@
 and L.M.
-provided trait data for Australia; P.U-P.
+provided trait data for Australia; A.S-K., W.G.
+and P.U-P.
+provided trait data for Europe; P.U-P.
 provided body form trait data for European and North American invertebrates; C.P.H., N.L.P., and L.T.
 provided trait data for North America; C.D.M.
-provided trait data for New Zealand;
-B.J.K., A.S-K., C.D.M, W.G., N.L.P., L.M., and C.P.H.
+provided trait data for New Zealand; B.J.K., A.S-K., C.D.M, W.G., N.L.P., L.M., and C.P.H.
 provided in depth information on trait data and discussed the procedure of analysis; S.K.
@@
 % Table 1
-\begin{landscape}
-  \begin{longtable}{m{2.0cm}|m{4.0cm}|m{4.2cm}|m{4.2cm}|m{1.7cm}|m{2cm}|m{2.2cm}}
-      \caption{Excerpt of the comparison of trait definition differences between invertebrate trait databases for the traits predator and swimming.
-The definition is quoted if it enables differences to be identified, otherwise the differences are described.
-Bullet points indicate when several traits have been used to describe a morphological or behavioural property.
-The full version and further information can be found in the supporting information Table \ref{stab:trait_definitions}.}
-      \label{tab:trait_definitions}
-      \endfirsthead
-      \toprule[.1em]
-      Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & CONUS & Vieira & Australia & \specialcell{New \\ Zealand} \\
-      \toprule[.1em]
-      Feeding predator & 
-        "Eating from prey" & 
-        \begin{itemize}
-            \item Carvers, engulfers \& swallowers
-            \item Piercers (plants \& animals) are an additional trait
-        \end{itemize} & % Notes: Tachet -> Piercer (plants & animals)
-        Engulfers ("ingest prey whole or in parts") \& 
-        piercers ("prey tissues and suck fluids") & 
-        Predator &
-        Piercer \& engulfer &
-        Predator
-        \\ 
-        \midrule
-        Locomotion swimming & 
-        \begin{itemize}
-            \item Passive movement like floating or drifting (trait swimming/scating)
-            \item Active movement (trait swimming/diving)
-        \end{itemize}. &
-        \begin{itemize}
-            \item Surface swimmers (over and under the water surface)
-            \item Full water swimmers (e.g. Baetidae).
-        \end{itemize} & 
-        "Adapted for "fishlike" swimming" & 
-        Swimmer & 
-        Traits swimmer and skater & 
-        Swimmers (water column)
-        \\
-      \bottomrule
-  \end{longtable}
-\end{landscape}
-
-% Table 2
 \begin{longtable}{m{2.5cm}|m{4cm}|m{7.5cm}}
@@
   \midrule
-Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattenend\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattenend, dorsoventrally flattened$^{\dagger}$ \\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
+  Body Form    & \begin{tabular}[c]{@{}l@{}}Cylindrical \\ Flattened\\ Spherical\\ Streamlined\end{tabular}                       & \begin{tabular}[c]{@{}l@{}}Cylindrical, tubular\\ Flattened, dorsoventrally flattened$^{\dagger}$ \\ Spherical, round (humped)\\ Streamlined, fusiform\end{tabular}                                                                                                                                                                          \\
   \midrule
@@
 
-\newpage
 % Table 2 (Start Results)
@@
 \begin{landscape}
+  \begin{longtable}{m{2.0cm}|m{4.0cm}|m{4.2cm}|m{4.2cm}|m{1.7cm}|m{2cm}|m{2.2cm}}
+      \caption{Excerpt of the comparison of trait definition differences between invertebrate trait databases for the traits predator and swimming.
+The definition is quoted if it enables differences to be identified, otherwise the differences are described.
+Bullet points indicate when several traits have been used to describe a morphological or behavioural property.
+The full version and further information can be found in the supporting information Table \ref{stab:trait_definitions}.}
+      \label{tab:trait_definitions}
+      \endfirsthead
+      \toprule[.1em]
+      Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & CONUS & Vieira & Australia & \specialcell{New \\ Zealand} \\
+      \toprule[.1em]
+      Feeding predator & 
+        "Feed on prey" & 
+        \begin{itemize}
+            \item Carvers, engulfers \& swallowers
+            \item Piercers (plants \& animals) are an additional trait
+        \end{itemize} & % Notes: Tachet -> Piercer (plants & animals)
+        Engulfers ("ingest prey whole or in parts") \& 
+        piercers ("prey tissues and suck fluids") & 
+        Predator &
+        Piercer \& engulfer &
+        Predator
+        \\ 
+        \midrule
+        Locomotion swimming & 
+        \begin{itemize}
+            \item Passively floating  in lakes or drifting in rivers (trait swimming/scating)
+            \item Active swimming or diving (trait swimming/diving)
+        \end{itemize}. &
+        \begin{itemize}
+            \item Surface swimmers (over and under the water surface)
+            \item Full water swimmers (e.g. Baetidae).
+        \end{itemize} & 
+        "Adapted for "fishlike" swimming" & 
+        Swimmer & 
+        Traits swimmer and skater & 
+        Swimmers (water column)
+        \\
+      \bottomrule
+  \end{longtable}
+\end{landscape}
+
+\newpage
+
+% Table 5
+\begin{landscape}
 \begin{longtable}{m{2.5cm}|m{3.5cm}|m{2cm}|m{1.5cm}|m{1.5cm}|m{4.8cm}|m{2cm}}
@@
 
-% Table 5
+% Table 6
 \begin{landscape}
@@
     \centering
-    \caption{Percentage of differing cases, minimum, maximum, mean, and standard deviation of absolute differences between trait affinities assigned at family level by experts and aggregated trait affinities from five different aggregation methods.}
+    \caption{Percentage of differing cases, minimum, maximum, mean, and standard deviation of absolute differences between trait affinities assigned at family level by experts and aggregated trait affinities from five different aggregation methods for all compared grouping features.}
     \label{tab:summary_stat_aggr_vs_fam_assigned}
@@
     \toprule[.1em]
-    \multirow{4}{*}{\specialcell{AUS}} & \specialcell{\textit{direct\_agg\textsubscript{median}}} & 16.53 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
-    & \specialcell{\textit{direct\_agg\textsubscript{mean}}} & 23.24 & $< 0.01$ & 0.99 & 0.34 & 0.23 \\ 
-    & \specialcell{\textit{stepwise\_agg\textsubscript{median}}} & 17.90 & 0.01 & 1.00 & 0.42 & 0.26 \\ 
-    & \specialcell{\textit{stepwise\_agg\textsubscript{mean}}} & 23.24 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
-    & \specialcell{\textit{weighted\_agg}} & 23.24 & $< 0.01$ & 1.00 & 0.34 & 0.24 \\ 
+    \multirow{4}{*}{\specialcell{AUS}} & \specialcell{\textit{direct\_agg\textsubscript{median}}} & 21.93  & 0.07 & 1.00 & 0.69 & 0.32 \\ 
+    & \specialcell{\textit{direct\_agg\textsubscript{mean}}} & 27.61  & 0.01 & 1.00 & 0.54 & 0.32 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{median}}} & 23.01 & 0.01 & 1.00 & 0.65 & 0.32 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{mean}}} & 27.56  & $< 0.01$ & 1.00 & 0.54 & 0.32 \\ 
+    & \specialcell{\textit{weighted\_agg}} & 27.61  & $< 0.01$ & 1.00 & 0.55 & 0.32 \\ 
     \midrule
-    \multirow{4}{*}{\specialcell{NA}} & \specialcell{\textit{direct\_agg\textsubscript{median}}} & 15.33 & 0.17 & 1.00 & 0.70 & 0.26 \\ 
-    & \specialcell{\textit{direct\_agg\textsubscript{mean}}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.26 \\ 
-    & \specialcell{\textit{stepwise\_agg\textsubscript{median}}} & 18.00 & 0.08 & 1.00 & 0.63 & 0.28 \\ 
-    & \specialcell{\textit{stepwise\_agg\textsubscript{mean}}} & 47.00 & $< 0.01$ & 1.00 & 0.30 & 0.27 \\ 
-    & \specialcell{\textit{weighted\_agg}} & 47.00 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
+    \multirow{4}{*}{\specialcell{NA}} & \specialcell{\textit{direct\_agg\textsubscript{median}}} & 15.52 & 0.25 & 1.00 & 0.68 & 0.27 \\ 
+    & \specialcell{\textit{direct\_agg\textsubscript{mean}}} & 44.81 & $< 0.01$ & 1.00 & 0.31 & 0.26 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{median}}} & 18.71 & 0.12 & 1.00 & 0.60 & 0.29 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{mean}}} & 44.81 & $< 0.01$ & 1.00 & 0.31 & 0.27 \\ 
+    & \specialcell{\textit{weighted\_agg}} & 44.81 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
     \bottomrule

### 2022-03-26 R/Not_implemented_yet/00_NOA_affinity_scores.R
26.03: Removed few old R scripts

@@ -1,68 +1,0 @@
-# _____________________________________________________________________
-#### Calculate "affinity scores" based on frequency ####
-# Frequency of each trait state is converted into a probability
-# Code is from Laura Twardochleb and just slightly changed
-# TODO:Improve Code by using DT
-# _____________________________________________________________________
-
-library(data.table)
-library(dplyr)
-library(tidyr)
-
-# read in
-Trait_Noa_new <- fread(file.path(data_in, "North_America", "Trait_table_LauraT.csv"))
-
-
-# select a few columns
-Subset_Noa_new <- Trait_Noa_new[, .(Voltinism_abbrev, 
-                                    Max_body_size_abbrev,
-                                    Resp_abbrev,
-                                    Habit_prim, 
-                                    Feed_prim_abbrev,
-                                    Genus, 
-                                    Family,
-                                    Order)]
-
-# set "Other" as category to NA
-for(j in names(Subset_Noa_new)) {
-  data.table::set(Subset_Noa_new,
-                  which(Subset_Noa_new[[j]] %in% "Other (specify in comments)"),
-                  j,
-                  NA)
-}
-mode_fn <-
-  function(x) {
-    ifelse(any(!is.na(x)), names(which.max(table(x))), as.character(NA))
-  }
-
-# trait mode according to Laura
-Subset_Noa_new %>% 
-  filter(!is.na(Genus)) %>%
-  group_by(Genus) %>% 
-  summarize_all(mode_fn)
-
-# reshape table into long format
-keycol=c("Trait_group")
-valuecol=c("Trait")
-gathercol <- c(
-  "Habit_prim",
-  "Habit_sec",
-  "Thermal_pref",
-  "Voltinism_abbrev"
-)
-
-# long format
-traits_long <- Subset_Noa_new  %>%
-  filter(!is.na(Genus)) %>%
-  tidyr::gather_(keycol, valuecol, gathercol) 
-
-
-# calculate frequency of trait state occurrence per genus and trait
-# convert data back to wide format
-traits_long %>%
-  filter(!is.na(Trait)) %>%
-  group_by(Genus, Trait_group, Trait) %>%
-  tally() %>%
-  mutate(Percent = n / sum(n)) %>%
-  dcast(., Genus ~ Trait+ Trait_group) %>%
-  filter(grepl("Acentrella", Genus))

### 2022-03-26 R/Not_implemented_yet/01_01_Freshecol_Dispersal.R

@@ -1,48 +1,0 @@
-# Dispersal Data from Sarremejane -----------------------------------------
-
-# dissem traits contain -99 -> change to NA
-# col <- grep("dissem", names(dat_EU), value = TRUE)
-# dat_EU[, (col) := lapply(.SD, function(y) {
-#   ifelse(y == -99, NA, y)
-# }), .SDcols = names(dat_EU) %like% "dissem"]
-
-
-# disp_EU <-
-#   fread(
-#     file = file.path(data_in, "Europe", "Flying_propensity.csv"),
-#     na.strings = ""
-#   )
-# 
-# # fly propensity NA to medium
-# disp_EU[grepl("NA", Flying_propensity), Flying_propensity := "Medium"]
-# 
-# # turn propensity trait into wide format
-# disp_EU <- dcast(
-#   data = disp_EU[!is.na(Flying_propensity)],
-#   formula = Taxon  ~ Flying_propensity,
-#   fun.aggregate = length,
-#   value.var = "Flying_propensity"
-# )
-# 
-# # filter for "dae"
-# # ** -> ony family level identification possible, average of traits for all genera
-# # in the given family
-# disp_EU[grepl(".*dae", Taxon), `:=`(Family = sub("\\*\\*|[[:space:]]\\*\\*", "",
-#                                                  Taxon),
-#                                     Taxon = NA_character_)]
-# # spp. to Genus
-# disp_EU[grepl("spp\\.", Taxon), `:=`(Genus = sub("[[:space:]]spp\\.", "", Taxon),
-#                                      Taxon = NA_character_)]
-# 
-# # * -> trait information from phylogenetically closest genera
-# disp_EU[grepl("\\*", Taxon), Taxon := sub("\\*","",Taxon)]
-# 
-# # del group in Taxon
-# disp_EU[grepl("group", Taxon), Taxon := sub("[[:space:]]group","", Taxon)]
-# 
-# # rename
-# setnames(disp_EU, "Taxon", "Species")
-# 
-# # change col type to numeric for Medium, Strong, Weak
-# disp_EU[, c("Medium", "Strong", "Weak") := lapply(.SD, as.numeric),
-#         .SDcols = c("Medium", "Strong", "Weak")]

### 2022-03-26 R/test.r

@@ -1,64 +1,0 @@
-# 
-aus_old <- readRDS(file.path(data_cleaned, "Australia", "Trait_AUS_agg_old.rds"))
-
-aus_old[!family %in% Trait_AUS_agg$family, ]
-
-
-# Testing a function for finding thoses families with excess zeros ----
-# Consider for median aggregation!
-test <- Trait_Noa_new[family == "Leptoceridae", .SD,
-    .SDcols = patterns("size|species|genus|family|order")
-]
-
-# Create a function out of this
-test_excess_zeros <- function(trait_data,
-                              trait_pattern) {
-    family <- na.omit(trait_data[, .SD,
-        .SDcols = patterns(paste0(trait_pattern, "|family"))
-    ]) %>%
-        .[, lapply(.SD, function(y) (sum(y == 0) / .N) > 0.5),
-            by = .(family)
-        ] %>%
-        .[, all(.SD), .SDcols = patterns(trait_pattern), by = .(family)] %>%
-        .[V1 == 1, family]
-
-    list(
-        "families" = family,
-        "trait" = trait_pattern
-    )
-}
-
-for (pat in c("feed", "size")) {
-    test_excess_zeros(
-        trait_data = Trait_Noa_new,
-        trait = pat
-    ) %>% print()
-}
-
-
-
-direct_agg <- function(trait_data,
-                       non_trait_cols,
-                       method,
-                       na.rm = TRUE) {
-    # get names of trait columns
-    pat <- paste0(non_trait_cols, collapse = "|")
-    trait_col <- grep(pat, names(trait_data), value = TRUE, invert = TRUE)
-
-    # aggregate to family-level
-    # subset so that no NA values occur in data
-    # (otherwise all NA entries are viewed as a group &
-    # aggregated as well)
-    agg_data <- trait_data[!is.na(family),
-        lapply(.SD, method, na.rm = na.rm),
-        .SDcols = trait_col,
-        by = "family"
-    ]
-
-    # merge information on order back
-    agg_data[trait_data,
-        `:=`(order = i.order),
-        on = "family"
-    ]
-    agg_data
-}

### 2022-03-26 R/02_AUS_harmonize_traits.R
26.03: Small updates to a few R scripts

@@ -673,6 +673,18 @@ for (j in trait_cols) {
   data.table::set(Trait_AUS, which(is.infinite(Trait_AUS[[j]])), j, 0)
 }
 
+## Normalization ----
+# All trait states of one trait are divided by the row sum
+# Hence, trait affinities are represented as "%" or ratios 
+Trait_AUS <- normalize_by_rowSum(
+  x = Trait_AUS,
+  non_trait_cols = c("unique_id",
+                     "species",
+                     "genus",
+                     "family",
+                     "order")
+)
+
 # save
 saveRDS(
   object = Trait_AUS,

### 2022-03-26 R/02_EU_harmonize_new.R

@@ -759,7 +759,7 @@ Trait_EU[, c(
 # Oviposition ----
 # ovip_aqu: Reproduction via aquatic eggs
 # ovip_ter: Reproduction via terrestric eggs
-# ovip_ovo: Reproduction via ovoviparity
+# ovip_ovo: Reproduction via ovoviviparity
 # rep_parasitic no entries
 # rep_asexual is deleted
 # Harmonising using the sum in comb with na.rm = TRUE
@@ -861,8 +861,10 @@ Trait_EU[, c(
 
 # _________________________________________________________________________
 # Temperature ----
-# temp_coldsteno: cold stenotherm (cos); preference for a small cold temperature range (below 10°C)
-# temp_warmsteno: warm stenotherm	(was);	preference for a small warm temperature range (above 18°C)
+# temp_coldsteno: cold stenotherm (cos); preference for a small cold temperature range
+# (below 10°C)
+# temp_warmsteno: warm stenotherm	(was);	preference for a small warm temperature range 
+# (above 18°C)
 # temp_euryt: eurytherm	(eut)	no specific preference, wide temperature range
 # temp eurytherm (no specific preference)
 # psychrophilic (< 15 °C)
@@ -887,6 +889,7 @@ Trait_EU[, c(
 #              "temp_warmsteno", 
 #              "temp_thermophil_tachet"
 #              ) := NULL]
+
 # _________________________________________________________________________
 # Body form ----
 # bf_streamlined: streamlined/fusiform
@@ -1022,9 +1025,9 @@ Trait_EU[, `:=`(
 )]
 
 # _________________________________________________________________________
-
 # Postprocessing ----
-# normalize again (actually only needed for bf data)
+
+## Normalize again (actually only needed for bf data) ----
 normalize_by_rowSum(
   x = Trait_EU,
   non_trait_cols = c(

### 2022-03-26 R/02_NZ_harmonize_traits.R

@@ -240,6 +240,7 @@ Trait_NZ[, `:=`(
   dev_holometabol = ifelse(Order %in% holometabola, 1, 0)
 )]
 
+# Postprocessing ----
 # subset to relevant traits
 # missing currently: aquatic stages, dispersal/dissemination, T, pH
 Trait_NZ <-
@@ -262,6 +263,16 @@ setcolorder(
     names(Trait_NZ),
     value = TRUE
   )
+)
+
+## Normalization ----
+Trait_NZ <- normalize_by_rowSum(
+  x = Trait_NZ,
+  non_trait_cols = c("order",
+                     "family",
+                     "genus",
+                     "species",
+                     "unique_id")
 )
 
 # save

### 2022-03-26 R/03_AUS_aggregate_traits.R

@@ -12,20 +12,6 @@ Trait_AUS <- readRDS(
   )
 )
 
-# _________________________________________________________________________ 
-# Normalization ----
-# All trait states of one trait are divided by the row sum
-# Hence, trait affinities are represented as "%" or ratios 
-# _________________________________________________________________________ 
-Trait_AUS <- normalize_by_rowSum(
-  x = Trait_AUS,
-  non_trait_cols = c("unique_id",
-                     "species",
-                     "genus",
-                     "family",
-                     "order")
-)
-
 # test how complete trait sets are 
 completeness_trait_data(
   x = Trait_AUS,

### 2022-03-26 R/03_NZ_aggregate_traits.R

@@ -5,20 +5,8 @@
 # read in Trait NZ
 Trait_NZ <- readRDS(file.path(data_cleaned, "NZ", "Trait_NZ_pp_harmonized.rds"))
 
-# _________________________________________________________________________
-# Normalization ----
-# _________________________________________________________________________
-Trait_NZ <- normalize_by_rowSum(
-  x = Trait_NZ,
-  non_trait_cols = c("order",
-                     "family",
-                     "genus",
-                     "species",
-                     "unique_id")
-)
-
 # Subset to interesting orders:
-#   "Amphipoda" & "Venerida" missing
+# "Amphipoda" & "Venerida" missing
 Trait_NZ <- Trait_NZ[order %in% c(
   "Ephemeroptera",
   "Hemiptera",

### 2022-03-26 R/06_NOA_NEW_aggregate_traits.R

@@ -1,6 +1,9 @@
 # _________________________________________________________________________
 # Aggregation of traits NOA data from Laura T ----
-# TODO: Check and simplify Aggregation functions
+# NoA trait data already normalised
+# for(i in c("locom", "feed", "resp", "volt", "bf", "size", "dev", "ovip")) {
+# print(all(!rowSums(Trait_Noa_new[, .SD, .SDcols = patterns(i)], na.rm = TRUE) > 1))
+# }
 # _________________________________________________________________________
 
 # read in pp_harmonized

### 2022-03-26 Paper/Submission_new/Latex_Supplementary_File.tex
26.03: Updated paper files, most recent in Submission_new

--- 2021-07-13 Paper/Submission_new/Latex_Supplementary_File.tex
@@
 
-\title{Supporting Information - Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
+\title{Supporting Information - Tackling inconsistencies among freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
 \author[1]{Stefan Kunz}
@@
 \subsection*{Effects of harmonisation and trait aggregation on inferences regarding trait-environment relationships}
-
-\begin{table}[H]
-    \centering
-    \caption{Mean, median and standard deviation of the affinities of traits that were responsive to the salinity gradient in the original study but not in the re-analysis using the harmonised European trait dataset.}
-    \label{tab:SI_resp_traits_summary_stats}
-    \begin{tabular}{l|l|c|c|c|c}
-    \toprule[.1em]
-    Type & Trait & Mean & Median & SD & Responsive? \\ 
-    \toprule[.1em]
-    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 & No \\ 
-      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 & No\\ 
-      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 & No\\ 
-      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 & No\\ 
-      Weighted & Shredder & 0.19 & 0.14 & 0.22 & No \\ 
-      Harmonised; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 & No \\ 
-      Original & Shredder & 0.25 & 0.14 & 0.32 & Yes\\ 
-      \midrule
-      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 & Yes\\ 
-      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 & Yes\\ 
-      Direct\_median & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
-      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
-      Weighted & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
-      Harmonised; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 & No \\ 
-      Original & Gills & 0.28 & 0.00 & 0.33 & Yes \\ 
-      \midrule
-      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 & No \\ 
-      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 & No \\ 
-      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 & Yes \\ 
-      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 & Yes \\ 
-      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 & Yes\\ 
-      Harmonised; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 & Yes \\ 
-      Original & Short life cycle & 0.64 & 0.75 & 0.40 & Yes \\ 
-      \midrule
-      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 & No \\ 
-      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 & No \\
-      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 & Yes\\ 
-      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 & Yes \\ 
-      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 & Yes \\ 
-      Harmonised; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 & Yes \\ 
-      Original & Long life cylce & 0.36 & 0.25 & 0.40 & Yes\\ 
-    \bottomrule
-    \end{tabular}
-\end{table}
+\label{sec:effects_harmonisation_trait_env_rel}
 
@@
     \centering
-    \includegraphics[width=18.5cm, height=16cm]{boxplot_scores_combined_REMAIN_SI.png}
+    \includegraphics[width=18.5cm, height=15cm]{boxplot_scores_combined_REMAIN_SI.png}
     \caption{RDA of traits constrained by electric conductivity for the data aggregated with \textit{direct\_agg \textsubscript{mean}}, \textit{stepwise\_agg \textsubscript{mean}}, and \textit{weighted\_agg}.
@@
 We selected the ecologically relevant traits identified by \citet{szocs_effects_2014} that increased (shredder, life cycle duration $ > 1 $ year, gills, bi/multivoltine, ovoviviparity) or decreased (univoltine, eggs in clutches/cemented or fixed, life cycle duration $ <= 1$ year) with increasing salinity and used these in the fourth corner analysis.
-The selected traits have also reacted to salinity in other studies (but see the discussion in \citet{szocs_effects_2014}).
-For some sites, environmental and abundance data have been sampled multiple times per year.
-\citet{szocs_effects_2014} used the full data and did not consider repeated sampling.
-We applied two analysis: one where we did not consider multiple samplings.
-And second where we selected, for the sites with multiple samplings, only those sampling events with the highest macroinvertebrate abundances per year and accordingly only used the conductivity data for these sampling events (this was not done for the RDA approach).Fourth corner analysis was carried out in R with the \textit{fourthcorner()} function from the ade4 package.
-With the fourth corner analysis fewer trait-conductivity relationships than with the RDA approach were detected.
-With the original dataset significant relationships to conductivity were found for the traits shredder and ovoviviparity.
-In three out of the six aggregated and harmonised datasets (\textit{direct\_agg\textsubscript{mean}}, \textit{weighted\_agg}, harmonised (not aggregated)) four to five significant relationships (for the traits shredder, univoltinism, bi/multivoltine, ovoviviparity, and aquatic oviposition) were detected.
-In the remaining three datasets (\textit{stepwise\_agg\textsubscript{median}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{direct\_agg\textsubscript{median}}) two significant relationships for the traits univoltinism and bi/multivoltinism were detected.
-Results were only slightly different when not considering multiple samplings (original dataset: one significant trait-conductivity relationship, others three to four).
-For the significant trait-conductivity relationships, the classification into characteristic traits for downstream and upstream sites was consistent with the results of the RDA analysis.
+The selected traits also responded to salinity in other studies (but see \cite{szocs_effects_2014}).
+
+Environmental and abundance data have been sampled multiple times per year in 12 of 15 sites.
+\citet{szocs_effects_2014} used the full data and ignored repeated sampling.
+To avoid temporal pseudoreplication, we selected, for all sites with multiple samplings only the sampling event with the highest macroinvertebrate abundance of each year and the corresponding conductivity data.
+Fourth corner analysis was carried out in R with the \textit{fourthcorner()} function from the ade4 package.
+
+As expected, the fourth corner analysis detected fewer trait-conductivity relationships than the RDA approach.
+With the original dataset, a significant relationship to conductivity were found for the trait ovoviviparity (0.042) and almost for the trait shredder a p-value close to the significance level (0.077).
+In four out of the six aggregated and harmonised datasets (\textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{median}}, harmonised (not aggregated)) four significant relationships (for the traits univoltinism, bi/multivoltine, ovoviviparity, and aquatic oviposition) were detected.
+In the remaining two datasets (\textit{direct\_agg\textsubscript{median}}, \textit{weighted\_agg}), two significant relationships for the traits univoltinism and bi/multivoltinism were detected (Table \ref{stab:fc_selected_reduced}).
+The results were only slightly different when multiple samplings were ignored (original dataset: four significant trait-conductivity relationship (shredders, univoltine, bi-multivoltine, ovoviviparity), other datasets two to four, Table \ref{stab:fc_selected_full}).
+For all significant trait-conductivity relationships, the classification into characteristic traits for downstream and upstream sites was consistent with the results of the RDA analysis.
+
+\newpage
+
+\begin{longtable}[H]{m{2.6cm}|m{7.3cm}|m{1cm}|m{1.4cm}|m{1.5cm}|m{1.5cm}}
+    \caption{Results of the fourth corner analysis, after accounting for multiple samplings per year, with the original dataset, harmonised (not aggregated), and aggregated trait datasets.}
+    \label{stab:fc_selected_reduced}
+    \endfirsthead
+    \toprule[.1em]
+    Dataset & Test & Obs & Std.Obs & Pvalue & Pvalue.adj \\ 
+    \toprule[.1em]
+      stepw\_median & cond / feed\_shredder & 0.39 & 1.75 & 0.08 & 0.246 \\ 
+      stepw\_median & cond / resp\_gil & 0.47 & 1.81 & 0.06 & 0.224 \\ 
+      stepw\_median & cond / volt\_uni & -0.56 & -2.15 & 0.01 & 0.05 * \\ 
+      stepw\_median & cond / volt\_bi\_multi & 0.56 & 2.19 & 0.01 & 0.048 * \\ 
+      stepw\_median & cond / ovip\_aqu & -0.53 & -2.16 & 0.01 & 0.045 * \\ 
+      stepw\_median & cond / ovip\_ovo & 0.54 & 2.17 & 0.01 & 0.045 * \\ 
+      stepw\_median & cond / Life cycle duration $<=$ 1 year & -0.32 & -1.23 & 0.26 & 0.518 \\ 
+      stepw\_median & cond / Life cycle duration $>$ 1 year & 0.32 & 1.23 & 0.26 & 0.518 \\
+      \midrule 
+      stepw\_mean & cond / feed\_shredder & 0.39 & 1.80 & 0.06 & 0.2 \\ 
+      stepw\_mean & cond / resp\_gil & 0.47 & 1.84 & 0.05 & 0.2 \\ 
+      stepw\_mean & cond / volt\_uni & -0.56 & -2.26 & 0.01 & 0.042 * \\ 
+      stepw\_mean & cond / volt\_bi\_multi & 0.57 & 2.26 & 0.01 & 0.042 * \\ 
+      stepw\_mean & cond / ovip\_aqu & -0.53 & -2.21 & 0.01 & 0.05 * \\ 
+      stepw\_mean & cond / ovip\_ovo & 0.54 & 2.22 & 0.01 & 0.05 * \\ 
+      stepw\_mean & cond / Life cycle duration $<=$ 1 year & -0.33 & -1.31 & 0.21 & 0.426 \\ 
+      stepw\_mean & cond / Life cycle duration $>$ 1 year & 0.33 & 1.31 & 0.21 & 0.426 \\ 
+      \midrule
+      direct\_median & cond / feed\_shredder & 0.38 & 1.73 & 0.09 & 0.27 \\ 
+      direct\_median & cond / resp\_gil & 0.47 & 1.82 & 0.05 & 0.216 \\ 
+      direct\_median & cond / volt\_uni & -0.56 & -2.25 & 0.01 & 0.035 * \\ 
+      direct\_median & cond / volt\_bi\_multi & 0.57 & 2.28 & 0.00 & 0.032 * \\ 
+      direct\_median & cond / ovip\_aqu & -0.53 & -2.27 & 0.02 & 0.055 . \\ 
+      direct\_median & cond / ovip\_ovo & 0.54 & 2.28 & 0.01 & 0.055 . \\ 
+      direct\_median & cond / Life cycle duration $<=$ 1 year & -0.34 & -1.38 & 0.20 & 0.39 \\ 
+      direct\_median & cond / Life cycle duration $>$ 1 year & 0.34 & 1.38 & 0.20 & 0.39 \\ 
+      \midrule
+      direct\_mean & cond / feed\_shredder & 0.38 & 1.78 & 0.07 & 0.225 \\ 
+      direct\_mean & cond / resp\_gil & 0.47 & 1.92 & 0.04 & 0.152 \\ 
+      direct\_mean & cond / volt\_uni & -0.56 & -2.22 & 0.01 & 0.04 * \\ 
+      direct\_mean & cond / volt\_bi\_multi & 0.57 & 2.26 & 0.01 & 0.04 * \\ 
+      direct\_mean & cond / ovip\_aqu & -0.53 & -2.33 & 0.01 & 0.045 * \\ 
+      direct\_mean & cond / ovip\_ovo & 0.54 & 2.20 & 0.01 & 0.042 * \\ 
+      direct\_mean & cond / Life cycle duration $<=$ 1 year & -0.34 & -1.42 & 0.17 & 0.342 \\ 
+      direct\_mean & cond / Life cycle duration $>$ 1 year & 0.34 & 1.42 & 0.17 & 0.342 \\
+      \midrule 
+      weighted & cond / feed\_shredder & 0.38 & 1.69 & 0.09 & 0.261 \\ 
+      weighted & cond / resp\_gil & 0.47 & 1.90 & 0.04 & 0.156 \\ 
+      weighted & cond / volt\_uni & -0.56 & -2.23 & 0.01 & 0.03 * \\ 
+      weighted & cond / volt\_bi\_multi & 0.57 & 2.46 & 0.00 & 0.024 * \\ 
+      weighted & cond / ovip\_aqu & -0.53 & -2.19 & 0.01 & 0.055 . \\ 
+      weighted & cond / ovip\_ovo & 0.54 & 2.20 & 0.01 & 0.055 . \\ 
+      weighted & cond / Life cycle duration $<=$ 1 year & -0.34 & -1.34 & 0.21 & 0.414 \\ 
+      weighted & cond / Life cycle duration $>$ 1 year & 0.34 & 1.34 & 0.21 & 0.414 \\
+      \midrule 
+      not\_aggregated & cond / feed\_shredder & 0.41 & 1.83 & 0.05 & 0.188 \\ 
+      not\_aggregated & cond / resp\_gil & 0.47 & 1.88 & 0.05 & 0.188 \\ 
+      not\_aggregated & cond / volt\_uni & -0.57 & -2.16 & 0.01 & 0.035 * \\ 
+      not\_aggregated & cond / volt\_bi\_multi & 0.58 & 2.21 & 0.00 & 0.024 * \\ 
+      not\_aggregated & cond / ovip\_aqu & -0.55 & -2.24 & 0.01 & 0.045 * \\ 
+      not\_aggregated & cond / ovip\_ovo & 0.55 & 2.25 & 0.01 & 0.045 * \\ 
+      not\_aggregated & cond / Life cycle duration $<=$ 1 year & -0.33 & -1.25 & 0.22 & 0.446 \\ 
+      not\_aggregated & cond / Life cycle duration $>$ 1 year & 0.33 & 1.25 & 0.22 & 0.446 \\
+      \midrule 
+      original & cond / Feeding habits shredder & 0.54 & 2.19 & 0.01 & 0.077 . \\
+      original & cond / Respiration gill & 0.47 & 1.83 & 0.05 & 0.255 \\ 
+      original & cond / Potential number of cycles per year 1 & -0.48 & -1.83 & 0.05 & 0.255 \\ 
+      original & cond / Potential number of cycles per year $>$ 1 & 0.49 & 1.91 & 0.04 & 0.222 \\
+      original & cond / Reproduction ovoviviparity & 0.58 & 2.39 & 0.01 & 0.042 * \\ 
+      original & cond / Reproduction clutches, cemented or fixed & -0.33 & -1.27 & 0.23 & 0.612 \\
+      original & cond / Life cycle duration $<=$ 1 year & -0.33 & -1.31 & 0.20 & 0.612 \\ 
+      original & cond / Life cycle duration $>$ 1 year & 0.33 & 1.31 & 0.20 & 0.612 \\          
+      \bottomrule
+\end{longtable}
+
+\begin{longtable}[H]{m{2.6cm}|m{7.3cm}|m{1cm}|m{1.4cm}|m{1.5cm}|m{1.5cm}}
+    \caption{Results of the fourth corner analysis without accounting for multiple samplings per year, with the original dataset, harmonised, and aggregated trait datasets.}
+    \label{stab:fc_selected_full}
+    \endfirsthead
+    \toprule[.1em]
+    Dataset & Test & Obs & Std.Obs & Pvalue & Pvalue.adj \\ 
+    \toprule[.1em]
+      stepw\_median & cond / feed\_shredder & 0.33 & 1.68 & 0.08 & 0.24 \\ 
+      stepw\_median & cond / resp\_gil & 0.39 & 1.79 & 0.06 & 0.24 \\ 
+      stepw\_median & cond / volt\_uni & -0.52 & -2.41 & 0.00 & 0.028 * \\ 
+      stepw\_median & cond / volt\_bi\_multi & 0.53 & 2.50 & 0.00 & 0.024 * \\ 
+      stepw\_median & cond / ovip\_aqu & -0.46 & -2.44 & 0.01 & 0.065 . \\ 
+      stepw\_median & cond / ovip\_ovo & 0.46 & 2.75 & 0.01 & 0.06 . \\ 
+      stepw\_median & cond / Life cycle duration $<=$ 1 year & -0.28 & -1.26 & 0.22 & 0.446 \\ 
+      stepw\_median & cond / Life cycle duration $>$ 1 year & 0.28 & 1.26 & 0.22 & 0.446 \\ 
+      \midrule
+      stepw\_mean & cond / feed\_shredder & 0.33 & 1.81 & 0.05 & 0.216 \\ 
+      stepw\_mean & cond / resp\_gil & 0.39 & 1.74 & 0.07 & 0.216 \\ 
+      stepw\_mean & cond / volt\_uni & -0.53 & -2.46 & 0.00 & 0.021 * \\ 
+      stepw\_mean & cond / volt\_bi\_multi & 0.53 & 2.56 & 0.00 & 0.016 * \\ 
+      stepw\_mean & cond / ovip\_aqu & -0.46 & -2.35 & 0.01 & 0.045 * \\ 
+      stepw\_mean & cond / ovip\_ovo & 0.46 & 2.58 & 0.01 & 0.042 * \\ 
+      stepw\_mean & cond / Life cycle duration $<=$ 1 year & -0.28 & -1.34 & 0.21 & 0.412 \\ 
+      stepw\_mean & cond / Life cycle duration $>$ 1 year & 0.28 & 1.34 & 0.21 & 0.412 \\
+      \midrule 
+      direct\_median & cond / feed\_shredder & 0.32 & 1.81 & 0.06 & 0.236 \\ 
+      direct\_median & cond / resp\_gil & 0.39 & 1.81 & 0.06 & 0.236 \\ 
+      direct\_median & cond / volt\_uni & -0.53 & -3.59 & 0.00 & 0.008 ** \\ 
+      direct\_median & cond / volt\_bi\_multi & 0.54 & 3.65 & 0.00 & 0.008 ** \\ 
+      direct\_median & cond / ovip\_aqu & -0.46 & -2.34 & 0.01 & 0.06 . \\ 
+      direct\_median & cond / ovip\_ovo & 0.46 & 2.58 & 0.00 & 0.024 * \\ 
+      direct\_median & cond / Life cycle duration $<=$ 1 year & -0.30 & -1.42 & 0.18 & 0.37 \\ 
+      direct\_median & cond / Life cycle duration $>$ 1 year & 0.30 & 1.42 & 0.18 & 0.37 \\
+      \midrule 
+      direct\_mean & cond / feed\_shredder & 0.32 & 1.67 & 0.09 & 0.27 \\ 
+      direct\_mean & cond / resp\_gil & 0.39 & 1.82 & 0.06 & 0.228 \\ 
+      direct\_mean & cond / volt\_uni & -0.53 & -3.54 & 0.00 & 0.008 ** \\ 
+      direct\_mean & cond / volt\_bi\_multi & 0.54 & 2.62 & 0.00 & 0.014 * \\ 
+      direct\_mean & cond / ovip\_aqu & -0.46 & -2.39 & 0.01 & 0.03 * \\ 
+      direct\_mean & cond / ovip\_ovo & 0.46 & 2.67 & 0.00 & 0.014 * \\ 
+      direct\_mean & cond / Life cycle duration $<=$ 1 year & -0.30 & -1.43 & 0.17 & 0.332 \\ 
+      direct\_mean & cond / Life cycle duration $>$ 1 year & 0.30 & 1.43 & 0.17 & 0.332 \\
+      \midrule 
+      weighted & cond / feed\_shredder & 0.32 & 1.69 & 0.09 & 0.268 \\ 
+      weighted & cond / resp\_gil & 0.39 & 1.77 & 0.07 & 0.268 \\ 
+      weighted & cond / volt\_uni & -0.53 & -3.57 & 0.00 & 0.008 ** \\ 
+      weighted & cond / volt\_bi\_multi & 0.54 & 3.63 & 0.00 & 0.008 ** \\ 
+      weighted & cond / ovip\_aqu & -0.46 & -2.37 & 0.00 & 0.012 * \\ 
+      weighted & cond / ovip\_ovo & 0.46 & 2.61 & 0.00 & 0.015 * \\ 
+      weighted & cond / Life cycle duration $<=$ 1 year & -0.30 & -1.40 & 0.20 & 0.398 \\ 
+      weighted & cond / Life cycle duration $>$ 1 year & 0.30 & 1.40 & 0.20 & 0.398 \\
+      \midrule 
+      not\_aggregated & cond / feed\_shredder & 0.35 & 1.82 & 0.06 & 0.236 \\ 
+      not\_aggregated & cond / resp\_gil & 0.38 & 1.76 & 0.07 & 0.236 \\ 
+      not\_aggregated & cond / volt\_uni & -0.53 & -3.80 & 0.00 & 0.008 ** \\ 
+      not\_aggregated & cond / volt\_bi\_multi & 0.54 & 3.87 & 0.00 & 0.008 ** \\ 
+      not\_aggregated & cond / ovip\_aqu & -0.47 & -2.37 & 0.01 & 0.03 * \\ 
+      not\_aggregated & cond / ovip\_ovo & 0.48 & 2.72 & 0.00 & 0.024 * \\ 
+      not\_aggregated & cond / Life cycle duration $<=$ 1 year & -0.29 & -1.40 & 0.19 & 0.372 \\ 
+      not\_aggregated & cond / Life cycle duration $>$ 1 year & 0.29 & 1.40 & 0.19 & 0.372 \\
+      \midrule 
+      original & cond / Feeding habits shredder & 0.45 & 2.17 & 0.01 & 0.042 * \\
+      original & cond / Respiration gill & 0.38 & 1.80 & 0.06 & 0.252 \\  
+      original & cond / Potential number of cycles per year 1 & -0.47 & -2.23 & 0.01 & 0.042 * \\ 
+      original & cond / Potential number of cycles per year $>$ 1 & 0.47 & 2.26 & 0.01 & 0.042 * \\ 
+      original & cond / Reproduction ovoviviparity & 0.51 & 2.89 & 0.00 & 0.016 * \\ 
+      original & cond / Reproduction clutches, cemented or fixed & -0.34 & -1.58 & 0.13 & 0.402 \\  
+      original & cond / Life cycle duration $<=$ 1 year & -0.29 & -1.41 & 0.18 & 0.402 \\ 
+      original & cond / Life cycle duration $>$ 1 year & 0.29 & 1.41 & 0.18 & 0.402 \\
+      \bottomrule
+\end{longtable}
+
+\newpage
 

### 2022-03-26 Paper/Submission_new/Main_Document-Latex.tex
26.03: Updated paper files, most recent in Submission_new

@@
 \documentclass[12pt]{article} 
+%\usepackage[a4paper, margin = 1n]{geometry}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{lmodern}
+\usepackage{fancyhdr}
 \usepackage[
@@
 
-% raplace "and" in authoryear in-text citations with "&" 
+% replace "and" in authoryear in-text citations with "&" 
 \renewcommand*{\finalnamedelim}{%
@@
 
+% custom style for first page
+\fancypagestyle{firstpage}
+{
+    \fancyhead[L]{Data-related issues in trait databases}    
+    \fancyhead[R]{}
+}
+
 \myexternaldocument{Latex_Supplementary_File}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
+\thispagestyle{firstpage}
+\title{Tackling inconsistencies among freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution}
 \author[1]{Stefan Kunz}
@@
 1.
-Use of invertebrate traits rather than species composition may facilitate large-scale comparisons of community structure and responses to disturbance in freshwater ecology because the same traits can potentially occur everywhere.
+Use of invertebrate traits rather than species composition may facilitate large-scale comparisons of community structure and responses to disturbance in freshwater ecology because the same traits potentially occur everywhere.
 In recent years, comprehensive invertebrate trait databases have been established at different scales (e.g.
 regions, continents).
-The wide availability of invertebrate trait data supports trait-based studies, especially at large scales.
+The wide availability of invertebrate trait data supports large scale studies.
 However, a number of data-related issues complicate the use of invertebrate traits for ecological studies.
-For example, standardised definitions for freshwater invertebrate traits are lacking, which impedes comparisons across regions.
-Moreover, it is uncertain how harmonising varying trait definitions among databases might influence identification of trait-environment relationships.
-In addition, taxonomic resolution between taxonomic composition data and trait data can differ, making aggregation of traits necessary.
-However, at present, it is unknown how different trait aggregation approaches compare with expert-assigned trait affinities.
-% In this study we aimed to identify discrepancies in trait definitions across freshwater invertebrate databases and to compare trait aggregation methods to identify how phylogenetic structure and trait variability influence results from different aggregation methods.
+It is uncertain how harmonising varying trait definitions among databases might influence subsequent identification of trait-environment relationships.
+Furthermore, there have been few comparisons of trait aggregation approaches with expert-assigned trait affinities.
 
 2.
-We describe discrepancies in the definitions of traits used to create freshwater invertebrate trait databases in Europe, North America, New Zealand, and Australia.
-Based on our comparisons of these trait databases, we established four novel trait datasets by harmonising trait definitions of commonly used traits.
+We describe inconsistencies in the definitions of traits used to create freshwater invertebrate trait databases in Europe, North America, New Zealand, and Australia.
+Based on our comparisons of these databases, we established four novel trait datasets by harmonising definitions of commonly used traits.
 Next, we used two of these datasets to compare aggregated traits obtained by different aggregation methods with traits assigned by experts, both at the family level.
@@
 3.
-We found that among trait databases, trait definitions often differed because varying numbers of traits were used to describe groups of related traits (e.g., respiration traits) and the focus of descriptions for groups of related traits also varied (e.g., for feeding mode some databases focused on the food source, whereas others focused on mouthpart morphology).
+We found that among databases, trait definitions often differed because varying numbers of traits were used to describe particular functions (e.g., respiration traits) and the way those functions were described also varied (e.g., for feeding mode some databases focused on the food source, whereas others focused on mouthpart morphology).
 The coding to describe traits (binary, fuzzy) also varied among databases.
-Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially when aggregation was based on the median.
-% ,and that trait coding method, uneven phylogenetic structure, and high trait variability can influence aggregated trait affinities. 
-We further showed that harmonised and aggregated data performed similarly to non-aggregated and harmonised data from the case study in identifying trait–environment relationships, but were only partially able to yield similar values for functional diversity metrics in the case study.
 
 4.
-By identifying discrepancies in trait definitions we hope to motivate the development of standardised definitions for invertebrate traits.
+Our comparison of different aggregation methods showed that family-level aggregated and expert-assigned traits were similar, especially when traits were aggregated based on the median of trait values of taxa within a family.
+% ,and that trait coding method, uneven phylogenetic structure, and high trait variability can influence aggregated trait affinities. 
+% We further showed that harmonised and aggregated data performed similarly to non-aggregated and harmonised data from the case study in identifying trait–environment relationships, but were only partially able to yield similar values for functional diversity metrics in the case study.
+The case study showed that harmonised and aggregated data identified similar trait-environment relationships to non-aggregated data.
+However, harmonised and aggregated data yielded only partially similar values for functional diversity metrics when compared to the case study results.
+
+5.
+By identifying inconsistencies in trait definitions we hope to motivate the development of standardised definitions for invertebrate traits.
 Our results also illustrate the usefulness of harmonised datasets for ecological study and provide guidance for the circumstances under which the choice of trait aggregation method is important.
@@
 Explaining and predicting how communities are shaped by environmental factors is a primary goal of ecology.
-Species traits are measurable properties of an organism (\cite{mcgill_rebuilding_2006}), and comparing communities based on the traits possessed by species may facilitate testing of a range of ecological hypotheses (\cite{statzner_perspectives_2001}).
+Species traits are measurable properties of an organism that strongly influence individual performance (\cite{mcgill_rebuilding_2006}), and comparing communities based on the traits possessed by species may facilitate testing of a range of ecological hypotheses (\cite{statzner_perspectives_2001}).
 Traits are assumed to be adaptations (e.g., physiological, behavioural) of organisms to their environment, which represent either direct or indirect linkages between the biological response of an organism or a population and its environment (\cite{southwood_habitat_1977, verberk_delivering_2013}).
@@
 The availability of invertebrate trait data from different continents enables comparisons of regional trait variation and allows for testing the consistency of trait structure–environmental factor relationships across both small and large spatial extents.
-In fact, the first studies on the link between habitat utilization and traits in the Upper Rhône river initiated the compilation of aquatic invertebrate trait information (\cite{bournaudApproachSynthesisQualitative1992,usseglio-polateraTheoreticalHabitatTemplets1994}).
+In fact, the first studies on the link between habitat use and traits in the Upper Rhône river initiated the compilation of aquatic invertebrate trait information (\cite{bournaudApproachSynthesisQualitative1992,usseglio-polateraTheoreticalHabitatTemplets1994}).
 At large scales, consistent responses of traits to environmental stressors have been reported, e.g.
@@
 
-Finally, discrepancies in the taxonomic resolutions (e.g., species, genus, or family) used when comparing among trait databases, or when linking observed taxonomic data to trait databases, presents another challenge (\cite{gayraudInvertebrateTraitsBiomonitoring2003, doledecAccurateDescriptionAbundance2000}).
+Finally, differences in the taxonomic resolutions (e.g., species, genus, or family) used when comparing among trait databases, or when linking observed taxonomic data to trait databases, presents another challenge (\cite{gayraudInvertebrateTraitsBiomonitoring2003, doledecAccurateDescriptionAbundance2000}).
 When taxonomic composition or data in a trait database are at a more precise taxonomic level than other trait data (e.g.
@@
 These challenges motivated us to assess the characteristics and comparability of different freshwater invertebrate trait databases with the goal of facilitating future syntheses.
-We aimed to identify methods of improving the comparability of trait data across databases, despite differences in trait definitions and the taxonomic level of data in three ways: (1) by describing discrepancies in trait definitions between trait databases from Europe, North America, Australia, and New Zealand; (2) by harmonising trait definitions across databases to provide consistent grouping features for comparison across geographic locations; and (3) by comparing the influence of different trait aggregation methods and grouping-feature harmonisation on the detection of trait–environment relationships.
+We aimed to identify methods of improving the comparability of trait data across databases, despite differences in trait definitions and the taxonomic level of data in three ways: (1) by describing inconsistencies in trait definitions between trait databases from Europe, North America, Australia, and New Zealand; (2) by harmonising trait definitions across databases to provide consistent grouping features for comparison across geographic locations; and (3) by comparing the influence of different trait aggregation methods and grouping-feature harmonisation on the detection of trait–environment relationships.
 
@@
 To address our study objectives, we took a multi-prong approach to describing, combining, and assessing multiple sources of freshwater invertebrate data that differed in grouping-feature definitions and taxonomic resolution.
-Discrepancies in trait definitions served as a starting point to develop four novel invertebrate trait datasets by harmonising seven grouping features present in the existing trait databases.
+Inconsistencies in trait definitions served as a starting point to develop four novel invertebrate trait datasets by harmonising seven grouping features present in the existing trait databases.
 The harmonised trait datasets were used to evaluate the influence of different trait aggregation methods on the identification of trait–environment relationships, our third study objective, in two ways by (1) comparing family-level aggregated trait affinities with family-level trait affinities assigned by experts for two of the established trait datasets where such data were available and (2) comparing the influence of phylogenetic structure and trait variability on the outcomes of the different trait aggregation approaches for simulated data.
@@
 A criterion for trait selection was that the traits occurred in all databases, to allow for an analysis of potential differences in trait definitions and of the influence of grouping-feature harmonisation on trait-environment relationships.
-Thus, we only used biological traits and omitted ecological traits that describe habitat preferences (e.g.
+Thus, we only used biological traits, i.e.
+traits describing survival ability in an environment (\cite{violleLetConceptTrait2007}), and omitted ecological traits that describe habitat preferences (e.g.
 temperature preference) because these traits are missing in the New Zealand trait database.
@@
 
-\begin{figure}
-  \centering
-  \subfile{Flowchart/Flowchart_methods.tex}
-\end{figure}
-\newpage
-\begin{center}
-\captionof{figure}{Data processing steps of the selected traits.
-Intermediate (grey) and main (orange) steps of data preparation are depicted.
-The dashed bottom box illustrates the different trait aggregation methods (hypothetical data in the upper left corner).
-The aggregation methods (purple) and intermediate steps of the aggregation methods (pink) are displayed.
-Abbreviations: EU, Europe; NOA, North America; AUS, Australia; NZ, New Zealand.}
-\label{fig:data_proc_overview}
-\end{center}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-All data processing and RDA analyses were carried out using R version 3.6.1 (\cite{cite_R}).
-RDA was computed using the vegan package (\cite{cite_vegan}).
-Raw data and the R code for data processing and grouping feature harmonisation are located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
-Scripts and data to reproduce the trait aggregation, comparison of aggregated and assigned traits, and the RDA analysis are located in the Github repository: \url{https://github.com/KunzstLD/Trait-aggregation}.
+All data processing, RDA analyses, and FD analysis were carried out using R version 3.6.1 (\cite{cite_R}).
+RDA was computed using the vegan package (\cite{cite_vegan}) and FD metrics were calculated with the FD package (\cite{cite_FD}).
 
@@
 
-\subsubsection*{Discrepancies in invertebrate trait definitions across databases}
+\subsubsection*{Inconsistencies in invertebrate trait definitions across databases}
 
@@
 
-The definitions of grouping features also varied across databases in their differentiation into traits and in their focus, both which can lead to discrepancies in trait definitions (see Table \ref{tab:trait_definitions} and Table \ref{stab:trait_definitions} for a summary of discrepancies in trait definitions).
+The definitions of grouping features also varied across databases in their differentiation into traits and in their focus, both which can lead to inconsistencies in trait definitions (see Table \ref{tab:trait_definitions} and Table \ref{stab:trait_definitions} for a summary of inconsistencies in trait definitions).
 Varying levels of differentiation among the trait databases were present in all investigated grouping features (Table \ref{tab:trait_definitions}, Table \ref{tab:trait_databases_coding_differentiation}, and Table \ref{stab:trait_definitions}).
 
-For example, for the grouping feature feeding mode, discrepancies arose because traits were assigned in different ways.
+For example, for the grouping feature feeding mode, inconsistencies arose because traits were assigned in different ways.
 The Tachet database defined predators as carvers, engulfers, and swallowers.
@@
 
-The percentage of differing cases of aggregated versus assigned trait affinities varied by method between 21.9 and 27.6 \% for the Australian dataset and between 15.5 and 44.8 \% for the North American dataset (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
+The percentage of differing cases of aggregated versus assigned trait affinities varied by method between 16.7 and 23.4 \% for the Australian dataset and between 15.6 and 44.9 \% for the North American dataset (Table \ref{tab:summary_stat_aggr_vs_fam_assigned}).
 In general, median aggregation methods yielded fewer cases with differences compared with mean aggregation methods.
@@
 Maximum differences of 1 (i.e., the maximum possible difference) occurred for all investigated grouping features in both datasets (Figure \ref{fig:diff_aggr_traits_combined}).
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=16.5cm, height=12cm]{Deviances_trait_agg_combined.png}
-  \caption{Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the Australian and North American dataset.
-Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the grouping features feeding mode and body size.
-Results for the North American dataset for the grouping features locomotion, respiration, and voltinism are shown in the supporting information (Figure \ref{fig:diff_aggr_traits_pyne}).
-Absolute differences in trait affinities are depicted as grey dots.
-\textit{n} denotes the number of cases per comparison where differences occurred.
-The blue dot indicates the mean of absolute differences, and the error bars show the standard deviation.
-The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.
-Abbreviations: AUS, Australia; NA, North America.}
-  \label{fig:diff_aggr_traits_combined}
-\end{figure}
 
@@
 RDA using harmonised, but not aggregated, grouping features identified some, but not all, of the same traits that were identified by the original analysis (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
-The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (higher salinity) were characterised by the traits: ovoviviparity, multivoltinism, long life-cycle duration ($> 1$ year), shredder, and gill respiration, whereas RDA with the harmonised data identified the first three traits but did not include shredder or gill respiration traits.
-The original RDA indicated that upstream sites (lower salinity) were characterised by the traits: univoltinism, oviposition in clutches, and short life-cycle duration ($< 1$ year), and RDA with the harmonised data characterised upstream sites by univoltine taxa with short life-cycle durations that lay their eggs in an aquatic environment (aquatic eggs).
+The original RDA in \citet{szocs_effects_2014} indicated that downstream sites (higher salinity) were characterised by the traits: ovoviviparity, multivoltinism, shredder, long life-cycle duration ($> 1$ year), and gill respiration, whereas RDA with the harmonised data identified the first three traits but did not include long life-cycle duration ($> 1$ year) or gill respiration traits.
+The original RDA indicated that upstream sites (lower salinity) were characterised by the traits: univoltinism, oviposition in clutches, and short life-cycle duration ($< 1$ year), and RDA with the harmonised data characterised upstream sites by univoltine taxa that lay their eggs in an aquatic environment (aquatic eggs).
 This difference in the oviposition trait is not substantial because the trait aquatic eggs of the harmonised grouping feature oviposition was derived by combining the trait oviposition in clutches and other related traits (Table \ref{tab:traits_harmonisation}).
@@
 RDA based on harmonised traits that were aggregated to family level also produced results similar to the original analysis but with fewer traits distinguishing upstream and downstream sites (Figures \ref{fig:violin_plot_species_sc} and \ref{fig:boxplot_scores_on_constrained_axis}).
-The \textit{direct\_agg\textsubscript{mean}}, \textit{direct\_agg\textsubscript{median}}, and \textit{weighted\_agg} characterised the downstream sites with the same traits as the original analysis except the trait shredder.
-As for the RDA with harmonised but not aggregated data, RDA with these three aggregation methods characterised upstream sites by the traits univoltinism, short life-cycle duration, and aquatic eggs.
-The \textit{stepwise\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}} methods produced the same results except that none of the life-cycle traits characterised upstream or downstream sites.
-Thus, compared with the original study’s findings, aggregating by the direct and weighted methods yielded less change than the stepwise methods in interpretation of the RDA results.
-Given the criticism of approaches relying on CWM traits we also applied fourth corner analysis with the original, harmonised, and aggregated trait datasets to detect relationships between traits and conductivity (methods and results in the supporting information \ref{sec:effects_harmonisation_trait_env_rel}).
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
-    \caption{Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonised grouping features, and using harmonised grouping features with traits aggregated to family level with five different aggregation methods.
-The dots represent the individual species scores for each analysed trait along the conductivity axis.
-The violin plot shows the density estimate of the species scores.
-Grey vertical lines indicate the median of the obtained species scores.}
-    \label{fig:violin_plot_species_sc}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=17cm, height=14.5cm]{boxplot_scores_combined.png}
-\end{figure}
-\begin{center}
-\captionof{figure}{RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{median}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
-Shown are boxplots of the site scores along the conductivity axis.
-The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
-Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
-For better comparability, species scores of the original analysis were multiplied by -1.
-Results for the other aggregated methods are shown in the supporting information (Figure \ref{fig:boxplots_scores_on_constrained_axis_REMAIN}).
-Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.}
-\label{fig:boxplot_scores_on_constrained_axis}
-\end{center}
+The \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}}, and \textit{weighted\_agg} characterised the downstream sites with the same traits as the original analysis except the trait life cycle duration $> 1$ year.
+As for the RDA with harmonised but not aggregated data, RDA with the five aggregation methods characterised upstream sites by the traits univoltinism and aquatic eggs.
+The \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}} methods produced the same results as the harmonised but not aggregated data.
+Thus, compared with the original study’s findings, aggregating by the mean and weighted methods yielded less change than the aggregation with the median in interpretation of the RDA results.
+Given the criticism of approaches relying on CWM traits we also applied fourth corner analysis with the original, harmonised, and aggregated trait datasets to detect relationships between traits and conductivity (methods and results in the Supplementary Materials).
 
 The calculation of FD metrics for the original, harmonised (not aggregated), and aggregated datasets suggested that harmonising trait data preserves FRic and FDiv values, whereas aggregated trait data only preserved FRic values.
-The FRic and FDiv values calculated from harmonised trait data correlated highly to FRic and FDiv values from the original dataset ($R^2 = 0.96$ and $0.86$, respectively).
-FRic and FDiv calculated for aggregated trait data showed moderate to high correlations to the FRic and FDiv values calculated with the original dataset (FRic: $0.78 <= R^2 <= 0.84$ , FDiv: $0.42 <= R^2 <= 0.62$, Figure \ref{fig:FRic} and \ref{fig:FDiv}).
-By contrast, FEve values calculated with harmonised and aggregated trait data were unrelated to the FEve values calculated with the original dataset (all $R^2 < 0.1$), except for \textit{stepwise\_agg \textsubscript{median}}, which showed a moderate correlation to FEve values calculated from the original dataset ($R^2  = 0.48$, Figure \ref{fig:FEve}).
+The FRic and FDiv values calculated from harmonised trait data correlated highly to FRic and FDiv values from the original dataset ($R^2 = 0.96$ and $0.88$, respectively).
+FRic and FDiv calculated for aggregated trait data showed moderate to high correlations to the FRic and FDiv values calculated with the original dataset (FRic: $0.78 <= R^2 <= 0.85$ , FDiv: $0.49 <= R^2 <= 0.6$, Figure \ref{fig:FRic} and \ref{fig:FDiv}).
+By contrast, FEve values calculated with harmonised and aggregated trait data were unrelated to the FEve values calculated with the original dataset (all $R^2 <= 0.05$).
 
@@
 
-Freshwater invertebrate trait databases are a valuable source of data that are freely available to researchers and that can offer opportunities for large-scale, cross-regional ecological study without the need for time-consuming and expensive field work.
+Freshwater invertebrate trait databases are a valuable source of data that are freely available to researchers and that can offer opportunities for large-scale, cross-regional study of some ecological questions.
 However, a lack of consistency among regional and continent-wide databases in trait definitions, trait affinity coding, and taxonomic resolution can greatly limit the use of combined databases.
 We explored the effects of harmonising grouping features and aggregating trait affinities at different taxonomic levels from databases from four different continents on the outcomes of trait affinities and on analysis of trait–environment relationships.
-We found that despite discrepancies in trait definitions and taxonomic resolution across databases, harmonised and aggregated data were generally effective in identifying trait–environmental relationships, as evidenced by similar results from RDA as were found using observational data.
-Our results have implications for future multi-regional ecological studies that may benefit from the use of existing databases and provide insight into methods for harmonising traits with differing trait definitions and selecting aggregation methods that minimize either cases or ranges of differences in trait affinity scores when aggregating from higher to lower taxonomic precision.
+We found that despite inconsistencies in trait definitions and taxonomic resolution across databases, harmonised and aggregated data were generally effective in identifying trait–environmental relationships, as shown by the similarity of results from RDA and observational data.
+Future multi-regional ecological studies may benefit from the use of existing databases and our study provides insight into methods for harmonising traits when trait definitions differ and for selecting aggregation methods that minimize either cases or ranges of differences in trait affinity scores when aggregating from higher to lower taxonomic precision.
 
@@
 Synthesising trait information from multiple trait databases is crucial for developing the full potential of trait-based approaches, such as for studying community trait responses to environmental gradients across geographic regions.
-Others have noted the lack of standardised trait terminology in freshwater ecology (\cite{baird_toward_2011, brink_traits-based_2011}), but in this study we show for the first time the discrepancies that exist across some commonly used grouping features.
+Others have noted the lack of standardised trait terminology in freshwater ecology (\cite{baird_toward_2011, brink_traits-based_2011}), but in this study we show for the first time the inconsistencies that exist across some commonly used grouping features.
 Furthermore, we offer insight into the need for, and process of, harmonising invertebrate trait information from trait databases of different regions.
 Some of the challenges we found were that grouping features were resolved differently into traits in different databases and that various codings (fuzzy, categorical, binary) were used to describe traits.
-In addition, the same traits were sometimes defined differently, requiring expert knowledge to reclassify these traits (e.g.
+In addition, the same traits were sometimes defined differently, requiring expert knowledge to reclassify them (e.g.
 the trait piercer).
@@
 
-To resolve definition discrepancies and facilitate data synthesis in the future, terminological standards are needed.
+To resolve inconsistencies in trait definitions and facilitate data synthesis in the future, standards are needed for trait terminology.
 Harmonised definitions and concepts of traits have been developed in the past for other organism groups, such as for plants with the \textit{Thesaurus of Plant Characteristics} (TOP) initiative (\cite{garnier_towards_2017}).
@@
 Our re-analysis of the data on salinisation effects on biological traits yielded only slightly different results compared with the original study, which agrees with previous findings that family-level traits can be sensitive enough to detect environmental impacts (\cite{beketov_spear_2009}).
-However, some of the traits that had responded in the original analysis did not respond in the re-analysis, specifically feeding mode shredder, respiration gills, and life-cycle duration traits.
-There are several possible reasons for these discrepancies.
-The non-responsive traits were those closest to the threshold for association with either higher or lower salinity, and so the precision lost through trait harmonisation may have decreased our ability to detect a relatively weak association.
-The shredder feeding mode was the only trait that was non-responsive when using harmonised (but not aggregated) data as well as when using aggregated data.
-This result was likely because of the harmonisation procedure, in which this trait was combined based on three traits (miner, xylophagus, and shredder) used in the original databases.
-Consequently, the trait affinities in the original data had a higher mean and standard deviation than in the harmonised and aggregated data (Table \ref{tab:SI_resp_traits_summary_stats}), suggesting that the signal in the original data was weakened by harmonisation.
+However, some of the traits that had responded in the original analysis did not respond in the re-analysis, specifically gill respiration and life-cycle duration traits.
+A reason for this discrepancy is that the non-responsive traits were close to the threshold we chose for association with either higher or lower salinity, and hence the loss of precision during trait harmonisation may have decreased our ability to detect a difference for these traits.
 Given this result, we suggest that if harmonisation is necessary, harmonised and non-harmonised data, if available, should be compared, and possible averaging effects should be considered in further analyses.
@@
 
-Although comprehensive freshwater invertebrate trait databases have been developed for several regions in the past, data synthesis presents challenges because of discrepancies in trait definitions, coding of trait affinities, and taxonomic resolution.
-By providing an overview of discrepancies in definitions, we have set a starting point for the development of standardised trait definitions through which invertebrate trait databases can be linked.
+Although comprehensive freshwater invertebrate trait databases have been developed for several regions in the past, data synthesis presents challenges because of inconsistencies in trait definitions, coding of trait affinities, and taxonomic resolution.
+By providing an overview of inconsistencies in definitions, we have set a starting point for the development of standardised trait definitions through which invertebrate trait databases can be linked.
 Agreement on standard trait definitions and the subsequent development of ontologies are the next steps to facilitate trait-based analysis at large geographical scales.
@@
 
-Harmonised invertebrate trait datasets for Australia, Europe, North America and New Zealand are deposited in the Github repository: \url{https://github.com/KunzstLD/Trait-aggregation}.
+Raw data and the R code for data processing and grouping feature harmonisation are located in the Github repository: \url{https://github.com/KunzstLD/Invertebrate_traits}.
+Scripts and data to reproduce the trait aggregation, comparison of aggregated and assigned traits, RDA analysis, FD analysis, and harmonised invertebrate trait datasets for Australia, Europe, North America and New Zealand are located in the Github repository: \url{https://github.com/KunzstLD/Trait-aggregation}.
 
@@
 Bullet points indicate when several traits have been used to describe a morphological or behavioural property.
-The full version and further information can be found in the supporting information Table \ref{stab:trait_definitions}.}
+The full version and further information can be found in the Supplementary Materials Table \ref{stab:trait_definitions}.}
       \label{tab:trait_definitions}
@@
 \begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont
-      $\dagger$ Some of the feeding mode traits used in the Australian database were similar (e.g. trait \textit{Shredder}, \textit{Shredder, Detrivore}, and \textit{Collector, Shredder}).
+      $\dagger$ Some of the feeding mode traits used in the Australian database were similar (e.g. trait \textit{Shredder}; \textit{Shredder, Detrivore}; and \textit{Collector, Shredder}).
       \newline
@@
     \toprule[.1em]
-    \multirow{4}{*}{\specialcell{AUS}} & \specialcell{\textit{direct\_agg\textsubscript{median}}} & 21.93  & 0.07 & 1.00 & 0.69 & 0.32 \\ 
-    & \specialcell{\textit{direct\_agg\textsubscript{mean}}} & 27.61  & 0.01 & 1.00 & 0.54 & 0.32 \\ 
-    & \specialcell{\textit{stepwise\_agg\textsubscript{median}}} & 23.01 & 0.01 & 1.00 & 0.65 & 0.32 \\ 
-    & \specialcell{\textit{stepwise\_agg\textsubscript{mean}}} & 27.56  & $< 0.01$ & 1.00 & 0.54 & 0.32 \\ 
-    & \specialcell{\textit{weighted\_agg}} & 27.61  & $< 0.01$ & 1.00 & 0.55 & 0.32 \\ 
+    \multirow{4}{*}{\specialcell{AUS}} & \specialcell{\textit{direct\_agg\textsubscript{median}}} & 16.65 & 0.01 & 1.00 & 0.45 & 0.27 \\ 
+    & \specialcell{\textit{direct\_agg\textsubscript{mean}}} & 23.35 & 0.01 & 0.98 & 0.33 & 0.23 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{median}}} & 18.01 & 0.01 & 1.00 & 0.41 & 0.26 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{mean}}} & 23.35 & $< 0.01$ & 0.99 & 0.33 & 0.22 \\ 
+    & \specialcell{\textit{weighted\_agg}} & 23.35 & $< 0.01$ & 1.00 & 0.34 & 0.24 \\ 
     \midrule
-    \multirow{4}{*}{\specialcell{NA}} & \specialcell{\textit{direct\_agg\textsubscript{median}}} & 15.52 & 0.25 & 1.00 & 0.68 & 0.27 \\ 
-    & \specialcell{\textit{direct\_agg\textsubscript{mean}}} & 44.81 & $< 0.01$ & 1.00 & 0.31 & 0.26 \\ 
+    \multirow{4}{*}{\specialcell{NA}} & \specialcell{\textit{direct\_agg\textsubscript{median}}} & 15.58 & 0.25 & 1.00 & 0.68 & 0.27 \\ 
+    & \specialcell{\textit{direct\_agg\textsubscript{mean}}} & 44.87 & $< 0.01$ & 1.00 & 0.31 & 0.26 \\ 
     & \specialcell{\textit{stepwise\_agg\textsubscript{median}}} & 18.71 & 0.12 & 1.00 & 0.60 & 0.29 \\ 
-    & \specialcell{\textit{stepwise\_agg\textsubscript{mean}}} & 44.81 & $< 0.01$ & 1.00 & 0.31 & 0.27 \\ 
-    & \specialcell{\textit{weighted\_agg}} & 44.81 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
+    & \specialcell{\textit{stepwise\_agg\textsubscript{mean}}} & 44.87 & $< 0.01$ & 1.00 & 0.31 & 0.27 \\ 
+    & \specialcell{\textit{weighted\_agg}} & 44.87 & $< 0.01$ & 1.00 & 0.31 & 0.28 \\ 
     \bottomrule
@@
 \end{landscape}
+
+\section*{Figures}
+
+\begin{figure}
+  \centering
+  \subfile{Flowchart/Flowchart_methods.tex}
+\end{figure}
+\newpage
+\begin{center}
+\captionof{figure}{Data processing steps of the selected traits.
+Intermediate (grey) and main (orange) steps of data preparation are depicted.
+The dashed bottom box illustrates the different trait aggregation methods (hypothetical data in the upper left corner).
+The aggregation methods (purple) and intermediate steps of the aggregation methods (pink) are displayed.
+Abbreviations: EU, Europe; NOA, North America; AUS, Australia; NZ, New Zealand.}
+\label{fig:data_proc_overview}
+\end{center}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=16.5cm, height=12cm]{Deviances_trait_agg_combined.png}
+  \caption{Cases (factor combination of investigated families and traits) where differences occurred between aggregated traits and expert assigned traits at family level for the Australian and North American dataset.
+Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the grouping features feeding mode and body size.
+Results for the North American dataset for the grouping features locomotion, respiration, and voltinism are shown in the Supplementary Materials (Figure \ref{fig:diff_aggr_traits_pyne}).
+Absolute differences in trait affinities are depicted as grey dots.
+\textit{n} denotes the number of cases per comparison where differences occurred.
+The blue dot indicates the mean of absolute differences, and the error bars show the standard deviation.
+The grey vertical lines show the 25\textsuperscript{th}, 50\textsuperscript{th} and 75\textsuperscript{th} quantiles of the density estimate.
+Abbreviations: AUS, Australia; NA, North America.}
+  \label{fig:diff_aggr_traits_combined}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=16.5cm, height=10cm]{Species_scores_rda.png}
+  \caption{Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonised grouping features, and using harmonised grouping features with traits aggregated to family level with five different aggregation methods.
+The dots represent the individual species scores for each analysed trait along the conductivity axis.
+The violin plot shows the density estimate of the species scores.
+Grey vertical lines indicate the median of the obtained species scores.}
+  \label{fig:violin_plot_species_sc}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=17cm, height=14.5cm]{boxplot_scores_combined.png}
+\end{figure}
+\begin{center}
+\captionof{figure}{RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{mean}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
+Shown are boxplots of the site scores along the conductivity axis.
+The rug on the right side of each plot indicates species scores of the traits on the conductivity axis.
+Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled.
+For better comparability, species scores of the original analysis were multiplied by -1.
+Results for the other aggregated methods are shown in the Supplementary Materials (Figure \ref{fig:boxplots_scores_on_constrained_axis_REMAIN}).
+Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.}
+\label{fig:boxplot_scores_on_constrained_axis}
+\end{center}
 
@@
 Violin plots - mirrored density plots - show the density of the absolute trait affinity differences for the grouping features feeding mode and body size.
-Results for the North American dataset for the grouping features locomotion, respiration, and voltinism are shown in the supporting information (Figure \ref{fig:diff_aggr_traits_pyne}).
+Results for the North American dataset for the grouping features locomotion, respiration, and voltinism are shown in the Supplementary Materials (Figure \ref{fig:diff_aggr_traits_pyne}).
 Absolute differences in trait affinities are depicted as grey dots.
@@
 
-Ranges of aggregated trait affinities for the three examples of phylogenetic structures and simulated levels of trait variability.
-Shown are the results only for one simulated trait (T1).
-Similar results were obtained for the other simulated traits (Figure \ref{fig:overview_sim_results_T2_T3}).
-Boxplots depict results for 100 replicated simulations of each trait aggregation method.
-The boxplot depicts the median and encompasses the 25\textsuperscript{th} and 75\textsuperscript{th} percentile.
-Horizontal black lines depict the median.
-Whiskers extend to the largest and smallest value respectively no further than 1.5 $\times$ the inter-quartile range.
-Outliers beyond the end of the whiskers are plotted as grey dots.
-Trait aggregation methods are in order of least to greatest produced ranges to improve visual inspection.
-\\
-
-\noindent{\textbf{Figure caption 4:}}
-
-Comparison between the aggregated trait affinities produced by the different trait aggregation methods for every simulated dataset across all 3 simulated traits (5,000 comparisons per scenario).
-Results are shown for different levels of trait variability which is represented by the standard deviation (SD) of the simulated traits.
-Dots depict comparisons where absolute differences between aggregated trait affinities were greater than 0.1.
-Overall, there are 10 possible unique comparisons of which 7 produced absolute differences greater than 0.1.
-\newline
-  Comparisons: \newline
-  1) \textit{direct\_agg\textsubscript{median}} - \textit{stepwise\_agg\textsubscript{mean}} \newline
-  2) \textit{direct\_agg\textsubscript{median}} - \textit{weighted\_agg} \newline
-  3) \textit{stepwise\_agg\textsubscript{mean}} - \textit{stepwise\_agg\textsubscript{median}} \newline
-  4) \textit{stepwise\_agg\textsubscript{mean}} - \textit{weighted\_agg} \newline  
-  5) \textit{direct\_agg\textsubscript{mean}} - \textit{stepwise\_agg\textsubscript{median}} \newline
-  6) \textit{direct\_agg\textsubscript{median}} - \textit{stepwise\_agg\textsubscript{median}} \newline
-  7) \textit{stepwise\_agg\textsubscript{median}} - \textit{weighted\_agg}
-\\
-
-\noindent{\textbf{Figure caption 5:}}
-
 Species scores obtained by RDA from the original analysis (\cite{szocs_effects_2014}), using harmonised grouping features, and using harmonised grouping features with traits aggregated to family level with five different aggregation methods.
@@
 
-\noindent{\textbf{Figure caption 6:}}
+\noindent{\textbf{Figure caption 4:}}
 
-RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{median}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
+RDA of traits constrained by electric conductivity for harmonised but not aggregated data, data aggregated with \textit{stepwise\_agg \textsubscript{median}} (largest difference in terms of responsive traits to salinity to the original study), data aggregated with \textit{direct\_agg \textsubscript{mean}} (smallest difference in terms of responsive traits to salinity to the original study), and the original study.
 Shown are boxplots of the site scores along the conductivity axis.
@@
 For better comparability, species scores of the original analysis were multiplied by -1.
-Results for the other aggregated methods are shown in the supporting information (Figure \ref{fig:boxplots_scores_on_constrained_axis_REMAIN}).
+Results for the other aggregated methods are shown in the Supplementary materials (Figure \ref{fig:boxplots_scores_on_constrained_axis_REMAIN}).
 Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.
